### 2016-10-07 mu/mpxerr.tex
up Dab, ~Dab, and -Dab plots.

\documentclass{article}
\begin{document}

\gdef\mpxshipout{\shipout\hbox\bgroup
  \setbox0=\hbox\bgroup}
\gdef\stopmpxshipout{\egroup  \dimen0=\ht0 \advance\dimen0\dp0
  \dimen1=\ht0 \dimen2=\dp0
  \setbox0=\hbox\bgroup
    \box0
    \ifnum\dimen0>0 \vrule width1sp height\dimen1 depth\dimen2 
    \else \vrule width1sp height1sp depth0sp\relax
    \fi\egroup
  \ht0=0pt \dp0=0pt \box0 \egroup}
\mpxshipout% line 125 ./up-Dxb.mp
-500000%
\stopmpxshipout
\mpxshipout% line 128 ./up-Dxb.mp
-400000%
\stopmpxshipout
\mpxshipout% line 131 ./up-Dxb.mp
-300000%
\stopmpxshipout
\mpxshipout% line 134 ./up-Dxb.mp
-200000%
\stopmpxshipout
\mpxshipout% line 137 ./up-Dxb.mp
-100000%
\stopmpxshipout
\mpxshipout% line 140 ./up-Dxb.mp
0%
\stopmpxshipout
\mpxshipout% line 143 ./up-Dxb.mp
100000%
\stopmpxshipout
\mpxshipout% line 146 ./up-Dxb.mp
200000%
\stopmpxshipout
\mpxshipout% line 149 ./up-Dxb.mp
300000%
\stopmpxshipout
\mpxshipout% line 152 ./up-Dxb.mp
400000%
\stopmpxshipout
\mpxshipout% line 155 ./up-Dxb.mp
500000%
\stopmpxshipout
\mpxshipout% line 159 ./up-Dxb.mp
0%
\stopmpxshipout
\mpxshipout% line 163 ./up-Dxb.mp
0.2%
\stopmpxshipout
\mpxshipout% line 167 ./up-Dxb.mp
0.4%
\stopmpxshipout
\mpxshipout% line 171 ./up-Dxb.mp
0.6%
\stopmpxshipout
\mpxshipout% line 175 ./up-Dxb.mp
0.8%
\stopmpxshipout
\mpxshipout% line 179 ./up-Dxb.mp
1%
\stopmpxshipout
\mpxshipout% line 183 ./up-Dxb.mp
1.2%
\stopmpxshipout
\mpxshipout% line 187 ./up-Dxb.mp
C$_{16}$H$_{8}$-up%
\stopmpxshipout
\mpxshipout% line 189 ./up-Dxb.mp
\Large $\mu^{abcd}(\,J\,s^{-1}\,V^{-2})$%
\stopmpxshipout
\mpxshipout% line 191 ./up-Dxb.mp
{\Large Photon Energy (eV)}%
\stopmpxshipout
\mpxshipout% line 194 ./up-Dxb.mp
D^{xx}%
\stopmpxshipout
% line 262 ./up-Dxb.mp
 \end{document}

\end{document}

### 2017-02-02 mu/mpxerr.tex
Checking most intense responses for v^ab.

@@
   \ht0=0pt \dp0=0pt \box0 \egroup}
-\mpxshipout% line 125 ./up-Dxb.mp
--500000%
+\mpxshipout% line 125 ./intense-responses-mu-all.mp
+-2e-06%
 \stopmpxshipout
-\mpxshipout% line 128 ./up-Dxb.mp
--400000%
+\mpxshipout% line 128 ./intense-responses-mu-all.mp
+-1.8e-06%
 \stopmpxshipout
-\mpxshipout% line 131 ./up-Dxb.mp
--300000%
+\mpxshipout% line 131 ./intense-responses-mu-all.mp
+-1.6e-06%
 \stopmpxshipout
-\mpxshipout% line 134 ./up-Dxb.mp
--200000%
+\mpxshipout% line 134 ./intense-responses-mu-all.mp
+-1.4e-06%
 \stopmpxshipout
-\mpxshipout% line 137 ./up-Dxb.mp
--100000%
+\mpxshipout% line 137 ./intense-responses-mu-all.mp
+-1.2e-06%
 \stopmpxshipout
-\mpxshipout% line 140 ./up-Dxb.mp
+\mpxshipout% line 140 ./intense-responses-mu-all.mp
+-1e-06%
+\stopmpxshipout
+\mpxshipout% line 143 ./intense-responses-mu-all.mp
+-8e-07%
+\stopmpxshipout
+\mpxshipout% line 146 ./intense-responses-mu-all.mp
+-6e-07%
+\stopmpxshipout
+\mpxshipout% line 149 ./intense-responses-mu-all.mp
+-4e-07%
+\stopmpxshipout
+\mpxshipout% line 152 ./intense-responses-mu-all.mp
+-2e-07%
+\stopmpxshipout
+\mpxshipout% line 155 ./intense-responses-mu-all.mp
 0%
 \stopmpxshipout
-\mpxshipout% line 143 ./up-Dxb.mp
-100000%
+\mpxshipout% line 158 ./intense-responses-mu-all.mp
+2e-07%
 \stopmpxshipout
-\mpxshipout% line 146 ./up-Dxb.mp
-200000%
-\stopmpxshipout
-\mpxshipout% line 149 ./up-Dxb.mp
-300000%
-\stopmpxshipout
-\mpxshipout% line 152 ./up-Dxb.mp
-400000%
-\stopmpxshipout
-\mpxshipout% line 155 ./up-Dxb.mp
-500000%
-\stopmpxshipout
-\mpxshipout% line 159 ./up-Dxb.mp
+\mpxshipout% line 162 ./intense-responses-mu-all.mp
 0%
 \stopmpxshipout
-\mpxshipout% line 163 ./up-Dxb.mp
-0.2%
+\mpxshipout% line 166 ./intense-responses-mu-all.mp
+0.5%
 \stopmpxshipout
-\mpxshipout% line 167 ./up-Dxb.mp
-0.4%
-\stopmpxshipout
-\mpxshipout% line 171 ./up-Dxb.mp
-0.6%
-\stopmpxshipout
-\mpxshipout% line 175 ./up-Dxb.mp
-0.8%
-\stopmpxshipout
-\mpxshipout% line 179 ./up-Dxb.mp
+\mpxshipout% line 170 ./intense-responses-mu-all.mp
 1%
 \stopmpxshipout
-\mpxshipout% line 183 ./up-Dxb.mp
-1.2%
+\mpxshipout% line 174 ./intense-responses-mu-all.mp
+1.5%
 \stopmpxshipout
-\mpxshipout% line 187 ./up-Dxb.mp
-C$_{16}$H$_{8}$-up%
+\mpxshipout% line 178 ./intense-responses-mu-all.mp
+2%
 \stopmpxshipout
-\mpxshipout% line 189 ./up-Dxb.mp
-\Large $\mu^{abcd}(\,J\,s^{-1}\,V^{-2})$%
+\mpxshipout% line 182 ./intense-responses-mu-all.mp
+2.5%
 \stopmpxshipout
-\mpxshipout% line 191 ./up-Dxb.mp
+\mpxshipout% line 186 ./intense-responses-mu-all.mp
+3%
+\stopmpxshipout
+\mpxshipout% line 191 ./intense-responses-mu-all.mp
 {\Large Photon Energy (eV)}%
 \stopmpxshipout
-\mpxshipout% line 194 ./up-Dxb.mp
-D^{xx}%
+\mpxshipout% line 194 ./intense-responses-mu-all.mp
+cdse zzzz%
 \stopmpxshipout
-% line 262 ./up-Dxb.mp
+\mpxshipout% line 501 ./intense-responses-mu-all.mp
+gaas xxxxhnbGh-aa/hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xyxx_xyxy_xyxz_xyyx_xyyy_xyyz_xyzx_xyzy_xyzz_14452_75-spin_scissor_0_Nc_32%
+\stopmpxshipout
+% line 814 ./intense-responses-mu-all.mp
  \end{document}

### 2017-02-02 mu/hnbGh-aa/comparing.sh

@@ -1,10 +1,10 @@
 files=( hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32
         hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32 )
 
+counter=0
 for i in ${files[@]}; do
         gnuplot -p <<- EOF
         # p "${i} u 1:2 w l; pause -1"
         p "${i}" u 1:2 w l
-        # pause -1
 EOF
 done

### 2017-02-02 mu/hnbGh-aa/hnbGh-aa-mu-nonzero_diff.sh

@@ -99,63 +99,63 @@ rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy
 # rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32' u 1:($4*k) w l lw 3 # almost zero
 # rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32' u 1:($6*k) w l lw 3 # almost zero
 rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32' u 1:($7*k) w l lw 3
-rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32' u 1:($10*k) w l lw 3
+p 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32' u 1:($10*k) w l lw 3 # intense
 
-rep 'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xyxx_xyxy_xyxz_xyyx_xyyy_xyyz_xyzx_xyzy_xyzz_14452_75-spin_scissor_0_Nc_32' u 1:($2*k) w l lw 3
+p   'hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xyxx_xyxy_xyxz_xyyx_xyyy_xyyz_xyzx_xyzy_xyzz_14452_75-spin_scissor_0_Nc_32' u 1:($2*k) w l lw 3
[…]

### 2017-02-23 checking_maths/checking_maths.tex
Running layer responses.

\documentclass[landscape]{article}

\usepackage[spanish]{babel}
\decimalpoint
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{amsmath}
\usepackage{multicol}
% \usepackage{eurosym}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.12}

\author{Reinaldo Arturo Zapata Pe\~na}
\title{Checking Maths for $\mathcal{V}^{\mathrm{ab}}$} 
\date{}

\begin{document}
\maketitle

The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$ plane
is given by
\begin{align*}
\mathcal{V}^{\mathrm{ab}} 
&= \frac{\mu^{\mathrm{abxx}}E^{2}\cos^{2}\theta + 
\mu^{\mathrm{abyy}}E^{2}\sin^{2}\theta + 
2\mu^{\mathrm{abxy}}E^{2}\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}E^{2}\cos^{2}\theta + \xi^{\mathrm{yy}}E^{2}\sin^{2}\theta}, \\
&= \frac{\mu^{\mathrm{abxx}}\cos^{2}\theta + 
\mu^{\mathrm{abyy}}\sin^{2}\theta + 2\mu^{\mathrm{abxy}}\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}\cos^{2}\theta + \xi^{\mathrm{yy}}\sin^{2}\theta}.
\end{align*}
For an angle $\theta = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align*}
\mathcal{V}^{\mathrm{ab}} 
&= \frac{\mu^{\mathrm{abxx}} + \mu^{\mathrm{abyy}} + 2\mu^{\mathrm{abxy}}}
{\xi^{\mathrm{xx}} + \xi^{\mathrm{yy}}}.
\end{align*}

The input files are

{\tt
\begin{tabular}{lr}
chi1.kk\_xx\_yy\_zz\_\ldots &  {\rm 7 columns} \\
\hline
mu.kk\_xxxx\_xxxy\_xxxz\_xxyx\_xxyy\_xxyz\_xxzx\_xxzy\_xxzz\_\ldots & {\rm 10 columns}\\
mu.kk\_xyxx\_xyxy\_xyxz\_xyyx\_xyyy\_xyyz\_xyzx\_xyzy\_xyzz\_\ldots & \\
mu.kk\_xzxx\_xzxy\_xzxz\_xzyx\_xzyy\_xzyz\_xzzx\_xzzy\_xzzz\_\ldots & \\
mu.kk\_yxxx\_yxxy\_yxxz\_yxyx\_yxyy\_yxyz\_yxzx\_yxzy\_yxzz\_\ldots & \\
mu.kk\_yyxx\_yyxy\_yyxz\_yyyx\_yyyy\_yyyz\_yyzx\_yyzy\_yyzz\_\ldots & \\
mu.kk\_yzxx\_yzxy\_yzxz\_yzyx\_yzyy\_yzyz\_yzzx\_yzzy\_yzzz\_\ldots & \\
\end{tabular}
}

\vspace{0.5cm}
Then I pasted first each \textbf{\tt mu.kk\ldots} followed for the \textbf{\tt
chi1.kk\ldots} file to have 17 column file

\vspace{0.5cm}
{\footnotesize
\begin{tabular}{lcccccccccccccccccc}
& \multicolumn{10}{c}{\tt mu.kk\ldots} & \multicolumn{7}{c}{\tt chi1.kk\ldots} \\
\cline {2-11} \cline{13-19}
&energy & abxx & abxy & abxz & abyx & abyy & abyz & abzx & abzy & abzz & &
energy & Re xx & Im xx & Re yy & Im yy & Re zz & Im zz \\
column: & 1& 2& 3& 4& 5& 6& 7& 8& 9& 10 & & 11& 12& 13& 14& 15& 16& 17\\
\end{tabular}
}

\newpage
I defined the variables
\begin{align*}
&\texttt{coscuad} = \cos^{2}\theta \\
&\texttt{sincuad} = \sin^{2} \theta\\
&\texttt{cossin}  = \cos\theta \sin\theta 
\end{align*}
and used {\tt awk} comand to produce the corresponding \tt{\textbf{v.kk\_ab...}}
file as follows:

\noindent
{\tt awk \textquotesingle\{ print \$1, ((\$2*\textquotesingle
\,``\$coscuad''\textquotesingle + \$6* \textquotesingle\,``\$sincuad''
\textquotesingle + 2* \$3* \textquotesingle\,``\$cossin''\textquotesingle)/(\$13*
\textquotesingle\,``\$coscuad'' \textquotesingle + \$15* \textquotesingle
\,``\$sincuad'' \textquotesingle + 0.00001)) \}\textquotesingle }

\end{document}

### 2017-03-01 gnuplot-vectors/pol_vec-vab.sh
Going home before finishing the 3D polarization plot script.

@@ -1,0 +1,28 @@
+#/bin/bash
+
+scriptname="$(basename $0)"
+
+if [ -z $3 ]; then
+    clear
+    echo -e "\tUsage:"
+    echo -e "\t\t$scriptname [V^{ax} filename] [V^{ay} filename] [V^{az} filename] "
+    echo -e ""
+    echo -e "\t\tfrom the input files V^{ab}, the superscript \"a\" is for the "
+    echo -e "\t\tvelocity and \"b\" for the spin polarization. "
+    echo -e ""
+    exit 0
+fi
+
+vax=$1
+vay=$2
+vaz=$3
+
+# paste $vax $vay $vaz 
+
+# Calculation of the diferences between rows for the energy, V^{ax}, V^{ay}, and V^{az}
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $1-p)} {p=$1}'  > .diffener
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $2-p)} {p=$2}'  > .diffvax
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $4-p)} {p=$4}'  > .diffvay
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
+
+paste $vax $vay $vaz .diffener .diffvax .diffvay .diffvaz #| awk '{printf (%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n )}'

### 2017-03-01 gnuplot-vectors/pol_vec-vab.sh
SAB

@@ -25,4 +25,6 @@ paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $2-p)} {p=$2}'  > .diffvax
 paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $4-p)} {p=$4}'  > .diffvay
 paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
 
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
+
 paste $vax $vay $vaz .diffener .diffvax .diffvay .diffvaz #| awk '{printf (%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n )}'

### 2017-03-01 gnuplot-vectors/pol_vec-vab.sh
sab

@@ -28,3 +28,6 @@ paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
 paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
 
 paste $vax $vay $vaz .diffener .diffvax .diffvay .diffvaz #| awk '{printf (%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n )}'
+
+
+paste cos-sin | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $3, $1-p, $2-q, $3-r)} {p=$1, q=$2, r=$3}'  

### 2017-03-01 gnuplot-vectors/pol_vec-vab.sh
Need to check final plot.

@@ -20,14 +20,11 @@ vaz=$3
 # paste $vax $vay $vaz 
 
 # Calculation of the diferences between rows for the energy, V^{ax}, V^{ay}, and V^{az}
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $1-p)} {p=$1}'  > .diffener
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $2-p)} {p=$2}'  > .diffvax
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $4-p)} {p=$4}'  > .diffvay
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E\n", $1-p, $2-q, $4-r, $6-s)} {p=$1} {q=$2} {r=$4} {r=$6}' | sed  '$ d' > .diff
+paste $vax $vay $vaz .diff | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6), $7, $8, $9 )}' > output
 
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E\n", $6-p)} {p=$6}'  > .diffvaz
-
-paste $vax $vay $vaz .diffener .diffvax .diffvay .diffvaz #| awk '{printf (%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n )}'
+rm .diff
 
 
-paste cos-sin | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $3, $1-p, $2-q, $3-r)} {p=$1, q=$2, r=$3}'  
+# paste cos-sin | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $3, $1-p, $2-q, $3-r)} {p=$1} {q=$2} {r=$3}'  
+# paste cos-sin | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E\n", $1-p, $2-q, $3-r)} {p=$1} {q=$2} {r=$3}' | sed  '$ d' > temp

### 2017-03-01 gnuplot-vectors/pol_vec-vab.sh
Test of polarization almost finished
Test of polarization vectors in 3D plot almost finished using
V^{ab} for the up structure.

@@ -9,6 +9,16 @@ if [ -z $3 ]; then
     echo -e ""
     echo -e "\t\tfrom the input files V^{ab}, the superscript \"a\" is for the "
     echo -e "\t\tvelocity and \"b\" for the spin polarization. "
+    echo -e "\t\tThe output file contains 9 columns corresponding to:"
+    echo -e "\t\t  1: Energy"
+    echo -e "\t\t  2: V^{ax}"
+    echo -e "\t\t  3: V^{ay}"
+    echo -e "\t\t  4: V^{az}"
+    echo -e "\t\t  5: sqrt [(V^{ax})^2 + (V^{ay})^2 + (V^{az})^2]"
+    echo -e "\t\t  6: Difference between consecutive rows of energy."
+    echo -e "\t\t  7: Difference between consecutive rows of V^{ax}."
+    echo -e "\t\t  8: Difference between consecutive rows of V^{ay}."
+    echo -e "\t\t  9: Difference between consecutive rows of V^{az}."
     echo -e ""
     exit 0
 fi
@@ -17,11 +27,10 @@ vax=$1
 vay=$2
 vaz=$3
 
-# paste $vax $vay $vaz 
 
 # Calculation of the diferences between rows for the energy, V^{ax}, V^{ay}, and V^{az}
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E\n", $1-p, $2-q, $4-r, $6-s)} {p=$1} {q=$2} {r=$4} {r=$6}' | sed  '$ d' > .diff
-paste $vax $vay $vaz .diff | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6), $7, $8, $9 )}' > output
+paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E\n", $1-p, $2-q, $4-r, $6-s)} {p=$1} {q=$2} {r=$4} {r=$6}'  > .diff
+paste $vax $vay $vaz .diff | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6), $7, $8, $9, $10 )}' > output
 
 rm .diff
 

### 2017-03-02 gnuplot-3d_vectors/pol_vec-vab.sh
Manig final test plots

@@ -1,0 +1,33 @@
+#/bin/bash
+
+scriptname="$(basename $0)"
+
+if [ -z $3 ]; then
+    clear
+    echo -e "\tUsage:"
+    echo -e "\t\t$scriptname [V^{ax} filename] [V^{ay} filename] [V^{az} filename] [output filename]"
+    echo -e ""
+    echo -e "\t\tFrom the input files V^{ab}, the superscript \"a\" is for the "
+    echo -e "\t\tvelocity and \"b\" for the spin polarization. "
+    echo -e "\t\tThe output file contains 5 columns corresponding to:"
+    echo -e "\t\t  1: Energy"
+    echo -e "\t\t  2: V^{ax}"
+    echo -e "\t\t  3: V^{ay}"
+    echo -e "\t\t  4: V^{az}"
+    echo -e "\t\t  5: sqrt [(V^{ax})^2 + (V^{ay})^2 + (V^{az})^2]"
+    echo -e ""
+    exit 0
+fi
+
+vax=$1
+vay=$2
+vaz=$3
+out=$4
+
+if [ -z $out ]; then
+    out=output-vav
+fi
+
+
+paste $vax $vay $vaz | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) )}' > $out
+

### 2017-03-02 gnuplot-vectors/pol_vec-vab.sh

@@ -1,38 +1,0 @@
-#/bin/bash
-
-scriptname="$(basename $0)"
-
-if [ -z $3 ]; then
-    clear
-    echo -e "\tUsage:"
-    echo -e "\t\t$scriptname [V^{ax} filename] [V^{ay} filename] [V^{az} filename] "
-    echo -e ""
-    echo -e "\t\tFrom the input files V^{ab}, the superscript \"a\" is for the "
-    echo -e "\t\tvelocity and \"b\" for the spin polarization. "
-    echo -e "\t\tThe output file contains 9 columns corresponding to:"
-    echo -e "\t\t  1: Energy"
-    echo -e "\t\t  2: V^{ax}"
-    echo -e "\t\t  3: V^{ay}"
-    echo -e "\t\t  4: V^{az}"
-    echo -e "\t\t  5: sqrt [(V^{ax})^2 + (V^{ay})^2 + (V^{az})^2]"
-    echo -e "\t\t  6: Difference between consecutive rows of energy."
-    echo -e "\t\t  7: Difference between consecutive rows of V^{ax}."
-    echo -e "\t\t  8: Difference between consecutive rows of V^{ay}."
-    echo -e "\t\t  9: Difference between consecutive rows of V^{az}."
-    exit 0
-fi
-
-vax=$1
-vay=$2
-vaz=$3
-
-
-# Calculation of the diferences between rows for the energy, V^{ax}, V^{ay}, and V^{az}
-paste $vax $vay $vaz | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E\n", $1-p, $2-q, $4-r, $6-s)} {p=$1} {q=$2} {r=$4} {r=$6}'  > .diff
-paste $vax $vay $vaz .diff | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6), $7, $8, $9, $10 )}' > output
-
-rm .diff
-
-
-# paste cos-sin | awk 'NR>1{printf("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $3, $1-p, $2-q, $3-r)} {p=$1} {q=$2} {r=$3}'  
[…]

### 2017-03-05 gnuplot-3d_vectors/pol_vec-vab.sh
Making 3D energy, theta, phi plots.

@@ -1,33 +1,0 @@
-#/bin/bash
-
-scriptname="$(basename $0)"
-
-if [ -z $3 ]; then
-    clear
-    echo -e "\tUsage:"
-    echo -e "\t\t$scriptname [V^{ax} filename] [V^{ay} filename] [V^{az} filename] [output filename]"
-    echo -e ""
-    echo -e "\t\tFrom the input files V^{ab}, the superscript \"a\" is for the "
-    echo -e "\t\tvelocity and \"b\" for the spin polarization. "
-    echo -e "\t\tThe output file contains 5 columns corresponding to:"
-    echo -e "\t\t  1: Energy"
-    echo -e "\t\t  2: V^{ax}"
-    echo -e "\t\t  3: V^{ay}"
-    echo -e "\t\t  4: V^{az}"
-    echo -e "\t\t  5: sqrt [(V^{ax})^2 + (V^{ay})^2 + (V^{az})^2]"
-    echo -e ""
-    exit 0
-fi
-
-vax=$1
-vay=$2
-vaz=$3
-out=$4
-
-if [ -z $out ]; then
-    out=output-vav
-fi
-
-
-paste $vax $vay $vaz | awk '{printf ("%1.6E   %1.6E   %1.6E   %1.6E   %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) )}' > $out
-

### 2017-03-08 mu/alt/alt-scripts/alt-vab-angles.sh
V^{ab} for angles from 0 to 180 with 5deg steps.

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+angles=( 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${angles[@]}; do
+    vab.sh 14452 65 0 32 0.03 "$i"
+done

### 2017-03-08 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-layers.sh

@@ -1,0 +1,24 @@
+#!/bin/bash
+
+############################## T O   C H A N G E ###############################
+strc=
+kpts=
+pws=
+layers=( 1 2 3 4 5 6 )
+################################################################################
+
+for i in ${layers[@]}; do
+    START=$(date)
+
+    chose_layers.sh $i
+    echo -e "\n\n\n"
+    sleep 20
+    run_tiniba.sh -r run -k "$kpts" -N 1 -x 2 -C 12 -P "$pws" -c
+    clear
+
+    END=$(date)
+    ssh cassandra "echo -e 'Calculations completed: layer $i for $strc \nStarted at $START \nFinished at $END \n\nArray of layers: \n${layers[@]} ' | mail -s 'layer $i for $strc' reychino@gmail.com"
+
+done
+
+run_tiniba.sh -r erase

### 2017-03-08 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-res.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+layers=( 1 2 3 4 5 6 )
+
+
+for i in ${layers[@]}; do    
+    clear
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xxxx xxxy xxxz xxyx xxyy xxyz xxzx xxzy xxzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xyxx xyxy xyxz xyyx xyyy xyyz xyzx xyzy xyzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xzxx xzxy xzxz xzyx xzyy xzyz xzzx xzzy xzzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yxxx yxxy yxxz yxyx yxyy yxyz yxzx yxzy yxzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yyxx yyxy yyxz yyyx yyyy yyyz yyzx yyzy yyzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yzxx yzxy yzxz yzyx yzyy yzyz yzzx yzzy yzzz" -b 0.03
+    #all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zxxx zxxy zxxz zxyx zxyy zxyz zxzx zxzy zxzz" -b 0.03
+    #all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zyxx zyxy zyxz zyyx zyyy zyyz zyzx zyzy zyzz" -b 0.03
+    #all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zzxx zzxy zzxz zzyx zzyy zzyz zzzx zzzy zzzz" -b 0.03
+done

### 2017-03-08 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-angles.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+angles=( 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${angles[@]}; do
+    vab.sh 14452 75 0 32 0.03 "$i"
+done

### 2017-03-08 mu/alt/alt-scripts/alt-magvab-inang.sh
Datafiles for |V^{ab}| and incidence angle completed.

@@ -1,0 +1,41 @@
+#!/bin/bash
+
+
+outputxkk=magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magv.kk_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputxkk=( v.kk_xx_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.kk_xy_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.kk_xz_14452_65-spin_scissor_0_Nc_32_ang_ )
+inputxsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xy_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xz_14452_65-spin_scissor_0_Nc_32_ang_ )
+
+
+
+
+
+outputykk=magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magv.kk_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputykk=( v.kk_yx_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.kk_yy_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.kk_yz_14452_65-spin_scissor_0_Nc_32_ang_ )
+inputysm=( v.sm_0.03_yx_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yy_14452_65-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_ )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+for i in ${angles[@]}; do
[…]

### 2017-03-08 mu/alt/alt-scripts/alt-vab-angles.sh

@@ -1,7 +1,0 @@
-#!/bin/bash
-
-angles=( 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
-
-for i in ${angles[@]}; do
-    vab.sh 14452 65 0 32 0.03 "$i"
-done

### 2017-03-08 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-magvab-inang.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+
+outputxkk=magv.sm_0.03_xb_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magv.kk_xb_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputxkk=( v.kk_xx_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.kk_xy_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.kk_xz_14452_75-spin_scissor_0_Nc_32_ang_ )
+inputxsm=( v.sm_0.03_xx_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xy_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xz_14452_75-spin_scissor_0_Nc_32_ang_ )
+
+
+
+
+
+outputykk=magv.sm_0.03_yb_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magv.kk_yb_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputykk=( v.kk_yx_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.kk_yy_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.kk_yz_14452_75-spin_scissor_0_Nc_32_ang_ )
+inputysm=( v.sm_0.03_yx_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yy_14452_75-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yz_14452_75-spin_scissor_0_Nc_32_ang_ )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+for i in ${angles[@]}; do
[…]

### 2017-03-08 mu/up/up-scripts/up-magvab-inang.sh

@@ -1,0 +1,41 @@
+#!/bin/bash
+
+
+outputxkk=magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magv.kk_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputxkk=( v.kk_xx_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.kk_xy_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.kk_xz_12802_40-spin_scissor_0_Nc_32_ang_ )
+inputxsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xy_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_xz_12802_40-spin_scissor_0_Nc_32_ang_ )
+
+
+
+
+
+outputykk=magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magv.kk_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputykk=( v.kk_yx_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.kk_yy_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.kk_yz_12802_40-spin_scissor_0_Nc_32_ang_ )
+inputysm=( v.sm_0.03_yx_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yy_12802_40-spin_scissor_0_Nc_32_ang_  
+           v.sm_0.03_yz_12802_40-spin_scissor_0_Nc_32_ang_ )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+for i in ${angles[@]}; do
[…]

### 2017-03-08 mu/up/up-scripts/up-absvab-anginc-3D.sh
-

@@ -1,0 +1,6 @@
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${angles[@]}; do
+    paste v.sm_0.03_yx_12802_40-spin_scissor_0_Nc_32_ang_"$i" v.sm_0.03_yy_12802_40-spin_scissor_0_Nc_32_ang_"$i" v.sm_0.03_yz_12802_40-spin_scissor_0_Nc_32_ang_"$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4 + $6*$6),  00 }' >>  up-absvyz-anginc-3D
+done

### 2017-03-14 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-layers.sh
Starting layers for ab structure. See full commit.
There was an error trying to make the layers with the current unit cell:

-5.493523078    -0.000012783    9.013134903
-5.490765917     0.000006198    7.031903998
-2.747804419     0.000006198    6.046251835
-2.744858933    -0.000005757    3.009985643
-0.002169046     0.000003422    2.122751619
 0.000000000     0.000000000    0.000000000

because rlayer.sh was not working with x negative components.

To solve temporary this issue I made a test in the aa structure for which rlayer.sh
worked properly. I moved all the structure in the x direction m

@@ -1,0 +1,24 @@
+#!/bin/bash
+
+############################## T O   C H A N G E ###############################
+strc=ab
+kpts=14452
+pws=9111
+layers=( 1 2 3 4 5 6 )
+################################################################################
+
+for i in ${layers[@]}; do
+    START=$(date)
+
+    chose_layers.sh $i
+    echo -e "\n\n\n"
+    sleep 20
+    run_tiniba.sh -r run -k "$kpts" -N 1 -x 2 -C 12 -P "$pws" -c
+    clear
+
+    END=$(date)
+    ssh cassandra "echo -e 'Calculations completed: layer $i for $strc \nStarted at $START \nFinished at $END \n\nArray of layers: \n${layers[@]} ' | mail -s 'layer $i for $strc' reychino@gmail.com"
+
+done
+
+run_tiniba.sh -r erase

### 2017-03-14 mu/structures-report/structures-report.tex
making a report

\documentclass{article}

% \usepackage{fullpage}
\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}

\title{Structures Report}
\author{Reinaldo Zapata}
\date{}

\pagestyle{empty}
\thispagestyle{empty}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Up} % (fold)
\label{sec:up}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:upmagvxbincang1}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components.}
    \label{fig:xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:upvxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

\subsection{$\mathcal{V}^{\mathrm{yb}} $: energy range: 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:upmagvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yz-angcomp.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb1}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 1.8--2.1 eV }

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:upmagxbincang2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:upvxb2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:upmagybincang2}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb2}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$|\mathcal{V}^{\mathrm{ab}}|$ energy range 0.0--0.2 eV: angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-1.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-1.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:uprtp1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-1.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:uplay1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-1.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:upcomp1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$|\mathcal{V}^{\mathrm{ab}}|$ energy range 1.8--2.1 eV: angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-2.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-2.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:uprtp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-2.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:uplay2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-2.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:upcomp2}
\end{figure}

% section up (end)

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{alt} % (fold)
\label{sec:alt}

\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 0.6--1.0 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:upmagvxbincang1}
\end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
%     \caption{Cheking angle of incidence for $xb$ components.}
%     \label{fig:xbangcomp}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
%     \label{fig:upvxb1}
% \end{figure}

% section alt (end)

\end{document}

### 2017-03-14 mu/structures-report/structures-report.tex
Report continue

@@
 
-% \usepackage{fullpage}
 \usepackage{geometry}
@@
 \usepackage{subfigure}
+
+\usepackage[section]{placeins}
+\let\Oldsection\section
+\renewcommand{\section}{\FloatBarrier\Oldsection}
+\let\Oldsubsection\subsection
+\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}
+\let\Oldsubsubsection\subsubsection
+\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}
 
@@
     40$^{\circ}$.}
-    \label{fig:upmagvxbincang1}
+    \label{fig:up-magvxbincang1}
 \end{figure}
@@
     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
-    \caption{Cheking angle of incidence for $xb$ components.}
-    \label{fig:xbangcomp}
+    \caption{Cheking angle of incidence for $xb$ components for up structure.}
+    \label{fig:up-xbangcomp}
 \end{figure}
@@
     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
-    \label{fig:upvxb1}
+    \label{fig:up-vxb1}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
 
@@
     40$^{\circ}$.}
-    \label{fig:upmagvybincang1}
+    \label{fig:up-magvybincang1}
 \end{figure}
@@
     \caption{Cheking angle of incidence for $yb$ components.}
-    \label{fig:ybangcomp}
+    \label{fig:up-ybangcomp}
 \end{figure}
@@
     \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
-    \label{fig:upvyb1}
+    \label{fig:up-vyb1}
 \end{figure}
-
-\clearpage
 
@@
     40$^{\circ}$.}
-    \label{fig:upmagxbincang2}
+    \label{fig:up-magxbincang2}
 \end{figure}
@@
     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
-    \label{fig:upvxb2}
+    \label{fig:up-vxb2}
 \end{figure}
@@
     40$^{\circ}$.}
-    \label{fig:upmagybincang2}
+    \label{fig:up-magybincang2}
 \end{figure}
@@
     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-    \label{fig:uprtp1}
+    \label{fig:up-rtp1}
 \end{figure}
@@
     $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:uplay1}
+    \label{fig:up-lay1}
 \end{figure}
@@
     responses of CdSe and GaAs.}
-    \label{fig:upcomp1}
+    \label{fig:up-comp1}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$|\mathcal{V}^{\mathrm{ab}}|$ energy range 1.8--2.1 eV: angles
-$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs}
+\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
+range of 1.8--2.1 eV}
 
@@
     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-    \label{fig:uprtp2}
+    \label{fig:up-rtp2}
 \end{figure}
@@
     $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:uplay2}
+    \label{fig:up-lay2}
 \end{figure}
@@
     responses of CdSe and GaAs.}
-    \label{fig:upcomp2}
+    \label{fig:up-comp2}
 \end{figure}
@@
 % section up (end)
-
-\clearpage
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 0.6--1.0 eV }
-\begin{figure}[h]
+\begin{figure}[h!]
     \centering
@@
     \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
-    40$^{\circ}$.}
-    \label{fig:upmagvxbincang1}
+    145$^{\circ}$.}
+    \label{fig:alt-magvxbincang1}
 \end{figure}
-% \begin{figure}[h]
-%     \centering
-%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
-%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
-%     \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
-%     \caption{Cheking angle of incidence for $xb$ components.}
-%     \label{fig:xbangcomp}
-% \end{figure}
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
-%     \label{fig:upvxb1}
-% \end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
+    \caption{Cheking angle of incidence for $xb$ components.}
+    \label{fig:alt-xbangcomp}
+\end{figure}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
+    \label{fig:alt-vxb1}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{V}^{\mathrm{yb}} $: energy range: 0.6--1.0 eV }
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    145$^{\circ}$.}
+    \label{fig:alt-magvybincang1}
+\end{figure}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
+    \caption{Cheking angle of incidence for $yb$ components.}
+    \label{fig:alt-ybangcomp}
+\end{figure}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
+    \label{fig:alt-vyb1}
+\end{figure}
+
+\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
 

### 2017-03-14 mu/info-plots.sh

@@ -1,0 +1,45 @@
+
+set colors classic
+unset key
+set ticslevel 0
+set hidden3d
+
+set view 45,45
+set ytics 30
+
+pf=29.98        # prefactor
+sl=299792.458   # speed of light
+f=pf*sl
+
+set xrange [0.0:0.2] # up
+set xrange [1.8:2.1] # up
+
+set xrange [0.6:1.8] # alt
+
+set xrange [0.5:2.7] # aa & ab
+
+set title 'V^{xb}' font ",20"
+sp 'magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5' u 1:($3*f):2 w l lw 1.5 lt 7
+
+set title 'V^{yb}' font ",20"
+sp 'magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5' u 1:($3*f):2 w l lw 1.5 lt 7
+
+
+
+plot '1.dat' using 1:($3==0?$2:1/0)
+
+
+set view 89,90
+response angles:
+up 40º:
+    xb: [0.0:0.2] ~ 60 Km/s; [0.0:0.2] ~ 09 Km/s
+    yb: [1.8:2.1] ~ 90 Km/s; [1.8:2.1] ~ 50 Km/s
+alt 150º:
+    xb: [0.6:1.8] ~ 32 Km/s
+    yb: [0.6:1.8] ~ 52 Km/s
+aa 140º (x) & 175º (y):
+    xb [0.5:2.7] ~ 10.5Km/s
+    yb [0.5:2.7] ~ 11 Km/s
+ab 150º:
+    xb [0.5:2.7] ~ 2.6Km/s
+    yb [0.5:2.7] ~ 

### 2017-03-15 mu/structures-report/structures-report.tex
Alt report completed.
aa structure report completed.

@@
 
-\pagestyle{empty}
-\thispagestyle{empty}
-
 \begin{document}
@@
 
-\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 0.0--0.2 eV }
+\subsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
 \begin{figure}[h]
@@
 
-\subsection{$\mathcal{V}^{\mathrm{yb}} $: energy range: 0.0--0.2 eV }
+\subsection{$\mathcal{V}^{\mathrm{yb}}$ energy range 0.0--0.2 eV }
 \begin{figure}[h]
@@
 
-\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 1.8--2.1 eV }
+\subsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 1.8--2.1 eV }
 
@@
 %%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$|\mathcal{V}^{\mathrm{ab}}|$ energy range 0.0--0.2 eV: angles
-$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs}
+\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
+range of 0.0--0.2 eV.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$\mathcal{V}^{\mathrm{xb}} $: energy range: 0.6--1.0 eV }
+\subsection{$\mathcal{V}^{\mathrm{xb}}$}
 \begin{figure}[h!]
@@
     145$^{\circ}$.}
-    \label{fig:alt-magvxbincang1}
+    \label{fig:alt-magvxbincang}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{$\mathcal{V}^{\mathrm{yb}} $: energy range: 0.6--1.0 eV }
+\subsection{$\mathcal{V}^{\mathrm{yb}}$}
 \begin{figure}[h]
@@
 
+%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
 $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
+    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+    \label{fig:alt-rtp}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vyz-layers.pdf}
+    \caption{Layer decomposition for the most intense response:
+    $\mathcal{V}^{\mathrm{yz}}$.}
+    \label{fig:alt-lay}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-comp.pdf}
+    \caption{Comparisson of the most intense response vs the most intense
+    responses of CdSe and GaAs.}
+    \label{fig:alt-comp}
+\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{aa} % (fold)
+\label{sec:aa}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{V}^{\mathrm{xb}} $}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+    155$^{\circ}$.}
+    \label{fig:aa-magvxbincang}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxx.pdf}
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxz.pdf}
+    \caption{Cheking angle of incidence for $xb$ components. There is a
+    different angle for each component to have the most intense response.}
+    \label{fig:aa-xbangcomp}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
+    polarization angles.}
+    \label{fig:aa-magvxb}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
+    \label{fig:aa-vxb1}
+\end{figure}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{V}^{\mathrm{yb}} $}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    155$^{\circ}$.}
+    \label{fig:aa-magvybincang}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyx.pdf}
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyz.pdf}
+    \caption{Cheking angle of incidence for $yb$ components. There is a
+    different angle for each component to have the most intense response.}
+    \label{fig:aa-ybangcomp}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
+    polarization angles.}
+    \label{fig:aa-magvyb}
+\end{figure}
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-2.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 175$^{\circ}$.}
+    \label{fig:aa-vyb2}
+\end{figure}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
+    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
+    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+    \label{fig:aa-rtp}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
+    \caption{Layer decomposition for the most intense response:
+    $\mathcal{V}^{\mathrm{yz}}$.}
+    \label{fig:aa-lay}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vab-comp.pdf}
+    \caption{Comparisson of the most intense response vs the most intense
+    responses of CdSe and GaAs.}
+    \label{fig:aa-comp}
+\end{figure}
+
+% section aa (end)
+
 \end{document}

### 2017-03-15 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-calvab.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-an=180   # Pol. angle of incoming light
+an=175   # Pol. angle of incoming light
 layers=(1 2 3 4 5 6)
 kp=14452
 ec=75

### 2017-03-15 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-rtp.sh

@@ -1,6 +1,6 @@
 #/bin/bash
 
-an=180
+an=175
 
 kp=14452
 ec=75

### 2017-03-15 mu/structures-report/structures-report.tex
Report almost finished. Need fix minimal issues.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AB %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{ab} % (fold)
+\label{sec:ab}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{V}^{\mathrm{xb}} $}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+    155$^{\circ}$.}
+    \label{fig:ab-magvxbincang}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
+    \caption{Cheking angle of incidence for $xb$ components. There is a
+    different angle for each component to have the most intense response.}
+    \label{fig:ab-xbangcomp}
+\end{figure}
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
+    polarization angles.}
+    \label{fig:ab-magvxb}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
+    \label{fig:ab-vxb}
+\end{figure}
+
+\clearpage
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$\mathcal{V}^{\mathrm{yb}} $}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    155$^{\circ}$.}
+    \label{fig:ab-magvybincang}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyx.pdf}
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyy.pdf}\\
+    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyz.pdf}
+    \caption{Cheking angle of incidence for $yb$ components. There is a
+    different angle for each component to have the most intense response.}
+    \label{fig:ab-ybangcomp}
+\end{figure}
+
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
+    polarization angles.}
+    \label{fig:ab-magvyb}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 125$^{\circ}$.}
+    \label{fig:ab-vyb}
+\end{figure}
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
+    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+    \label{fig:ab-rtp}
+\end{figure}
+
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
+%     \caption{Layer decomposition for the most intense response:
+%     $\mathcal{V}^{\mathrm{yz}}$.}
+%     \label{fig:aa-lay}
+% \end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vab-comp.pdf}
+    \caption{Comparisson of the most intense response vs the most intense
+    responses of CdSe and GaAs.}
+    \label{fig:ab-comp}
+\end{figure}
+
+% section ab (end)
+
 \end{document}

### 2017-03-15 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-vab-rtp.sh
minimal changes

@@ -1,6 +1,6 @@
 #/bin/bash
 
-an=115
+an=125
 
 kp=14452
 ec=75

### 2017-03-22 mu/structures-report/structures-report.tex
minimal changes
Starting bands
sab
Almost finishing report.
Making bands.

@@
 \usepackage{subfigure}
+\usepackage[inline  ]{showlabels}
 
@@
 
-\section{Up} % (fold)
+\section{Up (graphone)} % (fold)
 \label{sec:up}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{../up/up-figures/up-1}
+    \includegraphics[width=0.45\textwidth]{../up/up-figures/up-2}
+    \caption{Up structure}
+    \label{fig:upstruc}
+\end{figure}
 
@@
     \label{fig:up-vyb1}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \label{fig:up-xbybcomp-1}
 \end{figure}
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
+    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \label{fig:up-xbybcomp-2}
+\end{figure}
+
 % section up (end)
@@
 \label{sec:alt}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.45\textwidth]{../alt/alt-figures/alt-1}
+    \includegraphics[width=0.45\textwidth]{../alt/alt-figures/alt-2}
+    \caption{Alt structure.}
+    \label{fig:altstruc}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \label{fig:alt-xbybcomp}
+\end{figure}
+
 % section alt (end)
@@
 
-\section{aa} % (fold)
-\label{sec:aa}
+\section{HNBC$_{2}$H-aa} % (fold)
+% \label{sec:aa}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.3\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
+    \caption{HNBC$_{2}$H-aa structure}
+    \label{fig:aastruc}
+\end{figure}
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
+    \label{fig:aa-xbybcomp}
+\end{figure}
+
 % section aa (end)
@@
 
-\section{ab} % (fold)
+\section{HNBC$_{2}$H-ab} % (fold)
 \label{sec:ab}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.3\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
+    \caption{HNBC$_{2}$H-ab structure}
+    \label{fig:abstruc}
+\end{figure}
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb.pdf}
     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
@@
 
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
-%     \caption{Layer decomposition for the most intense response:
-%     $\mathcal{V}^{\mathrm{yz}}$.}
-%     \label{fig:aa-lay}
-% \end{figure}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
+    \caption{Layer decomposition for the most intense response:
+    $\mathcal{V}^{\mathrm{yz}}$.}
+    \label{fig:aa-lay}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
+    \label{fig:ab-xbybcomp}
+\end{figure}
+
 % section ab (end)

### 2017-03-27 mu/info-plots.sh
Making band structures.

@@ -1,45 +1,0 @@
-
-set colors classic
-unset key
-set ticslevel 0
-set hidden3d
-
-set view 45,45
-set ytics 30
-
-pf=29.98        # prefactor
-sl=299792.458   # speed of light
-f=pf*sl
-
-set xrange [0.0:0.2] # up
-set xrange [1.8:2.1] # up
-
-set xrange [0.6:1.8] # alt
-
-set xrange [0.5:2.7] # aa & ab
-
-set title 'V^{xb}' font ",20"
-sp 'magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5' u 1:($3*f):2 w l lw 1.5 lt 7
-
-set title 'V^{yb}' font ",20"
-sp 'magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5' u 1:($3*f):2 w l lw 1.5 lt 7
-
-
-
-plot '1.dat' using 1:($3==0?$2:1/0)
-
-
-set view 89,90
-response angles:
-up 40º:
-    xb: [0.0:0.2] ~ 60 Km/s; [0.0:0.2] ~ 09 Km/s
-    yb: [1.8:2.1] ~ 90 Km/s; [1.8:2.1] ~ 50 Km/s
-alt 150º:
-    xb: [0.6:1.8] ~ 32 Km/s
-    yb: [0.6:1.8] ~ 52 Km/s
-aa 140º (x) & 175º (y):
-    xb [0.5:2.7] ~ 10.5Km/s
-    yb [0.5:2.7] ~ 11 Km/s
-ab 150º:
-    xb [0.5:2.7] ~ 2.6Km/s
-    yb [0.5:2.7] ~ 

### 2017-03-29 mu/alt/alt-scripts/alt-layers.sh
Checking layers sum

@@ -4,7 +4,8 @@
 strc=alt
 kpts=14452
 pws=10174
-layers=( 1 2 3 4 )
+# layers=( 1 2 3 4 )
+layers=( 1 2 3 4 5 6 )
 ################################################################################
 
 for i in ${layers[@]}; do

### 2017-03-29 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-res.sh
Making correction in Vyb for ab structre

@@ -3,15 +3,21 @@
 layers=( 1 2 3 4 5 6 )
 
 
+# for i in ${layers[@]}; do    
+#     clear
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xxxx xxxy xxxz xxyx xxyy xxyz xxzx xxzy xxzz" -b 0.03
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xyxx xyxy xyxz xyyx xyyy xyyz xyzx xyzy xyzz" -b 0.03
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xzxx xzxy xzxz xzyx xzyy xzyz xzzx xzzy xzzz" -b 0.03
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yxxx yxxy yxxz yxyx yxyy yxyz yxzx yxzy yxzz" -b 0.03
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yyxx yyxy yyxz yyyx yyyy yyyz yyzx yyzy yyzz" -b 0.03
+#     all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yzxx yzxy yzxz yzyx yzyy yzyz yzzx yzzy yzzz" -b 0.03
+#     #all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zxxx zxxy zxxz zxyx zxyy zxyz zxzx zxzy zxzz" -b 0.03
+#     #all_responses.sh -w layer -m 14452_"$i"_75-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zyxx zyxy zyxz zyyx zyyy zyyz zyzx zyzy zyzz" -b 0.03
[…]

### 2017-03-29 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-rtp.sh
Almost finishing things to fix

@@ -1,6 +1,6 @@
 #/bin/bash
 
-an=175
+an=085
 
 kp=14452
 ec=75

### 2017-03-29 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-vab-rtp.sh

@@ -1,6 +1,6 @@
 #/bin/bash
 
-an=125
+an=085
 
 kp=14452
 ec=75

### 2017-03-30 mu/hnbGh-aa/comparing.sh
Finishing all plots

@@ -1,10 +1,0 @@
-files=( hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32
-        hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_14452_75-spin_scissor_0_Nc_32 )
-
-counter=0
-for i in ${files[@]}; do
-        gnuplot -p <<- EOF
-        # p "${i} u 1:2 w l; pause -1"
-        p "${i}" u 1:2 w l
-EOF
-done

### 2017-04-02 mu/structures-report/structures-report.tex
Making chi layer by layer
mag inc alg color zones completed for all structures.
aa and ab atomic structures completed

@@
 \label{sec:up}
-
+figure
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 \subsection{$\mathcal{V}^{\mathrm{xb}}$}
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
@@
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
@@
 \subsection{$\mathcal{V}^{\mathrm{yb}}$}
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
+    \includegraphics[width=0.45\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-1}
+    \includegraphics[width=0.45\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
     \caption{HNBC$_{2}$H-aa structure}
@@
 \subsection{$\mathcal{V}^{\mathrm{xb}} $}
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
+    \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
+    \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
     \caption{HNBC$_{2}$H-ab structure}
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
-    \caption{Layer decomposition for the most intense response:
-    $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:aa-lay}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=0.7\textwidth]{}
+%     \caption{Layer decomposition for the most intense response:
+%     $\mathcal{V}^{\mathrm{yz}}$.}
+%     \label{fig:ab-lay}
+% \end{figure}
 

### 2017-04-03 mu/article/article.tex
Article started. Continue with response descriptions.

\documentclass[]{article}
% \documentclass[twocolumn]{article}

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[inline  ]{showlabels}

\usepackage[section]{placeins}
\let\Oldsection\section
\renewcommand{\section}{\FloatBarrier\Oldsection}
\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}
\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na,
Bernardo S. Mendoza,
Anatoli I. Shkrebtii}
\date{}

\begin{document}
\maketitle

\section{Introuction} % (fold)
\label{sec:introuction}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/altstruc1}\hspace{0.05\textwidth}
    \includegraphics[width=0.45\textwidth]{figures/altstruc2}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/upstruc1}\hspace{0.05\textwidth}
    \includegraphics[width=0.45\textwidth]{figures/upstruc2}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-1}\hspace{0.05\textwidth}
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-1}\hspace{0.05\textwidth}
%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% % section introuction (end)

\section{Theory} % (fold)
\label{sec:theory}
The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
plane is given by
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)E^{2}(\omega)\cos^{2}\theta + 
\mu^{\mathrm{abyy}}(\omega)E^{2}(\omega)\sin^{2}\theta + 
2\mu^{\mathrm{abxy}}(\omega)E^{2}(\omega)\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}(\omega)E^{2}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)E^{2}(\omega)\sin^{2}\theta},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}\theta + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}\theta + 2\mu^{\mathrm{abxy}}(\omega)\cos\theta\sin\theta }
{\xi^{\mathrm{xx}}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)\sin^{2}\theta}.
\label{eq:vab}
\end{align}
For an angle $\theta = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:vab-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left(  \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang} \\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi. \\ 
\label{eq:azimuthal-ang} 
\end{align}

% section theory (end)

\section{Results} % (fold)
\label{sec:results}

We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
noncentrosymmetric semi-infinite carbon systems with 50\% hydrogenation in
different arrangements. The \emph{alt} system has alternating hydrogen atoms on
the upper and bottom sides of the carbon sheet, while the \emph{up} system has H
only on the upper side. We take the hexagonal carbon lattice to be on the $xy$
plane for both structures, and the carbon-hydrogen bonds on the perpendicular
$xz$ plane, as depicted in Figs.
\ref{fig:altstruc} and \ref{fig:upstruc}.

Using the ABINIT code \cite{gonzeCPC09} we calculated the self- consistent
ground state and the Kohn-Sham states using density functional theory in the
local density approximation (DFT-LDA) with a planewave basis. We used
Hartwigsen- Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction for
calculating $\mathcal{V}^{\mathrm{a}}(\omega)$.

The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures. As mentioned in
\cite{zapataPSB2016}, using DFT the LDA is only one method of many other that
can be used to calculate the electronic structure of materials. Also it is known
that all methods predict a different band gap than the obtained in the
experiment. A correction for the band gap energy value can be calculated by
other \emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02}
being this outside the scope of this paper.

The structures presented here where divided into layers to analyze the he layer-
by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
structure was divided in six layers corresponding the first one to the top
hydrogen atoms, from the second to the forth to carbon atoms in different $z$
positions, and the sixth and last one to the bottom hydrogen atoms. The
\emph{up} structure was divided into two layers, the first one comprised by the
top hydrogen atoms and the second by the carbon atoms. The layer divisions and atom positions for the unit cells are shown in Tables \ref{tab:altunitcell} and 
\ref{tab:upunitcell}.

\begin{table}[tb]
\caption{Unit cell of \emph{alt} structure.}
\center
\begin{tabular}{ccccc}\label{tab:altunitcell}  \\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline\\
\end{tabular} \\
\begin{minipage}{0.42\textwidth}
Layer division, atom types and positions for the \emph{alt} structure.
The structure unit cell was divided in six layers corresponding each one to
atoms in different $z$ positions.
\end{minipage}
\end{table}

\begin{table}[tb]
\caption{Unit cell of \emph{up} structure.}
\center
\begin{tabular}{ccccc}\label{tab:upunitcell}  \\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline\\
\end{tabular} \\
\begin{minipage}{0.42\textwidth}
Layer division, atom types and positions for the \emph{up} structure.
The structure unit cell was divided in two layers corresponding to
hydrogen and carbon atoms.
\end{minipage}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{alt} % (fold)
\label{sec:results-alt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{xb}}$}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components.}
    \label{fig:alt-xbangcomp}
\end{figure}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$\mathcal{V}^{\mathrm{yb}}$}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    145$^{\circ}$.}
    \label{fig:alt-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:alt-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vyb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:alt-rtp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vyz-layers.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:alt-lay}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-comp.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:alt-comp}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

% subsection alt (end)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Up (graphone)} % (fold)
\label{sec:results-up}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvxbincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
    \caption{Cheking angle of incidence for $xb$ components for up structure.}
    \label{fig:up-xbangcomp}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{yb}}$ energy range 0.0--0.2 eV }
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-1-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magvybincang1}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yx-angcomp.pdf}
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yy-angcomp.pdf}\\
    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yz-angcomp.pdf}
    \caption{Cheking angle of incidence for $yb$ components.}
    \label{fig:up-ybangcomp}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vyb1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 1.8--2.1 eV }

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magxbincang2}
\end{figure}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
    \label{fig:up-vxb2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-2-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    40$^{\circ}$.}
    \label{fig:up-magybincang2}
\end{figure}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-2.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
    \label{fig:upvyb2}
\end{figure}

\clearpage

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
range of 0.0--0.2 eV.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-1.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-1.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-1.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay1}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-1.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
range of 1.8--2.1 eV}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-2.pdf}
    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-2.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:up-rtp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-2.pdf}
    \caption{Layer decomposition for the most intense response:
    $\mathcal{V}^{\mathrm{yz}}$.}
    \label{fig:up-lay2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-2.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:up-comp2}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

% subsection up (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{HNBC$_{2}$H-aa} % (fold)
% % \label{sec:results-aa}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{xb}} $}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:aa-magvxbincang}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxx.pdf}
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxy.pdf}\\
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxz.pdf}
%     \caption{Cheking angle of incidence for $xb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:aa-xbangcomp}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
%     polarization angles.}
%     \label{fig:aa-magvxb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
%     \label{fig:aa-vxb1}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{yb}} $}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:aa-magvybincang}
% \end{figure}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyx.pdf}
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyy.pdf}\\
%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:aa-ybangcomp}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
%     polarization angles.}
%     \label{fig:aa-magvyb}
% \end{figure}
% \begin{figure}[t!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-2.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 175$^{\circ}$.}
%     \label{fig:aa-vyb2}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:aa-rtp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:aa-lay}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:aa-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
%     \label{fig:aa-xbybcomp}
% \end{figure}

% % subsection aa (end)

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AB %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{HNBC$_{2}$H-ab} % (fold)
% \label{sec:results-ab}

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{xb}} $}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:ab-magvxbincang}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
%     \caption{Cheking angle of incidence for $xb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:ab-xbangcomp}
% \end{figure}

% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
%     polarization angles.}
%     \label{fig:ab-magvxb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
%     \label{fig:ab-vxb}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{yb}} $}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
%     155$^{\circ}$.}
%     \label{fig:ab-magvybincang}
% \end{figure}
% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyx.pdf}
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyy.pdf}\\
%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components. There is a
%     different angle for each component to have the most intense response.}
%     \label{fig:ab-ybangcomp}
% \end{figure}

% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
%     polarization angles.}
%     \label{fig:ab-magvyb}
% \end{figure}
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 125$^{\circ}$.}
%     \label{fig:ab-vyb}
% \end{figure}

% \clearpage

% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
%     \label{fig:ab-rtp}
% \end{figure}

% % \begin{figure}[ht]
% %     \centering
% %     \includegraphics[width=0.7\textwidth]{}
% %     \caption{Layer decomposition for the most intense response:
% %     $\mathcal{V}^{\mathrm{yz}}$.}
% %     \label{fig:ab-lay}
% % \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vab-comp.pdf}
%     \caption{Comparisson of the most intense response vs the most intense
%     responses of CdSe and GaAs.}
%     \label{fig:ab-comp}
% \end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
%     \label{fig:ab-xbybcomp}
% \end{figure}

% % subsection ab (end)

% section results (end)

\bibliographystyle{plain}
\bibliography{article.bib}

\end{document}

### 2017-04-03 mu/alt/alt-scripts/alt-layers.sh

@@ -4,7 +4,6 @@
 strc=alt
 kpts=14452
 pws=10174
-# layers=( 1 2 3 4 )
 layers=( 1 2 3 4 5 6 )
 ################################################################################
 

### 2017-04-03 mu/article/figures/makefigs.sh

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+pdflatex arrows1.tex
+rmtex arrows1.
+pdfcrop arrows1.pdf arrows1.pdf
+
+pdflatex arrows2.tex
+rmtex arrows2.
+pdfcrop arrows2.pdf arrows2.pdf
+
+pdflatex altstruc1.tex
+rmtex altstruc1.
+pdfcrop altstruc1.pdf altstruc1.pdf
+
+pdflatex altstruc2.tex
+rmtex altstruc2.
+pdfcrop altstruc2.pdf altstruc2.pdf
+
+pdflatex upstruc1.tex
+rmtex upstruc1.
+pdfcrop upstruc1.pdf upstruc1.pdf
+
+pdflatex upstruc2.tex
+rmtex upstruc2.
+pdfcrop upstruc2.pdf upstruc2.pdf
+

### 2017-04-03 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-layers.sh

@@ -14,6 +14,7 @@ for i in ${layers[@]}; do
     echo -e "\n\n\n"
     sleep 20
     run_tiniba.sh -r run -k "$kpts" -N 1 -x 2 -C 12 -P "$pws" -c
+    
     clear
 
     END=$(date)

### 2017-04-03 mu/article/article.tex
Alt redaction at half completion.

@@
-\documentclass[]{article}
-% \documentclass[twocolumn]{article}
+% \documentclass[]{article}
+\documentclass[twocolumn]{article}
 
@@
 \usepackage{subfigure}
-\usepackage[inline  ]{showlabels}
+\usepackage{cuted}
+\usepackage{blindtext}
+\usepackage{color}
+\usepackage[inline]{showlabels}
+\usepackage{showframe}
 
@@
 
+\textcolor{red}{
+{\huge Filling with text.}\\
+\blindtext
+}
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/altstruc1}\hspace{0.05\textwidth}
-    \includegraphics[width=0.45\textwidth]{figures/altstruc2}
+    \includegraphics[width=\linewidth]{figures/altstruc1}
+    \includegraphics[width=\linewidth]{figures/altstruc2}
     \caption{Alt structure.}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/upstruc1}\hspace{0.05\textwidth}
-    \includegraphics[width=0.45\textwidth]{figures/upstruc2}
+    \includegraphics[width=\linewidth]{figures/upstruc1}
+    \includegraphics[width=\linewidth]{figures/upstruc2}
     \caption{Up structure}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-1}\hspace{0.05\textwidth}
-%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-aa-2}
+%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
+%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
 %     \caption{HNBC$_{2}$H-aa structure}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-1}\hspace{0.05\textwidth}
-%     \includegraphics[width=0.45\textwidth]{figures/hnbGh-ab-2}
+%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
+%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
 %     \caption{HNBC$_{2}$H-ab structure}
@@
 % % section introuction (end)
+\textcolor{red}{
+\blindtext
+\blindtext
+\blindtext
+}
 
@@
 The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
-plane is given by
+plane with a polarization angle $\alpha$ is given by
+
+\begin{strip}
 \begin{align}
 \mathcal{V}^{\mathrm{ab}} (\omega) 
-&= \frac{\mu^{\mathrm{abxx}}(\omega)E^{2}(\omega)\cos^{2}\theta + 
-\mu^{\mathrm{abyy}}(\omega)E^{2}(\omega)\sin^{2}\theta + 
-2\mu^{\mathrm{abxy}}(\omega)E^{2}(\omega)\cos\theta\sin\theta }
-{\xi^{\mathrm{xx}}(\omega)E^{2}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)E^{2}(\omega)\sin^{2}\theta},
+&= \frac{\mu^{\mathrm{abxx}}(\omega)
+E^{2}(\omega)\cos^{2}(\alpha) + 
+\mu^{\mathrm{abyy}}(\omega)
+E^{2}(\omega)\sin^{2}(\alpha) + 
+2\mu^{\mathrm{abxy}}(\omega)
+E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
+{\xi^{\mathrm{xx}}(\omega)
+E^{2}(\omega)\cos^{2}(\alpha) + 
+\xi^{\mathrm{yy}}(\omega)
+E^{2}(\omega)\sin^{2}(\alpha)},
 \nonumber \\
-&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}\theta + 
-\mu^{\mathrm{abyy}}(\omega)\sin^{2}\theta + 2\mu^{\mathrm{abxy}}(\omega)\cos\theta\sin\theta }
-{\xi^{\mathrm{xx}}(\omega)\cos^{2}\theta + \xi^{\mathrm{yy}}(\omega)\sin^{2}\theta}.
+&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
+\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
+2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
+{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
+\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
 \label{eq:vab}
 \end{align}
-For an angle $\theta = \frac{\pi}{4}$ this expression can be reduced to 
+\end{strip}
+
+For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
 \begin{align}
@@
 
-The structures presented here where divided into layers to analyze the he layer-
-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
-structure was divided in six layers corresponding the first one to the top
-hydrogen atoms, from the second to the forth to carbon atoms in different $z$
-positions, and the sixth and last one to the bottom hydrogen atoms. The
-\emph{up} structure was divided into two layers, the first one comprised by the
-top hydrogen atoms and the second by the carbon atoms. The layer divisions and atom positions for the unit cells are shown in Tables \ref{tab:altunitcell} and 
-\ref{tab:upunitcell}.
-
 \begin{table}[tb]
-\caption{Unit cell of \emph{alt} structure.}
 \center
-\begin{tabular}{ccccc}\label{tab:altunitcell}  \\
+\begin{tabular}{ccccc}\\
 \hline
@@
 6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
-\hline\\
-\end{tabular} \\
-\begin{minipage}{0.42\textwidth}
-Layer division, atom types and positions for the \emph{alt} structure.
-The structure unit cell was divided in six layers corresponding each one to
-atoms in different $z$ positions.
-\end{minipage}
+\hline
+\end{tabular}
+\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
+positions for the \emph{alt} structure. The structure unit cell was divided in
+six layers corresponding each one to atoms in different $z$ positions.}
+\label{tab:altunitcell}
 \end{table}
 
+The structures presented here where divided into layers to analyze the he layer-
+by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
+structure was divided in six layers corresponding the first one to the top
+hydrogen atoms, from the second to the forth to carbon atoms in different $z$
+positions, and the sixth and last one to the bottom hydrogen atoms. The
+\emph{up} structure was divided into two layers, the first one comprised by the
+top hydrogen atoms and the second by the carbon atoms. The layer divisions and
+atom positions for the unit cells are shown in Tables \ref{tab:altunitcell} and
+\ref{tab:upunitcell}.
+
 \begin{table}[tb]
-\caption{Unit cell of \emph{up} structure.}
 \center
-\begin{tabular}{ccccc}\label{tab:upunitcell}  \\
+\begin{tabular}{ccccc}\\
 \hline
@@
 2 & C &  0.61516 &  0.35763 & -0.49087 \\
-\hline\\
-\end{tabular} \\
-\begin{minipage}{0.42\textwidth}
-Layer division, atom types and positions for the \emph{up} structure.
-The structure unit cell was divided in two layers corresponding to
-hydrogen and carbon atoms.
-\end{minipage}
+\hline
+\end{tabular}
+\caption{Unit cell of \emph{up} structure. Layer division, atom types and
+positions for the \emph{up} structure. The structure unit cell was divided in
+two layers corresponding to hydrogen and carbon atoms.}
+\label{tab:upunitcell}
 \end{table}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{alt} % (fold)
@@
 
+In Fig. \ref{fig:alt-magvxbincang} we present the $\mathcal{V}^{\mathrm{x}}$
+spectra resulting from evaluate the Eq. \eqref{eq:vab-mag} at using different
+polarization angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_16$H$_8$-alt
+structure. The onset of the response is when the energy of the incoming light is
+the same of the gap energy. From this picture we can see that for the zone
+between the energy range of 0.90\,eV-0.93\,eV and polarization angles between
+120$^{\circ}$ and 150$^{\circ}$ is the zone of the maximum response is held
+reaching values of $\mathcal{V}^{\mathrm{x}}$ near to 30\,Km/s. Also there is a
+second zone between the energy range of 0.70\,eV-0.74\,eV and same polarization
+angles where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near
+to 22\,Km/s.We also found that the absolute maximum of the response is obtained
+for a polarization angle $\alpha = 145^{\circ}$. The decomposition of
+$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
+$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
+depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
+energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
+contribute with almost the same intensity. In the other hand, for the energy
+range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
+$\mathcal{V}^{\mathrm{xz}}$ component.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$\mathcal{V}^{\mathrm{xb}}$}
-\begin{figure}[ht!]
+% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
+\begin{figure}[]
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-magvxb-incang-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
-    145$^{\circ}$.}
+    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
+    \caption{$\mathcal{V}^{\mathrm{x}}$ for C$_16$H$_8$-alt structure. The
+    maximum response zone is localized for an energy range from 0.90\,eV to
+    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
     \label{fig:alt-magvxbincang}
 \end{figure}
-\begin{figure}[ht!]
+
+\begin{figure}[]
     \centering
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
-    \caption{Cheking angle of incidence for $xb$ components.}
-    \label{fig:alt-xbangcomp}
-\end{figure}
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-xb.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 145$^{\circ}$.}
-    \label{fig:alt-vxb1}
+    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
+    \label{fig:alt-vxb}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$\mathcal{V}^{\mathrm{yb}}$}
+\subsubsection{$\mathcal{V}^{\mathrm{y}}$}
 \begin{figure}[ht]
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-magvyb-incang-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
     145$^{\circ}$.}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxx.pdf}
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxy.pdf}\\
-    \includegraphics[width=0.45\textwidth]{altplots/alt-vxz.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
+    \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
     \caption{Cheking angle of incidence for $yb$ components.}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-yb.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 145$^{\circ}$.}
+    \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
     \label{fig:alt-vyb1}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vyz-layers.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
     \caption{Layer decomposition for the most intense response:
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-vab-comp.pdf}
+    \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
     \caption{Comparisson of the most intense response vs the most intense
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
-    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
     \label{fig:alt-xbybcomp}
@@
 
-\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 0.0--0.2 eV }
+\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-1-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
     40$^{\circ}$.}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xx-angcomp.pdf}
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xy-angcomp.pdf}\\
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-xz-angcomp.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
+    \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
     \caption{Cheking angle of incidence for $xb$ components for up structure.}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-1.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
+    \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
     \label{fig:up-vxb1}
@@
 
-\subsubsection{$\mathcal{V}^{\mathrm{yb}}$ energy range 0.0--0.2 eV }
+\subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-1-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
     40$^{\circ}$.}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yx-angcomp.pdf}
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yy-angcomp.pdf}\\
-    \includegraphics[width=0.45\textwidth]{upplots/up-vab-yz-angcomp.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
+    \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
     \caption{Cheking angle of incidence for $yb$ components.}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-1.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
     \label{fig:up-vyb1}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
-    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
+    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
     \label{fig:up-xbybcomp-1}
@@
 
-\subsubsection{$\mathcal{V}^{\mathrm{xb}}$ energy range 1.8--2.1 eV }
+\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-magvxb-incang-2-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
     40$^{\circ}$.}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-xb-2.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 40$^{\circ}$.}
+    \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
     \label{fig:up-vxb2}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-magvyb-incang-2-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
+    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
     40$^{\circ}$.}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yb-2.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 40$^{\circ}$.}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
+    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
     \label{fig:upvyb2}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-1.pdf}
-    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-1.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-1.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
     \caption{Layer decomposition for the most intense response:
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-1.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
     \caption{Comparisson of the most intense response vs the most intense
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vxb-rtp-2.pdf}
-    \includegraphics[width=0.7\textwidth]{upplots/up-vyb-rtp-2.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vyz-layers-2.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
     \caption{Layer decomposition for the most intense response:
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-vab-yz-comp-2.pdf}
+    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
     \caption{Comparisson of the most intense response vs the most intense
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
-    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
+    \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
+    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
     \label{fig:up-xbybcomp-2}
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{xb}} $}
+% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
 % \begin{figure}[ht!]
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
 %     155$^{\circ}$.}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxx.pdf}
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxy.pdf}\\
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vxz.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxx.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxy.pdf}\\
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxz.pdf}
 %     \caption{Cheking angle of incidence for $xb$ components. There is a
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvxb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
 %     polarization angles.}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-1.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
 %     \label{fig:aa-vxb1}
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{yb}} $}
+% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
 % \begin{figure}[h!]
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
 %     155$^{\circ}$.}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyx.pdf}
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyy.pdf}\\
-%     \includegraphics[width=0.45\textwidth]{aaplots/hnbGh-aa-vyz.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyy.pdf}\\
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyz.pdf}
 %     \caption{Cheking angle of incidence for $yb$ components. There is a
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-magvyb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
 %     polarization angles.}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-2.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 175$^{\circ}$.}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-2.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 175$^{\circ}$.}
 %     \label{fig:aa-vyb2}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
 %     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
 %     \caption{Layer decomposition for the most intense response:
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vab-comp.pdf}
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vab-comp.pdf}
 %     \caption{Comparisson of the most intense response vs the most intense
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
+%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-absvab.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
 %     \label{fig:aa-xbybcomp}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
-%     \includegraphics[width=0.45\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
+%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
+%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
 %     \caption{HNBC$_{2}$H-ab structure}
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{xb}} $}
+% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
 % \begin{figure}[ht!]
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
 %     155$^{\circ}$.}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxx.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxy.pdf}\\
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxz.pdf}
 %     \caption{Cheking angle of incidence for $xb$ components. There is a
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
 %     polarization angles.}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
 %     \label{fig:ab-vxb}
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{yb}} $}
+% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
 % \begin{figure}[h!]
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
 %     155$^{\circ}$.}
@@
 %     \centering
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyx.pdf}
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyy.pdf}\\
-%     \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyz.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyx.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyy.pdf}\\
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyz.pdf}
 %     \caption{Cheking angle of incidence for $yb$ components. There is a
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
 %     polarization angles.}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 125$^{\circ}$.}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 125$^{\circ}$.}
 %     \label{fig:ab-vyb}
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
 %     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
@@
 % %     \centering
-% %     \includegraphics[width=0.7\textwidth]{}
+% %     \includegraphics[width=\linewidth]{}
 % %     \caption{Layer decomposition for the most intense response:
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vab-comp.pdf}
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vab-comp.pdf}
 %     \caption{Comparisson of the most intense response vs the most intense
@@
 %     \centering
-%     \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
+%     \includegraphics[width=\linewidth]{abplots/hnbGh-absvab.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
 %     \label{fig:ab-xbybcomp}

### 2017-04-04 mu/article/article.tex
Makkng layer divisions in structures.
Changing format to revtex4-1

@@
 
+\section{abstract} % (fold)
+\label{sec:abstract}
+\textcolor{red}{{\huge Filling with text.}\\ \blindtext}
+% section abstract (end)
+
 \section{Introuction} % (fold)
@@
 
-\textcolor{red}{
-{\huge Filling with text.}\\
-\blindtext
-}
-\begin{figure}[h]
+\textcolor{red}{\blindtext}
+\begin{figure}[ht!]
     \centering
+    \includegraphics[width=\linewidth]{figures/altstruc2}
     \includegraphics[width=\linewidth]{figures/altstruc1}
-    \includegraphics[width=\linewidth]{figures/altstruc2}
     \caption{Alt structure.}
@@
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
+    \includegraphics[width=\linewidth]{figures/upstruc2}
     \includegraphics[width=\linewidth]{figures/upstruc1}
-    \includegraphics[width=\linewidth]{figures/upstruc2}
     \caption{Up structure}
@@
 \end{figure}
-% \begin{figure}[h]
+% \begin{figure}[tb]
 %     \centering
@@
 % \end{figure}
-% \begin{figure}[h]
+% \begin{figure}[tb]
 %     \centering
@@
 We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
-\begin{equation}\label{eq:vab-mag}
+\begin{equation}\label{eq:va-mag}
 |\mathcal{V}^{\mathrm{a}}| = 
@@
 \hline
+% \multicolumn{5}{c}{\includegraphics[width=0.4\linewidth]{figures/alt-unitcell-layers.pdf}} \\
+% \hline
 \end{tabular}
@@
 positions for the \emph{alt} structure. The structure unit cell was divided in
-six layers corresponding each one to atoms in different $z$ positions.}
-\label{tab:altunitcell}
+six layers corresponding each one to atoms in different $z$ positions. The
+corresponding layer atom position is depicted in Fig. \ref{fig:altstruc} with
+the corresponding number of layer.}
+\label{tab:alt-unitcell}
 \end{table}
@@
 top hydrogen atoms and the second by the carbon atoms. The layer divisions and
-atom positions for the unit cells are shown in Tables \ref{tab:altunitcell} and
-\ref{tab:upunitcell}.
+atom positions for the unit cells are shown in Tables \ref{tab:alt-unitcell} and
+\ref{tab:up-unitcell}.
 
@@
 positions for the \emph{up} structure. The structure unit cell was divided in
-two layers corresponding to hydrogen and carbon atoms.}
-\label{tab:upunitcell}
+two layers corresponding to hydrogen and carbon atoms.The corresponding layer
+atom position is depicted in Fig. \ref{fig:upstruc} with the corresponding
+number of layer.}
+\label{tab:up-unitcell}
 \end{table}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{alt} % (fold)
@@
 
-In Fig. \ref{fig:alt-magvxbincang} we present the $\mathcal{V}^{\mathrm{x}}$
-spectra resulting from evaluate the Eq. \eqref{eq:vab-mag} at using different
-polarization angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_16$H$_8$-alt
-structure. The onset of the response is when the energy of the incoming light is
-the same of the gap energy. From this picture we can see that for the zone
-between the energy range of 0.90\,eV-0.93\,eV and polarization angles between
-120$^{\circ}$ and 150$^{\circ}$ is the zone of the maximum response is held
-reaching values of $\mathcal{V}^{\mathrm{x}}$ near to 30\,Km/s. Also there is a
-second zone between the energy range of 0.70\,eV-0.74\,eV and same polarization
-angles where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near
-to 22\,Km/s.We also found that the absolute maximum of the response is obtained
-for a polarization angle $\alpha = 145^{\circ}$. The decomposition of
+For the \emph{alt} structure we analized the energby range from 0.6\,eV to
+1.0\,eV where we found the major response for $\mathcal{V}^{\mathrm{ab}}$ and
+$|\mathcal{V}^{\mathrm{a}}|$. In Fig. \ref{fig:alt-magvxbincang} we present the
+$|\mathcal{V}^{\mathrm{x}}|$ spectra resulting from evaluate Eq.
+\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.
+\eqref{eq:vab} forthe C$_{16}$H$_{8}$-alt structure. The onset of the response
+is when the energy of the incoming light is the same of the gap energy. From
+this picture we can see that for the zone between the energy range of
+0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
+150$^{\circ}$ is the zone of the maximum response is held reaching
+$|\mathcal{V}^{\mathrm{x}}|$ values of near to 30\,Km/s. Also there is a second
+zone between the energy range of 0.70\,eV-0.74\,eV and same polarization angles
+where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near to
+22\,Km/s.We also found that the absolute maximum of the response is obtained for
+a polarization angle $\alpha = 145^{\circ}$. The decomposition of
 $|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
-\begin{figure}[]
+\begin{figure}[tb]
     \centering
     \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
-    \caption{$\mathcal{V}^{\mathrm{x}}$ for C$_16$H$_8$-alt structure. The
+    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}  
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt structure. The
     maximum response zone is localized for an energy range from 0.90\,eV to
@@
 \end{figure}
-
-\begin{figure}[]
+\begin{figure}[tb]
     \centering
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$\mathcal{V}^{\mathrm{y}}$}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-    145$^{\circ}$.}
-    \label{fig:alt-magvybincang1}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
-    \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
-    \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
-    \caption{Cheking angle of incidence for $yb$ components.}
-    \label{fig:alt-ybangcomp}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
-    \label{fig:alt-vyb1}
-\end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
+%     145$^{\circ}$.}
+%     \label{fig:alt-magvybincang1}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
+%     \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
+%     \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
+%     \caption{Cheking angle of incidence for $yb$ components.}
+%     \label{fig:alt-ybangcomp}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
+%     \label{fig:alt-vyb1}
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
-    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
-    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-    \label{fig:alt-rtp}
-\end{figure}
+% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
+%     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
+%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+%     \label{fig:alt-rtp}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
-    \caption{Layer decomposition for the most intense response:
-    $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:alt-lay}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
+%     \caption{Layer decomposition for the most intense response:
+%     $\mathcal{V}^{\mathrm{yz}}$.}
+%     \label{fig:alt-lay}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
-    \caption{Comparisson of the most intense response vs the most intense
-    responses of CdSe and GaAs.}
-    \label{fig:alt-comp}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
+%     \caption{Comparisson of the most intense response vs the most intense
+%     responses of CdSe and GaAs.}
+%     \label{fig:alt-comp}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
-    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-    \label{fig:alt-xbybcomp}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
+%     \label{fig:alt-xbybcomp}
+% \end{figure}
 
-% subsection alt (end)
+% % subsection alt (end)
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Up (graphone)} % (fold)
-\label{sec:results-up}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Up (graphone)} % (fold)
+% \label{sec:results-up}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-    40$^{\circ}$.}
-    \label{fig:up-magvxbincang1}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
-    \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
-    \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
-    \caption{Cheking angle of incidence for $xb$ components for up structure.}
-    \label{fig:up-xbangcomp}
-\end{figure}
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
-    \label{fig:up-vxb1}
-\end{figure}
+% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
+%     40$^{\circ}$.}
+%     \label{fig:up-magvxbincang1}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
+%     \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
+%     \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
+%     \caption{Cheking angle of incidence for $xb$ components for up structure.}
+%     \label{fig:up-xbangcomp}
+% \end{figure}
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
+%     \label{fig:up-vxb1}
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-    40$^{\circ}$.}
-    \label{fig:up-magvybincang1}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
-    \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
-    \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
-    \caption{Cheking angle of incidence for $yb$ components.}
-    \label{fig:up-ybangcomp}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
-    \label{fig:up-vyb1}
-\end{figure}
+% \subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
+%     40$^{\circ}$.}
+%     \label{fig:up-magvybincang1}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
+%     \caption{Cheking angle of incidence for $yb$ components.}
+%     \label{fig:up-ybangcomp}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
+%     \label{fig:up-vyb1}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
-    \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-    \label{fig:up-xbybcomp-1}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
+%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
+%     \label{fig:up-xbybcomp-1}
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }
+% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-    40$^{\circ}$.}
-    \label{fig:up-magxbincang2}
-\end{figure}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
-    \label{fig:up-vxb2}
-\end{figure}
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
+%     40$^{\circ}$.}
+%     \label{fig:up-magxbincang2}
+% \end{figure}
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
+%     \label{fig:up-vxb2}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
-    \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-    40$^{\circ}$.}
-    \label{fig:up-magybincang2}
-\end{figure}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
-    \label{fig:upvyb2}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
+%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
+%     40$^{\circ}$.}
+%     \label{fig:up-magybincang2}
+% \end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
+%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
+%     \label{fig:upvyb2}
+% \end{figure}
 
-\clearpage
+% \clearpage
 
-%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
-range of 0.0--0.2 eV.}
+% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
+% range of 0.0--0.2 eV.}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
-    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
-    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-    \label{fig:up-rtp1}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
+%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
+%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+%     \label{fig:up-rtp1}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
-    \caption{Layer decomposition for the most intense response:
-    $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:up-lay1}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
+%     \caption{Layer decomposition for the most intense response:
+%     $\mathcal{V}^{\mathrm{yz}}$.}
+%     \label{fig:up-lay1}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
-    \caption{Comparisson of the most intense response vs the most intense
-    responses of CdSe and GaAs.}
-    \label{fig:up-comp1}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
+%     \caption{Comparisson of the most intense response vs the most intense
+%     responses of CdSe and GaAs.}
+%     \label{fig:up-comp1}
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
-range of 1.8--2.1 eV}
+% %%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
+% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
+% range of 1.8--2.1 eV}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
-    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
-    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-    \label{fig:up-rtp2}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
+%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
+%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
+%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
+%     \label{fig:up-rtp2}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
-    \caption{Layer decomposition for the most intense response:
-    $\mathcal{V}^{\mathrm{yz}}$.}
-    \label{fig:up-lay2}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
+%     \caption{Layer decomposition for the most intense response:
+%     $\mathcal{V}^{\mathrm{yz}}$.}
+%     \label{fig:up-lay2}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
-    \caption{Comparisson of the most intense response vs the most intense
-    responses of CdSe and GaAs.}
-    \label{fig:up-comp2}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
+%     \caption{Comparisson of the most intense response vs the most intense
+%     responses of CdSe and GaAs.}
+%     \label{fig:up-comp2}
+% \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
-    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-    \label{fig:up-xbybcomp-2}
-\end{figure}
+% \begin{figure}[ht]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
+%     % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
+%     \label{fig:up-xbybcomp-2}
+% \end{figure}
 
-% subsection up (end)
+% % subsection up (end)
 
@@
 
-% \begin{figure}[h]
+% \begin{figure}[tb]
 %     \centering

### 2017-04-04 mu/revtex4-1-example/revtex4-1-example.tex
Changing format to revtex4-1

\documentclass[prb,11pt,twocolumn]{revtex4-1}

% preamble:

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\raggedbottom           % don't add extra vertical space
\begin{comment}
\pagestyle{empty}       % use if page numbers not wanted
\end{comment}

\begin{document}

\title{Introduction to \LaTeX}
\author{Harvey Gould}
\affiliation{Clark University, Department of Physics, Worcester, MA 01610}
\affiliation{Boston University, Department of Physics, Boston, MA 02215}

\date{16 June 2013}

\begin{abstract}
We give a brief introduction to the use of \LaTeX\ in the context of REVTeX~4.1.
\end{abstract}

\maketitle

\section{Introduction}
\LaTeX\ looks more difficult than it is. It is
almost as easy as $\pi$. See how easy it is to make special
symbols such as $\alpha$,
$\beta$, $\gamma$,
$\delta$, $\sin x$, $\hbar$, $\lambda$, $\ldots$\ . We also can make
subscripts,
$A_{x}$, $A_{xy}$, and superscripts, $e^x$, $e^{x^2}$, and
$e^{a^b}$. We will use \LaTeX, which is based on \TeX\ and has
many higher-level commands (macros) for formatting, making
tables, etc. More information can be found in Refs.~\onlinecite{latex, website}.

We just made a new paragraph. Extra lines and spaces make no
difference. Note that all formulas are enclosed by
\$ and occur in \textit{math mode}.

The default font is Computer Modern. It includes \textit{italics},
\textbf{boldface},
\textsl{slanted}, and \texttt{monospaced} fonts.

\section{Equations}
Let us see how easy it is to write equations.
\begin{equation}
\Delta =\sum_{i=1}^N w_i (x_i - \bar{x})^2.
\end{equation}
It is a good idea to number equations, but we can have a
equation without a number:
\begin{equation}
P(x) = \frac{x - a}{b - a}, \nonumber
\end{equation}
and
\begin{equation}
g = \frac{1}{2} \sqrt{2\pi}. \nonumber
\end{equation}

We can give an equation a label so that we can refer to it later.
\begin{equation}
\label{eq:ising}
E = -J \sum_{i=1}^N s_i s_{i+1},
\end{equation}
Equation~\eqref{eq:ising} expresses the energy of a configuration
of spins in the Ising model.\footnote{REVTeX~4.1 places the footnotes in the bibliography. It is necessary to run BibTEX for footnotes to appear.}

We can define our own macros to save typing. For example, suppose
that we introduce the macros:
\begin{verbatim}
 \newcommand{\lb}{{\langle}}
 \newcommand{\rb}{{\rangle}}
\end{verbatim}
\newcommand{\lb}{{\langle}}
\newcommand{\rb}{{\rangle}}
Then we can write the average value of $x$ as
\begin{verbatim}
\begin{equation}
\lb x \rb = 3
\end{equation}
\end{verbatim}
The result is
\begin{equation}
\lb x \rb = 3.
\end{equation}

Examples of more complicated equations:
\begin{equation}
I = \! \int_{-\infty}^\infty f(x)\,dx \label{eq:fine}.
\end{equation}
We can do some fine tuning by adding small amounts of horizontal
spacing:
\begin{verbatim}
 \, small space       \! negative space
\end{verbatim}
as is done in Eq.~\eqref{eq:fine}.

We also can align several equations:
\begin{align}
a & = b \\
c &= d,
\end{align}
or number them as subequations:
\begin{subequations}
\begin{align}
a & = b \\
c &= d.
\end{align}
\end{subequations}

We can also have different cases:
\begin{equation}
\label{eq:mdiv}
m(T) =
\begin{cases}
0 & \text{($T > T_c$)} \\
\big(1 - [\sinh 2 \beta J]^{-4} \big)^{\! 1/8} & \text{($T < T_c$)},
\end{cases}
\end{equation}
write matrices
\begin{align}
\textbf{T} &=
\begin{pmatrix}
T_{++} \hfill & T_{+-} \\
T_{-+} & T_{--} \hfill 
\end{pmatrix}, \nonumber \\
& =
\begin{pmatrix}
e^{\beta (J + B)} \hfill & e^{-\beta J} \hfill \\
e^{-\beta J} \hfill & e^{\beta (J - B)} \hfill
\end{pmatrix}.
\end{align}
and 
\newcommand{\rv}{\textbf{r}}
\begin{equation}
\sum_i \vec A \cdot \vec B = -P\!\int\! \rv \cdot
\hat{\mathbf{n}}\, dA = P\!\int \! {\vec \nabla} \cdot \rv\, dV.
\end{equation}

\section{Tables}
Tables are a little more difficult. TeX
automatically calculates the width of the columns.

\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|l|}
\hline
lattice & $d$ & $q$ & $T_{\rm mf}/T_c$ \\
\hline
square & 2 & 4 & 1.763 \\
\hline
triangular & 2 & 6 & 1.648 \\
\hline
simple cubic & 3 & 6 & 1.330 \\
\hline
bcc & 3 & 8 & 1.260 \\
\hline
fcc & 3 & 12 & 1.225 \\
\hline
\end{tabular}
\caption{\label{tab:5/tc}Comparison of mean-field predictions
for the critical temperature of the Ising model with exact results
and the best known estimates for different dimensions 
and lattice symmetries.}
\end{table}

\section{Lists}

Some example of formatted lists include the
following:

\begin{enumerate}

\item bread

\item cheese

\end{enumerate}

\begin{itemize}
\setlength{\itemsep}{-5pt}       % made items closer together

\item Tom

\item Dick
\end{itemize}
\section{Figures}

We can make figures bigger or smaller by scaling them. Figure~\ref{fig:sine}
has been scaled by 60\%.

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{../article/figures/altstruc2}

\caption{\label{fig:sine}Show me a sine.}
\end{figure}

\section{Literal text}
It is desirable to print program code as it is typed in a
monospaced font. Use \verb+\begin{verbatim}+ and
\verb+\end{verbatim}+ as in the following example:
\begin{verbatim}
double y0 = 10; // example of declaration and assignment statement
double v0 = 0;  // initial velocity
double t = 0;   // time
double dt = 0.01; // time step
double y = y0;
\end{verbatim}
The command \verb+\verbatiminput{programs/Square.java}+ allows
you to list the file \texttt{Square.java} in the directory
programs.

\section{Special Symbols}

\subsection{Common Greek letters}

These commands may be used only in math mode. Only the most common
letters are included here.

$\alpha, 
\beta, \gamma, \Gamma,
\delta,\Delta,
\epsilon, \zeta, \eta, \theta, \Theta, \kappa,
\lambda, \Lambda, \mu, \nu,
\xi, \Xi,
\pi, \Pi,
\rho,
\sigma, 
\tau,
\phi, \Phi,
\chi,
\psi, \Psi,
\omega, \Omega$

\subsection{Special symbols}

The derivative is defined as
\begin{equation}
\frac{dy}{dx} = \lim_{\Delta x \to 0} \frac{\Delta y}
{\Delta x}
\end{equation}
\begin{equation}
f(x) \to y \quad \mbox{as} \quad x \to
x_{0}
\end{equation}
\begin{equation}
f(x) \mathop {\longrightarrow}
\limits_{x \to x_0} y
\end{equation}

\noindent Order of magnitude:
\begin{equation}
\log_{10}f \simeq n
\end{equation}
\begin{equation}
f(x)\sim 10^{n}
\end{equation}
Approximate equality:
\begin{equation}
f(x)\simeq g(x)
\end{equation}
\LaTeX\ is simple if we keep everything in proportion:
\begin{equation}
f(x) \propto x^3.
\end{equation}

Finally we can skip some space by using commands such as
\begin{verbatim}
\bigskip    \medskip    \smallskip    \vspace{1pc}
\end{verbatim}
The space can be negative.

\section{Use of Color}

{\color{blue}{We can change colors for emphasis}},
{\color{green}{but}} {\color{cyan}{who is going pay for the ink?}}

\section{\label{morefig}Subfigures}

As soon as many users start becoming comfortable using \LaTeX, they want
to use some of its advanced features. So we will show you how to place two
figures side by side.

\begin{figure}[h!]
\centering
\subfigure[\ Real and imaginary.]{
\includegraphics[width=\linewidth]{../article/altplots/alt-magvxb-incang-4545.pdf}}
\subfigure[\ Amplitude and phase.]{
\includegraphics[width=\linewidth]{../article/altplots/alt-magvyb-incang-4545.pdf}}
\caption{\label{fig:qm/complexfunctions} Two representations of complex
wave functions.}
\end{figure}

We first have to include the package,
\verb+\usepackage{subfigure}+, which has to go in the preamble (before
\verb+\begin{document}+). It sometimes can be difficult to place a figure in
the desired place.

Your LaTeX document can be easily modified to make a poster or a screen
presentation similar to (and better than) PowerPoint. Conversion to HTML is
straightforward.

\begin{thebibliography}{5}

\bibitem{latex}Helmut Kopka and Patrick W. Daly, \textsl{A Guide to
\LaTeX: Document Preparation for Beginners and Advanced Users} (Addison-Wesley, 2004), 4th ed.

\bibitem{website}Some useful links are
given at \url{}.

\end{thebibliography}

\end{document}

### 2017-04-04 mu/article/article-revtex.tex
Converting documentclass from article t revtex4-1.

--- 2017-04-04 mu/revtex4-1-example/revtex4-1-example.tex
@@
 \usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
+\usepackage{blindtext}  % fill text
+
 \raggedbottom           % don't add extra vertical space
-\begin{comment}
 \pagestyle{empty}       % use if page numbers not wanted
-\end{comment}
 
@@
 
-\title{Introduction to \LaTeX}
-\author{Harvey Gould}
-\affiliation{Clark University, Department of Physics, Worcester, MA 01610}
-\affiliation{Boston University, Department of Physics, Boston, MA 02215}
+\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
+\author{Reinaldo Zapata-Pe\~na, Bernardo S. Mendoza, Anatoli I. Shkrebtii}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150, M\'exico}
+\affiliation{University of Ontario, Institute of Technology, Oshawa, ON, L1H 7L7, Canada}
 
-\date{16 June 2013}
+\date{\today}
 
 \begin{abstract}
-We give a brief introduction to the use of \LaTeX\ in the context of REVTeX~4.1.
+\blindtext
 \end{abstract}

### 2017-04-04 mu/alt/alt-scripts/alt-res.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+
+# layers=( 1 2 3 4 5 6 )
+# layers=1
+# layers=2
+# layers=3
+# layers=4
+# layers=5
+layers=6
+
+
+for i in ${layers[@]}; do    
+    clear
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xxxx xxxy xxxz xxyx xxyy xxyz xxzx xxzy xxzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xyxx xyxy xyxz xyyx xyyy xyyz xyzx xyzy xyzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "xzxx xzxy xzxz xzyx xzyy xzyz xzzx xzzy xzzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yxxx yxxy yxxz yxyx yxyy yxyz yxzx yxzy yxzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yyxx yyxy yyxz yyyx yyyy yyyz yyzx yyzy yyzz" -b 0.03
+    all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "yzxx yzxy yzxz yzyx yzyy yzyz yzzx yzzy yzzz" -b 0.03
+    # all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zxxx zxxy zxxz zxyx zxyy zxyz zxzx zxzy zxzz" -b 0.03
+    # all_responses.sh -w layer -m 14452_"$i"_65-spin -s 0 -o 1 -v 18 -c 32 -r 49 -t "zyxx zyxy zyxz zyyx zyyy zyyz zyzx zyzy zyzz" -b 0.03
[…]

### 2017-04-05 mu/article/article.tex
Alt responses almost finished.

@@
-% \documentclass[]{article}
-\documentclass[twocolumn]{article}
+\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
 
-\usepackage{geometry}
-\geometry{letterpaper, margin=2cm}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{cuted}
-\usepackage{blindtext}
+% preamble:
+
+\usepackage{amsmath}    % need for subequations
+\usepackage{graphicx}   % need for figures
+\usepackage{verbatim}   % useful for program listings
+\usepackage{color}      % use if color is used in text
+\usepackage{subfigure}  % use for side-by-side figures
+\usepackage{hyperref}   % use for hypertext links, including those to external
+                        % documents and URLs 
+\usepackage{blindtext}  % fill text
 \usepackage{color}
-\usepackage[inline]{showlabels}
-\usepackage{showframe}
+% \usepackage{showframe}
+% \usepackage[inline]{showlabels}
 
-\usepackage[section]{placeins}
-\let\Oldsection\section
-\renewcommand{\section}{\FloatBarrier\Oldsection}
-\let\Oldsubsection\subsection
-\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}
-\let\Oldsubsubsection\subsubsection
-\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}
+\raggedbottom           % don't add extra vertical space
+
+\begin{document}
 
 \title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
-\author{Reinaldo Zapata-Pe\~na,
-Bernardo S. Mendoza,
-Anatoli I. Shkrebtii}
-\date{}
+\author{Reinaldo Zapata-Pe\~na\textsuperscript{1},
+        Bernardo S. Mendoza\textsuperscript{1},
+        Anatoli I. Shkrebtii\textsuperscript{2}}
+\affiliation{\textsuperscript{1}Centro de Investigaciones en \'Optica, Le\'on,
+Guanajuato 37150, M\'exico}
+\affiliation{\textsuperscript{2}University of Ontario, Institute of Technology,
+Oshawa, ON, L1H 7L7, Canada}
 
-\begin{document}
+\date{\today}
+
+\begin{abstract}
+\blindtext
+\end{abstract}
+
 \maketitle
 
-\section{abstract} % (fold)
-\label{sec:abstract}
-\textcolor{red}{{\huge Filling with text.}\\ \blindtext}
-% section abstract (end)
-
-\section{Introuction} % (fold)
-\label{sec:introuction}
-
-\textcolor{red}{\blindtext}
+\section{Introduction}
+\blindtext
 \begin{figure}[ht!]
     \centering
-    \includegraphics[width=\linewidth]{figures/altstruc2}
-    \includegraphics[width=\linewidth]{figures/altstruc1}
+    \subfigure[\ $xz$ plane view]
+    {\includegraphics[width=\linewidth]{figures/altstruc2}}
+    \label{fig:alt-struc-xz}
+    \\
+    \subfigure[\ $xy$ plane view]
+    {\includegraphics[width=\linewidth]{figures/altstruc1}}
+    \label{fig:alt-struc-xy}
     \caption{Alt structure.}
-    \label{fig:altstruc}
+    \label{fig:alt-struc}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/upstruc2}
-    \includegraphics[width=\linewidth]{figures/upstruc1}
+    \subfigure[\ $xz$ plane view]
+    {\includegraphics[width=\linewidth]{figures/upstruc2}}
+    \label{fig:up-struc-xz}
+    \\
+    \subfigure[\ $xy$ plane view]
+    {\includegraphics[width=\linewidth]{figures/upstruc1}}
+    \label{fig:up-struc-xy}
     \caption{Up structure}
-    \label{fig:upstruc}
+    \label{fig:up-struc}
 \end{figure}
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
-%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
-%     \caption{HNBC$_{2}$H-aa structure}
-%     \label{fig:aastruc}
-% \end{figure}
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
-%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
-%     \caption{HNBC$_{2}$H-ab structure}
-%     \label{fig:abstruc}
-% \end{figure}
-
-% % section introuction (end)
-\textcolor{red}{
 \blindtext
 \blindtext
+
 \blindtext
-}
 
@@
 
-\begin{strip}
+\begin{widetext}
 \begin{align}
@@
 \end{align}
-\end{strip}
+\end{widetext}
 
@@
 & 0 \leq &\theta \leq \pi, 
-\label{eq:polar-ang} \\
-\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}{\mathcal{V}^{\mathrm{ax}}} \right),
-& 0 \leq &\varphi \leq 2\pi. \\ 
+\label{eq:polar-ang}
+\\
+\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
+{\mathcal{V}^{\mathrm{ax}}} \right),
+& 0 \leq &\varphi \leq 2\pi.
 \label{eq:azimuthal-ang} 
@@
 $xz$ plane, as depicted in Figs.
-\ref{fig:altstruc} and \ref{fig:upstruc}.
+\ref{fig:alt-struc} and \ref{fig:up-struc}.
 
@@
 Hartwigsen- Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
-pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction for
-calculating $\mathcal{V}^{\mathrm{a}}(\omega)$.
+pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
+for calculating $\mathcal{V}^{\mathrm{a}}(\omega)$.
 
@@
 the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
-40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
-using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
-Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
-respectively for the \emph{alt} and \emph{up} structures. As mentioned in
+40\,Ha, respectively. The energy eigenvalues and matrix elements were
+calculated using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the
+irreducible Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV
+and 0.088\,eV, respectively for the \emph{alt} and \emph{up} structures. As
+mentioned in
 \cite{zapataPSB2016}, using DFT the LDA is only one method of many other that
-can be used to calculate the electronic structure of materials. Also it is known
-that all methods predict a different band gap than the obtained in the
+can be used to calculate the electronic structure of materials. Also it is
+known that all methods predict a different band gap than the obtained in the
 experiment. A correction for the band gap energy value can be calculated by
@@
 \hline
-% \multicolumn{5}{c}{\includegraphics[width=0.4\linewidth]{figures/alt-unitcell-layers.pdf}} \\
-% \hline
 \end{tabular}
@@
 six layers corresponding each one to atoms in different $z$ positions. The
-corresponding layer atom position is depicted in Fig. \ref{fig:altstruc} with
+corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
 the corresponding number of layer.}
@@
 
-The structures presented here where divided into layers to analyze the he layer-
-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
-structure was divided in six layers corresponding the first one to the top
-hydrogen atoms, from the second to the forth to carbon atoms in different $z$
-positions, and the sixth and last one to the bottom hydrogen atoms. The
-\emph{up} structure was divided into two layers, the first one comprised by the
-top hydrogen atoms and the second by the carbon atoms. The layer divisions and
-atom positions for the unit cells are shown in Tables \ref{tab:alt-unitcell} and
-\ref{tab:up-unitcell}.
+The structures presented here where divided into layers to analyze the he
+layer-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The
+\emph{alt} structure was divided in six layers corresponding the first one to
+the top hydrogen atoms, from the second to the forth to carbon atoms in
+different $z$ positions, and the sixth and last one to the bottom hydrogen
+atoms. The \emph{up} structure was divided into two layers, the first one
+comprised by the top hydrogen atoms and the second by the carbon atoms. The
+layer divisions and atom positions for the unit cells are shown in Tables
+\ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.
 
@@
 two layers corresponding to hydrogen and carbon atoms.The corresponding layer
-atom position is depicted in Fig. \ref{fig:upstruc} with the corresponding
+atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
 number of layer.}
@@
 \label{sec:results-alt}
-
-For the \emph{alt} structure we analized the energby range from 0.6\,eV to
-1.0\,eV where we found the major response for $\mathcal{V}^{\mathrm{ab}}$ and
-$|\mathcal{V}^{\mathrm{a}}|$. In Fig. \ref{fig:alt-magvxbincang} we present the
-$|\mathcal{V}^{\mathrm{x}}|$ spectra resulting from evaluate Eq.
-\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab} forthe C$_{16}$H$_{8}$-alt structure. The onset of the response
-is when the energy of the incoming light is the same of the gap energy. From
-this picture we can see that for the zone between the energy range of
-0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone of the maximum response is held reaching
-$|\mathcal{V}^{\mathrm{x}}|$ values of near to 30\,Km/s. Also there is a second
-zone between the energy range of 0.70\,eV-0.74\,eV and same polarization angles
-where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near to
-22\,Km/s.We also found that the absolute maximum of the response is obtained for
-a polarization angle $\alpha = 145^{\circ}$. The decomposition of
-$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
-$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
-depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
-energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
-contribute with almost the same intensity. In the other hand, for the energy
-range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
-$\mathcal{V}^{\mathrm{xz}}$ component.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
@@
     \centering
-    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
-    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}  
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt structure. The
-    maximum response zone is localized for an energy range from 0.90\,eV to
-    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
-    \label{fig:alt-magvxbincang}
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
+    {\includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}}
+    \label{fig:alt-vx}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
+    {\includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}}
+    \label{fig:alt-vy}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
+    structure. The maximum response zone is localized for an energy range from
+    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
+    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
+    \label{fig:alt-vab-mag}
 \end{figure}
+For the \emph{alt} structure we analyzed the energy range of energy from
+0.6\,eV to 1.0\,eV where we found the most intense response for
+$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
+\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
+resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
+angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
+can see that the onset of the response is when the energy of the incoming light
+is the same of the gap energy.
+%
+From this picture we can see that for the zone between the energy range of
+0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
+150$^{\circ}$ is the zone of the absolute maximum response having for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
+another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
+maximum is obtained.
+%
+From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
+values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
+the second one. 
+%
+We also found that the absolute maximum of the response is obtained for a
+polarization angle $\alpha = 145^{\circ}$. The decomposition of
+$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
+$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
+depicted in Fig. \ref{fig:alt-vx-comp} and the decomposition of
+$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
+$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
+\ref{fig:alt-vy} for this polarization angle.
+%
+Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
+energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
+contribute with almost the same intensity giving a total spin-velocity near to
+30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
+there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
+component resulting in a spin-velocity near to 20\,Km/s.
+%
+Also we notice that for the range of 0.70-0.74\,eV all the contributions are
+positive while for the range of 0.88-0.95\,eV the $xx$ component remains
+positive but the components $xy$ and $xz$ change in direction. This is due to
+\textcolor{red}{\large a change in the spin polarization}.
+%
+Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
+times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
+energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
+lesser contribution than $yz$ but for the energy range all three components
+have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
+both cases.
+%
+Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
+negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
+the same spin polarization for all this range.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[tb]
     \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
-    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
-    \label{fig:alt-vxb}
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    {\includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}}
+    \label{fig:alt-vx-comp}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    {\includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}}
+    \label{fig:alt-vy-comp}
+    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{alt} structure. Both maxima where obtained for a polarization
+    angle $\alpha=145^{\circ}$. }
+    \label{fig:alt-vab-xy-comp}
 \end{figure}
@@
 %     \label{fig:alt-magvybincang1}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
-%     \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
-%     \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
-%     \caption{Cheking angle of incidence for $yb$ components.}
-%     \label{fig:alt-ybangcomp}
 % \end{figure}
@@
 
-\bibliographystyle{plain}
 \bibliography{article.bib}

### 2017-04-07 mu/alt/alt-scripts/alt-magsvab-inang.sh
Making spin velocities.

@@ -1,0 +1,42 @@
+#!/bin/bash
+
+
+outputxkk=magsv.sm_0.03_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.kk_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsxkk=( v.kk_xx_14452_65-spin_scissor_0_Nc_32_ang_  
+            v.kk_yx_14452_65-spin_scissor_0_Nc_32_ang_  )
+inputsxsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yx_14452_65-spin_scissor_0_Nc_32_ang_  )
+
+
+
+
+
+outputykk=magsv.sm_0.03_ay_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magsv.kk_ay_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsykk=( v.kk_xy_14452_65-spin_scissor_0_Nc_32_ang_  
+            v.kk_yy_14452_65-spin_scissor_0_Nc_32_ang_  )
+inputsysm=( v.sm_0.03_xy_14452_65-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yy_14452_65-spin_scissor_0_Nc_32_ang_  )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsysm[0]}""$i"  "${inputsysm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputykk
+    echo "" >> $outputykk
+done
+
+for i in ${angles[@]}; do
[…]

### 2017-04-07 mu/alt/alt-scripts/alt-svab-rg.sh

@@ -1,0 +1,28 @@
+#/bin/bash
+
+an=145
+
+kp=14452
+ec=65
+sc=0
+nc=32
+sm=0.03
+
+
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=svab-rg.sm_"$sm"_sx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+xy=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outy=svab-rg.sm_"$sm"_sy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outx
+paste $xx $xy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outx
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outy
+paste $yx $yy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outy
+
+

### 2017-04-07 mu/alt/alt-scripts/alt-vab-rtp.sh

@@ -6,18 +6,18 @@ kp=14452
 ec=65
 sc=0
 nc=32
+sm=0.03
 
 
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 
-xx=v.sm_0.03_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xy=v.sm_0.03_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_0.03_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_0.03_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-
-yx=v.sm_0.03_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-yy=v.sm_0.03_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-yz=v.sm_0.03_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outy=vab-rtp.sm_0.03_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yz=v.sm_"$sm"_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-07 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-magsvab-inang.sh

@@ -1,0 +1,44 @@
+#!/bin/bash
+
+
+outputxkk=magsv.sm_0.03_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.kk_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsxkk=( v.kk_xx_14452_75-spin_scissor_0_Nc_32_ang_  
+            v.kk_yx_14452_75-spin_scissor_0_Nc_32_ang_  )
+inputsxsm=( v.sm_0.03_xx_14452_75-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yx_14452_75-spin_scissor_0_Nc_32_ang_  )
+
+
+
+
+
+outputykk=magsv.sm_0.03_ay_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magsv.kk_ay_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsykk=( v.kk_xy_14452_75-spin_scissor_0_Nc_32_ang_  
+            v.kk_yy_14452_75-spin_scissor_0_Nc_32_ang_  )
+inputsysm=( v.sm_0.03_xy_14452_75-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yy_14452_75-spin_scissor_0_Nc_32_ang_  )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsysm[0]}""$i"  "${inputsysm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputykk
+    echo "" >> $outputykk
+done
+
+for i in ${angles[@]}; do
[…]

### 2017-04-07 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-svab-rg.sh

@@ -1,0 +1,28 @@
+#/bin/bash
+
+an=085
+
+kp=14452
+ec=75
+sc=0
+nc=32
+sm=0.03
+
+
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=svab-rg.sm_"$sm"_sx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+xy=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outy=svab-rg.sm_"$sm"_sy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outx
+paste $xx $xy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outx
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outy
+paste $yx $yy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outy
+
+

### 2017-04-07 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-vab-rtp.sh

@@ -6,17 +6,18 @@ kp=14452
 ec=75
 sc=0
 nc=32
+sm=0.03
 
 
-xx=v.sm_0.03_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xy=v.sm_0.03_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_0.03_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_0.03_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 
-yx=v.sm_0.03_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-yy=v.sm_0.03_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-yz=v.sm_0.03_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outy=vab-rtp.sm_0.03_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yz=v.sm_"$sm"_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-07 mu/up/up-scripts/up-magsvab-inang.sh

@@ -1,0 +1,42 @@
+#!/bin/bash
+
+
+outputxkk=magsv.sm_0.03_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.kk_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsxkk=( v.kk_xx_12802_40-spin_scissor_0_Nc_32_ang_  
+            v.kk_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
+inputsxsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
+
+
+
+
+
+outputykk=magsv.sm_0.03_ay_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputysm=magsv.kk_ay_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+
+inputsykk=( v.kk_xy_12802_40-spin_scissor_0_Nc_32_ang_  
+            v.kk_yy_12802_40-spin_scissor_0_Nc_32_ang_  )
+inputsysm=( v.sm_0.03_xy_12802_40-spin_scissor_0_Nc_32_ang_  
+            v.sm_0.03_yy_12802_40-spin_scissor_0_Nc_32_ang_  )
+
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+rm "$outputxkk" "$outputxsm" "$outputykk" "$outputysm" > /dev/null 2>&1
+
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsysm[0]}""$i"  "${inputsysm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputykk
+    echo "" >> $outputykk
+done
+
+for i in ${angles[@]}; do
[…]

### 2017-04-07 mu/up/up-scripts/up-svab-rg.sh

@@ -1,0 +1,28 @@
+#/bin/bash
+
+an=040
+
+kp=12802
+ec=40
+sc=0
+nc=32
+sm=0.03
+
+
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=svab-rg.sm_"$sm"_sx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+xy=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outy=svab-rg.sm_"$sm"_sy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outx
+paste $xx $xy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outx
+
+
+echo -e "Energy          V^{xb}          V^{yb}          r               gamma" > $outy
+paste $yx $yy  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, sqrt($2*$2 + $4*$4), atan2($4,$2) ) }' > $outy
+
+

### 2017-04-07 mu/up/up-scripts/up-vab-rtp.sh

@@ -6,20 +6,20 @@ kp=12802
 ec=40
 sc=0
 nc=32
+sm=0.03
 
 
+xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 
-xx=v.sm_0.03_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xy=v.sm_0.03_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_0.03_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_0.03_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yx=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yy=v.sm_"$sm"_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+yz=v.sm_"$sm"_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+outy=vab-rtp.sm_"$sm"_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 
-yx=v.sm_0.03_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-yy=v.sm_0.03_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-07 mu/alt/alt-scripts/alt-magsvab-inang.sh
Making correction in V_{s^x}.

@@ -1,5 +1,8 @@
 #!/bin/bash
 
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+############################## V_{s^x} #########################################
 
 outputxkk=magsv.sm_0.03_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
 outputxsm=magsv.kk_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -9,9 +12,16 @@ inputsxkk=( v.kk_xx_14452_65-spin_scissor_0_Nc_32_ang_
 inputsxsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yx_14452_65-spin_scissor_0_Nc_32_ang_  )
 
+echo -e "E              Vsx               PolAng" > $outputxkk
+echo -e "E              Vsx               PolAng" > $outputxsm
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputykk
+done
 
-
-
+############################## V_{s^y} #########################################
 
 outputykk=magsv.sm_0.03_ay_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
 outputysm=magsv.kk_ay_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -21,22 +31,30 @@ inputsykk=( v.kk_xy_14452_65-spin_scissor_0_Nc_32_ang_
 inputsysm=( v.sm_0.03_xy_14452_65-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yy_14452_65-spin_scissor_0_Nc_32_ang_  )
 
-
[…]

### 2017-04-07 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-magsvab-inang.sh

@@ -1,5 +1,8 @@
 #!/bin/bash
 
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+############################## V_{s^x} #########################################
 
 outputxkk=magsv.sm_0.03_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
 outputxsm=magsv.kk_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -9,9 +12,16 @@ inputsxkk=( v.kk_xx_14452_75-spin_scissor_0_Nc_32_ang_
 inputsxsm=( v.sm_0.03_xx_14452_75-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yx_14452_75-spin_scissor_0_Nc_32_ang_  )
 
+echo -e "E              Vsx               PolAng" > $outputxkk
+echo -e "E              Vsx               PolAng" > $outputxsm
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputykk
+done
 
-
-
+############################## V_{s^y} #########################################
 
 outputykk=magsv.sm_0.03_ay_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
 outputysm=magsv.kk_ay_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -21,24 +31,30 @@ inputsykk=( v.kk_xy_14452_75-spin_scissor_0_Nc_32_ang_
 inputsysm=( v.sm_0.03_xy_14452_75-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yy_14452_75-spin_scissor_0_Nc_32_ang_  )
 
-
[…]

### 2017-04-07 mu/up/up-scripts/up-magsvab-inang.sh

@@ -1,5 +1,8 @@
 #!/bin/bash
 
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+############################## V_{s^x} #########################################
 
 outputxkk=magsv.sm_0.03_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
 outputxsm=magsv.kk_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -9,9 +12,16 @@ inputsxkk=( v.kk_xx_12802_40-spin_scissor_0_Nc_32_ang_
 inputsxsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
 
+echo -e "E              Vsx               PolAng" > $outputxkk
+echo -e "E              Vsx               PolAng" > $outputxsm
+for i in ${angles[@]}; do
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    echo "" >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputykk
+done
 
-
-
+############################## V_{s^y} #########################################
 
 outputykk=magsv.sm_0.03_ay_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
 outputysm=magsv.kk_ay_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
@@ -21,22 +31,30 @@ inputsykk=( v.kk_xy_12802_40-spin_scissor_0_Nc_32_ang_
 inputsysm=( v.sm_0.03_xy_12802_40-spin_scissor_0_Nc_32_ang_  
             v.sm_0.03_yy_12802_40-spin_scissor_0_Nc_32_ang_  )
 
-
[…]

### 2017-04-07 mu/alt/alt-scripts/alt-magsvab-inang.sh
Completed V_{s^b} for up

@@ -4,8 +4,8 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 ############################## V_{s^x} #########################################
 
-outputxkk=magsv.sm_0.03_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-outputxsm=magsv.kk_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxkk=magsv.kk_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.sm_0.03_ax_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
 
 inputsxkk=( v.kk_xx_14452_65-spin_scissor_0_Nc_32_ang_  
             v.kk_yx_14452_65-spin_scissor_0_Nc_32_ang_  )
@@ -15,16 +15,16 @@ inputsxsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_
 echo -e "E              Vsx               PolAng" > $outputxkk
 echo -e "E              Vsx               PolAng" > $outputxsm
 for i in ${angles[@]}; do
-    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
     echo "" >> $outputxkk
-    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
-    echo "" >> $outputykk
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputxsm
 done
 
[…]

### 2017-04-07 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-magsvab-inang.sh

@@ -4,8 +4,8 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 ############################## V_{s^x} #########################################
 
-outputxkk=magsv.sm_0.03_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
-outputxsm=magsv.kk_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxkk=magsv.kk_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.sm_0.03_ax_14452_75-spin_scissor_0_Nc_32_incang_0-180-step5
 
 inputsxkk=( v.kk_xx_14452_75-spin_scissor_0_Nc_32_ang_  
             v.kk_yx_14452_75-spin_scissor_0_Nc_32_ang_  )
@@ -15,16 +15,16 @@ inputsxsm=( v.sm_0.03_xx_14452_75-spin_scissor_0_Nc_32_ang_
 echo -e "E              Vsx               PolAng" > $outputxkk
 echo -e "E              Vsx               PolAng" > $outputxsm
 for i in ${angles[@]}; do
-    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
     echo "" >> $outputxkk
-    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
-    echo "" >> $outputykk
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputxsm
 done
 
[…]

### 2017-04-07 mu/up/up-scripts/up-magsvab-inang.sh

@@ -4,8 +4,8 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 ############################## V_{s^x} #########################################
 
-outputxkk=magsv.sm_0.03_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
-outputxsm=magsv.kk_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxkk=magsv.kk_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+outputxsm=magsv.sm_0.03_ax_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
 
 inputsxkk=( v.kk_xx_12802_40-spin_scissor_0_Nc_32_ang_  
             v.kk_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
@@ -15,16 +15,16 @@ inputsxsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_
 echo -e "E              Vsx               PolAng" > $outputxkk
 echo -e "E              Vsx               PolAng" > $outputxsm
 for i in ${angles[@]}; do
-    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
+    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxkk
     echo "" >> $outputxkk
-    paste "${inputsxkk[0]}""$i"  "${inputsxkk[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
-    echo "" >> $outputykk
+    paste "${inputsxsm[0]}""$i"  "${inputsxsm[1]}""$i" | awk '{printf("%1.5E    %1.6E    %3.0f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"' }' >> $outputxsm
+    echo "" >> $outputxsm
 done
 
[…]

### 2017-04-20 mu/article/article.tex
Cheking bms notes.
Making spin velocities.
Continuation of article.

@@
 \usepackage{color}
-% \usepackage{showframe}
-% \usepackage[inline]{showlabels}
+\usepackage{showframe}
+\usepackage[inline]{showlabels}
 
@@
 \maketitle
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Theory} % (fold)
@@
 \mathcal{V}^{\mathrm{ab}} (\omega) 
-&= \frac{\mu^{\mathrm{abxx}}(\omega)
+&= \frac{2}{\hbar}
+\frac{\mu^{\mathrm{abxx}}(\omega)
 E^{2}(\omega)\cos^{2}(\alpha) + 
@@
 \nonumber \\
-&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
+&= \frac{2}{\hbar}
+\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
 \mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
-2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
+\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
 {\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
@@
 \mathcal{V}^{\mathrm{ab}} (\omega)
-&= \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
+&= \frac{2}{\hbar}
+\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
 2\mu^{\mathrm{abxy}}(\omega)}
@@
 
-We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Fixing velocity.}\label{sec:theory-fixvel}
+Considering that we have 2D structures we fixed the velocity in the $xy$ plane
+along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
 \begin{equation}\label{eq:va-mag}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Fixing spin}\label{sec:theory-fixspin}
+In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
+$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
+\begin{align}
+|\mathcal{V}_{\sigma^{\mathrm{b}}}| 
+&=
+\sqrt{
+(\mathcal{V}^{\mathrm{ax}})^{2} +
+(\mathcal{V}^{\mathrm{ay}})^{2} 
+}, \\
+\gamma_{\mathrm{b}} 
+&=
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
+{\mathcal{V}^{\mathrm{ax}}} \right),
+\end{align}
+where the angle is measured in the counter-clockwise direction from the positive
+$x$ axis.
+
 % section theory (end)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{alt} % (fold)
-\label{sec:results-alt}
-% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Fixing spin} % (fold)
+\label{sec:res-fixspin}
+
 \begin{figure}[tb]
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
-    {\includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}}
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
     \label{fig:alt-vx}
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
-    {\includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}}
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
     \label{fig:alt-vy}
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-%     145$^{\circ}$.}
-%     \label{fig:alt-magvybincang1}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
-%     \label{fig:alt-vyb1}
-% \end{figure}
-
 % %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RES UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % \subsection{Up (graphone)} % (fold)
@@
 \end{document}
+
+\section{Fixing velocity} % (fold)
+\label{sec:fixing_velocity}
+
+\begin{equation}
+\mathcal{V}^\mathrm{a}_{\sigma} 
+= 
+\sqrt{
+\mathcal{V}^\mathrm{ax} + 
+\mathcal{V}^\mathrm{ay} +
+\mathcal{V}^\mathrm{az}
+}
+\end{equation}
+
+\begin{equation}
+\mathcal{V}^\mathrm{a}_{\sigma\parallel} 
+= 
+\sqrt{
+\mathcal{V}^\mathrm{ax} + 
+\mathcal{V}^\mathrm{ay} 
+}
+\end{equation}
+
+\begin{align}
+\theta_{a} 
+&=
+\sin^{-1}
+\left( 
+\frac{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
+{\mathcal{V}^\mathrm{a}_{\sigma}}
+\right)
+\\
+\varphi_{a} 
+&=
+\sin^{-1}
+\left(
+\frac{\mathcal{V}^\mathrm{ay}}{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
+\right)
+\end{align}
+
+% section fixing_velocity (end)
+
+\section{Fixing spin} % (fold)
+\label{sec:fixing_spin}
+
+% section fixing_spin (end)

### 2017-04-20 mu/alt/alt-scripts/alt-vab-rtp.sh
Making alt-vab-rtp.sh with deg and all positive angles.

@@ -8,6 +8,8 @@ sc=0
 nc=32
 sm=0.03
 
+deg=180/3.141592
+
 
 xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
@@ -22,6 +24,7 @@ outy=vab-rtp.sm_"$sm"_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
 paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
+paste .temp1 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
 
 echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $outx
 paste .temp1 .temp2 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $outx

### 2017-04-20 mu/alt/alt-scripts/alt-vab-rtp.sh
Completed alt-vab-rtp.sh with deg and all positive angles for all structures.

@@ -1,7 +1,6 @@
 #/bin/bash
 
 an=145
-
 kp=14452
 ec=65
 sc=0
@@ -10,32 +9,31 @@ sm=0.03
 
 deg=180/3.141592
 
+calc (){
+paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
+paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
+paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
+
+echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $out
+paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $out
+}
+
+################################ |V^{x}|, rtp ##################################
 
 xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
+################################ |V^{y}|, rtp ##################################
[…]

### 2017-04-20 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-rtp.sh

@@ -1,38 +1,39 @@
 #/bin/bash
 
 an=085
-
 kp=14452
 ec=75
 sc=0
 nc=32
 sm=0.03
 
+deg=180/3.141592
+
+calc (){
+paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
+paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
+paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
+
+echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $out
+paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $out
+}
+
+################################ |V^{x}|, rtp ##################################
 
 xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
+################################ |V^{y}|, rtp ##################################
 
[…]

### 2017-04-20 mu/up/up-scripts/up-vab-rtp.sh

@@ -1,38 +1,39 @@
 #/bin/bash
 
 an=040
-
 kp=12802
 ec=40
 sc=0
 nc=32
 sm=0.03
 
+deg=180/3.141592
+
+calc (){
+paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
+paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
+paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
+
+echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $out
+paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $out
+}
+
+################################ |V^{x}|, rtp ##################################
 
 xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-outx=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
+################################ |V^{y}|, rtp ##################################
 
[…]

### 2017-04-20 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-rtp.sh
Correction in the azimuthal angles. Now 0<= phi<360.

@@ -12,7 +12,7 @@ deg=180/3.141592
 calc (){
 paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
 paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
-paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
+paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+360) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
 
 echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $out
 paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $out
@@ -22,7 +22,7 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-20 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-vab-rtp.sh

@@ -12,7 +12,7 @@ deg=180/3.141592
 calc (){
 paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
 paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
-paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+180) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
+paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+360) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
 
 echo -e "Energy          V^{ax}          V^{ay}          V^{az}          r               polar           azimuth" > $out
 paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $3, $4, $5, $6, $7) }'  >> $out

### 2017-04-21 mu/article/article.tex
New multiplots with V^{a} vs thetha and phy and x y z comonents.

@@
 \usepackage{color}
-\usepackage{showframe}
-\usepackage[inline]{showlabels}
+% \usepackage{showframe}
+% \usepackage[inline]{showlabels}
 
@@
 
-\subsection{Fixing spin} % (fold)
-\label{sec:res-fixspin}
+\subsection{Fixing velocity} % (fold)
+\label{sec:res-fixvel}
 
@@
 \end{figure}
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
+    \label{fig:alt-vx-comp-rtp}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
+    \label{fig:alt-vy-comp-rtp}
+    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{alt} structure. Both maxima where obtained for a polarization
+    angle $\alpha=145^{\circ}$. }
+    \label{fig:alt-vab-xy-comp-rtp}
+\end{figure}
+
 For the \emph{alt} structure we analyzed the energy range of energy from
@@
 $\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
-depicted in Fig. \ref{fig:alt-vx-comp} and the decomposition of
+depicted in Fig. \ref{fig:alt-vx-comp-rtp} and the decomposition of
 $|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tb]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
-    {\includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}}
-    \label{fig:alt-vx-comp}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
-    {\includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}}
-    \label{fig:alt-vy-comp}
-    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{alt} structure. Both maxima where obtained for a polarization
-    angle $\alpha=145^{\circ}$. }
-    \label{fig:alt-vab-xy-comp}
-\end{figure}
 

### 2017-04-21 mu/hnbGh-aa/hnbGh-aa-scripts/hnbGh-aa-vab-rtp.sh

@@ -10,7 +10,7 @@ sm=0.03
 deg=180/3.141592
 
 calc (){
-paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
+paste $ax $ay $az  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
 paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
 paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+360) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
 
@@ -20,18 +20,18 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-21 mu/hnbGh-ab/hnbGh-ab-scripts/hnbGh-ab-vab-rtp.sh

@@ -10,7 +10,7 @@ sm=0.03
 deg=180/3.141592
 
 calc (){
-paste $xx $xy $xz  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
+paste $ax $ay $az  | awk '{ printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E\n", $1, $2, $4, $6, sqrt($2*$2 + $4*$4 + $6*$6) ) }' > .temp1
 paste .temp1 | awk '{if($5 != 0) {printf("%1.6E    %1.6E\n", 2*atan2((sqrt(1-($4/($5))^2)),(1+($4/($5)))), atan2($3,$2) ) ;} else if($5==0) {printf("%1.6E    %1.6E\n"), 0,0 } }' > .temp2
 paste .temp2 | awk '{if($2 < 0) {printf("%010.6f    %010.6f\n", ($1*'"$deg"'), ($2*'"$deg"')+360) ;} else {printf("%010.6f    %010.6f\n"), ($1*'"$deg"'), $2*'"$deg"' } }' > .deg1
 
@@ -20,18 +20,18 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-xx=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xy=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-xz=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
[…]

### 2017-04-24 mu/article/article.tex
Writin article.

@@
 % \usepackage{showframe}
-% \usepackage[inline]{showlabels}
+\usepackage[inline]{showlabels}
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vx}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
-    \label{fig:alt-vx}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vy}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
-    \label{fig:alt-vy}
     \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
@@
 \end{figure}
+
 \begin{figure}[tb]
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
     {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
-    \label{fig:alt-vx-comp-rtp}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vy-comp-rtp}]
     {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
-    \label{fig:alt-vy-comp-rtp}
     \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
@@
     angle $\alpha=145^{\circ}$. }
-    \label{fig:alt-vab-xy-comp-rtp}
+    \label{fig:alt-vab-comp-rtp}
 \end{figure}
@@
 0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone of the absolute maximum response having for both,
+150$^{\circ}$ is the zone of the absolute maximum response for both,
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
@@
 maximum is obtained.
-%
-From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
+From Fig. \ref{fig:alt-3d-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
 values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
 the second one. 
+% %%%%%%%%%%%%%%%%
+% %% Starting description of ALT |V^{a}|, components and RTP
+% %%%%%%%%%%%%%%%%
+We also found that the absolute maximum of the response is obtained when the
+polarization angle is $\alpha = 145^{\circ}$. 
 %
-We also found that the absolute maximum of the response is obtained for a
-polarization angle $\alpha = 145^{\circ}$. The decomposition of
-$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
-$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
-depicted in Fig. \ref{fig:alt-vx-comp-rtp} and the decomposition of
-$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
-$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
-\ref{fig:alt-vy} for this polarization angle.
+In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
+\ref{fig:alt-vy-comp-rtp} we present the results for
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
+polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the photon
+energy and the corresponding azimuthal $\theta$ and polar $\varphi$ angles.
 %
-Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
-energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
-contribute with almost the same intensity giving a total spin-velocity near to
-30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
-there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
-component resulting in a spin-velocity near to 20\,Km/s.
+Also in the bottom frames of Figs. \ref{fig:alt-vx-comp-rtp} and 
+%
+\ref{fig:alt-vy-comp-rtp} we present the decomposition of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
+corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
+$\mathcal{V}^{\mathrm{xz}}$ and
+$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
+$\mathcal{V}^{\mathrm{yz}}$ components for the fixed polarization angle.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{x}|, components and RTP
+% %%%%%%%%%%%%%%%%
+Making the analysis for the components and angles for
+$|\mathcal{V}^{\mathrm{x}}|$ we can see that for the energy range from 0.70\,eV
+to 0.74\,eV all the $xx$, $xy$, and $xz$ components contribute with almost the
+same intensity giving a total spin-velocity near to 30\,Km/s and spin angles
+$\theta$ and $\varphi$ near to $45.8^{\circ}$ and $40.7^{\circ}$, respectively.
+%
+In the other hand, for the energy range from 0.88\,eV to 0.95\,eV there is a
+major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$ component
+resulting in a spin-velocity magnitude near to 20\,Km/s. In this case the spin
+angle over the $xy$ plane have values near to $290^{\circ}$ and the
+corresponding polar angle correspond to values near to $153^{\circ}$.
 %
@@
 \textcolor{red}{\large a change in the spin polarization}.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{y}|, components and RTP
+% %%%%%%%%%%%%%%%%
+Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, we notice that this
+response is almost two times more intense than $|\mathcal{V}^{\mathrm{x}}|$. For
+the energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more
+intense response than $yx$ and $yy$ components. This results in a spin azimuthal
+angle near to $221^{\circ}$ and polar angle near to $141^{\circ}$.
 %
-Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
-times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
-energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
-lesser contribution than $yz$ but for the energy range all three components
-have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
-both cases.
+For the energy range all three components have
+almost the same intensity resulting in a spin-velocity near to 50\,Km/s in both
+cases.
 %

### 2017-04-25 mu/article/article.tex
Description for V^x and v^y completed for Alt structure.

@@
 From Fig. \ref{fig:alt-3d-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
-values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
+values of 30\,Km/s for the first zone mentioned before and 20\,Km/s for
 the second one. 
@@
 % %% Description of ALT |V^{x}|, components and RTP
+% %% files: vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%        alt-plots/alt-vab-rtp.gp
 % %%%%%%%%%%%%%%%%
@@
 to 0.74\,eV all the $xx$, $xy$, and $xz$ components contribute with almost the
-same intensity giving a total spin-velocity near to 30\,Km/s and spin angles
-$\theta$ and $\varphi$ near to $45.8^{\circ}$ and $40.7^{\circ}$, respectively.
+same intensity giving a total spin-velocity of 19.3\,Km/s and spin polar and azimuthal angles
+$\varphi = 45.8^{\circ}$ and $\theta=40.7^{\circ}$.
 %
@@
 major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$ component
-resulting in a spin-velocity magnitude near to 20\,Km/s. In this case the spin
-angle over the $xy$ plane have values near to $290^{\circ}$ and the
-corresponding polar angle correspond to values near to $153^{\circ}$.
+resulting in a spin-velocity magnitude of 30.9\,Km/s being this magnitude the
+most intense for $|\mathcal{V}^{\mathrm{x}}|$. In this case the polar angle is
+$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is $\theta=290.4^{\circ}$.
 %
@@
 % %% Description of ALT |V^{y}|, components and RTP
+% %% files: vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%        alt-plots/alt-vab-rtp.gp
 % %%%%%%%%%%%%%%%%
-Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, we notice that this
-response is almost two times more intense than $|\mathcal{V}^{\mathrm{x}}|$. For
-the energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more
-intense response than $yx$ and $yy$ components. This results in a spin azimuthal
-angle near to $221^{\circ}$ and polar angle near to $141^{\circ}$.
+Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ we have that for the
+energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more intense
+response than $yx$ and $yy$ components and they give a total spin-velocity of
+51.9\,Km/s and result in polar angle $\varphi=140.7^{\circ}$ and spin azimuthal
+angle of $\theta=221.5^{\circ}$.
 %
-For the energy range all three components have
-almost the same intensity resulting in a spin-velocity near to 50\,Km/s in both
-cases.
+For the energy range from 0.88\,eV to 0.95\,eV all three components have similar
+intensities resulting in a spin-velocity magnitude of
+$|\mathcal{V}^{\mathrm{y}}| =$ 52.3\,Km/s being this response 1.7 times mores
+intense than the most intense response of $|\mathcal{V}^{\mathrm{x}}|$. The
+corresponding polar and azimuthal angles for $|\mathcal{V}^{\mathrm{y}}|$ in
+this energy range are $\theta = 129.0 ^{\circ}$ and $\varphi = 228.9 ^{\circ}$.
 %
 Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
-negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
+negative for the energy range from 0.60\,eV to 1.0\,eV \textcolor{red}{keeping
 the same spin polarization for all this range.}

### 2017-04-25 mu/article/article.tex
Alt V^yz layer description completed.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vy-comp-rtp}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
     {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
@@
 Making the analysis for the components and angles for
-$|\mathcal{V}^{\mathrm{x}}|$ we can see that for the energy range from 0.70\,eV
-to 0.74\,eV all the $xx$, $xy$, and $xz$ components contribute with almost the
-same intensity giving a total spin-velocity of 19.3\,Km/s and spin polar and azimuthal angles
-$\varphi = 45.8^{\circ}$ and $\theta=40.7^{\circ}$.
+$|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
+see that for the energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and
+$xz$ components contribute with almost the same intensity giving a total spin-
+velocity of 19.3\,Km/s and spin polar and azimuthal angles $\varphi =
+45.8^{\circ}$ and $\theta=40.7^{\circ}$.
 %
@@
 % %%%%%%%%%%%%%%%%
-Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ we have that for the
-energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more intense
-response than $yx$ and $yy$ components and they give a total spin-velocity of
-51.9\,Km/s and result in polar angle $\varphi=140.7^{\circ}$ and spin azimuthal
-angle of $\theta=221.5^{\circ}$.
+Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
+\ref{fig:alt-vy-comp-rtp} we have that for the energy range from 0.70\,eV to
+0.74\,eV the $yz$ component have a more intense response than $yx$ and $yy$
+components and they give a total spin-velocity of 51.9\,Km/s and result in polar
+angle $\varphi=140.7^{\circ}$ and spin azimuthal angle of
+$\theta=221.5^{\circ}$.
 %
@@
 the same spin polarization for all this range.} 
+%
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-lay}]
+    {\includegraphics[width=\linewidth]{figures/blank}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-lay}]
+    {\includegraphics[width=\linewidth]{figures/blank}}
+    \caption{Layer-by-layer contribution of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ for a polarization angle $\alpha=145^{\circ}$
+    for the \emph{alt} structure.}
+    \label{fig:alt-vab-lay}
+\end{figure}
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
+    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
+     \emph{alt} structure.}
+    \label{fig:alt-vyz-lay}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT layer |V^{ab}|
+% %% files: 
+% %%%%%%%%%%%%%%%%
+In Fig. \ref{fig:alt-vab-lay} we show the layer-by-layer contribution of
+$|\mathcal{V}^{\mathrm{ab}}|$  for the \emph{alt} structure. The corresponding
+layer division and atom types and positions are presented in Table 
+% 
+\ref{tab:alt-unitcell} and depicted in Fig. \ref{fig:alt-struc}. In the layer-
+by-layer contribution for $|\mathcal{V}^{\mathrm{x}}|$ (Fig. \ref{fig:alt-vx-lay})
+we have that
+% 
+\textcolor{red}{\ldots}
+% 
+Also, for the layer-by-layer contribution for $|\mathcal{V}^{\mathrm{y}}|$ (Fig.
+\ref{fig:alt-vy-lay}) we have that
+% 
+\textcolor{red}{\ldots}
+%
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT layer |V^{yz}|
+% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
+% %%         alt-plots/alt-vab-layers.gp
+% %%%%%%%%%%%%%%%%
+From the bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
+the \emph{alt} structure the most intense component of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
+$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an
+energy incident beam of 0.72\,eV. This component and the corresponding layer by
+layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
+we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
+layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
+Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
+4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
+for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
+from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
+in the same direction resulting in a total response
+$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
+0.912\,eV.
 
-% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.6:1.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp.pdf}
-%     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp.pdf}
-%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-%     \label{fig:alt-rtp}
-% \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vyz-layers.pdf}
-%     \caption{Layer decomposition for the most intense response:
-%     $\mathcal{V}^{\mathrm{yz}}$.}
-%     \label{fig:alt-lay}
-% \end{figure}
+\subsection{Fixing spin} % (fold)
+\label{sec:res-fixspin}
 
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vab-comp.pdf}
-%     \caption{Comparisson of the most intense response vs the most intense
-%     responses of CdSe and GaAs.}
-%     \label{fig:alt-comp}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-absvab.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-%     \label{fig:alt-xbybcomp}
-% \end{figure}
-
-% % subsection alt (end)
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RES UP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsection{Up (graphone)} % (fold)
-% \label{sec:results-up}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 0.0--0.2 eV }
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-1-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-%     40$^{\circ}$.}
-%     \label{fig:up-magvxbincang1}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-xx-angcomp.pdf}
-%     \includegraphics[width=\linewidth]{upplots/up-vab-xy-angcomp.pdf}\\
-%     \includegraphics[width=\linewidth]{upplots/up-vab-xz-angcomp.pdf}
-%     \caption{Cheking angle of incidence for $xb$ components for up structure.}
-%     \label{fig:up-xbangcomp}
-% \end{figure}
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-1.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
-%     \label{fig:up-vxb1}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.0:0.2] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsubsection{$\mathcal{V}^{\mathrm{y}}$ energy range 0.0--0.2 eV }
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-1-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-%     40$^{\circ}$.}
-%     \label{fig:up-magvybincang1}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yx-angcomp.pdf}
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yy-angcomp.pdf}\\
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-angcomp.pdf}
-%     \caption{Cheking angle of incidence for $yb$ components.}
-%     \label{fig:up-ybangcomp}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-1.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
-%     \label{fig:up-vyb1}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-absvab-1.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-%     \label{fig:up-xbybcomp-1}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [1.8:2.1] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsubsection{$\mathcal{V}^{\mathrm{x}}$ energy range 1.8--2.1 eV }
-
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-magvxb-incang-2-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-%     40$^{\circ}$.}
-%     \label{fig:up-magxbincang2}
-% \end{figure}
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-xb-2.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 40$^{\circ}$.}
-%     \label{fig:up-vxb2}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-magvyb-incang-2-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-%     40$^{\circ}$.}
-%     \label{fig:up-magybincang2}
-% \end{figure}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yb-2.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 40$^{\circ}$.}
-%     \label{fig:upvyb2}
-% \end{figure}
-
-% \clearpage
-
-% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.0:0.2] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
-% range of 0.0--0.2 eV.}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-1.pdf}
-%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-1.pdf}
-%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-%     \label{fig:up-rtp1}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1.pdf}
-%     \caption{Layer decomposition for the most intense response:
-%     $\mathcal{V}^{\mathrm{yz}}$.}
-%     \label{fig:up-lay1}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-1.pdf}
-%     \caption{Comparisson of the most intense response vs the most intense
-%     responses of CdSe and GaAs.}
-%     \label{fig:up-comp1}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%% |V^{ab}| [1.8:2.1] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs for the energy
-% range of 1.8--2.1 eV}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-2.pdf}
-%     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-2.pdf}
-%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-%     \label{fig:up-rtp2}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2.pdf}
-%     \caption{Layer decomposition for the most intense response:
-%     $\mathcal{V}^{\mathrm{yz}}$.}
-%     \label{fig:up-lay2}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-vab-yz-comp-2.pdf}
-%     \caption{Comparisson of the most intense response vs the most intense
-%     responses of CdSe and GaAs.}
-%     \label{fig:up-comp2}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-absvab-2.pdf}
-%     % \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$}    
-%     \label{fig:up-xbybcomp-2}
-% \end{figure}
-
-% % subsection up (end)
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsection{HNBC$_{2}$H-aa} % (fold)
-% % \label{sec:results-aa}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-%     155$^{\circ}$.}
-%     \label{fig:aa-magvxbincang}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxx.pdf}
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxy.pdf}\\
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxz.pdf}
-%     \caption{Cheking angle of incidence for $xb$ components. There is a
-%     different angle for each component to have the most intense response.}
-%     \label{fig:aa-xbangcomp}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvxb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
-%     polarization angles.}
-%     \label{fig:aa-magvxb}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-1.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
-%     \label{fig:aa-vxb1}
-% \end{figure}
-
-% \clearpage
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-%     155$^{\circ}$.}
-%     \label{fig:aa-magvybincang}
-% \end{figure}
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx.pdf}
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyy.pdf}\\
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyz.pdf}
-%     \caption{Cheking angle of incidence for $yb$ components. There is a
-%     different angle for each component to have the most intense response.}
-%     \label{fig:aa-ybangcomp}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-magvyb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
-%     polarization angles.}
-%     \label{fig:aa-magvyb}
-% \end{figure}
-% \begin{figure}[t!]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-2.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 175$^{\circ}$.}
-%     \label{fig:aa-vyb2}
-% \end{figure}
-
-% \clearpage
-
-% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
-%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-%     \label{fig:aa-rtp}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
-%     \caption{Layer decomposition for the most intense response:
-%     $\mathcal{V}^{\mathrm{yz}}$.}
-%     \label{fig:aa-lay}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-vab-comp.pdf}
-%     \caption{Comparisson of the most intense response vs the most intense
-%     responses of CdSe and GaAs.}
-%     \label{fig:aa-comp}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{aaplots/hnbGh-aa-absvab.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
-%     \label{fig:aa-xbybcomp}
-% \end{figure}
-
-% % subsection aa (end)
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AB %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsection{HNBC$_{2}$H-ab} % (fold)
-% \label{sec:results-ab}
-
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-1}
-%     \includegraphics[width=\linewidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
-%     \caption{HNBC$_{2}$H-ab structure}
-%     \label{fig:abstruc}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{x}} $}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{x}} $ is for 
-%     155$^{\circ}$.}
-%     \label{fig:ab-magvxbincang}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxx.pdf}
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxy.pdf}\\
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxz.pdf}
-%     \caption{Cheking angle of incidence for $xb$ components. There is a
-%     different angle for each component to have the most intense response.}
-%     \label{fig:ab-xbangcomp}
-% \end{figure}
-
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvxb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ for different
-%     polarization angles.}
-%     \label{fig:ab-magvxb}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 155$^{\circ}$.}
-%     \label{fig:ab-vxb}
-% \end{figure}
-
-% \clearpage
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$\mathcal{V}^{\mathrm{y}} $}
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
-%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
-%     155$^{\circ}$.}
-%     \label{fig:ab-magvybincang}
-% \end{figure}
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyx.pdf}
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyy.pdf}\\
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyz.pdf}
-%     \caption{Cheking angle of incidence for $yb$ components. There is a
-%     different angle for each component to have the most intense response.}
-%     \label{fig:ab-ybangcomp}
-% \end{figure}
-
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-magvyb.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{y}}|$ for different
-%     polarization angles.}
-%     \label{fig:ab-magvyb}
-% \end{figure}
-% \begin{figure}[ht!]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb.pdf}
-%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 125$^{\circ}$.}
-%     \label{fig:ab-vyb}
-% \end{figure}
-
-% \clearpage
-
-% %%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsubsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
-% $\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
-%     \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
-%     corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
-%     \label{fig:ab-rtp}
-% \end{figure}
-
-% % \begin{figure}[ht]
-% %     \centering
-% %     \includegraphics[width=\linewidth]{}
-% %     \caption{Layer decomposition for the most intense response:
-% %     $\mathcal{V}^{\mathrm{yz}}$.}
-% %     \label{fig:ab-lay}
-% % \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-ab-vab-comp.pdf}
-%     \caption{Comparisson of the most intense response vs the most intense
-%     responses of CdSe and GaAs.}
-%     \label{fig:ab-comp}
-% \end{figure}
-
-% \begin{figure}[ht]
-%     \centering
-%     \includegraphics[width=\linewidth]{abplots/hnbGh-absvab.pdf}
-%     \caption{Comparisson of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.}    
-%     \label{fig:ab-xbybcomp}
-% \end{figure}
-
-% % subsection ab (end)
-
-% section results (end)
+% subsection res-fixspin (end)
 
@@
 \end{document}
-
-\section{Fixing velocity} % (fold)
-\label{sec:fixing_velocity}
-
-\begin{equation}
-\mathcal{V}^\mathrm{a}_{\sigma} 
-= 
-\sqrt{
-\mathcal{V}^\mathrm{ax} + 
-\mathcal{V}^\mathrm{ay} +
-\mathcal{V}^\mathrm{az}
-}
-\end{equation}
-
-\begin{equation}
-\mathcal{V}^\mathrm{a}_{\sigma\parallel} 
-= 
-\sqrt{
-\mathcal{V}^\mathrm{ax} + 
-\mathcal{V}^\mathrm{ay} 
-}
-\end{equation}
-
-\begin{align}
-\theta_{a} 
-&=
-\sin^{-1}
-\left( 
-\frac{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
-{\mathcal{V}^\mathrm{a}_{\sigma}}
-\right)
-\\
-\varphi_{a} 
-&=
-\sin^{-1}
-\left(
-\frac{\mathcal{V}^\mathrm{ay}}{\mathcal{V}^\mathrm{a}_{\sigma\parallel}}
-\right)
-\end{align}
-
-% section fixing_velocity (end)
-
-\section{Fixing spin} % (fold)
-\label{sec:fixing_spin}
-
-% section fixing_spin (end)

### 2017-04-25 mu/article/article.tex
Starting up V^{ab} description

@@
     structure. The maximum response zone is localized for an energy range from
-    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
+    0.90\,eV to 0.93\,eV and for a polarization angle of the
     incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
@@
 % %% Starting description of ALT |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
 % %%%%%%%%%%%%%%%%
@@
 most intense for $|\mathcal{V}^{\mathrm{x}}|$. In this case the polar angle is
-$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is $\theta=290.4^{\circ}$.
+$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is
+$\theta=290.4^{\circ}$.
 %
@@
 
-\subsection{Fixing spin} % (fold)
-\label{sec:res-fixspin}
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vx-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vy-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
+    structure. The maximum response zone is localized for an energy range from
+    0.04\,eV to 0.12\,eV and for a polarization angle of the
+    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
+    \label{fig:up-vab-mag-1}
+\end{figure}
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vx-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vy-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
+    structure. The local maximum response zone is localized for an energy range
+    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
+    from 25$^{\circ}$ to 50$^{\circ}$.}
+    \label{fig:up-vab-mag-2}
+\end{figure}
 
-% subsection res-fixspin (end)
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
+    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{up} structure. Both maxima where obtained for a polarization
+    angle $\alpha=40^{\circ}$. }
+    \label{fig:up-vab-comp-rtp-1}
+\end{figure}
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
+    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{up} structure. Both maxima where obtained for a polarization
+    angle $\alpha=40^{\circ}$. }
+    \label{fig:up-vab-comp-rtp-2}
+\end{figure}
 

### 2017-04-26 mu/article/article.tex
tarting V^a description for Up.

@@
 
+% %%%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{a}| 3D
+% %% files: 
+% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
 \begin{figure}[tb]
@@
     incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
-    \label{fig:alt-vab-mag}
+    \label{fig:alt-3d}
 \end{figure}
@@
 
-For the \emph{alt} structure we analyzed the energy range of energy from
-0.6\,eV to 1.0\,eV where we found the most intense response for
-$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
-\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
-resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
-angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
-can see that the onset of the response is when the energy of the incoming light
-is the same of the gap energy.
+For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
+1.0\,eV where we found the most intense response for
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
+\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
+from evaluate Eq. \eqref{eq:va-mag} using different polarization angles $\alpha$
+in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
+onset of the response is when the energy of the incoming light is the same of
+the gap energy.
 %
@@
 150$^{\circ}$ is the zone of the absolute maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
-another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
-maximum is obtained.
-From Fig. \ref{fig:alt-3d-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
-values of 30\,Km/s for the first zone mentioned before and 20\,Km/s for
-the second one. 
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
+% 
+\textcolor{red}{
+Also there is another zone of interest for energies from 0.70\,eV to 0.74\,eV
+and same polarization angles range where a local maximum is obtained. From Figs.
+\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
+$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
+respectively.
+}
 % %%%%%%%%%%%%%%%%
@@
 We also found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha = 145^{\circ}$. 
-%
-In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
-\ref{fig:alt-vy-comp-rtp} we present the results for
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
+polarization angle is $\alpha = 145^{\circ}$. In the top frames of Figs.
+\ref{fig:alt-vx-comp-rtp}  and \ref{fig:alt-vy-comp-rtp} we present the results
+for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
 polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the photon
-energy and the corresponding azimuthal $\theta$ and polar $\varphi$ angles.
-%
+energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles.
 Also in the bottom frames of Figs. \ref{fig:alt-vx-comp-rtp} and 
@@
 
+% %%%%%%%%%%%%%%%%%
+% %% Description of UP |V^{a}| 3D
+% %% files: 
+% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% up-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
 \begin{figure}[tb]
@@
     incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-vab-mag-1}
+    \label{fig:up-3d-1}
 \end{figure}
-\begin{figure}[tb]
+\begin{figure}[b]
     \centering
@@
     from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-vab-mag-2}
+    \label{fig:up-3d-2}
 \end{figure}
 
-\begin{figure}[tb]
+For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
+0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
+and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
+$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
+\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
+\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
+onset of the response is when the energy of the incoming light is the same of
+the gap energy.
+%
+From this picture we can see that for the zone between the energy range of
+0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
+$45^{\circ}$ is the zone of the absolute maximum response for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
+% 
+Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
+where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
+same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
+\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
+^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
+% %%%%%%%%%%%%%%%%
+% %% Starting description of ALT |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%
+\begin{figure}[t]
     \centering
@@
 \end{figure}
-\begin{figure}[tb]
+\begin{figure}[t]
     \centering
@@
 \end{figure}
+\textcolor{red}{
+We found that the absolute maximum of the response is obtained when the
+polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 
+%
+\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
+results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
+the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
+energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
+the energy range from 0.0\,eV to 0.16\,eV and from 
+}
 

### 2017-04-26 mu/article/article.tex
Up V^a at half description.

@@
 
+\begin{table}[t]
+\center
+\begin{tabular}{ccccc}\\
+\hline
+Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
+\cline{3-5}
+No. & type & $x$ & $y$ & $z$  \\
+\hline
+1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
+2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
+3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
+4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
+5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
+6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
+\hline
+\end{tabular}
+\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
+positions for the \emph{alt} structure. The structure unit cell was divided in
+six layers corresponding each one to atoms in different $z$ positions. The
+corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
+the corresponding number of layer.}
+\label{tab:alt-unitcell}
+\end{table}
+% 
+\begin{table}[t]
+\center
+\begin{tabular}{ccccc}\\
+\hline
+Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
+\cline{3-5}
+No. & type & $x$ & $y$ & $z$  \\
+\hline
+1 & H & -0.61516 & -1.77416 &  0.73196 \\
+1 & H &  0.61518 &  0.35514 &  0.73175 \\
+2 & C & -0.61516 & -1.77264 & -0.49138 \\
+2 & C & -0.61516 & -0.35600 & -0.72316 \\
+2 & C &  0.61516 &  0.35763 & -0.49087 \\
+\hline
+\end{tabular}
+\caption{Unit cell of \emph{up} structure. Layer division, atom types and
+positions for the \emph{up} structure. The structure unit cell was divided in
+two layers corresponding to hydrogen and carbon atoms.The corresponding layer
+atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
+number of layer.}
+\label{tab:up-unitcell}
+\end{table}
+
 We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
@@
 
-\begin{table}[tb]
-\center
-\begin{tabular}{ccccc}\\
-\hline
-Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
-\cline{3-5}
-No. & type & $x$ & $y$ & $z$  \\
-\hline
-1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
-2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
-3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
-4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
-5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
-6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
-\hline
-\end{tabular}
-\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
-positions for the \emph{alt} structure. The structure unit cell was divided in
-six layers corresponding each one to atoms in different $z$ positions. The
-corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
-the corresponding number of layer.}
-\label{tab:alt-unitcell}
-\end{table}
-
 The structures presented here where divided into layers to analyze the he
@@
 \ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.
-
-\begin{table}[tb]
-\center
-\begin{tabular}{ccccc}\\
-\hline
-Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
-\cline{3-5}
-No. & type & $x$ & $y$ & $z$  \\
-\hline
-1 & H & -0.61516 & -1.77416 &  0.73196 \\
-1 & H &  0.61518 &  0.35514 &  0.73175 \\
-2 & C & -0.61516 & -1.77264 & -0.49138 \\
-2 & C & -0.61516 & -0.35600 & -0.72316 \\
-2 & C &  0.61516 &  0.35763 & -0.49087 \\
-\hline
-\end{tabular}
-\caption{Unit cell of \emph{up} structure. Layer division, atom types and
-positions for the \emph{up} structure. The structure unit cell was divided in
-two layers corresponding to hydrogen and carbon atoms.The corresponding layer
-atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
-number of layer.}
-\label{tab:up-unitcell}
-\end{table}
 
@@
 0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone of the absolute maximum response for both,
+150$^{\circ}$ is the zone of the maximum response for both,
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
 % 
-\textcolor{red}{
-Also there is another zone of interest for energies from 0.70\,eV to 0.74\,eV
-and same polarization angles range where a local maximum is obtained. From Figs.
-\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
-$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
-respectively.
-}
 % %%%%%%%%%%%%%%%%
@@
 $\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ components for the fixed polarization angle.
+$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $145^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 $|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
-see that for the energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and
+see that for the energy range from 0.70\,eV to 0.75\,eV all the $xx$, $xy$, and
 $xz$ components contribute with almost the same intensity giving a total spin-
@@
 $\theta=290.4^{\circ}$.
+%
+Also there is another zone of interest for energies from 0.70\,eV to 0.75\,eV
+and same polarization angles range where a local maximum is obtained. From Figs.
+\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
+$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
+respectively.
 % 
@@
 % %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
 % %% Description of UP |V^{a}| 3D
@@
 % %%%%%%%%%%%%%%%%%
-\begin{figure}[tb]
+\begin{figure}[t]
     \centering
@@
 \end{figure}
-\begin{figure}[b]
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
+    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{up} structure. Both maxima where obtained for a polarization
+    angle $\alpha=40^{\circ}$. }
+    \label{fig:up-vab-comp-rtp-1}
+\end{figure}
+For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
+0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
+and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
+$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
+\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
+\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
+onset of the response is when the energy of the incoming light is the same of
+the gap energy.
+% %%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Starting description of UP |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%
+From this picture we can see that for the zone between the energy range of
+0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
+$45^{\circ}$ is the zone of the maximum response for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$.
+% %%%%%%%%%%%%%%%%%
+% %% 1.8 eV - 2.0 eV
+% %% Description of UP |V^{a}| 3D
+% %% files: 
+% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% up-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
+We found that the absolute maximum of the response is obtained when the
+polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is 0.088\,eV. 
+%
+\ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present the results
+for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
+polarization angle to $40^{\circ}$ for the \emph{up} structure vs photon energy
+and the corresponding polar $\varphi$ and azimuthal $\theta$ angles. In the
+bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vx-comp-rtp-1}
+we present the decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and
+$|\mathcal{V}^{\mathrm{y}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
+$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
+$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
+$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $40^{\circ}$. From
+Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with energy of
+0.088\,eV the three components have similar contributions and have values of
+$\mathcal{V}^{\mathrm{xx}}= -36.5$\,Km/s,
+$\mathcal{V}^{\mathrm{xy}}=-23.2$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}=39.8$\,Km/s resulting in a value of
+$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s and corresponding to polar and azimuthal
+angles of $\varphi=47.4$ and $\theta=212.5$, respectively. Also we found that. Now, from Fig.
+\ref{fig:up-vy-comp-rtp-1} we have that for the same incoming beam energy the
+$yx$ and $yy$ components have less contributions for the total response than the
+$yz$ having values of $\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s
+$\mathcal{V}^{\mathrm{yy}}=  8.5$\,Km/s $\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s
+and resulting in a value of the total response of
+$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal angles
+$\varphi=7.6$ $\theta=132.6$, respectively.
+\begin{figure}[t]
     \centering
@@
 \end{figure}
-
-For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
-0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
-and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
-$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
-\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
-\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
-onset of the response is when the energy of the incoming light is the same of
-the gap energy.
-%
-From this picture we can see that for the zone between the energy range of
-0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone of the absolute maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
-% 
-Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
-where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
-same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
-\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
-^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
-% %%%%%%%%%%%%%%%%
-% %% Starting description of ALT |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        alt-plots/alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%
-\begin{figure}[t]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
-    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{up} structure. Both maxima where obtained for a polarization
-    angle $\alpha=40^{\circ}$. }
-    \label{fig:up-vab-comp-rtp-1}
-\end{figure}
 \begin{figure}[t]
@@
 \end{figure}
-\textcolor{red}{
+Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
+where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
+same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
+\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
+^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
+% %%%%%%%%%%%%%%%%
+% %% Starting description of UP |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%
 We found that the absolute maximum of the response is obtained when the
@@
 the energy range from 0.0\,eV to 0.16\,eV and from
-}
 

### 2017-04-27 mu/article/article.tex
sab

@@
 \end{figure}
+% %%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Starting description of UP |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%
 For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
@@
 the gap energy.
-% %%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Starting description of UP |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        alt-plots/alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%
+% 
 From this picture we can see that for the zone between the energy range of
@@
 %
-\ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present the results
-for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
-polarization angle to $40^{\circ}$ for the \emph{up} structure vs photon energy
-and the corresponding polar $\varphi$ and azimuthal $\theta$ angles. In the
-bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vx-comp-rtp-1}
-we present the decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and
-$|\mathcal{V}^{\mathrm{y}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
-$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
+In Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present
+the results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
+fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
+vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
+angles. In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and 
+%
+\ref{fig:up-vx-comp-rtp-1} we present the decomposition of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
+corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
+$\mathcal{V}^{\mathrm{xz}}$ and
 $\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
@@
 $|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s and corresponding to polar and azimuthal
-angles of $\varphi=47.4$ and $\theta=212.5$, respectively. Also we found that. Now, from Fig.
-\ref{fig:up-vy-comp-rtp-1} we have that for the same incoming beam energy the
-$yx$ and $yy$ components have less contributions for the total response than the
-$yz$ having values of $\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s
-$\mathcal{V}^{\mathrm{yy}}=  8.5$\,Km/s $\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s
-and resulting in a value of the total response of
-$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal angles
-$\varphi=7.6$ $\theta=132.6$, respectively.
+angles of $\varphi=47.4$ and $\theta=212.5$, respectively.
+% 
+Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $yx$ and $yy$
+components have less contributions for the total response than the $yz$ and for
+the same incoming beam energy have values of $\mathcal{V}^{\mathrm{yx}}=
+-7.9$\,Km/s $\mathcal{V}^{\mathrm{yy}}= 8.5$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s resulting in a value of the total
+response of $|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal
+angles $\varphi=7.6$ $\theta=132.7$, respectively.
 \begin{figure}[t]
@@
 \end{figure}
-Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
-where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
-same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
-\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
-^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
+Also there is another energy range of interest, from 1.80\,eV to 2.10\,eV and
+same polarization angle $\alpha=40^{\circ}$ depicted in Fig. \ref{fig:up-3d-2},
+where two local maxima are obtained the \emph{up} structure. Again, in the
+bottom frame of Fig. \ref{fig:up-vx-comp- rtp-2} we have the three components
+$\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$, and
+$\mathcal{V}^{\mathrm{xz}}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and in
+the bottom frame of Fig.
+\ref{fig:up-vy-comp-rtp-2} the three components $\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ corresponding to $|\mathcal{V}^{\mathrm{y}}|$
 % %%%%%%%%%%%%%%%%

### 2017-04-27 mu/article/article.tex
sab
Finishing final description for alt structure

@@
 0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone of the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
-% 
+150$^{\circ}$ is the zone where the maximum response for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
 % %%%%%%%%%%%%%%%%
@@
 We also found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha = 145^{\circ}$. In the top frames of Figs.
-\ref{fig:alt-vx-comp-rtp}  and \ref{fig:alt-vy-comp-rtp} we present the results
-for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the
-polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the photon
-energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles.
-Also in the bottom frames of Figs. \ref{fig:alt-vx-comp-rtp} and 
+energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
+145^{\circ}$. In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
 %
+\ref{fig:alt-vy-comp-rtp} we present the results for
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)fixing
+the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the
+photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
+angles (left scale). Also in the bottom frames of Figs. 
+\ref{fig:alt-vx-comp-rtp} and
 \ref{fig:alt-vy-comp-rtp} we present the decomposition of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
-corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
+$|\mathcal{V}^{\mathrm{x}}|$ and 
+$|\mathcal{V}^{\mathrm{y}}|$ 
+in the corresponding components
+$\mathcal{V}^{\mathrm{xx}}$, 
+$\mathcal{V}^{\mathrm{xy}}$,
 $\mathcal{V}^{\mathrm{xz}}$ and
-$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $145^{\circ}$.
+$\mathcal{V}^{\mathrm{yx}}$,
+$\mathcal{V}^{\mathrm{yy}}$
+$\mathcal{V}^{\mathrm{yz}}$ 
+with $\alpha$ fixed to $145^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 $|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
-see that for the energy range from 0.70\,eV to 0.75\,eV all the $xx$, $xy$, and
-$xz$ components contribute with almost the same intensity giving a total spin-
-velocity of 19.3\,Km/s and spin polar and azimuthal angles $\varphi =
-45.8^{\circ}$ and $\theta=40.7^{\circ}$.
+see that for an incoming beam energy of 0.720\,eV the components contributions 
+are similar having values of
 %
-In the other hand, for the energy range from 0.88\,eV to 0.95\,eV there is a
-major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$ component
-resulting in a spin-velocity magnitude of 30.9\,Km/s being this magnitude the
-most intense for $|\mathcal{V}^{\mathrm{x}}|$. In this case the polar angle is
-$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is
-$\theta=290.4^{\circ}$.
+$\mathcal{V}^{\mathrm{xx}}= 10.5$\,Km/s, 
+$\mathcal{V}^{\mathrm{xy}}=  9.1$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}= 13.5$\,Km/s
 % 
-Also there is another zone of interest for energies from 0.70\,eV to 0.75\,eV
-and same polarization angles range where a local maximum is obtained. From Figs.
-\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
-$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
-respectively.
+resulting in a total spin-velocity 
 % 
-Also we notice that for the range of 0.70-0.74\,eV all the contributions are
-positive while for the range of 0.88-0.95\,eV the $xx$ component remains
-positive but the components $xy$ and $xz$ change in direction. This is due to
-\textcolor{red}{\large a change in the spin polarization}.
+$|\mathcal{V}^{\mathrm{x}}|=19.4$\,Km/s 
+% 
+and spin polar and azimuthal angles $\varphi = 45.8^{\circ}$ and
+$\theta=40.7^{\circ}$, respectively.
+%
+In the other hand, for an energy of the incoming beam equal to 0.912\,eV
+we found that the contribution of the components are 
+% 
+$\mathcal{V}^{\mathrm{xx}}=   4.8$\,Km/s
+$\mathcal{V}^{\mathrm{xy}}= -12.8$\,Km/s, and 
+$\mathcal{V}^{\mathrm{xz}}= -27.7$\,Km/s
+% 
+having a mayor response coming from the $xz$ component and resulting in a spin-
+velocity magnitude $|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s being this the
+absolute maximum fixing the spin-velocity in the $x$ direction. Then, the
+components give us polar and azimuthal angles with values of
+$\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
+variation with the incoming energy beam are presented in the right scale of the
+top frame of Fig \ref{fig:alt-vx-comp-rtp}.
+% 
+Finally we have that since the onset of the response till an energy of the
+incoming bean of 0.744\,eV the three components of $|\mathcal{V}^{\mathrm{x}}|$
+are positive while for the range from 0.746\,eV to 0.886\,eV the
+$\mathcal{V}^{\mathrm{xx}}$ component is positive but the
+$\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
+direction. This is due to a change in the spin polarization direction. Finally after the enrgy value of 0.886\,eV the response decreases and goes to zero. 
 % %%%%%%%%%%%%%%%%
@@
 Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
-\ref{fig:alt-vy-comp-rtp} we have that for the energy range from 0.70\,eV to
-0.74\,eV the $yz$ component have a more intense response than $yx$ and $yy$
-components and they give a total spin-velocity of 51.9\,Km/s and result in polar
-angle $\varphi=140.7^{\circ}$ and spin azimuthal angle of
-$\theta=221.5^{\circ}$.
+\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV the $yz$ component have a major contribution than the $yx$ and $yy$ components having values of 
 % 
-For the energy range from 0.88\,eV to 0.95\,eV all three components have similar
-intensities resulting in a spin-velocity magnitude of
-$|\mathcal{V}^{\mathrm{y}}| =$ 52.3\,Km/s being this response 1.7 times mores
-intense than the most intense response of $|\mathcal{V}^{\mathrm{x}}|$. The
-corresponding polar and azimuthal angles for $|\mathcal{V}^{\mathrm{y}}|$ in
-this energy range are $\theta = 129.0 ^{\circ}$ and $\varphi = 228.9 ^{\circ}$.
+$\mathcal{V}^{\mathrm{yx}}= -24.6$\,Km/s, 
+$\mathcal{V}^{\mathrm{yy}}= -21.8$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
 %
-Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
-negative for the energy range from 0.60\,eV to 1.0\,eV \textcolor{red}{keeping
-the same spin polarization for all this range.} 
+resulting in a total spin-velocity
 % 
-\begin{figure}[tb]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-lay}]
-    {\includegraphics[width=\linewidth]{figures/blank}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-lay}]
-    {\includegraphics[width=\linewidth]{figures/blank}}
-    \caption{Layer-by-layer contribution of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ for a polarization angle $\alpha=145^{\circ}$
-    for the \emph{alt} structure.}
-    \label{fig:alt-vab-lay}
-\end{figure}
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
-    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
-     \emph{alt} structure.}
-    \label{fig:alt-vyz-lay}
-\end{figure}
-
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT layer |V^{ab}|
-% %% files: 
-% %%%%%%%%%%%%%%%%
-In Fig. \ref{fig:alt-vab-lay} we show the layer-by-layer contribution of
-$|\mathcal{V}^{\mathrm{ab}}|$  for the \emph{alt} structure. The corresponding
-layer division and atom types and positions are presented in Table 
+$|\mathcal{V}^{\mathrm{y}}|=51.9$\,Km/s
 %
-\ref{tab:alt-unitcell} and depicted in Fig. \ref{fig:alt-struc}. In the layer-
-by-layer contribution for $|\mathcal{V}^{\mathrm{x}}|$ (Fig. \ref{fig:alt-vx-lay})
-we have that
+and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and $\theta=221.6^{\circ}$, respectively.
 %
-\textcolor{red}{\ldots}
+Also, for an energy of the incoming beam of 0.912\,eV we found that the contribution of the components are 
 % 
-Also, for the layer-by-layer contribution for $|\mathcal{V}^{\mathrm{y}}|$ (Fig.
-\ref{fig:alt-vy-lay}) we have that
+$\mathcal{V}^{\mathrm{xx}}=-26.7$\,Km/s
+$\mathcal{V}^{\mathrm{xy}}=-30.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}=-32.9$\,Km/s
 % 
-\textcolor{red}{\ldots}
+having all the three components similar contributions and resulting in a spin-
+velocity magnitude $|\mathcal{V}^{\mathrm{y}}|=52.3$\,Km/s being this the
+absolute maximum spin-velocity for the velocity fixed to the $y$ direction and
+being 1.7 times more intense than the maximum of $|\mathcal{V}^{\mathrm{x}}|$.
+The components then give us the polar and azimuthal angles with values of
+$\varphi=129.0^{\circ}$ and $\theta=228.9^{\circ}$, respectively. This angles
+and the corresponding variation is presented in the right sale of the top frame
+of Fig. \ref{fig:alt-vy-comp-rtp}.
 % 
+We also have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
+negative keeping the same spin polarization since the onset of the response to a
+energy of the incoming beam of 0.886\,eV when the response decreases and goes to
+zero.
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-From the bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
+From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
 the \emph{alt} structure the most intense component of
@@
 We found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is 0.088\,eV. 
+polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
+0.088\,eV.
 %
@@
 where two local maxima are obtained the \emph{up} structure. Again, in the
-bottom frame of Fig. \ref{fig:up-vx-comp- rtp-2} we have the three components
+bottom frame of Fig. \ref{fig:up-vx-comp-rtp-2} we have the three components
 $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$, and

### 2017-04-28 mu/article/article.tex
Cheking lost fig.
Up first energy rane description completed.

@@
 
+\textbf{Alt structure.}
+
 % %%%%%%%%%%%%%%%%%
@@
 energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
-145^{\circ}$. In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
+145^{\circ}$. 
+% 
+In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
 %
 \ref{fig:alt-vy-comp-rtp} we present the results for
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)fixing
-the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs the
-photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles (left scale). Also in the bottom frames of Figs. 
-\ref{fig:alt-vx-comp-rtp} and
-\ref{fig:alt-vy-comp-rtp} we present the decomposition of
-$|\mathcal{V}^{\mathrm{x}}|$ and 
-$|\mathcal{V}^{\mathrm{y}}|$ 
-in the corresponding components
-$\mathcal{V}^{\mathrm{xx}}$, 
-$\mathcal{V}^{\mathrm{xy}}$,
-$\mathcal{V}^{\mathrm{xz}}$ and
-$\mathcal{V}^{\mathrm{yx}}$,
-$\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ 
-with $\alpha$ fixed to $145^{\circ}$.
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
+fixing the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs
+the photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
+angles (right scale). Also in the bottom frames of Figs. 
+% 
+\ref{fig:alt-vx-comp-rtp} and \ref{fig:alt-vy-comp-rtp} we present the
+decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
+in the corresponding components $\mathcal{V}^{\mathrm{xx}}$,
+$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
+$\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$
+$\mathcal{V}^{\mathrm{yz}}$ with $\alpha$ fixed to $145^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 having a mayor response coming from the $xz$ component and resulting in a spin-
-velocity magnitude $|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s being this the
-absolute maximum fixing the spin-velocity in the $x$ direction. Then, the
-components give us polar and azimuthal angles with values of
+velocity magnitude 
+% 
+$|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s 
+% 
+being this the absolute maximum fixing the spin-velocity in the $x$ direction.
+Then, the components give us polar and azimuthal angles with values of
 $\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
@@
 $\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
-direction. This is due to a change in the spin polarization direction. Finally after the enrgy value of 0.886\,eV the response decreases and goes to zero. 
+direction. This is due to a change in the spin polarization direction. Finally
+after the energy value of 0.886\,eV the response decreases and goes to zero.
 % %%%%%%%%%%%%%%%%
@@
 Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
-\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV the $yz$ component have a major contribution than the $yx$ and $yy$ components having values of 
+\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV
+the $yz$ component have a major contribution than the $yx$ and $yy$ components
+having values of
 % 
@@
 %
-and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and $\theta=221.6^{\circ}$, respectively.
+and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and
+$\theta=221.6^{\circ}$, respectively.
 %
-Also, for an energy of the incoming beam of 0.912\,eV we found that the contribution of the components are 
+Also, for an energy of the incoming beam of 0.912\,eV we found that the
+contribution of the components are
 % 
@@
 % %%%%%%%%%%%%%%%%
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
+    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
+     \emph{alt} structure.}
+    \label{fig:alt-vyz-lay}
+\end{figure}
 From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{Up structure.}
 
@@
 \end{figure}
-% %%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Starting description of UP |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        alt-plots/alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%
+
 For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
@@
 0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone of the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
+$45^{\circ}$ is the zone where the maximum responses for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
+% 
+We found that the absolute maximum of the response is obtained when the
+polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
+0.088\,eV.
+%
+In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
+% 
+\ref{fig:up-vy-comp-rtp-1} we present the results for
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
+fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
+vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
+angles (right scale). In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1}
+% 
+and \ref{fig:up-vx-comp-rtp-1} we present the decomposition of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
+corresponding $\mathcal{V}^{\mathrm{xx}}$, 
+$\mathcal{V}^{\mathrm{xy}}$,
+$\mathcal{V}^{\mathrm{xz}}$, and
+$\mathcal{V}^{\mathrm{yx}}$, 
+$\mathcal{V}^{\mathrm{yy}}$,
+$\mathcal{V}^{\mathrm{yz}}$ 
+components with $\alpha$ fixed to $40^{\circ}$. 
 % %%%%%%%%%%%%%%%%%
 % %% 1.8 eV - 2.0 eV
+% %% Description of UP |V^{a}|, components and RTP
+% %% files: 
+% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
+% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
+% %% up-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
+From Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with
+energy of 0.088\,eV the three components have similar contributions and have
+values of 
+% 
+$\mathcal{V}^{\mathrm{xx}}=-36.5$\,Km/s,
+$\mathcal{V}^{\mathrm{xy}}=-23.2$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}= 39.8$\,Km/s 
+% 
+resulting in a value of
+% 
+$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s 
+% 
+being this value the absolute maximum obtained when the spin-velocity is fixed
+in the $x$ direction. To this value corresponds a polar and azimuthal angles of
+$\varphi=47.4$ and $\theta=212.5$, respectively.
+% 
+Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $yx$ and $yy$
+components have less contributions for the total response than the $yz$ and for
+the same incoming beam energy have values of 
+% 
+$\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s 
+$\mathcal{V}^{\mathrm{yy}}=  8.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}= 87.2$\,Km/s 
+% 
+resulting in a value of the total response of
+% 
+$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s
+% 
+being this value the absolute maximum obtained when the spin-velocity is fixed
+in the $y$ direction and being 1.5 times more intense than
+$|\mathcal{V}^{\mathrm{x}}|$ and corresponding spin polar and azimuthal angles
+$\varphi=7.6$ $\theta=132.7$, respectively. We also found that since the onset
+of the response till an energy for the incoming beam of 0.118\,eV the components
+of both, $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have no
+change in the spin polarization direction. Finally, after this energy value both
+goes to zero.
+% %%%%%%%%%%%%%%%%%
+% %% 1.80 eV - 2.10 eV
 % %% Description of UP |V^{a}| 3D
@@
 % %%%%%%%%%%%%%%%%%
-We found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
-0.088\,eV.
-%
-In Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present
-the results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
-fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
-vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles. In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and 
-%
-\ref{fig:up-vx-comp-rtp-1} we present the decomposition of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
-corresponding $\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$,
-$\mathcal{V}^{\mathrm{xz}}$ and
-$\mathcal{V}^{\mathrm{yx}},\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $40^{\circ}$. From
-Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with energy of
-0.088\,eV the three components have similar contributions and have values of
-$\mathcal{V}^{\mathrm{xx}}= -36.5$\,Km/s,
-$\mathcal{V}^{\mathrm{xy}}=-23.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}=39.8$\,Km/s resulting in a value of
-$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s and corresponding to polar and azimuthal
-angles of $\varphi=47.4$ and $\theta=212.5$, respectively.
-% 
-Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $yx$ and $yy$
-components have less contributions for the total response than the $yz$ and for
-the same incoming beam energy have values of $\mathcal{V}^{\mathrm{yx}}=
--7.9$\,Km/s $\mathcal{V}^{\mathrm{yy}}= 8.5$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s resulting in a value of the total
-response of $|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal
-angles $\varphi=7.6$ $\theta=132.7$, respectively.
 \begin{figure}[t]

### 2017-04-28 mu/article/article.tex
Description completed.

@@
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
-$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.21374498\,Km/s for an
+$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
 energy incident beam of 0.72\,eV. This component and the corresponding layer by
@@
 0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone where the maximum responses for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
+$45^{\circ}$ is the zone where the maximum zone of response for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
 % 
@@
 % 
-\ref{fig:up-vy-comp-rtp-1} we present the results for
+\ref{fig:up-vy-comp-rtp-1} we present the results of
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
@@
 vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles (right scale). In the bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1}
-% 
-and \ref{fig:up-vx-comp-rtp-1} we present the decomposition of
+angles (right scale). In the bottom frames of same figures we present the decomposition of
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
@@
 components with $\alpha$ fixed to $40^{\circ}$. 
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vx-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vy-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
+    structure. The local maximum response zone is localized for an energy range
+    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
+    from 25$^{\circ}$ to 50$^{\circ}$.}
+    \label{fig:up-3d-2}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
+    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{up} structure. Both maxima where obtained for a polarization
+    angle $\alpha=40^{\circ}$. }
+    \label{fig:up-vab-comp-rtp-2}
+\end{figure}
 % %%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%
+Also there is another energy range of interest for an incoming energy beam from
+1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-2} where two local maxima
+of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ are obtained
+for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:va-mag} and
+\eqref{eq:vab}.
+% 
+From this figure we have that for the zone between the energy ranges from
+1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and angles from $30^{\circ}$
+to $45^{\circ}$ those maxima zones are hold. 
+% 
+We found that the maxima are obtained when the polarization angle is fixed to
+$40^{\circ}$ and the corresponding energies are 1.934\,eV and 1.972\,eV.
+% 
+Again, in the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
+% 
+\ref{fig:up-vy-comp-rtp-2} we present the results of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
+fixing the polarization angle to $\alpha=40^{\circ}$ vs the photon energy and
+the corresponding polar $\varphi$ and azimuthal $\theta$ angles (right scale)
+for the \emph{up} structure. In the bottom frames of same figures we present the
+three components $\mathrm{xx}$, $\mathrm{xy}$, $\mathrm{xz}$, and $\mathrm{yx}$,
+$\mathrm{yy}$, $\mathrm{yz}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and
+$|\mathcal{V}^{\mathrm{y}}|$ fixing the polarization angle to $40^{\circ}$.
 \begin{figure}[t]
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vx-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
+    \subfigure[\ \label{fig:up-vyz-lay-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vy-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
-    structure. The local maximum response zone is localized for an energy range
-    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
-    from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-3d-2}
+    \subfigure[\ \label{fig:up-vyz-lay-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
+    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
+     \emph{up} structure.}
+    \label{fig:up-vyz-lay}
 \end{figure}
-\begin{figure}[t]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
-    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{up} structure. Both maxima where obtained for a polarization
-    angle $\alpha=40^{\circ}$. }
-    \label{fig:up-vab-comp-rtp-2}
-\end{figure}
-Also there is another energy range of interest, from 1.80\,eV to 2.10\,eV and
-same polarization angle $\alpha=40^{\circ}$ depicted in Fig. \ref{fig:up-3d-2},
-where two local maxima are obtained the \emph{up} structure. Again, in the
-bottom frame of Fig. \ref{fig:up-vx-comp-rtp-2} we have the three components
-$\mathcal{V}^{\mathrm{xx}}$, $\mathcal{V}^{\mathrm{xy}}$, and
-$\mathcal{V}^{\mathrm{xz}}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and in
-the bottom frame of Fig.
-\ref{fig:up-vy-comp-rtp-2} the three components $\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ corresponding to $|\mathcal{V}^{\mathrm{y}}|$
 % %%%%%%%%%%%%%%%%
-% %% Starting description of UP |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        alt-plots/alt-3d-vab.gp
+% %% Starting description of UP |V^{x}|, components and RTP
+% %% files: vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
+% %%        vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
+% %%        alt-plots/up-vab-rtp.gp
 % %%%%%%%%%%%%%%%%
-We found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 
+We found that for both cases, $|\mathcal{V}^{\mathrm{x}}|$ and
+$|\mathcal{V}^{\mathrm{y}}|$, the corresponding components have similar
+contributions and for an incoming energy beam of 1.934\,eV have values of
 % 
-\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
-results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
-the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
-energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
-the energy range from 0.0\,eV to 0.16\,eV and from
+$\mathcal{V}^{\mathrm{xx}}= 2.3$\,Km/s, 
+$\mathcal{V}^{\mathrm{xy}}= 3.8$\,Km/s, 
+$\mathcal{V}^{\mathrm{xz}}= 4.9$\,Km/s, and
+$\mathcal{V}^{\mathrm{yx}}=11.5$\,Km/s,
+$\mathcal{V}^{\mathrm{yy}}=17.0$\,Km/s,
+$\mathcal{V}^{\mathrm{yz}}=20.4$\,Km/s
+resulting in a in values of 
+$|\mathcal{V}^{\mathrm{x}}|= 6.6$\,Km/s
+$|\mathcal{V}^{\mathrm{y}}|=28.7$\,Km/s
+% 
+being $|\mathcal{V}^{\mathrm{y}}|$ 4.3 times more intense than
+$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
+and azimuthal spin polarization angels $\varphi= 42.0^{\circ}$ and $\theta=
+58.7^{\circ}$ for $|\mathcal{V}^{\mathrm{x}}|$ and $\varphi= 45.2^{\circ}$ and
+$\theta= 56.0^{\circ}$ for $|\mathcal{V}^{\mathrm{y}}|$.
+% 
+Alike, for an incoming energy beam of 1.972\,eV all the components of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have similar
+contributions having values of
+% 
+$\mathcal{V}^{\mathrm{xx}}= -5.0$\,Km/s, 
+$\mathcal{V}^{\mathrm{xy}}= -5.8$\,Km/s, 
+$\mathcal{V}^{\mathrm{xz}}= -6.2$\,Km/s, and
+$\mathcal{V}^{\mathrm{yx}}=-26.8$\,Km/s,
+$\mathcal{V}^{\mathrm{yy}}=-28.9$\,Km/s,
+$\mathcal{V}^{\mathrm{yz}}=-29.7$\,Km/s
+resulting in a in values of 
+$|\mathcal{V}^{\mathrm{x}}|= 9.9$\,Km/s
+$|\mathcal{V}^{\mathrm{y}}|=49.4$\,Km/s
+% 
+being $|\mathcal{V}^{\mathrm{y}}|$ 5.0 times more intense than
+$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
+and azimuthal spin polarization angles $\varphi=129.0^{\circ}$
+$\theta=229.1^{\circ}$ or $|\mathcal{V}^{\mathrm{x}}|$ and
+$\varphi=127.0^{\circ}$ and $\theta= 227.1^{\circ}$ for
+$|\mathcal{V}^{\mathrm{y}}|$.
+% 
+Finally we have that all the tree components of $|\mathcal{V}^{\mathrm{x}}|$ and
+$|\mathcal{V}^{\mathrm{y}}|$ keep the spin polarization positive till an energy
+of the incoming beam equal to 1.954\,eV when the spin polarization changes the
+direction and after an energy for the incoming beam equal to 2.05\,eV both
+responses goes to zero.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT layer |V^{yz}|
+% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
+% %%         alt-plots/alt-vab-layers.gp
+% %%%%%%%%%%%%%%%%
+From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
+% 
+\ref{fig:up-vab-comp-rtp-2} we can see that for the \emph{up} structure again
+the most intense component of $|\mathcal{V}^{\mathrm{x}}|$ and
+$|\mathcal{V}^{\mathrm{y}}|$ corresponds to $\mathcal{V}^{\mathrm{yz}}$ which
+has a value of 87.2\,Km/s for an energy incident beam of 0.088\,eV and
+-29.7\,Km/s for an energy incident beam of 1.972\,eV. This component and the
+corresponding layer by layer contribution is depicted in Fig. 
+\ref{fig:up-vyz-lay}s.
+% 
+From this figure we have that for the energy range from 0\,eV to 0.2\,eV the
+response comes from the second layer composed by carbon atoms presented in Tab.
+\ref{tab:up-unitcell} and denoted by the number 2 in Fig. \ref{fig:up-struc}. In
+the other hand, the response for the energy range from 1.8\,eV to 2.1\,eV almost
+all the response comes from the carbon atoms having a leaser contribution from
+the hydrogen layer.
 

### 2017-05-03 mu/article/article.tex
Thery section added for layer contribution.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Fixing velocity.}\label{sec:theory-fixvel}
-Considering that we have 2D structures we fixed the velocity in the $xy$ plane
-along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
-\begin{equation}\label{eq:va-mag}
-|\mathcal{V}^{\mathrm{a}}| = 
-\sqrt {
-(\mathcal{V}^{\mathrm{ax}})^{2} +
-(\mathcal{V}^{\mathrm{ay}})^{2} +
-(\mathcal{V}^{\mathrm{az}})^{2} 
-},
-\end{equation}
-and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
-\begin{align}
-\theta  =& \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}}
-{|\mathcal{V}^{\mathrm{a}}|} \right),
-& 0 \leq &\theta \leq \pi, 
-\label{eq:polar-ang}
-\\
-\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
-{\mathcal{V}^{\mathrm{ax}}} \right),
-& 0 \leq &\varphi \leq 2\pi.
-\label{eq:azimuthal-ang} 
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}| 
+|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
 &=
 \sqrt{
-(\mathcal{V}^{\mathrm{ax}})^{2} +
-(\mathcal{V}^{\mathrm{ay}})^{2} 
-}, \\
-\gamma_{\mathrm{b}} 
+(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
+(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
+}, 
+\label{eq:vs-mag}
+\\
+\gamma_{\mathrm{b}} (\omega)
 &=
-\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
-{\mathcal{V}^{\mathrm{ax}}} \right),
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
+{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
+\label{eq:gamma-ang}
 \end{align}
@@
 $x$ axis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Fixing velocity.}\label{sec:theory-fixvel}
+Considering that we have 2D structures we fixed the velocity in the $xy$ plane
+along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
+\begin{equation}
+|\mathcal{V}^{\mathrm{a}}| (\omega)= 
+\sqrt {
+(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
+(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
+(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
+},
+\label{eq:vv-mag}
+\end{equation}
+and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
+\begin{align}
+\theta  (\omega)
+=& 
+\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
+{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
+& 0 \leq &\theta \leq \pi, 
+\label{eq:polar-ang}
+\\
+\varphi (\omega)
+=& 
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
+{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
+& 0 \leq &\varphi \leq 2\pi.
+\label{eq:azimuthal-ang} 
+\end{align}
+
+\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}
+
+For a layered system we have that the total contribution of Eqns. 
+\eqref{eq:vs-mag} and \eqref{eq:vv-mag} is given \cite{arzatePRB14} by
+
+\begin{align}
+|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|
+=& 
+\ell_{\mathrm{eff}}
+\sum_{\ell=1}^{N_{\mathrm{eff}}}
+|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega)|
+\label{eq:vs-layer}
+\\
+|\mathcal{V}^{\mathrm{a}}(\omega)|
+=&
+\ell_{\mathrm{eff}}
+\sum_{\ell=1}^{N_{\mathrm{eff}}}
+|\mathcal{V}^{\mathrm{a}} (\ell | \omega)|
+\label{eq:vv-layer}
+\end{align}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Fixing spin} % (fold)
+\label{sec:res-fixspin}
+
+% section res-fixspin (end)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
-from evaluate Eq. \eqref{eq:va-mag} using different polarization angles $\alpha$
+from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$
 in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
@@
 $\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
-\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
+\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
 \eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
@@
 of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ are obtained
-for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:va-mag} and
+for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:vv-mag} and
 \eqref{eq:vab}.

### 2017-05-03 mu/article/article.tex
Mu included in theory. Theory sec reorganized.

@@
 \label{sec:theory}
-The equation for $\mathcal{V}^{\mathrm{ab}}$ for normal incidence in the $xy$
-plane with a polarization angle $\alpha$ is given by
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Pure spin current %%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Pure spin-current} % (fold)
+\label{sec:theory-pure_spin_current}
+
+The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
+direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
+\begin{equation}
+\dot{K} = \mu^{\mathrm{abcd}}(\omega)
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
+\label{eq:dotk}
+\end{equation}
+where
+\begin{widetext}
+\begin{equation}
+\mu^{\mathrm{abcd}} (\omega) =
+\frac{\pi e^{2}}{\hbar^{2}} \int 
+\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
+\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
+r^{\mathrm{c}}_{vc'} 
+r^{\mathrm{d}}_{cv } +
+r^{\mathrm{d}}_{vc'} 
+r^{\mathrm{c}}_{cv } ) \right]
+\delta(\omega-\omega_{cv})
+\label{eq:mu}
+\end{equation}
+\end{widetext}
+is the corresponding spin density injection current pseudotensor. The $'$
+in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
+covers these states.
+
+Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
+which the spin polarized in the $\mathrm{b}$   direction moves along the
+$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
+polarization angle $\alpha$. Then,
 \begin{widetext}
@@
 
+% section theory-pure_spin_current (end)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Fixing spin}\label{sec:theory-fixspin}
-In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
-$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
+Considering that we have 2D structures we can fix the spin direction along the
+$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
+spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle
+$\gamma_{b}$ as
 \begin{align}
@@
 \subsection{Fixing velocity.}\label{sec:theory-fixvel}
-Considering that we have 2D structures we fixed the velocity in the $xy$ plane
-along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
+
+In a similar way we can fix the velocity in the $xy$ plane
+along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
 \begin{equation}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Fixing spin} % (fold)
 \label{sec:res-fixspin}
+
+\blindtext
 

### 2017-05-04 mu/article/article.tex
Reorganization of sections.

@@
 
-\subsection{Pure spin-current} % (fold)
+\subsection{Pure spin velocity} % (fold)
 \label{sec:theory-pure_spin_current}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Spin velocity} % (fold)
+\label{sec:res-pure_spin_current_and_spin_velocity}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{plots/vab-str-comp}
+    \caption{Comparison of most intense responses for
+    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs structures}
+    \label{fig:vab-str-comp}
+\end{figure}
+
+In figure \ref{fig:vab-str-comp}
+
+% section res-pure_spin_current_and_spin_velocity (end)
 
@@
 
-\section{Fixing spin} % (fold)
+\subsection{Fixing spin} % (fold)
 \label{sec:res-fixspin}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Fixing velocity} % (fold)
 \label{sec:res-fixvel}
-
-\textbf{Alt structure.}
-
-% %%%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{a}| 3D
-% %% files: 
-% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%%
-\begin{figure}[tb]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vx}]
-    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vy}]
-    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
-    structure. The maximum response zone is localized for an energy range from
-    0.90\,eV to 0.93\,eV and for a polarization angle of the
-    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
-    \label{fig:alt-3d}
-\end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
-    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
-    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
-    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{alt} structure. Both maxima where obtained for a polarization
-    angle $\alpha=145^{\circ}$. }
-    \label{fig:alt-vab-comp-rtp}
-\end{figure}
-
-For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
-1.0\,eV where we found the most intense response for 
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
-\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
-from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$
-in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
-onset of the response is when the energy of the incoming light is the same of
-the gap energy.
-%
-From this picture we can see that for the zone between the energy range of
-0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone where the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
-% %%%%%%%%%%%%%%%%
-% %% Starting description of ALT |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        alt-plots/alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%
-We also found that the absolute maximum of the response is obtained when the
-energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
-145^{\circ}$. 
-% 
-In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
-%
-\ref{fig:alt-vy-comp-rtp} we present the results for
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
-fixing the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs
-the photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles (right scale). Also in the bottom frames of Figs. 
-% 
-\ref{fig:alt-vx-comp-rtp} and \ref{fig:alt-vy-comp-rtp} we present the
-decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
-in the corresponding components $\mathcal{V}^{\mathrm{xx}}$,
-$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
-$\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ with $\alpha$ fixed to $145^{\circ}$.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{x}|, components and RTP
-% %% files: vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        alt-plots/alt-vab-rtp.gp
-% %%%%%%%%%%%%%%%%
-Making the analysis for the components and angles for
-$|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
-see that for an incoming beam energy of 0.720\,eV the components contributions 
-are similar having values of
-%
-$\mathcal{V}^{\mathrm{xx}}= 10.5$\,Km/s, 
-$\mathcal{V}^{\mathrm{xy}}=  9.1$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}= 13.5$\,Km/s
-% 
-resulting in a total spin-velocity 
-% 
-$|\mathcal{V}^{\mathrm{x}}|=19.4$\,Km/s 
-% 
-and spin polar and azimuthal angles $\varphi = 45.8^{\circ}$ and
-$\theta=40.7^{\circ}$, respectively.
-%
-In the other hand, for an energy of the incoming beam equal to 0.912\,eV
-we found that the contribution of the components are 
-% 
-$\mathcal{V}^{\mathrm{xx}}=   4.8$\,Km/s
-$\mathcal{V}^{\mathrm{xy}}= -12.8$\,Km/s, and 
-$\mathcal{V}^{\mathrm{xz}}= -27.7$\,Km/s
-% 
-having a mayor response coming from the $xz$ component and resulting in a spin-
-velocity magnitude 
-% 
-$|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s 
-% 
-being this the absolute maximum fixing the spin-velocity in the $x$ direction.
-Then, the components give us polar and azimuthal angles with values of
-$\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
-variation with the incoming energy beam are presented in the right scale of the
-top frame of Fig \ref{fig:alt-vx-comp-rtp}.
-% 
-Finally we have that since the onset of the response till an energy of the
-incoming bean of 0.744\,eV the three components of $|\mathcal{V}^{\mathrm{x}}|$
-are positive while for the range from 0.746\,eV to 0.886\,eV the
-$\mathcal{V}^{\mathrm{xx}}$ component is positive but the
-$\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
-direction. This is due to a change in the spin polarization direction. Finally
-after the energy value of 0.886\,eV the response decreases and goes to zero.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{y}|, components and RTP
-% %% files: vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        alt-plots/alt-vab-rtp.gp
-% %%%%%%%%%%%%%%%%
-Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
-\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV
-the $yz$ component have a major contribution than the $yx$ and $yy$ components
-having values of
-% 
-$\mathcal{V}^{\mathrm{yx}}= -24.6$\,Km/s, 
-$\mathcal{V}^{\mathrm{yy}}= -21.8$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
-%
-resulting in a total spin-velocity
-% 
-$|\mathcal{V}^{\mathrm{y}}|=51.9$\,Km/s
-%
-and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and
-$\theta=221.6^{\circ}$, respectively.
-%
-Also, for an energy of the incoming beam of 0.912\,eV we found that the
-contribution of the components are
-% 
-$\mathcal{V}^{\mathrm{xx}}=-26.7$\,Km/s
-$\mathcal{V}^{\mathrm{xy}}=-30.6$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}=-32.9$\,Km/s
-% 
-having all the three components similar contributions and resulting in a spin-
-velocity magnitude $|\mathcal{V}^{\mathrm{y}}|=52.3$\,Km/s being this the
-absolute maximum spin-velocity for the velocity fixed to the $y$ direction and
-being 1.7 times more intense than the maximum of $|\mathcal{V}^{\mathrm{x}}|$.
-The components then give us the polar and azimuthal angles with values of
-$\varphi=129.0^{\circ}$ and $\theta=228.9^{\circ}$, respectively. This angles
-and the corresponding variation is presented in the right sale of the top frame
-of Fig. \ref{fig:alt-vy-comp-rtp}.
-% 
-We also have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
-negative keeping the same spin polarization since the onset of the response to a
-energy of the incoming beam of 0.886\,eV when the response decreases and goes to
-zero.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT layer |V^{yz}|
-% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
-% %%         alt-plots/alt-vab-layers.gp
-% %%%%%%%%%%%%%%%%
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
-    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
-     \emph{alt} structure.}
-    \label{fig:alt-vyz-lay}
-\end{figure}
-From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
-the \emph{alt} structure the most intense component of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
-$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
-energy incident beam of 0.72\,eV. This component and the corresponding layer by
-layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
-we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
-layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
-Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
-4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
-for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
-from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
-in the same direction resulting in a total response
-$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
-0.912\,eV.
 
@@
 $|\mathcal{V}^{\mathrm{y}}|$ fixing the polarization angle to $40^{\circ}$.
-\begin{figure}[t]
-    \centering
-    \subfigure[\ \label{fig:up-vyz-lay-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
-    \\
-    \subfigure[\ \label{fig:up-vyz-lay-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
-    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
-     \emph{up} structure.}
-    \label{fig:up-vyz-lay}
-\end{figure}
 % %%%%%%%%%%%%%%%%
@@
 responses goes to zero.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{Alt structure.}
+
+% %%%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{a}| 3D
+% %% files: 
+% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %% alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vx}]
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vy}]
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
+    structure. The maximum response zone is localized for an energy range from
+    0.90\,eV to 0.93\,eV and for a polarization angle of the
+    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
+    \label{fig:alt-3d}
+\end{figure}
+
+\begin{figure}[tb]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
+    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
+    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
+    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
+    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
+    \emph{alt} structure. Both maxima where obtained for a polarization
+    angle $\alpha=145^{\circ}$. }
+    \label{fig:alt-vab-comp-rtp}
+\end{figure}
+
+For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
+1.0\,eV where we found the most intense response for 
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
+\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
+from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$
+in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
+onset of the response is when the energy of the incoming light is the same of
+the gap energy.
+%
+From this picture we can see that for the zone between the energy range of
+0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
+150$^{\circ}$ is the zone where the maximum response for both,
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
 % %%%%%%%%%%%%%%%%
-% %% Description of ALT layer |V^{yz}|
+% %% Starting description of ALT |V^{a}|, components and RTP
+% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        alt-plots/alt-3d-vab.gp
+% %%%%%%%%%%%%%%%%
+We also found that the absolute maximum of the response is obtained when the
+energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
+145^{\circ}$. 
+% 
+In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
+%
+\ref{fig:alt-vy-comp-rtp} we present the results for
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
+fixing the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs
+the photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
+angles (right scale). Also in the bottom frames of Figs. 
+% 
+\ref{fig:alt-vx-comp-rtp} and \ref{fig:alt-vy-comp-rtp} we present the
+decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
+in the corresponding components $\mathcal{V}^{\mathrm{xx}}$,
+$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
+$\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$
+$\mathcal{V}^{\mathrm{yz}}$ with $\alpha$ fixed to $145^{\circ}$.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{x}|, components and RTP
+% %% files: vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%        alt-plots/alt-vab-rtp.gp
+% %%%%%%%%%%%%%%%%
+Making the analysis for the components and angles for
+$|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
+see that for an incoming beam energy of 0.720\,eV the components contributions 
+are similar having values of
+%
+$\mathcal{V}^{\mathrm{xx}}= 10.5$\,Km/s, 
+$\mathcal{V}^{\mathrm{xy}}=  9.1$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}= 13.5$\,Km/s
+% 
+resulting in a total spin-velocity 
+% 
+$|\mathcal{V}^{\mathrm{x}}|=19.4$\,Km/s 
+% 
+and spin polar and azimuthal angles $\varphi = 45.8^{\circ}$ and
+$\theta=40.7^{\circ}$, respectively.
+%
+In the other hand, for an energy of the incoming beam equal to 0.912\,eV
+we found that the contribution of the components are 
+% 
+$\mathcal{V}^{\mathrm{xx}}=   4.8$\,Km/s
+$\mathcal{V}^{\mathrm{xy}}= -12.8$\,Km/s, and 
+$\mathcal{V}^{\mathrm{xz}}= -27.7$\,Km/s
+% 
+having a mayor response coming from the $xz$ component and resulting in a spin-
+velocity magnitude 
+% 
+$|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s 
+% 
+being this the absolute maximum fixing the spin-velocity in the $x$ direction.
+Then, the components give us polar and azimuthal angles with values of
+$\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
+variation with the incoming energy beam are presented in the right scale of the
+top frame of Fig \ref{fig:alt-vx-comp-rtp}.
+% 
+Finally we have that since the onset of the response till an energy of the
+incoming bean of 0.744\,eV the three components of $|\mathcal{V}^{\mathrm{x}}|$
+are positive while for the range from 0.746\,eV to 0.886\,eV the
+$\mathcal{V}^{\mathrm{xx}}$ component is positive but the
+$\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
+direction. This is due to a change in the spin polarization direction. Finally
+after the energy value of 0.886\,eV the response decreases and goes to zero.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{y}|, components and RTP
+% %% files: vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%        alt-plots/alt-vab-rtp.gp
+% %%%%%%%%%%%%%%%%
+Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
+\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV
+the $yz$ component have a major contribution than the $yx$ and $yy$ components
+having values of
+% 
+$\mathcal{V}^{\mathrm{yx}}= -24.6$\,Km/s, 
+$\mathcal{V}^{\mathrm{yy}}= -21.8$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
+%
+resulting in a total spin-velocity
+% 
+$|\mathcal{V}^{\mathrm{y}}|=51.9$\,Km/s
+%
+and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and
+$\theta=221.6^{\circ}$, respectively.
+%
+Also, for an energy of the incoming beam of 0.912\,eV we found that the
+contribution of the components are
+% 
+$\mathcal{V}^{\mathrm{xx}}=-26.7$\,Km/s
+$\mathcal{V}^{\mathrm{xy}}=-30.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}=-32.9$\,Km/s
+% 
+having all the three components similar contributions and resulting in a spin-
+velocity magnitude $|\mathcal{V}^{\mathrm{y}}|=52.3$\,Km/s being this the
+absolute maximum spin-velocity for the velocity fixed to the $y$ direction and
+being 1.7 times more intense than the maximum of $|\mathcal{V}^{\mathrm{x}}|$.
+The components then give us the polar and azimuthal angles with values of
+$\varphi=129.0^{\circ}$ and $\theta=228.9^{\circ}$, respectively. This angles
+and the corresponding variation is presented in the right sale of the top frame
+of Fig. \ref{fig:alt-vy-comp-rtp}.
+% 
+We also have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
+negative keeping the same spin polarization since the onset of the response to a
+energy of the incoming beam of 0.886\,eV when the response decreases and goes to
+zero.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: Layer-by-layer  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Layer-by-layer analysis} % (fold)
+\label{sec:res-layer_by_layer_analysis}
+
+% %%%%%%%%%%%%%%%%
+% %% Description of Up layer |V^{yz}|
 % %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
-% %%         alt-plots/alt-vab-layers.gp
+% %%         calv.sm_0.03_yz_12802_1_40-spin_scissor_0_Nc_18_ang_40
+% %%         calv.sm_0.03_yz_12802_2_40-spin_scissor_0_Nc_18_ang_40
+% %%         up-plots/up-vab-layers.gp
 % %%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \subfigure[\ \label{fig:up-vyz-lay-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
+    \\
+    \subfigure[\ \label{fig:up-vyz-lay-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
+    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
+     \emph{up} structure.}
+    \label{fig:up-vyz-lay}
+\end{figure}
+
 From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
@@
 the hydrogen layer.
+% %%%%%%%%%%%%%%%%
+% %% Description of ALT layer |V^{yz}|
+% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
+% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
+% %%         alt-plots/alt-vab-layers.gp
+% %%%%%%%%%%%%%%%%
+From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
+the \emph{alt} structure the most intense component of
+$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
+$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
+energy incident beam of 0.72\,eV. This component and the corresponding layer by
+layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
+we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
+layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
+Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
+4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
+for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
+from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
+in the same direction resulting in a total response
+$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
+0.912\,eV.
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
+    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
+     \emph{alt} structure.}
+    \label{fig:alt-vyz-lay}
+\end{figure}
+
+% section res-layer_by_layer_analysis (end)
 

### 2017-05-04 mu/article/article.tex
sab
2D vs bulk comparison completed.

@@
 \usepackage{color}
+\usepackage{multirow}
 % \usepackage{showframe}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%  I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  T H E O R Y  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Pure spin current %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% section theory-pure_spin_current (end)
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% section theory (end)
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   R E S U L T S   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hline
-Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
+\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
 \cline{3-5}
-No. & type & $x$ & $y$ & $z$  \\
+\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
 \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{sec:res-pure_spin_current_and_spin_velocity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \caption{Comparison of most intense responses for
-    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs structures}
+    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs
+    structures}
     \label{fig:vab-str-comp}
@@
 
-In figure \ref{fig:vab-str-comp}
-
-% section res-pure_spin_current_and_spin_velocity (end)
+In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
+responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
+\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
+this figure the most intense response corresponds to the \emph{up} structure
+centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
+spin velocity of 87.16\,Km/s.
+% 
+In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
+four structures have contributions in the same order of magnitude. 
+% 
+Starting with the 2D structures we have that the \emph{up} structure has other
+two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
+22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
+peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
+and -32.9\,Km/s, respectively.
+% 
+Then, for the bulk structures we have that the CdSe has only one intense
+response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
+GaAs structure has a large and almost planar zone where the response is hold
+reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
+spin velocity of -21.6\,Km/s.
+% 
+In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
+% 
+\begin{table}[t]
+\begin{tabular}{cccccc}
+\hline
+\hline
+Kind of  & 
+\multirow{2}{*}{\quad Structure \quad} & 
+Pol. &
+Energy & 
+\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
+\cline{5-6}
+system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
+\hline
+\hline
+2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
+     &              &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
+     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
+\hline
+2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
+     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
+\hline
+bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
+\hline
+bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
+\hline
+\hline
+\end{tabular}
+\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
+for different structures and the corresponding polarization angles and energy
+values.}
+\label{tab:vab-str-comp}
+\end{table}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\blindtext
 \blindtext
 
-% section res-fixspin (end)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing velocity %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \textbf{Up structure.}
@@
 \textbf{Alt structure.}
-
 % %%%%%%%%%%%%%%%%%
@@
 
-% section res-layer_by_layer_analysis (end)
-
 \bibliography{article.bib}

### 2017-05-04 mu/article/article.tex
sab

@@
 \caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
-for different structures and the corresponding polarization angles and energy
+for different structures and the corresponding polarization angle $\alpha$ and energy
 values.}

### 2017-05-04 mu/article/article.tex
Starting plots modifications.

@@
 \caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
-for different structures and the corresponding polarization angle $\alpha$ and energy
-values.}
+for different structures and the corresponding polarization angle $\alpha$ and
+energy values.}
 \label{tab:vab-str-comp}
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
     \label{fig:up-3d-vy-1}]
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
     \label{fig:up-3d-vy-2}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
-    structure. The local maximum response zone is localized for an energy range
-    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
-    from 25$^{\circ}$ to 50$^{\circ}$.}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
+    response for C$_{16}$H$_{8}$-up structure. The local maxima responses zones
+    are localized for an energy range from 1.95\,eV to 2.00\,eV and for
+    polarization angles of the incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
     \label{fig:up-3d-2}
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
     \label{fig:alt-3d-vy}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
-    structure. The maximum response zone is localized for an energy range from
-    0.90\,eV to 0.93\,eV and for a polarization angle of the
-    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
+    \caption{$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
+    responses for C$_{16}$H$_{8}$-alt structure. The maxima responses zones are
+    localized for an energy range from 0.90\,eV to 0.93\,eV and for polarization
+    angles of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
     \label{fig:alt-3d}

### 2017-05-04 mu/article/article.tex
Ading arrows to V^{ab} rtp plots.
Including fixing spin plots.

@@
 \documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
-
-% preamble:
 
@@
 
+{\color{red}
 \subsection{Pure spin velocity} % (fold)
@@
 polarization angle $\alpha$. Then,
+} % COLOR RED END
 \begin{widetext}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Layer by layer %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+{\color{red}
 \subsection{Layer-by-layer analysis.}\label{sec:theory-layer}
@@
 \end{align}
+
+} % COLOR RED END
 
@@
 
+{\color{red}
+
 \subsection{Spin velocity} % (fold)
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{figure}[t]
@@
 \begin{table}[t]
+
 \begin{tabular}{cccccc}
 \hline
-\hline
-Kind of  & 
-\multirow{2}{*}{\quad Structure \quad} & 
+\multirow{2}{*}{Structure \quad} & 
+Kind of \quad & 
 Pol. &
@@
 \cline{5-6}
-system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
+& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
 \hline
-\hline
-2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
+\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
              &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
-     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
-\hline
-2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
-     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
-\hline
-bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
-\hline
-bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
-\hline
+             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\ \\
+\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
+             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\ \\
+ CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\ \\
+ GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
 \hline
 \end{tabular}
-\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
+\caption{\color{red} Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
 for different structures and the corresponding polarization angle $\alpha$ and
@@
 \end{table}
-
+} % COLOR RED END
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\blindtext
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\blindtext
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsx-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svax-1}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsy-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svay-1}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsz-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
+
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
+    structure.}
+    \label{fig:up-3d-vsb-1}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsx-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svax-2}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsy-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svay-2}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vsy-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}
+
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
+    structure.}
+    \label{fig:up-3d-vsb-1}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \subfigure[\ \label{fig:up-vaz-rag-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
+    \\
+    \subfigure[\ \label{fig:up-vaz-rag-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}
+
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
+    \emph{up} structure.}
+    \label{fig:up-vaz-rag}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vsx}]
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-svax}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vsy}]
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-svay}}
+    \\
+    \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vsz}]
+    {\includegraphics[width=\linewidth]{altplots/alt-3d-svaz}}
+
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+    $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for \emph{alt} structure. }
+    \label{fig:alt-3d-vsb}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
+    \emph{alt} structure.}
+    \label{fig:figure1}
+\end{figure}
+
 \blindtext
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vx-1}]
+    \label{fig:up-3d-vvx-1}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vy-1}]
+    \label{fig:up-3d-vvy-1}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
@@
     incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-3d-1}
+    \label{fig:up-3d-vva-1}
 \end{figure}
@@
 0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
-and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
+and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-vva-1} we present the
 $\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vx-2}]
+    \label{fig:up-3d-vvx-2}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vy-2}]
+    \label{fig:up-3d-vvy-2}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
@@
     polarization angles of the incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-3d-2}
+    \label{fig:up-3d-vva-2}
 \end{figure}
@@
 Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-2} where two local maxima
+1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-vva-2} where two local maxima
 of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ are obtained
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vx}]
+    \label{fig:alt-3d-vvx}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vy}]
+    \label{fig:alt-3d-vvy}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
@@
     angles of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
-    \label{fig:alt-3d}
+    \label{fig:alt-3d-vva}
 \end{figure}
@@
 $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
-\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
+\ref{fig:alt-3d-vva} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
 from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$

### 2017-05-08 mu/article/article.tex
Correction of descriptions when velocity is fixed

--- 2017-05-04 mu/article/article.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%  I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{widetext}
-\begin{equation}
-\mu^{\mathrm{abcd}} (\omega) =
+\begin{align}
+\mu^{\mathrm{abcd}} (\omega) 
+&=
 \frac{\pi e^{2}}{\hbar^{2}} \int 
@@
 \label{eq:mu}
-\end{equation}
+\\
+K^{\mathrm{ab}}_{mn}
+&=
+\sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
+\label{eq:velspi-matelem}
+\end{align}
 \end{widetext}
@@
 \begin{align}
-\theta  (\omega)
+\theta_{\mathrm{a}}  (\omega)
 =& 
@@
 \\
-\varphi (\omega)
+\varphi_{\mathrm{a}} (\omega)
 =& 
@@
 \end{tabular}
+
 \caption{Unit cell of \emph{alt} structure. Layer division, atom types and
@@
 \end{tabular}
+
 \caption{Unit cell of \emph{up} structure. Layer division, atom types and
@@
 
-Using the ABINIT code \cite{gonzeCPC09} we calculated the self- consistent
-ground state and the Kohn-Sham states using density functional theory in the
-local density approximation (DFT-LDA) with a planewave basis. We used
-Hartwigsen- Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
+Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
+state and the Kohn-Sham states using density functional theory in the local
+density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
+Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
 pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
-for calculating $\mathcal{V}^{\mathrm{a}}(\omega)$.
-
+\textcolor{red}{ needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
+\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).}
+%
+{\color{red} 
+It is known that using DFT-LDA to calculate the electronic structure of
+materials predict a different band gap than the obtained experimentally. A
+correction for the band gap energy value can be calculated by other \emph{ab-
+initio} methods such as the GW approximation \cite{onidaRMP02} but this is
+outside the scope of this paper.
+} % COLOR RED END
+% 
 The convergence parameters for the calculations of our results corresponding to
 the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
-40\,Ha, respectively. The energy eigenvalues and matrix elements were
-calculated using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the
-irreducible Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV
-and 0.088\,eV, respectively for the \emph{alt} and \emph{up} structures. As
-mentioned in
-\cite{zapataPSB2016}, using DFT the LDA is only one method of many other that
-can be used to calculate the electronic structure of materials. Also it is
-known that all methods predict a different band gap than the obtained in the
-experiment. A correction for the band gap energy value can be calculated by
-other \emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02}
-being this outside the scope of this paper.
-
-The structures presented here where divided into layers to analyze the he
-layer-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The
-\emph{alt} structure was divided in six layers corresponding the first one to
-the top hydrogen atoms, from the second to the forth to carbon atoms in
-different $z$ positions, and the sixth and last one to the bottom hydrogen
-atoms. The \emph{up} structure was divided into two layers, the first one
-comprised by the top hydrogen atoms and the second by the carbon atoms. The
-layer divisions and atom positions for the unit cells are shown in Tables
-\ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.
+40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
+using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
+Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
+respectively for the \emph{alt} and \emph{up} structures.
 
@@
 
+{\color{red}
+
 \subsection{Spin velocity} % (fold)
-\label{sec:res-pure_spin_current_and_spin_velocity}
+\label{sec:res-spin_velocity}
 
@@
     \includegraphics[width=\linewidth]{plots/vab-str-comp}
-    \caption{Comparison of most intense responses for
-    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs
-    structures}
+
+    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
+    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
+    polarization angles.}
     \label{fig:vab-str-comp}
@@
 response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
-GaAs structure has a large and almost planar zone where the response is hold
+GaAs structure has a large and almost planar zone where the response is held
 reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
@@
 % 
-In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
+In table \ref{tab:vab-str-comp} we present the comparison of this values for the
+2D and bulk structures.
 % 
@@
 \hline
-\hline
-Kind of  & 
-\multirow{2}{*}{\quad Structure \quad} & 
+\multirow{2}{*}{Structure \quad} & 
+Kind of \quad & 
 Pol. &
@@
 \cline{5-6}
-system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
+& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
 \hline
-\hline
-2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
+\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
              &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
              &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
-\hline
-2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
+\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
              &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
-\hline
-bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
-\hline
-bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
-\hline
+ CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
+ GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
 \hline
 \end{tabular}
-\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
-for different structures and the corresponding polarization angle $\alpha$ and energy
-values.}
+
+\caption{\color{red} Comparison of the reported maxima values of
+$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
+polarization angle $\alpha$ and energy values.}
 \label{tab:vab-str-comp}
 \end{table}
+} % COLOR RED END
 
@@
 
-\subsection{Fixing spin} % (fold)
-\label{sec:res-fixspin}
+% \subsection{Fixing spin} % (fold)
+% \label{sec:res-fixspin}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \blindtext
 
-\blindtext
-\blindtext
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure}[t]
+%     \centering
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsx-1}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-1}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsy-1}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-1}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsz-1}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
+
+%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
+%     structure.}
+%     \label{fig:up-3d-vsb-1}
+% \end{figure}
+
+% \begin{figure}[t]
+%     \centering
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsx-2}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-2}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsy-2}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-2}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
+%     \label{fig:up-3d-vsz-2}]
+%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}
+
+%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
+%     structure.}
+%     \label{fig:up-3d-vsb-2}
+% \end{figure}
+
+% \begin{figure}[t]
+%     \centering
+%     \subfigure[\, \label{fig:up-vaz-rag-1}]
+%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
+%     \\
+%     \subfigure[\, \label{fig:up-vaz-rag-2}]
+%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}
+
+%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
+%     \emph{up} structure.}
+%     \label{fig:up-vaz-rag}
+% \end{figure}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure}[t]
+%     \centering
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{alt} structure 
+%     \label{fig:alt-3d-vsx}]
+%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svax}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{alt} structure 
+%     \label{fig:alt-3d-vsy}]
+%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svay}}
+%     \\
+%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{alt} structure 
+%     \label{fig:alt-3d-vsz}]
+%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svaz}}
+
+%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
+%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
+%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for \emph{alt} structure. }
+%     \label{fig:alt-3d-vsb}
+% \end{figure}
+
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
+%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
+%     \emph{alt} structure.}
+%     \label{fig:figure1}
+% \end{figure}
+
+% \blindtext
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \textbf{Up structure.}
-
 % %%%%%%%%%%%%%%%%%
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vx-1}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
+    \label{fig:up-3d-vvx-1}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vy-1}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
+    \label{fig:up-3d-vvy-1}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
-    structure. The maximum response zone is localized for an energy range from
-    0.04\,eV to 0.12\,eV and for a polarization angle of the
-    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-3d-1}
+
+    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    polarization angle for the \emph{up} structure. The absolute maxima of both
+    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
+    range from 0.07\,eV to 0.10\,eV and for polarization angles from
+    $25^{\circ}$ to $50^{\circ}$.}
+    \label{fig:up-3d-vva-1}
 \end{figure}
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
+    \label{fig:up-vx-comp-rtp-1}]
     {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
+    \label{fig:up-vy-comp-rtp-1}]
     {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
-    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{up} structure. Both maxima where obtained for a polarization
-    angle $\alpha=40^{\circ}$. }
+
+    \caption{Most intense response of
+    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
+    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
+    frames right scale), and the corresponding three components (bottom frames)
+    for the \emph{up} structure fixing the polarization angle to
+    $\alpha=40^{\circ}$ to maximize the response.}
     \label{fig:up-vab-comp-rtp-1}
@@
 For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
-0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
-and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
-$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
+0.16\,eV where we found the most intense response and the absolute maxima for
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+In Fig. \ref{fig:up-3d-vva-1} we present the
+$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate Eq.
 \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
-onset of the response is when the energy of the incoming light is the same of
-the gap energy.
+\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
+response is when the energy of the incoming light is the same of the gap energy.
 %
@@
 0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone where the maximum zone of response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
-% 
-We found that the absolute maximum of the response is obtained when the
-polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
-0.088\,eV.
-%
+$45^{\circ}$ is the zone where the maximum response is held for both,
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+% %%%%%%%%%%%%%%%%%
+% %% 1.8 eV - 2.0 eV
+% %% Description of UP |V^{a}|, components and RTP
+% %% files: 
+% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
+% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
+% %% up-3d-vab.gp
+% %%%%%%%%%%%%%%%%%
+
 In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
 % 
-\ref{fig:up-vy-comp-rtp-1} we present the results of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
-fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
-vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles (right scale). In the bottom frames of same figures we present the decomposition of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
-corresponding $\mathcal{V}^{\mathrm{xx}}$, 
-$\mathcal{V}^{\mathrm{xy}}$,
-$\mathcal{V}^{\mathrm{xz}}$, and
-$\mathcal{V}^{\mathrm{yx}}$, 
-$\mathcal{V}^{\mathrm{yy}}$,
-$\mathcal{V}^{\mathrm{yz}}$ 
-components with $\alpha$ fixed to $40^{\circ}$. 
+\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
+for which the response is maximized for the \emph{up} structure. In the same
+figures and frames we present in dashed lines the corresponding polar
+$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
+right scale. Also, in the bottom frames of those figures we present the
+decomposition of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+$|\mathcal{V}^{\mathrm{y}}|(\omega)$ in the corresponding
+$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
+components.
 \begin{figure}[t]
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vx-2}]
+    \label{fig:up-3d-vvx-2}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vy-2}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vvy-2}]
     {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
-    structure. The local maximum response zone is localized for an energy range
-    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
-    from 25$^{\circ}$ to 50$^{\circ}$.}
-    \label{fig:up-3d-2}
+
+    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    polarization angle for the \emph{up} structure. The local maxima of both
+    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy range from
+    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
+    $50^{\circ}$.}
+    \label{fig:up-3d-vva-2}
 \end{figure}
-
 \begin{figure}[t]
@@
     {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
-    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{up} structure. Both maxima where obtained for a polarization
-    angle $\alpha=40^{\circ}$. }
+
+    \caption{Intense response of
+    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
+    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
+    frames right scale), and the corresponding three components (bottom frames)
+    for the \emph{up} structure fixing the polarization angle to
+    $\alpha=40^{\circ}$ to maximize the response.}
+
     \label{fig:up-vab-comp-rtp-2}
@@
 From Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with
-energy of 0.088\,eV the three components have similar contributions and have
+energy of 0.088\,eV the three components have similar contributions and with
 values of 
 % 
-$\mathcal{V}^{\mathrm{xx}}=-36.5$\,Km/s,
-$\mathcal{V}^{\mathrm{xy}}=-23.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}= 39.8$\,Km/s 
+$\mathcal{V}^{\mathrm{xx}}(\omega)=-36.5$\,Km/s,
+$\mathcal{V}^{\mathrm{xy}}(\omega)=-23.2$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}(\omega)= 39.8$\,Km/s 
 % 
@@
 % 
-$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s 
+$|\mathcal{V}^{\mathrm{x}}|(\omega)=58.7$\,Km/s 
 % 
@@
 in the $x$ direction. To this value corresponds a polar and azimuthal angles of
-$\varphi=47.4$ and $\theta=212.5$, respectively.
+$\theta_{\mathrm{x}}(\omega)=47$ and $\varphi_{\mathrm{x}}(\omega)=212$,
+respectively, being directed upper the third Cartesian Quadrant of the $xy$
+plane. Also from this figure we have that those angle values are hold for almost
+all the peak of the response having a deviation of $\pm 2^{\circ}$ in the range
+of energies from 0.028\,eV to 0.098\,eV from the corresponding to the absolute
+maximum mentioned before.
 % 
-Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $yx$ and $yy$
-components have less contributions for the total response than the $yz$ and for
-the same incoming beam energy have values of 
+Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $\mathrm{yx}$ and
+$\mathrm{yy}$ components have less contributions for the total response than the
+$\mathrm{yz}$ and for the same incoming beam energy have values of
 % 
-$\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s 
-$\mathcal{V}^{\mathrm{yy}}=  8.6$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}= 87.2$\,Km/s 
+$\mathcal{V}^{\mathrm{yx}}(\omega)= -7.9$\,Km/s 
+$\mathcal{V}^{\mathrm{yy}}(\omega)=  8.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}(\omega)= 87.2$\,Km/s 
 % 
@@
 % 
-$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s
+$|\mathcal{V}^{\mathrm{y}}|(\omega)=87.9$\,Km/s
 % 
@@
 in the $y$ direction and being 1.5 times more intense than
-$|\mathcal{V}^{\mathrm{x}}|$ and corresponding spin polar and azimuthal angles
-$\varphi=7.6$ $\theta=132.7$, respectively. We also found that since the onset
-of the response till an energy for the incoming beam of 0.118\,eV the components
-of both, $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have no
-change in the spin polarization direction. Finally, after this energy value both
-goes to zero.
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ To this absolute maximum correspond spin
+polar and azimuthal angles $\theta_{\mathrm{y}}(\omega)=8$ and
+$\varphi_{\mathrm{y}}(\omega)=133$, respectively, being directed almost
+perpendicularly over the $xy$ plane and being localized on the first Cartesian
+Quadrant. In a different way than in the $|\mathcal{V}^{\mathrm{x}}|(\omega)$
+case only the polar angle is hold for the peak of the response having a
+deviation of $\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but
+the azimuthal angle changes since the onset to 0.106\,eV from $99^{\circ}$ to
+$176^{\circ}$.
+% 
+We also found that since the onset of the response till an
+energy for the incoming beam of 0.118\,eV the components of both,
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+have no change in the spin polarization direction. Finally, after this energy
+value both goes to zero.
 % %%%%%%%%%%%%%%%%%
@@
 Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-2} where two local maxima
-of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ are obtained
-for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:vv-mag} and
-\eqref{eq:vab}.
+1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-vva-2} where two local
+maxima of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+$|\mathcal{V}^{\mathrm{y}}|(\omega)$ are obtained for the \emph{up} structure.
 % 
 From this figure we have that for the zone between the energy ranges from
-1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and angles from $30^{\circ}$
-to $45^{\circ}$ those maxima zones are hold. 
+1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and for polarization angles
+from $30^{\circ}$ to $45^{\circ}$ those two local maxima zones are held.
 % 
-We found that the maxima are obtained when the polarization angle is fixed to
-$40^{\circ}$ and the corresponding energies are 1.934\,eV and 1.972\,eV.
-% 
-Again, in the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
-% 
-\ref{fig:up-vy-comp-rtp-2} we present the results of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
-fixing the polarization angle to $\alpha=40^{\circ}$ vs the photon energy and
-the corresponding polar $\varphi$ and azimuthal $\theta$ angles (right scale)
-for the \emph{up} structure. In the bottom frames of same figures we present the
-three components $\mathrm{xx}$, $\mathrm{xy}$, $\mathrm{xz}$, and $\mathrm{yx}$,
-$\mathrm{yy}$, $\mathrm{yz}$ corresponding to $|\mathcal{V}^{\mathrm{x}}|$ and
-$|\mathcal{V}^{\mathrm{y}}|$ fixing the polarization angle to $40^{\circ}$.
+We found that the two local maxima are obtained for an energy of the incident
+beam energies of 1.934\,eV and 1.972\,eV fixing again the polarization angle to
+$40^{\circ}$. 
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-We found that for both cases, $|\mathcal{V}^{\mathrm{x}}|$ and
-$|\mathcal{V}^{\mathrm{y}}|$, the corresponding components have similar
-contributions and for an incoming energy beam of 1.934\,eV have values of
+In the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
 % 
-$\mathcal{V}^{\mathrm{xx}}= 2.3$\,Km/s, 
-$\mathcal{V}^{\mathrm{xy}}= 3.8$\,Km/s, 
-$\mathcal{V}^{\mathrm{xz}}= 4.9$\,Km/s, and
-$\mathcal{V}^{\mathrm{yx}}=11.5$\,Km/s,
-$\mathcal{V}^{\mathrm{yy}}=17.0$\,Km/s,
-$\mathcal{V}^{\mathrm{yz}}=20.4$\,Km/s
-resulting in a in values of 
-$|\mathcal{V}^{\mathrm{x}}|= 6.6$\,Km/s
-$|\mathcal{V}^{\mathrm{y}}|=28.7$\,Km/s
+\ref{fig:up-vy-comp-rtp-2} we present in solid lines the results of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
+for which the response is maximized for the \emph{up} structure. In the same
+figures and frames we present in dashed lines the corresponding polar
+($\theta_{\mathrm{x}}(\omega)$ and $\theta_{\mathrm{y}}(\omega)$) and azimuthal
+($\varphi_{\mathrm{x}}(\omega)$ and $\varphi_{\mathrm{y}}(\omega)$) angles
+related to the right scale. In the bottom frames of same figures we present the
+decomposition of the responses in the three corresponding components
+$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$. 
 % 
-being $|\mathcal{V}^{\mathrm{y}}|$ 4.3 times more intense than
-$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
-and azimuthal spin polarization angels $\varphi= 42.0^{\circ}$ and $\theta=
-58.7^{\circ}$ for $|\mathcal{V}^{\mathrm{x}}|$ and $\varphi= 45.2^{\circ}$ and
-$\theta= 56.0^{\circ}$ for $|\mathcal{V}^{\mathrm{y}}|$.
+We found that for both cases, the components have similar contributions and for
+an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
+in a value of $|\mathcal{V}^{\mathrm{x}}|(\omega)= 6.6$\,Km/s along the $x$
+direction  with polar and azimuthal spin polarization angles
+$\theta_{\mathrm{x}}(\omega)= 42^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega)=59^{\circ}$ having fluctuations but being directed
+over the first Cartesian Quadrant of the $xy$ plane.
 % 
-Alike, for an incoming energy beam of 1.972\,eV all the components of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ have similar
-contributions having values of
+For the spin moving along the $y$ direction we have a value of
+$|\mathcal{V}^{\mathrm{y}}|(\omega)=28.7$\,Km/s with polar and azimuthal angles
+$\theta_{\mathrm{y}}(\omega)=45^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega)=56^{\circ}$ having variations of $\pm5^{\circ}$
+for energy variations of $\pm0.01$\,eV and being directed over the fir Cartesian
+Quadrant of the $xy$ plane.
 % 
-$\mathcal{V}^{\mathrm{xx}}= -5.0$\,Km/s, 
-$\mathcal{V}^{\mathrm{xy}}= -5.8$\,Km/s, 
-$\mathcal{V}^{\mathrm{xz}}= -6.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{yx}}=-26.8$\,Km/s,
-$\mathcal{V}^{\mathrm{yy}}=-28.9$\,Km/s,
-$\mathcal{V}^{\mathrm{yz}}=-29.7$\,Km/s
-resulting in a in values of 
-$|\mathcal{V}^{\mathrm{x}}|= 9.9$\,Km/s
-$|\mathcal{V}^{\mathrm{y}}|=49.4$\,Km/s
+Alike, for an incoming energy beam of 1.972\,eV we found the second and more
+intense local maxima with all the components of both responses having similar
+contributions and resulting in values of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)=9.9$\,Km/s and spin polarization angles
+$\theta_{\mathrm{x}}(\omega)=129^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega)=229^{\circ}$ being almost constant in the width of
+the peak having variations of $\pm1^{\circ}$ for variations in energy of
+$\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the
+$xy$ plane.
 % 
-being $|\mathcal{V}^{\mathrm{y}}|$ 5.0 times more intense than
-$|\mathcal{V}^{\mathrm{x}}|$ for this photon energy. The responses have polar
-and azimuthal spin polarization angles $\varphi=129.0^{\circ}$
-$\theta=229.1^{\circ}$ or $|\mathcal{V}^{\mathrm{x}}|$ and
-$\varphi=127.0^{\circ}$ and $\theta= 227.1^{\circ}$ for
-$|\mathcal{V}^{\mathrm{y}}|$.
+For the spin moving in the $y$ direction we have a value of
+$|\mathcal{V}^{\mathrm{y}}|(\omega)=49.4$\,Km/s with spin polarization angles
+$\theta_{\mathrm{y}}(\omega)=127^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega)=227^{\circ}$ being almost constant with variations
+of $\pm1^{\circ}$ for variations in energy of $\pm1$\,eV and being directed
+downward the third Cartesian Quadrant of the $xy$ plane.
 % 
-Finally we have that all the tree components of $|\mathcal{V}^{\mathrm{x}}|$ and
-$|\mathcal{V}^{\mathrm{y}}|$ keep the spin polarization positive till an energy
+Finally we have that for bot energies $|\mathcal{V}^{\mathrm{y}}|(\omega)$ is
+more intense than $|\mathcal{V}^{\mathrm{x}}|(\omega)$ being 4.4 times more
+intense for 1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the
+components of the responses keep the spin polarization positive till an energy
 of the incoming beam equal to 1.954\,eV when the spin polarization changes the
@@
     \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vx}]
+    \label{fig:alt-3d-vvx}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vy}]
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
+    \label{fig:alt-3d-vvy}]
     {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
-    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
-    structure. The maximum response zone is localized for an energy range from
-    0.90\,eV to 0.93\,eV and for a polarization angle of the
-    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
-    \label{fig:alt-3d}
+
+    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    polarization angle for the \emph{alt} structure. The absolute maxima of both
+    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy range from
+    0.90\,eV to 0.93\,eV and for polarization angles from 120$^{\circ}$ to
+    150$^{\circ}$.}
+    \label{fig:alt-3d-vva}
 \end{figure}
@@
     {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
-    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
-    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
-    \emph{alt} structure. Both maxima where obtained for a polarization
-    angle $\alpha=145^{\circ}$. }
+
+    \caption{Most intense response of
+    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
+    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
+    frames right scale), and the corresponding three components (bottom frames)
+    for the \emph{alt} structure fixing the polarization angle to
+    $\alpha=145^{\circ}$ to maximize the response.}
     \label{fig:alt-vab-comp-rtp}
@@
 For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
-1.0\,eV where we found the most intense response for 
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
-\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
-from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$
-in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
-onset of the response is when the energy of the incoming light is the same of
-the gap energy.
+1.0\,eV where we found the a local maxima and the most intense responses for
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{a}}|(\omega)$.
+In Fig. \ref{fig:alt-3d-vva} we present the $|\mathcal{V}^{\mathrm{a}}|(\omega)$
+spectra resulting from evaluate again Eq. \eqref{eq:vv-mag} using different
+polarization angles $\alpha$ in Eq. \eqref{eq:vab} but now for the \emph{alt}
+structure. We can see that the onset of the response is when the energy of the
+incoming light is the same of the gap energy.
 %
@@
 150$^{\circ}$ is the zone where the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is kept.
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$ is
+held. We also found that the first peak is obtained when the energy of the
+incoming beam is 0.720\,eV and  the absolute maximum of the response is obtained
+when for 0.912\,eV, both for a polarization angle $\alpha = 145^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 % %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
+% %%        vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
+% %%        vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
 % %%        alt-plots/alt-3d-vab.gp
 % %%%%%%%%%%%%%%%%
-We also found that the absolute maximum of the response is obtained when the
-energy of the incoming bean is 0.912\,eV and the polarization angle is $\alpha =
-145^{\circ}$. 
-% 
 In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
 %
-\ref{fig:alt-vy-comp-rtp} we present the results for
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
-fixing the polarization angle to $145^{\circ}$ for the \emph{alt} structure vs
-the photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
-angles (right scale). Also in the bottom frames of Figs. 
+\ref{fig:alt-vy-comp-rtp} we present in solid lines the results of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+related to the left scale, fixing the polarization angle to $\alpha=145^{\circ}$
+for which the response is maximized for the \emph{alt} structure. In the same
+figures and frames we present ind dashed lines the spin polarization angles
+related to the right scale and in the bottom frames the corresponding three
+components.
 % 
-\ref{fig:alt-vx-comp-rtp} and \ref{fig:alt-vy-comp-rtp} we present the
-decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$
-in the corresponding components $\mathcal{V}^{\mathrm{xx}}$,
-$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
-$\mathcal{V}^{\mathrm{yx}}$, $\mathcal{V}^{\mathrm{yy}}$
-$\mathcal{V}^{\mathrm{yz}}$ with $\alpha$ fixed to $145^{\circ}$.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{x}|, components and RTP
-% %% files: vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        alt-plots/alt-vab-rtp.gp
-% %%%%%%%%%%%%%%%%
-Making the analysis for the components and angles for
-$|\mathcal{V}^{\mathrm{x}}|$ depicted in Fig. \ref{fig:alt-vx-comp-rtp} we can
-see that for an incoming beam energy of 0.720\,eV the components contributions 
-are similar having values of
+Making the analysis for the components and angles when the spin current is
+directed in the $x$ direction, corresponding to the Fig. 
 % 
-$\mathcal{V}^{\mathrm{xx}}= 10.5$\,Km/s, 
-$\mathcal{V}^{\mathrm{xy}}=  9.1$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}= 13.5$\,Km/s
+\ref{fig:alt-vx-comp-rtp}, we found that for the \emph{alt} structure when the
+energy of the incoming beam is 0.720\,eV we have similar contributions from all
+the components resulting in a response of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)=19.4$\,Km/s and polar and azimuthal spin
+polarization angles $\theta_{\mathrm{x}}(\omega)=46^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega)=41^{\circ}$ having variations in the range of the
+peak but being directed over the first Cartesian Quadrant of the $xy$ plane;
 % 
-resulting in a total spin-velocity 
+for an energy of 0.912\,eV we have a major contribution from the
+$\mathcal{V}^{\mathrm{xz}}(\omega)$ component resulting in a total response of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)=30.9$\,Km/s and angles
+$\theta_{\mathrm{x}}(\omega)=154^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega)=290^{\circ}$ having variations of $\pm3^{\circ}$
+in for energy variations of $\pm1$\,eV and being directed downward the fourth
+Cartesian Quadrant of the $xy$ plane.
 % 
-$|\mathcal{V}^{\mathrm{x}}|=19.4$\,Km/s 
+Making now the analysis for the components and angles when the spin current is
+directed along the $y$ direction, corresponding to the Fig.
 % 
-and spin polar and azimuthal angles $\varphi = 45.8^{\circ}$ and
-$\theta=40.7^{\circ}$, respectively.
+\ref{fig:alt-vy-comp-rtp}, we found that when the energy of the incoming beam is
+0.720\,eV we have more contribution from the $\mathcal{V}^{\mathrm{yz}}(\omega)$
+component resulting in a response of
+$|\mathcal{V}^{\mathrm{y}}|(\omega)=51.9$\,Km/s and angles
+$\theta_{\mathrm{y}}(\omega)=141^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega)=222^{\circ}$ being the first constant and the
+second having variations of $\pm3^{\circ}$ for energy variations of $\pm0.3$\,eV
+and being directed downward the third Cartesian Quadrant of the $xy$ plane.
 % 
-In the other hand, for an energy of the incoming beam equal to 0.912\,eV
-we found that the contribution of the components are 
+Then, for the peak centered at 0.912\,eV we have similar contributions of all
+the components resulting in a response
+$|\mathcal{V}^{\mathrm{y}}|(\omega)=52.3$\,Km/s being this the absolute maximum
+response for the \emph{alt} structure. The corresponding angles are
+$\theta_{\mathrm{y}}(\omega)=129^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega)=229^{\circ}$ being both constant for the energy
+range of the peak and being directed downward the third Cartesian Quadrant of
+the $xy$ plane.
 % 
-$\mathcal{V}^{\mathrm{xx}}=   4.8$\,Km/s
-$\mathcal{V}^{\mathrm{xy}}= -12.8$\,Km/s, and 
-$\mathcal{V}^{\mathrm{xz}}= -27.7$\,Km/s
-% 
-having a mayor response coming from the $xz$ component and resulting in a spin-
-velocity magnitude 
-% 
-$|\mathcal{V}^{\mathrm{x}}|=30.9$\,Km/s 
-% 
-being this the absolute maximum fixing the spin-velocity in the $x$ direction.
-Then, the components give us polar and azimuthal angles with values of
-$\varphi=153.8^{\circ}$ and $\theta=290.4^{\circ}$. This angles and its
-variation with the incoming energy beam are presented in the right scale of the
-top frame of Fig \ref{fig:alt-vx-comp-rtp}.
-% 
-Finally we have that since the onset of the response till an energy of the
-incoming bean of 0.744\,eV the three components of $|\mathcal{V}^{\mathrm{x}}|$
-are positive while for the range from 0.746\,eV to 0.886\,eV the
-$\mathcal{V}^{\mathrm{xx}}$ component is positive but the
-$\mathcal{V}^{\mathrm{xy}}$ and $\mathcal{V}^{\mathrm{xz}}$ components change in
-direction. This is due to a change in the spin polarization direction. Finally
-after the energy value of 0.886\,eV the response decreases and goes to zero.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{y}|, components and RTP
-% %% files: vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        alt-plots/alt-vab-rtp.gp
-% %%%%%%%%%%%%%%%%
-Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ depicted in Fig.
-\ref{fig:alt-vy-comp-rtp} we have that for an incoming energy beam of 0.720\,eV
-the $yz$ component have a major contribution than the $yx$ and $yy$ components
-having values of
-% 
-$\mathcal{V}^{\mathrm{yx}}= -24.6$\,Km/s, 
-$\mathcal{V}^{\mathrm{yy}}= -21.8$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
-%
-resulting in a total spin-velocity
-% 
-$|\mathcal{V}^{\mathrm{y}}|=51.9$\,Km/s
-%
-and spin polar and azimuthal angles $\varphi=140.7^{\circ}$ and
-$\theta=221.6^{\circ}$, respectively.
-%
-Also, for an energy of the incoming beam of 0.912\,eV we found that the
-contribution of the components are
-% 
-$\mathcal{V}^{\mathrm{xx}}=-26.7$\,Km/s
-$\mathcal{V}^{\mathrm{xy}}=-30.6$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}=-32.9$\,Km/s
-% 
-having all the three components similar contributions and resulting in a spin-
-velocity magnitude $|\mathcal{V}^{\mathrm{y}}|=52.3$\,Km/s being this the
-absolute maximum spin-velocity for the velocity fixed to the $y$ direction and
-being 1.7 times more intense than the maximum of $|\mathcal{V}^{\mathrm{x}}|$.
-The components then give us the polar and azimuthal angles with values of
-$\varphi=129.0^{\circ}$ and $\theta=228.9^{\circ}$, respectively. This angles
-and the corresponding variation is presented in the right sale of the top frame
-of Fig. \ref{fig:alt-vy-comp-rtp}.
-% 
-We also have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
+Finally we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
 negative keeping the same spin polarization since the onset of the response to a
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% Res: Layer-by-layer  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{sec:res-layer_by_layer_analysis}
+
+The structures presented here where divided into layers to analyze the he
+layer-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The
+\emph{alt} structure was divided in six layers corresponding the first one to
+the top hydrogen atoms, from the second to the forth to carbon atoms in
+different $z$ positions, and the sixth and last one to the bottom hydrogen
+atoms. The \emph{up} structure was divided into two layers, the first one
+comprised by the top hydrogen atoms and the second by the carbon atoms. The
+layer divisions and atom positions for the unit cells are shown in Tables
+\ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.
 
@@
     {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
+
     \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
@@
     \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
+
     \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the

### 2017-05-08 mu/article/article.tex
Starting description when spin is fixed

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{plots/vab-str-comp}
-
-    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
-    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
-    polarization angles.}
-    \label{fig:vab-str-comp}
-\end{figure}
-
-In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
-responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
-\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
-this figure the most intense response corresponds to the \emph{up} structure
-centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
-spin velocity of 87.16\,Km/s.
-% 
-In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
-four structures have contributions in the same order of magnitude. 
-% 
-Starting with the 2D structures we have that the \emph{up} structure has other
-two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
-22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
-peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
-and -32.9\,Km/s, respectively.
-% 
-Then, for the bulk structures we have that the CdSe has only one intense
-response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
-GaAs structure has a large and almost planar zone where the response is held
-reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
-spin velocity of -21.6\,Km/s.
-% 
-In table \ref{tab:vab-str-comp} we present the comparison of this values for the
-2D and bulk structures.
-% 
-\begin{table}[t]
+\begin{table}[b]
 \begin{tabular}{cccccc}
@@
 \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{plots/vab-str-comp}
+
+    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
+    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
+    polarization angles.}
+    \label{fig:vab-str-comp}
+\end{figure}
+
+In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
+responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
+\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
+this figure the most intense response corresponds to the \emph{up} structure
+centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
+spin velocity of 87.16\,Km/s.
+% 
+In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
+four structures have contributions in the same order of magnitude. 
+% 
+Starting with the 2D structures we have that the \emph{up} structure has other
+two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
+22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
+peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
+and -32.9\,Km/s, respectively.
+% 
+Then, for the bulk structures we have that the CdSe has only one intense
+response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
+GaAs structure has a large and almost planar zone where the response is held
+reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
+spin velocity of -21.6\,Km/s.
+% 
+In table \ref{tab:vab-str-comp} we present the comparison of this values for the
+2D and bulk structures.
+% 
 } % COLOR RED END
@@
 
-% \subsection{Fixing spin} % (fold)
-% \label{sec:res-fixspin}
-
-% \blindtext
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fixing spin} % (fold)
+\label{sec:res-fixspin}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \subfigure[\, \label{fig:up-vaz-rag-1}]
-%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
-%     \\
-%     \subfigure[\, \label{fig:up-vaz-rag-2}]
-%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}
-
-%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
-%     \emph{up} structure.}
-%     \label{fig:up-vaz-rag}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+    \centering
+    \subfigure[\ \label{fig:up-3d-vsz-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
+    \\
+    \subfigure[\ \label{fig:up-3d-vsz-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}
+
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
+    structure for two energy ranges. The absolute maxima is located for an
+    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
+    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
+    $50^{\circ}$.}
+    \label{fig:up-3d-vsz}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \subfigure[\, \label{fig:up-vaz-rag-1}]
+    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
+    \\
+    \subfigure[\, \label{fig:up-vaz-rag-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}
+
+    \caption{\color{red} Most intense response of
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
+    figs (a) and (b)), the corresponding velocity angle
+    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
+    (circled box) and perpendicular (square box) angles, and the two components
+    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
+    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
+    }
+    \label{fig:up-vaz-rag}
+\end{figure}
+
+We first present two energy ranges for the \emph{up} structure, the first for an
+incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)$ response is obtained and the
+second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
+found.
+% 
+In Fig. \ref{fig:up-3d-vsz} we present the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
+the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
+Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
+onset of the response starts when the energy of the incoming beam is the same of
+the gap energy.
+% 
+From this figure we obtained that the zone where the maximum response is held
+corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
+and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
+local maxima are held for same polarization angles but for an energy range of
+the incoming beam between 1.90\,eV and 2.05\,eV.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
-%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
-%     \emph{alt} structure.}
-%     \label{fig:figure1}
-% \end{figure}
-
-% \blindtext
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
+    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
+    structure. The absolute maximum is located for an energy range from 0.90\,eV
+    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
+    $150^{\circ}$.}
+    \label{fig:alt-3d-vsb}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
+    \caption{Most intense response of
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
+    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
+    scale), the collinear (circled box) and perpendicular (square box) angles,
+    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
+    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
+    structure fixing the energy to 0.912\,eV.}
+    \label{fig:figure1}
+\end{figure}
+
+\blindtext
 
@@
     $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
-    range from 0.07\,eV to 0.10\,eV and for polarization angles from
+    range from 0.08\,eV to 0.10\,eV and for polarization angles from
     $25^{\circ}$ to $50^{\circ}$.}
@@
 $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+% 
 In Fig. \ref{fig:up-3d-vva-1} we present the
-$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate Eq.
-\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
+$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
+\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
 \eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the

### 2017-05-08 mu/article/article.tex
Continuation of Fix spin description

@@
 
-% \begin{figure}[t]
-%     \centering
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsx-1}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-1}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsy-1}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-1}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsz-1}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
-
-%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
-%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
-%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
-%     structure.}
-%     \label{fig:up-3d-vsb-1}
-% \end{figure}
-
-% \begin{figure}[t]
-%     \centering
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsx-2}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-2}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsy-2}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-2}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
-%     \label{fig:up-3d-vsz-2}]
-%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}
-
-%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
-%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
-%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
-%     structure.}
-%     \label{fig:up-3d-vsb-2}
-% \end{figure}
-
 \begin{figure}[t]
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
     \centering
@@
 incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)$ response is obtained and the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
 second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
@@
 the incoming beam between 1.90\,eV and 2.05\,eV.
+% 
+In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
+present in solid lines the result of evaluate
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
+the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
+which the response is maximized for the \emph{up} structure. In the same figures
+and frames we present in dashed lines, related to the right scale, the
+corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
+frames of those figures the corresponding components
+$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
+Also we present two circled and square boxes indicating the value where the
+angles of the spin velocity is parallel and perpendicular and the the
+corresponding arrows is directed to the value of the response corresponding to
+those angles.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure}[t]
-%     \centering
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{alt} structure 
-%     \label{fig:alt-3d-vsx}]
-%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svax}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{alt} structure 
-%     \label{fig:alt-3d-vsy}]
-%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svay}}
-%     \\
-%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{alt} structure 
-%     \label{fig:alt-3d-vsz}]
-%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svaz}}
-
-%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
-%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
-%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for \emph{alt} structure. }
-%     \label{fig:alt-3d-vsb}
-% \end{figure}
 
@@
 
-\blindtext
+For the \emph{alt} structure we present the energy range of the incoming beam from 0.6\,eV to 1.0\,eV, where the absolute and a local maxima of the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response are obtained.
+% 
+In Fig. \ref{fig:alt-3d-vsb} we present the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
+again the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
+the Eq. \eqref{eq:vab} for the \emph{alt} structure. In the figure we have that
+the onset of the response starts when the energy of the incoming beam is the
+same of the gap energy.
+% 
+From this figure we obtained that the zone where the absolute maximum response
+is held corresponds to a energy range of the incident beam from 0.90\,eV to
+0093\,eV and polarization angles $\alpha$ between $120^{\circ}$ and
+$150^{\circ}$. The local maximum is held or the same polarization angles but for
+energies between 0.67\,eV and 0.75\,eV.
 

### 2017-05-08 mu/article/article.tex
Changing working station: Description of V_{s^z} for up.

@@
 
-\begin{figure}[b]
+\begin{figure}[t]
     \centering
@@
 those angles.
+% 
+From Fig. \ref{fig:up-vaz-rag-1} we have that the maximum response is obtained
+for an incoming beam with energy of 0.088\,eV and polarization angle of
+$40^{\circ}$ resulting in a value of 37.4\,Km/s coming from the contribution of
+the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s and
+$\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s and being this response the
+absolute maximum of the spin velocity polarized in the $\mathrm{z}$ direction
+for the \emph{up} structure and corresponding a velocity angle
+$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
+% 
+In the same figure the green circled box indicates the angle 
+% cicled green box; deviation?
+
+% From the same figure we have that for a polarization angle $\alpha=65^{\circ}$
+% the response is directed in the same angle direction being collinear and
+% resulting in a value of
+% $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s;
 

### 2017-05-09 mu/article/article.tex
sab

--- 2017-05-08 mu/article/article.tex
@@
 those angles.
+% 
+From Fig. \ref{fig:up-vaz-rag-1} we have that the maximum response is obtained
+for an incoming beam with energy of 0.088\,eV and polarization angle
+$\alpha=40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the
+contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
+and $\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s and being this response the
+absolute maximum of the spin velocity polarized in the $\mathrm{z}$ direction
+for the \emph{up} structure and corresponding a velocity angle
+$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
+% 
+In the same figure the green circled box indicates the value for which the
+polarization angle $\alpha$ and the response direction angle
+$\gamma_{\mathrm{x}}(\omega)$ are collinear at $65.5^{\circ}$ and being almost
+constant in the complete range corresponding to a response
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated with the
+green arrow; also the blue square box indicates the value for which the
+polarization angle and the response angle are perpendicular corresponding to
+$\alpha=155.5^{\circ}$ and corresponding to a response
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.5$\,Km/s indicated with the blue
+arrow.
+% 
+Now from Fig. \ref{fig:up-vaz-rag-2} we have that a local maxima of the response
+is obtained for an incoming beam with energy of 0.912\,eV and same polarization
+angle $\alpha=40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s and corresponding a
+velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane. Again
+the green circled box indicates the value for which the polarization angle
+$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega)$ are
+collinear corresponding to $78^{\circ}$ and having variations of $\pm 2^{\circ}$
+for $0^{\circ} \leq \alpha \leq 122^{\circ}$; this value corresponds to a response $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the green arrow.
+The blue square box indicates the value for which the polarization angle and the response angle are perpendicular corresponding to
+% 
+% WRONG
+% $\alpha=78.5^{\circ}$ and being held for  and corresponding to a response $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=10.3$\,Km/s indicated with the blue arrow.
 

### 2017-05-09 mu/article/article.tex
Description almost finished
There is only needed to chewck in the articles the meaning of a -
sign for V^{ab} and make a description of the non centrocym

--- 2017-05-08 mu/article/article.tex
@@
 
-{\color{red}
 \subsection{Pure spin velocity} % (fold)
@@
 polarization angle $\alpha$. Then,
-} % COLOR RED END
 \begin{widetext}
@@
 
-{\color{red}
 \subsection{Layer-by-layer analysis.}\label{sec:theory-layer}
@@
 \end{align}
-
-} % COLOR RED END
 
@@
 pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
-\textcolor{red}{ needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
-\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).}
-%
-{\color{red} 
+needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
+\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).
+%
 It is known that using DFT-LDA to calculate the electronic structure of
@@
 outside the scope of this paper.
-} % COLOR RED END
 % 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-{\color{red}
 
@@
 
-\caption{\color{red} Comparison of the reported maxima values of
+\caption{Comparison of the reported maxima values of
 $\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
@@
 this figure the most intense response corresponds to the \emph{up} structure
-centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
+centered at 0.088\,eV corresponding to the THz radiation and reaching a
 spin velocity of 87.16\,Km/s.
 % 
-In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
-four structures have contributions in the same order of magnitude. 
+In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
+to energies of the Thz and visible radiation, all the four structures have
+contributions in the same order of magnitude.
 % 
@@
 %
-} % COLOR RED END
 
@@
 
-    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
     vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
@@
 
-    \caption{\color{red} Most intense response of
+    \caption{Most intense response of
     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
@@
 
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
+% %% Description of UP |V_{s^z}| 3D
+% %%%%%%%%%%%%%%%%%
+\textbf{Up structure}
+
 We first present two energy ranges for the \emph{up} structure, the first for an
-incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained and the
-second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
-found.
+incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range where
+the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
+response is obtained and the second for an energy range from 1.80\,eV to 2.1\,eV
+where two local maxima are found.
 % 
@@
 From this figure we obtained that the zone where the maximum response is held
-corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
-and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
-local maxima are held for same polarization angles but for an energy range of
-the incoming beam between 1.90\,eV and 2.05\,eV.
-% 
+corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV,
+corresponding to the THz radiation, and polarization angles $\alpha$ between
+$30^{\circ}$ and $45^{\circ}$. Also two local maxima are held for same
+polarization angles but for an energy range of the incoming beam between
+1.90\,eV and 2.05\,eV corresponding to the THz and visible radiation.
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
+% %%%%%%%%%%%%%%%%%
 In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
@@
 the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
-which the response is maximized for the \emph{up} structure. In the same figures
-and frames we present in dashed lines, related to the right scale, the
-corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom
-frames of those figures the corresponding components
-$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$.
-Also we present two circled and square boxes indicating the value where the
-angles of the spin velocity is parallel and perpendicular and the the
-corresponding arrows is directed to the value of the response corresponding to
-those angles.
+which value the response is maximized for the \emph{up} structure. In the same
+figures and frames we present in dashed lines, related to the right scale, the
+corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ obtained from the
+evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of those
+figures the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega)$. Also we present two circled and square
+boxes indicating the values where the angles of the spin velocity are parallel
+and perpendicular and the the arrows are directed to the value of the response
+corresponding to those angles.
+% 
+From Figs. \ref{fig:up-vaz-rag-1} and \ref{fig:up-3d-vsz-1} we have that the
+absolute maximum response for the \emph{up} structure is obtained for an
+incoming beam with energy of 0.088\,eV and polarization angle
+$\alpha=40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the
+contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
+and $\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s for the spin polarized in the
+$\mathrm{z}$ direction and having a velocity angle
+$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
+% 
+In the same figure the green circled box indicates the value for which the
+polarization angle $\alpha$ and the response direction angle
+$\gamma_{\mathrm{z}}(\omega)$ are collinear being this angle $65.5^{\circ}$
+resulting in a value of the response of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated by the upward
+green arrow.
+% 
+Also the blue square box indicates the value for which the polarization angle
+and the response angle are perpendicular being $\alpha=155.5^{\circ}$ and
+$\gamma_{\mathrm{x}}(\omega)=65.5^{\circ}$; for this angles the response has a
+value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=24.8$\,Km/s indicated by
+the blue downward arrow.
+% 
+The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
+then, for this variation in the $\gamma_{\mathrm{z}}(\omega)$ angle the complete
+range of $\alpha$ angle is included because this last is almost constant.
+% 
+Now from Figs. \ref{fig:up-vaz-rag-2} and \ref{fig:up-3d-vsz-2} we have that a
+local maxima of the response is obtained for an incoming beam with energy of
+0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s directed in a
+velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane for
+the spin polarized in the $z$ direction.
+% 
+Again the green circled box indicates the value for which the polarization angle
+$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega)$ are
+collinear being both $78.5^{\circ}$ and having a response value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the
+green upward arrow. We found that for variations in the response angle of $\pm
+2^{\circ}$, indicated with the error bars, corresponds a range in the
+polarization angle of $0^{\circ} \leq \alpha \leq 122^{\circ}$ having then a
+large range for which the direction of the response is directed to this angle.
+% 
+The blue square box indicates the value for which the polarization angle and the
+response angle are perpendicular being $\alpha=168.5^{\circ}$
+$\gamma_{\mathrm{z}}(\omega)=78.5^{\circ}$ and having a response
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=9.0$\,Km/s indicated with the blue
+upward arrow. Again, for variations in the response angle of $\pm2^{\circ}$,
+indicated with the error bars, corresponds a range in the polarization angle of
+$155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a large range for which
+the direction of the response is held.
 
@@
     \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
-    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
     vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
@@
     structure fixing the energy to 0.912\,eV.}
-    \label{fig:figure1}
-\end{figure}
-
-For the \emph{alt} structure we present the energy range of the incoming beam from 0.6\,eV to 1.0\,eV, where the absolute and a local maxima of the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response are obtained.
-% 
+    \label{fig:alt-vaz-rag}
+\end{figure}
+
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
+% %% Description of ALT |V_{s^z}| 3D
+% %%%%%%%%%%%%%%%%%
+\textbf{Alt structure}
+
 In Fig. \ref{fig:alt-3d-vsb} we present the
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
-again the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
-the Eq. \eqref{eq:vab} for the \emph{alt} structure. In the figure we have that
-the onset of the response starts when the energy of the incoming beam is the
-same of the gap energy.
-% 
-From this figure we obtained that the zone where the absolute maximum response
-is held corresponds to a energy range of the incident beam from 0.90\,eV to
-0093\,eV and polarization angles $\alpha$ between $120^{\circ}$ and
-$150^{\circ}$. The local maximum is held or the same polarization angles but for
-energies between 0.67\,eV and 0.75\,eV.
+again the Eq. \eqref{eq:vs-mag} vs. the photon energy of the incident beam vs.
+the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the \emph{alt}
+structure . In the figure we have that the onset of the response starts when the
+energy of the incoming beam is the same of the gap energy.
+% 
+From this figure we found that the zone where the absolute maximum response is
+held corresponds to a energy range from 0.90\,eV to 0.93\,eV, corresponding to
+the THz raduation, and polarization angles $\alpha$ between $120^{\circ}$ and
+$150^{\circ}$. Also, a local maximum is obtained for the same polarization
+angles but for energies between 0.67\,eV and 0.75\,eV.
+% 
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
+% %%%%%%%%%%%%%%%%%
+In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
+result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
+left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
+the response is maximized for the \emph{alt} structure. In the same figure and
+frame we present in dashed line, related to the right scale, the velocity angle
+$\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
+$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
+components. Again, the circled and square boxes indicate the values for which
+the polarization angle and the velocity angle are parallel and perpendicular and
+with arrows are indicated the corresponding response value.
+% 
+From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
+maximum response for the \emph{alt} structure is obtained for an incoming beam
+with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
+polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
+$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the $xy$ plane. The circled box for
+the collinear angle corresponds for angles $\alpha$ and
+$\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
+box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
+$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
+for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
+presented with the error bars on the boxes, correspond ranges for the
+polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
+\alpha \leq 175^{\circ}$ because the response angle
+$\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range of the
+polarization angle $\alpha$.
 
@@
 \textbf{Up structure.}
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Description of UP |V^{a}| 3D
-% %% files: 
-% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% up-3d-vab.gp
-% %%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Description of UP |V^{a}| 3D
+% %%%%%%%%%%%%%%%%%
 For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
-0.16\,eV where we found the most intense response and the absolute maxima for
+0.16\,eV, where we found the most intense response and the absolute maxima for
 $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
@@
 From this picture we can see that for the zone between the energy range of
-0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone where the maximum response is held for both,
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+0.084\,eV-0.093\,eV,corresponding to the THz radiation, and polarization angles
+between $30^{\circ}$ and $45^{\circ}$ is the zone where the maximum response is
+held for both, $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+$|\mathcal{V}^{\mathrm{y}}|(\omega)$.
 % %%%%%%%%%%%%%%%%%
@@
 % %% Description of UP |V^{a}|, components and RTP
-% %% files: 
-% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
-% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
-% %% up-3d-vab.gp
 % %%%%%%%%%%%%%%%%%
@@
 % %% Description of UP |V^{a}| 3D
-% %% files: 
-% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% up-3d-vab.gp
 % %%%%%%%%%%%%%%%%%
 Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV presented in Fig. \ref{fig:up-3d-vva-2} where two local
-maxima of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-$|\mathcal{V}^{\mathrm{y}}|(\omega)$ are obtained for the \emph{up} structure.
+1.80\,eV to 2.10\,eV, corresponding to the THz and visible radiation, presented
+in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+are obtained for the \emph{up} structure.
 % 
@@
 % %% Starting description of UP |V^{x}|, components and RTP
-% %% files: vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
-% %%        vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
-% %%        alt-plots/up-vab-rtp.gp
 % %%%%%%%%%%%%%%%%
@@
 \textbf{Alt structure.}
-% %%%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{a}| 3D
-% %% files: 
-% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %% alt-3d-vab.gp
-% %%%%%%%%%%%%%%%%%
 \begin{figure}[tb]
@@
 
+% %%%%%%%%%%%%%%%%%
+% %% Description of ALT |V^{a}| 3D
+% %%%%%%%%%%%%%%%%%
 For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
-1.0\,eV where we found the a local maxima and the most intense responses for
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{a}}|(\omega)$.
-In Fig. \ref{fig:alt-3d-vva} we present the $|\mathcal{V}^{\mathrm{a}}|(\omega)$
-spectra resulting from evaluate again Eq. \eqref{eq:vv-mag} using different
-polarization angles $\alpha$ in Eq. \eqref{eq:vab} but now for the \emph{alt}
-structure. We can see that the onset of the response is when the energy of the
-incoming light is the same of the gap energy.
+1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
+and the most intense responses for $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
+$|\mathcal{V}^{\mathrm{a}}|(\omega)$. In Fig. \ref{fig:alt-3d-vva} we present
+the $|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate again
+Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
+\eqref{eq:vab} but now for the \emph{alt} structure. We can see that the onset
+of the response is when the energy of the incoming light is the same of the gap
+energy.
 %
@@
 % %% Starting description of ALT |V^{a}|, components and RTP
-% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
-% %%        vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%        alt-plots/alt-3d-vab.gp
 % %%%%%%%%%%%%%%%%
@@
 % %% Description of Up layer |V^{yz}|
-% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_12802_1_40-spin_scissor_0_Nc_18_ang_40
-% %%         calv.sm_0.03_yz_12802_2_40-spin_scissor_0_Nc_18_ang_40
-% %%         up-plots/up-vab-layers.gp
 % %%%%%%%%%%%%%%%%
@@
 % %% Description of ALT layer |V^{yz}|
-% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
-% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
-% %%         alt-plots/alt-vab-layers.gp
 % %%%%%%%%%%%%%%%%

### 2017-05-11 mu/article/article.tex
Review 1 sent to BMS

@@
 
-We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
-C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
-noncentrosymmetric semi-infinite carbon systems with 50\% hydrogenation in
-different arrangements. The \emph{alt} system has alternating hydrogen atoms on
-the upper and bottom sides of the carbon sheet, while the \emph{up} system has H
-only on the upper side. We take the hexagonal carbon lattice to be on the $xy$
-plane for both structures, and the carbon-hydrogen bonds on the perpendicular
-$xz$ plane, as depicted in Figs.
+We preset the results for $|\mathcal{V}^{\mathrm{a}}|(\omega)$ and
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ for the C$_{16}$H$_{8}$-alt and
+C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite carbon
+systems with 50\% hydrogenation in different arrangements. The \emph{alt} system
+has alternating hydrogen atoms on the upper and bottom sides of the carbon
+sheet, while the \emph{up} system has H only on the upper side. We take the
+hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
+carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
 \ref{fig:alt-struc} and \ref{fig:up-struc}.
@@
 needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
-\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).
+\eqref{eq:mu}), $\mathcal{V}^{\mathrm{ab}}(\omega)$ (Eq. \eqref{eq:vab}),
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ (Eq. \eqref{eq:vs-mag}) and
+$|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vv-mag}).
 %
@@
 materials predict a different band gap than the obtained experimentally. A
-correction for the band gap energy value can be calculated by other \emph{ab-
-initio} methods such as the GW approximation \cite{onidaRMP02} but this is
-outside the scope of this paper.
+correction for the band gap energy value can be calculated by other 
+\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
+is outside the scope of this paper.
 % 
@@
 responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
-\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
+\emph{up} 2D structures vs. CdSe and GaAs bulk systems. As we can see from
 this figure the most intense response corresponds to the \emph{up} structure
 centered at 0.088\,eV corresponding to the THz radiation and reaching a
-spin velocity of 87.16\,Km/s.
+spin velocity of 87.2\,Km/s.
 % 
@@
 GaAs structure has a large and almost planar zone where the response is held
-reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
-spin velocity of -21.6\,Km/s.
+reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
+a spin velocity of -21.6\,Km/s.
 % 
@@
 
-We first present two energy ranges for the \emph{up} structure, the first for an
-incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range where
-the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
-response is obtained and the second for an energy range from 1.80\,eV to 2.1\,eV
-where two local maxima are found.
+We first analyzed two energy ranges for the \emph{up} structure, the first for
+an incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range,
+where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
+response is obtained and the second for an energy range from 1.80\,eV to
+2.1\,eV, corresponding to the THz and visible radiation, where two local maxima
+are found.
 % 
@@
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
-the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
-Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
-onset of the response starts when the energy of the incoming beam is the same of
-the gap energy.
-% 
-From this figure we obtained that the zone where the maximum response is held
-corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV,
-corresponding to the THz radiation, and polarization angles $\alpha$ between
-$30^{\circ}$ and $45^{\circ}$. Also two local maxima are held for same
-polarization angles but for an energy range of the incoming beam between
-1.90\,eV and 2.05\,eV corresponding to the THz and visible radiation.
+Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in Eq.
+\eqref{eq:vab}. From the figure we have that the onset of the response starts
+when the energy of the incoming beam is the same of the gap energy.
+% 
+Making the analysis, we obtained that the zone where the maximum response is
+held corresponds to a energy range of the incident beam from 0.084\,eV to
+0.093\,eV and polarization angles $\alpha$ between $30^{\circ}$ and
+$45^{\circ}$. Also two local maxima are held for same polarization angles but
+for an energy range of the incoming beam between 1.90\,eV and 2.05\,eV.
 % %%%%%%%%%%%%%%%%%
@@
 boxes indicating the values where the angles of the spin velocity are parallel
-and perpendicular and the the arrows are directed to the value of the response
+and perpendicular and the arrows are directed to the value of the response
 corresponding to those angles.
 % 
-From Figs. \ref{fig:up-vaz-rag-1} and \ref{fig:up-3d-vsz-1} we have that the
+From Figs. \ref{fig:up-3d-vsz-1} and \ref{fig:up-vaz-rag-1} we have that the
 absolute maximum response for the \emph{up} structure is obtained for an
@@
 $\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=37.4$\,Km/s coming from the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=95.8$\,Km/s coming from the
 contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
@@
 polarization angle $\alpha$ and the response direction angle
-$\gamma_{\mathrm{z}}(\omega)$ are collinear being this angle $65.5^{\circ}$
+$\gamma_{\mathrm{z}}(\omega)$ are collinear being both angle $65.5^{\circ}$ and
 resulting in a value of the response of
@@
 The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
-then, for this variation in the $\gamma_{\mathrm{z}}(\omega)$ angle the complete
-range of $\alpha$ angle is included because this last is almost constant.
-% 
-Now from Figs. \ref{fig:up-vaz-rag-2} and \ref{fig:up-3d-vsz-2} we have that a
+then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega)$ the
+complete range of $\alpha$ angle is included because this last is almost
+constant.
+% 
+Now from Figs. \ref{fig:up-3d-vsz-2} and \ref{fig:up-vaz-rag-2} we have that a
 local maxima of the response is obtained for an incoming beam with energy of
 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s directed in a
-velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the $xy$ plane for
-the spin polarized in the $z$ direction.
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s. This comes from a
+major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega)$ component being
+directed in a velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the
+first Cartesian Quadrant of the $xy$ plane, for the spin polarized in the $z$
+direction.
 % 
@@
 the direction of the response is held.
+% 
+% 
+The most interesting case in which the spin is perpendicular to the surface of
+the structure and also for the \emph{up} structure the most intense was the
+presented before for which the spin is polarized in the $\mathrm{z}$ direction.
+We also made the analysis for the cases when the spin polarization is directed
+in the $\mathrm{x}$ and $\mathrm{y}$ direction but we do not present the
+corresponding plots. For those cases we have that the absolute maxima response
+is obtained for an energy of the incoming beam equal to 0.088\,eV and
+polarization angle $\alpha=40^{\circ}$ resulting in values of
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=37.4$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=24.8$\,Km/s.
 
@@
 
+For the \emph{alt} structure we analyzed the energy range for the incident beam from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained.
+% 
 In Fig. \ref{fig:alt-3d-vsb} we present the
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
-again the Eq. \eqref{eq:vs-mag} vs. the photon energy of the incident beam vs.
-the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the \emph{alt}
-structure . In the figure we have that the onset of the response starts when the
-energy of the incoming beam is the same of the gap energy.
+again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
+\eqref{eq:vab} for the \emph{alt} structure. In the figure we have that the
+onset of the response starts when the energy of the incoming beam is the same of
+the gap energy.
 % 
 From this figure we found that the zone where the absolute maximum response is
-held corresponds to a energy range from 0.90\,eV to 0.93\,eV, corresponding to
-the THz raduation, and polarization angles $\alpha$ between $120^{\circ}$ and
-$150^{\circ}$. Also, a local maximum is obtained for the same polarization
-angles but for energies between 0.67\,eV and 0.75\,eV.
-% 
+held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
+angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
+is obtained for the same polarization angles but for energies between 0.67\,eV
+and 0.75\,eV.
 % %%%%%%%%%%%%%%%%%
@@
 the response is maximized for the \emph{alt} structure. In the same figure and
-frame we present in dashed line, related to the right scale, the velocity angle
-$\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
+frame we present with dashed line, related to the right scale, the velocity
+angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
 $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
@@
 polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
-$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the $xy$ plane. The circled box for
-the collinear angle corresponds for angles $\alpha$ and
-$\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
+$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
+$xy$ plane. The circled box for the collinear angle corresponds for angles
+$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
 box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
@@
 polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
-\alpha \leq 175^{\circ}$ because the response angle
-$\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range of the
-polarization angle $\alpha$.
+\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
+angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
+of the polarization angle $\alpha$.
+% 
+Again, for the cases in which the spin polarization is parallel to the surface
+of the \emph{alt} structure was calculated but the plots are not presented here.
+The absolute maxima for the case when the spin polarization is directed in the
+$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
+incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
+resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=27.1$\,Km/s
+and $|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=33.2$\,Km/s.
 
@@
 0.16\,eV, where we found the most intense response and the absolute maxima for
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
-% 
-In Fig. \ref{fig:up-3d-vva-1} we present the
-$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
-\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
+\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
 \eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
@@
 From this picture we can see that for the zone between the energy range of
-0.084\,eV-0.093\,eV,corresponding to the THz radiation, and polarization angles
-between $30^{\circ}$ and $45^{\circ}$ is the zone where the maximum response is
-held for both, $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-$|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
+$45^{\circ}$ is the zone where the maximum response is held for both,
+$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
 % %%%%%%%%%%%%%%%%%
@@
 related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
-for which the response is maximized for the \emph{up} structure. In the same
+for which the response is maximized. In the same
 figures and frames we present in dashed lines the corresponding polar

### 2017-05-16 mu/article/article.tex
Correction of plot labels and eqns in text.

@@
 \begin{align}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
+|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)| 
 &=
 \sqrt{
-(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
-(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
+[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2}\ +
+[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2}\ 
 }, 
@@
 \begin{equation}
-|\mathcal{V}^{\mathrm{a}}| (\omega)= 
+|\mathcal{V}^{\mathrm{a}}(\omega)| = 
 \sqrt {
-(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
-(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
-(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
+[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2} +
+[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2} +
+[\mathcal{V}^{\mathrm{az}}(\omega)]^{2} 
 },
@@
 
-We preset the results for $|\mathcal{V}^{\mathrm{a}}|(\omega)$ and
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ for the C$_{16}$H$_{8}$-alt and
-C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite carbon
-systems with 50\% hydrogenation in different arrangements. The \emph{alt} system
-has alternating hydrogen atoms on the upper and bottom sides of the carbon
-sheet, while the \emph{up} system has H only on the upper side. We take the
-hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
-carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
+We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega)|$ and
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|$ for the C$_{16}$H$_{8}$-alt and
+C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
+carbon systems with 50\% hydrogenation in different arrangements. The \emph{alt}
+system has alternating hydrogen atoms on the upper and bottom sides of the
+carbon sheet, while the \emph{up} system has H only on the upper side. We take
+the hexagonal carbon lattice to be on the $xy$ plane for both structures, and
+the carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
 \ref{fig:alt-struc} and \ref{fig:up-struc}.
@@
 pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
-needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
-\eqref{eq:mu}), $\mathcal{V}^{\mathrm{ab}}(\omega)$ (Eq. \eqref{eq:vab}),
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ (Eq. \eqref{eq:vs-mag}) and
-$|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vv-mag}).
+needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ presented in Eq.
+\eqref{eq:mu}.
 % 
@@
     \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
-    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
-    polarization angles.}
+    for 2D \emph{alt} and \emph{up}, and bulk CdSe and GaAs structures and the
+    corresponding polarization angles.}
     \label{fig:vab-str-comp}
@@
 
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
     vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
@@
     \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frames, right scale of
     figs (a) and (b)), the corresponding velocity angle
@@
 an incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range,
-where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$
+where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$
 response is obtained and the second for an energy range from 1.80\,eV to
@@
 In Fig. \ref{fig:up-3d-vsz} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
 Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in Eq.
@@
 present in solid lines the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the left scale, fixing
 the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
@@
 $\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=95.8$\,Km/s coming from the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=95.8$\,Km/s coming from the
 contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
@@
 resulting in a value of the response of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated by the upward
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=82.3$\,Km/s indicated by the upward
 green arrow.
@@
 $\gamma_{\mathrm{x}}(\omega)=65.5^{\circ}$; for this angles the response has a
-value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=24.8$\,Km/s indicated by
+value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=24.8$\,Km/s indicated by
 the blue downward arrow.
@@
 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s. This comes from a
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=30.3$\,Km/s. This comes from a
 major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega)$ component being
@@
 collinear being both $78.5^{\circ}$ and having a response value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=23.5$\,Km/s indicated with the
 green upward arrow. We found that for variations in the response angle of $\pm
@@
 $\gamma_{\mathrm{z}}(\omega)=78.5^{\circ}$ and having a response
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=9.0$\,Km/s indicated with the blue
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=9.0$\,Km/s indicated with the blue
 upward arrow. Again, for variations in the response angle of $\pm2^{\circ}$,
@@
 polarization angle $\alpha=40^{\circ}$ resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=37.4$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=24.8$\,Km/s.
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=37.4$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=24.8$\,Km/s.
 
@@
     \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
     vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
@@
     \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frame, left scale) the
     corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
@@
 
-For the \emph{alt} structure we analyzed the energy range for the incident beam from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained.
+For the \emph{alt} structure we analyzed the energy range for the incident beam
+from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute
+maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
 % 
 In Fig. \ref{fig:alt-3d-vsb} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
 again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
-\eqref{eq:vab} for the \emph{alt} structure. In the figure we have that the
-onset of the response starts when the energy of the incoming beam is the same of
-the gap energy.
+\eqref{eq:vab} for the \emph{alt} structure.
 % 
@@
 In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
-result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
+result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
 left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
@@
 with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
 polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
@@
 $\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
 box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
 $\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
 for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
@@
 incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
-resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=27.1$\,Km/s
-and $|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=33.2$\,Km/s.
+resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
+and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ for \emph{up} structure
     \label{fig:up-3d-vvx-1}]
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ for \emph{up} structure
     \label{fig:up-3d-vvy-1}]
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
     polarization angle for the \emph{up} structure. The absolute maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
+    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy
     range from 0.08\,eV to 0.10\,eV and for polarization angles from
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ 
     \label{fig:up-vx-comp-rtp-1}]
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ 
     \label{fig:up-vy-comp-rtp-1}]
@@
     \caption{Most intense response of
-    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
+    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
     (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
@@
 0.16\,eV, where we found the most intense response and the absolute maxima for
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
 presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
 \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
-response is when the energy of the incoming light is the same of the gap energy.
+\eqref{eq:vab} for the \emph{up} structure.
 %
@@
 $45^{\circ}$ is the zone where the maximum response is held for both,
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$.
 % %%%%%%%%%%%%%%%%%
@@
 \ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
 related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
@@
 right scale. Also, in the bottom frames of those figures we present the
-decomposition of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-$|\mathcal{V}^{\mathrm{y}}|(\omega)$ in the corresponding
+decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega)|$ in the corresponding
 $\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
     polarization angle for the \emph{up} structure. The local maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy range from
+    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy range from
     1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
@@
     \caption{Intense response of
-    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
+    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
     (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
@@
 % 
-$|\mathcal{V}^{\mathrm{x}}|(\omega)=58.7$\,Km/s 
+$|\mathcal{V}^{\mathrm{x}}(\omega)|=58.7$\,Km/s 
 % 
@@
 % 
-$|\mathcal{V}^{\mathrm{y}}|(\omega)=87.9$\,Km/s
+$|\mathcal{V}^{\mathrm{y}}(\omega)|=87.9$\,Km/s
 % 
@@
 in the $y$ direction and being 1.5 times more intense than
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ To this absolute maximum correspond spin
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ To this absolute maximum correspond spin
 polar and azimuthal angles $\theta_{\mathrm{y}}(\omega)=8$ and
@@
 perpendicularly over the $xy$ plane and being localized on the first Cartesian
-Quadrant. In a different way than in the $|\mathcal{V}^{\mathrm{x}}|(\omega)$
+Quadrant. In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega)|$
 case only the polar angle is hold for the peak of the response having a
@@
 energy for the incoming beam of 0.118\,eV the components of both,
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
 have no change in the spin polarization direction. Finally, after this energy
@@
 in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
 are obtained for the \emph{up} structure.
@@
 \ref{fig:up-vy-comp-rtp-2} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
 related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
@@
 an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
-in a value of $|\mathcal{V}^{\mathrm{x}}|(\omega)= 6.6$\,Km/s along the $x$
+in a value of $|\mathcal{V}^{\mathrm{x}}(\omega)|= 6.6$\,Km/s along the $x$
 direction  with polar and azimuthal spin polarization angles
@@
 For the spin moving along the $y$ direction we have a value of
-$|\mathcal{V}^{\mathrm{y}}|(\omega)=28.7$\,Km/s with polar and azimuthal angles
+$|\mathcal{V}^{\mathrm{y}}(\omega)|=28.7$\,Km/s with polar and azimuthal angles
 $\theta_{\mathrm{y}}(\omega)=45^{\circ}$ and
@@
 contributions and resulting in values of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)=9.9$\,Km/s and spin polarization angles
+$|\mathcal{V}^{\mathrm{x}}(\omega)|=9.9$\,Km/s and spin polarization angles
 $\theta_{\mathrm{x}}(\omega)=129^{\circ}$ and
@@
 For the spin moving in the $y$ direction we have a value of
-$|\mathcal{V}^{\mathrm{y}}|(\omega)=49.4$\,Km/s with spin polarization angles
+$|\mathcal{V}^{\mathrm{y}}(\omega)|=49.4$\,Km/s with spin polarization angles
 $\theta_{\mathrm{y}}(\omega)=127^{\circ}$ and
@@
 % 
-Finally we have that for bot energies $|\mathcal{V}^{\mathrm{y}}|(\omega)$ is
-more intense than $|\mathcal{V}^{\mathrm{x}}|(\omega)$ being 4.4 times more
+Finally we have that for bot energies $|\mathcal{V}^{\mathrm{y}}(\omega)|$ is
+more intense than $|\mathcal{V}^{\mathrm{x}}(\omega)|$ being 4.4 times more
 intense for 1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
     polarization angle for the \emph{alt} structure. The absolute maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy range from
+    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy range from
     0.90\,eV to 0.93\,eV and for polarization angles from 120$^{\circ}$ to
@@
 1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
-and the most intense responses for $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
-$|\mathcal{V}^{\mathrm{a}}|(\omega)$. In Fig. \ref{fig:alt-3d-vva} we present
-the $|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate again
+and the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega)|$. In Fig. \ref{fig:alt-3d-vva} we present
+the $|\mathcal{V}^{\mathrm{a}}(\omega)|$ spectra resulting from evaluate again
 Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
@@
 150$^{\circ}$ is the zone where the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$ is
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$ is
 held. We also found that the first peak is obtained when the energy of the
@@
 \ref{fig:alt-vy-comp-rtp} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
+$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
 related to the left scale, fixing the polarization angle to $\alpha=145^{\circ}$
@@
 the components resulting in a response of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)=19.4$\,Km/s and polar and azimuthal spin
+$|\mathcal{V}^{\mathrm{x}}(\omega)|=19.4$\,Km/s and polar and azimuthal spin
 polarization angles $\theta_{\mathrm{x}}(\omega)=46^{\circ}$ and
@@
 $\mathcal{V}^{\mathrm{xz}}(\omega)$ component resulting in a total response of
-$|\mathcal{V}^{\mathrm{x}}|(\omega)=30.9$\,Km/s and angles
+$|\mathcal{V}^{\mathrm{x}}(\omega)|=30.9$\,Km/s and angles
 $\theta_{\mathrm{x}}(\omega)=154^{\circ}$, and
@@
 component resulting in a response of
-$|\mathcal{V}^{\mathrm{y}}|(\omega)=51.9$\,Km/s and angles
+$|\mathcal{V}^{\mathrm{y}}(\omega)|=51.9$\,Km/s and angles
 $\theta_{\mathrm{y}}(\omega)=141^{\circ}$ and
@@
 the components resulting in a response
-$|\mathcal{V}^{\mathrm{y}}|(\omega)=52.3$\,Km/s being this the absolute maximum
+$|\mathcal{V}^{\mathrm{y}}(\omega)|=52.3$\,Km/s being this the absolute maximum
 response for the \emph{alt} structure. The corresponding angles are

### 2017-05-16 mu/article/article.tex
Changin working station

@@
 
-Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
-state and the Kohn-Sham states using density functional theory in the local
-density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
+We calculated the self-consistent ground state and the Kohn-Sham states using
+density functional theory in the local density approximation (DFT-LDA) with a
+planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
 Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
@@
 In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the Thz and visible radiation, all the four structures have
-contributions in the same order of magnitude.
+to energies of the near infrared (NIR) and visible radiation, all the four
+structures have contributions in the same order of magnitude.
 % 

### 2017-05-17 mu/article/article.tex
Changing working station.

@@
 In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the near infrared (NIR) and visible radiation, all the four
+to energies of the Near Infrared (NIR) and visible radiation, all the four
 structures have contributions in the same order of magnitude.
@@
 We first analyzed two energy ranges for the \emph{up} structure, the first for
-an incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range,
-where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$
-response is obtained and the second for an energy range from 1.80\,eV to
-2.1\,eV, corresponding to the THz and visible radiation, where two local maxima
-are found.
+an incoming energy beam from 0.0\,eV to 0.2\,eV which inlude the THz and the Mid
+Infrared (MIR) range, where the absolute maximum of the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained and the
+second for an energy range from 1.80\,eV to 2.1\,eV, corresponding to visible
+radiation, where two local maxima are found.
 % 
@@
 % %%%%%%%%%%%%%%%%%
+
 \textbf{Alt structure}
@@
 For the \emph{alt} structure we analyzed the energy range for the incident beam
-from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute
+from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
 maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
@@
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
-again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
-\eqref{eq:vab} for the \emph{alt} structure.
+again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
+polarization angle $\alpha$ for the \emph{alt} structure.
 % 

### 2017-05-17 mu/article/article.tex
Changing alpha dependence formulae till line 596

@@
 \begin{equation}
-\dot{K} = \mu^{\mathrm{abcd}}(\omega)
+\dot{K}(\omega) = \mu^{\mathrm{abcd}}(\omega)
 E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
@@
 \begin{align}
-\mathcal{V}^{\mathrm{ab}} (\omega) 
+\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
 &= \frac{2}{\hbar}
@@
 $x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
-spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle
-$\gamma_{b}$ as
+spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ in a fixed angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ as
 \begin{align}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)| 
+|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
 &=
 \sqrt{
-[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2}\ +
-[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2}\ 
+[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
+[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
 }, 
@@
 \\
-\gamma_{\mathrm{b}} (\omega)
+\gamma_{\mathrm{b}} (\omega,\alpha)
 &=
-\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
-{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
+{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
 \label{eq:gamma-ang}
@@
 In a similar way we can fix the velocity in the $xy$ plane
-along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
-\begin{equation}
-|\mathcal{V}^{\mathrm{a}}(\omega)| = 
-\sqrt {
-[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2} +
-[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2} +
-[\mathcal{V}^{\mathrm{az}}(\omega)]^{2} 
+along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ as
+\begin{align}
+|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
+&\sqrt { 
+[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
+[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
+[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
 },
 \label{eq:vv-mag}
-\end{equation}
+\end{align}
 and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
 \begin{align}
-\theta_{\mathrm{a}}  (\omega)
+\theta_{\mathrm{a}}  (\omega,\alpha)
 =& 
-\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
-{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
+\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
+{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
 & 0 \leq &\theta \leq \pi, 
@@
 \\
-\varphi_{\mathrm{a}} (\omega)
+\varphi_{\mathrm{a}} (\omega,\alpha)
 =& 
-\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
-{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
+{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
 & 0 \leq &\varphi \leq 2\pi.
@@
 \begin{align}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|
+|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|
 =& 
@@
 \sum_{\ell=1}^{N_{\mathrm{eff}}}
-|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega)|
+|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|
 \label{eq:vs-layer}
 \\
-|\mathcal{V}^{\mathrm{a}}(\omega)|
+|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|
 =&
@@
 \sum_{\ell=1}^{N_{\mathrm{eff}}}
-|\mathcal{V}^{\mathrm{a}} (\ell | \omega)|
+|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|
 \label{eq:vv-layer}
@@
 
-We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega)|$ and
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|$ for the C$_{16}$H$_{8}$-alt and
-C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
+We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ and
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ for the C$_{16}$H$_{8}$-alt
+and C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
 carbon systems with 50\% hydrogenation in different arrangements. The \emph{alt}
@@
 density functional theory in the local density approximation (DFT-LDA) with a
-planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
+planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
+Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
 pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
-needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ presented in Eq.
+needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
 \eqref{eq:mu}.
@@
 Energy & 
-\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
+\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
 \cline{5-6}
@@
 
-In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
-responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
-\emph{up} 2D structures vs. CdSe and GaAs bulk systems. As we can see from
-this figure the most intense response corresponds to the \emph{up} structure
-centered at 0.088\,eV corresponding to the THz radiation and reaching a
-spin velocity of 87.2\,Km/s.
+{\Large  We calculated the $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$} response In figure
+\ref{fig:vab-str-comp} we present a comparison of the most intense responses
+resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and \emph{up}
+2D structures and CdSe and GaAs bulk systems. As we can see from this figure the
+most intense response corresponds to the \emph{up} structure centered at
+0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
+velocity of 87.2\,Km/s.
 % 
@@
 In table \ref{tab:vab-str-comp} we present the comparison of this values for the
-2D and bulk structures.
+2D and bulk structures. We found that the most intense response for the spin
+velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
+4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
+structure has a response more intense than the bulk systems but being less
+intense than the corresponding to the \emph{up} one.
 %
@@
 
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
-    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
-    structure for two energy ranges. The absolute maxima is located for an
-    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
-    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
-    $50^{\circ}$.}
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
+    as a function of the photon energy and polarization angle $\alpha$ for the
+    \emph{up} structure for two energy ranges. The absolute maxima is located
+    for an energy range from 0.08\,eV to 0.10\,eV and the local maximum from
+    1.95\,eV to 2.0\,eV and both for polarization angles between $25^{\circ}$
+    and $50^{\circ}$.}
     \label{fig:up-3d-vsz}   
@@
     \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frames, right scale of
-    figs (a) and (b)), the corresponding velocity angle
-    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
-    (circled box) and perpendicular (square box) angles, and the two components
-    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
-    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
-    }
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frames, right
+    scale of figs (a) and (b)), the corresponding velocity angle
+    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (top frames, right scale), the
+    collinear (circled box) and perpendicular (square box) angles, and the two
+    components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+    $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ (bottom frames) for the \emph{up}
+    structure fixing the energy to 0.088\,eV. }
     \label{fig:up-vaz-rag}
@@
 % %%%%%%%%%%%%%%%%%
+
+Using the Eq. \eqref{eq:vs-mag}, we calculated the
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega,\alpha)$ response and made the
+analysis for the case when the spin is fixed in the $z$ direction, directed
+perpendicularly to the surface of the \emph{alt} and \emph{up} structures. Also,
+using the Eq. \eqref{eq:gamma-ang}, we determined the angle
+$\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
+surface of the each structure.
+
 \textbf{Up structure}
@@
 Infrared (MIR) range, where the absolute maximum of the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained and the
-second for an energy range from 1.80\,eV to 2.1\,eV, corresponding to visible
-radiation, where two local maxima are found.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained and
+the second for an energy range from 1.80\,eV to 2.1\,eV, corresponding to
+visible radiation, where two local maxima are found.
 % 
 In Fig. \ref{fig:up-3d-vsz} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
-Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab}. From the figure we have that the onset of the response starts
-when the energy of the incoming beam is the same of the gap energy.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
+evaluate Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
+Eq. \eqref{eq:vab}. From the figure we have that the onset of the response
+starts when the energy of the incoming beam is the same of the gap energy.
 % 
@@
 present in solid lines the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the left scale, fixing
-the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively, for
-which value the response is maximized for the \emph{up} structure. In the same
-figures and frames we present in dashed lines, related to the right scale, the
-corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ obtained from the
-evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of those
-figures the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega)$. Also we present two circled and square
-boxes indicating the values where the angles of the spin velocity are parallel
-and perpendicular and the arrows are directed to the value of the response
-corresponding to those angles.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related to the left scale,
+fixing the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively,
+for which value the response is maximized for the \emph{up} structure. In the
+same figures and frames we present in dashed lines, related to the right scale,
+the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ obtained
+from the evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of
+those figures the corresponding components
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
+square boxes indicating the values where the angles of the spin velocity are
+parallel and perpendicular and the arrows are directed to the value of the
+response corresponding to those angles.
 % 
@@
 $\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=95.8$\,Km/s coming from the
-contribution of the components $\mathcal{V}^{\mathrm{xz}}(\omega)=39.8$\,Km/s
-and $\mathcal{V}^{\mathrm{yz}}(\omega)=87.2$\,Km/s for the spin polarized in the
-$\mathrm{z}$ direction and having a velocity angle
-$\gamma_{\mathrm{z}}(\omega)=65^{\circ}$ on the $xy$ plane.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=95.8$\,Km/s coming from the
+contribution of the components
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s for the spin polarized in
+the $\mathrm{z}$ direction and having a velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha)=65^{\circ}$ on the $xy$ plane.
 % 
@@
 polarization angle $\alpha$ and the response direction angle
-$\gamma_{\mathrm{z}}(\omega)$ are collinear being both angle $65.5^{\circ}$ and
-resulting in a value of the response of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=82.3$\,Km/s indicated by the upward
-green arrow.
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ are collinear being both angle
+$65.5^{\circ}$ and resulting in a value of the response of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=82.3$\,Km/s indicated by the
+upward green arrow.
 % 
@@
 and the response angle are perpendicular being $\alpha=155.5^{\circ}$ and
-$\gamma_{\mathrm{x}}(\omega)=65.5^{\circ}$; for this angles the response has a
-value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=24.8$\,Km/s indicated by
-the blue downward arrow.
+$\gamma_{\mathrm{x}}(\omega,\alpha)=65.5^{\circ}$; for this angles the response
+has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=24.8$\,Km/s
+indicated by the blue downward arrow.
 % 
 The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
-then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega)$ the
-complete range of $\alpha$ angle is included because this last is almost
+then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega,\alpha)$
+the complete range of $\alpha$ angle is included because this last is almost
 constant.
@@
 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=30.3$\,Km/s. This comes from a
-major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega)$ component being
-directed in a velocity angle $\gamma_{\mathrm{z}}(\omega)=78^{\circ}$ on the
-first Cartesian Quadrant of the $xy$ plane, for the spin polarized in the $z$
-direction.
+of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
+from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
+component being directed in a velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first Cartesian Quadrant
+of the $xy$ plane, for the spin polarized in the $z$ direction.
 % 
 Again the green circled box indicates the value for which the polarization angle
-$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega)$ are
-collinear being both $78.5^{\circ}$ and having a response value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=23.5$\,Km/s indicated with the
-green upward arrow. We found that for variations in the response angle of $\pm
-2^{\circ}$, indicated with the error bars, corresponds a range in the
+$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega,\alpha)$
+are collinear being both $78.5^{\circ}$ and having a response value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=23.5$\,Km/s indicated with
+the green upward arrow. We found that for variations in the response angle of
+$\pm 2^{\circ}$, indicated with the error bars, corresponds a range in the
 polarization angle of $0^{\circ} \leq \alpha \leq 122^{\circ}$ having then a
@@
 response angle are perpendicular being $\alpha=168.5^{\circ}$
-$\gamma_{\mathrm{z}}(\omega)=78.5^{\circ}$ and having a response
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=9.0$\,Km/s indicated with the blue
-upward arrow. Again, for variations in the response angle of $\pm2^{\circ}$,
-indicated with the error bars, corresponds a range in the polarization angle of
-$155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a large range for which
-the direction of the response is held.
+$\gamma_{\mathrm{z}}(\omega,\alpha)=78.5^{\circ}$ and having a response
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=9.0$\,Km/s indicated with
+the blue upward arrow. Again, for variations in the response angle of
+$\pm2^{\circ}$, indicated with the error bars, corresponds a range in the
+polarization angle of $155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a
+large range for which the direction of the response is held.
 % 
@@
 polarization angle $\alpha=40^{\circ}$ resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=37.4$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=24.8$\,Km/s.
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=24.8$\,Km/s.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
+$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response and made the analysis for the case
+when the velocity is fixed in the $x$ and $y$ direction over the surface of the
+\emph{alt} and \emph{up} structures. Also, using the Eqns. \eqref{eq:polar-ang}
+and \eqref{eq:azimuthal-ang}, we determined the polar
+$\theta_{\mathrm{a}}(\omega)$ and azimuthal $\varphi_{\mathrm{a}}(\omega)$
+angles where the spin polarization is directed.
 

### 2017-05-17 mu/article/article.tex
Adding alpha dependence in text for all formulae

@@
 % 
-% 
 The most interesting case in which the spin is perpendicular to the surface of
@@
     \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
     vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
@@
     \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frame, left scale) the
-    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
-    scale), the collinear (circled box) and perpendicular (square box) angles,
-    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frame, left scale)
+    the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame,
+    right scale), the collinear (circled box) and perpendicular (square box)
+    angles, and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
     $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
@@
 from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
-maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
+maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
+obtained.
 % 
 In Fig. \ref{fig:alt-3d-vsb} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
-again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
+evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
 polarization angle $\alpha$ for the \emph{alt} structure.
@@
 In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
-result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
-left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
-the response is maximized for the \emph{alt} structure. In the same figure and
-frame we present with dashed line, related to the right scale, the velocity
-angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
-$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
-components. Again, the circled and square boxes indicate the values for which
-the polarization angle and the velocity angle are parallel and perpendicular and
-with arrows are indicated the corresponding response value.
+result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related
+to the left scale, fixing the energy of the incoming beam to 0.912\,eV for which
+value the response is maximized for the \emph{alt} structure. In the same figure
+and frame we present with dashed line, related to the right scale, the velocity
+angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ and in the bottom frame the
+corresponding $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components. Again, the circled and
+square boxes indicate the values for which the polarization angle and the
+velocity angle are parallel and perpendicular and with arrows are indicated the
+corresponding response value.
 % 
@@
 with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43.0$\,Km/s and for the spin
 polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
-$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
-$xy$ plane. The circled box for the collinear angle corresponds for angles
-$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
-box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
-$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
-for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
-presented with the error bars on the boxes, correspond ranges for the
-polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
-\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
-angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
-of the polarization angle $\alpha$.
+$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
+of the $xy$ plane. The circled box for the collinear angle corresponds for
+angles $\alpha$ and $\gamma_{\mathrm{z}}(\omega,\alpha)$ equal to $53.5^{\circ}$
+with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=12.7$\,Km/s,
+and the blue square box indicates the perpendicular angles for values
+$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ with a
+value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s. Finally
+we found that for variations of $\pm0.5^{\circ}$ of those collinear and
+perpendicular angles, presented with the error bars on the boxes, correspond
+ranges for the polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and
+$95^{\circ} \leq \alpha \leq 175^{\circ}$ covering a wide range of angles
+because the response angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ has small
+variations for the complete range of the polarization angle $\alpha$.
 % 
@@
 incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
-resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
-and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.
+resulting in values of
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.
 
@@
 Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
-$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response and made the analysis for the case
-when the velocity is fixed in the $x$ and $y$ direction over the surface of the
-\emph{alt} and \emph{up} structures. Also, using the Eqns. \eqref{eq:polar-ang}
-and \eqref{eq:azimuthal-ang}, we determined the polar
-$\theta_{\mathrm{a}}(\omega)$ and azimuthal $\varphi_{\mathrm{a}}(\omega)$
-angles where the spin polarization is directed.
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response and made the analysis for
+the case when the velocity is fixed in the $x$ and $y$ direction over the
+surface of the \emph{alt} and \emph{up} structures. Also, using the Eqns.
+\eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the polar
+$\theta_{\mathrm{a}}(\omega,\alpha)$ and azimuthal
+$\varphi_{\mathrm{a}}(\omega,\alpha)$ angles where the spin polarization is
+directed.
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ for \emph{up} structure
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for \emph{up}
+    structure
     \label{fig:up-3d-vvx-1}]
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ for \emph{up} structure
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ for \emph{up}
+    structure
     \label{fig:up-3d-vvy-1}]
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
-    polarization angle for the \emph{up} structure. The absolute maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
+    energy vs. polarization angle for the \emph{up} structure. The absolute
+    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
     range from 0.08\,eV to 0.10\,eV and for polarization angles from
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ 
     \label{fig:up-vx-comp-rtp-1}]
@@
     \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ 
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ 
     \label{fig:up-vy-comp-rtp-1}]
@@
     \caption{Most intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
+    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
+    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
+    angles (top frames right scale), and the corresponding three components
+    (bottom frames) for the \emph{up} structure fixing the polarization angle to
+    $\alpha=40^{\circ}$ to maximize the response.}
+    \label{fig:up-vab-comp-rtp-1}
+\end{figure}
+
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Description of UP |V^{a}| 3D
+% %%%%%%%%%%%%%%%%%
+For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
+0.16\,eV, where we found the most intense response and the absolute maxima for
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ presented in Fig.
+% 
+\ref{fig:up-3d-vva-1} and resulting from evaluate Eq. \eqref{eq:vv-mag} as a
+function of the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the
+\emph{up} structure.
+%
+From this picture we can see that for the zone between the energy range of
+0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
+$45^{\circ}$ is the zone where the maximum response is held for both,
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$.
+% %%%%%%%%%%%%%%%%%
+% %% 1.8 eV - 2.0 eV
+% %% Description of UP |V^{a}|, components and RTP
+% %%%%%%%%%%%%%%%%%
+
+In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
+% 
+\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$,
+related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
+for which the response is maximized. In the same
+figures and frames we present in dashed lines the corresponding polar
+$\theta_{a}(\omega,\alpha)$ and azimuthal $\varphi_{a}(\omega,\alpha)$ angles related to the
+right scale. Also, in the bottom frames of those figures we present the
+decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ in the corresponding
+$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and $\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
+components.
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vvx-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
+    \label{fig:up-3d-vvy-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
+
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon energy vs.
+    polarization angle for the \emph{up} structure. The local maxima of both
+    responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy range from
+    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
+    $50^{\circ}$.}
+    \label{fig:up-3d-vva-2}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
+    \\
+    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
+    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
+
+    \caption{Intense response of
+    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs. (a) and
     (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
@@
     $\alpha=40^{\circ}$ to maximize the response.}
-    \label{fig:up-vab-comp-rtp-1}
-\end{figure}
-
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Description of UP |V^{a}| 3D
-% %%%%%%%%%%%%%%%%%
-For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
-0.16\,eV, where we found the most intense response and the absolute maxima for
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
-presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
-\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab} for the \emph{up} structure.
-%
-From this picture we can see that for the zone between the energy range of
-0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone where the maximum response is held for both,
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$.
-% %%%%%%%%%%%%%%%%%
-% %% 1.8 eV - 2.0 eV
-% %% Description of UP |V^{a}|, components and RTP
-% %%%%%%%%%%%%%%%%%
-
-In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
-% 
-\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
-related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
-for which the response is maximized. In the same
-figures and frames we present in dashed lines the corresponding polar
-$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
-right scale. Also, in the bottom frames of those figures we present the
-decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega)|$ in the corresponding
-$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
-components.
-\begin{figure}[t]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vvx-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vvy-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
-
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
-    polarization angle for the \emph{up} structure. The local maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy range from
-    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
-    $50^{\circ}$.}
-    \label{fig:up-3d-vva-2}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
-
-    \caption{Intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
-    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
-    frames right scale), and the corresponding three components (bottom frames)
-    for the \emph{up} structure fixing the polarization angle to
-    $\alpha=40^{\circ}$ to maximize the response.}
 
@@
 % 
-$\mathcal{V}^{\mathrm{xx}}(\omega)=-36.5$\,Km/s,
-$\mathcal{V}^{\mathrm{xy}}(\omega)=-23.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}(\omega)= 39.8$\,Km/s 
+$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)=-36.5$\,Km/s,
+$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)=-23.2$\,Km/s, and
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)= 39.8$\,Km/s 
 % 
@@
 % 
-$|\mathcal{V}^{\mathrm{x}}(\omega)|=58.7$\,Km/s 
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s 
 % 
@@
 in the $x$ direction. To this value corresponds a polar and azimuthal angles of
-$\theta_{\mathrm{x}}(\omega)=47$ and $\varphi_{\mathrm{x}}(\omega)=212$,
-respectively, being directed upper the third Cartesian Quadrant of the $xy$
-plane. Also from this figure we have that those angle values are hold for almost
-all the peak of the response having a deviation of $\pm 2^{\circ}$ in the range
-of energies from 0.028\,eV to 0.098\,eV from the corresponding to the absolute
-maximum mentioned before.
+$\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upper
+the third Cartesian Quadrant of the $xy$ plane. Also from this figure we have
+that those angle values are hold for almost all the peak of the response having
+a deviation of $\pm 2^{\circ}$ in the range of energies from 0.028\,eV to
+0.098\,eV from the corresponding to the absolute maximum mentioned before.
 % 
@@
 % 
-$\mathcal{V}^{\mathrm{yx}}(\omega)= -7.9$\,Km/s 
-$\mathcal{V}^{\mathrm{yy}}(\omega)=  8.6$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}(\omega)= 87.2$\,Km/s 
+$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)= -7.9$\,Km/s 
+$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)=  8.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)= 87.2$\,Km/s 
 % 
@@
 % 
-$|\mathcal{V}^{\mathrm{y}}(\omega)|=87.9$\,Km/s
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=87.9$\,Km/s
 % 
@@
 in the $y$ direction and being 1.5 times more intense than
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ To this absolute maximum correspond spin
-polar and azimuthal angles $\theta_{\mathrm{y}}(\omega)=8$ and
-$\varphi_{\mathrm{y}}(\omega)=133$, respectively, being directed almost
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ To this absolute maximum correspond
+spin polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha)=8$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=133$, respectively, being directed almost
 perpendicularly over the $xy$ plane and being localized on the first Cartesian
-Quadrant. In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega)|$
-case only the polar angle is hold for the peak of the response having a
-deviation of $\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but
-the azimuthal angle changes since the onset to 0.106\,eV from $99^{\circ}$ to
-$176^{\circ}$.
-% 
-We also found that since the onset of the response till an
-energy for the incoming beam of 0.118\,eV the components of both,
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
-have no change in the spin polarization direction. Finally, after this energy
-value both goes to zero.
+Quadrant. In a different way than in the
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case only the polar angle is hold
+for the peak of the response having a deviation of $\pm 2^{\circ}$ since the
+onset to a energy value of 0.106\,eV but the azimuthal angle changes since the
+onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.
+% 
+We also found that since the onset of the response till an energy for the
+incoming beam of 0.118\,eV the components of both,
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ have no change in the spin
+polarization direction. Finally, after this energy value both goes to zero.
 % %%%%%%%%%%%%%%%%%
@@
 in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
-are obtained for the \emph{up} structure.
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are obtained for the \emph{up}
+structure.
 % 
@@
 \ref{fig:up-vy-comp-rtp-2} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
-related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
-for which the response is maximized for the \emph{up} structure. In the same
-figures and frames we present in dashed lines the corresponding polar
-($\theta_{\mathrm{x}}(\omega)$ and $\theta_{\mathrm{y}}(\omega)$) and azimuthal
-($\varphi_{\mathrm{x}}(\omega)$ and $\varphi_{\mathrm{y}}(\omega)$) angles
-related to the right scale. In the bottom frames of same figures we present the
-decomposition of the responses in the three corresponding components
-$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$. 
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
+the polarization angle to $\alpha=40^{\circ}$ for which the response is
+maximized for the \emph{up} structure. In the same figures and frames we present
+in dashed lines the corresponding polar ($\theta_{\mathrm{x}}(\omega,\alpha)$
+and $\theta_{\mathrm{y}}(\omega,\alpha)$) and azimuthal
+($\varphi_{\mathrm{x}}(\omega,\alpha)$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale. In the
+bottom frames of same figures we present the decomposition of the responses in
+the three corresponding components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
 % 
@@
 an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
-in a value of $|\mathcal{V}^{\mathrm{x}}(\omega)|= 6.6$\,Km/s along the $x$
-direction  with polar and azimuthal spin polarization angles
-$\theta_{\mathrm{x}}(\omega)= 42^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega)=59^{\circ}$ having fluctuations but being directed
-over the first Cartesian Quadrant of the $xy$ plane.
+in a value of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the
+$x$ direction  with polar and azimuthal spin polarization angles
+$\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ having fluctuations but being
+directed over the first Cartesian Quadrant of the $xy$ plane.
 % 
 For the spin moving along the $y$ direction we have a value of
-$|\mathcal{V}^{\mathrm{y}}(\omega)|=28.7$\,Km/s with polar and azimuthal angles
-$\theta_{\mathrm{y}}(\omega)=45^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega)=56^{\circ}$ having variations of $\pm5^{\circ}$
-for energy variations of $\pm0.01$\,eV and being directed over the fir Cartesian
-Quadrant of the $xy$ plane.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=28.7$\,Km/s with polar and azimuthal
+angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ having variations of
+$\pm5^{\circ}$ for energy variations of $\pm0.01$\,eV and being directed over
+the fir Cartesian Quadrant of the $xy$ plane.
 % 
@@
 contributions and resulting in values of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|=9.9$\,Km/s and spin polarization angles
-$\theta_{\mathrm{x}}(\omega)=129^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega)=229^{\circ}$ being almost constant in the width of
-the peak having variations of $\pm1^{\circ}$ for variations in energy of
-$\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=9.9$\,Km/s and spin polarization
+angles $\theta_{\mathrm{x}}(\omega,\alpha)=129^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being almost constant in the
+width of the peak having variations of $\pm1^{\circ}$ for variations in energy
+of $\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the
 $xy$ plane.
@@
 For the spin moving in the $y$ direction we have a value of
-$|\mathcal{V}^{\mathrm{y}}(\omega)|=49.4$\,Km/s with spin polarization angles
-$\theta_{\mathrm{y}}(\omega)=127^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega)=227^{\circ}$ being almost constant with variations
-of $\pm1^{\circ}$ for variations in energy of $\pm1$\,eV and being directed
-downward the third Cartesian Quadrant of the $xy$ plane.
-% 
-Finally we have that for bot energies $|\mathcal{V}^{\mathrm{y}}(\omega)|$ is
-more intense than $|\mathcal{V}^{\mathrm{x}}(\omega)|$ being 4.4 times more
-intense for 1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the
-components of the responses keep the spin polarization positive till an energy
-of the incoming beam equal to 1.954\,eV when the spin polarization changes the
-direction and after an energy for the incoming beam equal to 2.05\,eV both
-responses goes to zero.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=49.4$\,Km/s with spin polarization
+angles $\theta_{\mathrm{y}}(\omega,\alpha)=127^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being almost constant with
+variations of $\pm1^{\circ}$ for variations in energy of $\pm1$\,eV and being
+directed downward the third Cartesian Quadrant of the $xy$ plane.
+% 
+Finally we have that for bot energies
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is more intense than
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ being 4.4 times more intense for
+1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the components of
+the responses keep the spin polarization positive till an energy of the incoming
+beam equal to 1.954\,eV when the spin polarization changes the direction and
+after an energy for the incoming beam equal to 2.05\,eV both responses goes to
+zero.
 
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
-    polarization angle for the \emph{alt} structure. The absolute maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy range from
-    0.90\,eV to 0.93\,eV and for polarization angles from 120$^{\circ}$ to
-    150$^{\circ}$.}
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
+    energy vs. polarization angle for the \emph{alt} structure. The absolute
+    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
+    range from 0.90\,eV to 0.93\,eV and for polarization angles from
+    120$^{\circ}$ to 150$^{\circ}$.}
     \label{fig:alt-3d-vva}
@@
     \caption{Most intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
-    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
-    frames right scale), and the corresponding three components (bottom frames)
-    for the \emph{alt} structure fixing the polarization angle to
-    $\alpha=145^{\circ}$ to maximize the response.}
+    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
+    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
+    angles (top frames right scale), and the corresponding three components
+    (bottom frames) for the \emph{alt} structure fixing the polarization angle
+    to $\alpha=145^{\circ}$ to maximize the response.}
     \label{fig:alt-vab-comp-rtp}
@@
 1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
-and the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega)|$. In Fig. \ref{fig:alt-3d-vva} we present
-the $|\mathcal{V}^{\mathrm{a}}(\omega)|$ spectra resulting from evaluate again
-Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
-\eqref{eq:vab} but now for the \emph{alt} structure. We can see that the onset
-of the response is when the energy of the incoming light is the same of the gap
-energy.
+and the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$
+and $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. In Fig. \ref{fig:alt-3d-vva} we
+present the $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ spectra resulting from
+evaluate again Eq. \eqref{eq:vv-mag} using different polarization angles
+$\alpha$ in Eq. \eqref{eq:vab} but now for the \emph{alt} structure. We can see
+that the onset of the response is when the energy of the incoming light is the
+same of the gap energy.
 %
@@
 150$^{\circ}$ is the zone where the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$ is
-held. We also found that the first peak is obtained when the energy of the
-incoming beam is 0.720\,eV and  the absolute maximum of the response is obtained
-when for 0.912\,eV, both for a polarization angle $\alpha = 145^{\circ}$.
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is held. We also found that the
+first peak is obtained when the energy of the incoming beam is 0.720\,eV and
+the absolute maximum of the response is obtained when for 0.912\,eV, both for a
+polarization angle $\alpha = 145^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 \ref{fig:alt-vy-comp-rtp} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
-related to the left scale, fixing the polarization angle to $\alpha=145^{\circ}$
-for which the response is maximized for the \emph{alt} structure. In the same
-figures and frames we present ind dashed lines the spin polarization angles
-related to the right scale and in the bottom frames the corresponding three
-components.
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
+the polarization angle to $\alpha=145^{\circ}$ for which the response is
+maximized for the \emph{alt} structure. In the same figures and frames we
+present ind dashed lines the spin polarization angles related to the right scale
+and in the bottom frames the corresponding three components.
 % 
@@
 the components resulting in a response of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|=19.4$\,Km/s and polar and azimuthal spin
-polarization angles $\theta_{\mathrm{x}}(\omega)=46^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega)=41^{\circ}$ having variations in the range of the
-peak but being directed over the first Cartesian Quadrant of the $xy$ plane;
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar and azimuthal
+spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha)=46^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha)=41^{\circ}$ having variations in the range
+of the peak but being directed over the first Cartesian Quadrant of the $xy$
+plane;
 % 
 for an energy of 0.912\,eV we have a major contribution from the
-$\mathcal{V}^{\mathrm{xz}}(\omega)$ component resulting in a total response of
-$|\mathcal{V}^{\mathrm{x}}(\omega)|=30.9$\,Km/s and angles
-$\theta_{\mathrm{x}}(\omega)=154^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega)=290^{\circ}$ having variations of $\pm3^{\circ}$
-in for energy variations of $\pm1$\,eV and being directed downward the fourth
-Cartesian Quadrant of the $xy$ plane.
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component resulting in a total
+response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and angles
+$\theta_{\mathrm{x}}(\omega,\alpha)=154^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ having variations of
+$\pm3^{\circ}$ in for energy variations of $\pm1$\,eV and being directed
+downward the fourth Cartesian Quadrant of the $xy$ plane.
 % 
@@
 \ref{fig:alt-vy-comp-rtp}, we found that when the energy of the incoming beam is
-0.720\,eV we have more contribution from the $\mathcal{V}^{\mathrm{yz}}(\omega)$
-component resulting in a response of
-$|\mathcal{V}^{\mathrm{y}}(\omega)|=51.9$\,Km/s and angles
-$\theta_{\mathrm{y}}(\omega)=141^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega)=222^{\circ}$ being the first constant and the
-second having variations of $\pm3^{\circ}$ for energy variations of $\pm0.3$\,eV
-and being directed downward the third Cartesian Quadrant of the $xy$ plane.
+0.720\,eV we have more contribution from the
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component resulting in a response of
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=51.9$\,Km/s and angles
+$\theta_{\mathrm{y}}(\omega,\alpha)=141^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=222^{\circ}$ being the first constant and
+the second having variations of $\pm3^{\circ}$ for energy variations of
+$\pm0.3$\,eV and being directed downward the third Cartesian Quadrant of the
+$xy$ plane.
 % 
@@
 the components resulting in a response
-$|\mathcal{V}^{\mathrm{y}}(\omega)|=52.3$\,Km/s being this the absolute maximum
-response for the \emph{alt} structure. The corresponding angles are
-$\theta_{\mathrm{y}}(\omega)=129^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega)=229^{\circ}$ being both constant for the energy
-range of the peak and being directed downward the third Cartesian Quadrant of
-the $xy$ plane.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=52.3$\,Km/s being this the absolute
+maximum response for the \emph{alt} structure. The corresponding angles are
+$\theta_{\mathrm{y}}(\omega,\alpha)=129^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=229^{\circ}$ being both constant for the
+energy range of the peak and being directed downward the third Cartesian
+Quadrant of the $xy$ plane.
 % 

### 2017-05-18 mu/article/article.tex
Changing subfigures.

@@
     \centering
-    \subfigure[\ $xz$ plane view]
-    {\includegraphics[width=\linewidth]{figures/altstruc2}}
+    \includegraphics[width=\linewidth]{figures/altstruc2}
     \label{fig:alt-struc-xz}
     \\
-    \subfigure[\ $xy$ plane view]
-    {\includegraphics[width=\linewidth]{figures/altstruc1}}
+    \includegraphics[width=\linewidth]{figures/altstruc1}
     \label{fig:alt-struc-xy}
@@
     \centering
-    \subfigure[\ $xz$ plane view]
-    {\includegraphics[width=\linewidth]{figures/upstruc2}}
+    \includegraphics[width=\linewidth]{figures/upstruc2}
     \label{fig:up-struc-xz}
     \\
-    \subfigure[\ $xy$ plane view]
-    {\includegraphics[width=\linewidth]{figures/upstruc1}}
+    \includegraphics[width=\linewidth]{figures/upstruc1}
     \label{fig:up-struc-xy}
@@
 
-{\Large  We calculated the $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$} response In figure
-\ref{fig:vab-str-comp} we present a comparison of the most intense responses
-resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and \emph{up}
-2D structures and CdSe and GaAs bulk systems. As we can see from this figure the
-most intense response corresponds to the \emph{up} structure centered at
+Using the Eq. \eqref{eq:vab}, we calculated the
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{alt} and
+\emph{up} 2D structures and for the CdSe and GaAs bulk systems and the results
+are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
+the response of each structure is that for which the response is maximized in
+each case.
+% 
+From the figure we have that the onset of the response starts when the energy of
+the incoming beam is the same of the gap energy.
+% 
+The most intense response corresponds to the \emph{up} structure centered at
 0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
@@
     \centering
-    \subfigure[\ \label{fig:up-3d-vsz-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
-    \\
-    \subfigure[\ \label{fig:up-3d-vsz-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}
+    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
+    \label{fig:up-3d-vsz-1}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}
+    \label{fig:up-3d-vsz-2}
 
@@
     \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV and the local maximum from
-    1.95\,eV to 2.0\,eV and both for polarization angles between $25^{\circ}$
-    and $50^{\circ}$.}
+    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared, and the
+    local maximum from 1.95\,eV to 2.0\,eV, in the visible, both for
+    polarization angles between $25^{\circ}$ and $50^{\circ}$.}
     \label{fig:up-3d-vsz}   
@@
     \centering
-    \subfigure[\, \label{fig:up-vaz-rag-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
-    \\
-    \subfigure[\, \label{fig:up-vaz-rag-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}
+    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
+     \label{fig:up-vaz-rag-1}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
+     \label{fig:up-vaz-rag-2}
 
@@
 evaluate Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
-Eq. \eqref{eq:vab}. From the figure we have that the onset of the response
-starts when the energy of the incoming beam is the same of the gap energy.
+Eq. \eqref{eq:vab}.
 % 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for \emph{up}
-    structure
-    \label{fig:up-3d-vvx-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ for \emph{up}
-    structure
-    \label{fig:up-3d-vvy-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
+    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
+    \label{fig:up-3d-vvx-1}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
+    \label{fig:up-3d-vvy-1}
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ 
-    \label{fig:up-vx-comp-rtp-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ 
-    \label{fig:up-vy-comp-rtp-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
+    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
+    \label{fig:up-vx-comp-rtp-1}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
+    \label{fig:up-vy-comp-rtp-1}
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vvx-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
-    \label{fig:up-3d-vvy-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
-
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon energy vs.
-    polarization angle for the \emph{up} structure. The local maxima of both
-    responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy range from
-    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
-    $50^{\circ}$.}
+    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
+    \label{fig:up-3d-vvx-2}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
+    \label{fig:up-3d-vvy-2}
+
+    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
+    energy vs. polarization angle for the \emph{up} structure. The local maxima
+    of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
+    range from 1.95\,eV to 2.00\,eV and for polarization angles from
+    $25^{\circ}$ to $50^{\circ}$.}
     \label{fig:up-3d-vva-2}
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
+    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
+    \label{fig:up-vx-comp-rtp-2}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
+    \label{fig:up-vy-comp-rtp-2}
 
@@
     $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs. (a) and
-    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
-    frames right scale), and the corresponding three components (bottom frames)
-    for the \emph{up} structure fixing the polarization angle to
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
+    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
+    angles (top frames right scale), and the corresponding three components
+    (bottom frames) for the \emph{up} structure fixing the polarization angle to
     $\alpha=40^{\circ}$ to maximize the response.}
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vvx}]
-    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{alt} structure 
-    \label{fig:alt-3d-vvy}]
-    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
+    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
+    \label{fig:alt-3d-vvx}
+    \\
+    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
+    \label{fig:alt-3d-vvy}
 
@@
     \centering
-    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:alt-vx-comp-rtp}]
-    {\includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}}
-    \\
-    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:alt-vy-comp-rtp}]
-    {\includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}}
+    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
+    \label{fig:alt-vx-comp-rtp}
+    \\
+    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
+    \label{fig:alt-vy-comp-rtp}
 
@@
     \centering
-    \subfigure[\ \label{fig:up-vyz-lay-1}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
-    \\
-    \subfigure[\ \label{fig:up-vyz-lay-2}]
-    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
+    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}
+    \label{fig:up-vyz-lay-1}
+    \\
+    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}
+    \label{fig:up-vyz-lay-2}
 

### 2017-05-18 mu/article/article.tex
Changing working station.

@@
 
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
     as a function of the photon energy and polarization angle $\alpha$ for the
     \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared, and the
-    local maximum from 1.95\,eV to 2.0\,eV, in the visible, both for
-    polarization angles between $25^{\circ}$ and $50^{\circ}$.}
+    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
+    range, and two local maxima from 1.90\,eV to 1.93\,eV and  1.96\,eV to
+    2.0\,eV, in the visible, all for polarization angles between $25^{\circ}$
+    and $50^{\circ}$.}
     \label{fig:up-3d-vsz}   
@@
     \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
-    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
-    structure. The absolute maximum is located for an energy range from 0.90\,eV
-    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
-    $150^{\circ}$.}
+    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
+    as a function of the photon energy and polarization angle $\alpha$  for the
+    \emph{alt} structure. A local maximum and the absolute maximum are located
+    for the energy ranges from 0.67\,eV to 0.73\,eV and 0.90\,eV to 0.93\,eV and
+    both for polarization angles between $120^{\circ}$ and $150^{\circ}$.}
     \label{fig:alt-3d-vsb}
@@
 evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
-polarization angle $\alpha$ for the \emph{alt} structure.
+energy and polarization angle $\alpha$ of the incoming beam for the \emph{alt}
+structure.
 % 
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
-    energy vs. polarization angle for the \emph{up} structure. The absolute
-    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
-    range from 0.08\,eV to 0.10\,eV and for polarization angles from
+    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
+    photon energy and polarization angle $alpha$ for the \emph{up} structure.
+    The absolute maxima of both are localized in the energy range from 0.08\,eV
+    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
     $25^{\circ}$ to $50^{\circ}$.}

### 2017-05-19 mu/article/article.tex
Changing working station

@@
     for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
-    range, and two local maxima from 1.90\,eV to 1.93\,eV and  1.96\,eV to
-    2.0\,eV, in the visible, all for polarization angles between $25^{\circ}$
+    range, and two local maxima from 1.90\,eV to 1.93\,eV and from 1.96\,eV to
+    2.0\,eV, in the visible radiation range, all for polarization angles between $25^{\circ}$
     and $50^{\circ}$.}
@@
     as a function of the photon energy and polarization angle $\alpha$  for the
-    \emph{alt} structure. A local maximum and the absolute maximum are located
-    for the energy ranges from 0.67\,eV to 0.73\,eV and 0.90\,eV to 0.93\,eV and
-    both for polarization angles between $120^{\circ}$ and $150^{\circ}$.}
+    \emph{alt} structure. The local and the absolute maxima are located in the
+    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
+    respectively, and both in the Near Infrared and for polarization angles
+    between $120^{\circ}$ and $150^{\circ}$.}
     \label{fig:alt-3d-vsb}
@@
     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
-    photon energy and polarization angle $alpha$ for the \emph{up} structure.
+    photon energy and polarization angle $\alpha$ for the \emph{up} structure.
     The absolute maxima of both are localized in the energy range from 0.08\,eV
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
-    energy vs. polarization angle for the \emph{up} structure. The local maxima
-    of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
-    range from 1.95\,eV to 2.00\,eV and for polarization angles from
-    $25^{\circ}$ to $50^{\circ}$.}
+    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
+    the photon energy and polarization angle $\alpha$ for the \emph{up}
+    structure. Two local maxima of both responses are localized in the energy
+    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the visible
+    radiation range, and for polarization angles between $25^{\circ}$ and
+    $50^{\circ}$.}
     \label{fig:up-3d-vva-2}
@@
 
-    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
-    energy vs. polarization angle for the \emph{alt} structure. The absolute
-    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
-    range from 0.90\,eV to 0.93\,eV and for polarization angles from
-    120$^{\circ}$ to 150$^{\circ}$.}
+    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
+    the photon energy and polarization angle $\alpha$ for the \emph{alt}
+    structure. The local and the absolute maxima are located in the
+    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
+    respectively, and both in the Near Infrared and for polarization angles
+    between $120^{\circ}$ and $150^{\circ}$.}
     \label{fig:alt-3d-vva}

### 2017-05-19 mu/article/article.tex
Changing working station

@@
 \subsection{Fixing spin}\label{sec:theory-fixspin}
-Considering that we have 2D structures we can fix the spin direction along the
-$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
-spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ in a fixed angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ as
+Considering that we have 2D structures, one of the options is fix the spin along
+the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
+velocity with spin polarization along the $\mathrm{b}$ direction as 
 \begin{align}
@@
 \label{eq:vs-mag}
-\\
+\end{align}
+and the angle at which the spin velocity is directed as
+\begin{align}
 \gamma_{\mathrm{b}} (\omega,\alpha)
@@
 where the angle is measured in the counter-clockwise direction from the positive
-$x$ axis.
+$x$ Cartesian coordinate.
 
@@
 
-In a similar way we can fix the velocity in the $xy$ plane
-along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ as
+In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
+Cartesian coordinate and then define the magnitude of the spin velocity directed
+along the $\mathrm{a}$ direction as
 \begin{align}
@@
 [\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
-[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
+[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
 },
@@
 \end{align}
-and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
+Then, the spin direction depends of the components of the previous equation and
+so we define the spin polar and azimuthal angles as
 \begin{align}
@@
 \end{align}
+where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
+negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
+measured on the $xy$ plane in the counter-clockwise direction from the positive
+$x$ Cartesian coordinate.
 
@@
 % 
-It is known that using DFT-LDA to calculate the electronic structure of
-materials predict a different band gap than the obtained experimentally. A
-correction for the band gap energy value can be calculated by other 
-\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
-is outside the scope of this paper.
-% 
 The convergence parameters for the calculations of our results corresponding to
 the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
-40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
-using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
-Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
-respectively for the \emph{alt} and \emph{up} structures.
+40\,Ha, respectively. The energy eigenvalues and matrix elements for the
+\emph{up} ad \emph{alt} structures were calculated using 14452 $\mathbf{k}$
+points and 8452 $\mathbf{k}$ points in the irreducible Brillouin zone (IBZ)
+presenting LDA energy band gaps of 0.72\,eV and 0.088\,eV, respectively.
+% 
+We notice that within DFT, the LDA is only one of other possible methods that
+can be used to determine the electronic structure of materials. Recent
+investigations on graphene show some of the differences in calculated values
+from several of these methods\cite{karamanisJPCC15,botelloACR14}. We note that
+the LDA is as good as these other approaches. It is also known that the DFT
+calculations predict a band gap for the material that differs from experiment.
+This can be corrected using other \emph{ab initio} techniques, such as the GW
+approximation\cite{onidaRMP02}, but this calculation has a very high
+computational cost and is out of the scope in this paper. Even so, DFT still
+remains as an effective and useful tool for computing diverse properties derived
+from the electronic band structure.
 

### 2017-05-23 mu/article/article.tex
ChWS

@@
     \includegraphics[width=\linewidth]{figures/altstruc2}
-    \label{fig:alt-struc-xz}
     \\
     \includegraphics[width=\linewidth]{figures/altstruc1}
-    \label{fig:alt-struc-xy}
     \caption{Alt structure.}
@@
     \includegraphics[width=\linewidth]{figures/upstruc2}
-    \label{fig:up-struc-xz}
     \\
     \includegraphics[width=\linewidth]{figures/upstruc1}
-    \label{fig:up-struc-xy}
     \caption{Up structure}
@@
 
-The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
-direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
-\begin{equation}
-\dot{K}(\omega) = \mu^{\mathrm{abcd}}(\omega)
+The spin density injection current $\dot{K}^{\mathrm{ab}}$ can be written in
+terms of a material response pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as
+% with speed along direction $\mathrm{a}$ and spin
+% polarization along $\mathrm{b}$ is defined as
+\begin{equation*}
+\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
 E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
 \label{eq:dotk}
-\end{equation}
-where
+\end{equation*}
+where the roman superscripts denote Cartesian components corresponding
+$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
+polarization direction and the pseudotensor can be written as
 \begin{widetext}
@@
 \frac{\pi e^{2}}{\hbar^{2}} \int 
-\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
-\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
+\frac{d^{3}K}{8 \pi^{3}}
+\sum_{vcc'}^{'}
+\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} 
+\left( 
 r^{\mathrm{c}}_{vc'} 
 r^{\mathrm{d}}_{cv } +
-r^{\mathrm{d}}_{vc'} 
-r^{\mathrm{c}}_{cv } ) \right]
+(c \leftrightarrow d)
+\right) 
+\right]
 \delta(\omega-\omega_{cv})
 \label{eq:mu}
-\\
-K^{\mathrm{ab}}_{mn}
-&=
-\sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
-\label{eq:velspi-matelem}
+% \\
+% K^{\mathrm{ab}}_{mn}
+% &=
+% \sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
+% \label{eq:velspi-matelem}
 \end{align}
 \end{widetext}
-is the corresponding spin density injection current pseudotensor. The $'$
-in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
-covers these states.
-
-Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
-which the spin polarized in the $\mathrm{b}$   direction moves along the
-$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
-polarization angle $\alpha$. Then,
+where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
+\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
+the spin current matrix elements that, using time reversal invariance,
+$K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k}) $. The $'$ in
+the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
+covers these states and since $mu$ is real we have that
+$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
+
+Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
+the speed at which the spin polarized in the $\mathrm{b}$   direction moves
+along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
+plane with a polarization angle $\alpha$. Then,
 \begin{widetext}
@@
 {\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
-\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
+\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
 \label{eq:vab}
@@
 \end{widetext}
-
+where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
+components\cite{arzatePRB14}.
+% 
 For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
@@
 \end{align}
-and the angle at which the spin velocity is directed as
+and the angle at which the spin velocity is directed on the $xy$ plane as
 \begin{align}
@@
 where the angle is measured in the counter-clockwise direction from the positive
-$x$ Cartesian coordinate.
+$x$ Cartesian coordinate. We also define two special angles
+\begin{align}
+\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
+\label{eq:gammapar} 
+\\
+\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
+\label{eq:gammaperp}
+\end{align}
+The first corresponds to the case when the spin velocity is directed, on the
+$xy$ plane in the same direction of the polarization angle of the incoming beam;
+the second one corresponds to the case when the spin velocity is directed
+perpendicularly respect to the polarization angle of the incoming beam.
 
@@
 Then, the spin direction depends of the components of the previous equation and
-so we define the spin polar and azimuthal angles as
+so we define the spin orientation polar and azimuthal angles as
 \begin{align}
@@
 % 
+A negative quantity in the spin velocity means a change in the spin polarization traveling in the opposite direction.
+% 
 In table \ref{tab:vab-str-comp} we present the comparison of this values for the
@@
     \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
-    \label{fig:up-3d-vsz-1}
     \\
     \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}
-    \label{fig:up-3d-vsz-2}
 
@@
     range, and two local maxima from 1.90\,eV to 1.93\,eV and from 1.96\,eV to
-    2.0\,eV, in the visible radiation range, all for polarization angles between $25^{\circ}$
-    and $50^{\circ}$.}
+    2.0\,eV, in the visible radiation range, all for polarization angles between
+    $25^{\circ}$ and $50^{\circ}$.}
     \label{fig:up-3d-vsz}   
@@
     \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
-     \label{fig:up-vaz-rag-1}
     \\
     \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
-     \label{fig:up-vaz-rag-2}
 
@@
 
-We first analyzed two energy ranges for the \emph{up} structure, the first for
-an incoming energy beam from 0.0\,eV to 0.2\,eV which inlude the THz and the Mid
-Infrared (MIR) range, where the absolute maximum of the
+The most interesting case is that for which the spin is perpendicular to the
+surface corresponding to $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$.
+% 
+For this case we first analyzed two energy ranges for the \emph{up} structure,
+the first for an incoming energy beam from 0.0\,eV to 0.2\,eV which include the
+THz and the Mid Infrared (MIR) range, where the absolute maximum of the
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained and
@@
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
-evaluate Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
-Eq. \eqref{eq:vab}.
+evaluate Eq. \eqref{eq:vs-mag}.
 % 
@@
 % %%%%%%%%%%%%%%%%%
-In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we
+In the top frames of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we
 present in solid lines the result of evaluate
@@
 for which value the response is maximized for the \emph{up} structure. In the
-same figures and frames we present in dashed lines, related to the right scale,
+same panels and frames we present in dashed lines, related to the right scale,
 the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ obtained
-from the evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of
-those figures the corresponding components
+from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the
+panels we present the corresponding components
 $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
@@
 square boxes indicating the values where the angles of the spin velocity are
-parallel and perpendicular and the arrows are directed to the value of the
-response corresponding to those angles.
-% 
-From Figs. \ref{fig:up-3d-vsz-1} and \ref{fig:up-vaz-rag-1} we have that the
-absolute maximum response for the \emph{up} structure is obtained for an
-incoming beam with energy of 0.088\,eV and polarization angle
+parallel (Eq. \ref{eq:gammapar}) and perpendicular (Eq. \ref{eq:gammaperp}) and
+the arrows are directed to the value of the response corresponding to those
+angles.
+% 
+From top panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we have
+that the absolute maximum response for the \emph{up} structure is obtained for
+an incoming beam with energy of 0.088\,eV and polarization angle
 $\alpha=40^{\circ}$ resulting in a value of
@@
 % 
-In the same figure the green circled box indicates the value for which the
-polarization angle $\alpha$ and the response direction angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ are collinear being both angle
-$65.5^{\circ}$ and resulting in a value of the response of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=82.3$\,Km/s indicated by the
-upward green arrow.
+From the top panel of Fig. \ref{fig:up-vaz-rag} we have that the velocity angle
+is almost constant for all the polarization angle range having values of
+$\gamma_{\mathrm{z}}(\omega,\alpha) = 65.5^{\circ} \pm 0.5^{\circ}$. In this
+panel the green circled box indicates the value for which the polarization angle
+and the response direction angle are collinear (Eq. \ref{eq:gammapar}) being
+$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in a
+value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+82.3$\,Km/s indicated by the upward green arrow.
 % 
@@
 and the response angle are perpendicular being $\alpha=155.5^{\circ}$ and
-$\gamma_{\mathrm{x}}(\omega,\alpha)=65.5^{\circ}$; for this angles the response
-has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=24.8$\,Km/s
-indicated by the blue downward arrow.
-% 
-The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
-then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega,\alpha)$
-the complete range of $\alpha$ angle is included because this last is almost
-constant.
-% 
-Now from Figs. \ref{fig:up-3d-vsz-2} and \ref{fig:up-vaz-rag-2} we have that a
-local maxima of the response is obtained for an incoming beam with energy of
-0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
-of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
-from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
-component being directed in a velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first Cartesian Quadrant
-of the $xy$ plane, for the spin polarized in the $z$ direction.
-% 
-Again the green circled box indicates the value for which the polarization angle
-$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega,\alpha)$
-are collinear being both $78.5^{\circ}$ and having a response value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=23.5$\,Km/s indicated with
-the green upward arrow. We found that for variations in the response angle of
-$\pm 2^{\circ}$, indicated with the error bars, corresponds a range in the
-polarization angle of $0^{\circ} \leq \alpha \leq 122^{\circ}$ having then a
-large range for which the direction of the response is directed to this angle.
-% 
-The blue square box indicates the value for which the polarization angle and the
-response angle are perpendicular being $\alpha=168.5^{\circ}$
-$\gamma_{\mathrm{z}}(\omega,\alpha)=78.5^{\circ}$ and having a response
+$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$; for this angle the
+response has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+24.8$\,Km/s indicated by the blue downward arrow.
+% 
+Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we
+have that a local maximum of the response is obtained for an incoming beam with
+energy of 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in
+a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This
+comes from a major contribution of the
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component being directed in a
+velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first
+Cartesian Quadrant on the $xy$ plane, for the spin polarized in the $z$
+direction.
+% 
+Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found that the
+velocity angle is almost constant at $78^{\circ}$ and has variations of
+$1^{\circ}$ for polarization angles between $0^{\circ}$ and $100^{\circ}$. In
+this range the green circled box indicates the value for which the polarization
+angle and the response direction angle are collinear corresponding to
+$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ and having a
+response value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+23.5$\,Km/s indicated with the green upward arrow.
+% 
+Finally, the blue square box indicates the value for which the polarization
+angle and the response angle are perpendicular being $\alpha=168.5^{\circ}$
+$\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 78.5^{\circ}$ and having a response
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=9.0$\,Km/s indicated with
-the blue upward arrow. Again, for variations in the response angle of
-$\pm2^{\circ}$, indicated with the error bars, corresponds a range in the
-polarization angle of $155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a
-large range for which the direction of the response is held.
-% 
-The most interesting case in which the spin is perpendicular to the surface of
-the structure and also for the \emph{up} structure the most intense was the
-presented before for which the spin is polarized in the $\mathrm{z}$ direction.
+the blue upward arrow.
+% 
 We also made the analysis for the cases when the spin polarization is directed
-in the $\mathrm{x}$ and $\mathrm{y}$ direction but we do not present the
-corresponding plots. For those cases we have that the absolute maxima response
-is obtained for an energy of the incoming beam equal to 0.088\,eV and
-polarization angle $\alpha=40^{\circ}$ resulting in values of
+along the $\mathrm{x}$ and $\mathrm{y}$ Cartesian coordinates but we do not
+present here the corresponding plots. For those cases we have that the absolute
+maxima responses are obtained for an energy of the incoming beam equal to
+0.088\,eV and polarization angle $\alpha=40^{\circ}$ resulting in values of
 $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
@@
 In Fig. \ref{fig:alt-3d-vsb} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
-evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
-energy and polarization angle $\alpha$ of the incoming beam for the \emph{alt}
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra for the \emph{alt}
 structure.
 % 
-From this figure we found that the zone where the absolute maximum response is
-held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
-angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
-is obtained for the same polarization angles but for energies between 0.67\,eV
-and 0.75\,eV.
+% From this figure we found that the zone where the absolute maximum response is
+% held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
+% angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
+% is obtained for the same polarization angles but for energies between 0.67\,eV
+% and 0.75\,eV.
 % %%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%
-In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
-result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related
-to the left scale, fixing the energy of the incoming beam to 0.912\,eV for which
-value the response is maximized for the \emph{alt} structure. In the same figure
-and frame we present with dashed line, related to the right scale, the velocity
-angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ and in the bottom frame the
-corresponding $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components. Again, the circled and
-square boxes indicate the values for which the polarization angle and the
-velocity angle are parallel and perpendicular and with arrows are indicated the
-corresponding response value.
-% 
-From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
-maximum response for the \emph{alt} structure is obtained for an incoming beam
-with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43.0$\,Km/s and for the spin
+% 
+From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have that the
+absolute maximum response is obtained for an incoming beam with polarization
+angle $\alpha=145^{\circ}$ reaching a velocity of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
 polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
 $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
-of the $xy$ plane. The circled box for the collinear angle corresponds for
-angles $\alpha$ and $\gamma_{\mathrm{z}}(\omega,\alpha)$ equal to $53.5^{\circ}$
-with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=12.7$\,Km/s,
-and the blue square box indicates the perpendicular angles for values
-$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ with a
-value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s. Finally
-we found that for variations of $\pm0.5^{\circ}$ of those collinear and
-perpendicular angles, presented with the error bars on the boxes, correspond
-ranges for the polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and
-$95^{\circ} \leq \alpha \leq 175^{\circ}$ covering a wide range of angles
-because the response angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ has small
-variations for the complete range of the polarization angle $\alpha$.
+of the $xy$ plane.
+% 
+Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
+velocity angle has small variations being centered at $51.5^{\circ}$ and having
+variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
+\alpha \leq 180^{\circ}$.
+% 
+Again the circled box indicates the collinear angle (Eq.
+\eqref{eq:gammapar}) corresponding to
+$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 53.5^{\circ}$ corresponding a
+value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the
+blue square box indicates the perpendicular angles corresponding values
+$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
+with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.
 % 
@@
     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
-    \label{fig:up-3d-vvx-1}
     \\
     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
-    \label{fig:up-3d-vvy-1}
 
@@
     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
-    \label{fig:up-vx-comp-rtp-1}
     \\
     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
-    \label{fig:up-vy-comp-rtp-1}
 
@@
 % %%%%%%%%%%%%%%%%%
-For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
-0.16\,eV, where we found the most intense response and the absolute maxima for
+In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ presented in Fig.
-% 
-\ref{fig:up-3d-vva-1} and resulting from evaluate Eq. \eqref{eq:vv-mag} as a
-function of the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ resulting from evaluate the Eq.
+\eqref{eq:vv-mag} in the energy range from 0.00\,eV to 0.16\,eV for the
 \emph{up} structure.
 %
-From this picture we can see that for the zone between the energy range of
+From this figure we can see that for the zone between the energy range of
 0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
@@
 
-In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
-% 
-\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$,
-related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
-for which the response is maximized. In the same
-figures and frames we present in dashed lines the corresponding polar
-$\theta_{a}(\omega,\alpha)$ and azimuthal $\varphi_{a}(\omega,\alpha)$ angles related to the
-right scale. Also, in the bottom frames of those figures we present the
-decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ in the corresponding
-$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and $\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
-components.
+In the top frames of top and bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we
+present in solid lines the results of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
+the polarization angle to $\alpha=40^{\circ}$ for which the response is
+maximized. In the same panels and frames we present in dashed lines the
+corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
+$\varphi_{a}(\omega,\alpha)$ spin angles related to the right scale. Also, in
+the bottom frames we present the corresponding components
+$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and
+$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
 \begin{figure}[t]
@@
 % %%%%%%%%%%%%%%%%%
-From Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with
-energy of 0.088\,eV the three components have similar contributions and with
-values of 
+From the top panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that for an
+incoming bean of energy 0.088\,eV the three components have similar
+contributions with values of
 % 
@@
 $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)=-23.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)= 39.8$\,Km/s 
-% 
-resulting in a value of
-% 
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s 
-% 
-being this value the absolute maximum obtained when the spin-velocity is fixed
-in the $x$ direction. To this value corresponds a polar and azimuthal angles of
-$\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)= 39.8$\,Km/s resulting in a response
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s being this value the
+absolute maximum obtained when the spin-velocity is fixed in the $x$ direction.
+% 
+To this value corresponds the polar and azimuthal spin
+angles of $\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
 $\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upper
 the third Cartesian Quadrant of the $xy$ plane. Also from this figure we have
-that those angle values are hold for almost all the peak of the response having
-a deviation of $\pm 2^{\circ}$ in the range of energies from 0.028\,eV to
-0.098\,eV from the corresponding to the absolute maximum mentioned before.
-% 
-Now, from Fig. \ref{fig:up-vy-comp-rtp-1} we have that the $\mathrm{yx}$ and
-$\mathrm{yy}$ components have less contributions for the total response than the
-$\mathrm{yz}$ and for the same incoming beam energy have values of
+that those angle values are held for almost all the peak of the response having
+a variation of $\pm 2^{\circ}$.
+% 
+Now, from the bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that the
+$\mathrm{yx}$ and $\mathrm{yy}$ components have less contributions for the total
+response than the $\mathrm{yz}$ and for the same incoming beam energy the components have values of
 % 
@@
 % 
-resulting in a value of the total response of
-% 
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=87.9$\,Km/s
-% 
-being this value the absolute maximum obtained when the spin-velocity is fixed
-in the $y$ direction and being 1.5 times more intense than
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ To this absolute maximum correspond
-spin polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha)=8$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=133$, respectively, being directed almost
-perpendicularly over the $xy$ plane and being localized on the first Cartesian
-Quadrant. In a different way than in the
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case only the polar angle is hold
-for the peak of the response having a deviation of $\pm 2^{\circ}$ since the
-onset to a energy value of 0.106\,eV but the azimuthal angle changes since the
-onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.
+resulting in a response $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=87.9$\,Km/s.
+This value is the absolute maximum obtained when the spin-velocity is fixed in
+the $y$ direction and is 1.5 times more intense than
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$. For this absolute maximum
+corresponds spin polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha)
+= 8^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 133^{\circ}$ being
+directed the spin almost perpendicularly over the $xy$ plane and  localized on
+the first Cartesian Quadrant. 
+% 
+In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case
+only the polar angle is hold for the peak of the response having a deviation of
+$\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but the azimuthal
+angle changes since the onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.
 % 

### 2017-05-23 mu/article/article.tex
Almost finishing the corrections.

@@
     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
-    \label{fig:up-3d-vvx-2}
     \\
     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
-    \label{fig:up-3d-vvy-2}
 
@@
     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
-    \label{fig:up-vx-comp-rtp-2}
     \\
     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
-    \label{fig:up-vy-comp-rtp-2}
 
@@
 In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case
-only the polar angle is hold for the peak of the response having a deviation of
-$\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but the azimuthal
-angle changes since the onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.
+only the polar angle is hold at $8^{\circ}$ for the peak of the response having
+variations of $\pm 2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$
+to $176^{\circ}$ having a value of $133^{\circ}$ for the maximum.
 % 
 We also found that since the onset of the response till an energy for the
-incoming beam of 0.118\,eV the components of both,
+incoming beam of 0.118\,eV the components of both responses,
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ have no change in the spin
-polarization direction. Finally, after this energy value both goes to zero.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, have no change in the spin
+polarization direction. Finally, after this energy value the responses go to
+zero.
 % %%%%%%%%%%%%%%%%%
@@
 Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV, corresponding to the THz and visible radiation, presented
+1.80\,eV to 2.10\,eV, corresponding to visible radiation, presented
 in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
@@
 structure.
-% 
-From this figure we have that for the zone between the energy ranges from
-1.92\,eV to 1.94\,eV and from 1.96\,eV to 1.98\,eV and for polarization angles
-from $30^{\circ}$ to $45^{\circ}$ those two local maxima zones are held.
 % 
@@
 % %%%%%%%%%%%%%%%%
-In the top frames of Figs. \ref{fig:up-vx-comp-rtp-2} and 
-% 
-\ref{fig:up-vy-comp-rtp-2} we present in solid lines the results of
+In the top frames of top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2}
+we present in solid lines the results of
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
@@
 the polarization angle to $\alpha=40^{\circ}$ for which the response is
-maximized for the \emph{up} structure. In the same figures and frames we present
+maximized for the \emph{up} structure. In the same panels and frames we present
 in dashed lines the corresponding polar ($\theta_{\mathrm{x}}(\omega,\alpha)$
@@
 ($\varphi_{\mathrm{x}}(\omega,\alpha)$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale. In the
-bottom frames of same figures we present the decomposition of the responses in
-the three corresponding components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
-% 
-We found that for both cases, the components have similar contributions and for
+$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale and  In
+the bottom frames the corresponding response components.
+% 
+We found that for both cases the components have similar contributions for the corresponding response and for
 an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
@@
 $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ having fluctuations but being
+$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin
 directed over the first Cartesian Quadrant of the $xy$ plane.
@@
 angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ having variations of
-$\pm5^{\circ}$ for energy variations of $\pm0.01$\,eV and being directed over
-the fir Cartesian Quadrant of the $xy$ plane.
+$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ being  the spin directed over
+the first Cartesian Quadrant of the $xy$ plane.
 % 
 Alike, for an incoming energy beam of 1.972\,eV we found the second and more
-intense local maxima with all the components of both responses having similar
-contributions and resulting in values of
+intense local maxima for which all the components have similar contributions for
+the corresponding response resulting in values of
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=9.9$\,Km/s and spin polarization
 angles $\theta_{\mathrm{x}}(\omega,\alpha)=129^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being almost constant in the
-width of the peak having variations of $\pm1^{\circ}$ for variations in energy
-of $\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the
-$xy$ plane.
+$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being the spin directed
+downward the third Cartesian Quadrant of the $xy$ plane.
 % 
@@
 angles $\theta_{\mathrm{y}}(\omega,\alpha)=127^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being almost constant with
-variations of $\pm1^{\circ}$ for variations in energy of $\pm1$\,eV and being
+$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ and the spin being
 directed downward the third Cartesian Quadrant of the $xy$ plane.
 % 
-Finally we have that for bot energies
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is more intense than
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ being 4.4 times more intense for
-1.932\,eV and 5.0 times more intense for 1.972\,eV. Also all the components of
-the responses keep the spin polarization positive till an energy of the incoming
-beam equal to 1.954\,eV when the spin polarization changes the direction and
-after an energy for the incoming beam equal to 2.05\,eV both responses goes to
-zero.
+Also all the components of the responses keep the spin polarization positive
+till an energy of the incoming beam equal to 1.954\,eV when the spin
+polarization ad current changes the direction and after an energy for the
+incoming beam equal to 2.05\,eV both responses goes to zero.
 
@@
     \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
-    \label{fig:alt-3d-vvx}
     \\
     \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
-    \label{fig:alt-3d-vvy}
 
@@
     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
-    \label{fig:alt-vx-comp-rtp}
     \\
     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
-    \label{fig:alt-vy-comp-rtp}
 
@@
 For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
-1.0\,eV, corresponding to the THz radiation, where we found the a local maxima
-and the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$
-and $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. In Fig. \ref{fig:alt-3d-vva} we
-present the $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ spectra resulting from
-evaluate again Eq. \eqref{eq:vv-mag} using different polarization angles
-$\alpha$ in Eq. \eqref{eq:vab} but now for the \emph{alt} structure. We can see
-that the onset of the response is when the energy of the incoming light is the
-same of the gap energy.
-%
-From this picture we can see that for the zone between the energy range of
+1.0\,eV, corresponding to the NIR radiation, where we found a local maxima and
+the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$; the corresponding spectra is
+shown in Fig. \ref{fig:alt-3d-vva}.
+%
+From this figure we can see that for the zone between the energy range of
 0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone where the maximum response for both,
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ is held. We also found that the
-first peak is obtained when the energy of the incoming beam is 0.720\,eV and
-the absolute maximum of the response is obtained when for 0.912\,eV, both for a
-polarization angle $\alpha = 145^{\circ}$.
+150$^{\circ}$ is the zone where the maximum for both responses is held.
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
-%
-\ref{fig:alt-vy-comp-rtp} we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+In the top frames of top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we
+present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
 $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
-the polarization angle to $\alpha=145^{\circ}$ for which the response is
-maximized for the \emph{alt} structure. In the same figures and frames we
-present ind dashed lines the spin polarization angles related to the right scale
-and in the bottom frames the corresponding three components.
+the polarization angle to $\alpha=145^{\circ}$. In the same figures and frames
+we present the spin polarization angles related to the right scale and in the
+bottom frames the corresponding three components.
 % 
 Making the analysis for the components and angles when the spin current is
-directed in the $x$ direction, corresponding to the Fig.
-% 
-\ref{fig:alt-vx-comp-rtp}, we found that for the \emph{alt} structure when the
-energy of the incoming beam is 0.720\,eV we have similar contributions from all
-the components resulting in a response of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar and azimuthal
-spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha)=46^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=41^{\circ}$ having variations in the range
-of the peak but being directed over the first Cartesian Quadrant of the $xy$
-plane;
-% 
-for an energy of 0.912\,eV we have a major contribution from the
+directed in the $x$ direction, corresponding to the top panel of Fig.
+% 
+\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
+is 0.720\,eV we have similar contributions from all the components resulting in
+a response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar
+and azimuthal spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) =
+46^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 41^{\circ}$ being the
+spin directed over the first Cartesian Quadrant of the $xy$ plane;
+% 
+then, for an energy of 0.912\,eV we have a major contribution from the
 $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component resulting in a total
-response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and angles
+response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s being this
+value the absolute maximum when the spin velocity is directed in the $x$
+Cartesian direction. The corresponding polar and azimuthal angles are
 $\theta_{\mathrm{x}}(\omega,\alpha)=154^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ having variations of
-$\pm3^{\circ}$ in for energy variations of $\pm1$\,eV and being directed
+$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ being the spin directed
 downward the fourth Cartesian Quadrant of the $xy$ plane.
@@
 Making now the analysis for the components and angles when the spin current is
-directed along the $y$ direction, corresponding to the Fig.
-% 
-\ref{fig:alt-vy-comp-rtp}, we found that when the energy of the incoming beam is
-0.720\,eV we have more contribution from the
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component resulting in a response of
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=51.9$\,Km/s and angles
-$\theta_{\mathrm{y}}(\omega,\alpha)=141^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=222^{\circ}$ being the first constant and
-the second having variations of $\pm3^{\circ}$ for energy variations of
-$\pm0.3$\,eV and being directed downward the third Cartesian Quadrant of the
-$xy$ plane.
-% 
-Then, for the peak centered at 0.912\,eV we have similar contributions of all
-the components resulting in a response
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=52.3$\,Km/s being this the absolute
-maximum response for the \emph{alt} structure. The corresponding angles are
-$\theta_{\mathrm{y}}(\omega,\alpha)=129^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=229^{\circ}$ being both constant for the
-energy range of the peak and being directed downward the third Cartesian
-Quadrant of the $xy$ plane.
+directed along the $y$ direction, corresponding to the bottom panel of Fig.
+\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
+is 0.720\,eV we have more contribution from the
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component and the response has a
+value of $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 51.9$\,Km/s corresponding
+the polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha) =
+141^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 222^{\circ}$ being the
+spin directed downward the third Cartesian Quadrant of the $xy$ plane.
+% 
+For the peak centered at 0.912\,eV we have similar contributions of all the
+components resulting in a response $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| =
+52.3$\,Km/s being this the absolute maximum response for the \emph{alt}
+structure. The corresponding angles are $\theta_{\mathrm{y}}(\omega,\alpha) =
+129^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 229^{\circ}$ being the
+spin directed downward the third Cartesian Quadrant of the $xy$ plane.
 % 
 Finally we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
-negative keeping the same spin polarization since the onset of the response to a
-energy of the incoming beam of 0.886\,eV when the response decreases and goes to
-zero.
+negative keeping the same spin polarization and velocity direction since the
+onset of the response to a energy of the incoming beam of 0.886\,eV when the
+response decreases and goes to zero.
 

### 2017-05-23 mu/article/article.tex
sab

@@
 % 
-A negative quantity in the spin velocity means a change in the spin polarization traveling in the opposite direction.
+A negative quantity in the spin velocity means a change in the spin polarization
+traveling in the opposite direction.
 % 
@@
 $\mathrm{yx}$ and $\mathrm{yy}$ components have less contributions for the total
-response than the $\mathrm{yz}$ and for the same incoming beam energy the components have values of
+response than the $\mathrm{yz}$ and for the same incoming beam energy the
+components have values of
 % 
@@
 % 
-We found that for both cases the components have similar contributions for the corresponding response and for
-an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
-in a value of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the
-$x$ direction  with polar and azimuthal spin polarization angles
+We found that for both cases the components have similar contributions for the
+corresponding response and for an incoming energy beam of 1.934\,eV  we have the
+first local maximum resulting in a value of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the $x$ direction
+with polar and azimuthal spin polarization angles
 $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin
-directed over the first Cartesian Quadrant of the $xy$ plane.
+$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin directed over
+the first Cartesian Quadrant of the $xy$ plane.
 % 

### 2017-05-24 mu/up/up-scripts/up-magsvab-inang-lay.sh
New layer script.

@@ -8,6 +8,9 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
+lay = ( 1 2 )
+
+
 deg=180/3.141592
 
 calc () {
@@ -25,6 +28,8 @@ for i in ${angles[@]}; do
     echo  "" >> $outputsm
 done
 }
+
+for i in ${lay[@]}; do
 
 ############################## V_{s^x} #########################################
 
@@ -61,3 +66,5 @@ inputsm=( v.sm_0.03_xz_12802_40-spin_scissor_0_Nc_32_ang_
           v.sm_0.03_yz_12802_40-spin_scissor_0_Nc_32_ang_  )
 
 calc
+
+done

### 2017-05-25 mu/article/article.tex
Made calv.kk* and calv.sm_0.03* for 0-360 deg for up and alt structures

@@
 
-The spin density injection current $\dot{K}^{\mathrm{ab}}$ can be written in
-terms of a material response pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as
-% with speed along direction $\mathrm{a}$ and spin
-% polarization along $\mathrm{b}$ is defined as
+The spin density injection current $\dot{K}^{\mathrm{ab}}(\omega)$, where the
+roman superscripts denote Cartesian components corresponding $\mathrm{a}$ to the
+spin velocity direction and $\mathrm{b}$ to the spin polarization direction, can
+be written in terms of a material response pseudotensor
+$\mu^{\mathrm{abcd}}(\omega)$ as
 \begin{equation*}
@@
 \end{equation*}
-where the roman superscripts denote Cartesian components corresponding
-$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
-polarization direction and the pseudotensor can be written as
+where the pseudotensor is given by\cite{bhatPRL05}
 \begin{widetext}
@@
 \label{eq:mu}
-% \\
-% K^{\mathrm{ab}}_{mn}
-% &=
-% \sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
-% \label{eq:velspi-matelem}
 \end{align}
@@
 \sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
-the spin current matrix elements that, using time reversal invariance,
-$K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k}) $. The $'$ in
-the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
-covers these states and since $mu$ is real we have that
+the spin current matrix elements that, using time reversal invariance, satisfy
+the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
+$. The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and
+the sum only covers these states and since $\mu$ is real we have that
 $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
@@
 along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
-plane with a polarization angle $\alpha$. Then,
+plane with a polarization angle $\alpha$ as
 \begin{widetext}
@@
 For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
-\begin{align}
+\begin{equation*}\label{eq:vab-90deg}
 \mathcal{V}^{\mathrm{ab}} (\omega)
-&= \frac{2}{\hbar}
+= \frac{2}{\hbar}
 \frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
@@
 {\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
-\label{eq:vab-90deg}
-\end{align}
+\end{equation*}
 
@@
 \subsection{Fixing spin}\label{sec:theory-fixspin}
-Considering that we have 2D structures, one of the options is fix the spin along
-the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
-velocity with spin polarization along the $\mathrm{b}$ direction as 
+
+Considering that we have 2D structures, one of the options to analyze the spin
+velocity (Eq. \eqref{eq:vab}) is fixing the spin along the $x$, $y$, or $z$
+Cartesian coordinates. We define the magnitude of the spin velocity with spin
+polarization along the $\mathrm{b}$ direction as
 \begin{align}
@@
 \gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
-\label{eq:gammapar} 
+\label{eq:gamma-par} 
 \\
 \gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
-\label{eq:gammaperp}
+\label{eq:gamma-perp}
 \end{align}
@@
 
-In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
-Cartesian coordinate and then define the magnitude of the spin velocity directed
-along the $\mathrm{a}$ direction as
+Another possibility to analyze the spin velocity (Eq. \eqref{eq:vab}) is fixing
+the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
+define the magnitude of the spin velocity directed along the $\mathrm{a}$
+direction as
 \begin{align}
@@
 Using the Eq. \eqref{eq:vs-mag}, we calculated the
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega,\alpha)$ response and made the
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ response and made the
 analysis for the case when the spin is fixed in the $z$ direction, directed
-perpendicularly to the surface of the \emph{alt} and \emph{up} structures. Also,
+perpendicularly to the surface of the \emph{up} and \emph{alt} structures. Also,
 using the Eq. \eqref{eq:gamma-ang}, we determined the angle
@@
 surface of the each structure.
+% 
+For both cases, the most interesting case is that for which the spin is
+perpendicular to the surface corresponding to $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$.
 
@@
 
-The most interesting case is that for which the spin is perpendicular to the
-surface corresponding to $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$.
-% 
-For this case we first analyzed two energy ranges for the \emph{up} structure,
-the first for an incoming energy beam from 0.0\,eV to 0.2\,eV which include the
-THz and the Mid Infrared (MIR) range, where the absolute maximum of the
+% 
+We first analyzed two energy ranges for the \emph{up} structure, the first for
+an incoming energy beam from 0.0\,eV to 0.2\,eV which include the THz and the
+Mid Infrared (MIR) radiation, where the absolute maximum of the
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained and
@@
 fixing the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively,
-for which value the response is maximized for the \emph{up} structure. In the
+values for which the response is maximized for the \emph{up} structure. In the
 same panels and frames we present in dashed lines, related to the right scale,
 the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ obtained
-from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the
-panels we present the corresponding components
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
+from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the panels we
+present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
+and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
 square boxes indicating the values where the angles of the spin velocity are
-parallel (Eq. \ref{eq:gammapar}) and perpendicular (Eq. \ref{eq:gammaperp}) and
-the arrows are directed to the value of the response corresponding to those
+parallel (Eq. \ref{eq:gamma-par}) and perpendicular (Eq. \ref{eq:gamma-perp})
+and the arrows are directed to the value of the response corresponding to those
 angles.
@@
 panel the green circled box indicates the value for which the polarization angle
-and the response direction angle are collinear (Eq. \ref{eq:gammapar}) being
+and the response direction angle are collinear corresponding to
 $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in a
@@
 Again the circled box indicates the collinear angle (Eq.
-\eqref{eq:gammapar}) corresponding to
+\eqref{eq:gamma-par}) corresponding to
 $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 53.5^{\circ}$ corresponding a

### 2017-05-25 mu/alt/alt-scripts/alt-calvab.sh

@@ -1,39 +1,65 @@
 #!/bin/bash
 
-an=145   # Pol. angle of incoming light
-layers=(1 2 3 4 5 6)
+# Pol. angles of incoming light
+an=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+         095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
+         185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
+         275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
+
+layers=( 1 2 3 4 5 6 )
+
 kp=14452
 ec=65
 nc=32
 
-
-
 # semaring
 sm=0.03
 
-
 pi=`echo "4*a(1)" | bc -l`
-rad=`echo "$an*($pi/180)" | bc -l`
-cos=`echo "c($rad)" | bc -l`
-coscuad=`echo "$cos*$cos" | bc -l`
-sin=`echo "s($rad)" | bc -l`
-sincuad=`echo "$sin*$sin" | bc -l`
-cossin=`echo "$cos*$sin" | bc -l`
 
+for i in ${an[@]}; do
 
-for i in ${layers[@]}; do
-    paste calmu.kk_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_"$kp"_"$i"_"$ec"-spin_scissor_0_Nc_"$nc"  chi1.kk_xx_yy_zz_"$kp"_"$ec"-spin_scissor_0_Nc_32 | awk '{ print $1, (($2*'"$coscuad"'+$6*'"$sincuad"'+2*$3*'"$cossin"')/($13*'"$coscuad"'+$15*'"$sincuad"'+0.00001)) }' >  calv.kk_xx_"$kp"_"$i"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$an"
[…]

### 2017-05-25 mu/up/up-scripts/up-calvab.sh

@@ -1,44 +1,63 @@
 #!/bin/bash
 
-# Pol. angle of incoming light
-an=40 
+# Pol. angles of incoming light
+an=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+         095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
+         185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
+         275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
+
+layers=( 1 2 )
+
+kp=12802
+ec=40
+nc=18
+
+
 # semaring
 sm=0.03
 
-
 pi=`echo "4*a(1)" | bc -l`
-rad=`echo "$an*($pi/180)" | bc -l`
-cos=`echo "c($rad)" | bc -l`
-coscuad=`echo "$cos*$cos" | bc -l`
-sin=`echo "s($rad)" | bc -l`
-sincuad=`echo "$sin*$sin" | bc -l`
-cossin=`echo "$cos*$sin" | bc -l`
 
+for i in ${an[@]}; do
 
+    rad=`echo "$an*($pi/180)" | bc -l`
+    cos=`echo "c($rad)" | bc -l`
+    coscuad=`echo "$cos*$cos" | bc -l`
+    sin=`echo "s($rad)" | bc -l`
+    sincuad=`echo "$sin*$sin" | bc -l`
+    cossin=`echo "$cos*$sin" | bc -l`
 
[…]

### 2017-05-25 mu/alt/alt-scripts/alt-magsvab-inang-lay.sh
Checking enegy error for up svab

@@ -1,0 +1,72 @@
+#!/bin/bash
+
+# angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+#              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+             095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
+             185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
+             275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
+
+layers=( 1 2 3 4 5 6 )
+
+deg=180/3.141592
+
+calc () {
+echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
+echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
+for i in ${angles[@]}; do
+    paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp1
+    paste .temp1 | awk '{if($1 < 0) {printf("%010.6f\n", ($1*'"$deg"')+180) ;} else {printf("%010.6f\n"), $1*'"$deg"' } }' > .deg1
+    paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i"  .deg1 | awk '{printf("%02.5E    %02.6E    %03.0f    %02.6E    %02.6E    %010.6f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"', $2, $4, $5 }' >> $outputkk
+    echo  "" >> $outputkk
+    
+    paste "${inputsm[0]}""$i"  "${inputsm[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp2
[…]

### 2017-05-25 mu/up/up-scripts/up-calvab.sh

@@ -12,7 +12,6 @@ kp=12802
 ec=40
 nc=18
 
-
 # semaring
 sm=0.03
 

### 2017-05-25 mu/up/up-scripts/up-magsvab-inang-lay.sh

@@ -10,6 +10,8 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 deg=180/3.141592
 
+layers=( 1 2 )
+
 calc () {
 echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
 echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
@@ -26,38 +28,44 @@ for i in ${angles[@]}; do
 done
 }
 
-############################## V_{s^x} #########################################
 
-outputkk=magsv.kk_ax_12802_40-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
-outputsm=magsv.sm_0.03_ax_12802_40-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
+for j in ${layers[@]}; do
 
-inputkk=( v.kk_xx_12802_40-spin_scissor_0_Nc_32_ang_  
-          v.kk_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
-inputsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_  
-          v.sm_0.03_yx_12802_40-spin_scissor_0_Nc_32_ang_  )
+  ########################### Cal V_{s^x} ######################################
 
-calc
+  outputkk=magCalsv.kk_ax_12802_"$j"_40-spin_scissor_0_Nc_18_incang_${angles[0]}-${angles[${#angles[@]}-1]}
+  outputsm=magCalsv.sm_0.03_ax_12802_"$j"_40-spin_scissor_0_Nc_18_incang_${angles[0]}-${angles[${#angles[@]}-1]}
 
-############################## V_{s^y} #########################################
+  inputkk=( calv.kk_xx_12802_"$j"_40-spin_scissor_0_Nc_18_ang_  
+            calv.kk_yx_12802_"$j"_40-spin_scissor_0_Nc_18_ang_  )
+  inputsm=( calv.sm_0.03_xx_12802_"$j"_40-spin_scissor_0_Nc_18_ang_  
[…]

### 2017-05-25 mu/up/up-scripts/up-magsvab-inang.sh

@@ -8,6 +8,16 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
+
+# FIXED ENERGY:
+en1="8.80000E-02"
+en2="9.12000E-01"
+
+# OUTPUT FILE SUFIX:
+fs1="0.088eV"
+fs2="0.912eV"
+
+
 deg=180/3.141592
 
 calc () {
@@ -38,6 +48,13 @@ inputsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_
 
 calc
 
+grep "$en1" "$outputkk" > magsv.kk_0.03_ax_12802_40-"$fs1"
+grep "$en1" "$outputsm" > magsv.sm_0.03_ax_12802_40-"$fs1"
+
+grep "$en2" "$outputkk" > magsv.kk_0.03_ax_12802_40-"$fs2"
+grep "$en2" "$outputsm" > magsv.sm_0.03_ax_12802_40-"$fs2"
+
+
 ############################## V_{s^y} #########################################
 
 outputkk=magsv.kk_ay_12802_40-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -50,6 +67,13 @@ inputsm=( v.sm_0.03_xy_12802_40-spin_scissor_0_Nc_32_ang_
 
 calc
 
+grep "$en1" "$outputkk" > magsv.kk_0.03_ay_12802_40-"$fs1"
+grep "$en1" "$outputsm" > magsv.sm_0.03_ay_12802_40-"$fs1"
+
+grep "$en2" "$outputkk" > magsv.kk_0.03_ay_12802_40-"$fs2"
+grep "$en2" "$outputsm" > magsv.sm_0.03_ay_12802_40-"$fs2"
+
+
 ############################## V_{s^z} #########################################
 
 outputkk=magsv.kk_az_12802_40-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -61,3 +85,13 @@ inputsm=( v.sm_0.03_xz_12802_40-spin_scissor_0_Nc_32_ang_
[…]

### 2017-05-25 mu/up/up-scripts/up-magsvab-inang.sh
Corection in energy label for up

@@ -11,11 +11,11 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 # FIXED ENERGY:
 en1="8.80000E-02"
-en2="9.12000E-01"
+en2="1.97200E+00"
 
 # OUTPUT FILE SUFIX:
 fs1="0.088eV"
-fs2="0.912eV"
+fs2="1.972eV"
 
 
 deg=180/3.141592

### 2017-05-25 mu/alt/alt-scripts/alt-magsvab-inang-lay.sh
Making CalV_{s^a} responses to plot

@@ -10,6 +10,12 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 
 layers=( 1 2 3 4 5 6 )
 
+# FIXED ENERGY:
+en1="9.12000E-01"
+
+# OUTPUT FILE SUFIX:
+fs1="0.912eV"
+
 deg=180/3.141592
 
 calc () {
@@ -42,6 +48,9 @@ for j in ${layers[@]}; do
 
     calc
 
+    grep "$en1" "$outputkk" > magCalsv.kk_0.03_ax_14452_"$j"_65-"$fs1"
+    grep "$en1" "$outputsm" > magCalsv.sm_0.03_ax_14452_"$j"_65-"$fs1"
+
     ########################## Cal V_{s^y} #####################################
 
     outputkk=magCalsv.kk_ay_14452_"$j"_65-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -54,6 +63,9 @@ for j in ${layers[@]}; do
 
     calc
 
+    grep "$en1" "$outputkk" > magCalsv.kk_0.03_ay_14452_"$j"_65-"$fs1"
+    grep "$en1" "$outputsm" > magCalsv.sm_0.03_ay_14452_"$j"_65-"$fs1"
+
     ########################## Cal V_{s^z} #####################################
 
     outputkk=magCalsv.kk_az_14452_"$j"_65-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -65,6 +77,9 @@ for j in ${layers[@]}; do
               calv.sm_0.03_yz_14452_"$j"_65-spin_scissor_0_Nc_32_ang_  )
 
     calc
+
+    grep "$en1" "$outputkk" > magCalsv.kk_0.03_az_14452_"$j"_65-"$fs1"
+    grep "$en1" "$outputsm" > magCalsv.sm_0.03_az_14452_"$j"_65-"$fs1"
 
 done
 

### 2017-05-25 mu/up/up-scripts/up-magsvab-inang-lay.sh

@@ -8,6 +8,14 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
+# FIXED ENERGY:
+en1="8.80000E-02"
+en2="1.97200E+00"
+
+# OUTPUT FILE SUFIX:
+fs1="0.088eV"
+fs2="1.972eV"
+
 deg=180/3.141592
 
 layers=( 1 2 )
@@ -43,6 +51,12 @@ for j in ${layers[@]}; do
 
   calc
 
+  grep "$en1" "$outputkk" > magCalsv.kk_0.03_ax_12802_"$j"_40-"$fs1"
+  grep "$en1" "$outputsm" > magCalsv.sm_0.03_ax_12802_"$j"_40-"$fs1"
+
+  grep "$en2" "$outputkk" > magCalsv.kk_0.03_ax_12802_"$j"_40-"$fs2"
+  grep "$en2" "$outputsm" > magCalsv.sm_0.03_ax_12802_"$j"_40-"$fs2"
+
   ########################### Cal V_{s^y} ######################################
 
   outputkk=magCalsv.kk_ay_12802_"$j"_40-spin_scissor_0_Nc_18_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -55,6 +69,12 @@ for j in ${layers[@]}; do
 
   calc
 
+  grep "$en1" "$outputkk" > magCalsv.kk_0.03_ay_12802_"$j"_40-"$fs1"
+  grep "$en1" "$outputsm" > magCalsv.sm_0.03_ay_12802_"$j"_40-"$fs1"
+
+  grep "$en2" "$outputkk" > magCalsv.kk_0.03_ay_12802_"$j"_40-"$fs2"
+  grep "$en2" "$outputsm" > magCalsv.sm_0.03_ay_12802_"$j"_40-"$fs2"
+
   ########################### Cal V_{s^z} ######################################
 
   outputkk=magCalsv.kk_az_12802_"$j"_40-spin_scissor_0_Nc_18_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -66,6 +86,12 @@ for j in ${layers[@]}; do
[…]

### 2017-05-25 mu/up/up-scripts/up-magsvab-inang.sh

@@ -8,7 +8,6 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
-
 # FIXED ENERGY:
 en1="8.80000E-02"
 en2="1.97200E+00"
@@ -16,7 +15,6 @@ en2="1.97200E+00"
 # OUTPUT FILE SUFIX:
 fs1="0.088eV"
 fs2="1.972eV"
-
 
 deg=180/3.141592
 

### 2017-05-27 mu/alt/alt-scripts/alt-calvab.sh
Completed plots for Cal V_{s^z}

@@ -17,16 +17,20 @@ sm=0.03
 
 pi=`echo "4*a(1)" | bc -l`
 
-for i in ${an[@]}; do
+pi=`echo "4*a(1)" | bc -l`
 
-    rad=`echo "$an*($pi/180)" | bc -l`
-    cos=`echo "c($rad)" | bc -l`
-    coscuad=`echo "$cos*$cos" | bc -l`
-    sin=`echo "s($rad)" | bc -l`
-    sincuad=`echo "$sin*$sin" | bc -l`
-    cossin=`echo "$cos*$sin" | bc -l`
+for j in ${layers[@]}; do
 
-    for j in ${layers[@]}; do
+    for i in ${an[@]}; do
+
+        rad=`echo "$i*($pi/180)" | bc -l`
+        cos=`echo "c($rad)" | bc -l`
+        coscuad=`echo "$cos*$cos" | bc -l`
+        sin=`echo "s($rad)" | bc -l`
+        sincuad=`echo "$sin*$sin" | bc -l`
+        cossin=`echo "$cos*$sin" | bc -l`
+
+        
         paste calmu.kk_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"  chi1.kk_xx_yy_zz_"$kp"_"$ec"-spin_scissor_0_Nc_32 | awk '{ print $1, (($2*'"$coscuad"'+$6*'"$sincuad"'+2*$3*'"$cossin"')/($13*'"$coscuad"'+$15*'"$sincuad"'+0.00001)) }' >  calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"
         # ~/tiniba/smear/rsmear2  1   calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  calv.sm_"$sm"_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  "$sm"
         rsmear2  1   calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  calv.sm_"$sm"_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  "$sm"

### 2017-05-27 mu/up/up-scripts/up-calvab.sh

@@ -17,16 +17,17 @@ sm=0.03
 
 pi=`echo "4*a(1)" | bc -l`
 
-for i in ${an[@]}; do
+for j in ${layers[@]}; do
 
-    rad=`echo "$an*($pi/180)" | bc -l`
-    cos=`echo "c($rad)" | bc -l`
-    coscuad=`echo "$cos*$cos" | bc -l`
-    sin=`echo "s($rad)" | bc -l`
-    sincuad=`echo "$sin*$sin" | bc -l`
-    cossin=`echo "$cos*$sin" | bc -l`
+    for i in ${an[@]}; do
 
-    for j in ${layers[@]}; do
+        rad=`echo "$i*($pi/180)" | bc -l`
+        cos=`echo "c($rad)" | bc -l`
+        coscuad=`echo "$cos*$cos" | bc -l`
+        sin=`echo "s($rad)" | bc -l`
+        sincuad=`echo "$sin*$sin" | bc -l`
+        cossin=`echo "$cos*$sin" | bc -l`
+
         paste calmu.kk_xxxx_xxxy_xxxz_xxyx_xxyy_xxyz_xxzx_xxzy_xxzz_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"  chi1.kk_xx_yy_zz_"$kp"_"$ec"-spin_scissor_0_Nc_32 | awk '{ print $1, (($2*'"$coscuad"'+$6*'"$sincuad"'+2*$3*'"$cossin"')/($13*'"$coscuad"'+$15*'"$sincuad"'+0.00001)) }' >  calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"
         # ~/tiniba/smear/rsmear2  1   calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  calv.sm_"$sm"_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  "$sm"
         rsmear2  1   calv.kk_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  calv.sm_"$sm"_xx_"$kp"_"$j"_"$ec"-spin_scissor_0_Nc_"$nc"_ang_"$i"  "$sm"

### 2017-05-31 mu/article/article.tex
Completed plots for Cal V_{s^z}
V_{s^z} layer description completed

@@
 \usepackage{blindtext}  % fill text
-\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 \usepackage{multirow}
@@
 \section{Introduction}
+
 \blindtext
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=\linewidth]{figures/upstruc2}
+    \\
+    \includegraphics[width=\linewidth]{figures/upstruc1}
+    \caption{Up structure}
+    \label{fig:up-struc}
+\end{figure}
 \begin{figure}[ht!]
@@
 \end{figure}
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=\linewidth]{figures/upstruc2}
-    \\
-    \includegraphics[width=\linewidth]{figures/upstruc1}
-    \caption{Up structure}
-    \label{fig:up-struc}
-\end{figure}
 \blindtext
@@
 
-The spin density injection current $\dot{K}^{\mathrm{ab}}(\omega)$, where the
+The spin density injection current $\dot{K}^{\mathrm{ab}}(\omega)$, 
+% 
+{
+\color{red}
+where the
 roman superscripts denote Cartesian components corresponding $\mathrm{a}$ to the
@@
 $\mu^{\mathrm{abcd}}(\omega)$ as
+}
 \begin{equation*}
@@
 \end{widetext}
+{\color{red}
 where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
@@
 the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
-$. The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and
-the sum only covers these states and since $\mu$ is real we have that
+$. 
+}% 
+The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and
+the sum only covers these states and 
+{\color{red}
+since $\mu$ is real we have that
 $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
-
+}
 Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
@@
 \end{widetext}
+{\color{red}
 where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
 components\cite{arzatePRB14}.
+}
 % 
@@
 
-Considering that we have 2D structures, one of the options to analyze the spin
-velocity (Eq. \eqref{eq:vab}) is fixing the spin along the $x$, $y$, or $z$
-Cartesian coordinates. We define the magnitude of the spin velocity with spin
-polarization along the $\mathrm{b}$ direction as
+{\color{red} Considering that we have 2D structures, one of the options to
+analyze the spin velocity (Eq. \eqref{eq:vab}) is fixing the spin parallel to
+the surface of the structure in the $x$ or $y$ directions or perpendicularly to
+it in the $z$ direction. We define the magnitude of the spin velocity with spin
+polarization along the $\mathrm{b}$ Cartesian coordinate as}
 \begin{align}
@@
 where the angle is measured in the counter-clockwise direction from the positive
-$x$ Cartesian coordinate. We also define two special angles
+$x$ Cartesian coordinate. 
+{\color{red}
+We also define two special angles
 \begin{align}
@@
 perpendicularly respect to the polarization angle of the incoming beam.
+}
 
@@
 
-Another possibility to analyze the spin velocity (Eq. \eqref{eq:vab}) is fixing
-the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
-define the magnitude of the spin velocity directed along the $\mathrm{a}$
-direction as
+{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab} is fixing the velocity on
+the $xy$ plane along $x$ or $y$ Cartesian coordinate and then define the
+magnitude of the spin velocity directed along the $\mathrm{a}$ direction as}
 \begin{align}
@@
 \end{align}
-Then, the spin direction depends of the components of the previous equation and
-so we define the spin orientation polar and azimuthal angles as
+{\color{red} Then, the spin direction depends of the $x$, $y$, and $z$
+components of the previous equation and so we define the spin orientation polar
+and azimuthal angles as}
 \begin{align}
@@
 \end{align}
-where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
-negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
-measured on the $xy$ plane in the counter-clockwise direction from the positive
-$x$ Cartesian coordinate.
+{\color{red} where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
+positive to the negative $z$ Cartesian coordinate and
+$\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
+counter-clockwise direction from the positive $x$ Cartesian coordinate.}
 
@@
 
+\begin{table}[t]
+\center
+\begin{tabular}{ccccc}\\
+\hline
+\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
+\cline{3-5}
+\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
+\hline
+1 & H & -0.61516 & -1.77416 &  0.73196 \\
+1 & H &  0.61518 &  0.35514 &  0.73175 \\
+2 & C & -0.61516 & -1.77264 & -0.49138 \\
+2 & C & -0.61516 & -0.35600 & -0.72316 \\
+2 & C &  0.61516 &  0.35763 & -0.49087 \\
+\hline
+\end{tabular}
+
+\caption{Unit cell of \emph{up} structure. Layer division, atom types and
+positions for the \emph{up} structure. The structure unit cell was divided in
+two layers corresponding to hydrogen and carbon atoms.The corresponding layer
+atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
+number of layer.}
+\label{tab:up-unitcell}
+\end{table}
+% 
+% 
 \begin{table}[t]
@@
 \end{table}
-% 
-\begin{table}[t]
-\center
-\begin{tabular}{ccccc}\\
-\hline
-\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
-\cline{3-5}
-\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
-\hline
-1 & H & -0.61516 & -1.77416 &  0.73196 \\
-1 & H &  0.61518 &  0.35514 &  0.73175 \\
-2 & C & -0.61516 & -1.77264 & -0.49138 \\
-2 & C & -0.61516 & -0.35600 & -0.72316 \\
-2 & C &  0.61516 &  0.35763 & -0.49087 \\
-\hline
-\end{tabular}
-
-\caption{Unit cell of \emph{up} structure. Layer division, atom types and
-positions for the \emph{up} structure. The structure unit cell was divided in
-two layers corresponding to hydrogen and carbon atoms.The corresponding layer
-atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
-number of layer.}
-\label{tab:up-unitcell}
-\end{table}
 
@@
 and C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
-carbon systems with 50\% hydrogenation in different arrangements. The \emph{alt}
-system has alternating hydrogen atoms on the upper and bottom sides of the
-carbon sheet, while the \emph{up} system has H only on the upper side. We take
-the hexagonal carbon lattice to be on the $xy$ plane for both structures, and
-the carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
-\ref{fig:alt-struc} and \ref{fig:up-struc}.
-
-We calculated the self-consistent ground state and the Kohn-Sham states using
-density functional theory in the local density approximation (DFT-LDA) with a
-planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
-Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
-pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
-needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
+carbon systems with 50\% hydrogenation in different arrangements. The \emph{up}
+structure has hydrogen atoms only on the upper side of the carbon sheet while
+the \emph{alt} structure has alternating hydrogen atoms on the upper and bottom
+sides. We take the hexagonal carbon lattice to be on the $xy$ plane for both
+structures, and the carbon-hydrogen bonds on the perpendicular $xz$ plane, as
+depicted in Figs. \ref{fig:alt-struc} and \ref{fig:up-struc}
+% 
+{\color{blue} and the coordinates for the \emph{up} and \emph{alt} unit cells of
+the structures are presented in Tables \ref{tab:up-unitcell} and
+% 
+\ref{tab:alt-unitcell}. In same tables we present the layer division needed to
+calculate the layer-by-layer contribution for the
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ presented in Eqns. 
+% 
+\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was divided
+in two layers, the first comprised of the top hydrogen atoms denoted by the
+number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc} and
+the second comprised of carbon atoms and denoted by the number 2. The \emph{alt}
+structure was divided in six layers denoted with numbers from 1 to 6 in Table
+\ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and sixth
+layers correspond to hydrogen atoms in the top and bottom positions and from the
+second to the fifth correspond to carbon atoms placed in different positions.}
+
+{\color{red} We calculated the self-consistent ground state and the Kohn-Sham
+states using density functional theory in the local density approximation (DFT-
+LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.}
+% 
+We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
+Gaussian pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit
+interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
+in Eq.
 \eqref{eq:mu}.
@@
 points and 8452 $\mathbf{k}$ points in the irreducible Brillouin zone (IBZ)
-presenting LDA energy band gaps of 0.72\,eV and 0.088\,eV, respectively.
+{\color{red} resulting in LDA energy band gaps of 0.72\,eV and 0.088\,eV,
+respectively.
 % 
@@
 remains as an effective and useful tool for computing diverse properties derived
-from the electronic band structure.
+from the electronic band structure.}
 
@@
 
-Using the Eq. \eqref{eq:vab}, we calculated the
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{alt} and
-\emph{up} 2D structures and for the CdSe and GaAs bulk systems and the results
+{\color{red}Using the Eq. \eqref{eq:vab}, we calculated the
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{up} and
+\emph{alt} 2D structures and for the CdSe and GaAs bulk systems; the results
 are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
 the response of each structure is that for which the response is maximized in
-each case.
+each case.}
 % 
@@
 The most intense response corresponds to the \emph{up} structure centered at
-0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
-velocity of 87.2\,Km/s.
+0.088\,eV corresponding to the {\color{red} Mid Infrared (MIR)} radiation and
+reaching a spin velocity of 87.2\,Km/s.
 % 
 In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the Near Infrared (NIR) and visible radiation, all the four
+to energies of the {\color{red} Near Infrared (NIR) to visible radiation}, all the four
 structures have contributions in the same order of magnitude.
 % 
-Starting with the 2D structures we have that the \emph{up} structure has other
-two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
-22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
-peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
-and -32.9\,Km/s, respectively.
+For this energy range the \emph{up} structure has two peaks centered at 1.94\,eV
+and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s,
+respectively, and the \emph{alt} structure has two peaks centered at 0.72\,eV
+and 0.91\,eV reaching spin velocities of -40.2\,Km/s and -32.9\,Km/s,
+respectively.
 % 
@@
 % 
-A negative quantity in the spin velocity means a change in the spin polarization
-traveling in the opposite direction.
+{\color{red} A negative quantity in the spin velocity means a change in the spin
+polarization traveling in the opposite direction.
 % 
@@
 2D and bulk structures. We found that the most intense response for the spin
-velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
-4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
-structure has a response more intense than the bulk systems but being less
-intense than the corresponding to the \emph{up} one.
+velocity corresponds to the \emph{up} structure being 3.25 times more intense
+than that of the CdSe and 4.03 times more intense than that of the GaAs bulk
+structures. Also, the \emph{alt} structure has a response more intense than the
+bulk systems but being less intense than the corresponding to the \emph{up}
+one.}
 %
@@
 
-Using the Eq. \eqref{eq:vs-mag}, we calculated the
+{\color{red} Using the Eq. \eqref{eq:vs-mag}, we calculated the
 $|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ response and made the
-analysis for the case when the spin is fixed in the $z$ direction, directed
+analysis for the case when the spin is fixed in the $z$ coordinate, directed
 perpendicularly to the surface of the \emph{up} and \emph{alt} structures. Also,
@@
 $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
-surface of the each structure.
-% 
-For both cases, the most interesting case is that for which the spin is
-perpendicular to the surface corresponding to $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$.
+surface of the each structure.}
+%
 
@@
 
-% 
-We first analyzed two energy ranges for the \emph{up} structure, the first for
-an incoming energy beam from 0.0\,eV to 0.2\,eV which include the THz and the
-Mid Infrared (MIR) radiation, where the absolute maximum of the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained and
-the second for an energy range from 1.80\,eV to 2.1\,eV, corresponding to
-visible radiation, where two local maxima are found.
-% 
-In Fig. \ref{fig:up-3d-vsz} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
-evaluate Eq. \eqref{eq:vs-mag}.
+We first analyzed two energy ranges in Fig. \ref{fig:up-3d-vsz} for the
+\emph{up} structure, the first for an incoming energy beam from 0.0\,eV to
+0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR) radiation,
+where the absolute maximum of the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained, and
+the second for an energy range from 1.80\,eV to 2.1\,eV (bottom panel),
+corresponding to visible radiation, where two local maxima are found.
 % 
@@
 0.093\,eV and polarization angles $\alpha$ between $30^{\circ}$ and
-$45^{\circ}$. Also two local maxima are held for same polarization angles but
-for an energy range of the incoming beam between 1.90\,eV and 2.05\,eV.
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
-% %%%%%%%%%%%%%%%%%
+$45^{\circ}$. Also the two local maxima are held for same beam polarization
+angles but for an energy range between 1.90\,eV and 2.05\,eV.
 In the top frames of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we
@@
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related to the left scale,
-fixing the energy of the incoming beam to 0.088\,eV and 0.912\,eV, respectively,
+fixing the energy of the incoming beam to 0.088\,eV and 1.972\,eV, respectively,
 values for which the response is maximized for the \emph{up} structure. In the
 same panels and frames we present in dashed lines, related to the right scale,
-the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ obtained
-from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the panels we
-present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
-and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
+the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$, and in
+the bottom frames of the panels we present the corresponding components
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
 square boxes indicating the values where the angles of the spin velocity are
@@
 angles.
-% 
+% %%%%%%%%%%%%%%%%%
+% %% 0.0 eV - 0.16 eV
+% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
+% %%%%%%%%%%%%%%%%%
 From top panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we have
@@
 the $\mathrm{z}$ direction and having a velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)=65^{\circ}$ on the $xy$ plane.
-% 
-From the top panel of Fig. \ref{fig:up-vaz-rag} we have that the velocity angle
-is almost constant for all the polarization angle range having values of
-$\gamma_{\mathrm{z}}(\omega,\alpha) = 65.5^{\circ} \pm 0.5^{\circ}$. In this
-panel the green circled box indicates the value for which the polarization angle
-and the response direction angle are collinear corresponding to
-$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in a
-value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+$\gamma_{\mathrm{z}}(\omega,\alpha)=65^{\circ}$ on the first Cartesian quadrant
+of the $xy$ plane.
+% 
+{\color{red} From the top panel of Fig. \ref{fig:up-vaz-rag} we have that the
+velocity angle is almost constant for all the polarization angle range having
+values of $\gamma_{\mathrm{z}}(\omega,\alpha) = 65.5^{\circ} \pm 0.5^{\circ}$.
+In this panel the green circled box indicates the value for which the
+polarization angle and the response direction angle are collinear corresponding
+to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in
+a value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
 82.3$\,Km/s indicated by the upward green arrow.
@@
 response has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-24.8$\,Km/s indicated by the blue downward arrow.
+24.8$\,Km/s indicated by the blue downward arrow.}
 % 
 Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we
-have that a local maximum of the response is obtained for an incoming beam with
-energy of 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in
-a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This
-comes from a major contribution of the
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component being directed in a
-velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first
-Cartesian Quadrant on the $xy$ plane, for the spin polarized in the $z$
-direction.
-% 
-Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found that the
-velocity angle is almost constant at $78^{\circ}$ and has variations of
-$1^{\circ}$ for polarization angles between $0^{\circ}$ and $100^{\circ}$. In
+have that the most intense local maximum of the response is obtained for an
+incoming beam with energy of 1.972\,eV and same polarization angle
+$\alpha=40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes from
+a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component
+being directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
+78^{\circ}$ on the first Cartesian Quadrant on the $xy$ plane.
+% 
+{\color{red} Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found
+that the velocity angle is almost constant at $78^{\circ}$ and has variations of
+$1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq 100^{\circ}$. In
 this range the green circled box indicates the value for which the polarization
@@
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=9.0$\,Km/s indicated with
-the blue upward arrow.
+the blue upward arrow.}
 % 
@@
 
-For the \emph{alt} structure we analyzed the energy range for the incident beam
+In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
 from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
 maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
-obtained.
-% 
-In Fig. \ref{fig:alt-3d-vsb} we present the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra for the \emph{alt}
-structure.
-% 
+obtained for the \emph{alt} structure .
 % From this figure we found that the zone where the absolute maximum response is
@@
 % 
-From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have that the
-absolute maximum response is obtained for an incoming beam with polarization
-angle $\alpha=145^{\circ}$ reaching a velocity of
+{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
+that the absolute maximum response is obtained for an incoming beam with
+polarization angle $\alpha=145^{\circ}$ reaching a velocity of
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
@@
 Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
-velocity angle has small variations being centered at $51.5^{\circ}$ and having
-variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
+velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
+2^{\circ}$ for the polarization angle range $0^{\circ} \leq
 \alpha \leq 180^{\circ}$.
 % 
-Again the circled box indicates the collinear angle (Eq.
-\eqref{eq:gamma-par}) corresponding to
-$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 53.5^{\circ}$ corresponding a
-value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the
-blue square box indicates the perpendicular angles corresponding values
+As made in the previous analysis the circled box indicates the collinear angle
+(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
+53.5^{\circ}$ corresponding a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
+square box indicates the perpendicular angles corresponding values
 $\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
-with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.
+with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.}
 % 
@@
 of the \emph{alt} structure was calculated but the plots are not presented here.
-The absolute maxima for the case when the spin polarization is directed in the
+The absolute maxima for the cases when the spin polarization are directed in the
 $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
@@
 
-Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
+{\color{red} Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
 $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response and made the analysis for
@@
 $\varphi_{\mathrm{a}}(\omega,\alpha)$ angles where the spin polarization is
-directed.
+directed.}
 
@@
 % %%%%%%%%%%%%%%%%%
-In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present
+In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present the
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ resulting from evaluate the Eq.
-\eqref{eq:vv-mag} in the energy range from 0.00\,eV to 0.16\,eV for the
-\emph{up} structure.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ spectra resulting from evaluate the
+Eq. \eqref{eq:vv-mag} in the energy range for the incoming beam from 0.00\,eV to
+0.16\,eV for the \emph{up} structure.
 %
@@
 
-In the top frames of top and bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we
-present in solid lines the results of
+In the top frames of top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-1}
+we present in solid lines the results of
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
@@
 corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
-$\varphi_{a}(\omega,\alpha)$ spin angles related to the right scale. Also, in
-the bottom frames we present the corresponding components
-$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
+$\varphi_{a}(\omega,\alpha)$ spin polarization angles related to the right
+scale. Also, in the bottom frames of the panels we present the corresponding
+components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
 $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
@@
 From the top panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that for an
-incoming bean of energy 0.088\,eV the three components have similar
+incoming bean with energy of 0.088\,eV the three components have similar
 contributions with values of
@@
 % 
-To this value corresponds the polar and azimuthal spin
+{\color{red} To this value corresponds polar and azimuthal spin polarization
 angles of $\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upper
-the third Cartesian Quadrant of the $xy$ plane. Also from this figure we have
-that those angle values are held for almost all the peak of the response having
-a variation of $\pm 2^{\circ}$.
+$\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upward
+the third Cartesian quadrant of the $xy$ plane.
+% 
+Also from this figure we have that those angles values are held for almost all
+the peak of the response having variations of $\pm 2^{\circ}$ each one.
 % 
 Now, from the bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that the
-$\mathrm{yx}$ and $\mathrm{yy}$ components have less contributions for the total
-response than the $\mathrm{yz}$ and for the same incoming beam energy the
-components have values of
+components have contributions of
 % 
@@
 This value is the absolute maximum obtained when the spin-velocity is fixed in
-the $y$ direction and is 1.5 times more intense than
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$. For this absolute maximum
-corresponds spin polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha)
-= 8^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 133^{\circ}$ being
-directed the spin almost perpendicularly over the $xy$ plane and  localized on
-the first Cartesian Quadrant. 
+the $\mathrm{y}$ direction and is 1.5 times more intense than the maximum of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this absolute
+maximum corresponds spin polarization polar and azimuthal angles
+$\theta_{\mathrm{y}}(\omega,\alpha) = 8^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 133^{\circ}$ being directed the spin
+almost perpendicularly over the $xy$ plane and  localized on the first Cartesian
+quadrant.}
 % 
 In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case
-only the polar angle is hold at $8^{\circ}$ for the peak of the response having
-variations of $\pm 2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$
-to $176^{\circ}$ having a value of $133^{\circ}$ for the maximum.
+for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is held
+at $8^{\circ}$ for the peak of the response having variations of $\pm 2^{\circ}$
+but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$ having a
+value of $133^{\circ}$ for the maximum.
 % 
 We also found that since the onset of the response till an energy for the
-incoming beam of 0.118\,eV the components of both responses,
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, have no change in the spin
-polarization direction. Finally, after this energy value the responses go to
-zero.
+incoming beam of 0.118\,eV the components of both responses, have no change in
+the spin polarization-velocity direction. Finally, after this last energy value
+the responses go to zero.
 % %%%%%%%%%%%%%%%%%
@@
 Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV, corresponding to visible radiation, presented
-in Fig. \ref{fig:up-3d-vva-2} where two local maxima of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are obtained for the \emph{up}
-structure.
-% 
-We found that the two local maxima are obtained for an energy of the incident
-beam energies of 1.934\,eV and 1.972\,eV fixing again the polarization angle to
-$40^{\circ}$. 
+1.80\,eV to 2.10\,eV, corresponding to visible radiation, presented in Fig.
+\ref{fig:up-3d-vva-2} where two local of both responses are obtained for the
+\emph{up} structure for energies of 1.934\,eV and 1.972\,eV
+fixing again the polarization angle to $40^{\circ}$.
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-In the top frames of top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2}
-we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
-the polarization angle to $\alpha=40^{\circ}$ for which the response is
-maximized for the \emph{up} structure. In the same panels and frames we present
-in dashed lines the corresponding polar ($\theta_{\mathrm{x}}(\omega,\alpha)$
-and $\theta_{\mathrm{y}}(\omega,\alpha)$) and azimuthal
-($\varphi_{\mathrm{x}}(\omega,\alpha)$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale and  In
-the bottom frames the corresponding response components.
-% 
-We found that for both cases the components have similar contributions for the
-corresponding response and for an incoming energy beam of 1.934\,eV  we have the
-first local maximum resulting in a value of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the $x$ direction
-with polar and azimuthal spin polarization angles
+{\color{red} We found that for both cases the components have similar contributions for each
+response and for 1.934\,eV result in values of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 6.6$\,Km/s for the spin velocity
+moving along the $x$ direction with polar and azimuthal spin polarization angles
 $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
 $\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin directed over
-the first Cartesian Quadrant of the $xy$ plane.
-% 
-For the spin moving along the $y$ direction we have a value of
+the first Cartesian quadrant of the $xy$ plane;
+% 
+for the spin moving along the $\mathrm{y}$ direction we have a response
 $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=28.7$\,Km/s with polar and azimuthal
-angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
+spin polarization angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
 $\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ being  the spin directed over
-the first Cartesian Quadrant of the $xy$ plane.
+the first Cartesian quadrant of the $xy$ plane.
 % 
@@
 intense local maxima for which all the components have similar contributions for
-the corresponding response resulting in values of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=9.9$\,Km/s and spin polarization
-angles $\theta_{\mathrm{x}}(\omega,\alpha)=129^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being the spin directed
-downward the third Cartesian Quadrant of the $xy$ plane.
-% 
-For the spin moving in the $y$ direction we have a value of
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=49.4$\,Km/s with spin polarization
-angles $\theta_{\mathrm{y}}(\omega,\alpha)=127^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ and the spin being
-directed downward the third Cartesian Quadrant of the $xy$ plane.
+both responses.
+% 
+This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 9.9$\,Km/s
+and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with spin
+polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,
+$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$,
+$\theta_{\mathrm{y}}(\omega,\alpha) = 127^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being the spin directed
+downward the third Cartesian quadrant of the $xy$ plane when it moves in the $x$
+direction and downward the third Cartesian quadrant when it moves along the $y$
+direction.}
 % 
@@
 till an energy of the incoming beam equal to 1.954\,eV when the spin
-polarization ad current changes the direction and after an energy for the
-incoming beam equal to 2.05\,eV both responses goes to zero.
+polarization and current changes the direction. After an energy of 2.05\,eV both
+responses goes to zero.
 
@@
 % %%%%%%%%%%%%%%%%%
-For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
-1.0\,eV, corresponding to the NIR radiation, where we found a local maxima and
-the most intense responses for $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$; the corresponding spectra is
-shown in Fig. \ref{fig:alt-3d-vva}.
+{\color{red} For the \emph{alt} structure we analyzed the energy range from
+0.6\,eV to 1.0\,eV in Fig. \ref{fig:alt-3d-vva}, corresponding to the NIR
+radiation, where we found a local maxima and the most intense responses for
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$.}
 %
@@
 present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
-the polarization angle to $\alpha=145^{\circ}$. In the same figures and frames
-we present the spin polarization angles related to the right scale and in the
-bottom frames the corresponding three components.
-% 
-Making the analysis for the components and angles when the spin current is
-directed in the $x$ direction, corresponding to the top panel of Fig.
-% 
-\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
-is 0.720\,eV we have similar contributions from all the components resulting in
-a response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=19.4$\,Km/s and polar
-and azimuthal spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) =
-46^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 41^{\circ}$ being the
-spin directed over the first Cartesian Quadrant of the $xy$ plane;
-% 
-then, for an energy of 0.912\,eV we have a major contribution from the
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component resulting in a total
-response of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s being this
-value the absolute maximum when the spin velocity is directed in the $x$
-Cartesian direction. The corresponding polar and azimuthal angles are
-$\theta_{\mathrm{x}}(\omega,\alpha)=154^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=290^{\circ}$ being the spin directed
-downward the fourth Cartesian Quadrant of the $xy$ plane.
-% 
-Making now the analysis for the components and angles when the spin current is
-directed along the $y$ direction, corresponding to the bottom panel of Fig.
-\ref{fig:alt-vab-comp-rtp}, we found that when the energy of the incoming beam
-is 0.720\,eV we have more contribution from the
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component and the response has a
-value of $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 51.9$\,Km/s corresponding
-the polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha) =
-141^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 222^{\circ}$ being the
-spin directed downward the third Cartesian Quadrant of the $xy$ plane.
-% 
-For the peak centered at 0.912\,eV we have similar contributions of all the
-components resulting in a response $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| =
-52.3$\,Km/s being this the absolute maximum response for the \emph{alt}
-structure. The corresponding angles are $\theta_{\mathrm{y}}(\omega,\alpha) =
-129^{\circ}$ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 229^{\circ}$ being the
-spin directed downward the third Cartesian Quadrant of the $xy$ plane.
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ fixing the polarization angle to
+$\alpha=145^{\circ}$ for which the response is maximized and its corresponding
+polar and azimuthal angles; in the bottom frames of same panels we present the
+corresponding three components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
+$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
+% 
+{\color{red} Making the analysis when the energy of the incoming beam is
+0.720\,eV we have similar contributions from the components when the sping
+velocity is along the $x$ diection and a major contribution from
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ when the spin velocity is dierected
+alog $y$ Cartesian axis. This result in values of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 19.4$\,Km/s and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 51.9$\,Km/s with spin polarization
+angles $\theta_{\mathrm{x}}(\omega,\alpha) = 46^{\circ}$,
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 41^{\circ}$,
+$\theta_{\mathrm{y}}(\omega,\alpha) = 141^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 222^{\circ}$ being the spin polarization
+directed over the first Cartesian quadrant of the $xy$ plane when the spin
+velocity is directed along $x$ and directed downward the third Cartesian
+quadrant when the spin velocity is directed along $y$.
+% 
+Then, for an energy of 0.912\,eV we have values of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 52.3$\,Km/s. The first of them have
+a major contribution from the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
+component and the second one having similar contributions from all of three
+components. They result in polar and azimuthal angles
+$\theta_{\mathrm{x}}(\omega,\alpha) = 154^{\circ}$,
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 290^{\circ}$,
+$\theta_{\mathrm{y}}(\omega,\alpha) = 129^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 229^{\circ}$ being the spin polarization
+directed downward the fourth Cartesian quadrant of the $xy$ plane when the spin
+velocity is directed along $x$ and downward the third Cartesian quadrant of the
+$xy$ plane when the spin velocity is directed along $y$.}
 % 
@@
 
-The structures presented here where divided into layers to analyze the he
-layer-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The
-\emph{alt} structure was divided in six layers corresponding the first one to
-the top hydrogen atoms, from the second to the forth to carbon atoms in
-different $z$ positions, and the sixth and last one to the bottom hydrogen
-atoms. The \emph{up} structure was divided into two layers, the first one
-comprised by the top hydrogen atoms and the second by the carbon atoms. The
-layer divisions and atom positions for the unit cells are shown in Tables
-\ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.
+{\color{blue} As mentioned before in in the beginning of this section the
+\emph{up} and \emph{alt} structures presented here was divided into layers to
+analyze the layer-by-layer contribution for
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. Here we present the decomposition
+only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and for the
+corresponding components of the \emph{up} structure in Figs. 
+% 
+\ref{fig:up-vsz-lay-1} and \ref{fig:up-vsz-lay-2} and for the \emph{alt}
+structure in Fig. \ref{fig:alt-vsz-lay}. The
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented in those
+figures is the same than the presented in top frames of Figs. 
+% 
+\ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the layered
+responses.
+% 
+}
+% 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-1}
+
+    \caption{Layer-by-layer contribution of the
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
+    for the \emph{up} structure as a function of the polarization angle $\alpha$
+    for the energy fixed to 0.088\,eV for which the absolute maximum is
+    obtained.
+    % 
+    The corresponding layered contributions for the
+    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
+    central and bottom frames.}
+    \label{fig:up-vsz-lay-1}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-2}
+
+    \caption{Layer-by-layer contribution of the
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
+    for the \emph{up} structure as a function of the polarization angle $\alpha$
+    for the energy fixed to 1.972\,eV for which a local maximum is obtained.
+    % 
+    The corresponding layered contributions for the
+    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
+    central and bottom frames.}
+    \label{fig:up-vsz-lay-2}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay}
+
+\caption{Layer-by-layer contribution of the
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
+    for the \emph{alt} structure as a function of the polarization angle
+    $\alpha$ for the energy fixed to 0.912\,eV for which the absolute maximum is
+    obtained.
+    % 
+    The corresponding layered contributions for the
+    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
+    central and bottom frames.}
+    \label{fig:alt-vsz-lay}
+\end{figure}
+%
 
 % %%%%%%%%%%%%%%%%
-% %% Description of Up layer |V^{yz}|
+% %% Description of Up layer |V_{s^z}|
 % %%%%%%%%%%%%%%%%
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}
-    \label{fig:up-vyz-lay-1}
-    \\
-    \includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}
-    \label{fig:up-vyz-lay-2}
-
-    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
-     \emph{up} structure.}
-    \label{fig:up-vyz-lay}
-\end{figure}
-
-From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
-% 
-\ref{fig:up-vab-comp-rtp-2} we can see that for the \emph{up} structure again
-the most intense component of $|\mathcal{V}^{\mathrm{x}}|$ and
-$|\mathcal{V}^{\mathrm{y}}|$ corresponds to $\mathcal{V}^{\mathrm{yz}}$ which
-has a value of 87.2\,Km/s for an energy incident beam of 0.088\,eV and
--29.7\,Km/s for an energy incident beam of 1.972\,eV. This component and the
-corresponding layer by layer contribution is depicted in Fig. 
-\ref{fig:up-vyz-lay}s.
-% 
-From this figure we have that for the energy range from 0\,eV to 0.2\,eV the
-response comes from the second layer composed by carbon atoms presented in Tab.
-\ref{tab:up-unitcell} and denoted by the number 2 in Fig. \ref{fig:up-struc}. In
-the other hand, the response for the energy range from 1.8\,eV to 2.1\,eV almost
-all the response comes from the carbon atoms having a leaser contribution from
-the hydrogen layer.
+{\color{blue}
+From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1} we have that
+when the energy is fixed to 0.088\,eV almost all the response of the
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second layer
+comprised by carbon atoms having a minimal reduction produced by the hydrogen
+layer. Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response, presented
+in bottom frame of same figure, is produced only by the carbon layer. This
+result in a total response $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+95.8$\,Km/s coming from the carbon layer and being minimally reduced by the
+hydrogen layer as shown in the top frame of this figure.
+% 
+Now, for the same structure but now fixing the energy to 1.972\,eV we have from
+the central frame of Fig. \ref{fig:up-vsz-lay-2} that the the carbon layer
+produces the response of the $\mathcal{V}^{\mathrm{zx}}(\omega,\alpha)$
+component being decreased by the hydrogen layer. Opposite to that, in the bottom
+frame of same figure we obtained that the response of the carbon and hydrogen
+layer are not inverse and then contributing both to the total response of
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
+figure we have that the major contribution to the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ comes from the carbon layer
+with but being in this case reinforced by the contribution of the hydrogen layer
+and resulting in a value of 30.3\,Km/s}
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
-the \emph{alt} structure the most intense component of
-$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
-$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
-energy incident beam of 0.72\,eV. This component and the corresponding layer by
-layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
-we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
-layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
-Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
-4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
-for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
-from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
-in the same direction resulting in a total response
-$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
-0.912\,eV.
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
-
-    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
-     \emph{alt} structure.}
-    \label{fig:alt-vyz-lay}
-\end{figure}
+{\color{blue}
+Finally, for the \emph{alt} structure we have that the six layers contribute
+with similar magnitudes and reinforce the
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components resulting in a total
+response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 43$\,Km/s.
+}
 

### 2017-06-01 mu/article/article.tex
ChWS

@@
 
-\blindtext
 \begin{figure}[ht!]
@@
 \end{figure}
-\blindtext
-\blindtext
-
-\blindtext
+
+Since its discovery, graphene has attracted a great interest in materials
+science and condensed matter physics being a new class of materials that are
+only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
+lattice structure is almost transparent and presents properties like fractional
+quantum Hall effect at room temperature, excellent thermal transport properties,
+high conductivity and strength.\cite{geimNM07, reinaNL08, novoselov2S07,
+balandinNL08} Presenting a metallic band structure the band gap can be opened by changing the surface area\cite{hanPRL07}
 

### 2017-06-01 mu/article/article.tex
ChWS

--- 2017-05-31 mu/article/article.tex
@@
 \end{figure}
-\blindtext
-\blindtext
-
-\blindtext
+
+Since its discovery, graphene has attracted a great interest in materials
+science and condensed matter physics being a new class of materials that are
+only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
+lattice structure is almost transparent and presents properties like fractional
+quantum Hall effect at room temperature, excellent thermal transport properties,
+high conductivity and strength.\cite{geimNM07, reinaNL08, novoselov2S07,
+balandinNL08} Graphene has a metallic band structure but the band gap can be
+opened by applying uniaxial strain \cite{niACSN08}, changing the surface
+area\cite{hanPRL07} or applying an electric field \cite{zhangN09}. Another option to open the gap is by doping the structure with
 

### 2017-06-01 mu/article/article.tex
Writing introduction.

--- 2017-05-31 mu/article/article.tex
@@
 \end{figure}
-\blindtext
-\blindtext
-
-\blindtext
+
+Since its discovery, graphene has attracted a great interest in materials
+science and condensed matter physics being a new class of materials that are
+only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
+lattice structure is almost transparent and presents properties like fractional
+quantum Hall effect at room temperature, excellent thermal transport
+properties, high conductivity and strength \cite{geimNM07, reinaNL08,
+novoselov2S07, balandinNL08} and is a perfect platform to be used in two-
+dimensions electronic systems; however most electronic applications are
+disabled by the absence of a semiconducting gap. Recent studies demonstrate
+that the band gap of graphene can be opened by applying an electric
+field\cite{zhangN09}, reducing the surface area\cite{hanPRL07} or applying
+uniaxial strain\cite{niACSN08}. Another option to open the gap is by doping;
+this has been successfully achieved using boron and nitrogen\cite{guoIJ11} and
+hydrogen\cite{eliasS09, guisingerNL09, samarakoonACSN10}.
+
+Hydrogenated graphene can result in different structures depending of the
+percentage of hydrogenation and the position at which they are bonded in the
+hexagonal lattice. In this paper we present a study made on two 50\%
+hydrogenated graphene structures, \emph{up} and \emph{alt} , both showing a
+opening of the gap. As shown in Figs. \ref{fig:up-struc} and 
+\ref{fig:alt-struc} the \emph{up} structure has hydrogen atoms bonded to the
+carbon layer only in the upper side of the structure while the \emph{alt}
+structure has hydrogen alternating in the upper and bottom sides of the carbon
+slab.
+
+We conduct a theoretical study of the spin velocity injection, being this a
+nonlinear response, in both structures. We analyze particularly the cases when
+the spin is polarized along a Cartesian direction or when the velocity is
+directed along the $x$ or $y$ directions on the $xy$ plane of the structures.
 
@@
 \color{red}
-where the
-roman superscripts denote Cartesian components corresponding $\mathrm{a}$ to the
-spin velocity direction and $\mathrm{b}$ to the spin polarization direction, can
-be written in terms of a material response pseudotensor
-$\mu^{\mathrm{abcd}}(\omega)$ as
-}
+where the roman superscripts denote Cartesian components corresponding
+$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
+polarization direction, can be written in terms of a material response
+pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as }
 \begin{equation*}
@@
 \end{align}
-where the angle is measured in the counter-clockwise direction from the positive
-$x$ Cartesian coordinate. 
-{\color{red}
-We also define two special angles
+where the angle is measured in the counter-clockwise direction from the
+positive $x$ Cartesian coordinate. {\color{red} We also define two special
+angles
 \begin{align}
@@
 The first corresponds to the case when the spin velocity is directed, on the
-$xy$ plane in the same direction of the polarization angle of the incoming beam;
-the second one corresponds to the case when the spin velocity is directed
-perpendicularly respect to the polarization angle of the incoming beam.
-}
+$xy$ plane in the same direction of the polarization angle of the incoming
+beam; the second one corresponds to the case when the spin velocity is directed
+perpendicularly respect to the polarization angle of the incoming beam. }
 
@@
 
-{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab} is fixing the velocity on
-the $xy$ plane along $x$ or $y$ Cartesian coordinate and then define the
-magnitude of the spin velocity directed along the $\mathrm{a}$ direction as}
+{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab} is fixing
+the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
+define the magnitude of the spin velocity directed along the $\mathrm{a}$
+direction as}
 \begin{align}
@@
 We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ and
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ for the C$_{16}$H$_{8}$-alt
-and C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
-carbon systems with 50\% hydrogenation in different arrangements. The \emph{up}
-structure has hydrogen atoms only on the upper side of the carbon sheet while
-the \emph{alt} structure has alternating hydrogen atoms on the upper and bottom
-sides. We take the hexagonal carbon lattice to be on the $xy$ plane for both
-structures, and the carbon-hydrogen bonds on the perpendicular $xz$ plane, as
-depicted in Figs. \ref{fig:alt-struc} and \ref{fig:up-struc}
-% 
-{\color{blue} and the coordinates for the \emph{up} and \emph{alt} unit cells of
-the structures are presented in Tables \ref{tab:up-unitcell} and
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ for the
+C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
+noncentrosymmetric semi-infinite 2D carbon systems with 50\% hydrogenation in
+different arrangements. The \emph{up} structure has hydrogen atoms only on the
+upper side of the carbon sheet while the \emph{alt} structure has alternating
+hydrogen atoms on the upper and bottom sides. We take the hexagonal carbon
+lattice to be on the $xy$ plane for both structures, and the carbon-hydrogen
+bonds on the perpendicular $xz$ plane, as depicted in Figs. \ref{fig:alt-struc}
+and \ref{fig:up-struc}
+% 
+{\color{blue} and the coordinates for the \emph{up} and \emph{alt} unit cells
+of the structures are presented in Tables \ref{tab:up-unitcell} and
 % 
@@
 % 
-\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was divided
-in two layers, the first comprised of the top hydrogen atoms denoted by the
-number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc} and
-the second comprised of carbon atoms and denoted by the number 2. The \emph{alt}
-structure was divided in six layers denoted with numbers from 1 to 6 in Table
-\ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and sixth
-layers correspond to hydrogen atoms in the top and bottom positions and from the
-second to the fifth correspond to carbon atoms placed in different positions.}
+\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was
+divided in two layers, the first comprised of the top hydrogen atoms denoted by
+the number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc}
+and the second comprised of carbon atoms and denoted by the number 2. The
+\emph{alt} structure was divided in six layers denoted with numbers from 1 to 6
+in Table \ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and
+sixth layers correspond to hydrogen atoms in the top and bottom positions and
+from the second to the fifth correspond to carbon atoms placed in different
+positions.}
 
@@
 computational cost and is out of the scope in this paper. Even so, DFT still
-remains as an effective and useful tool for computing diverse properties derived
-from the electronic band structure.}
+remains as an effective and useful tool for computing diverse properties
+derived from the electronic band structure.}
 
@@
 
-    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
-    for 2D \emph{alt} and \emph{up}, and bulk CdSe and GaAs structures and the
-    corresponding polarization angles.}
+    \caption{Comparison of most intense responses of
+    $\mathcal{V}^{\mathrm{ab}}$ for 2D \emph{alt} and \emph{up}, and bulk CdSe
+    and GaAs structures and the corresponding polarization angles.}
     \label{fig:vab-str-comp}
@@
 % 
-From the figure we have that the onset of the response starts when the energy of
-the incoming beam is the same of the gap energy.
+From the figure we have that the onset of the response starts when the energy
+of the incoming beam is the same of the gap energy.
 % 
@@
 In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the {\color{red} Near Infrared (NIR) to visible radiation}, all the four
-structures have contributions in the same order of magnitude.
-% 
-For this energy range the \emph{up} structure has two peaks centered at 1.94\,eV
-and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s,
+to energies of the {\color{red} Near Infrared (NIR) to visible radiation}, all
+the four structures have contributions in the same order of magnitude.
+% 
+For this energy range the \emph{up} structure has two peaks centered at
+1.94\,eV and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s,
 respectively, and the \emph{alt} structure has two peaks centered at 0.72\,eV
@@
 GaAs structure has a large and almost planar zone where the response is held
-reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
-a spin velocity of -21.6\,Km/s.
-% 
-{\color{red} A negative quantity in the spin velocity means a change in the spin
-polarization traveling in the opposite direction.
-% 
-In table \ref{tab:vab-str-comp} we present the comparison of this values for the
-2D and bulk structures. We found that the most intense response for the spin
-velocity corresponds to the \emph{up} structure being 3.25 times more intense
-than that of the CdSe and 4.03 times more intense than that of the GaAs bulk
-structures. Also, the \emph{alt} structure has a response more intense than the
-bulk systems but being less intense than the corresponding to the \emph{up}
-one.}
+reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting
+in a spin velocity of -21.6\,Km/s.
+% 
+{\color{red} A negative quantity in the spin velocity means a change in the
+spin polarization traveling in the opposite direction.
+% 
+In table \ref{tab:vab-str-comp} we present the comparison of this values for
+the 2D and bulk structures. We found that the most intense response for the
+spin velocity corresponds to the \emph{up} structure being 3.25 times more
+intense than that of the CdSe and 4.03 times more intense than that of the GaAs
+bulk structures. Also, the \emph{alt} structure has a response more intense
+than the bulk systems but being less intense than the corresponding to the
+\emph{up} one.}
 %
@@
     \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
-    range, and two local maxima from 1.90\,eV to 1.93\,eV and from 1.96\,eV to
-    2.0\,eV, in the visible radiation range, all for polarization angles between
-    $25^{\circ}$ and $50^{\circ}$.}
+    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared
+    radiation range, and two local maxima from 1.90\,eV to 1.93\,eV and from
+    1.96\,eV to 2.0\,eV, in the visible radiation range, all for polarization
+    angles between $25^{\circ}$ and $50^{\circ}$.}
     \label{fig:up-3d-vsz}   
@@
     components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-    $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ (bottom frames) for the \emph{up}
-    structure fixing the energy to 0.088\,eV. }
+    $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ (bottom frames) for the
+    \emph{up} structure fixing the energy to 0.088\,eV. }
     \label{fig:up-vaz-rag}
@@
 analysis for the case when the spin is fixed in the $z$ coordinate, directed
-perpendicularly to the surface of the \emph{up} and \emph{alt} structures. Also,
-using the Eq. \eqref{eq:gamma-ang}, we determined the angle
+perpendicularly to the surface of the \emph{up} and \emph{alt} structures.
+Also, using the Eq. \eqref{eq:gamma-ang}, we determined the angle
 $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
@@
 \emph{up} structure, the first for an incoming energy beam from 0.0\,eV to
-0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR) radiation,
-where the absolute maximum of the
+0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR)
+radiation, where the absolute maximum of the
 $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained, and
@@
 $45^{\circ}$. Also the two local maxima are held for same beam polarization
-angles but for an energy range between 1.90\,eV and 2.05\,eV.
-In the top frames of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we
-present in solid lines the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related to the left scale,
-fixing the energy of the incoming beam to 0.088\,eV and 1.972\,eV, respectively,
-values for which the response is maximized for the \emph{up} structure. In the
-same panels and frames we present in dashed lines, related to the right scale,
-the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$, and in
-the bottom frames of the panels we present the corresponding components
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
+angles but for an energy range between 1.90\,eV and 2.05\,eV. In the top frames
+of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we present in solid lines
+the result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$,
+related to the left scale, fixing the energy of the incoming beam to 0.088\,eV
+and 1.972\,eV, respectively, values for which the response is maximized for the
+\emph{up} structure. In the same panels and frames we present in dashed lines,
+related to the right scale, the corresponding velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha)$, and in the bottom frames of the panels we
+present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
+and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
 square boxes indicating the values where the angles of the spin velocity are
@@
 polarization angle and the response direction angle are collinear corresponding
-to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in
-a value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-82.3$\,Km/s indicated by the upward green arrow.
+to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting
+in a value of the response of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s indicated by
+the upward green arrow.
 % 
@@
 % 
-Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we
-have that the most intense local maximum of the response is obtained for an
+Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag}
+we have that the most intense local maximum of the response is obtained for an
 incoming beam with energy of 1.972\,eV and same polarization angle
 $\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes from
-a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component
-being directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
-78^{\circ}$ on the first Cartesian Quadrant on the $xy$ plane.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
+from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
+component being directed in a velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha) = 78^{\circ}$ on the first Cartesian
+Quadrant on the $xy$ plane.
 % 
 {\color{red} Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found
-that the velocity angle is almost constant at $78^{\circ}$ and has variations of
-$1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq 100^{\circ}$. In
-this range the green circled box indicates the value for which the polarization
-angle and the response direction angle are collinear corresponding to
-$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ and having a
-response value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-23.5$\,Km/s indicated with the green upward arrow.
+that the velocity angle is almost constant at $78^{\circ}$ and has variations
+of $1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq
+100^{\circ}$. In this range the green circled box indicates the value for which
+the polarization angle and the response direction angle are collinear
+corresponding to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$
+and having a response value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 23.5$\,Km/s indicated
+with the green upward arrow.
 % 
@@
     \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frame, left scale)
-    the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame,
-    right scale), the collinear (circled box) and perpendicular (square box)
-    angles, and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
+    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frame, left
+    scale) the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top
+    frame, right scale), the collinear (circled box) and perpendicular (square
+    box) angles, and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
     $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
@@
 obtained for the \emph{alt} structure .
-% From this figure we found that the zone where the absolute maximum response is
-% held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
-% angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
-% is obtained for the same polarization angles but for energies between 0.67\,eV
-% and 0.75\,eV.
+% From this figure we found that the zone where the absolute maximum response
+% is held corresponds to a energy range from 0.90\,eV to 0.93\,eV and
+% polarization angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a
+% local maximum is obtained for the same polarization angles but for energies
+% between 0.67\,eV and 0.75\,eV.
 % %%%%%%%%%%%%%%%%%
@@
 Again, for the cases in which the spin polarization is parallel to the surface
-of the \emph{alt} structure was calculated but the plots are not presented here.
-The absolute maxima for the cases when the spin polarization are directed in the
-$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
-incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
-resulting in values of
+of the \emph{alt} structure was calculated but the plots are not presented
+here. The absolute maxima for the cases when the spin polarization are directed
+in the $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of
+the incoming beam equal to 0.912\,eV and polarization angle
+$\alpha=145^{\circ}$ resulting in values of
 $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
@@
     angles (top frames right scale), and the corresponding three components
-    (bottom frames) for the \emph{up} structure fixing the polarization angle to
-    $\alpha=40^{\circ}$ to maximize the response.}
+    (bottom frames) for the \emph{up} structure fixing the polarization angle
+    to $\alpha=40^{\circ}$ to maximize the response.}
     \label{fig:up-vab-comp-rtp-1}
@@
 $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ spectra resulting from evaluate the
-Eq. \eqref{eq:vv-mag} in the energy range for the incoming beam from 0.00\,eV to
-0.16\,eV for the \emph{up} structure.
+Eq. \eqref{eq:vv-mag} in the energy range for the incoming beam from 0.00\,eV
+to 0.16\,eV for the \emph{up} structure.
 %
@@
     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
-    the photon energy and polarization angle $\alpha$ for the \emph{up}
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
+    of the photon energy and polarization angle $\alpha$ for the \emph{up}
     structure. Two local maxima of both responses are localized in the energy
-    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the visible
-    radiation range, and for polarization angles between $25^{\circ}$ and
-    $50^{\circ}$.}
+    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the
+    visible radiation range, and for polarization angles between $25^{\circ}$
+    and $50^{\circ}$.}
     \label{fig:up-3d-vva-2}
@@
     angles (top frames right scale), and the corresponding three components
-    (bottom frames) for the \emph{up} structure fixing the polarization angle to
-    $\alpha=40^{\circ}$ to maximize the response.}
+    (bottom frames) for the \emph{up} structure fixing the polarization angle
+    to $\alpha=40^{\circ}$ to maximize the response.}
 
@@
 the $\mathrm{y}$ direction and is 1.5 times more intense than the maximum of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this absolute
-maximum corresponds spin polarization polar and azimuthal angles
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this
+absolute maximum corresponds spin polarization polar and azimuthal angles
 $\theta_{\mathrm{y}}(\omega,\alpha) = 8^{\circ}$ and
 $\varphi_{\mathrm{y}}(\omega,\alpha) = 133^{\circ}$ being directed the spin
-almost perpendicularly over the $xy$ plane and  localized on the first Cartesian
-quadrant.}
+almost perpendicularly over the $xy$ plane and  localized on the first
+Cartesian quadrant.}
 % 
 In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case
-for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is held
-at $8^{\circ}$ for the peak of the response having variations of $\pm 2^{\circ}$
-but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$ having a
-value of $133^{\circ}$ for the maximum.
+for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is
+held at $8^{\circ}$ for the peak of the response having variations of $\pm
+2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$
+having a value of $133^{\circ}$ for the maximum.
 % 
@@
 % %%%%%%%%%%%%%%%%
-{\color{red} We found that for both cases the components have similar contributions for each
-response and for 1.934\,eV result in values of
+{\color{red} We found that for both cases the components have similar
+contributions for each response and for 1.934\,eV result in values of
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 6.6$\,Km/s for the spin velocity
-moving along the $x$ direction with polar and azimuthal spin polarization angles
-$\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
+moving along the $x$ direction with polar and azimuthal spin polarization
+angles $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
 $\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin directed over
@@
 Alike, for an incoming energy beam of 1.972\,eV we found the second and more
-intense local maxima for which all the components have similar contributions for
-both responses.
-% 
-This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 9.9$\,Km/s
-and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with spin
-polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,
+intense local maxima for which all the components have similar contributions
+for both responses.
+% 
+This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| =
+9.9$\,Km/s and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with
+spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,
 $\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$,
@@
 $\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being the spin directed
-downward the third Cartesian quadrant of the $xy$ plane when it moves in the $x$
-direction and downward the third Cartesian quadrant when it moves along the $y$
-direction.}
+downward the third Cartesian quadrant of the $xy$ plane when it moves in the
+$x$ direction and downward the third Cartesian quadrant when it moves along the
+$y$ direction.}
 % 
@@
 till an energy of the incoming beam equal to 1.954\,eV when the spin
-polarization and current changes the direction. After an energy of 2.05\,eV both
-responses goes to zero.
+polarization and current changes the direction. After an energy of 2.05\,eV
+both responses goes to zero.
 
@@
     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
-    the photon energy and polarization angle $\alpha$ for the \emph{alt}
-    structure. The local and the absolute maxima are located in the
-    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
+    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
+    of the photon energy and polarization angle $\alpha$ for the \emph{alt}
+    structure. The local and the absolute maxima are located in the energy
+    ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
     respectively, and both in the Near Infrared and for polarization angles
@@
 % %%%%%%%%%%%%%%%%
-In the top frames of top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we
-present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+In the top frames of top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp}
+we present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
 $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ fixing the polarization angle to
@@
 $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 52.3$\,Km/s. The first of them have
-a major contribution from the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
+$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 52.3$\,Km/s. The first of them
+have a major contribution from the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
 component and the second one having similar contributions from all of three
@@
 structure in Fig. \ref{fig:alt-vsz-lay}. The
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented in those
-figures is the same than the presented in top frames of Figs. 
-% 
-\ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the layered
-responses.
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented in
+those figures is the same than the presented in top frames of Figs.
+% 
+\ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
+layered responses.
 % 
@@
     $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
-    for the \emph{up} structure as a function of the polarization angle $\alpha$
-    for the energy fixed to 0.088\,eV for which the absolute maximum is
-    obtained.
+    for the \emph{up} structure as a function of the polarization angle
+    $\alpha$ for the energy fixed to 0.088\,eV for which the absolute maximum
+    is obtained.
     % 
@@
     $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
-    for the \emph{up} structure as a function of the polarization angle $\alpha$
-    for the energy fixed to 1.972\,eV for which a local maximum is obtained.
+    for the \emph{up} structure as a function of the polarization angle
+    $\alpha$ for the energy fixed to 1.972\,eV for which a local maximum is
+    obtained.
     % 
@@
     for the \emph{alt} structure as a function of the polarization angle
-    $\alpha$ for the energy fixed to 0.912\,eV for which the absolute maximum is
-    obtained.
+    $\alpha$ for the energy fixed to 0.912\,eV for which the absolute maximum
+    is obtained.
     % 
@@
 % %%%%%%%%%%%%%%%%
-{\color{blue}
-From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1} we have that
-when the energy is fixed to 0.088\,eV almost all the response of the
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second layer
-comprised by carbon atoms having a minimal reduction produced by the hydrogen
-layer. Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response, presented
-in bottom frame of same figure, is produced only by the carbon layer. This
-result in a total response $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-95.8$\,Km/s coming from the carbon layer and being minimally reduced by the
-hydrogen layer as shown in the top frame of this figure.
+{\color{blue} From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1}
+we have that when the energy is fixed to 0.088\,eV almost all the response of
+the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
+layer comprised by carbon atoms having a minimal reduction produced by the
+hydrogen layer. Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response,
+presented in bottom frame of same figure, is produced only by the carbon layer.
+This result in a total response
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 95.8$\,Km/s coming from
+the carbon layer and being minimally reduced by the hydrogen layer as shown in
+the top frame of this figure.
 % 
@@
 produces the response of the $\mathcal{V}^{\mathrm{zx}}(\omega,\alpha)$
-component being decreased by the hydrogen layer. Opposite to that, in the bottom
-frame of same figure we obtained that the response of the carbon and hydrogen
-layer are not inverse and then contributing both to the total response of
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
+component being decreased by the hydrogen layer. Opposite to that, in the
+bottom frame of same figure we obtained that the response of the carbon and
+hydrogen layer are not inverse and then contributing both to the total response
+of $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
 figure we have that the major contribution to the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ comes from the carbon layer
-with but being in this case reinforced by the contribution of the hydrogen layer
-and resulting in a value of 30.3\,Km/s}
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ comes from the carbon
+layer with but being in this case reinforced by the contribution of the
+hydrogen layer and resulting in a value of 30.3\,Km/s}
 % %%%%%%%%%%%%%%%%

### 2017-06-09 mu/article/article.tex
Introduction completed.

@@
 
-Since its discovery, graphene has attracted a great interest in materials
-science and condensed matter physics being a new class of materials that are
-only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
-lattice structure is almost transparent and presents properties like fractional
-quantum Hall effect at room temperature, excellent thermal transport
-properties, high conductivity and strength \cite{geimNM07, reinaNL08,
-novoselov2S07, balandinNL08} and is a perfect platform to be used in two-
-dimensions electronic systems; however most electronic applications are
-disabled by the absence of a semiconducting gap. Recent studies demonstrate
-that the band gap of graphene can be opened by applying an electric
-field\cite{zhangN09}, reducing the surface area\cite{hanPRL07} or applying
-uniaxial strain\cite{niACSN08}. Another option to open the gap is by doping;
-this has been successfully achieved using boron and nitrogen\cite{guoIJ11} and
-hydrogen\cite{eliasS09, guisingerNL09, samarakoonACSN10}.
-
-Hydrogenated graphene can result in different structures depending of the
-percentage of hydrogenation and the position at which they are bonded in the
-hexagonal lattice. In this paper we present a study made on two 50\%
-hydrogenated graphene structures, \emph{up} and \emph{alt} , both showing a
-opening of the gap. As shown in Figs. \ref{fig:up-struc} and 
-\ref{fig:alt-struc} the \emph{up} structure has hydrogen atoms bonded to the
-carbon layer only in the upper side of the structure while the \emph{alt}
-structure has hydrogen alternating in the upper and bottom sides of the carbon
-slab.
-
-We conduct a theoretical study of the spin velocity injection, being this a
-nonlinear response, in both structures. We analyze particularly the cases when
-the spin is polarized along a Cartesian direction or when the velocity is
-directed along the $x$ or $y$ directions on the $xy$ plane of the structures.
+{
+\color{blue}
+Spintronics is an emerging research field of electronics in which the
+manipulation and transport of spin of electrons in a solid state 
+media plays the determining role adding a new degree of freedom to the
+conventional charge manipulation.\cite{wolfSC04,fabianAPS07}
+% 
+At present there is an increasing interest in attain the same level of control
+over the transport of spin at micro or nano scales as has been done for the flow
+of charge in typical electronic devices.\cite{awschalomNP2007} Some
+semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
+dattaAPL90} and some of them require spin polarized electrical current
+\cite{awschalomSSBM13} or pure spin currents (PSC). In PSCs there is no net
+motion of charge; spin-up electrons move in a given direction while spin-down
+electrons travel in the opposite one. This phenomena can result from spin
+injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04} interference of two
+optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon absorption of
+linearly polarized light\cite{bhatPRL05} and has been observed in
+gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
+arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
+
+% Since its discovery, graphene has attracted a great interest in materials
+% science and condensed matter physics being a new class of materials that are
+% only one atom thick\cite{geimNM07}. 
+% 
+Graphene, an allotrope of carbon with hexagonal 2D lattice structure presents
+properties like fractional quantum Hall effect at room temperature, excellent
+thermal transport properties, high conductivity and strength \cite{geimNM07,
+reinaNL08, novoselov2S07, balandinNL08} being then a perfect platform to be used
+in two-dimensions electronic systems; however most electronic applications are
+disabled by the absence of a semiconducting gap. Recent studies demonstrate that
+the band gap of graphene can be opened by applying an electric
+field,\cite{zhangN09} reducing the surface area,\cite{hanPRL07} or applying
+uniaxial strain.\cite{niACSN08} Another possibility to open the gap is by
+doping; this has been successfully achieved using nitrogen,\cite{weiNL2009}
+boron-nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-metals, and
+hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
+% 
+Depending on the percentage of hydrogenation and spatial configurations of
+hydrogen-carbon bonds, hydrogenated graphene can result in different spatial
+configurations.
+% 
+In this paper we present two 50\% hydrogenated graphene non centrosymmetric
+structures both presenting a discernible band gap: the \emph{up} structure,
+shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
+only in the upper side of the structure while the \emph{alt} structure, shown in
+Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom sides
+of the carbon slab.\cite{zapataPSB2016}
+
+Using those structures we address a theoretical study of the spin velocity
+injection (SVI) by one-photon absorption of linearly polarized light making
+emphasis for the particular cases when the spin of electrons is directed along
+the the $z$ Cartesian coordinate, perpendicular to the $xy$ plane of the
+structure, or for the case when the velocity is directed along the $x$ and $y$
+Cartesian direction on the $xy$ plane of the structures.
+% 
+The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is a nonlinear optical
+effect that quantifies the velocity at which a PSC moves along the Cartesian
+direction $\mathrm{b}$ with the spin of electron polarized along the Cartesian
+direction $\mathrm{a}$. One photon absorption of linearly polarized light can
+promote a distribution of electrons in $\mathbf{k}$ space regardless the
+symmetry of the material resulting in a not net electrical
+current. Then, the electrons excited to the conduction bands at
+opposite $\mathbf{k}$ points will result in opposite spin polarizations 
+producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
+the material is not centrosymmetric the spin polarization injected at a given k
+point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC
+will be produced since the velocities of electrons at opposite $\mathbf{k}$
+points are opposite.
+
+This paper is organized as follows. In Section \ref{sec:theory} we present the
+theory and formulas that describe PSC and SVI. In Section \ref{sec:results} we
+describe the details of calculations and the corresponding SVI spectra for the 
+\emph{up} and \emph{alt} structures. Finally, in Section
+
+}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%   C O N C L U S I O N S  %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions} % (fold)
+\label{sec:conclusions}
+
 \bibliography{article.bib}

### 2017-06-09 mu/article/article.tex
Abstracts of references added in article.abstracts

@@
 producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
-the material is not centrosymmetric the spin polarization injected at a given k
-point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC
-will be produced since the velocities of electrons at opposite $\mathbf{k}$
-points are opposite.
+the material is not centrosymmetric the spin polarization injected at a given $
+\mathbf{k}$ point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and
+then a PSC will be produced since the velocities of electrons at opposite
+$\mathbf{k}$ points are opposite.
 

### 2017-06-11 mu/article/article.tex
Completed intro redaction of Spin Velocity Injection.

@@
 \usepackage{multirow}
-% \usepackage{showframe}
+\usepackage{showframe}
 \usepackage[inline]{showlabels}
@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 
-\subsection{Pure spin velocity} % (fold)
+In this section, we report a summary of the theory that involves the PSC
+phenomena from which rises the SVI treated in this paper. The full description 
+of it was presented by Bhat and Sipe et. al.\cite{bhatPRL05}
+
+As mentioned before in Section \ref{sec:introduction}, In PSCs there is no net
+motion of charge and spin-up electrons move in a given direction while spin-
+down electrons travel in the opposite one. This effect can result from one
+photon absorption of linearly polarized light by a semiconductor, with filled
+valence bands and empty conduction bands, illuminated by light with photon
+energy larger than the energy gap.
+% note 1
+Using i.e. a single weak continuous linearly polarized laser beam, is possible
+to promote electrons in $\mathbf{k}$ space regardless the symmetry of the system
+resulting in a net current equal to zero. Then, if the system presents inversion
+of symmetry, electrons promoted to the conduction bands at opposite $\mathbf{k}$
+points will have opposite spin polarization resulting in a total spin injection
+equal to zero. If the phenomena is produced in a noncentrosymmetric
+semiconducting media the spin polarization injected at a given $\mathbf{k}$
+point can be held\cite{alvaradoPRL85}, resulting in a PSC because the velocity
+of electrons at opposite $\mathbf{k}$ points are in opposite directions.
+
+\subsection{Spin velocity injection} % (fold)
 \label{sec:theory-pure_spin_current}
 
-The spin density injection current $\dot{K}^{\mathrm{ab}}(\omega)$, 
-% 
-{
-\color{red}
-where the roman superscripts denote Cartesian components corresponding
-$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
-polarization direction, can be written in terms of a material response
-pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as }
-\begin{equation*}
-\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
-E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
-\label{eq:dotk}
-\end{equation*}
-where the pseudotensor is given by\cite{bhatPRL05}
-\begin{widetext}
-\begin{align}
-\mu^{\mathrm{abcd}} (\omega) 
+We define the SVI as the velocity at which the spin, polarized along the
+direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
+\begin{equation}\label{eq:vab-w}
+\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
+\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
+\end{equation}  
+where the pure spin density injection current, $\dot{K}^{\mathrm{ab}} (\omega)$,
+and the carrier injection rate, $\dot{n}(\omega)$, are given by
+% 
+\begin{equation}\label{eq:dot-kn}
+\begin{aligned}
+\dot{K}^{\mathrm{ab}}(\omega) 
 &=
+\mu^{\mathrm{abcd}}(\omega)
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
+% \label{eq:dotk} 
+\\
+\dot{n}(\omega)
+&=
+\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
+% \label{eq:dotn}
+\end{aligned}
+\end{equation}
+where the roman superscripts denote Cartesian directions, and if repeated, they
+are to be summed over, the $\xi^{\mathrm{ab}}(\omega)$ are the carrier
+generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the pure
+spin-current pseudotensor components given by\cite{bhatPRL05}
+\begin{equation*}\label{eq:mu}
+\begin{aligned}
+\mu^{\mathrm{abcd}}  (\omega) &
+=
 \frac{\pi e^{2}}{\hbar^{2}} \int 
-\frac{d^{3}K}{8 \pi^{3}}
+\frac{d^{3}K}{8 \pi^{3}} \times \\
 \sum_{vcc'}^{'}
-\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} 
+\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'} 
 \left( 
@@
 \right) 
-\right]
-\delta(\omega-\omega_{cv})
-\label{eq:mu}
-\end{align}
-\end{widetext}
-{\color{red}
+\right] \delta(\omega-\omega_{cv}),
+\end{aligned}
+\end{equation*}
 where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
@@
 $. 
-}% 
-The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and
-the sum only covers these states and 
-{\color{red}
-since $\mu$ is real we have that
-$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
-}
-Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
-the speed at which the spin polarized in the $\mathrm{b}$   direction moves
-along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
-plane with a polarization angle $\alpha$ as
+% 
+The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
+sum only covers these states and since $\mu^{\mathrm{abcd}}(\omega)$ is real we
+have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
+% 
+Since we have 2D structures we use an incoming electric field parallel to the
+surface, $\mathbf{E}^{a}(\omega) = E^{\mathrm{a}} e^{i(\alpha + \omega t)}$,
+where the angle $\alpha$ corresponds to the linear polarization angle measured
+positively in the counter-clockwise from the $x$ direction on the
+surface of the structures.
+% 
+Then from Eq. \eqref{eq:dot-kn} we can rewrite the Eq. \eqref{eq:vab-w} and 
+including the polarization angle dependence we have
 \begin{widetext}
@@
 \xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
-\label{eq:vab}
+\label{eq:vab-aw}
 \end{align}
 \end{widetext}
-{\color{red}
-where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
-components\cite{arzatePRB14}.
-}
-% 
-For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
+% 
+If the polarization angle is fixed to $\alpha = \frac{\pi}{4}$ the previous
+expression can be reduced to 
 \begin{equation*}\label{eq:vab-90deg}
@@
 \end{equation*}
+Two interesting possibilities to analyze the SVI are fixing the spin along any
+of the three Cartesian coordinates and, for our cases, particularly for the spin
+directed along $z$ directed perpendicularly to the surface of the structure; or
+fixing the velocity along the $x$ or $y$ Cartesian coordinates on the $xy$ plane
+of the structures. In following subsections we present these cases.
 
@@
 
-{\color{red} Considering that we have 2D structures, one of the options to
-analyze the spin velocity (Eq. \eqref{eq:vab}) is fixing the spin parallel to
-the surface of the structure in the $x$ or $y$ directions or perpendicularly to
-it in the $z$ direction. We define the magnitude of the spin velocity with spin
-polarization along the $\mathrm{b}$ Cartesian coordinate as}
-\begin{align}
+Because we have 2D structures, one of the options to analyze the spin velocity
+(Eq. \eqref{eq:vab-aw}) is fixing the spin parallel to the surface of the
+structure in the $x$ or $y$ directions or perpendicularly to it in the $z$
+direction. We define the magnitude of the spin velocity with spin polarization
+along the $\mathrm{b}$ Cartesian coordinate as
+\begin{equation}
 |\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
-&=
+=
 \sqrt{
@@
 \label{eq:vs-mag}
-\end{align}
+\end{equation}
 and the angle at which the spin velocity is directed on the $xy$ plane as
-\begin{align}
+\begin{equation}
 \gamma_{\mathrm{b}} (\omega,\alpha)
-&=
+=
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
@@
 \label{eq:gamma-ang}
-\end{align}
+\end{equation}
 where the angle is measured in the counter-clockwise direction from the
@@
 
-{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab} is fixing
+{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab-aw} is fixing
 the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
@@
 
-\subsection{Spin velocity} % (fold)
+\subsection{Spin velocity injection} % (fold)
 \label{sec:res-spin_velocity}
@@
 
-{\color{red}Using the Eq. \eqref{eq:vab}, we calculated the
+{\color{red}Using the Eq. \eqref{eq:vab-aw}, we calculated the
 $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{up} and

### 2017-06-14 mu/article/article.tex
Conclusions and article almost completed before BMS review

@@
 \usepackage{multirow}
-\usepackage{showframe}
-\usepackage[inline]{showlabels}
+% \usepackage{showframe}
+% \usepackage[inline]{showlabels}
 
@@
 At present there is an increasing interest in attain the same level of control
-over the transport of spin at micro or nano scales as has been done for the flow
-of charge in typical electronic devices.\cite{awschalomNP2007} Some
+over the transport of spin at micro or nano scales as has been done for the
+flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
 semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
@@
 optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon absorption of
-linearly polarized light\cite{bhatPRL05} and has been observed in
-gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
-arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
+linearly polarized light\cite{bhatPRL05} and has been observed in gallium
+arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium arsenide
+(AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
 
@@
 thermal transport properties, high conductivity and strength \cite{geimNM07,
-reinaNL08, novoselov2S07, balandinNL08} being then a perfect platform to be used
-in two-dimensions electronic systems; however most electronic applications are
-disabled by the absence of a semiconducting gap. Recent studies demonstrate that
-the band gap of graphene can be opened by applying an electric
+reinaNL08, novoselov2S07, balandinNL08} being then a perfect platform to be
+used in two-dimensions electronic systems; however most electronic applications
+are disabled by the absence of a semiconducting gap. Recent studies demonstrate
+that the band gap of graphene can be opened by applying an electric
 field,\cite{zhangN09} reducing the surface area,\cite{hanPRL07} or applying
@@
 shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
-only in the upper side of the structure while the \emph{alt} structure, shown in
-Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom sides
-of the carbon slab.\cite{zapataPSB2016}
+only in the upper side of the structure while the \emph{alt} structure, shown
+in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
+sides of the carbon slab.\cite{zapataPSB2016}
 
 Using those structures we address a theoretical study of the spin velocity
-injection (SVI) by one-photon absorption of linearly polarized light making
-emphasis for the particular cases when the spin of electrons is directed along
-the the $z$ Cartesian coordinate, perpendicular to the $xy$ plane of the
-structure, or for the case when the velocity is directed along the $x$ and $y$
-Cartesian direction on the $xy$ plane of the structures.
-% 
-The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is a nonlinear optical
-effect that quantifies the velocity at which a PSC moves along the Cartesian
-direction $\mathrm{b}$ with the spin of electron polarized along the Cartesian
-direction $\mathrm{a}$. One photon absorption of linearly polarized light can
-promote a distribution of electrons in $\mathbf{k}$ space regardless the
-symmetry of the material resulting in a not net electrical
-current. Then, the electrons excited to the conduction bands at
-opposite $\mathbf{k}$ points will result in opposite spin polarizations 
-producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
-the material is not centrosymmetric the spin polarization injected at a given $
-\mathbf{k}$ point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and
-then a PSC will be produced since the velocities of electrons at opposite
-$\mathbf{k}$ points are opposite.
+injection (SVI) by one-photon absorption of linearly polarized light that does
+not seem to have been reported previously.
+% 
+We calculated the responses for the particular cases when the spin of electrons
+is directed along the the $z$ Cartesian coordinate, perpendicular to the $xy$
+plane of the structure, or for the case when the velocity is directed along the
+$x$ and $y$ Cartesian direction on the $xy$ plane of the structures.
+% 
+The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is optical effect that
+quantifies the velocity at which a PSC moves along the Cartesian direction
+$\mathrm{b}$ with the spin of electron polarized along the Cartesian direction
+$\mathrm{a}$. One photon absorption of linearly polarized light can promote a
+distribution of electrons in $\mathbf{k}$ space regardless the symmetry of the
+material resulting in a not net electrical current. Then, the electrons excited
+to the conduction bands at opposite $\mathbf{k}$ points will result in opposite
+spin polarizations producing no net spin injection.\cite{bhatPRL05} If the
+crystalline structure of the material is not centrosymmetric the spin
+polarization injected at a given $\mathbf{k}$ point could not
+vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC will be produced
+since the velocities of electrons at opposite $\mathbf{k}$ points are opposite.
 
@@
 Using i.e. a single weak continuous linearly polarized laser beam, is possible
-to promote electrons in $\mathbf{k}$ space regardless the symmetry of the system
-resulting in a net current equal to zero. Then, if the system presents inversion
-of symmetry, electrons promoted to the conduction bands at opposite $\mathbf{k}$
-points will have opposite spin polarization resulting in a total spin injection
-equal to zero. If the phenomena is produced in a noncentrosymmetric
-semiconducting media the spin polarization injected at a given $\mathbf{k}$
-point can be held\cite{alvaradoPRL85}, resulting in a PSC because the velocity
-of electrons at opposite $\mathbf{k}$ points are in opposite directions.
+to promote electrons in $\mathbf{k}$ space regardless the symmetry of the
+system resulting in a net current equal to zero. Then, if the system presents
+inversion of symmetry, electrons promoted to the conduction bands at opposite
+$\mathbf{k}$ points will have opposite spin polarization resulting in a total
+spin injection equal to zero. If the phenomena is produced in a
+noncentrosymmetric semiconducting media the spin polarization injected at a
+given $\mathbf{k}$ point can be held\cite{alvaradoPRL85}, resulting in a PSC
+because the velocity of electrons at opposite $\mathbf{k}$ points are in
+opposite directions.
 
@@
 \end{equation}  
-where the pure spin density injection current, $\dot{K}^{\mathrm{ab}} (\omega)$,
-and the carrier injection rate, $\dot{n}(\omega)$, are given by
+where the pure spin density injection current, $\dot{K}^{\mathrm{ab}}
+(\omega)$, and the carrier injection rate, $\dot{n}(\omega)$, are given by
 % 
@@
 are to be summed over, the $\xi^{\mathrm{ab}}(\omega)$ are the carrier
-generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the pure
-spin-current pseudotensor components given by\cite{bhatPRL05}
+generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the
+pure spin-current pseudotensor components given by\cite{bhatPRL05}
 \begin{equation*}\label{eq:mu}
@@
 Two interesting possibilities to analyze the SVI are fixing the spin along any
-of the three Cartesian coordinates and, for our cases, particularly for the spin
-directed along $z$ directed perpendicularly to the surface of the structure; or
-fixing the velocity along the $x$ or $y$ Cartesian coordinates on the $xy$ plane
-of the structures. In following subsections we present these cases.
+of the three Cartesian coordinates and, for our cases, particularly for the
+spin directed along $z$ directed perpendicularly to the surface of the
+structure; or fixing the velocity along the $x$ or $y$ Cartesian coordinates on
+the $xy$ plane of the structures. Also we can analyze the SVI contribution
+coming from each layer of the structure. In following subsections we present
+these three cases.
 
@@
 
-Because we have 2D structures, one of the options to analyze the spin velocity
-(Eq. \eqref{eq:vab-aw}) is fixing the spin parallel to the surface of the
-structure in the $x$ or $y$ directions or perpendicularly to it in the $z$
-direction. We define the magnitude of the spin velocity with spin polarization
-along the $\mathrm{b}$ Cartesian coordinate as
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the spin
+velocity with spin polarized along the $\mathrm{b}$ Cartesian coordinate as
 \begin{equation}
@@
 \sqrt{
-[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
-[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
+[\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)]^{2}\ +
+[\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)]^{2}\ 
 }, 
@@
 =
-\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
-{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
+\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
+{\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)} \right),
 \label{eq:gamma-ang}
 \end{equation}
-where the angle is measured in the counter-clockwise direction from the
-positive $x$ Cartesian coordinate. {\color{red} We also define two special
+where this angle is measured in the counter-clockwise direction from the
+positive $x$ Cartesian coordinate. We also define two special
 angles
@@
 The first corresponds to the case when the spin velocity is directed, on the
-$xy$ plane in the same direction of the polarization angle of the incoming
-beam; the second one corresponds to the case when the spin velocity is directed
-perpendicularly respect to the polarization angle of the incoming beam. }
+$xy$ plane in the same direction of the polarization angle $\alpha$ of the
+incoming beam; the second one corresponds to the case when the spin velocity is
+directed perpendicularly respect to the polarization angle of the incoming
+beam.
 
@@
 
-{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab-aw} is fixing
-the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
-define the magnitude of the spin velocity directed along the $\mathrm{a}$
-direction as}
+Analyzing now the SVI fixing the velocity along the $\mathrm{a}$ Cartesian
+coordinate on the surface of the structures we define the corresponding
+magnitude as
 \begin{align}
@@
 For a layered system we have that the total contribution of Eqns. 
-\eqref{eq:vs-mag} and \eqref{eq:vv-mag} is given \cite{arzatePRB14} by
-
+\eqref{eq:vs-mag} and \eqref{eq:vv-mag} are given \cite{arzatePRB14} by 
 \begin{align}
@@
 \end{align}
+where $|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|$ gives the contribution of
+the $\ell^{th}$ layer to the total SVI when the spin is fixed in the
+$\mathrm{b}$ direction or when the velocity is fixed in the $\mathrm{a}$
+direction, respectively. For the structures presented here this layers
+correspond to the total number of layers being two for the \emph{up} structure
+and six for the \emph{alt} structure.
 
@@
 $\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
-with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.}
+with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)|=43.0$\,Km/s.}
 % 
@@
 
+Spintronics devices are based on the control of spin and electrical charge
+through electrical and optical methods.
+% 
+Semiconductor spintronics gives the development possibility of devices that can
+perform high-volume information manipulation, processing, and storage, for
+computing and communications technologies. \cite{awschalomNP2007}
+% 
+We have performed an \emph{ab initio} calculation for the SVI by one-photon
+absorption of linearly polarized light in the \emph{up} and \emph{alt} 2D
+hydrogenated graphene structures that could result in spintronics devices
+development. This effect does not seem to have been reported previously.
+% 
+We calculated the responses for two cases: when the spin polarization is fixed
+along the Cartesian coordinates and when the spin velocity is directed along
+the $x$ and $y$ Cartesian directions on the $xy$ surface of the structures. We
+found that  the SVI is very susceptible to the characteristics of the
+structures presenting an anisotropic behavior.
+% 
+We found that for both structures it is possible to generate a SVI comparable
+being the response of the \emph{alt} structure comparable with GaAs and CdSe
+and the response of the \emph{up} structure much more intense than all.
+
+We analyzed the SVI as a function of the energy of the incoming beam and the
+polarization angle for the \emph{up} and \emph{alt} structures for the cases
+when the spin is polarized along the three Cartesian directions with a
+propagating angle on the surface of the structures measured in the counter-%
+clockwise direction from the $x$ Cartesian direction. We found that the most
+intense response was when the spin is directed perpendicularly to the plane of
+the structures in the $z$ direction.
+% 
+For this condition we found that the \emph{up} structure reaches a maximum
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s directed in
+an angle $\gamma_{\mathrm{z}} (\omega,\alpha) = 160^{\circ}$ on the $xy$ plane
+for an energy of the incoming beam of 0.088\,eV, for which the response is
+maximized, and polarization angle $\alpha
+= 40^{\circ}$.
+% 
+Similarly for the \emph{alt} structure we found that the maximum reached is $|
+\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s at $\gamma_{
+\mathrm{z}} (\omega,\alpha) = 50^{\circ}$ for an energy of the incoming beam of
+0.912\,eV and polarization angle $\alpha = 145^{\circ}$.
+% 
+Also we found two angles of interest for which the SVI, with spin polarized in
+the $z$ direction, propagates collinearly or perpendicularly to the
+polarization angle of the incoming beam. With this condition and fixing again
+the energy of the incoming beam to 0.088\,eV we found that
+$\gamma_{\mathrm{z}\parallel} (\omega,\alpha=65.5^{\circ}) = 65.5^{\circ}$
+resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
+82.3$\,Km/s and $\gamma_{\mathrm{z}\perp} (\omega,\alpha = 155.5^{\circ}) =
+65.5^{\circ}$ resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)| = 24.8$\,Km/s.
+% 
+Alike, for the \emph{alt} structure fixing the energy of the incoming
+beam to 0.912\,eV we found that the parallel and collinear angles are $\gamma_{
+\mathrm{z}\parallel} (\omega,\alpha = 53.5^{\circ}) = 53.5^{\circ}$ and
+$\gamma_{\mathrm{z}\perp} (\omega,\alpha = 140^{\circ}) = 50^{\circ}$ resulting
+in values of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s
+and $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s,
+respectively.
+
+We also examined the SVI for the cases when the velocity is directed along the
+$x$ and $y$ Cartesian coordinates on the $xy$ plane of the \emph{up} and
+\emph{alt} structures. We also defined the polar and azimuthal angles, the
+first measured from the positive to the negative $z$ Cartesian coordinate
+perpendicular to the structure and the second from the positive $x$ Cartesian
+direction in the counter-clockwise sense on the $xy$ plane.
+% 
+For this case we found that the responses for the \emph{up} structure,for an
+energy of the incoming bean of 0.088\,eV, reach the maximum values  of
+$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s wit polar and azimuthal
+% spin polarization angles $\theta_{\mathrm{x}} (\omega,\alpha)=47$ and
+% $\varphi_{\mathrm{x}} (\omega,\alpha)=212$, 
+directed upward the third Cartesian quadrant of the $xy$ plane; and
+$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)|=87.9$\,Km/s with polar and
+azimuthal spin polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) =
+8^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) = 133^{\circ}$ directed
+almost perpendicularly over the first Cartesian quadrant over the $xy$ plane.
+% 
+Likewise, for the \emph{alt} structure we found that, for an energy of the
+incoming beam of 1.972\,eV, the responses reach maximum values of
+$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| = 9.9$\,Km/s with spin
+% polarization angles $\theta_{\mathrm{x}} (\omega,\alpha) = 129^ {\circ}$ and
+% $\varphi_{\mathrm{x}} (\omega,\alpha)=229^{\circ}$ 
+directed downward the third Cartesian quadrant of the $xy$ plane; and
+$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.4$\,Km/s with spin
+polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and
+$\varphi_{\mathrm{y}} (\omega,\alpha)=227^{\circ}$ directed downward the third
+Cartesian quadrant.
+
+According to these results both structures are excellent candidates for
+spintronics applications.
+
 \bibliography{article.bib}

### 2017-06-15 mu/article/article.tex
Conclusions completed.

@@
 properties like fractional quantum Hall effect at room temperature, excellent
-thermal transport properties, high conductivity and strength \cite{geimNM07,
-reinaNL08, novoselov2S07, balandinNL08} being then a perfect platform to be
-used in two-dimensions electronic systems; however most electronic applications
-are disabled by the absence of a semiconducting gap. Recent studies demonstrate
-that the band gap of graphene can be opened by applying an electric
-field,\cite{zhangN09} reducing the surface area,\cite{hanPRL07} or applying
-uniaxial strain.\cite{niACSN08} Another possibility to open the gap is by
-doping; this has been successfully achieved using nitrogen,\cite{weiNL2009}
-boron-nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-metals, and
-hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
+thermal transport properties, excellent conductivity\cite{heerscheNat07} and
+strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08} being then a
+perfect platform to be used in two-dimensions electronic systems; however most
+electronic applications are disabled by the absence of a semiconducting gap.
+Recent studies demonstrate that the band gap of graphene can be opened by
+applying an electric field,\cite{zhangN09} reducing the surface
+area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
+possibility to open the gap is by doping; this has been successfully achieved
+using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
+silicon,\cite{colettiPRB10} noble-metals, and hydrogen.\cite{eliasS09,
+guisingerNL09, samarakoonACSN10}
 % 
@@
 perform high-volume information manipulation, processing, and storage, for
-computing and communications technologies. \cite{awschalomNP2007}
+computing and communications technologies.\cite{awschalomNP2007} 
 % 
@@
 
-According to these results both structures are excellent candidates for
-spintronics applications.
+Novel PSC devices for spintronics applications has been
+proposed.\cite{gotteNat16, pershinPRB08} One of the difficulties to achieve the
+development of spin current and PSC semiconductor devices is the fact that the
+spin relaxation time in a semiconducting media is short disabling the spin
+transport and then resulting in a no observable spin
+current.\cite{murakamiSc03}
+% 
+The spin relaxation time in pure and doped graphene is long enough in the order
+from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertler2009electron} The,
+according to our results the \emph{alt} structure is a good candidate and the
+\emph{up} structure an excellent candidate for the development of spintronics
+devices that require PSC due to the high spin velocity transport.
+
+\section{Acknowledgment} % (fold)
+
+This work has been supported by \emph{Consejo Nacional de Ciencia y
+Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
 

### 2017-06-16 mu/article/article.tex
Redaction completed. Ging with BMS.

@@
 using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
-silicon,\cite{colettiPRB10} noble-metals, and hydrogen.\cite{eliasS09,
-guisingerNL09, samarakoonACSN10}
+silicon,\cite{colettiPRB10} noble-metals,\cite{varykhalovPRB10} and
+hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
 % 
@@
 
-{\color{blue} As mentioned before in in the beginning of this section the
-\emph{up} and \emph{alt} structures presented here was divided into layers to
-analyze the layer-by-layer contribution for
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. Here we present the decomposition
-only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and for the
-corresponding components of the \emph{up} structure in Figs. 
+{\color{blue} 
+% 
+As mentioned before in in the beginning of this section the \emph{up} and
+\emph{alt} structures presented here was divided into layers to analyze the
+layer-by-layer contribution for $|\mathcal{V}_{\sigma^{\mathrm{b}}}
+(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$. Here we
+present the decomposition only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)|$ and for the corresponding components of the \emph{up}
+structure in Figs.
 % 
 \ref{fig:up-vsz-lay-1} and \ref{fig:up-vsz-lay-2} and for the \emph{alt}    
-structure in Fig. \ref{fig:alt-vsz-lay}. The
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented in
-those figures is the same than the presented in top frames of Figs.
-% 
-\ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
-layered responses.
+structure in Fig. \ref{fig:alt-vsz-lay}. 
+% 
+% The $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented
+% in those figures is the same than the presented in top frames of Figs.
+% \ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
+% layered responses.
 % 
@@
     \centering
-    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay}
+    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay-1}
 
@@
     for the \emph{alt} structure as a function of the polarization angle
-    $\alpha$ for the energy fixed to 0.912\,eV for which the absolute maximum
-    is obtained.
+    $\alpha$ for the energy fixed to 0.720\,eV.
     % 
@@
 layer comprised by carbon atoms having a minimal reduction produced by the
-hydrogen layer. Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response,
-presented in bottom frame of same figure, is produced only by the carbon layer.
-This result in a total response
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 95.8$\,Km/s coming from
-the carbon layer and being minimally reduced by the hydrogen layer as shown in
-the top frame of this figure.
+hydrogen layer. 
+% 
+Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response, presented in
+bottom frame of same figure, is produced only by the carbon layer. This result
+in a total response $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+95.8$\,Km/s coming from the carbon layer and being minimally reduced by the
+hydrogen layer as shown in the top frame of this figure for a fixed
+polarization angle $\alpha = 40^{\circ}$.
 % 
@@
 figure we have that the major contribution to the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ comes from the carbon
-layer with but being in this case reinforced by the contribution of the
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response comes from the
+carbon layer with but being in this case reinforced by the contribution of the
 hydrogen layer and resulting in a value of 30.3\,Km/s}
@@
 {\color{blue} 
-Finally, for the \emph{alt} structure we have that the six layers contribute
-with similar magnitudes and reinforce the
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components resulting in a total
-response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 43$\,Km/s.
+% 
+Finally, for the \emph{alt} structure we have that, for the response $|
+\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ when the energy is fixed to
+0.720\,eV the six layers contribute with similar magnitudes. 
+% 
+We found that for the $\mathcal{V}^{\mathrm{xz}} (\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ components the top hydrogen layer
+response, denoted by $\ell_{1}$, cancels partially the the bottom hydrogen
+layer response, denoted by $\ell_{6}$;
+% 
+a similar behavior occurs in the component $\mathcal{V}^{\mathrm{xz}}
+(\omega,\alpha)$ for the third and fourth carbon layers and in the component
+$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ for the second and fifth carbon
+layers.
+% 
+This result in a total response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) =
+42.4$\,Km/s for a fixed polarization angle $\alpha = 145^{\circ}$.
+% 
+Then, for this analysis we found that the $|\mathcal{V}_{\sigma^{\mathrm{z}}} 
+(\omega,\alpha)|$ and in general, $\mu^{\mathrm{abcd}} (\omega)$ responses are
+very susceptible to the symmetry of the system. The \emph{up} structure is 
+\emph{more} non-centrosymmetric than the \emph{alt} structure and then the
+response is quite larger.
 }
@@
 \emph{up} structure an excellent candidate for the development of spintronics
-devices that require PSC due to the high spin velocity transport.
+devices that require PSC due to the high spin velocity transport. The fact that
+the \emph{up} structure is better than the \emph{alt} structure comes from the
+symmetry: the first one is \emph{more} non-centrosymmetric than
+the second resulting in a more intense response of the system.
 

### 2017-06-16 mu/alt/alt-scripts/alt-magsvab-inang-lay.sh

@@ -11,10 +11,12 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 layers=( 1 2 3 4 5 6 )
 
 # FIXED ENERGY:
-en1="9.12000E-01"
+# en1="9.12000E-01"
+en1="7.20000E-01"
 
 # OUTPUT FILE SUFIX:
-fs1="0.912eV"
+# fs1="0.912eV"
+fs1="0.720eV"
 
 deg=180/3.141592
 

### 2017-06-16 mu/alt/alt-scripts/alt-magsvab-inang.sh

@@ -9,10 +9,12 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
 # FIXED ENERGY:
-en1="9.12000E-01"
+# en1="9.12000E-01"
+en1="7.20000E-01"
 
 # OUTPUT FILE SUFIX:
-fs1="0.912eV"
+# fs1="0.912eV"
+fs1="0.720eV"
 
 deg=180/3.141592
 

### 2017-06-16 mu/article/article.checkrefs.sh

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+files=(article.tex article.abstracts)
+
+references=(`grep @ article.bib`)
+# echo ${references[@]}
+
+for i in ${references[@]}; do
+    tofind+=(`echo $i | cut -c 10- | sed 's/.$//'`)
+done
+
+# echo ${tofind[@]}
+
+for j in ${files[@]}; do
+    for i in ${tofind[@]}; do
+        number=`grep $i $j | wc -l`
+        if [ $number = 0 ]; then
+            echo -e "$number \t $j \t $i "
+        fi
+    done
+done

### 2017-07-01 mu/article/article.tex
sab
Corrections completed

@@
 \usepackage{multirow}
+\usepackage[capitalize]{cleveref}
 % \usepackage{showframe}
-% \usepackage[inline]{showlabels}
+\usepackage[inline]{showlabels}
 
@@
 
-{
-\color{blue}
 Spintronics is an emerging research field of electronics in which the
@@
 semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
-dattaAPL90} and some of them require spin polarized electrical current
-\cite{awschalomSSBM13} or pure spin currents (PSC). In PSCs there is no net
+dattaAPL90,gotteNat16,pershinPRB08} and some of them require spin polarized
+electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
+% 
+One of the difficulties to achieve the development of spin current and PSC
+semiconductor devices is the fact that the spin relaxation time in a
+semiconducting media is short disabling the spin transport and then resulting
+in a no observable spin current.\cite{murakamiSc03}
+% 
+In PSCs there is no net
 motion of charge; spin-up electrons move in a given direction while spin-down
@@
 
-% Since its discovery, graphene has attracted a great interest in materials
-% science and condensed matter physics being a new class of materials that are
-% only one atom thick\cite{geimNM07}. 
-% 
 Graphene, an allotrope of carbon with hexagonal 2D lattice structure presents
@@
 % 
-In this paper we present two 50\% hydrogenated graphene non centrosymmetric
+In this paper we present two 50\% hydrogenated graphene noncentrosymmetric
 structures both presenting a discernible band gap: the \emph{up} structure,
@@
 Using those structures we address a theoretical study of the spin velocity
-injection (SVI) by one-photon absorption of linearly polarized light that does
-not seem to have been reported previously.
-% 
-We calculated the responses for the particular cases when the spin of electrons
-is directed along the the $z$ Cartesian coordinate, perpendicular to the $xy$
-plane of the structure, or for the case when the velocity is directed along the
-$x$ and $y$ Cartesian direction on the $xy$ plane of the structures.
-% 
-The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is optical effect that
-quantifies the velocity at which a PSC moves along the Cartesian direction
-$\mathrm{b}$ with the spin of electron polarized along the Cartesian direction
-$\mathrm{a}$. One photon absorption of linearly polarized light can promote a
-distribution of electrons in $\mathbf{k}$ space regardless the symmetry of the
-material resulting in a not net electrical current. Then, the electrons excited
-to the conduction bands at opposite $\mathbf{k}$ points will result in opposite
-spin polarizations producing no net spin injection.\cite{bhatPRL05} If the
-crystalline structure of the material is not centrosymmetric the spin
-polarization injected at a given $\mathbf{k}$ point could not
-vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC will be produced
-since the velocities of electrons at opposite $\mathbf{k}$ points are opposite.
+injection (SVI) by one-photon absorption of linearly polarized light.
+% 
+% We calculated the responses for the particular cases when the spin of
+% electrons is directed along the the $z$ Cartesian coordinate, perpendicular
+% to the $xy$ plane of the structure, or for the case when the velocity is
+% directed along the $x$ and $y$ Cartesian direction on the $xy$ plane of the
+% structures.
+{\color{red}
+% 
+Because we have 2D structures we made the analysis for tow cases. The first is
+fixing the spin of the electrons along the $z$ Cartesian direction with the
+velocity directed on the surface of the structure in the $xy$ plane. The second
+is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
+in $xyz$.}
+% 
+The SVI is an optical effect that quantifies the velocity at which a PSC moves
+along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
+along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
+polarized light can promote a distribution of electrons in $\mathbf{k}$ space
+regardless the symmetry of the material resulting in a null electrical current.
+Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
+points will result in opposite spin polarizations producing no net spin
+injection.\cite{bhatPRL05} If the crystalline structure of the material is
+noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
+could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} 
+% 
+{\color{red}
+% 
+and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
+opposite, a pure spin current will be produced. Since the structures presented
+here are noncentrosymmetric, they are good candidates in which this effect can
+be induced.}
 
@@
 describe the details of calculations and the corresponding SVI spectra for the
-\emph{up} and \emph{alt} structures. Finally, in Section
-
-}
+\emph{up} and \emph{alt} structures. Finally, we present our conclusions in
+Section \ref{sec:conclusions}.
 
@@
 In this section, we report a summary of the theory that involves the PSC
-phenomena from which rises the SVI treated in this paper. The full description 
-of it was presented by Bhat and Sipe et. al.\cite{bhatPRL05}
-
-As mentioned before in Section \ref{sec:introduction}, In PSCs there is no net
-motion of charge and spin-up electrons move in a given direction while spin-
-down electrons travel in the opposite one. This effect can result from one
-photon absorption of linearly polarized light by a semiconductor, with filled
-valence bands and empty conduction bands, illuminated by light with photon
-energy larger than the energy gap.
+phenomena from which rises the SVI treated in this paper.
+
+In PSCs there is no net motion of electrical charge and spin-up electrons move
+in a given direction while spin-down electrons travel in the opposite one.
+This effect can result from one photon absorption of linearly polarized light
+by a semiconductor, with filled valence bands and empty conduction bands,
+illuminated by light with photon energy larger than the energy gap.
 % note 1
-Using i.e. a single weak continuous linearly polarized laser beam, is possible
+Using a single continuous linearly polarized laser beam, it is possible
 to promote electrons in $\mathbf{k}$ space regardless the symmetry of the
-system resulting in a net current equal to zero. Then, if the system presents
-inversion of symmetry, electrons promoted to the conduction bands at opposite
-$\mathbf{k}$ points will have opposite spin polarization resulting in a total
-spin injection equal to zero. If the phenomena is produced in a
-noncentrosymmetric semiconducting media the spin polarization injected at a
-given $\mathbf{k}$ point can be held\cite{alvaradoPRL85}, resulting in a PSC
-because the velocity of electrons at opposite $\mathbf{k}$ points are in
-opposite directions.
-
-\subsection{Spin velocity injection} % (fold)
-\label{sec:theory-pure_spin_current}
-
-We define the SVI as the velocity at which the spin, polarized along the
-direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
-\begin{equation}\label{eq:vab-w}
-\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
-\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
+system resulting in a net current equal to zero. 
+% 
+If the phenomena is produced in a noncentrosymmetric semiconducting media, the
+electrons promoted to the conduction bands at opposite $\mathbf{k}$ points
+can produce a net spin polarization different to zero\cite{alvaradoPRL85},
+resulting in a PSC because the velocity of electrons
+at opposite $\mathbf{k}$ points are in opposite directions.
+
+Using the multiple scale approach to solve the equation of motion for the
+single particle density matrix $\rho_{mn}(\mathbf{k};t)$ we have that 
+\begin{equation*}
+\begin{aligned}
+&\frac{\partial \rho_{cc'}}{\partial t} =
+-i (\omega_{cc'} - i \epsilon) \rho_{cc'}
++
+\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
+{i \hbar^{2}}
+\times \\
+& \quad \sum_{v}r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'}
+\left( \frac{1}{\omega - \omega_{c'v} - i \epsilon} 
+- 
+\frac{1}{\omega - \omega_{cv} + i \epsilon} \right).
+\end{aligned}
+\end{equation*}
+Taking in the first term $\epsilon \rightarrow 0$ and changing the density
+matrix operator to the interaction representation, $\tilde{\hat{\rho}} = e^{iH_
+{0}t/\hbar} \hat{\rho} e^{-iH_{0}t/\hbar}$, with $H_{0}$ the ground state
+Hamiltonian, the matrix elements can be written as
+\begin{equation*}
+\tilde{\rho}_{cc'(\mathbf{k})} 
+= \langle c\mathbf{k}| \tilde{\hat{\rho}} | c'\mathbf{k} \rangle
+= e^{i \omega_{cc'}t} \rho_{cc'}(\mathbf{k}).
+\end{equation*}
+where $H_{0}|n\mathbf{k}\rangle = \hbar \omega_{n}(\mathbf{k})|n
+\mathbf{k}\rangle$ with $\hbar \omega_{n}(\mathbf{k})$ the energy of the
+electronic band $n$ at point $\mathbf{k}$ in the irreducible Brillouin zone
+(IBZ), and $|n\mathbf{k}\rangle$ the Bloch state. Then, the time derivative of
+$\tilde{\rho}_{cc'}(\mathbf{k})$ is given by 
+\begin{equation}\label{eq:derden}
+\begin{aligned}
+&\frac{d\tilde{\rho}_{cc'}(\mathbf{k})}{dt} 
+= 
+\frac{e^{2} E^\mathrm{a}(\omega) E^{\mathrm{b*}}(\omega)}{i\hbar^{2}} 
+e^{i\omega_{cc'}t} 
+\times \\
+&\quad \sum_{v}r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'}
+\left( \frac{1}{\omega - \omega_{c'v} - i \epsilon} 
+- 
+\frac{1}{\omega - \omega_{cv} + i \epsilon} \right),
+\end{aligned}
 \end{equation}
-where the pure spin density injection current, $\dot{K}^{\mathrm{ab}}
-(\omega)$, and the carrier injection rate, $\dot{n}(\omega)$, are given by
-% 
-\begin{equation}\label{eq:dot-kn}
-\begin{aligned}
-\dot{K}^{\mathrm{ab}}(\omega) 
+where $\epsilon \rightarrow 0$ still needs to be taken. 
+% 
+The expectation value of an observable $\mathcal{O}$ with quantum mechanical
+operator associated $\hat{\mathcal{O}}$ is given by
+\begin{equation}\label{eq:trace}
+\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}}),
+\end{equation}
+where $\mathrm{Tr}$ denotes the trace. Then
+\begin{align}
+\mathcal{O} 
+=&
+\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c \mathbf{k} 
+| \hat{\rho} \hat{\mathcal{O}} |
+c\mathbf{k} \rangle \nonumber \\
+=& 
+\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \tilde{\rho}_{cc'}(\mathbf{k}) 
+\mathcal{O}_{c'c}(\mathbf{k}),
+\label{eq:expectation}
+\end{align}
+where we used the interaction picture representation,
+$\tilde{\mathcal{O}}_{cc'} = \langle c'\mathbf{k} | e^{iH_{0}t/\hbar}
+\hat{\mathcal{O}} e^{-iH_{0}t/\hbar} | c\mathbf{k} \rangle$, and the closure
+relationship $\sum_{c}|c\mathbf{k}\rangle \langle c\mathbf{k} = 1$. So, the
+rate of change of $\mathcal{O}$ can be written from Eq. \eqref{eq:derden}, Eq.
+\eqref{eq:trace}, and Eq. \eqref{eq:expectation} as
+\begin{align}
+\dot{\mathcal{O}} 
 &=
+\mathrm{Tr} \left( \frac{d \hat{\tilde{\rho}}}{dt} 
+\tilde{\mathcal{O}} \right), 
+\nonumber \\
+&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
+\sum \mathcal{O}_{c'c} r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'} \times
+\nonumber \\
+& \left( \frac{1}{\omega - \omega_{c'v} - i\epsilon} - 
+\frac{1}{\omega - \omega_{cv} + i\epsilon} \right)
+E^{\mathrm{a}}(\omega) E^{\mathrm{b*}}(\omega)
+\label{eq:dotO}
+\end{align}
+
+Replacing the operator $\mathcal{O} \rightarrow \hat{K}^{\mathrm{ab}} \equiv v^
+{\mathrm{a}} S^{\mathrm{b}}$ the matrix elements are given by
+\begin{equation}
+K^{\mathrm{ab}}_{nm}(\mathbf{k}) = 
+\sum_{l} v^{\mathrm{a}}_{nl}(\mathbf{k})S^{\mathrm{b}}_{lm}(\mathbf{k}), 
+\label{eq:velspimatelem}
+\end{equation}
+and using time-reversal invariance it follows that 
+\begin{equation}
+K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}). 
+\label{eq:k-timerev}
+\end{equation}
+Now the time derivative $\dot{K}^\mathrm{ab}$ can be obtained as we proceeded
+in Eq. \eqref{eq:dotk-dev} of Appendix \ref{sec:mathder} and then we write
+\begin{equation}
+\dot{K}^{\mathrm{ab}}(\omega) =
 \mu^{\mathrm{abcd}}(\omega)
 E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
-% \label{eq:dotk} 
-\\
-\dot{n}(\omega)
-&=
-\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
-% \label{eq:dotn}
-\end{aligned}
+\label{eq:dotk}
 \end{equation}
-where the roman superscripts denote Cartesian directions, and if repeated, they
-are to be summed over, the $\xi^{\mathrm{ab}}(\omega)$ are the carrier
-generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the
-pure spin-current pseudotensor components given by\cite{bhatPRL05}
-\begin{equation*}\label{eq:mu}
+where the pure spin-current pseudotensor components
+\begin{equation}\label{eq:mu}
 \begin{aligned}
@@
 \end{aligned}
-\end{equation*}
-where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
-\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
-the spin current matrix elements that, using time reversal invariance, satisfy
-the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
-$. 
+\end{equation}
+are obtained from Eq. \eqref{eq:k-final} of the Appendix.
 % 
@@
 sum only covers these states and since $\mu^{\mathrm{abcd}}(\omega)$ is real we
-have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
+have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$. This
+previous equation is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05}
+obtained by using the semiconductor optical Bloch equations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Spin velocity injection} % (fold)
+\label{sec:theory-pure_spin_current}
+
+We define the SVI as the velocity at which the spin, polarized along the
+direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
+\begin{equation}\label{eq:vab-w}
+\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
+\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
+\end{equation}  
+where $\dot{K}^{\mathrm{ab}} (\omega)$ is given by Eqns. \eqref{eq:dotk} and
+\eqref{eq:mu} and the carrier
+injection rate,
+$\dot{n}(\omega)$, are given by
+% 
+\begin{equation}
+\dot{n}(\omega) =
+\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
+\label{eq:dotn}
+\end{equation}
+where $\xi^{\mathrm{ab}}(\omega)$ are the carrier
+generation rate tensor components. 
 % 
 Since we have 2D structures we use an incoming electric field parallel to the
-surface, $\mathbf{E}^{a}(\omega) = E^{\mathrm{a}} e^{i(\alpha + \omega t)}$,
-where the angle $\alpha$ corresponds to the linear polarization angle measured
-positively in the counter-clockwise from the $x$ direction on the
-surface of the structures.
-% 
-Then from Eq. \eqref{eq:dot-kn} we can rewrite the Eq. \eqref{eq:vab-w} and 
-including the polarization angle dependence we have
+surface, $\mathbf{E}^{\mathrm{a}}(\omega,\alpha) = E^{\mathrm{a}}(\omega)
+e^{i\alpha}$, where $\alpha$ corresponds to the linear polarization angle.
+% 
+Then from Eq. \eqref{eq:dotk}, Eq. \eqref{eq:vab-w}, and \eqref{eq:dotn}, and
+including the polarization angle dependence we obtain
 \begin{widetext}
@@
 \mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
-&= \frac{2}{\hbar}
-\frac{\mu^{\mathrm{abxx}}(\omega)
-E^{2}(\omega)\cos^{2}(\alpha) + 
-\mu^{\mathrm{abyy}}(\omega)
-E^{2}(\omega)\sin^{2}(\alpha) + 
-2\mu^{\mathrm{abxy}}(\omega)
-E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
-{\xi^{\mathrm{xx}}(\omega)
-E^{2}(\omega)\cos^{2}(\alpha) + 
-\xi^{\mathrm{yy}}(\omega)
-E^{2}(\omega)\sin^{2}(\alpha)},
-\nonumber \\
-&= \frac{2}{\hbar}
+% &= 
+% \frac{2}{\hbar}
+% \frac{\mu^{\mathrm{abxx}}(\omega)
+% E^{2}(\omega)\cos^{2}(\alpha) + 
+% \mu^{\mathrm{abyy}}(\omega)
+% E^{2}(\omega)\sin^{2}(\alpha) + 
+% 2\mu^{\mathrm{abxy}}(\omega)
+% E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
+% {\xi^{\mathrm{xx}}(\omega)
+% E^{2}(\omega)\cos^{2}(\alpha) + 
+% \xi^{\mathrm{yy}}(\omega)
+% E^{2}(\omega)\sin^{2}(\alpha)},
+% \nonumber \\
+&= 
+\frac{2}{\hbar}
 \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
@@
 % 
-If the polarization angle is fixed to $\alpha = \frac{\pi}{4}$ the previous
-expression can be reduced to 
-\begin{equation*}\label{eq:vab-90deg}
-\mathcal{V}^{\mathrm{ab}} (\omega)
-= \frac{2}{\hbar}
-\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
-2\mu^{\mathrm{abxy}}(\omega)}
-{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
-\end{equation*}
-Two interesting possibilities to analyze the SVI are fixing the spin along any
-of the three Cartesian coordinates and, for our cases, particularly for the
-spin directed along $z$ directed perpendicularly to the surface of the
-structure; or fixing the velocity along the $x$ or $y$ Cartesian coordinates on
-the $xy$ plane of the structures. Also we can analyze the SVI contribution
-coming from each layer of the structure. In following subsections we present
-these three cases.
+Two interesting possibilities to analyze the SVI are fixing the spin along $z$,
+directed perpendicularly to the surface of the structure, or fixing the
+velocity along $x$ or $y$ on the $xy$ plane of the structures. Also we can
+analyze the SVI contribution coming from each layer of the structure. In
+following subsections we present these three cases.
 
@@
 Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the spin
-velocity with spin polarized along the $\mathrm{b}$ Cartesian coordinate as
+velocity with spin polarized along the $\mathrm{b}$ direction as
 \begin{equation}
@@
 where this angle is measured in the counter-clockwise direction from the
-positive $x$ Cartesian coordinate. We also define two special
-angles
-\begin{align}
-\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
+positive $x$. We also define two special angles
+\begin{equation}
+\gamma_{\mathrm{b \parallel}}(\omega,\alpha) = \alpha, 
 \label{eq:gamma-par} 
-\\
-\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
+\end{equation}
+and
+\begin{equation}
+\gamma_{\mathrm{b \perp}}(\omega,\alpha) = \alpha \pm 90^{\circ}.
 \label{eq:gamma-perp}
-\end{align}
-The first corresponds to the case when the spin velocity is directed, on the
-$xy$ plane in the same direction of the polarization angle $\alpha$ of the
-incoming beam; the second one corresponds to the case when the spin velocity is
-directed perpendicularly respect to the polarization angle of the incoming
-beam.
+\end{equation}
+The first corresponds to the case when the spin velocity is directed, in the
+same direction of the polarization angle $\alpha$ of the incoming beam and the
+second one corresponds to the case when the spin velocity is directed
+perpendicularly with respect to the polarization angle of the incoming beam.
 
@@
 
-Analyzing now the SVI fixing the velocity along the $\mathrm{a}$ Cartesian
-coordinate on the surface of the structures we define the corresponding
-magnitude as
+Fixing the velocity along $x$ or $y$ we define the corresponding magnitude as
 \begin{align}
@@
 \end{align}
-{\color{red} Then, the spin direction depends of the $x$, $y$, and $z$
-components of the previous equation and so we define the spin orientation polar
-and azimuthal angles as}
+Then, the spin direction depends on the components of the previous equation and
+so we define the spin orientation polar and azimuthal angles as
 \begin{align}
@@
 \end{align}
-{\color{red} where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
-positive to the negative $z$ Cartesian coordinate and
-$\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
-counter-clockwise direction from the positive $x$ Cartesian coordinate.}
+% where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
+% positive to the negative $z$ Cartesian coordinate and
+% $\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
+% counter-clockwise direction from the positive $x$ Cartesian coordinate.
 
@@
 =& 
-\ell_{\mathrm{eff}}
 \sum_{\ell=1}^{N_{\mathrm{eff}}}
@@
 =&
-\ell_{\mathrm{eff}}
 \sum_{\ell=1}^{N_{\mathrm{eff}}}
@@
 noncentrosymmetric semi-infinite 2D carbon systems with 50\% hydrogenation in
-different arrangements. The \emph{up} structure has hydrogen atoms only on the
-upper side of the carbon sheet while the \emph{alt} structure has alternating
-hydrogen atoms on the upper and bottom sides. We take the hexagonal carbon
-lattice to be on the $xy$ plane for both structures, and the carbon-hydrogen
-bonds on the perpendicular $xz$ plane, as depicted in Figs. \ref{fig:alt-struc}
-and \ref{fig:up-struc}
-% 
-{\color{blue} and the coordinates for the \emph{up} and \emph{alt} unit cells
-of the structures are presented in Tables \ref{tab:up-unitcell} and
-% 
-\ref{tab:alt-unitcell}. In same tables we present the layer division needed to
-calculate the layer-by-layer contribution for the
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ presented in Eqns. 
-% 
-\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was
-divided in two layers, the first comprised of the top hydrogen atoms denoted by
-the number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc}
-and the second comprised of carbon atoms and denoted by the number 2. The
-\emph{alt} structure was divided in six layers denoted with numbers from 1 to 6
-in Table \ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and
-sixth layers correspond to hydrogen atoms in the top and bottom positions and
-from the second to the fifth correspond to carbon atoms placed in different
-positions.}
-
-{\color{red} We calculated the self-consistent ground state and the Kohn-Sham
+different arrangements. We recall that the \emph{up} structure has hydrogen
+atoms only on the upper side of the carbon sheet while the \emph{alt} structure
+has alternating hydrogen atoms on the upper and bottom sides. Also we take the
+hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
+carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
+\ref{fig:alt-struc} and \ref{fig:up-struc}. The coordinates for the
+\emph{up} and \emph{alt} unit cells of the structures are presented in Tables
+\ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
+
+We calculated the self-consistent ground state and the Kohn-Sham
 states using density functional theory in the local density approximation (DFT-
-LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.}
+LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
 % 
@@
 interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
-in Eq.
-\eqref{eq:mu}.
+in Eq. \eqref{eq:mu}.
 % 
@@
 the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
-40\,Ha, respectively. The energy eigenvalues and matrix elements for the
-\emph{up} ad \emph{alt} structures were calculated using 14452 $\mathbf{k}$
-points and 8452 $\mathbf{k}$ points in the irreducible Brillouin zone (IBZ)
-{\color{red} resulting in LDA energy band gaps of 0.72\,eV and 0.088\,eV,
-respectively.
-% 
-We notice that within DFT, the LDA is only one of other possible methods that
-can be used to determine the electronic structure of materials. Recent
-investigations on graphene show some of the differences in calculated values
-from several of these methods\cite{karamanisJPCC15,botelloACR14}. We note that
-the LDA is as good as these other approaches. It is also known that the DFT
-calculations predict a band gap for the material that differs from experiment.
-This can be corrected using other \emph{ab initio} techniques, such as the GW
-approximation\cite{onidaRMP02}, but this calculation has a very high
-computational cost and is out of the scope in this paper. Even so, DFT still
-remains as an effective and useful tool for computing diverse properties
-derived from the electronic band structure.}
+40\,Ha, resulting in LDA energy band gaps of 0.72\,eV and 0.088\,eV,
+respectively. The energy eigenvalues and matrix elements for the \emph{up} and
+\emph{alt} structures were calculated using 14452 $\mathbf{k}$ points and 8452
+$\mathbf{k}$ points in the IBZ.
+% 
+It is known that the DFT with LDA approximation misestimates the energy band
+gap of semiconductors. To correct this one has to include the many-body
+interaction using i.e. the so-called GW approximation but this technique has a
+very high computational cost and is out of the scope in this paper.
+Nevertheless, DFT still remains a mainstream tool for calculating diverse
+properties derived from the electronic band structure.
 
@@
 \hline
-\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
-             &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
-             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
-\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
-             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
- CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
- GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
+\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.2    \\
+             &      &       & 1.94  & $\mathrm{yz}$ &  22.2    \\
+             &      &       & 1.97  & $\mathrm{yz}$ & -29.7    \\
+\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.2    \\
+             &      &       & 0.91  & $\mathrm{yz}$ & -32.9    \\
+ CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.9    \\
+ GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.6    \\
 \hline
@@
 \caption{Comparison of the reported maxima values of
-$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
-polarization angle $\alpha$ and energy values.}
+$\mathcal{V}^{\mathrm{ab}}$ for the different structures and their
+corresponding polarization angle $\alpha$ and energy values of the incoming
+beam at which the maxima is obtained.}
 \label{tab:vab-str-comp}
@@
     $\mathcal{V}^{\mathrm{ab}}$ for 2D \emph{alt} and \emph{up}, and bulk CdSe
-    and GaAs structures and the corresponding polarization angles.}
+    and GaAs structures and their corresponding polarization angle $\alpha$.}
     \label{fig:vab-str-comp}
@@
 
-{\color{red}Using the Eq. \eqref{eq:vab-aw}, we calculated the
+Using the Eq. \eqref{eq:vab-aw}, we calculated the
 $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{up} and
@@
 the response of each structure is that for which the response is maximized in
-each case.}
-% 
-From the figure we have that the onset of the response starts when the energy
-of the incoming beam is the same of the gap energy.
+each case.
 % 
 The most intense response corresponds to the \emph{up} structure centered at
-0.088\,eV corresponding to the {\color{red} Mid Infrared (MIR)} radiation and
-reaching a spin velocity of 87.2\,Km/s.
-% 
-In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the {\color{red} Near Infrared (NIR) to visible radiation}, all
-the four structures have contributions in the same order of magnitude.
+0.088\,eV corresponding to the Mid Infrared (MIR) radiation and reaching a spin
+velocity of 87.2\,Km/s.
+% 
+For an energy range from 0.66\,eV to 3.0\,eV, corresponding
+to energies of the Near Infrared (NIR) to visible radiation, all
+the four structures have contributions of the same order of magnitude.
 % 
 For this energy range the \emph{up} structure has two peaks centered at
-1.94\,eV and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s,
-respectively, and the \emph{alt} structure has two peaks centered at 0.72\,eV
+1.94\,eV and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s and the \emph{alt} structure has two peaks centered at 0.72\,eV
 and 0.91\,eV reaching spin velocities of -40.2\,Km/s and -32.9\,Km/s,
@@
 response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
-GaAs structure has a large and almost planar zone where the response is held
-reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting
-in a spin velocity of -21.6\,Km/s.
-% 
-{\color{red} A negative quantity in the spin velocity means a change in the
-spin polarization traveling in the opposite direction.
+GaAs structure response reaches the maximum for an incoming beam of energy of
+2.31\,eV and resulting in a spin velocity of -21.6\,Km/s.
 % 
 In table \ref{tab:vab-str-comp} we present the comparison of this values for
-the 2D and bulk structures. We found that the most intense response for the
-spin velocity corresponds to the \emph{up} structure being 3.25 times more
-intense than that of the CdSe and 4.03 times more intense than that of the GaAs
-bulk structures. Also, the \emph{alt} structure has a response more intense
-than the bulk systems but being less intense than the corresponding to the
-\emph{up} one.}
-%
+the 2D and bulk structures; a positive (negative) spin-velocity means that the
+velocity moves (anti-)parallel to the electric field.
+% 
+From the table also we obtain that particularly the 2D \emph{up} structure is
+the one with the highest response being between 4 and 5 times more intense than
+the corresponding to the bulk structures.
 
@@
     \\
+    \vspace{4mm}
     \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
@@
 
-{\color{red} Using the Eq. \eqref{eq:vs-mag}, we calculated the
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ response and made the
-analysis for the case when the spin is fixed in the $z$ coordinate, directed
-perpendicularly to the surface of the \emph{up} and \emph{alt} structures.
-Also, using the Eq. \eqref{eq:gamma-ang}, we determined the angle
-$\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed on the
-surface of the each structure.}
-%
-
-\textbf{Up structure}
-
-We first analyzed two energy ranges in Fig. \ref{fig:up-3d-vsz} for the
-\emph{up} structure, the first for an incoming energy beam from 0.0\,eV to
-0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR)
-radiation, where the absolute maximum of the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is obtained, and
-the second for an energy range from 1.80\,eV to 2.1\,eV (bottom panel),
-corresponding to visible radiation, where two local maxima are found.
-% 
-Making the analysis, we obtained that the zone where the maximum response is
-held corresponds to a energy range of the incident beam from 0.084\,eV to
-0.093\,eV and polarization angles $\alpha$ between $30^{\circ}$ and
+Using Eq. \eqref{eq:vs-mag}, we calculated $|\mathcal{V}_{\sigma^{\mathrm{b}}}
+(\omega,\alpha)|$ and made the analysis for the case when the spin is fixed
+along $z$ directed perpendicularly to the surface of the \emph{up} and
+\emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
+angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
+on the surface of the each structure.
+%
+
+\subsubsection{Up structure}
+
+We present in Fig. \ref{fig:up-3d-vsz} the result of evaluate
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
+for two energy ranges on the \emph{up} structure.
+% 
+We obtained that the zone where the maximum response is reached corresponds to
+a energy range of the incident beam from 0.084\,eV to 0.093\,eV, in the far
+infrared (FIR) and polarization angles $\alpha$ between $30^{\circ}$ and
 $45^{\circ}$. Also the two local maxima are held for same beam polarization
-angles but for an energy range between 1.90\,eV and 2.05\,eV. In the top frames
-of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we present in solid lines
-the result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$,
-related to the left scale, fixing the energy of the incoming beam to 0.088\,eV
-and 1.972\,eV, respectively, values for which the response is maximized for the
-\emph{up} structure. In the same panels and frames we present in dashed lines,
-related to the right scale, the corresponding velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$, and in the bottom frames of the panels we
-present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
-and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and
-square boxes indicating the values where the angles of the spin velocity are
-parallel (Eq. \ref{eq:gamma-par}) and perpendicular (Eq. \ref{eq:gamma-perp})
-and the arrows are directed to the value of the response corresponding to those
-angles.
+angles but for an energy range between 1.90\,eV and 2.05\,eV, in the visible
+radiation range.
 % %%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%
-From top panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we have
-that the absolute maximum response for the \emph{up} structure is obtained for
-an incoming beam with energy of 0.088\,eV and polarization angle
-$\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=95.8$\,Km/s coming from the
-contribution of the components
+In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
+Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy of the
+incoming beam to 0.088\,eV for which the response is maximized as shown in the
+top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
+the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s. This value
+comes from the contribution of the components
 $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s for the spin polarized in
-the $\mathrm{z}$ direction and having a velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)=65^{\circ}$ on the first Cartesian quadrant
-of the $xy$ plane.
-% 
-{\color{red} From the top panel of Fig. \ref{fig:up-vaz-rag} we have that the
-velocity angle is almost constant for all the polarization angle range having
-values of $\gamma_{\mathrm{z}}(\omega,\alpha) = 65.5^{\circ} \pm 0.5^{\circ}$.
-In this panel the green circled box indicates the value for which the
-polarization angle and the response direction angle are collinear corresponding
-to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting
-in a value of the response of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s indicated by
-the upward green arrow.
-% 
-Also the blue square box indicates the value for which the polarization angle
-and the response angle are perpendicular being $\alpha=155.5^{\circ}$ and
-$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$; for this angle the
-response has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-24.8$\,Km/s indicated by the blue downward arrow.}
-% 
-Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag}
-we have that the most intense local maximum of the response is obtained for an
-incoming beam with energy of 1.972\,eV and same polarization angle
-$\alpha=40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
-from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
-component being directed in a velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha) = 78^{\circ}$ on the first Cartesian
-Quadrant on the $xy$ plane.
-% 
-{\color{red} Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found
-that the velocity angle is almost constant at $78^{\circ}$ and has variations
-of $1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq
-100^{\circ}$. In this range the green circled box indicates the value for which
-the polarization angle and the response direction angle are collinear
-corresponding to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$
-and having a response value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 23.5$\,Km/s indicated
-with the green upward arrow.
-% 
-Finally, the blue square box indicates the value for which the polarization
-angle and the response angle are perpendicular being $\alpha=168.5^{\circ}$
-$\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 78.5^{\circ}$ and having a response
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=9.0$\,Km/s indicated with
-the blue upward arrow.}
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s not presented here.
+% 
+In the same panel we present the corresponding velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
+the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 65^{\circ}$. Also
+we present two boxes indicating the values for which the angles of the spin
+velocity and the polarization angle are parallel (Eq. \ref{eq:gamma-par}, green
+circled box), corresponding to $\alpha =
+\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$; and perpendicular
+(Eq. \ref{eq:gamma-perp}, blue squared box), corresponding to $\alpha=155.5^
+{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$. The green
+and blue dashed arrows are directed from those angles to the respective value
+of the response corresponding to
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 24.8$\,Km/s.
+% 
+We also found that the velocity angle is almost constant for all the
+polarization angle range having values of $\gamma_{\mathrm{z}}(\omega,\alpha) =
+65.5^{\circ}\pm 0.5^{\circ}$.
+% 
+In the bottom panel of Fig. \ref{fig:up-vaz-rag} we present for the same
+structure the result of evaluate Eq. \eqref{eq:vs-mag} fixing now the energy of
+the incoming beam to 1.972\,eV for which the response has a local maximum as
+shown in the bottom panel of Fig. \ref{fig:up-3d-vsz}. The local maximum is
+obtained again when the polarization angle is $\alpha = 40^{\circ}$ resulting
+in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
+30.3$\,Km/s directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
+78^{\circ}$.
+% 
+Again, the  green circled box indicates the parallel angles $\alpha =
+\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ corresponding to a
+spin-velocity $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
+23.5$\,Km/s indicated with the green arrow
+% 
+and the blue squared box indicates the perpendicular pair of angles $\alpha =
+155.5^ {\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 65.5^{\circ}$.
+% 
+We found again that the velocity angle is almost constant at $78^{\circ}$ and
+has variations of $\pm 1^{\circ}$ for polarization angles $0^{\circ} \leq
+\alpha \leq 100^{\circ}$.
 % 
 We also made the analysis for the cases when the spin polarization is directed
-along the $\mathrm{x}$ and $\mathrm{y}$ Cartesian coordinates but we do not
-present here the corresponding plots. For those cases we have that the absolute
-maxima responses are obtained for an energy of the incoming beam equal to
-0.088\,eV and polarization angle $\alpha=40^{\circ}$ resulting in values of
+along $\mathrm{x}$ and $\mathrm{y}$ but we do not present here the
+corresponding plots. For those cases we have that the responses maxima are
+obtained for an energy of 0.088\,eV and polarization angle $\alpha=40^{\circ}$
+resulting in values of
 $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
@@
 
-\textbf{Alt structure}
-
-In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
-from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
-maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
-obtained for the \emph{alt} structure .
-% From this figure we found that the zone where the absolute maximum response
-% is held corresponds to a energy range from 0.90\,eV to 0.93\,eV and
-% polarization angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a
-% local maximum is obtained for the same polarization angles but for energies
-% between 0.67\,eV and 0.75\,eV.
+\subsubsection{Alt structure}
+
+We present in Fig. \ref{fig:alt-3d-vsb} the result of evaluate
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
+on the \emph{alt} structure.
+% 
+We obtained that the zone where the maximum response is reached corresponds to
+energies from 0.90\,eV to 0.93\,eV and a local maximum is obtained
+for energies between 0.67\,eV and 0.75\,eV both located in the FIR radiation
+range and for polarization angles between $120^{\circ}$ and $150^{\circ}$.
 % %%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%
-% 
-{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
-that the absolute maximum response is obtained for an incoming beam with
-polarization angle $\alpha=145^{\circ}$ reaching a velocity of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
-polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
-of the $xy$ plane.
-% 
-Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
-velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
-2^{\circ}$ for the polarization angle range $0^{\circ} \leq
+In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
+Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy to
+0.912\,eV for which the response is maximized as shown in the
+top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
+the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s.
+% 
+In the same panel we present the velocity angle
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
+the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 145^{\circ}$.
+% 
+As explained for the previous case, the green circled box indicates the
+parallel pair of angles $\alpha = \gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
+53.5^{\circ}$ with a corresponding value
+$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s indicated
+with the green arrow, and the blue square box indicates the perpendicular pair
+of angles, $\alpha=140^{\circ}$ and
+$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, with a value of
+$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|=43.0$\,Km/s indicated with
+the blue arrow.
+% 
+We also have that the velocity angle is centered at $51.5^{\circ}$ having
+variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
 \alpha \leq 180^{\circ}$.
-% 
-As made in the previous analysis the circled box indicates the collinear angle
-(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
-53.5^{\circ}$ corresponding a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
-square box indicates the perpendicular angles corresponding values
-$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
-with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)|=43.0$\,Km/s.}
 % 
@@
 here. The absolute maxima for the cases when the spin polarization are directed
-in the $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of
-the incoming beam equal to 0.912\,eV and polarization angle
-$\alpha=145^{\circ}$ resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.
+in the $x$ and $y$ direction are obtained for an energy of 0.912\,eV and
+polarization angle $\alpha=145^{\circ}$ resulting in values of
+$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)| = 27.1$\,Km/s and
+$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)| = 33.2$\,Km/s.
 
@@
 
-{\color{red} Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response and made the analysis for
-the case when the velocity is fixed in the $x$ and $y$ direction over the
-surface of the \emph{alt} and \emph{up} structures. Also, using the Eqns.
-\eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the polar
-$\theta_{\mathrm{a}}(\omega,\alpha)$ and azimuthal
-$\varphi_{\mathrm{a}}(\omega,\alpha)$ angles where the spin polarization is
-directed.}
-
-\textbf{Up structure.}
+Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
+$|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$ for the case when the velocity is
+fixed in the $x$ and $y$ direction on the surface of the \emph{up} and
+\emph{alt} structures. Also, using the Eqns. \eqref{eq:polar-ang} and 
+\eqref{eq:azimuthal-ang}, we determined the polar $\theta_{\mathrm{a}}
+(\omega,\alpha)$ and azimuthal $\varphi_{\mathrm{a}} (\omega,\alpha)$ angles
+corresponding to the direction of the spin.
+
+\subsubsection{Up structure}
+
 \begin{figure}[t]
@@
     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
-    \\
+    \\ \vspace{4mm}
     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
@@
 \end{figure}
-
 % %%%%%%%%%%%%%%%%%
@@
 In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present the
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ spectra resulting from evaluate the
-Eq. \eqref{eq:vv-mag} in the energy range for the incoming beam from 0.00\,eV
-to 0.16\,eV for the \emph{up} structure.
-%
-From this figure we can see that for the zone between the energy range of
-0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
-$45^{\circ}$ is the zone where the maximum response is held for both,
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$.
-% %%%%%%%%%%%%%%%%%
-% %% 1.8 eV - 2.0 eV
-% %% Description of UP |V^{a}|, components and RTP
-% %%%%%%%%%%%%%%%%%
-
-In the top frames of top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-1}
-we present in solid lines the results of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
-the polarization angle to $\alpha=40^{\circ}$ for which the response is
-maximized. In the same panels and frames we present in dashed lines the
-corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
-$\varphi_{a}(\omega,\alpha)$ spin polarization angles related to the right
-scale. Also, in the bottom frames of the panels we present the corresponding
-components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and
-$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
+result of evaluate Eq. \eqref{eq:vv-mag} for the
+\emph{up} structure fixing the velocity in the $x$ and $y$ direction.
+%
+From this figure we can see that the two absolute maxima are obtained for
+energies between 0.084\,eV and 0.093\,eV, in the FIR, and polarization angles
+between $30^ {\circ}$ and $45^{\circ}$.
+% 
+In the top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-1} we present $|
+\mathcal{V}^{\mathrm{x}} (\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}
+(\omega,\alpha)|$ (left scale, black solid line) fixing the polarization angle
+to $\alpha=40^{\circ}$ for which the responses have absolute maxima of
+58.7\,Km/s and 87.9\,Km/s, respectively, for an energy of 0.088\,eV.
+% 
+In same panels we present the corresponding polar (right scale, red dashed
+line) and azimuthal (right scale, blue dashed line) spin polarization angles
+that have values of $\theta_{\mathrm{x}}(\omega,\alpha) = 47^{\circ}$,
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 212^{\circ}$, $\theta_{\mathrm{y}}
+(\omega,\alpha) = 8^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) =
+133^{\circ}$. In this way, the spin is directed upward the third Cartesian
+quadrant of the $xy$ plane when it moves along $x$, and is directed almost
+perpendicularly over the $xy$ plane when it moves along $y$.
+% 
+Also from this figure we have that when the spin moves along $x$ the angles are
+almost constant for the peak of the response having variations of $\pm
+2^{\circ}$ but when the spin moves along $y$ the azimuthal angle changes from
+$99^{\circ}$ to $176^{\circ}$
+
 \begin{figure}[t]
@@
     \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
-    \\
+    \\ \vspace{4mm}
     \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
@@
 % %%%%%%%%%%%%%%%%%
-% %% 1.8 eV - 2.0 eV
-% %% Description of UP |V^{a}|, components and RTP
-% %%%%%%%%%%%%%%%%%
-From the top panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that for an
-incoming bean with energy of 0.088\,eV the three components have similar
-contributions with values of
-% 
-$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)=-36.5$\,Km/s,
-$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)=-23.2$\,Km/s, and
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)= 39.8$\,Km/s resulting in a response
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s being this value the
-absolute maximum obtained when the spin-velocity is fixed in the $x$ direction.
-% 
-{\color{red} To this value corresponds polar and azimuthal spin polarization
-angles of $\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upward
-the third Cartesian quadrant of the $xy$ plane.
-% 
-Also from this figure we have that those angles values are held for almost all
-the peak of the response having variations of $\pm 2^{\circ}$ each one.
-% 
-Now, from the bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we have that the
-components have contributions of
-% 
-$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)= -7.9$\,Km/s 
-$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)=  8.6$\,Km/s, and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)= 87.2$\,Km/s 
-% 
-resulting in a response $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=87.9$\,Km/s.
-This value is the absolute maximum obtained when the spin-velocity is fixed in
-the $\mathrm{y}$ direction and is 1.5 times more intense than the maximum of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this
-absolute maximum corresponds spin polarization polar and azimuthal angles
-$\theta_{\mathrm{y}}(\omega,\alpha) = 8^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 133^{\circ}$ being directed the spin
-almost perpendicularly over the $xy$ plane and  localized on the first
-Cartesian quadrant.}
-% 
-In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case
-for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is
-held at $8^{\circ}$ for the peak of the response having variations of $\pm
-2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$
-having a value of $133^{\circ}$ for the maximum.
-% 
-We also found that since the onset of the response till an energy for the
-incoming beam of 0.118\,eV the components of both responses, have no change in
-the spin polarization-velocity direction. Finally, after this last energy value
-the responses go to zero.
-% %%%%%%%%%%%%%%%%%
 % %% 1.80 eV - 2.10 eV
@@
 % %%%%%%%%%%%%%%%%%
-Also there is another energy range of interest for an incoming energy beam from
-1.80\,eV to 2.10\,eV, corresponding to visible radiation, presented in Fig.
-\ref{fig:up-3d-vva-2} where two local of both responses are obtained for the
-\emph{up} structure for energies of 1.934\,eV and 1.972\,eV
-fixing again the polarization angle to $40^{\circ}$.
-% %%%%%%%%%%%%%%%%
-% %% Starting description of UP |V^{x}|, components and RTP
-% %%%%%%%%%%%%%%%%
-{\color{red} We found that for both cases the components have similar
-contributions for each response and for 1.934\,eV result in values of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 6.6$\,Km/s for the spin velocity
-moving along the $x$ direction with polar and azimuthal spin polarization
-angles $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin directed over
-the first Cartesian quadrant of the $xy$ plane;
-% 
-for the spin moving along the $\mathrm{y}$ direction we have a response
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=28.7$\,Km/s with polar and azimuthal
-spin polarization angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ being  the spin directed over
-the first Cartesian quadrant of the $xy$ plane.
-% 
-Alike, for an incoming energy beam of 1.972\,eV we found the second and more
-intense local maxima for which all the components have similar contributions
-for both responses.
-% 
-This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| =
-9.9$\,Km/s and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with
-spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,
-$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$,
-$\theta_{\mathrm{y}}(\omega,\alpha) = 127^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being the spin directed
-downward the third Cartesian quadrant of the $xy$ plane when it moves in the
-$x$ direction and downward the third Cartesian quadrant when it moves along the
-$y$ direction.}
-% 
-Also all the components of the responses keep the spin polarization positive
-till an energy of the incoming beam equal to 1.954\,eV when the spin
-polarization and current changes the direction. After an energy of 2.05\,eV
-both responses goes to zero.
+
+In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
+result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
+velocity in the $x$ and $y$ direction for other range of energies that present
+a intense response.
+% 
+From this figure we can see that the two local maxima are obtained for energies
+between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
+polarization angles between $30^ {\circ}$ and $45^{\circ}$.
+% 
+From the top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2} we have that
+$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| =  9.8$\,Km/s and
+$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.3$\,Km/s fixing the
+polarization angle to $\alpha=40^{\circ}$ and the beam energy to 1.932\,eV.
+% 
+In same panels we present the corresponding polar and azimuthal spin
+polarization angles that have values of $\theta_{\mathrm{x}}(\omega,\alpha) =
+129^{\circ}$, $\varphi_{\mathrm{x}}(\omega,\alpha) = 229^{\circ}$,
+$\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and $\varphi_{\mathrm{y}}
+(\omega,\alpha) = 227^{\circ}$ being constant all of them in the peak of the
+local maxima. Then, the spin is directed downward the third Cartesian quadrant
+of the $xy$ plane when it moves along $x$ and $y$ directions.
 
@@
 
-\textbf{Alt structure.}
+\subsubsection{Alt structure}
+
 \begin{figure}[tb]
@@
     \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
-    \\
+    \\ \vspace{4mm}
     \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
@@
 % %%%%%%%%%%%%%%%%%
-{\color{red} For the \emph{alt} structure we analyzed the energy range from
-0.6\,eV to 1.0\,eV in Fig. \ref{fig:alt-3d-vva}, corresponding to the NIR
-radiation, where we found a local maxima and the most intense responses for
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$.}
-%
-From this figure we can see that for the zone between the energy range of
-0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$ is the zone where the maximum for both responses is held.
-% %%%%%%%%%%%%%%%%
-% %% Starting description of ALT |V^{a}|, components and RTP
-% %%%%%%%%%%%%%%%%
-In the top frames of top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp}
-we present the spectra of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ fixing the polarization angle to
-$\alpha=145^{\circ}$ for which the response is maximized and its corresponding
-polar and azimuthal angles; in the bottom frames of same panels we present the
-corresponding three components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
-$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
-% 
-{\color{red} Making the analysis when the energy of the incoming beam is
-0.720\,eV we have similar contributions from the components when the sping
-velocity is along the $x$ diection and a major contribution from
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ when the spin velocity is dierected
-alog $y$ Cartesian axis. This result in values of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 19.4$\,Km/s and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 51.9$\,Km/s with spin polarization
-angles $\theta_{\mathrm{x}}(\omega,\alpha) = 46^{\circ}$,
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 41^{\circ}$,
-$\theta_{\mathrm{y}}(\omega,\alpha) = 141^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 222^{\circ}$ being the spin polarization
-directed over the first Cartesian quadrant of the $xy$ plane when the spin
+
+In top and bottom panels of Fig. \ref{fig:alt-3d-vva} we present the
+result of evaluate Eq. \eqref{eq:vv-mag} for the
+\emph{up} structure fixing the velocity in the $x$ and $y$ direction.
+% 
+From this figure we have that the relative maxima for the spin velocity along
+$x$ and $y$ are obtained for energies between 0.70\,eV to 0.75\,eV and the
+absolute maxima are obtained for energies between 0.90\,eV and 0.93\,eV, all
+cases in the NIR radiation, and polarization angles between 120$^{\circ}$ and
+150$^{\circ}$.
+% 
+From the top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we have that
+that the local maxima are $|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| =
+19.4$\,Km/s and $|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 51.9$\,Km/s
+fixing the energy to 0.720\,eV and the absolute maxima are
+$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| = 30.9$\,Km/s and
+$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 52.2$\,Km/s fixing the energy to
+0.912\,eV all for a polarization angle $\alpha=145^{\circ}$.
+% 
+The corresponding polar and azimuthal angles for the local maxima are
+$\theta_{\mathrm{x}} (\omega,\alpha) = 46^{\circ}$, $\varphi_{\mathrm{x}}
+(\omega,\alpha) = 41^{\circ}$, $\theta_{\mathrm{y}} (\omega,\alpha) =
+141^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) = 222^{\circ}$ being the
+spin directed over the first Cartesian quadrant of the $xy$ plane when the spin
 velocity is directed along $x$ and directed downward the third Cartesian
-quadrant when the spin velocity is directed along $y$.
-% 
-Then, for an energy of 0.912\,eV we have values of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=30.9$\,Km/s and
-$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 52.3$\,Km/s. The first of them
-have a major contribution from the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
-component and the second one having similar contributions from all of three
-components. They result in polar and azimuthal angles
-$\theta_{\mathrm{x}}(\omega,\alpha) = 154^{\circ}$,
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 290^{\circ}$,
-$\theta_{\mathrm{y}}(\omega,\alpha) = 129^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 229^{\circ}$ being the spin polarization
-directed downward the fourth Cartesian quadrant of the $xy$ plane when the spin
-velocity is directed along $x$ and downward the third Cartesian quadrant of the
-$xy$ plane when the spin velocity is directed along $y$.}
-% 
-Finally we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
-negative keeping the same spin polarization and velocity direction since the
-onset of the response to a energy of the incoming beam of 0.886\,eV when the
-response decreases and goes to zero.
+quadrant when the spin velocity is directed along $y$. Finally, the angles for
+the absolute maxima are $\theta_{\mathrm{x}}(\omega,\alpha) = 154^{\circ}$,
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 290^{\circ}$, $\theta_{\mathrm{y}}
+(\omega,\alpha) = 129^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) =
+229^{\circ}$ being the spin polarization directed downward the fourth Cartesian
+quadrant when the spin velocity is directed along $x$ and downward the third
+Cartesian quadrant when the spin velocity is directed along $y$.
 
@@
 
-\section{Layer-by-layer analysis} % (fold)
+\subsection{Layer-by-layer analysis} % (fold)
 \label{sec:res-layer_by_layer_analysis}
 
-{\color{blue} 
-% 
 As mentioned before in in the beginning of this section the \emph{up} and
@@
 layer-by-layer contribution for $|\mathcal{V}_{\sigma^{\mathrm{b}}}
-(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$. Here we
-present the decomposition only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$. 
+% 
+In Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell} we present the layer
+division needed to calculate the layer-by-layer contribution for the
+$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ and
+$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ presented in Eqns.
+\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was
+divided in two layers, the first comprised of the top hydrogen atoms denoted by
+the number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc}
+and the second comprised of carbon atoms and denoted by the number 2. The
+\emph{alt} structure was divided in six layers denoted with numbers from 1 to 6
+in Table \ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and
+sixth layers correspond to hydrogen atoms in the top and bottom positions and
+from the second to the fifth correspond to carbon atoms placed in different
+positions.
+% 
+Here we present the decomposition only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}
 (\omega,\alpha)|$ and for the corresponding components of the \emph{up}
@@
 % layered responses.
-% 
-}
 % 
@@
 % %%%%%%%%%%%%%%%%
-{\color{blue} From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1}
-we have that when the energy is fixed to 0.088\,eV almost all the response of
-the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
+From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1} we have that
+when the energy is fixed to 0.088\,eV almost all the response of the
+$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
 layer comprised by carbon atoms having a minimal reduction produced by the
@@
 carbon layer with but being in this case reinforced by the contribution of the
-hydrogen layer and resulting in a value of 30.3\,Km/s}
+hydrogen layer and resulting in a value of 30.3\,Km/s.
 % %%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%
-{\color{blue} 
-% 
 Finally, for the \emph{alt} structure we have that, for the response $|
@@
 response is quite larger.
-}
 
@@
 
-Spintronics devices are based on the control of spin and electrical charge
-through electrical and optical methods.
-% 
-Semiconductor spintronics gives the development possibility of devices that can
-perform high-volume information manipulation, processing, and storage, for
-computing and communications technologies.\cite{awschalomNP2007} 
-% 
 We have performed an \emph{ab initio} calculation for the SVI by one-photon
 absorption of linearly polarized light in the \emph{up} and \emph{alt} 2D
-hydrogenated graphene structures that could result in spintronics devices
-development. This effect does not seem to have been reported previously.
-% 
-We calculated the responses for two cases: when the spin polarization is fixed
-along the Cartesian coordinates and when the spin velocity is directed along
-the $x$ and $y$ Cartesian directions on the $xy$ surface of the structures. We
-found that  the SVI is very susceptible to the characteristics of the
-structures presenting an anisotropic behavior.
-% 
-We found that for both structures it is possible to generate a SVI comparable
-being the response of the \emph{alt} structure comparable with GaAs and CdSe
-and the response of the \emph{up} structure much more intense than all.
-
-We analyzed the SVI as a function of the energy of the incoming beam and the
-polarization angle for the \emph{up} and \emph{alt} structures for the cases
-when the spin is polarized along the three Cartesian directions with a
-propagating angle on the surface of the structures measured in the counter-%
-clockwise direction from the $x$ Cartesian direction. We found that the most
-intense response was when the spin is directed perpendicularly to the plane of
-the structures in the $z$ direction.
-% 
-For this condition we found that the \emph{up} structure reaches a maximum
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s directed in
-an angle $\gamma_{\mathrm{z}} (\omega,\alpha) = 160^{\circ}$ on the $xy$ plane
-for an energy of the incoming beam of 0.088\,eV, for which the response is
-maximized, and polarization angle $\alpha
-= 40^{\circ}$.
-% 
-Similarly for the \emph{alt} structure we found that the maximum reached is $|
-\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s at $\gamma_{
-\mathrm{z}} (\omega,\alpha) = 50^{\circ}$ for an energy of the incoming beam of
-0.912\,eV and polarization angle $\alpha = 145^{\circ}$.
-% 
-Also we found two angles of interest for which the SVI, with spin polarized in
-the $z$ direction, propagates collinearly or perpendicularly to the
-polarization angle of the incoming beam. With this condition and fixing again
-the energy of the incoming beam to 0.088\,eV we found that
-$\gamma_{\mathrm{z}\parallel} (\omega,\alpha=65.5^{\circ}) = 65.5^{\circ}$
-resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
-82.3$\,Km/s and $\gamma_{\mathrm{z}\perp} (\omega,\alpha = 155.5^{\circ}) =
-65.5^{\circ}$ resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)| = 24.8$\,Km/s.
-% 
-Alike, for the \emph{alt} structure fixing the energy of the incoming
-beam to 0.912\,eV we found that the parallel and collinear angles are $\gamma_{
-\mathrm{z}\parallel} (\omega,\alpha = 53.5^{\circ}) = 53.5^{\circ}$ and
-$\gamma_{\mathrm{z}\perp} (\omega,\alpha = 140^{\circ}) = 50^{\circ}$ resulting
-in values of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s
-and $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s,
-respectively.
-
-We also examined the SVI for the cases when the velocity is directed along the
-$x$ and $y$ Cartesian coordinates on the $xy$ plane of the \emph{up} and
-\emph{alt} structures. We also defined the polar and azimuthal angles, the
-first measured from the positive to the negative $z$ Cartesian coordinate
-perpendicular to the structure and the second from the positive $x$ Cartesian
-direction in the counter-clockwise sense on the $xy$ plane.
-% 
-For this case we found that the responses for the \emph{up} structure,for an
-energy of the incoming bean of 0.088\,eV, reach the maximum values  of
-$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s wit polar and azimuthal
-% spin polarization angles $\theta_{\mathrm{x}} (\omega,\alpha)=47$ and
-% $\varphi_{\mathrm{x}} (\omega,\alpha)=212$, 
-directed upward the third Cartesian quadrant of the $xy$ plane; and
-$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)|=87.9$\,Km/s with polar and
-azimuthal spin polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) =
-8^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) = 133^{\circ}$ directed
-almost perpendicularly over the first Cartesian quadrant over the $xy$ plane.
-% 
-Likewise, for the \emph{alt} structure we found that, for an energy of the
-incoming beam of 1.972\,eV, the responses reach maximum values of
-$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| = 9.9$\,Km/s with spin
-% polarization angles $\theta_{\mathrm{x}} (\omega,\alpha) = 129^ {\circ}$ and
-% $\varphi_{\mathrm{x}} (\omega,\alpha)=229^{\circ}$ 
-directed downward the third Cartesian quadrant of the $xy$ plane; and
-$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.4$\,Km/s with spin
-polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and
-$\varphi_{\mathrm{y}} (\omega,\alpha)=227^{\circ}$ directed downward the third
-Cartesian quadrant.
-
-Novel PSC devices for spintronics applications has been
-proposed.\cite{gotteNat16, pershinPRB08} One of the difficulties to achieve the
-development of spin current and PSC semiconductor devices is the fact that the
-spin relaxation time in a semiconducting media is short disabling the spin
-transport and then resulting in a no observable spin
-current.\cite{murakamiSc03}
+hydrogenated graphene structures that and we made the calculation for the case
+when the spin is polarized in the $z$ direction or when the velocity is
+directed along $x$ or $y$; this effect does not seem to have been reported
+previously. 
+% 
+This SVI is very sensitive to the symmetry characteristics of the structures
+presenting an anisotropic behavior. We found that the \emph{up} structure has
+the most intense response resulting in $|\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)| = 95.8$\,Km/s and $|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)|
+= 87.9$\,Km/s for an energy of the incoming beam of 0.088\,eV. Also the
+response of the \emph{alt} structure is comparable to the response of GaAs and
+CdSe bulk semiconductors.
 % 
 The spin relaxation time in pure and doped graphene is long enough in the order
-from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertler2009electron} The,
+from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} The,
 according to our results the \emph{alt} structure is a good candidate and the
@@
 
+\appendix
+\section{Math derivation}
+\label[appendix]{sec:mathder}
+
+From Eq. \eqref{eq:dotO} and Eq. \eqref{eq:k-timerev}, using
+$\mathbf{r}_{nm}(-\mathbf{k}) = \mathbf{r}_{mn}(\mathbf{k})$ and taking
+$\epsilon \rightarrow 0$, we have 
+\begin{widetext}
+\begin{align}
+\dot K^{\mathrm{ab}}
+&=
+\frac{e^2}{i\hbar^2}
+\int\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
+\left(
+\frac{1}{\omega-\omega_{c'v}-i\epsilon}
+-
+\frac{1}
+{\omega-\omega_{cv}+i\epsilon}
+\right) 
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&=
+\frac{e^2}{i\hbar^2}
+\int\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+\Big(
+(K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}) \big |_{\mathbf{k}>0}
++
+(K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}) \big |_{\mathbf{k}<0}
+\Big) 
+\nonumber\\
+&\times 
+\left(
+\frac{1}{\omega-\omega_{c'v}-i\epsilon}
+-
+\frac{1}
+{\omega-\omega_{cv}+i\epsilon}
+\right) 
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&=
+\frac{e^2}{i\hbar^2}
+\int_{\mathbf{k}>0}\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+\Big(
+K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
++
+K^{\mathrm{ab}*}_{c'c}
+r^{\mathrm{c}}_{vc}r^{\mathrm{d}}_{c'v}
+\Big) 
+\nonumber\\
+&\times 
+\left(
+\frac{1}{\omega-\omega_{c'v}-i\epsilon}
+-
+\frac{1}
+{\omega-\omega_{cv}+i\epsilon}
+\right) 
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&=
+\frac{e^2}{i\hbar^2}
+\int_{\mathbf{k}>0}\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+\Big(
+K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
++
+(K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'})^*
+\Big) 
+\nonumber\\
+&\times 
+\left(
+\frac{1}{\omega-\omega_{c'v}-i\epsilon}
+-
+\frac{1}
+{\omega-\omega_{cv}+i\epsilon}
+\right) 
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&=
+\frac{e^2}{i\hbar^2}
+\frac{1}{2}
+\int\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+2\mathrm{Re}\Big[
+K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
+\Big]
+\Big\{
+\mathcal{P}\left(
+\frac{\omega_{c'c}}{(\omega-\omega_{c'v})(\omega-\omega_{cv})}
+\right) 
+\nonumber\\
+&+
+i\pi 
+\left(
+\delta(\omega-\omega_{c'v}) 
++
+\delta(\omega-\omega_{cv}) 
+\right) 
+\Big\}
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&\approx 
+\frac{\pi e^2}{\hbar^2}
+\int\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+\mathrm{Re}\Big[
+K^{\mathrm{ab}}_{c'c}
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
+\Big]
+\Big(
+\delta(\omega-\omega_{c'v}) 
++
+\delta(\omega-\omega_{cv}) 
+\Big) 
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
+\nonumber\\
+&=
+\frac{\pi e^2}{\hbar^2}
+\int\frac{d^3k}{8\pi^3}
+\sum_{vcc'}
+\mathrm{Re}
+\Big[ 
+K^{\mathrm{ab}}_{c'c} 
+r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
++ 
+K^{\mathrm{ab}}_{cc'} 
+r^{\mathrm{c}}_{c'v}r^{\mathrm{d}}_{vc}
+\Big]
+\delta(\omega-\omega_{cv})  
+E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega),
+\label{eq:dotk-dev}
+\end{align}
+since $\omega_{cc'} \sim 0$ and we exchange $c\leftrightarrow c'$. Now, from
+Eq. \eqref{eq:k-timerev} we obtain that 
+\begin{align}
+\mathrm{Re} \left[ 
+K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} 
+\right] 
+=&
+\frac{1}{2} \left(
+ K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} +
+(K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} )^{*}
+\right)
+\nonumber \\
+=&
+\frac{1}{2} \left(
+ K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} +
+(K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv} )
+\right)
+\nonumber \\
+=&
+\mathrm{Re}
+\left[
+K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
+\right]
+\label{eq:realk}
+\end{align}
+and then, Eq. \eqref{eq:dotk-dev} can be written as
+\begin{align}
+\dot{K}^{\mathrm{ab}}
+=&
+\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
+\sum_{vcc'} \mathrm{Re} 
+\left[ 
+K^{\mathrm{ab}}_{c'c} r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
+K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
+\right]
+\delta(\omega - \omega_{cv}) 
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega) 
+\nonumber \\
+=&
+\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
+\sum_{vcc'} \mathrm{Re} 
+\left[ 
+K^{\mathrm{ab}}_{c'c} 
+\left(
+r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
+r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
+\right)
+\right]
+\delta(\omega - \omega_{cv}) 
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
+\nonumber \\
+=&
+\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
+\sum_{vcc'} \mathrm{Re} 
+\left[ 
+K^{\mathrm{ab}}_{c'c} 
+\left(
+r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
+(\mathrm{c} \leftrightarrow \mathrm{d})
+\right)
+\right]
+\delta(\omega - \omega_{cv}) 
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
+\nonumber \\
+=&
+\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
+\sum_{vcc'} \mathrm{Re} 
+\left[ 
+K^{\mathrm{ab}}_{c'c} 
+\left(
+r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv} + 
+(\mathrm{c} \leftrightarrow \mathrm{d})
+\right)
+\right]
+\delta(\omega - \omega_{cv}) 
+E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
+\label{eq:k-final}
+\end{align}
+\end{widetext}
+
 \bibliography{article.bib}

### 2017-07-12 mu/article/makeplots.sh
Making plots in the BMS way

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+mpplotlin.sh plots/vab-str-comp.g
+mv plots/fig.pdf plots/vab-str-comp
+

### 2017-07-14 mu/article/article-review4_1.tex
Adding new plots to better explain the results.

--- 2017-07-01 mu/article/article.tex
@@
 \documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
-
 \usepackage{amsmath}    % need for subequations 
@@
                         % documents and URLs 
-\usepackage{blindtext}  % fill text
+%\usepackage{blindtext}  % fill text 
 \usepackage[dvipsnames]{xcolor}
 \usepackage{multirow}
-\usepackage[capitalize]{cleveref}
+%\usepackage[capitalize]{cleveref}
 % \usepackage{showframe}
 \usepackage[inline]{showlabels}
+\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
+% \input{/Users/bms/util/definitions}
 
@@
 \begin{abstract}
-\blindtext
+perro
+%\blindtext
 \end{abstract}
@@
 % structures.
-{\color{red}
+{
+% \color{red}
 % 
@@
 % 
-{\color{red}
+{
+% \color{red}
 % 
@@
 
+{\color{red}
 In PSCs there is no net motion of electrical charge and spin-up electrons move
@@
 at opposite $\mathbf{k}$ points are in opposite directions.
-
-Using the multiple scale approach to solve the equation of motion for the
-single particle density matrix $\rho_{mn}(\mathbf{k};t)$ we have that 
-\begin{equation*}
-\begin{aligned}
-&\frac{\partial \rho_{cc'}}{\partial t} =
--i (\omega_{cc'} - i \epsilon) \rho_{cc'}
-+
+}
+
+%%%BMSD
+The operator that describes the electronic PSC is written as
+\begin{align}\label{z.1}
+\hat K^{\rma\rmb}=\frac{1}{2}\left( \hat v^\rma \hat S^\rmb 
++\hat  S^\rmb \hat v^\rma\right) 
+,
+\end{align} 
+where $\hat\bfv=[\hat\bfr,\hat H_0]/i\hbar$ is the velocity operator, with
+$\hat \bfr$ the position operator,  $\hat H_0$ the unperturbed
+ground state Hamiltonian, and
+the Roman superscripts  indicate Cartesian coordinates. 
+To obtain the expectation value of 
+$\hat K^{\rma\rmb}$, we use the length gauge for the perturbing
+Hamiltonian, written as
+\begin{align}\label{z.2}
+\hat H_{\text{p}}=-e\hat\bfr\cdot\bfE(t)
+,
+\end{align}   
+where the electric field of the applied laser is given by
+\begin{align}\label{z.3}
+\bfE(t)= \bfE(\go)e^{-i\go t} + \bfE^*(\go)e^{i\go t}
+.
+\end{align}
+In order to 
+calculate the response of the system to $\bfE(t)$, one needs to
+take into account the excited coherent superposition
+of the spin-splited conduction bands inherent to the 
+noncentrosymmetric 
+semiconductors considered in this work.
+%Although, this splitting is small [15,16], is required to obtain the
+%correct results\cite{nastosPRB07}.
+% The conduction bands in the 
+% noncentrosymmetric  
+% semiconductors  
+% are spin split by a small amount,[15,16] typically
+%   smaller than the energy width of the laser pulse, and so the pulse
+%   excites a coherent superposition of the two conduction bands. Even
+%   for very long pulses with narrow energy widths, dephasing effects
+%   lead to an energy width of the bands large enough that spin-split
+%   states can become quasidegenerate. 
+To include the coherences, we follow Ref.~\onlinecite{nastosPRB05} and
+use a multiple
+scale approach that solves the equation of motion for the single
+particle density matrix $\gr_{mn}(\bfk;t)$, leading to
+\begin{align}\label{z.4}
+&\frac{\partial \rho_{cc'}(\bfk)}{\partial t} =
 \frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
 {i \hbar^{2}}
-\times \\
-& \quad \sum_{v}r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'}
-\left( \frac{1}{\omega - \omega_{c'v} - i \epsilon} 
+\sum_{v}r^{\mathrm{a}}_{cv}(\bfk) r^{\mathrm{b}}_{vc'}(\bfk)
+\nonumber\\
+&\times 
+\left( \frac{1}{\omega - \omega_{c'v}(\bfk) - i \epsilon} 
 - 
-\frac{1}{\omega - \omega_{cv} + i \epsilon} \right).
-\end{aligned}
-\end{equation*}
-Taking in the first term $\epsilon \rightarrow 0$ and changing the density
-matrix operator to the interaction representation, $\tilde{\hat{\rho}} = e^{iH_
-{0}t/\hbar} \hat{\rho} e^{-iH_{0}t/\hbar}$, with $H_{0}$ the ground state
-Hamiltonian, the matrix elements can be written as
-\begin{equation*}
-\tilde{\rho}_{cc'(\mathbf{k})} 
-= \langle c\mathbf{k}| \tilde{\hat{\rho}} | c'\mathbf{k} \rangle
-= e^{i \omega_{cc'}t} \rho_{cc'}(\mathbf{k}).
-\end{equation*}
-where $H_{0}|n\mathbf{k}\rangle = \hbar \omega_{n}(\mathbf{k})|n
-\mathbf{k}\rangle$ with $\hbar \omega_{n}(\mathbf{k})$ the energy of the
+\frac{1}{\omega - \omega_{cv}(\bfk) + i \epsilon} \right)
+,
+\end{align}
+where we assumed that the conduction bands $c$ and $c'$
+are quasidegenerate  states and we take $\ge\to 0$ at the end of the
+calculation.  The spin-splitting of the valence ($v$) bands is very
+small, and is neglected throughout this work.\cite{??} 
+% 􏱈 are close to  
+% one another, and that the pulse is short enough so that the energy
+% width overlaps the two bands, the equation of motion can be
+% solved. Leaving the details of the derivation to Ap- 
+% pendix A, the result for the off-diagonal component 􏰠 􏱈, c  
+%%%BMSU 
+The matriz elements of any operator $\calo$ are given by
+$\calo_{nm}(\bfk)=\bra{n\bfk}\hat\calo\ket{m\bfk}$,
+where 
+$H_{0}|n\mathbf{k}\rangle = \hbar \omega_{n}(\mathbf{k})|n\mathbf{k}\rangle$ 
+with $\hbar \omega_{n}(\mathbf{k})$ the energy of the
 electronic band $n$ at point $\mathbf{k}$ in the irreducible Brillouin zone
-(IBZ), and $|n\mathbf{k}\rangle$ the Bloch state. Then, the time derivative of
-$\tilde{\rho}_{cc'}(\mathbf{k})$ is given by 
-\begin{equation}\label{eq:derden}
-\begin{aligned}
-&\frac{d\tilde{\rho}_{cc'}(\mathbf{k})}{dt} 
+(IBZ),  $|n\mathbf{k}\rangle$ is the Bloch state, and 
+$\go_{nm}(\bfk)=\go_{n}(\bfk)-\go_{m}(\bfk)$.
+Using 
+$\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$
+for the expectation value of an observable $\mathcal{O}$, 
+where $\mathrm{Tr}$ denotes the trace, we obtain
+\begin{align}\label{z.5}
+\mathcal{O} 
+%=&
+%\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c \mathbf{k} 
+%| \hat{\rho} \hat{\mathcal{O}} |
+%c\mathbf{k} \rangle \nonumber \\
+=& 
+\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \rho_{cc'}(\mathbf{k}) 
+\mathcal{O}_{c'c}(\mathbf{k}),
+\end{align}
+where we used 
+the closure
+relationship $\sum_{n}|n\mathbf{k}\rangle \langle n\mathbf{k}| = 1$,
+where $n=v,c$,
+and the fact that $\rho_{vn}(\bfk)=\rho_{nv}(\bfk)=0$ for $n=c,c'$. 
+Therefore, 
+using  Eqs. \eqref{z.4} and \eqref{z.5},
+the
+rate of change of $\mathcal{O}$,
+$\dot{\mathcal{O}} 
 =
-\frac{e^{2} E^\mathrm{a}(\omega) E^{\mathrm{b*}}(\omega)}{i\hbar^{2}} 
-e^{i\omega_{cc'}t} 
-\times \\
-&\quad \sum_{v}r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'}
-\left( \frac{1}{\omega - \omega_{c'v} - i \epsilon} 
-- 
-\frac{1}{\omega - \omega_{cv} + i \epsilon} \right),
-\end{aligned}
-\end{equation}
-where $\epsilon \rightarrow 0$ still needs to be taken. 
-% 
-The expectation value of an observable $\mathcal{O}$ with quantum mechanical
-operator associated $\hat{\mathcal{O}}$ is given by
-\begin{equation}\label{eq:trace}
-\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}}),
-\end{equation}
-where $\mathrm{Tr}$ denotes the trace. Then
-\begin{align}
-\mathcal{O} 
-=&
-\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c \mathbf{k} 
-| \hat{\rho} \hat{\mathcal{O}} |
-c\mathbf{k} \rangle \nonumber \\
-=& 
-\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \tilde{\rho}_{cc'}(\mathbf{k}) 
-\mathcal{O}_{c'c}(\mathbf{k}),
-\label{eq:expectation}
-\end{align}
-where we used the interaction picture representation,
-$\tilde{\mathcal{O}}_{cc'} = \langle c'\mathbf{k} | e^{iH_{0}t/\hbar}
-\hat{\mathcal{O}} e^{-iH_{0}t/\hbar} | c\mathbf{k} \rangle$, and the closure
-relationship $\sum_{c}|c\mathbf{k}\rangle \langle c\mathbf{k} = 1$. So, the
-rate of change of $\mathcal{O}$ can be written from Eq. \eqref{eq:derden}, Eq.
-\eqref{eq:trace}, and Eq. \eqref{eq:expectation} as
+\mathrm{Tr} \left( \frac{\partial \hat{{\rho}}}{\partial t} \hat\calo \right)
+$,
+ is given by
 \begin{align}
 \dot{\mathcal{O}} 
-&=
-\mathrm{Tr} \left( \frac{d \hat{\tilde{\rho}}}{dt} 
-\tilde{\mathcal{O}} \right), 
+&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
+\sum'_{cc'} \mathcal{O}_{c'c}(\bfk) 
+r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  \times
 \nonumber \\
-&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
-\sum \mathcal{O}_{c'c} r^{\mathrm{a}}_{cv} r^{\mathrm{b}}_{vc'} \times
-\nonumber \\
-& \left( \frac{1}{\omega - \omega_{c'v} - i\epsilon} - 
-\frac{1}{\omega - \omega_{cv} + i\epsilon} \right)
+& \left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 
+\frac{1}{\omega - \omega_{cv}(\bfk)  + i\epsilon} \right)
 E^{\mathrm{a}}(\omega) E^{\mathrm{b*}}(\omega)
 \label{eq:dotO}
+.
 \end{align}
-
-Replacing the operator $\mathcal{O} \rightarrow \hat{K}^{\mathrm{ab}} \equiv v^
-{\mathrm{a}} S^{\mathrm{b}}$ the matrix elements are given by
-\begin{equation}
-K^{\mathrm{ab}}_{nm}(\mathbf{k}) = 
-\sum_{l} v^{\mathrm{a}}_{nl}(\mathbf{k})S^{\mathrm{b}}_{lm}(\mathbf{k}), 
-\label{eq:velspimatelem}
-\end{equation}
-and using time-reversal invariance it follows that 
-\begin{equation}
-K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}). 
-\label{eq:k-timerev}
-\end{equation}
-Now the time derivative $\dot{K}^\mathrm{ab}$ can be obtained as we proceeded
-in Eq. \eqref{eq:dotk-dev} of Appendix \ref{sec:mathder} and then we write
+Replacing  $\hat\calo \rightarrow \hat{K}^{\mathrm{ab}}$, in 
+above expression, one can show that
 \begin{equation}
@@
 \end{equation}
-where the pure spin-current pseudotensor components
+where repeated cartesian are summed, and 
 \begin{equation}\label{eq:mu}
@@
 \frac{\pi e^{2}}{\hbar^{2}} \int 
-\frac{d^{3}K}{8 \pi^{3}} \times \\
-\sum_{vcc'}^{'}
-\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'} 
+\frac{d^{3}k}{8 \pi^{3}} \sum'_{vcc'}
+  \delta(\omega-\omega_{cv}(\bfk) 
+\\
+\times\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 
 \left(  
-r^{\mathrm{c}}_{vc'} 
-r^{\mathrm{d}}_{cv } +
+r^{\mathrm{c}}_{vc'}(\bfk)   
+r^{\mathrm{d}}_{cv }(\bfk)  +
 (c \leftrightarrow d)  
 \right) 
-\right] \delta(\omega-\omega_{cv}),
+\right]
+,  
 \end{aligned}
 \end{equation} 
-are obtained from Eq. \eqref{eq:k-final} of the Appendix.
-% 
-The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
-sum only covers these states and since $\mu^{\mathrm{abcd}}(\omega)$ is real we
-have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$. This
-previous equation is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05}
+is the pseudotensor that describes the rate of change of the  PSC process in semiconductors.
+To derive above we used  
+$
+K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}). 
+$
+that follows from time-reversal invariance. 
+The prime $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
+sum only covers these states.  Since $\mu^{\mathrm{abcd}}(\omega)$ is real we
+have that $\mu^{\mathrm{abcd}}(\omega) =
+\mu^{\mathrm{abdc}}(\omega)$. 
+We remark that Eq.~\eqref{eq:mu} 
+ is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05}
 obtained by using the semiconductor optical Bloch equations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Spin velocity injection} % (fold)
-\label{sec:theory-pure_spin_current}
-
-We define the SVI as the velocity at which the spin, polarized along the
-direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
+Using the closure relation,
+\begin{equation}
+K^{\mathrm{ab}}_{cc'}(\mathbf{k}) = \frac{1}{2}
+\sum_{l=v,c}
+\left(v^{\mathrm{a}}_{cl}(\mathbf{k})S^{\mathrm{b}}_{lc'}(\mathbf{k})
++S^{\mathrm{b}}_{cl}(\mathbf{k}) v^{\mathrm{a}}_{lc'}(\mathbf{k})
+\right)
+.
+\label{eq:velspimatelem}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\subsection{Spin velocity injection} % (fold)
+%\label{sec:theory-pure_spin_current}
+Now, we define the spin velocity injection (SVI) as
 \begin{equation}\label{eq:vab-w}
@@
 \end{equation}  
-where $\dot{K}^{\mathrm{ab}} (\omega)$ is given by Eqns. \eqref{eq:dotk} and
-\eqref{eq:mu} and the carrier
-injection rate,
-$\dot{n}(\omega)$, are given by
-% 
+that gives 
+the velocity, along the direction $\mathrm{a}$, at which the spin moves polarized along the 
+direction $\mathrm{b}$.
+The carrier injection rate $\dot n(\go)$ is written as,\cite{nastosPRB05}
 \begin{equation}
@@
 \end{equation}
-where $\xi^{\mathrm{ab}}(\omega)$ are the carrier
-generation rate tensor components. 
-% 
-Since we have 2D structures we use an incoming electric field parallel to the
-surface, $\mathbf{E}^{\mathrm{a}}(\omega,\alpha) = E^{\mathrm{a}}(\omega)
-e^{i\alpha}$, where $\alpha$ corresponds to the linear polarization angle.
-% 
-Then from Eq. \eqref{eq:dotk}, Eq. \eqref{eq:vab-w}, and \eqref{eq:dotn}, and
-including the polarization angle dependence we obtain
+where the tensor 
+\begin{equation}\label{eq:xi}
+\begin{aligned}
+\xi^{\mathrm{ab}}(\omega)
+&
+=
+\frac{2\pi e^{2}}{\hbar^{2}} \int 
+\frac{d^{3}k}{8 \pi^{3}}
+\\\nonumber
+&\times \sum_{vc}
+r^{\mathrm{a}}_{vc'}(\bfk)  
+r^{\mathrm{b}}_{cv }(\bfk)  
+\delta(\omega-\omega_{cv}(\bfk) 
+, 
+\end{aligned}
+\end{equation}
+is related to the imaginary part of the linear optical 
+response tensor by
+$\mathrm{Im}[\ge^{\rma\rmb}(\go)]=2\pi\ge_0\hbar\xi^{\rma\rmb}(\go)$.
+
+The function $\calv^{\rma\rmb}(\go)$ allow us to quantify two very
+important aspects of PSC. On one hand, we can fix the spin direction
+along $\mathrm{b}$,   
+and calculate the resulting electron velocity.  
+On the other hand, we can fix de velocity of the electron
+along $\mathrm{b}$,  and study the resulting direction along which the
+spin is polarized.
+To this end, the added advantage of  2D structures, besides choosing
+them noncentrosymmetric, is that we can use an incoming linearly
+polarized beam of light
+at normal incidence, and use the  direction of the polarized  electric
+field to control $\calv^{\rma\rmb}(\go)$.
+Indeed, writing 
+$\bfE(\omega) = E_0(\omega)(\cos\ga\,\hat\bfx+\sin\ga\,\hat\bfy)$
+where $\alpha$ is the polarization angle, we obtain from
+ Eq. \eqref{eq:vab-w}
+that
 \begin{widetext}
@@
 \mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
-% &= 
-% \frac{2}{\hbar}
-% \frac{\mu^{\mathrm{abxx}}(\omega)
-% E^{2}(\omega)\cos^{2}(\alpha) + 
-% \mu^{\mathrm{abyy}}(\omega)
-% E^{2}(\omega)\sin^{2}(\alpha) + 
-% 2\mu^{\mathrm{abxy}}(\omega)
-% E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
-% {\xi^{\mathrm{xx}}(\omega)
-% E^{2}(\omega)\cos^{2}(\alpha) + 
-% \xi^{\mathrm{yy}}(\omega)
-% E^{2}(\omega)\sin^{2}(\alpha)},
-% \nonumber \\
 &= 
-\frac{2}{\hbar}
-\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
-\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
-\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
-{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
-\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
+\frac{2}{\hbar\xi(\go)}
+\left(\mu^{\mathrm{abxx}}(\omega)\cos^{2}\alpha + 
+\mu^{\mathrm{abyy}}(\omega)\sin^{2}\alpha + 
+\mu^{\mathrm{abxy}}(\omega)\sin 2\alpha\right)
 \label{eq:vab-aw}
@@
 \end{widetext}
-% 
-Two interesting possibilities to analyze the SVI are fixing the spin along $z$,
-directed perpendicularly to the surface of the structure, or fixing the
-velocity along $x$ or $y$ on the $xy$ plane of the structures. Also we can
-analyze the SVI contribution coming from each layer of the structure. In
-following subsections we present these three cases.
+as for the structures chosen in this article,
+$\xi^{\mathrm{xx}}(\go)=\xi^{\mathrm{yy}}(\go)\equiv\xi(\go)$, and $\xi^{\mathrm{xy}}(\go)=0$.
+Now, we formalize our two options for $\calv^{\rma\rmb}$.
+%
+
+% Two interesting possibilities to analyze the SVI are fixing the spin along $z$,
+% directed perpendicularly to the surface of the structure, or fixing the
+% velocity along $x$ or $y$ on the $xy$ plane of the structures. Also we can
+% analyze the SVI contribution coming from each layer of the structure. In
+% following subsections we present these three cases.
 
@@
 
-Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the spin
-velocity with spin polarized along the $\mathrm{b}$ direction as
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of
+the electron's in plane
+velocity with it's spin polarized along the $\mathrm{b}$ direction as
 \begin{equation}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
-=
+\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)
+\equiv
 \sqrt{
@@
 \end{equation}
-and the angle at which the spin velocity is directed on the $xy$ plane as
+and define the angle at which the velocity is directed on the $xy$ plane as
 \begin{equation}
-\gamma_{\mathrm{b}} (\omega,\alpha)
+\gamma_{\gs^\mathrm{b}} (\omega,\alpha)
 =
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
-{\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)} \right),
+{\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)} \right)
+.
 \label{eq:gamma-ang}
 \end{equation}
-where this angle is measured in the counter-clockwise direction from the
-positive $x$. We also define two special angles
+% where this angle is measured in the counter-clockwise direction from the
+% positive $x$. 
+We also define two special angles
 \begin{equation}
-\gamma_{\mathrm{b \parallel}}(\omega,\alpha) = \alpha, 
+\gamma_{\gs^\mathrm{b}}^\parallel(\omega,\alpha) = \alpha, 
 \label{eq:gamma-par} 
@@
 \begin{equation}
-\gamma_{\mathrm{b \perp}}(\omega,\alpha) = \alpha \pm 90^{\circ}.
+\gamma_{\gs\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
 \label{eq:gamma-perp}
 \end{equation}
-The first corresponds to the case when the spin velocity is directed, in the
-same direction of the polarization angle $\alpha$ of the incoming beam and the
-second one corresponds to the case when the spin velocity is directed
-perpendicularly with respect to the polarization angle of the incoming beam.
+corresponding to the electron velocity being parallel or perpendicular
+the incoming polarization, 
+respectively. The subscript $\gs^\rmb$ denotes the spin along $\rmb$.
 
@@
 
-Fixing the velocity along $x$ or $y$ we define the corresponding magnitude as
+Fixing the calculated velocity along $\rma=x$ or $\rma=y$
+ we define it's corresponding magnitude as
 \begin{align}
-|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
+\mathcal{V}_{\mathrm{a}}&(\omega,\alpha) \equiv \nonumber \\
 &\sqrt { 
@@
 [\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
-[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
+[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
 },
@@
 \end{align}
-Then, the spin direction depends on the components of the previous equation and
-so we define the spin orientation polar and azimuthal angles as
+from where we see that the spin would be oriented
+in the $xyz$ system's coordinates
+according to a polar angle
 \begin{align}
@@
 \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
-{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
+{\mathcal{V}_{\mathrm{a}}(\omega,\alpha)} \right),
 & 0 \leq &\theta \leq \pi, 
 \label{eq:polar-ang}
-\\
+\end{align}
+and an azimuthal angle
+\begin{align}
 \varphi_{\mathrm{a}} (\omega,\alpha)
@@
 \end{align}
-% where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
-% positive to the negative $z$ Cartesian coordinate and
-% $\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
-% counter-clockwise direction from the positive $x$ Cartesian coordinate.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Layer by layer %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}
-
-For a layered system we have that the total contribution of Eqns. 
-\eqref{eq:vs-mag} and \eqref{eq:vv-mag} are given \cite{arzatePRB14} by 
-\begin{align}
-|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|
-=& 
-\sum_{\ell=1}^{N_{\mathrm{eff}}}
-|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|
-\label{eq:vs-layer}
-\\
-|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|
-=&
-\sum_{\ell=1}^{N_{\mathrm{eff}}}
-|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|
-\label{eq:vv-layer}
-\end{align}
-where $|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|$ gives the contribution of
-the $\ell^{th}$ layer to the total SVI when the spin is fixed in the
-$\mathrm{b}$ direction or when the velocity is fixed in the $\mathrm{a}$
-direction, respectively. For the structures presented here this layers
-correspond to the total number of layers being two for the \emph{up} structure
-and six for the \emph{alt} structure.
 
@@
 
-We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ and
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ for the
-C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
+We preset the results for 
+and
+$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
+and
+$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ 
+for the
+C$_{16}$H$_{8}$-up  and C$_{16}$H$_{8}$-alt 
+structures being both
 noncentrosymmetric semi-infinite 2D carbon systems with 50\% hydrogenation in
@@
 carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
-\ref{fig:alt-struc} and \ref{fig:up-struc}. The coordinates for the
+\ref{fig:up-struc} and \ref{fig:alt-struc}. The coordinates for the
 \emph{up} and \emph{alt} unit cells of the structures are presented in Tables
@@
 The convergence parameters for the calculations of our results corresponding to
-the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
-40\,Ha, resulting in LDA energy band gaps of 0.72\,eV and 0.088\,eV,
+the \emph{up} and \emph{alt} structures are cutoff energies of 65\,Ha and
+40\,Ha, resulting in LDA energy band gaps of 0.088\,eV and 0.720\,eV,
 respectively. The energy eigenvalues and matrix elements for the \emph{up} and
-\emph{alt} structures were calculated using 14452 $\mathbf{k}$ points and 8452
-$\mathbf{k}$ points in the IBZ.
-% 
-It is known that the DFT with LDA approximation misestimates the energy band
-gap of semiconductors. To correct this one has to include the many-body
-interaction using i.e. the so-called GW approximation but this technique has a
-very high computational cost and is out of the scope in this paper.
-Nevertheless, DFT still remains a mainstream tool for calculating diverse
-properties derived from the electronic band structure.
+\emph{alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
+$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ 
+and $\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron
+method (LATM).\cite{nastosPRB07}
+We neglect the
+anomalous velocity term $\hbar(\bfgs\times\nabla V)/4m^2c^2$, 
+where $V$ is the crystal potential, in 
+ $\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give
+small contribution to PSC.\cite{bhatPRL05}
+Therefore, $[\hat\bfv,\hat\bfS]=0$ and 
+Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat
+S^\rmb=\hat S^\rmb \hat v^\rma$.
+
+% 
+% It is known that the DFT with LDA approximation misestimates the energy band
+% gap of semiconductors. To correct this one has to include the many-body
+% interaction using i.e. the so-called GW approximation but this technique has a
+% very high computational cost and is out of the scope in this paper.
+% Nevertheless, DFT still remains a mainstream tool for calculating diverse
+% properties derived from the electronic band structure.
 
@@
 
-\subsection{Spin velocity injection} % (fold)
+\subsection{SVI: Spin velocity injection} % (fold)
 \label{sec:res-spin_velocity}
@@
 \hline
-\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.2    \\
-             &      &       & 1.94  & $\mathrm{yz}$ &  22.2    \\
-             &      &       & 1.97  & $\mathrm{yz}$ & -29.7    \\
-\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.2    \\
-             &      &       & 0.91  & $\mathrm{yz}$ & -32.9    \\
- CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.9    \\
- GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.6    \\
+\emph{up}    & 2D   & 40    & 0.088  & $\mathrm{yz}$ &  87.2    \\
+             &      &       & 1.938  & $\mathrm{yz}$ &  22.2    \\
+             &      &       & 1.972  & $\mathrm{yz}$ & -29.7    \\
+\emph{alt}   & 2D   & 145   & 0.720  & $\mathrm{yz}$ & -40.2    \\
+             &      &       & 0.912  & $\mathrm{yz}$ & -32.9    \\
+ CdSe        & bulk & 90    & 0.906  & $\mathrm{zz}$ & -26.9    \\
+ GaAs        & bulk & 90    & 2.312  & $\mathrm{xx}$ & -21.6    \\
 \hline
@@
 
-Using the Eq. \eqref{eq:vab-aw}, we calculated the
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{up} and
-\emph{alt} 2D structures and for the CdSe and GaAs bulk systems; the results
-are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
+Using  Eq. \eqref{eq:vab-aw}, we calculated 
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{up} and
+\emph{alt} 2D structures and for CdSe and GaAs which are bulk systems; 
+the results
+are presented in Fig. \ref{fig:vab-str-comp}. 
+The angle $\alpha$ presented in
 the response of each structure is that for which the response is maximized in
@@
 The most intense response corresponds to the \emph{up} structure centered at
-0.088\,eV corresponding to the Mid Infrared (MIR) radiation and reaching a spin
-velocity of 87.2\,Km/s.
-% 
-For an energy range from 0.66\,eV to 3.0\,eV, corresponding
-to energies of the Near Infrared (NIR) to visible radiation, all
-the four structures have contributions of the same order of magnitude.
+0.088\,eV 
+corresponding to the long-wavelength infrared radiation (LWIR) 
+and reaching a $\calv^{\rmy\rmz}=87.2$ Km/s, which means the
+electrons moving along $y$ (parallel to the surface) with the spin
+polarized along $z$ (perpendicular to the surface),
+with a speed of 87.2 Km/s.
+% 
+For an energy range from 0.66\,eV to 3.0\,eV, 
+corresponding
+to energies of the Near Infrared (NIR) to visible radiation (VIS), 
+all
+four systems have contributions of the same order of magnitude.
 % 
 For this energy range the \emph{up} structure has two peaks centered at
-1.94\,eV and 1.97\,eV reaching spin velocities of 22.2\,Km/s and -29.7\,Km/s and the \emph{alt} structure has two peaks centered at 0.72\,eV
-and 0.91\,eV reaching spin velocities of -40.2\,Km/s and -32.9\,Km/s,
+1.938\,eV and 1.972\,eV reaching $\calv^{\rmy\rmz}=22.2$ Km/s and
+$\calv^{\rmy\rmz}=-29.7$ Km/s and the 
+\emph{alt} structure has two peaks centered at 0.720\,eV
+and 0.912\,eV reaching 
+$\calv^{\rmy\rmz}=-40.2$ Km/s
+and
+$\calv^{\rmy\rmz}=-32.9$ Km/s, 
 respectively.
@@
 Then, for the bulk structures we have that the CdSe has only one intense
-response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
-GaAs structure response reaches the maximum for an incoming beam of energy of
-2.31\,eV and resulting in a spin velocity of -21.6\,Km/s.
-% 
-In table \ref{tab:vab-str-comp} we present the comparison of this values for
+response centered at 0.906\,eV reaching 
+$\calv^{\rmz\rmz}=-26.9$ Km/s, 
+and the
+GaAs structure response reaches the maximum centered at
+2.312\,eV reaching
+$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-21.6$ Km/s.
+% 
+In table \ref{tab:vab-str-comp} we present the comparison of these values for
 the 2D and bulk structures; a positive (negative) spin-velocity means that the
@@
 % 
-From the table also we obtain that particularly the 2D \emph{up} structure is
-the one with the highest response being between 4 and 5 times more intense than
-the corresponding to the bulk structures.
+We remark that the 2D structures have resonances that give 
+larger values for $\calv^{\rma\rmb}$ than the
+bulk crystals; in particular
+the \emph{up} structure is
+$\sim 5$ times more intense.
 
@@
 
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
+    \caption{$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ response
     as a function of the photon energy and polarization angle $\alpha$ for the
     \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared
-    radiation range, and two local maxima from 1.90\,eV to 1.93\,eV and from
-    1.96\,eV to 2.0\,eV, in the visible radiation range, all for polarization
+    for an energy range from 0.08\,eV to 0.10\,eV, in the LWIR
+   range, and two local maxima from 1.90\,eV to 1.93\,eV and from
+    1.96\,eV to 2.0\,eV, in the VIS range, all for polarization
     angles between $25^{\circ}$ and $50^{\circ}$.}
@@
 
-    \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frames, right
-    scale of figs (a) and (b)), the corresponding velocity angle
-    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (top frames, right scale), the
-    collinear (circled box) and perpendicular (square box) angles, and the two
-    components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-    $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ (bottom frames) for the
-    \emph{up} structure fixing the energy to 0.088\,eV. }
+    \caption{For the {\it up} structure and  fixing the energy to
+      0.088 eV (top panel) and 1.972 eV (lower panel), 
+  we show 
+    $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ (left
+    scale), the corresponding velocity angle
+    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale), the
+    collinear (green arrow) and perpendicular (blue arrow) angles.
+}
     \label{fig:up-vaz-rag}
@@
 
-Using Eq. \eqref{eq:vs-mag}, we calculated $|\mathcal{V}_{\sigma^{\mathrm{b}}}
-(\omega,\alpha)|$ and made the analysis for the case when the spin is fixed
-along $z$ directed perpendicularly to the surface of the \emph{up} and
+Using Eq. \eqref{eq:vs-mag}, we calculated 
+$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
+and made the analysis for the case when the spin is fixed
+along $z$, i.e. directed perpendicularly to the surface of the \emph{up} and
 \emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
 angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
-on the surface of the each structure.
-%
-
-\subsubsection{Up structure}
-
-We present in Fig. \ref{fig:up-3d-vsz} the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
-for two energy ranges on the \emph{up} structure.
-% 
-We obtained that the zone where the maximum response is reached corresponds to
-a energy range of the incident beam from 0.084\,eV to 0.093\,eV, in the far
-infrared (FIR) and polarization angles $\alpha$ between $30^{\circ}$ and
-$45^{\circ}$. Also the two local maxima are held for same beam polarization
-angles but for an energy range between 1.90\,eV and 2.05\,eV, in the visible
-radiation range.
+along the surface of the each structure.
+%
+
+\subsubsection{{\it up} structure}\label{up:fs}
+
+We present in Fig. \ref{fig:up-3d-vsz} 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+% (Eq. \eqref{eq:vs-mag})
+for the two energy ranges of the \emph{up} structure that give the
+highest values for $\calv^{\rmy\rmz}$ shown in Fig.~\ref{fig:vab-str-comp}.
+% 
+We obtain that the zone where the maximum response is reached corresponds to
+a energy range of the incident beam from 0.084\,eV to 0.093\,eV, 
+corresponding to the LWIR,
+and polarization angles $\alpha$ 
+between $30^{\circ}$ and $45^{\circ}$. 
+Also,  two local maxima are held for same 
+$\ga$ between $30^{\circ}$ and $45^{\circ}$, 
+but for an energy range between 1.90\,eV and 2.05\,eV, in the VIS
+range.
 % %%%%%%%%%%%%%%%%% 
@@
 % %%%%%%%%%%%%%%%%%
-In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
-Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy of the
-incoming beam to 0.088\,eV for which the response is maximized as shown in the
-top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
-the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s. This value
-comes from the contribution of the components
+
+In the top panel of Fig. \ref{fig:up-vaz-rag} we first analyze the
+response for
+$\hbar\go= 0.088$ eV which gives the maximum as shown
+in Fig. \ref{fig:up-3d-vsz} . 
+We show 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+as a function of $\ga$
+(left scale, black solid line). 
+The absolute maximum is obtained when
+$\alpha = 40^{\circ}$ resulting in a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 95.8$\,Km/s, 
+that according to Eq.~\eqref{eq:vs-mag} 
+comes from 
 $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s not presented here.
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s.
 % 
@@
 $\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
-the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 65^{\circ}$. Also
-we present two boxes indicating the values for which the angles of the spin
-velocity and the polarization angle are parallel (Eq. \ref{eq:gamma-par}, green
-circled box), corresponding to $\alpha =
-\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$; and perpendicular
-(Eq. \ref{eq:gamma-perp}, blue squared box), corresponding to $\alpha=155.5^
-{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$. The green
-and blue dashed arrows are directed from those angles to the respective value
-of the response corresponding to
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 24.8$\,Km/s.
-% 
-We also found that the velocity angle is almost constant for all the
-polarization angle range having values of $\gamma_{\mathrm{z}}(\omega,\alpha) =
-65.5^{\circ}\pm 0.5^{\circ}$.
-% 
-In the bottom panel of Fig. \ref{fig:up-vaz-rag} we present for the same
-structure the result of evaluate Eq. \eqref{eq:vs-mag} fixing now the energy of
-the incoming beam to 1.972\,eV for which the response has a local maximum as
-shown in the bottom panel of Fig. \ref{fig:up-3d-vsz}. The local maximum is
-obtained again when the polarization angle is $\alpha = 40^{\circ}$ resulting
-in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
-30.3$\,Km/s directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
-78^{\circ}$.
-% 
-Again, the  green circled box indicates the parallel angles $\alpha =
-\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ corresponding to a
-spin-velocity $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-23.5$\,Km/s indicated with the green arrow
-% 
-and the blue squared box indicates the perpendicular pair of angles $\alpha =
-155.5^ {\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 65.5^{\circ}$.
-% 
-We found again that the velocity angle is almost constant at $78^{\circ}$ and
-has variations of $\pm 1^{\circ}$ for polarization angles $0^{\circ} \leq
-\alpha \leq 100^{\circ}$.
-% 
-We also made the analysis for the cases when the spin polarization is directed
-along $\mathrm{x}$ and $\mathrm{y}$ but we do not present here the
-corresponding plots. For those cases we have that the responses maxima are
-obtained for an energy of 0.088\,eV and polarization angle $\alpha=40^{\circ}$
-resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=24.8$\,Km/s.
+the absolute maximum at $\ga=40^\circ$ is
+$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) = 65^{\circ}$. 
+This results means that at $\hbar\go=0.088$ eV and a polarization
+angle of the incoming 
+electric field of $\ga=40^\circ$ 
+the electrons with a spin pointing along $z$ move at angle of 
+$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) =
+65^{\circ}$
+with respect to the $x$ direction,  
+with a  maximum speed
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  95.8 Km/s.
+Also,
+from Eq. \eqref{eq:gamma-par} we find that 
+$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=65.4^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 82.3$ Km/s 
+(see green arrow),  
+and 
+that from Eq. \eqref{eq:gamma-perp}, 
+$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=65.5^\circ$,
+gives $\ga=155.5^\circ$, with  
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 24.8$ Km/s
+(see blue arrow); thus, for $\hbar\go=0.088$ eV, an
+$\alpha=65.4^\circ$ ($\alpha=155.5^\circ$) gives 
+electrons with spin polarized along $z$
+moving 
+parallel (perpendicular) to the
+incident electric field,  with a speed of 82.3 (24.8) Km/s. 
+% 
+We also find that for all values of $\ga$,
+$\gamma_{\mathrm{z}}(\omega,\alpha) =65.4^{\circ}\pm 0.3^{\circ}$,
+being almost constant, and 20 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 95.8 Km/s.
+%
+
+In the bottom panel of Fig. \ref{fig:up-vaz-rag}, now we take
+$\hbar\go=1.972$ eV which is the local maximum 
+shown in the bottom panel of Fig. \ref{fig:up-3d-vsz}. 
+The local maximum is
+again at  $\alpha = 40^{\circ}$ with
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
+30.3$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
+78.2^{\circ}$.
+% 
+In this case,  
+$\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 78.4^{\circ}$ with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =18.8$ Km/s 
+(green circled box and arrow),
+and
+% 
+$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.5^{\circ}$, for 
+$\alpha =168.5^ {\circ}$ 
+(blue squared box and arrow).
+% 
+We find  that the velocity angle is almost constant at
+$78.4^{\circ}\pm 0.3^\circ$ 
+for  $0^{\circ} \leq
+\alpha \leq 100^{\circ}$,
+and 1 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 30.3 Km/s.
+% 
+Although no figures are presented, we also made the analysis for the
+cases when the spin polarization is directed 
+along $\mathrm{x}$ and $\mathrm{y}$, finding 
+the maxima for
+$\hbar\go=0.088$ eV and $\alpha=40^{\circ}$, with
+$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=37.4$ Km/s and
+$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=24.8$ Km/s,
+$\gamma_{\mathrm{x}}(\omega,\alpha) = 12.5^{\circ}$, and 
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 159.7^{\circ}$
 
@@
 
-\subsubsection{Alt structure}
-
-We present in Fig. \ref{fig:alt-3d-vsb} the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
-on the \emph{alt} structure.
-% 
-We obtained that the zone where the maximum response is reached corresponds to
-energies from 0.90\,eV to 0.93\,eV and a local maximum is obtained
-for energies between 0.67\,eV and 0.75\,eV both located in the FIR radiation
-range and for polarization angles between $120^{\circ}$ and $150^{\circ}$.
+\subsubsection{{\it alt} structure}
+
+We proceed to analyse the ${\it alt}$ structure, just as we did the
+{\it up} structure. 
+Fig. \ref{fig:alt-3d-vsb} shows
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (Eq. \eqref{eq:vs-mag}),
+where we see that
+% 
+the maximum response is reached for $\hbar\go=0.912$ eV
+and a local maximum is obtained at
+$\hbar\go=0.720$ eV, both located in the
+short-wavelength infrared radiation (SWIR)
+ range and for polarization angles, $\ga$,  between $120^{\circ}$ and $150^{\circ}$.
+
 % %%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%
-In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
-Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy to
-0.912\,eV for which the response is maximized as shown in the
-top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
-the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s.
+In Fig. \ref{fig:alt-vaz-rag} we plot $\calv_{\gs^z}(\go,\ga)$ vs. $\ga$
+(left scale, black solid line), fixing the energy to
+0.912 eV for which the response is maximized as shown in the
+top panel of Fig. \ref{fig:alt-3d-vsb}. The absolute maximum is
+obtained for
+$\alpha = 145^{\circ}$ with  
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 43.0$ Km/s.
 % 
 In the same panel we present the velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
-the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 145^{\circ}$.
-% 
-As explained for the previous case, the green circled box indicates the
-parallel pair of angles $\alpha = \gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
-53.5^{\circ}$ with a corresponding value
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s indicated
-with the green arrow, and the blue square box indicates the perpendicular pair
-of angles, $\alpha=140^{\circ}$ and
-$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, with a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|=43.0$\,Km/s indicated with
-the blue arrow.
-% 
-We also have that the velocity angle is centered at $51.5^{\circ}$ having
-variations of $\pm 2^{\circ}$ for the polarization angle range $0^{\circ} \leq
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red dashed line),
+that for the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) =
+49.9^{\circ}$.
+% 
+Also, the green circle indicates
+the value of $\ga$ for which the 
+electrons move parallel to the incoming electric field, 
+i.e. $\alpha = \gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
+53.5^{\circ}$, with 
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 12.7$ Km/s. 
+Likewise, the blue circle indicates
+the value of $\ga$ for which the electrons move perpendicular to the
+incoming electric field, i.e. 
+$\alpha=140^{\circ}$, with
+$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, and 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=43.0$ Km/s.
+% 
+We also have that 
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ 
+is centered at $51.5^{\circ}$ having
+variations of $\pm 2^{\circ}$ for $0^{\circ} \leq
 \alpha \leq 180^{\circ}$.
@@
 Again, for the cases in which the spin polarization is parallel to the surface
-of the \emph{alt} structure was calculated but the plots are not presented
-here. The absolute maxima for the cases when the spin polarization are directed
-in the $x$ and $y$ direction are obtained for an energy of 0.912\,eV and
-polarization angle $\alpha=145^{\circ}$ resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)| = 27.1$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)| = 33.2$\,Km/s.
+the maximum values are
+$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 27.1$ Km/s and
+$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 33.2$ Km/s, corresponding to 
+$\gamma_{\mathrm{x}}(\omega,\alpha) = 100.1^{\circ}$
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 67.9^{\circ}$
+and both for $\alpha=145^{\circ}$, where
+the plots are not presented.
 
@@
 
-Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
-$|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$ for the case when the velocity is
-fixed in the $x$ and $y$ direction on the surface of the \emph{up} and
-\emph{alt} structures. Also, using the Eqns. \eqref{eq:polar-ang} and 
-\eqref{eq:azimuthal-ang}, we determined the polar $\theta_{\mathrm{a}}
-(\omega,\alpha)$ and azimuthal $\varphi_{\mathrm{a}} (\omega,\alpha)$ angles
+ Using the Eq. \eqref{eq:vv-mag}, we calculated the
+$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ for the cases when the velocity is
+fixed along the $\rma=x$ or $\rma=y$ direction on the surface of the \emph{up} and
+\emph{alt} structures, and from the Eqns. \eqref{eq:polar-ang} and 
+\eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
+(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
 corresponding to the direction of the spin.
 
-\subsubsection{Up structure}
+\subsubsection{{\it up} structure}
 
@@
 % %%%%%%%%%%%%%%%%%
-In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present the
-result of evaluate Eq. \eqref{eq:vv-mag} for the
-\emph{up} structure fixing the velocity in the $x$ and $y$ direction.
-%
-From this figure we can see that the two absolute maxima are obtained for
-energies between 0.084\,eV and 0.093\,eV, in the FIR, and polarization angles
-between $30^ {\circ}$ and $45^{\circ}$.
-% 
-In the top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-1} we present $|
-\mathcal{V}^{\mathrm{x}} (\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}
-(\omega,\alpha)|$ (left scale, black solid line) fixing the polarization angle
-to $\alpha=40^{\circ}$ for which the responses have absolute maxima of
-58.7\,Km/s and 87.9\,Km/s, respectively, for an energy of 0.088\,eV.
-% 
-In same panels we present the corresponding polar (right scale, red dashed
-line) and azimuthal (right scale, blue dashed line) spin polarization angles
-that have values of $\theta_{\mathrm{x}}(\omega,\alpha) = 47^{\circ}$,
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 212^{\circ}$, $\theta_{\mathrm{y}}
-(\omega,\alpha) = 8^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) =
-133^{\circ}$. In this way, the spin is directed upward the third Cartesian
-quadrant of the $xy$ plane when it moves along $x$, and is directed almost
+In Fig. \ref{fig:up-3d-vva-1} we plot
+$\mathcal{V}^{\mathrm{x}}(\omega,\alpha)$  
+and
+$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$  
+for the
+\emph{up} structure, where
+%
+we see that each response has a maximum for
+$\hbar\omega=0.088$ eV,
+in the LWIR, and 
+$\ga=40^{\circ}$. 
+% 
+Fixing $\ga=40^{\circ}$ eV,
+in Fig. \ref{fig:up-vab-comp-rtp-1} we plot 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ 
+and $\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$
+(left scale, black solid line) 
+where each responses has a maximum of
+58.7\,Km/s and 87.9\,Km/s, respectively, for $\hbar\go=0.088$ eV.
+% 
+We also
+present the corresponding polar 
+(right scale, red dashed line) 
+and azimuthal 
+(right scale, blue dashed line)
+spin polarization angles
+that have values of 
+$\theta_{\mathrm{x}}(\omega,\alpha) = 47.4^{\circ}$,
+and $\varphi_{\mathrm{x}}(\omega,\alpha) = 212.5^{\circ}$
+ when the  electron moves along $x$,
+and  $\theta_{\mathrm{y}}(\omega,\alpha) = 7.6^{\circ}$, and
+ $\varphi_{\mathrm{y}} (\omega,\alpha) =132.7^{\circ}$,
+when the electron moves along $y$.
+This means that, the spin is directed upward the third Cartesian
+quadrant of the $xy$ plane when the electron moves along $x$, and is directed almost
 perpendicularly over the $xy$ plane when it moves along $y$.
 % 
-Also from this figure we have that when the spin moves along $x$ the angles are
-almost constant for the peak of the response having variations of $\pm
-2^{\circ}$ but when the spin moves along $y$ the azimuthal angle changes from
-$99^{\circ}$ to $176^{\circ}$
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
-    \\
-    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
-
-    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
-    of the photon energy and polarization angle $\alpha$ for the \emph{up}
-    structure. Two local maxima of both responses are localized in the energy
-    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the
-    visible radiation range, and for polarization angles between $25^{\circ}$
-    and $50^{\circ}$.}
-    \label{fig:up-3d-vva-2}
-\end{figure}
+Also, from this figure we have that when the electron moves along $x$ the spin
+direction is almost constant for all the energies across the peak of the
+response, having a ranges of $ 44.4^{\circ} < \theta_{\mathrm{x}}
+(\omega,\alpha) < 56.2^{\circ} $ and $210.3^{\circ} < \varphi_{\mathrm{x}}
+(\omega,\alpha) < 217.4^{\circ}$. Then, hen the electron moves along $y$ the
+spin's polar angle has again minimal variations, $ 9.76^{\circ} <
+\theta_{\mathrm{y}} (\omega,\alpha) < 13.7^{\circ}$, but in contrast with this
+the azimuthal angle has significative variations, $99.3^{\circ} <
+\varphi_{\mathrm{y}} (\omega,\alpha) < 196.1^{\circ}$.
+
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
+%     \\
+%     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
+
+%     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
+%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
+%     of the photon energy and polarization angle $\alpha$ for the \emph{up}
+%     structure. Two local maxima of both responses are localized in the energy
+%     range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the
+%     visible radiation range, and for polarization angles between $25^{\circ}$
+%     and $50^{\circ}$.}
+%     \label{fig:up-3d-vva-2}
+% \end{figure}
 \begin{figure}[t]
@@
 
-In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
-result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
-velocity in the $x$ and $y$ direction for other range of energies that present
-a intense response.
-% 
-From this figure we can see that the two local maxima are obtained for energies
-between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
-polarization angles between $30^ {\circ}$ and $45^{\circ}$.
-% 
-From the top and bottom panels of Fig. \ref{fig:up-vab-comp-rtp-2} we have that
-$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| =  9.8$\,Km/s and
-$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.3$\,Km/s fixing the
-polarization angle to $\alpha=40^{\circ}$ and the beam energy to 1.932\,eV.
-% 
-In same panels we present the corresponding polar and azimuthal spin
-polarization angles that have values of $\theta_{\mathrm{x}}(\omega,\alpha) =
-129^{\circ}$, $\varphi_{\mathrm{x}}(\omega,\alpha) = 229^{\circ}$,
-$\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and $\varphi_{\mathrm{y}}
-(\omega,\alpha) = 227^{\circ}$ being constant all of them in the peak of the
-local maxima. Then, the spin is directed downward the third Cartesian quadrant
-of the $xy$ plane when it moves along $x$ and $y$ directions.
-
+% From Sec.~\ref{up:fs}, we know that the {\it up} structure has two
+% more resonant structures at $\hbar\go=1.932$ eV, and
+% $\hbar\go=1.972??$ eV. For this case, where the velocity is fixed
+% along $x$ or $y$, we find that
+
+% In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
+% result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
+% velocity in the $x$ and $y$ direction for other range of energies that present
+% a intense response.
+% From this figure we can see that the two local maxima are obtained for energies
+% between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
+% polarization angles between $30^ {\circ}$ and $45^{\circ}$.
+%
+
+In  
+Fig. \ref{fig:up-vab-comp-rtp-2},  for 
+the {\it up} structure, 
+we plot 
+$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ vs. $\go$, and 
+fixing $\alpha=40^{\circ}$; the range of $\go$ lies in part of the
+VIS range.
+We see that there are two local maxima at $\hbar\go=1.932$ eV
+and $\hbar\go=1.972$ eV. For the latter that is the most intense
+we obtain
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  9.9$ Km/s and  
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 49.4$ Km/s.
+For these local maxima, 
+the corresponding polar and azimuthal spin
+polarization angles are
+$\theta_{\mathrm{x}}(\omega,\alpha) =129.1^{\circ}$, and $\varphi_{\mathrm{x}}
+(\omega,\alpha) = 229.2^{\circ}$,
+for the electron moving along $x$,
+and
+$\theta_{\mathrm{y}} (\omega,\alpha) = 127.0^{\circ}$,
+ and $\varphi_{\mathrm{y}}(\omega,\alpha) = 227.1^{\circ}$
+for the electron moving along $y$. 
+We remark that these angles
+are almost constant for all the energy values across the peak of the
+this local maxima, for which the spin is directed 
+downward in the third Cartesian quadrant
+of the $xy$ plane when it moves along either $x$ or $y$ directions.
+For the $\hbar\go=1.932$\,eV peak we obtain  
+$\theta_{\mathrm{x}} (\omega,\alpha) = 42.0^{\circ}$, and 
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 58.7^{\circ}$, with
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  6.6$ Km/s,
+ and 
+$\theta_{\mathrm{y}}(\omega,\alpha) =45.2$, and 
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 56.1$, with
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) =  29.0$ Km/s.
+However, for this local maximum, the spin angles are not constant
+across the resonant peak.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsubsection{Alt structure}
-
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
-    \\
-    \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
-
-    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
-    of the photon energy and polarization angle $\alpha$ for the \emph{alt}
-    structure. The local and the absolute maxima are located in the energy
-    ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
-    respectively, and both in the Near Infrared and for polarization angles
-    between $120^{\circ}$ and $150^{\circ}$.}
-    \label{fig:alt-3d-vva}
-\end{figure}
+\subsubsection{{\it alt} structure}
+
+% \begin{figure}[tb]
+%     \centering
+%     \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
+%     \\
+%     \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
+
+%     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
+%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
+%     of the photon energy and polarization angle $\alpha$ for the \emph{alt}
+%     structure. The local and the absolute maxima are located in the energy
+%     ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
+%     respectively, and both in the Near Infrared and for polarization angles
+%     between $120^{\circ}$ and $150^{\circ}$.}
+%     \label{fig:alt-3d-vva}
+% \end{figure}
 
@@
 
-In top and bottom panels of Fig. \ref{fig:alt-3d-vva} we present the
-result of evaluate Eq. \eqref{eq:vv-mag} for the
-\emph{up} structure fixing the velocity in the $x$ and $y$ direction.
-% 
-From this figure we have that the relative maxima for the spin velocity along
-$x$ and $y$ are obtained for energies between 0.70\,eV to 0.75\,eV and the
-absolute maxima are obtained for energies between 0.90\,eV and 0.93\,eV, all
-cases in the NIR radiation, and polarization angles between 120$^{\circ}$ and
-150$^{\circ}$.
-% 
-From the top and bottom panels of Fig. \ref{fig:alt-vab-comp-rtp} we have that
-that the local maxima are $|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| =
-19.4$\,Km/s and $|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 51.9$\,Km/s
-fixing the energy to 0.720\,eV and the absolute maxima are
-$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| = 30.9$\,Km/s and
-$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 52.2$\,Km/s fixing the energy to
-0.912\,eV all for a polarization angle $\alpha=145^{\circ}$.
-% 
-The corresponding polar and azimuthal angles for the local maxima are
-$\theta_{\mathrm{x}} (\omega,\alpha) = 46^{\circ}$, $\varphi_{\mathrm{x}}
-(\omega,\alpha) = 41^{\circ}$, $\theta_{\mathrm{y}} (\omega,\alpha) =
-141^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) = 222^{\circ}$ being the
-spin directed over the first Cartesian quadrant of the $xy$ plane when the spin
-velocity is directed along $x$ and directed downward the third Cartesian
-quadrant when the spin velocity is directed along $y$. Finally, the angles for
-the absolute maxima are $\theta_{\mathrm{x}}(\omega,\alpha) = 154^{\circ}$,
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 290^{\circ}$, $\theta_{\mathrm{y}}
-(\omega,\alpha) = 129^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) =
-229^{\circ}$ being the spin polarization directed downward the fourth Cartesian
-quadrant when the spin velocity is directed along $x$ and downward the third
-Cartesian quadrant when the spin velocity is directed along $y$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: Layer-by-layer  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Layer-by-layer analysis} % (fold)
-\label{sec:res-layer_by_layer_analysis}
-
-As mentioned before in in the beginning of this section the \emph{up} and
-\emph{alt} structures presented here was divided into layers to analyze the
-layer-by-layer contribution for $|\mathcal{V}_{\sigma^{\mathrm{b}}}
-(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$. 
-% 
-In Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell} we present the layer
-division needed to calculate the layer-by-layer contribution for the
-$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ and
-$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ presented in Eqns.
-\eqref{eq:vs-layer} and \eqref{eq:vv-layer}. The \emph{up} structure was
-divided in two layers, the first comprised of the top hydrogen atoms denoted by
-the number 1 in Table \ref{tab:up-unitcell} and in the Fig. \ref{fig:up-struc}
-and the second comprised of carbon atoms and denoted by the number 2. The
-\emph{alt} structure was divided in six layers denoted with numbers from 1 to 6
-in Table \ref{tab:alt-unitcell} and in Fig. \ref{fig:alt-struc}. The first and
-sixth layers correspond to hydrogen atoms in the top and bottom positions and
-from the second to the fifth correspond to carbon atoms placed in different
-positions.
-% 
-Here we present the decomposition only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)|$ and for the corresponding components of the \emph{up}
-structure in Figs.
-% 
-\ref{fig:up-vsz-lay-1} and \ref{fig:up-vsz-lay-2} and for the \emph{alt}    
-structure in Fig. \ref{fig:alt-vsz-lay}. 
-% 
-% The $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented
-% in those figures is the same than the presented in top frames of Figs.
-% \ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
-% layered responses.
-% 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-1}
-
-    \caption{Layer-by-layer contribution of the
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
-    for the \emph{up} structure as a function of the polarization angle
-    $\alpha$ for the energy fixed to 0.088\,eV for which the absolute maximum
-    is obtained.
-    % 
-    The corresponding layered contributions for the
-    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
-    central and bottom frames.}
-    \label{fig:up-vsz-lay-1}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-2}
-
-    \caption{Layer-by-layer contribution of the
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
-    for the \emph{up} structure as a function of the polarization angle
-    $\alpha$ for the energy fixed to 1.972\,eV for which a local maximum is
-    obtained.
-    % 
-    The corresponding layered contributions for the
-    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
-    central and bottom frames.}
-    \label{fig:up-vsz-lay-2}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay-1}
-
-\caption{Layer-by-layer contribution of the
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
-    for the \emph{alt} structure as a function of the polarization angle
-    $\alpha$ for the energy fixed to 0.720\,eV.
-    % 
-    The corresponding layered contributions for the
-    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
-    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
-    central and bottom frames.}
-    \label{fig:alt-vsz-lay}
-\end{figure}
-%
-
-% %%%%%%%%%%%%%%%%
-% %% Description of Up layer |V_{s^z}|
-% %%%%%%%%%%%%%%%%
-From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1} we have that
-when the energy is fixed to 0.088\,eV almost all the response of the
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
-layer comprised by carbon atoms having a minimal reduction produced by the
-hydrogen layer.
-% 
-Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response, presented in
-bottom frame of same figure, is produced only by the carbon layer. This result
-in a total response $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-95.8$\,Km/s coming from the carbon layer and being minimally reduced by the
-hydrogen layer as shown in the top frame of this figure for a fixed
-polarization angle $\alpha = 40^{\circ}$.
-% 
-Now, for the same structure but now fixing the energy to 1.972\,eV we have from
-the central frame of Fig. \ref{fig:up-vsz-lay-2} that the the carbon layer
-produces the response of the $\mathcal{V}^{\mathrm{zx}}(\omega,\alpha)$
-component being decreased by the hydrogen layer. Opposite to that, in the
-bottom frame of same figure we obtained that the response of the carbon and
-hydrogen layer are not inverse and then contributing both to the total response
-of $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
-figure we have that the major contribution to the
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response comes from the
-carbon layer with but being in this case reinforced by the contribution of the
-hydrogen layer and resulting in a value of 30.3\,Km/s.
-% %%%%%%%%%%%%%%%%
-% %% Description of ALT layer |V^{yz}|
-% %%%%%%%%%%%%%%%%
-Finally, for the \emph{alt} structure we have that, for the response $|
-\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ when the energy is fixed to
-0.720\,eV the six layers contribute with similar magnitudes. 
-% 
-We found that for the $\mathcal{V}^{\mathrm{xz}} (\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ components the top hydrogen layer
-response, denoted by $\ell_{1}$, cancels partially the the bottom hydrogen
-layer response, denoted by $\ell_{6}$;
-% 
-a similar behavior occurs in the component $\mathcal{V}^{\mathrm{xz}}
-(\omega,\alpha)$ for the third and fourth carbon layers and in the component
-$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ for the second and fifth carbon
-layers.
-% 
-This result in a total response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) =
-42.4$\,Km/s for a fixed polarization angle $\alpha = 145^{\circ}$.
-% 
-Then, for this analysis we found that the $|\mathcal{V}_{\sigma^{\mathrm{z}}} 
-(\omega,\alpha)|$ and in general, $\mu^{\mathrm{abcd}} (\omega)$ responses are
-very susceptible to the symmetry of the system. The \emph{up} structure is 
-\emph{more} non-centrosymmetric than the \emph{alt} structure and then the
-response is quite larger.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%   C O N C L U S I O N S  %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% In top and bottom panels of Fig. \ref{fig:alt-3d-vva} we present the
+% result of evaluate Eq. \eqref{eq:vv-mag} for the
+% \emph{up} structure fixing the velocity in the $x$ and $y$ direction.
+% % 
+% From this figure we have that the relative maxima for the spin velocity along
+% $x$ and $y$ are obtained for energies between 0.70\,eV to 0.75\,eV and the
+% absolute maxima are obtained for energies between 0.90\,eV and 0.93\,eV, all
+% cases in the NIR radiation, and polarization angles between 120$^{\circ}$ and
+% 150$^{\circ}$.
+%
+
+In Fig. \ref{fig:alt-vab-comp-rtp} 
+we show  for the {\it alt} structure
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ 
+and
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha)$ 
+vs. $\omega$, for $\ga=145^\circ$, the value that maximizes both
+responses as a function of $\ga$, where we see that each response has
+two local maxima. The one at $\hbar\go=0.720$ eV gives
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =19.4??$ Km/s,
+and $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 51.9??$ Km/s, and the
+other one at $\hbar\go=0.912??$ eV gives
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 30.9$ Km/s and
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 52.3$ Km/s.
+% 
+For $\hbar\go=0.720$ eV,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 45.8^{\circ}$, $\varphi_{\mathrm{x}}
+(\omega,\alpha) = 40.7^{\circ}$, 
+$\theta_{\mathrm{y}} (\omega,\alpha) =
+140.7^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha) =
+221.6^{\circ}$, implying
+% 
+that the spin is directed over the first Cartesian quadrant of the $xy$ plane
+when the spin velocity is directed along $x$, and directed downward the third
+Cartesian quadrant when the spin velocity is directed along $y$. Finally, for
+$\hbar\go=0.912$ eV, $\theta_{\mathrm{x}}(\omega,\alpha) = 153.8^{\circ}$,
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 290.4^{\circ}$, $\theta_{\mathrm{y}}
+(\omega,\alpha) = 129.0^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha)
+=228.9^{\circ}$, and the spin is directed downward in the fourth Cartesian
+quadrant of the $xy$ plane when the spin velocity is directed along $x$ and
+downward the third Cartesian quadrant when the spin velocity is directed along
+$y$.
 
@@
 
-\appendix
-\section{Math derivation}
-\label[appendix]{sec:mathder}
-
-From Eq. \eqref{eq:dotO} and Eq. \eqref{eq:k-timerev}, using
-$\mathbf{r}_{nm}(-\mathbf{k}) = \mathbf{r}_{mn}(\mathbf{k})$ and taking
-$\epsilon \rightarrow 0$, we have 
-\begin{widetext}
-\begin{align}
-\dot K^{\mathrm{ab}}
-&=
-\frac{e^2}{i\hbar^2}
-\int\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-\left(
-\frac{1}{\omega-\omega_{c'v}-i\epsilon}
--
-\frac{1}
-{\omega-\omega_{cv}+i\epsilon}
-\right) 
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&=
-\frac{e^2}{i\hbar^2}
-\int\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-\Big(
-(K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}) \big |_{\mathbf{k}>0}
-+
-(K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}) \big |_{\mathbf{k}<0}
-\Big) 
-\nonumber\\
-&\times 
-\left(
-\frac{1}{\omega-\omega_{c'v}-i\epsilon}
--
-\frac{1}
-{\omega-\omega_{cv}+i\epsilon}
-\right) 
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&=
-\frac{e^2}{i\hbar^2}
-\int_{\mathbf{k}>0}\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-\Big(
-K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-+
-K^{\mathrm{ab}*}_{c'c}
-r^{\mathrm{c}}_{vc}r^{\mathrm{d}}_{c'v}
-\Big) 
-\nonumber\\
-&\times 
-\left(
-\frac{1}{\omega-\omega_{c'v}-i\epsilon}
--
-\frac{1}
-{\omega-\omega_{cv}+i\epsilon}
-\right) 
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&=
-\frac{e^2}{i\hbar^2}
-\int_{\mathbf{k}>0}\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-\Big(
-K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-+
-(K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'})^*
-\Big) 
-\nonumber\\
-&\times 
-\left(
-\frac{1}{\omega-\omega_{c'v}-i\epsilon}
--
-\frac{1}
-{\omega-\omega_{cv}+i\epsilon}
-\right) 
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&=
-\frac{e^2}{i\hbar^2}
-\frac{1}{2}
-\int\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-2\mathrm{Re}\Big[
-K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-\Big]
-\Big\{
-\mathcal{P}\left(
-\frac{\omega_{c'c}}{(\omega-\omega_{c'v})(\omega-\omega_{cv})}
-\right) 
-\nonumber\\
-&+
-i\pi 
-\left(
-\delta(\omega-\omega_{c'v}) 
-+
-\delta(\omega-\omega_{cv}) 
-\right) 
-\Big\}
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&\approx 
-\frac{\pi e^2}{\hbar^2}
-\int\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-\mathrm{Re}\Big[
-K^{\mathrm{ab}}_{c'c}
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-\Big]
-\Big(
-\delta(\omega-\omega_{c'v}) 
-+
-\delta(\omega-\omega_{cv}) 
-\Big) 
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega) 
-\nonumber\\
-&=
-\frac{\pi e^2}{\hbar^2}
-\int\frac{d^3k}{8\pi^3}
-\sum_{vcc'}
-\mathrm{Re}
-\Big[ 
-K^{\mathrm{ab}}_{c'c} 
-r^{\mathrm{c}}_{cv}r^{\mathrm{d}}_{vc'}
-+ 
-K^{\mathrm{ab}}_{cc'} 
-r^{\mathrm{c}}_{c'v}r^{\mathrm{d}}_{vc}
-\Big]
-\delta(\omega-\omega_{cv})  
-E^{\mathrm{c}}(\omega)E^{\mathrm{d}*}(\omega),
-\label{eq:dotk-dev}
-\end{align}
-since $\omega_{cc'} \sim 0$ and we exchange $c\leftrightarrow c'$. Now, from
-Eq. \eqref{eq:k-timerev} we obtain that 
-\begin{align}
-\mathrm{Re} \left[ 
-K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} 
-\right] 
-=&
-\frac{1}{2} \left(
- K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} +
-(K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} )^{*}
-\right)
-\nonumber \\
-=&
-\frac{1}{2} \left(
- K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{c'v} r^{\mathrm{d}}_{vc} +
-(K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv} )
-\right)
-\nonumber \\
-=&
-\mathrm{Re}
-\left[
-K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
-\right]
-\label{eq:realk}
-\end{align}
-and then, Eq. \eqref{eq:dotk-dev} can be written as
-\begin{align}
-\dot{K}^{\mathrm{ab}}
-=&
-\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
-\sum_{vcc'} \mathrm{Re} 
-\left[ 
-K^{\mathrm{ab}}_{c'c} r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
-K^{\mathrm{ab}}_{cc'} r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
-\right]
-\delta(\omega - \omega_{cv}) 
-E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega) 
-\nonumber \\
-=&
-\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
-\sum_{vcc'} \mathrm{Re} 
-\left[ 
-K^{\mathrm{ab}}_{c'c} 
-\left(
-r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
-r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv}
-\right)
-\right]
-\delta(\omega - \omega_{cv}) 
-E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
-\nonumber \\
-=&
-\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
-\sum_{vcc'} \mathrm{Re} 
-\left[ 
-K^{\mathrm{ab}}_{c'c} 
-\left(
-r^{\mathrm{c}}_{cv} r^{\mathrm{d}}_{vc'} + 
-(\mathrm{c} \leftrightarrow \mathrm{d})
-\right)
-\right]
-\delta(\omega - \omega_{cv}) 
-E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
-\nonumber \\
-=&
-\frac{\pi e^{2}}{\hbar^{2}} \int \frac{d^{3}k}{8 \pi^{3}}
-\sum_{vcc'} \mathrm{Re} 
-\left[ 
-K^{\mathrm{ab}}_{c'c} 
-\left(
-r^{\mathrm{c}}_{vc'} r^{\mathrm{d}}_{cv} + 
-(\mathrm{c} \leftrightarrow \mathrm{d})
-\right)
-\right]
-\delta(\omega - \omega_{cv}) 
-E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
-\label{eq:k-final}
-\end{align}
-\end{widetext}
-
 \bibliography{article.bib}

### 2017-07-14 mu/article/article.tex
Minimal correction.
Adding new plots to better explain the results.

@@
     \centering
-    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
+    \includegraphics[width=\linewidth]{upplots/up-vsz-3d-1}
     \\
@@
 
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
+    \caption{$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ response
     as a function of the photon energy and polarization angle $\alpha$ for the
     \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared
-    radiation range, and two local maxima from 1.90\,eV to 1.93\,eV and from
-    1.96\,eV to 2.0\,eV, in the visible radiation range, all for polarization
+    for an energy range from 0.08\,eV to 0.10\,eV, in the LWIR
+   range, and two local maxima from 1.90\,eV to 1.93\,eV and from
+    1.96\,eV to 2.0\,eV, in the VIS range, all for polarization
     angles between $25^{\circ}$ and $50^{\circ}$.}
-    \label{fig:up-3d-vsz}   
+    \label{fig:up-vsz-3d}   
 \end{figure}
@@
 
-Using Eq. \eqref{eq:vs-mag}, we calculated $|\mathcal{V}_{\sigma^{\mathrm{b}}}
-(\omega,\alpha)|$ and made the analysis for the case when the spin is fixed
-along $z$ directed perpendicularly to the surface of the \emph{up} and
+Using Eq. \eqref{eq:vs-mag}, we calculated 
+$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
+and made the analysis for the case when the spin is fixed
+along $z$, i.e. directed perpendicularly to the surface of the \emph{up} and
 \emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
 angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
-on the surface of the each structure.
-%
-
-\subsubsection{Up structure}
-
-We present in Fig. \ref{fig:up-3d-vsz} the result of evaluate
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ (Eq. \eqref{eq:vs-mag})
-for two energy ranges on the \emph{up} structure.
-% 
-We obtained that the zone where the maximum response is reached corresponds to
-a energy range of the incident beam from 0.084\,eV to 0.093\,eV, in the far
-infrared (FIR) and polarization angles $\alpha$ between $30^{\circ}$ and
-$45^{\circ}$. Also the two local maxima are held for same beam polarization
-angles but for an energy range between 1.90\,eV and 2.05\,eV, in the visible
-radiation range.
+along the surface of the each structure.
+%
+
+\subsubsection{{\it up} structure}\label{up:fs}
+
+We present in Fig. \ref{fig:up-vsz-3d} 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+% (Eq. \eqref{eq:vs-mag})
+for the two energy ranges of the \emph{up} structure that give the
+highest values for $\calv^{\rmy\rmz}$ shown in Fig.~\ref{fig:vab-str-comp}.
+% 
+We obtain that the zone where the maximum response is reached corresponds to
+a energy range of the incident beam from 0.084\,eV to 0.093\,eV, 
+corresponding to the LWIR,
+and polarization angles $\alpha$ 
+between $30^{\circ}$ and $45^{\circ}$. 
+Also,  two local maxima are held for same 
+$\ga$ between $30^{\circ}$ and $45^{\circ}$, 
+but for an energy range between 1.90\,eV and 2.05\,eV, in the VIS
+range.
 % %%%%%%%%%%%%%%%%% 
@@
 % %%%%%%%%%%%%%%%%%
-In the top panel of Fig. \ref{fig:up-vaz-rag} we present the result of evaluate
-Eq. \eqref{eq:vs-mag} (left scale, black solid line) fixing the energy of the
-incoming beam to 0.088\,eV for which the response is maximized as shown in the
-top panel of Fig. \ref{fig:up-3d-vsz}. The absolute maximum is obtained when
-the polarization angle is $\alpha = 40^{\circ}$ resulting in a value of
-$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s. This value
-comes from the contribution of the components
+
+In the top panel of Fig. \ref{fig:up-vaz-rag} we first analyze the
+response for
+$\hbar\go= 0.088$ eV which gives the maximum as shown
+in Fig. \ref{fig:up-vsz-3d} . 
+We show 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+as a function of $\ga$
+(left scale, black solid line). 
+The absolute maximum is obtained when
+$\alpha = 40^{\circ}$ resulting in a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 95.8$\,Km/s, 
+that according to Eq.~\eqref{eq:vs-mag} 
+comes from 
 $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s not presented here.
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s.
 % 
@@
 $\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
-the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 65^{\circ}$. Also
-we present two boxes indicating the values for which the angles of the spin
-velocity and the polarization angle are parallel (Eq. \ref{eq:gamma-par}, green
-circled box), corresponding to $\alpha =
-\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$; and perpendicular
-(Eq. \ref{eq:gamma-perp}, blue squared box), corresponding to $\alpha=155.5^
-{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$. The green
-and blue dashed arrows are directed from those angles to the respective value
-of the response corresponding to
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 24.8$\,Km/s.
-% 
-We also found that the velocity angle is almost constant for all the
-polarization angle range having values of $\gamma_{\mathrm{z}}(\omega,\alpha) =
-65.5^{\circ}\pm 0.5^{\circ}$.
-% 
-In the bottom panel of Fig. \ref{fig:up-vaz-rag} we present for the same
-structure the result of evaluate Eq. \eqref{eq:vs-mag} fixing now the energy of
-the incoming beam to 1.972\,eV for which the response has a local maximum as
-shown in the bottom panel of Fig. \ref{fig:up-3d-vsz}. The local maximum is
-obtained again when the polarization angle is $\alpha = 40^{\circ}$ resulting
-in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
-30.3$\,Km/s directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
-78^{\circ}$.
-% 
-Again, the  green circled box indicates the parallel angles $\alpha =
-\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ corresponding to a
-spin-velocity $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
-23.5$\,Km/s indicated with the green arrow
-% 
-and the blue squared box indicates the perpendicular pair of angles $\alpha =
-155.5^ {\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 65.5^{\circ}$.
-% 
-We found again that the velocity angle is almost constant at $78^{\circ}$ and
-has variations of $\pm 1^{\circ}$ for polarization angles $0^{\circ} \leq
-\alpha \leq 100^{\circ}$.
-% 
-We also made the analysis for the cases when the spin polarization is directed
-along $\mathrm{x}$ and $\mathrm{y}$ but we do not present here the
-corresponding plots. For those cases we have that the responses maxima are
-obtained for an energy of 0.088\,eV and polarization angle $\alpha=40^{\circ}$
-resulting in values of
-$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=37.4$\,Km/s and
-$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=24.8$\,Km/s.
+the absolute maximum at $\ga=40^\circ$ is
+$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) = 65^{\circ}$. 
+This results means that at $\hbar\go=0.088$ eV and a polarization
+angle of the incoming 
+electric field of $\ga=40^\circ$ 
+the electrons with a spin pointing along $z$ move at angle of 
+$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) =
+65^{\circ}$
+with respect to the $x$ direction,  
+with a  maximum speed
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  95.8 Km/s.
+Also,
+from Eq. \eqref{eq:gamma-par} we find that 
+$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=65.4^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 82.3$ Km/s 
+(see green arrow),  
+and 
+that from Eq. \eqref{eq:gamma-perp}, 
+$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=65.5^\circ$,
+gives $\ga=155.5^\circ$, with  
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 24.8$ Km/s
+(see blue arrow); thus, for $\hbar\go=0.088$ eV, an
+$\alpha=65.4^\circ$ ($\alpha=155.5^\circ$) gives 
+electrons with spin polarized along $z$
+moving 
+parallel (perpendicular) to the
+incident electric field,  with a speed of 82.3 (24.8) Km/s. 
+% 
+We also find that for all values of $\ga$,
+$\gamma_{\mathrm{z}}(\omega,\alpha) =65.4^{\circ}\pm 0.3^{\circ}$,
+being almost constant, and 20 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 95.8 Km/s.
+%
+
+In the bottom panel of Fig. \ref{fig:up-vaz-rag}, now we take
+$\hbar\go=1.972$ eV which is the local maximum 
+shown in the bottom panel of Fig. \ref{fig:up-vsz-3d}. 
+The local maximum is
+again at  $\alpha = 40^{\circ}$ with
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
+30.3$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
+78.2^{\circ}$.
+% 
+In this case,  
+$\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 78.4^{\circ}$ with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =18.8$ Km/s 
+(green circled box and arrow),
+and
+% 
+$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.5^{\circ}$, for 
+$\alpha =168.5^ {\circ}$ 
+(blue squared box and arrow).
+% 
+We find  that the velocity angle is almost constant at
+$78.4^{\circ}\pm 0.3^\circ$ 
+for  $0^{\circ} \leq
+\alpha \leq 100^{\circ}$,
+and 1 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 30.3 Km/s.
+% 
+Although no figures are presented, we also made the analysis for the
+cases when the spin polarization is directed 
+along $\mathrm{x}$ and $\mathrm{y}$, finding 
+the maxima for
+$\hbar\go=0.088$ eV and $\alpha=40^{\circ}$, with
+$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=37.4$ Km/s and
+$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=24.8$ Km/s,
+$\gamma_{\mathrm{x}}(\omega,\alpha) = 12.5^{\circ}$, and 
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 159.7^{\circ}$
 

### 2017-07-14 mu/alt/alt-scripts/alt-vab-rtp.sh
Cheking kk vs sm vs v + 0.00001 & kpts for UP
Checking again kpts convergence in kk files for the up structure; the
doesn't mathc in the sm files.

The convergence was checked again using 12802 and 11252 kpts. Is Ok!

The value of the velocity is significatively higher using kk than sm
files and the gap matches according to the previous paper when the kk
files was used.

Also, when the V^ab is calculated I used a the value +0.00001
in the denominator to avoid divergences. I made a calculation using now
+0.0001 and the values are the same.

The next step is make again all the plots using now th

@@ -27,6 +27,13 @@ out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 calc
 
+ax=v.kk_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ay=v.kk_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+az=v.kk_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.kk_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
 ################################ |V^{y}|, rtp ##################################
 
 ax=v.sm_"$sm"_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
@@ -36,4 +43,15 @@ out=vab-rtp.sm_"$sm"_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 calc
 
+ax=v.kk_yx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ay=v.kk_yy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+az=v.kk_yz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.kk_y_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
+################################
+
 rm .temp1 .temp2 .deg1
+
+

### 2017-07-14 mu/up/up-scripts/up-vab-rtp.sh

@@ -1,5 +1,7 @@
 #/bin/bash
 
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
 an=040
 kp=12802
 ec=40
@@ -20,20 +22,36 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+
+calc
+
+ax=v.kk_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+ay=v.kk_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+az=v.kk_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
[…]

### 2017-07-19 mu/alt/alt-scripts/alt-magsvab-inang.sh
Copying files to make new plots for alt.

@@ -46,7 +46,7 @@ inputsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_
 
 calc
 
-grep "$en1" "$outputkk" > magsv.kk_0.03_ax_14452_65-"$fs1"
+grep "$en1" "$outputkk" > magsv.kk_ax_14452_65-"$fs1"
 grep "$en1" "$outputsm" > magsv.sm_0.03_ax_14452_65-"$fs1"
 
 ############################## V_{s^y} #########################################
@@ -61,7 +61,7 @@ inputsm=( v.sm_0.03_xy_14452_65-spin_scissor_0_Nc_32_ang_
 
 calc
 
-grep "$en1" "$outputkk" > magsv.kk_0.03_ay_14452_65-"$fs1"
+grep "$en1" "$outputkk" > magsv.kk_ay_14452_65-"$fs1"
 grep "$en1" "$outputsm" > magsv.sm_0.03_ay_14452_65-"$fs1"
 
 ############################## V_{s^z} #########################################
@@ -76,7 +76,7 @@ inputsm=( v.sm_0.03_xz_14452_65-spin_scissor_0_Nc_32_ang_
 
 calc
 
-grep "$en1" "$outputkk" > magsv.kk_0.03_az_14452_65-"$fs1"
+grep "$en1" "$outputkk" > magsv.kk_az_14452_65-"$fs1"
 grep "$en1" "$outputsm" > magsv.sm_0.03_az_14452_65-"$fs1"
 
 

### 2017-07-19 mu/alt/res-0.7-1.0-3500pts/alt-vab-angles.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${angles[@]}; do
+    vab.sh 14452 65 0 32 0.03 "$i"
+done

### 2017-07-19 mu/up/up-scripts/up-magsvab-inang.sh

@@ -1,20 +1,23 @@
 #!/bin/bash
 
-# angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
-#              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
-
 angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
-             095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
-             185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
-             275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
+             095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
 
-# FIXED ENERGY:
-en1="8.80000E-02"
-en2="1.97200E+00"
+# angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+#              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
+#              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
+#              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
-# OUTPUT FILE SUFIX:
-fs1="0.088eV"
-fs2="1.972eV"
+#### FIXED ENERGY:
+# en1="0.1954652E+01"
+en1="0.1957953E+01"
+
+# en2="1.95465E+00"
+en2="1.95795E+00"
+
+#### OUTPUT FILE SUFIX:
+# fs1="1.954eV"
+fs1="1.957eV"
 
 deg=180/3.141592
 
@@ -46,12 +49,8 @@ inputsm=( v.sm_0.03_xx_12802_40-spin_scissor_0_Nc_32_ang_
 
 calc
 
-grep "$en1" "$outputkk" > magsv.kk_0.03_ax_12802_40-"$fs1"
-grep "$en1" "$outputsm" > magsv.sm_0.03_ax_12802_40-"$fs1"
-
-grep "$en2" "$outputkk" > magsv.kk_0.03_ax_12802_40-"$fs2"
[…]

### 2017-07-19 mu/up/up-scripts/up-vab-rtp.sh

@@ -2,7 +2,7 @@
 
 angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
 
-an=040
+an=035
 kp=12802
 ec=40
 sc=0
@@ -22,33 +22,33 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
-ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
-az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
-out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
+az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 calc
 
-ax=v.kk_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
-ay=v.kk_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"-0.0001 
[…]

### 2017-07-19 mu/alt/alt-res-0.7-1.0-3500pts/alt-vab-angles.sh
new plots almost completed

@@ -1,7 +1,0 @@
-#!/bin/bash
-
-angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
-
-for i in ${angles[@]}; do
-    vab.sh 14452 65 0 32 0.03 "$i"
-done

### 2017-07-19 mu/alt/alt-scripts/alt-magsvab-inang.sh

@@ -1,16 +1,17 @@
 #!/bin/bash
 
-# angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
-#              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
-
 angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
-             095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
-             185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
-             275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
+             095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+# angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+             # 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 
+             # 185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
+             # 275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
 # FIXED ENERGY:
 # en1="9.12000E-01"
-en1="7.20000E-01"
+en1="0.7201200E+00"
+en2="7.20120E-01"
 
 # OUTPUT FILE SUFIX:
 # fs1="0.912eV"
@@ -46,8 +47,8 @@ inputsm=( v.sm_0.03_xx_14452_65-spin_scissor_0_Nc_32_ang_
 
 calc
 
-grep "$en1" "$outputkk" > magsv.kk_ax_14452_65-"$fs1"
-grep "$en1" "$outputsm" > magsv.sm_0.03_ax_14452_65-"$fs1"
+grep "$en2" "$outputkk" > magsv.kk_ax_14452_65-"$fs1"
+grep "$en2" "$outputsm" > magsv.sm_0.03_ax_14452_65-"$fs1"
 
 ############################## V_{s^y} #########################################
 
@@ -61,8 +62,8 @@ inputsm=( v.sm_0.03_xy_14452_65-spin_scissor_0_Nc_32_ang_
 
 calc
 
[…]

### 2017-07-20 mu/alt/alt-scripts/alt-magsvab-inang.sh
Analysis for kk responses completed

@@ -9,13 +9,15 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              # 275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
 # FIXED ENERGY:
-# en1="9.12000E-01"
-en1="0.7201200E+00"
-en2="7.20120E-01"
+# en1="0.7201200E+00"
+en1="0.9116748E+00"
+
+# en2="7.20120E-01"
+en2="9.11675E-01"
 
 # OUTPUT FILE SUFIX:
-# fs1="0.912eV"
-fs1="0.720eV"
+# fs1="0.720eV"
+fs1="0.912eV"
 
 deg=180/3.141592
 

### 2017-07-20 mu/up/up-scripts/up-magsvab-inang.sh

@@ -9,15 +9,18 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 #              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
 #### FIXED ENERGY:
+en1="0.8434217E-01"
 # en1="0.1954652E+01"
-en1="0.1957953E+01"
+# en1="0.1957953E+01"
 
+en2="8.43422E-02"
 # en2="1.95465E+00"
-en2="1.95795E+00"
+# en2="1.95795E+00"
 
 #### OUTPUT FILE SUFIX:
+fs1="0.084eV"
 # fs1="1.954eV"
-fs1="1.957eV"
+# fs1="1.957eV"
 
 deg=180/3.141592
 

### 2017-07-20 mu/article/article.tex
Finishing corrections

@@
 In this paper we present two 50\% hydrogenated graphene noncentrosymmetric
-structures both presenting a discernible band gap: the \emph{up} structure,
+structures both presenting a discernible band gap: the \emph{Up} structure,
 shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
-only in the upper side of the structure while the \emph{alt} structure, shown
+only in the upper side of the structure while the \emph{Alt} structure, shown
 in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
@@
 describe the details of calculations and the corresponding SVI spectra for the
-\emph{up} and \emph{alt} structures. Finally, we present our conclusions in
+\emph{Up} and \emph{Alt} structures. Finally, we present our conclusions in
 Section \ref{sec:conclusions}.
@@
 
-\caption{Unit cell of \emph{up} structure. Layer division, atom types and
-positions for the \emph{up} structure. The structure unit cell was divided in
+\caption{Unit cell of \emph{Up} structure. Layer division, atom types and
+positions for the \emph{Up} structure. The structure unit cell was divided in
 two layers corresponding to hydrogen and carbon atoms.The corresponding layer
@@
 
-\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
-positions for the \emph{alt} structure. The structure unit cell was divided in
+\caption{Unit cell of \emph{Alt} structure. Layer division, atom types and
+positions for the \emph{Alt} structure. The structure unit cell was divided in
 six layers corresponding each one to atoms in different $z$ positions. The
@@
 noncentrosymmetric semi-infinite 2D carbon systems with 50\% hydrogenation in
-different arrangements. We recall that the \emph{up} structure has hydrogen
-atoms only on the upper side of the carbon sheet while the \emph{alt} structure
+different arrangements. We recall that the \emph{Up} structure has hydrogen
+atoms only on the upper side of the carbon sheet while the \emph{Alt} structure
 has alternating hydrogen atoms on the upper and bottom sides. Also we take the
@@
 \ref{fig:up-struc} and \ref{fig:alt-struc}. The coordinates for the
-\emph{up} and \emph{alt} unit cells of the structures are presented in Tables
+\emph{Up} and \emph{Alt} unit cells of the structures are presented in Tables
 \ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
@@
 The convergence parameters for the calculations of our results corresponding to
-the \emph{up} and \emph{alt} structures are cutoff energies of 65\,Ha and
-40\,Ha, resulting in LDA energy band gaps of 0.088\,eV and 0.720\,eV,
-respectively. The energy eigenvalues and matrix elements for the \emph{up} and
-\emph{alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
-$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ 
-and $\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron
-method (LATM).\cite{nastosPRB07}
-We neglect the
-anomalous velocity term $\hbar(\bfgs\times\nabla V)/4m^2c^2$, 
-where $V$ is the crystal potential, in 
- $\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give
-small contribution to PSC.\cite{bhatPRL05}
-Therefore, $[\hat\bfv,\hat\bfS]=0$ and 
-Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat
-S^\rmb=\hat S^\rmb \hat v^\rma$.
+the \emph{Up} and \emph{Alt} structures are cutoff energies of 40\,Ha and
+65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
+respectively. The energy eigenvalues and matrix elements for the \emph{Up} and
+\emph{Alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
+$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ and
+$\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron method
+(LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
+$\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the crystal potential, in
+$\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give small contribution
+to PSC.\cite{bhatPRL05} Therefore, $[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1}
+reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$.
 
@@
 \hline
-\emph{up}    & 2D   & 40    & 0.088  & $\mathrm{yz}$ &  87.2    \\
-             &      &       & 1.938  & $\mathrm{yz}$ &  22.2    \\
-             &      &       & 1.972  & $\mathrm{yz}$ & -29.7    \\
-\emph{alt}   & 2D   & 145   & 0.720  & $\mathrm{yz}$ & -40.2    \\
-             &      &       & 0.912  & $\mathrm{yz}$ & -32.9    \\
- CdSe        & bulk & 90    & 0.906  & $\mathrm{zz}$ & -26.9    \\
- GaAs        & bulk & 90    & 2.312  & $\mathrm{xx}$ & -21.6    \\
+\emph{Up}    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  684.2    \\
+             &      &       & 1.954  & $\mathrm{yz}$ &  293.9    \\
+             &      &       & 1.958  & $\mathrm{yz}$ & -273.0    \\
+\emph{Alt}   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -722.2    \\
+             &      &       & 0.911  & $\mathrm{yz}$ & -357.8    \\
+ CdSe        & bulk & 90    & 0.912  & $\mathrm{zz}$ &  -32.3    \\
+ GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -29.9    \\
 \hline
@@
     \caption{Comparison of most intense responses of
-    $\mathcal{V}^{\mathrm{ab}}$ for 2D \emph{alt} and \emph{up}, and bulk CdSe
+    $\mathcal{V}^{\mathrm{ab}}$ for 2D \emph{Alt} and \emph{Up}, and bulk CdSe
     and GaAs structures and their corresponding polarization angle $\alpha$.}
@@
 Using  Eq. \eqref{eq:vab-aw}, we calculated 
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{up} and
-\emph{alt} 2D structures and for CdSe and GaAs which are bulk systems; 
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and
+\emph{Alt} 2D structures and for CdSe and GaAs which are bulk systems; 
 the results
@@
 % 
-The most intense response corresponds to the \emph{up} structure centered at
-0.088\,eV 
-corresponding to the long-wavelength infrared radiation (LWIR) 
-and reaching a $\calv^{\rmy\rmz}=87.2$ Km/s, which means the
-electrons moving along $y$ (parallel to the surface) with the spin
-polarized along $z$ (perpendicular to the surface),
-with a speed of 87.2 Km/s.
-% 
-For an energy range from 0.66\,eV to 3.0\,eV, 
-corresponding
-to energies of the Near Infrared (NIR) to visible radiation (VIS), 
-all
-four systems have contributions of the same order of magnitude.
-% 
-For this energy range the \emph{up} structure has two peaks centered at
-1.938\,eV and 1.972\,eV reaching $\calv^{\rmy\rmz}=22.2$ Km/s and
-$\calv^{\rmy\rmz}=-29.7$ Km/s and the 
-\emph{alt} structure has two peaks centered at 0.720\,eV
-and 0.912\,eV reaching 
-$\calv^{\rmy\rmz}=-40.2$ Km/s
-and
-$\calv^{\rmy\rmz}=-32.9$ Km/s, 
-respectively.
+The most intense response corresponds to the \emph{Alt} structure centered at
+0.720\,eV corresponding to the short-wavelength infrared radiation (SWIR) and
+reaching a $\calv^{\rmy\rmz}=-722.2$ Km/s, which means the electrons moving
+along $y$ (parallel to the surface) with the spin polarized along $z$
+(perpendicular to the surface), with a speed of -722.2 Km/s.
+% 
+For an energy range from 0.66\,eV to 3.0\,eV, corresponding to energies of the
+Near Infrared (NIR) to visible radiation (VIS), the \emph{Up} structure has two
+peaks centered at 1.954\,eV and 1.958\,eV reaching $\calv^{\rmy\rmz}=293.9$
+Km/s and $\calv^{\rmy\rmz}=-273.0$ Km/s and the \emph{Alt} structure one more
+peak centered at 0.0.911\,eV reaching $\calv^{\rmy\rmz}=-357.83$ Km/s.
 % 
 Then, for the bulk structures we have that the CdSe has only one intense
-response centered at 0.906\,eV reaching 
-$\calv^{\rmz\rmz}=-26.9$ Km/s, 
-and the
-GaAs structure response reaches the maximum centered at
-2.312\,eV reaching
-$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-21.6$ Km/s.
+response centered at 0.912\,eV reaching $\calv^{\rmz\rmz}=-32.3$ Km/s, and the
+GaAs structure response reaches the maximum centered at 2.326\,eV reaching
+$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=--28.9$ Km/s.
 % 
@@
 % 
-We remark that the 2D structures have resonances that give 
-larger values for $\calv^{\rma\rmb}$ than the
-bulk crystals; in particular
-the \emph{up} structure is
-$\sim 5$ times more intense.
+We remark that the 2D structures have resonances that give larger values for
+$\calv^{\rma\rmb}$ than the bulk crystals; in particular the \emph{Alt}
+structure is $\sim 22$ times more intense.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{upplots/up-vsz-3d-1}
-    \\
-    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}
-
-    \caption{$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ response
-    as a function of the photon energy and polarization angle $\alpha$ for the
-    \emph{up} structure for two energy ranges. The absolute maxima is located
-    for an energy range from 0.08\,eV to 0.10\,eV, in the LWIR
-   range, and two local maxima from 1.90\,eV to 1.93\,eV and from
-    1.96\,eV to 2.0\,eV, in the VIS range, all for polarization
-    angles between $25^{\circ}$ and $50^{\circ}$.}
-    \label{fig:up-vsz-3d}   
+    \includegraphics[width=\linewidth]{upplots/up-vsz-w1}
+    \caption{Caption here}
+    \label{fig:up-vsz-w1}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
-    \\
-    \vspace{4mm}
-    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
-
-    \caption{For the {\it up} structure and  fixing the energy to
-      0.088 eV (top panel) and 1.972 eV (lower panel), 
-  we show 
-    $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)$ (left
-    scale), the corresponding velocity angle
-    $\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale), the
-    collinear (green arrow) and perpendicular (blue arrow) angles.
-}
-    \label{fig:up-vaz-rag}
+    \includegraphics[width=\linewidth]{upplots/up-vsz-w2}
+    \caption{caption here}
+    \label{fig:up-vsz-w2}
 \end{figure}
@@
 
-Using Eq. \eqref{eq:vs-mag}, we calculated 
-$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
-and made the analysis for the case when the spin is fixed
-along $z$, i.e. directed perpendicularly to the surface of the \emph{up} and
-\emph{alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
+Using Eq. \eqref{eq:vs-mag}, we calculated $\mathcal{V}_{\sigma^{\mathrm{b}}}
+(\omega,\alpha)$ and made the analysis for the case when the spin is fixed
+along $z$, i.e. directed perpendicularly to the surface of the \emph{Up} and
+\emph{Alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
 angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
@@
 
-\subsubsection{{\it up} structure}\label{up:fs}
-
-We present in Fig. \ref{fig:up-vsz-3d} 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
-% (Eq. \eqref{eq:vs-mag})
-for the two energy ranges of the \emph{up} structure that give the
-highest values for $\calv^{\rmy\rmz}$ shown in Fig.~\ref{fig:vab-str-comp}.
-% 
-We obtain that the zone where the maximum response is reached corresponds to
-a energy range of the incident beam from 0.084\,eV to 0.093\,eV, 
-corresponding to the LWIR,
-and polarization angles $\alpha$ 
-between $30^{\circ}$ and $45^{\circ}$. 
-Also,  two local maxima are held for same 
-$\ga$ between $30^{\circ}$ and $45^{\circ}$, 
-but for an energy range between 1.90\,eV and 2.05\,eV, in the VIS
-range.
+\subsubsection{\emph{Up} structure}\label{up:fs}
+
+We present in Figs. \ref{fig:up-vsz-w1} and \ref{fig:up-vsz-w2}
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ for the two energy ranges
+of the \emph{Up} structure that give the highest values for $\calv^{\rmy\rmz}$
+shown in Fig.~\ref{fig:vab-str-comp}.
+% 
+We obtain that the zone where the maximum response is reached corresponds to a
+energy range of the incident beam from 0.084\,eV to 0.093\,eV, corresponding to
+the LWIR, and polarization angles $\alpha$ between $35^{\circ}$ and
+$55^{\circ}$. Also,  two local maxima are held for same $\ga$ between
+$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.950\,eV and
+1.960\,eV, in the VIS range.
 % %%%%%%%%%%%%%%%%% 
@@
 
-In the top panel of Fig. \ref{fig:up-vaz-rag} we first analyze the
-response for
-$\hbar\go= 0.088$ eV which gives the maximum as shown
-in Fig. \ref{fig:up-vsz-3d} . 
-We show 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
-as a function of $\ga$
-(left scale, black solid line). 
-The absolute maximum is obtained when
-$\alpha = 40^{\circ}$ resulting in a value of
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 95.8$\,Km/s, 
-that according to Eq.~\eqref{eq:vs-mag} 
-comes from 
-$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)=39.8$\,Km/s and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)=87.2$\,Km/s.
+In bottom panel of Fig. \ref{fig:up-vsz-w1} we first analyze the response for
+$\hbar\go= 0.084$ eV which gives the maximum. We show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\ga$
+(left scale, black solid line). The absolute maximum is obtained when $\alpha =
+35^{\circ}$ resulting in a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 758.2$\,Km/s, that according to Eq.~\eqref{eq:vs-mag} comes
+from $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 326.7$\,Km/s and
+$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha) = 684.2$\,Km/s.
 % 
 In the same panel we present the corresponding velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red dashed line), that for
-the absolute maximum at $\ga=40^\circ$ is
-$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) = 65^{\circ}$. 
-This results means that at $\hbar\go=0.088$ eV and a polarization
-angle of the incoming 
-electric field of $\ga=40^\circ$ 
-the electrons with a spin pointing along $z$ move at angle of 
-$\gamma_{\mathrm{z}}(\hbar\omega=0.088\text{eV},\alpha=40^\circ) =
-65^{\circ}$
-with respect to the $x$ direction,  
-with a  maximum speed
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  95.8 Km/s.
-Also,
-from Eq. \eqref{eq:gamma-par} we find that 
-$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=65.4^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 82.3$ Km/s 
-(see green arrow),  
-and 
-that from Eq. \eqref{eq:gamma-perp}, 
-$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=65.5^\circ$,
-gives $\ga=155.5^\circ$, with  
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 24.8$ Km/s
-(see blue arrow); thus, for $\hbar\go=0.088$ eV, an
-$\alpha=65.4^\circ$ ($\alpha=155.5^\circ$) gives 
-electrons with spin polarized along $z$
-moving 
-parallel (perpendicular) to the
-incident electric field,  with a speed of 82.3 (24.8) Km/s. 
-% 
-We also find that for all values of $\ga$,
-$\gamma_{\mathrm{z}}(\omega,\alpha) =65.4^{\circ}\pm 0.3^{\circ}$,
-being almost constant, and 20 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 95.8 Km/s.
-%
-
-In the bottom panel of Fig. \ref{fig:up-vaz-rag}, now we take
-$\hbar\go=1.972$ eV which is the local maximum 
-shown in the bottom panel of Fig. \ref{fig:up-vsz-3d}. 
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red line), that for the
+absolute maximum at $\ga = 35^\circ$ is $\gamma_{\mathrm{z}}(\hbar\omega =
+0.084\text{eV},\alpha = 35^\circ) = 64.475^{\circ}$. This results means that at
+$\hbar\go=0.084$ eV and a polarization angle of the incoming electric field of
+$\ga = 35^\circ$ the electrons with a spin pointing along $z$ move at angle of
+$\gamma_{\mathrm{z}}(\hbar\omega = 0.084\text{eV},\alpha=35^\circ) \sim
+64.5^{\circ}$ with respect to the $x$ direction, with a  maximum speed
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  758.2 Km/s. Also, from
+Eq. \eqref{eq:gamma-par} we find that
+$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.475^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 646.0$ Km/s (see green
+arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.47^\circ$, gives
+$\ga=154.47^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
+195.6$ Km/s (see blue arrow); thus, for $\hbar\go=0.084$ eV, an $\alpha \sim
+65.47^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
+along $z$ moving parallel (perpendicular) to the incident electric field,  with
+a speed of 646.0 (195.6) Km/s.
+% 
+We also find that for all values of $\ga$, $\gamma_{\mathrm{z}}(\omega,\alpha)
+\sim 64.48^{\circ}$, being almost constant, and 180.0 Km/s
+$<\calv_{\gs^z}(\go,\ga)<$ 758.2 Km/s.
+
+In the bottom panel of Fig. \ref{fig:up-vsz-w2}, now we take
+$\hbar\go=1.954$ eV which is the local maximum 
+shown in the to panel of same figure. 
 The local maximum is
-again at  $\alpha = 40^{\circ}$ with
+again at  $\alpha = 35^{\circ}$ with
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
-30.3$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
-78.2^{\circ}$.
-% 
-In this case,  
-$\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 78.4^{\circ}$ with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =18.8$ Km/s 
-(green circled box and arrow),
-and
-% 
-$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.5^{\circ}$, for 
-$\alpha =168.5^ {\circ}$ 
-(blue squared box and arrow).
-% 
-We find  that the velocity angle is almost constant at
-$78.4^{\circ}\pm 0.3^\circ$ 
-for  $0^{\circ} \leq
-\alpha \leq 100^{\circ}$,
-and 1 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 30.3 Km/s.
+300.4$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
+78.0^{\circ}$.
+% 
+In this case, $\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
+78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =183.7$
+Km/s (green circled box and arrow), and
+$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.0^{\circ}$, for $\alpha =168.0^
+{\circ}$ (blue squared box and arrow).
+% 
+We find  that the velocity angle is almost constant having a range from
+$77^{\circ}$ to $78.04^{\circ}$ for  $0^{\circ} \leq
+\alpha \leq 180^{\circ}$, and 6.8 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 300.4 Km/s.
 % 
@@
 the maxima for
-$\hbar\go=0.088$ eV and $\alpha=40^{\circ}$, with
-$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=37.4$ Km/s and
-$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=24.8$ Km/s,
-$\gamma_{\mathrm{x}}(\omega,\alpha) = 12.5^{\circ}$, and 
-$\gamma_{\mathrm{y}}(\omega,\alpha) = 159.7^{\circ}$
+$\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
+$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
+$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
+$\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
-    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
-    as a function of the photon energy and polarization angle $\alpha$  for the
-    \emph{alt} structure. The local and the absolute maxima are located in the
-    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
-    respectively, and both in the Near Infrared and for polarization angles
-    between $120^{\circ}$ and $150^{\circ}$.}
-    \label{fig:alt-3d-vsb}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
-    \caption{Most intense response of
-    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frame, left
-    scale) the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top
-    frame, right scale), the collinear (circled box) and perpendicular (square
-    box) angles, and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
-    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
-    structure fixing the energy to 0.912\,eV.}
-    \label{fig:alt-vaz-rag}
+    \includegraphics[width=\linewidth]{altplots/alt-vsz}
+    \caption{Caption here}
+    \label{fig:alt-vsz}
 \end{figure}
@@
 
-\subsubsection{{\it alt} structure}
-
-We proceed to analyse the ${\it alt}$ structure, just as we did the
-{\it up} structure. 
-Fig. \ref{fig:alt-3d-vsb} shows
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (Eq. \eqref{eq:vs-mag}),
-where we see that
-% 
-the maximum response is reached for $\hbar\go=0.912$ eV
-and a local maximum is obtained at
-$\hbar\go=0.720$ eV, both located in the
-short-wavelength infrared radiation (SWIR)
- range and for polarization angles, $\ga$,  between $120^{\circ}$ and $150^{\circ}$.
+\subsubsection{\emph{Alt} structure}
+
+We proceed to analyze the $\emph{Alt}$ structure, just as we did the \emph{Up}
+structure. Fig. \ref{fig:alt-vsz} shows $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ (Eq. \eqref{eq:vs-mag}), where we see that the maximum
+response is reached for $\hbar\go=0.720$ eV and a local maximum is obtained at
+$\hbar\go=0.912$ eV, both located in the short-wavelength infrared radiation
+(SWIR) range and for polarization angles, $\ga$,  between $135^{\circ}$ and
+$160^{\circ}$.
 
@@
 % %%%%%%%%%%%%%%%%%
-In Fig. \ref{fig:alt-vaz-rag} we plot $\calv_{\gs^z}(\go,\ga)$ vs. $\ga$
-(left scale, black solid line), fixing the energy to
-0.912 eV for which the response is maximized as shown in the
-top panel of Fig. \ref{fig:alt-3d-vsb}. The absolute maximum is
-obtained for
-$\alpha = 145^{\circ}$ with  
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 43.0$ Km/s.
+In bottom panel of Fig. \ref{fig:alt-vsz} we plot $\calv_{\gs^z}(\go,\ga)$ vs.
+$\ga$ (left scale, black line), fixing the energy to 0.720 eV. The absolute
+maximum is obtained for $\alpha = 150^{\circ}$ with
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.5$ Km/s.
 % 
 In the same panel we present the velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red dashed line),
-that for the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) =
-49.9^{\circ}$.
-% 
-Also, the green circle indicates
-the value of $\ga$ for which the 
-electrons move parallel to the incoming electric field, 
-i.e. $\alpha = \gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
-53.5^{\circ}$, with 
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 12.7$ Km/s. 
-Likewise, the blue circle indicates
-the value of $\ga$ for which the electrons move perpendicular to the
-incoming electric field, i.e. 
-$\alpha=140^{\circ}$, with
-$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$, and 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=43.0$ Km/s.
-% 
-We also have that 
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ 
-is centered at $51.5^{\circ}$ having
-variations of $\pm 2^{\circ}$ for $0^{\circ} \leq
+$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red line), that for
+the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 108.9^{\circ}$.
+% 
+Also, the green circle indicates the value of $\ga$ for which the electrons
+move parallel to the incoming electric field, i.e. $\alpha =
+\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 108.7^{\circ}$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 511.3$ Km/s. Likewise, the
+blue circle indicates the value of $\ga$ for which the electrons move
+perpendicular to the incoming electric field, i.e. $\alpha=19.8^{\circ}$, with
+$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=109.8^{\circ}$, and
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=61.5$ Km/s.
+% 
+We also have that $\gamma_{\mathrm{z}}(\omega,\alpha)$ is centered at
+$109.1^{\circ}$ having variations of $\pm 0.9^{\circ}$ for $0^{\circ} \leq
 \alpha \leq 180^{\circ}$.
@@
 Again, for the cases in which the spin polarization is parallel to the surface
-the maximum values are
-$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 27.1$ Km/s and
-$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 33.2$ Km/s, corresponding to 
-$\gamma_{\mathrm{x}}(\omega,\alpha) = 100.1^{\circ}$
-$\gamma_{\mathrm{y}}(\omega,\alpha) = 67.9^{\circ}$
-and both for $\alpha=145^{\circ}$, where
-the plots are not presented.
+the maximum values are $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) =
+297.8$ Km/s and $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$
+Km/s, corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.2^{\circ}$ and both for
+$\alpha=145^{\circ}$, where the plots are not presented.
 
@@
 
- Using the Eq. \eqref{eq:vv-mag}, we calculated the
-$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ for the cases when the velocity is
-fixed along the $\rma=x$ or $\rma=y$ direction on the surface of the \emph{up} and
-\emph{alt} structures, and from the Eqns. \eqref{eq:polar-ang} and 
-\eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
-(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
-corresponding to the direction of the spin.
-
-\subsubsection{{\it up} structure}
-
+Using the Eq. \eqref{eq:vv-mag}, we calculated the $\mathcal{V}^{\mathrm{a}}
+(\omega,\alpha)$ for the cases when the velocity is fixed along the $\rma=x$ or
+$\rma=y$ direction on the surface of the \emph{Up} and \emph{Alt} structures,
+and from the Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we
+determined the polar, $\theta_{\mathrm{a}} (\omega,\alpha)$, and azimuthal,
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, angles corresponding to the direction
+of the spin.
+% 
+The plots corresponding to the velocity fixed along the axes as a function of
+the energy and polarization angle for the \emph{Up} and \emph{Alt} structures
+are similar in shape to the top panels of Figs. \ref{fig:up-vsz-w1}, 
+\ref{fig:up-vsz-w2}, and \ref{fig:alt-vsz} and they are not presented here.
+
+\subsubsection{\emph{Up} structure}
+
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
+%     \\
+%     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
+%     \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
+%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
+%     photon energy and polarization angle $\alpha$ for the \emph{Up} structure.
+%     The absolute maxima of both are localized in the energy range from 0.08\,eV
+%     to 0.10\,eV, in the Far  Infrared, and for polarization angles from
+%     $25^{\circ}$ to $50^{\circ}$.}
+%     \label{fig:up-3d-vva-1}
+% \end{figure}
 \begin{figure}[t]
     \centering
-    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
-    \\
-    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
-
-    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
-    photon energy and polarization angle $\alpha$ for the \emph{up} structure.
-    The absolute maxima of both are localized in the energy range from 0.08\,eV
-    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
-    $25^{\circ}$ to $50^{\circ}$.}
-    \label{fig:up-3d-vva-1}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
-    \\ \vspace{4mm}
-    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
-
-    \caption{Most intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
-    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
-    angles (top frames right scale), and the corresponding three components
-    (bottom frames) for the \emph{up} structure fixing the polarization angle
-    to $\alpha=40^{\circ}$ to maximize the response.}
+    \includegraphics[width=\linewidth]{upplots/up-vx-vy-w1}
+    \caption{caption here}
     \label{fig:up-vab-comp-rtp-1}
@@
 % %%%%%%%%%%%%%%%%% 
-In Fig. \ref{fig:up-3d-vva-1} we plot
-$\mathcal{V}^{\mathrm{x}}(\omega,\alpha)$  
-and
-$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$  
-for the
-\emph{up} structure, where
-%
-we see that each response has a maximum for
-$\hbar\omega=0.088$ eV,
-in the LWIR, and 
-$\ga=40^{\circ}$. 
-% 
-Fixing $\ga=40^{\circ}$ eV,
-in Fig. \ref{fig:up-vab-comp-rtp-1} we plot 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ 
-and $\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$
-(left scale, black solid line) 
-where each responses has a maximum of
-58.7\,Km/s and 87.9\,Km/s, respectively, for $\hbar\go=0.088$ eV.
-% 
-We also
-present the corresponding polar 
-(right scale, red dashed line) 
-and azimuthal 
-(right scale, blue dashed line)
-spin polarization angles
-that have values of 
-$\theta_{\mathrm{x}}(\omega,\alpha) = 47.4^{\circ}$,
-and $\varphi_{\mathrm{x}}(\omega,\alpha) = 212.5^{\circ}$
- when the  electron moves along $x$,
-and  $\theta_{\mathrm{y}}(\omega,\alpha) = 7.6^{\circ}$, and
- $\varphi_{\mathrm{y}} (\omega,\alpha) =132.7^{\circ}$,
-when the electron moves along $y$.
-This means that, the spin is directed upward the third Cartesian
-quadrant of the $xy$ plane when the electron moves along $x$, and is directed almost
-perpendicularly over the $xy$ plane when it moves along $y$.
+We proceed to analyze the \emph{Up} structure for the case when the velocity is
+directed along the $x$ and $y$ coordinates. We found that each response has a
+maximum for $\hbar\omega=0.084$ eV, in the LWIR, and $\ga=35^{\circ}$.
+% 
+Fixing $\ga=35^{\circ}$, in Fig. \ref{fig:up-vab-comp-rtp-1} we plot
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$ (left scale, black
+line) where each responses has a maximum of 442.4\,Km/s and 705.5\,Km/s,
+respectively, for $\hbar\go=0.084$ eV.
+% 
+We also present the corresponding polar (right scale, red line) and azimuthal
+(right scale, blue dashed line) spin polarization angles that have values of
+% 
+$\theta_{\mathrm{x}}(\omega,\alpha) = 42.4^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.1^{\circ}$ 
+% 
+when the  electron moves along $x$, and  
+$\theta_{\mathrm{y}}(\omega,\alpha) = 14.1^{\circ}$, and
+$\varphi_{\mathrm{y}} (\omega,\alpha) = 81.4^{\circ}$, 
+% 
+when the electron moves along $y$. This means that, the spin is directed upward
+the third Cartesian quadrant of the $xy$ plane when the electron moves along
+$x$, and is directed almost perpendicularly over the $xy$ plane when it moves
+along $y$.
 % 
@@
 direction is almost constant for all the energies across the peak of the
-response, having a ranges of $ 44.4^{\circ} < \theta_{\mathrm{x}}
-(\omega,\alpha) < 56.2^{\circ} $ and $210.3^{\circ} < \varphi_{\mathrm{x}}
-(\omega,\alpha) < 217.4^{\circ}$. Then, hen the electron moves along $y$ the
-spin's polar angle has again minimal variations, $ 9.76^{\circ} <
-\theta_{\mathrm{y}} (\omega,\alpha) < 13.7^{\circ}$, but in contrast with this
-the azimuthal angle has significative variations, $99.3^{\circ} <
-\varphi_{\mathrm{y}} (\omega,\alpha) < 196.1^{\circ}$.
-
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
-%     \\
-%     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
-
-%     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
-%     of the photon energy and polarization angle $\alpha$ for the \emph{up}
-%     structure. Two local maxima of both responses are localized in the energy
-%     range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the
-%     visible radiation range, and for polarization angles between $25^{\circ}$
-%     and $50^{\circ}$.}
-%     \label{fig:up-3d-vva-2}
-% \end{figure}
+response, having a ranges of
+% 
+$42.4^{\circ} < \theta_{\mathrm{x}}(\omega,\alpha) < 53.6^{\circ} $ 
+and $208.1^{\circ} < \varphi_{\mathrm{x}} (\omega,\alpha) < 215.8^{\circ}$. 
+% 
+Then, when the electron moves along $y$ the spin's polar angle has again
+small variations,
+% 
+$7.6^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) < 14.1^{\circ}$, 
+% 
+but in contrast with this the azimuthal angle has significant variations,
+% 
+$81.4^{\circ} < \varphi_{\mathrm{y}} (\omega,\alpha) < 150.7^{\circ}$.
+
 \begin{figure}[t]
     \centering
-    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
-    \\ \vspace{4mm}
-    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
-
-    \caption{Intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
-    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
-    angles (top frames right scale), and the corresponding three components
-    (bottom frames) for the \emph{up} structure fixing the polarization angle
-    to $\alpha=40^{\circ}$ to maximize the response.}
-
-    \label{fig:up-vab-comp-rtp-2}
+    \includegraphics[width=\linewidth]{upplots/up-vx-vy-w2}
+    \caption{Caption here}
+    \label{fig:up-vx-vy-w2}
 \end{figure}
@@
 % %%%%%%%%%%%%%%%%%
-
-% From Sec.~\ref{up:fs}, we know that the {\it up} structure has two
-% more resonant structures at $\hbar\go=1.932$ eV, and
-% $\hbar\go=1.972??$ eV. For this case, where the velocity is fixed
-% along $x$ or $y$, we find that
-
-% In top and bottom panels of Fig. \ref{fig:up-3d-vva-2} we present the
-% result of evaluate Eq. \eqref{eq:vv-mag} for the same structure fixing the
-% velocity in the $x$ and $y$ direction for other range of energies that present
-% a intense response.
-% From this figure we can see that the two local maxima are obtained for energies
-% between 1.80\,eV and 2.10\,eV, in the range of visible radiation, and
-% polarization angles between $30^ {\circ}$ and $45^{\circ}$.
-%
-
-In  
-Fig. \ref{fig:up-vab-comp-rtp-2},  for 
-the {\it up} structure, 
-we plot 
-$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ vs. $\go$, and 
-fixing $\alpha=40^{\circ}$; the range of $\go$ lies in part of the
-VIS range.
-We see that there are two local maxima at $\hbar\go=1.932$ eV
-and $\hbar\go=1.972$ eV. For the latter that is the most intense
-we obtain
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  9.9$ Km/s and  
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 49.4$ Km/s.
-For these local maxima, 
-the corresponding polar and azimuthal spin
-polarization angles are
-$\theta_{\mathrm{x}}(\omega,\alpha) =129.1^{\circ}$, and $\varphi_{\mathrm{x}}
-(\omega,\alpha) = 229.2^{\circ}$,
-for the electron moving along $x$,
-and
-$\theta_{\mathrm{y}} (\omega,\alpha) = 127.0^{\circ}$,
- and $\varphi_{\mathrm{y}}(\omega,\alpha) = 227.1^{\circ}$
-for the electron moving along $y$. 
-We remark that these angles
-are almost constant for all the energy values across the peak of the
-this local maxima, for which the spin is directed 
-downward in the third Cartesian quadrant
-of the $xy$ plane when it moves along either $x$ or $y$ directions.
-For the $\hbar\go=1.932$\,eV peak we obtain  
-$\theta_{\mathrm{x}} (\omega,\alpha) = 42.0^{\circ}$, and 
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 58.7^{\circ}$, with
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  6.6$ Km/s,
- and 
-$\theta_{\mathrm{y}}(\omega,\alpha) =45.2$, and 
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 56.1$, with
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) =  29.0$ Km/s.
-However, for this local maximum, the spin angles are not constant
-across the resonant peak.  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In  Fig. \ref{fig:up-vx-vy-w2}, for the \emph{Up} structure, we plot
+$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ vs. $\go$, fixing
+$\alpha=35^{\circ}$; the range of $\go$ lies in part of the VIS range. We see
+that there are two local maxima at $\hbar\go=1.954$ eV and $\hbar\go=1.958$ eV.
+For the first that is the most intense we obtain
+% 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  93.9$ Km/s and  
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 456.3$ Km/s.
+% 
+For these local maxima, the corresponding polar and azimuthal spin polarization
+angles are
+% 
+$\theta_{\mathrm{x}} (\omega,\alpha) = 48.5^{\circ}$, and 
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 54.4^{\circ}$,
+% 
+for the electron moving along $x$, and
+% 
+$\theta_{\mathrm{y}} (\omega,\alpha) = 49.9^{\circ}$, and 
+$\varphi_{\mathrm{y}} (\omega,\alpha) = 51.8^{\circ}$
+% 
+for the electron moving along $y$. We remark that these angles are almost
+constant for all the energy values across the peak of this local maxima, for
+which the spin is directed downward in the third Cartesian quadrant of the $xy$
+plane when it moves along either $x$ or $y$ directions. 
+% 
+For the $\hbar\go=1.958$\,eV peak we obtain 
+$\theta_{\mathrm{x}} (\omega,\alpha) = 129.9^{\circ}$, and 
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.5^{\circ}$, with 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 88.8$ Km/s, and
+% 
+$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.4$, with 
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 431.4$ Km/s. 
+% 
+Again, for this local maxima, the spin angles are almost constant across the
+resonant peak.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{{\it alt} structure}
-
-% \begin{figure}[tb]
-%     \centering
-%     \includegraphics[width=\linewidth]{altplots/alt-3d-vxb}
-%     \\
-%     \includegraphics[width=\linewidth]{altplots/alt-3d-vyb}
-
-%     \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
-%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function
-%     of the photon energy and polarization angle $\alpha$ for the \emph{alt}
-%     structure. The local and the absolute maxima are located in the energy
-%     ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
-%     respectively, and both in the Near Infrared and for polarization angles
-%     between $120^{\circ}$ and $150^{\circ}$.}
-%     \label{fig:alt-3d-vva}
-% \end{figure}
+\subsubsection{\emph{Alt} structure}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{altplots/alt-vxb-rtp-m}
-    \\ \vspace{4mm}
-    \includegraphics[width=\linewidth]{altplots/alt-vyb-rtp-m}
-
-    \caption{Most intense response of
-    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
-    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
-    angles (top frames right scale), and the corresponding three components
-    (bottom frames) for the \emph{alt} structure fixing the polarization angle
-    to $\alpha=145^{\circ}$ to maximize the response.}
-    \label{fig:alt-vab-comp-rtp}
+    \includegraphics[width=\linewidth]{altplots/alt-vx-vy-w1}
+    \caption{Caption here}
+    \label{fig:alt-vx-vy-w1}
 \end{figure}
 
-% %%%%%%%%%%%%%%%%%
-% %% Description of ALT |V^{a}| 3D
-% %%%%%%%%%%%%%%%%%
-
-% In top and bottom panels of Fig. \ref{fig:alt-3d-vva} we present the
-% result of evaluate Eq. \eqref{eq:vv-mag} for the
-% \emph{up} structure fixing the velocity in the $x$ and $y$ direction.
-% % 
-% From this figure we have that the relative maxima for the spin velocity along
-% $x$ and $y$ are obtained for energies between 0.70\,eV to 0.75\,eV and the
-% absolute maxima are obtained for energies between 0.90\,eV and 0.93\,eV, all
-% cases in the NIR radiation, and polarization angles between 120$^{\circ}$ and
-% 150$^{\circ}$.
-%
-
-In Fig. \ref{fig:alt-vab-comp-rtp} 
-we show  for the {\it alt} structure
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ 
-and
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha)$ 
-vs. $\omega$, for $\ga=145^\circ$, the value that maximizes both
-responses as a function of $\ga$, where we see that each response has
-two local maxima. The one at $\hbar\go=0.720$ eV gives
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =19.4??$ Km/s,
-and $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 51.9??$ Km/s, and the
-other one at $\hbar\go=0.912??$ eV gives
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 30.9$ Km/s and
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 52.3$ Km/s.
-% 
-For $\hbar\go=0.720$ eV,
-$\theta_{\mathrm{x}} (\omega,\alpha) = 45.8^{\circ}$, $\varphi_{\mathrm{x}}
-(\omega,\alpha) = 40.7^{\circ}$, 
-$\theta_{\mathrm{y}} (\omega,\alpha) =
-140.7^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha) =
-221.6^{\circ}$, implying
-% 
-that the spin is directed over the first Cartesian quadrant of the $xy$ plane
-when the spin velocity is directed along $x$, and directed downward the third
-Cartesian quadrant when the spin velocity is directed along $y$. Finally, for
-$\hbar\go=0.912$ eV, $\theta_{\mathrm{x}}(\omega,\alpha) = 153.8^{\circ}$,
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 290.4^{\circ}$, $\theta_{\mathrm{y}}
-(\omega,\alpha) = 129.0^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha)
-=228.9^{\circ}$, and the spin is directed downward in the fourth Cartesian
-quadrant of the $xy$ plane when the spin velocity is directed along $x$ and
-downward the third Cartesian quadrant when the spin velocity is directed along
-$y$.
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\linewidth]{altplots/alt-vx-vy-w2}
+    \caption{Caption here}
+    \label{fig:alt-vx-vy-w2}
+\end{figure}
+
+In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2} we show  for the
+\emph{Alt} structure $\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha)$ as a function of $\omega$, for
+$\ga=150^\circ$, the value that maximizes both responses as a function of
+$\ga$.
+% 
+The absolute maxima at $\hbar\go=0.718$ eV gives
+% 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  355.9$ Km/s, and 
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 1008.6$ Km/s, 
+% 
+and the other one at $\hbar\go=0.911??$ eV gives
+% 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 337.2$ Km/s and
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 568.8$ Km/s.
+% 
+For $\hbar\go=0.718$ eV,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, 
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.2^{\circ}$, 
+% 
+$\theta_{\mathrm{y}} (\omega,\alpha) = 118.9^{\circ}$, and 
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 161.9^{\circ}$, 
+% 
+implying that the spin is directed over the first Cartesian quadrant of the
+$xy$ plane when the spin velocity is directed along $x$, and directed downward
+the third Cartesian quadrant when the spin velocity is directed along $y$.
+% 
+Finally, for $\hbar\go=0.912$ eV, 
+% 
+$\theta_{\mathrm{x}}(\omega,\alpha) = 153.8^{\circ}$, 
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 290.4^{\circ}$,
+$\theta_{\mathrm{y}} (\omega,\alpha) = 129.0^{\circ}$, and
+$\varphi_{\mathrm{y}} (\omega,\alpha) =228.9^{\circ}$, 
+% 
+and the spin is directed downward in the fourth Cartesian quadrant of the $xy$
+plane when the spin velocity is directed along $x$ and downward the third
+Cartesian quadrant when the spin velocity is directed along $y$.
 
@@
 We have performed an \emph{ab initio} calculation for the SVI by one-photon
-absorption of linearly polarized light in the \emph{up} and \emph{alt} 2D
+absorption of linearly polarized light in the \emph{Up} and \emph{Alt} 2D
 hydrogenated graphene structures that and we made the calculation for the case
@@
 This SVI is very sensitive to the symmetry characteristics of the structures
-presenting an anisotropic behavior. We found that the \emph{up} structure has
-the most intense response resulting in $|\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)| = 95.8$\,Km/s and $|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)|
-= 87.9$\,Km/s for an energy of the incoming beam of 0.088\,eV. Also the
-response of the \emph{alt} structure is comparable to the response of GaAs and
-CdSe bulk semiconductors.
+presenting an anisotropic behavior. We found that the \emph{Up} structure has
+the most intense response for the spin directed along $z$ resulting in 
+% 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 758.2$\,Km/s and 
+% 
+for an energy of the incoming beam of 0.084\,eV. Also the \emph{Alt} structure
+has the most intense response when the spin moves along the $y$ direction
+resulting in 
+% 
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 1008.6$\,Km/s
+% 
+for an energy of the incoming beam of 0.718\,eV.
 % 
@@
 from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} The,
-according to our results the \emph{alt} structure is a good candidate and the
-\emph{up} structure an excellent candidate for the development of spintronics
-devices that require PSC due to the high spin velocity transport. The fact that
-the \emph{up} structure is better than the \emph{alt} structure comes from the
-symmetry: the first one is \emph{more} non-centrosymmetric than
-the second resulting in a more intense response of the system.
+according to our results both are excellent candidates for the development of
+spintronics devices that require PSC due to the high spin velocity transport.
 

### 2017-07-20 mu/alt/alt-scripts/alt-vab-rtp.sh

@@ -1,6 +1,6 @@
 #/bin/bash
 
-an=145
+an=150
 kp=14452
 ec=65
 sc=0

### 2017-07-21 mu/article/article.tex
Corrections before review with BMS.

@@
 We calculated the self-consistent ground state and the Kohn-Sham
-states using density functional theory in the local density approximation (DFT-
-LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
+states using density functional theory in the local density approximation 
+(DFT-LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
 % 
@@
 \emph{Alt}   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -722.2    \\
-             &      &       & 0.911  & $\mathrm{yz}$ & -357.8    \\
+             &      &       & 0.911  & $\mathrm{yz}$ & -351.7    \\
  CdSe        & bulk & 90    & 0.912  & $\mathrm{zz}$ &  -32.3    \\
- GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -29.9    \\
+ GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -28.9    \\
 \hline
@@
 Using  Eq. \eqref{eq:vab-aw}, we calculated
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and
-\emph{Alt} 2D structures and for CdSe and GaAs which are bulk systems; 
-the results
-are presented in Fig. \ref{fig:vab-str-comp}. 
-The angle $\alpha$ presented in
-the response of each structure is that for which the response is maximized in
-each case.
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and \emph{Alt} 2D
+structures and for CdSe and GaAs which are bulk systems; the results are
+presented in Fig. \ref{fig:vab-str-comp}. The polarization angle of the
+incoming beam, $\alpha$, presented in the response of each structure is that
+for which the response is maximized in each case.
 % 
@@
 Km/s and $\calv^{\rmy\rmz}=-273.0$ Km/s and the \emph{Alt} structure one more
-peak centered at 0.0.911\,eV reaching $\calv^{\rmy\rmz}=-357.83$ Km/s.
+peak centered at 0.911\,eV reaching $\calv^{\rmy\rmz}=-351.7$ Km/s.
 % 
@@
 GaAs structure response reaches the maximum centered at 2.326\,eV reaching
-$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=--28.9$ Km/s.
+$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-28.9$ Km/s.
 % 
@@
 $55^{\circ}$. Also,  two local maxima are held for same $\ga$ between
-$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.950\,eV and
+$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.952\,eV and
 1.960\,eV, in the VIS range.
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\ga$
-(left scale, black solid line). The absolute maximum is obtained when $\alpha =
+(left scale, black line). The absolute maximum is obtained when $\alpha =
 35^{\circ}$ resulting in a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}
@@
 absolute maximum at $\ga = 35^\circ$ is $\gamma_{\mathrm{z}}(\hbar\omega =
-0.084\text{eV},\alpha = 35^\circ) = 64.475^{\circ}$. This results means that at
+0.084\text{eV},\alpha = 35^\circ) = 64.47^{\circ}$. This results means that at
 $\hbar\go=0.084$ eV and a polarization angle of the incoming electric field of
@@
 Eq. \eqref{eq:gamma-par} we find that
-$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.475^\circ$, with
+$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.47^\circ$, with
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 646.0$ Km/s (see green
@@
 195.6$ Km/s (see blue arrow); thus, for $\hbar\go=0.084$ eV, an $\alpha \sim
-65.47^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
+65.5^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
 along $z$ moving parallel (perpendicular) to the incident electric field,  with
@@
 In the bottom panel of Fig. \ref{fig:up-vsz-w2}, now we take
-$\hbar\go=1.954$ eV which is the local maximum 
+$\hbar\go=1.954$ eV which gives the local maximum 
 shown in the to panel of same figure. 
@@
 In this case, $\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
-78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =183.7$
+78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 187.6$
 Km/s (green circled box and arrow), and
 $\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.0^{\circ}$, for $\alpha =168.0^
-{\circ}$ (blue squared box and arrow).
+{\circ}$ (blue squared box and arrow) with $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 92.4$.
 % 
@@
 maximum is obtained for $\alpha = 150^{\circ}$ with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.5$ Km/s.
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.6$ Km/s.
 % 
@@
 \gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 108.7^{\circ}$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 511.3$ Km/s. Likewise, the
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 538.5$ Km/s. Likewise, the
 blue circle indicates the value of $\ga$ for which the electrons move
@@
 Km/s, corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
-$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.2^{\circ}$ and both for
-$\alpha=145^{\circ}$, where the plots are not presented.
+$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
+$\alpha=150^{\circ}$, where the plots are not presented.
 
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
-%     \\
-%     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
-%     \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
-%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
-%     photon energy and polarization angle $\alpha$ for the \emph{Up} structure.
-%     The absolute maxima of both are localized in the energy range from 0.08\,eV
-%     to 0.10\,eV, in the Far  Infrared, and for polarization angles from
-%     $25^{\circ}$ to $50^{\circ}$.}
-%     \label{fig:up-3d-vva-1}
-% \end{figure}
 \begin{figure}[t]
@@
 We also present the corresponding polar (right scale, red line) and azimuthal
-(right scale, blue dashed line) spin polarization angles that have values of
+(right scale, blue line) spin polarization angles that have values of
 % 
@@
 the third Cartesian quadrant of the $xy$ plane when the electron moves along
-$x$, and is directed almost perpendicularly over the $xy$ plane when it moves
-along $y$.
+$x$, and is directed almost parallel to the $xy$ plane in the first quadrant
+when it moves along $y$.
 % 
@@
 constant for all the energy values across the peak of this local maxima, for
-which the spin is directed downward in the third Cartesian quadrant of the $xy$
+which the spin is directed upward in the first Cartesian quadrant of the $xy$
 plane when it moves along either $x$ or $y$ directions. 
@@
 $\theta_{\mathrm{x}} (\omega,\alpha) = 129.9^{\circ}$, and 
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.5^{\circ}$, with 
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.6^{\circ}$, with 
 $\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 88.8$ Km/s, and
@@
 Again, for this local maxima, the spin angles are almost constant across the
-resonant peak.
+resonant peak directed for both cases downward the third quadrant of the $xy$
+plane.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % 
-The absolute maxima at $\hbar\go=0.718$ eV gives
+The absolute maxima at {\color{red} $\hbar\go=0.718$} eV gives
 % 
@@
 % 
-and the other one at $\hbar\go=0.911??$ eV gives
+and the other one at {\color{red} $\hbar\go=0.911$} eV gives
 % 
@@
 For $\hbar\go=0.718$ eV,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 61.3^{\circ}$, 
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 358.1^{\circ}$, 
+% 
+$\theta_{\mathrm{y}} (\omega,\alpha) = 118.9^{\circ}$, and 
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 161.9^{\circ}$, 
+% 
+and so the spin is directed upward the forth Cartesian quadrant of the
+$xy$ plane when the spin velocity is directed along $x$, and directed downward
+the second Cartesian quadrant when the spin velocity is directed along $y$.
+% 
+Finally, for $\hbar\go=0.912$ eV, 
+% 
 $\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, 
@@
 % 
-$\theta_{\mathrm{y}} (\omega,\alpha) = 118.9^{\circ}$, and 
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 161.9^{\circ}$, 
-% 
-implying that the spin is directed over the first Cartesian quadrant of the
+$\theta_{\mathrm{y}} (\omega,\alpha) = 129.0^{\circ}$, and 
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.1^{\circ}$, 
+% 
+implying that the spin is directed downward the forth Cartesian quadrant of the
 $xy$ plane when the spin velocity is directed along $x$, and directed downward
 the third Cartesian quadrant when the spin velocity is directed along $y$.
-% 
-Finally, for $\hbar\go=0.912$ eV, 
-% 
-$\theta_{\mathrm{x}}(\omega,\alpha) = 153.8^{\circ}$, 
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 290.4^{\circ}$,
-$\theta_{\mathrm{y}} (\omega,\alpha) = 129.0^{\circ}$, and
-$\varphi_{\mathrm{y}} (\omega,\alpha) =228.9^{\circ}$, 
-% 
-and the spin is directed downward in the fourth Cartesian quadrant of the $xy$
-plane when the spin velocity is directed along $x$ and downward the third
-Cartesian quadrant when the spin velocity is directed along $y$.
 

### 2017-07-23 mu/alt/alt-scripts/alt-broadening-vab-ang.sh
New files with 0.0002 of broadening.

@@ -1,0 +1,24 @@
+#!/bin/bash
+
+# # Broadening not working using variable!!!
+# # br=0.0002
+
+kp=14452
+ec=65
+sc=0
+nc=32
+
+comp=( xx xy xz yx yy yz zx xy zz )
+
+ang=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+          095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${comp[@]}; do
+    for j in ${ang[@]}; do
+        # # printf "0\n0\n$a\n0\n" | /opt/science/bin/dp-5.2.99-r1883-intel13.1.117/bin/broad  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+        printf "0\n0.0002\n$a\n0\n" | /opt/science/bin/dp-5.2.99-r1883-intel13.1.117/bin/broad  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+        mv  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j".brd  v.br_0.0002_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+    done
+done
+
+

### 2017-07-23 mu/alt/alt-scripts/alt-magsvab-inang.sh

@@ -1,5 +1,15 @@
 #!/bin/bash
 
+
+#### ENERGY TO FIND & FILE SUFIX TO USE:
+# en="7.20120E-01"   ;   fs="0.720eV"
+en="9.11675E-01"   ;   fs="0.912eV"
+
+
+
+########################
+
+
 angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
 
@@ -8,79 +18,152 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
              # 185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
              # 275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
-# FIXED ENERGY:
-# en1="0.7201200E+00"
-en1="0.9116748E+00"
-
-# en2="7.20120E-01"
-en2="9.11675E-01"
-
-# OUTPUT FILE SUFIX:
-# fs1="0.720eV"
-fs1="0.912eV"
 
 deg=180/3.141592
 
-calc () {
-echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
-echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
-for i in ${angles[@]}; do
-    paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp1
-    paste .temp1 | awk '{if($1 < 0) {printf("%010.6f\n", ($1*'"$deg"')+180) ;} else {printf("%010.6f\n"), $1*'"$deg"' } }' > .deg1
-    paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i"  .deg1 | awk '{printf("%02.5E    %02.6E    %03.0f    %02.6E    %02.6E    %010.6f\n"), $1, sqrt($2*$2 + $4*$4), '"$i"', $2, $4, $5 }' >> $outputkk
-    echo  "" >> $outputkk
-    
[…]

### 2017-07-23 mu/up/up-scripts/up-broadening-vab-ang.sh

@@ -1,0 +1,24 @@
+#!/bin/bash
+
+# # Broadening not working using variable!!!
+# # br=0.0002
+
+kp=12802
+ec=40
+sc=0
+nc=32
+
+comp=( xx xy xz yx yy yz zx xy zz )
+
+ang=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
+          095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
+
+for i in ${comp[@]}; do
+    for j in ${ang[@]}; do
+        # # printf "0\n0\n$a\n0\n" | /opt/science/bin/dp-5.2.99-r1883-intel13.1.117/bin/broad  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+        printf "0\n0.0002\n$a\n0\n" | /opt/science/bin/dp-5.2.99-r1883-intel13.1.117/bin/broad  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+        mv  v.kk_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j".brd  v.br_0.0002_"$i"_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$j"
+    done
+done
+
+

### 2017-07-23 mu/up/up-scripts/up-magsvab-inang.sh

@@ -1,5 +1,15 @@
 #!/bin/bash
 
+
+#### ENERGY TO FIND & FILE SUFIX TO USE:
+en="8.44422E-02"    ;  fs="0.084eV"
+# en="1.95415E+00"    ;  fs="1.954eV"
+# en="1.95765E+00"    ;  fs="1.957eV"
+
+
+########################
+
+
 angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 
              095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
 
@@ -8,82 +18,150 @@ angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085
 #              185 190 195 200 205 210 215 220 225 230 235 240 245 250 255 260 265 270 
 #              275 280 285 290 295 300 305 310 315 320 325 330 335 340 345 350 355 360 )
 
-#### FIXED ENERGY:
-en1="0.8434217E-01"
-# en1="0.1954652E+01"
-# en1="0.1957953E+01"
-
-en2="8.43422E-02"
-# en2="1.95465E+00"
-# en2="1.95795E+00"
-
-#### OUTPUT FILE SUFIX:
-fs1="0.084eV"
-# fs1="1.954eV"
-# fs1="1.957eV"
 
 deg=180/3.141592
 
-calc () {
-echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
-echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
-for i in ${angles[@]}; do
-    paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp1
-    paste .temp1 | awk '{if($1 < 0) {printf("%010.6f\n", ($1*'"$deg"')+180) ;} else {printf("%010.6f\n"), $1*'"$deg"' } }' > .deg1
[…]

### 2017-07-24 mu/alt/alt-res-0.7-1.0-3500pts/cp-data.sh
New plots with broadening 0.0002 almost completed.

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+cp magsv.br_0.0002_az_14452_65-spin_scissor_0_Nc_32_incang_000-180 ../../article/altplots-new/alt-vsz.data1
+cp magsv.br_0.0002_az_14452_65-0.720eV ../../article/altplots-new/alt-vsz.data2
+
+cp vab-rtp.br_0.0002_x_14452_65-spin_scissor_0_Nc_32_ang_150 ../../article/altplots-new/alt-vx-vy-w1.data1
+cp vab-rtp.br_0.0002_y_14452_65-spin_scissor_0_Nc_32_ang_150 ../../article/altplots-new/alt-vx-vy-w1.data2
+
+cp vab-rtp.br_0.0002_x_14452_65-spin_scissor_0_Nc_32_ang_150 ../../article/altplots-new/alt-vx-vy-w2.data1
+cp vab-rtp.br_0.0002_y_14452_65-spin_scissor_0_Nc_32_ang_150 ../../article/altplots-new/alt-vx-vy-w2.data2

### 2017-07-24 mu/alt/alt-scripts/alt-magsvab-inang.sh

@@ -35,6 +35,7 @@ if [ $1 == 1 ]; then
     calc () {
     echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
     echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
+    echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputbr
     for i in ${angles[@]}; do
         paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp1
         paste .temp1 | awk '{if($1 < 0) {printf("%010.6f\n", ($1*'"$deg"')+180) ;} else {printf("%010.6f\n"), $1*'"$deg"' } }' > .deg1
@@ -128,10 +129,10 @@ elif [ $1 == 2 ]; then
     grep "$en" "$outputsm" > magsv.sm_0.03_ax_14452_65-"$fs"
     grep "$en" "$outputbr" > magsv.br_0.0002_ax_14452_65-"$fs"
 
-    echo -e "\t You have created:"
-    echo -e "\t\t $outputkk"
-    echo -e "\t\t $outputsm"
-    echo -e "\t\t $outputbr"
+    echo -e "\tYou have created:"
+    echo -e "\t\t magsv.kk_ax_14452_65-$fs"
+    echo -e "\t\t magsv.sm_0.03_ax_14452_65-$fs"
+    echo -e "\t\t magsv.br_0.0002_ax_14452_65-$fs"
 
     outputkk=magsv.kk_ay_14452_65-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
     outputsm=magsv.sm_0.03_ay_14452_65-spin_scissor_0_Nc_32_incang_${angles[0]}-${angles[${#angles[@]}-1]}
@@ -141,9 +142,9 @@ elif [ $1 == 2 ]; then
     grep "$en" "$outputsm" > magsv.sm_0.03_ay_14452_65-"$fs"
     grep "$en" "$outputbr" > magsv.br_0.0002_ay_14452_65-"$fs"
 
-    echo -e "\t\t $outputkk"
[…]

### 2017-07-24 mu/alt/alt-scripts/alt-vab-rtp.sh

@@ -6,6 +6,7 @@ ec=65
 sc=0
 nc=32
 sm=0.03
+br=0.0002
 
 deg=180/3.141592
 
@@ -20,13 +21,6 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
-
-calc
-
 ax=v.kk_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 ay=v.kk_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
 az=v.kk_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
@@ -34,7 +28,28 @@ out=vab-rtp.kk_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 calc
 
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an" 
+
+calc
+
[…]

### 2017-07-24 mu/up/up-res-0-0.2-2000pts/cp-data.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+cp magsv.br_0.0002_az_12802_40-spin_scissor_0_Nc_32_incang_000-180 ../../article/upplots-new/up-vsz-w1.data1
+cp magsv.br_0.0002_az_12802_40-0.084eV ../../article/upplots-new/up-vsz-w1.data2
+
+cp vab-rtp.br_0.0002_x_12802_40-spin_scissor_0_Nc_32_ang_035 ../../article/upplots-new/up-vx-vy-w1.data1
+cp vab-rtp.br_0.0002_y_12802_40-spin_scissor_0_Nc_32_ang_035 ../../article/upplots-new/up-vx-vy-w1.data2

### 2017-07-24 mu/up/up-res-1.8-2.1-3000pts/cp-data.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+cp magsv.br_0.0002_az_12802_40-spin_scissor_0_Nc_32_incang_000-180 ../../article/upplots-new/up-vsz-w2.data1
+cp magsv.br_0.0002_az_12802_40-1.957eV ../../article/upplots-new/up-vsz-w2.data2
+
+cp vab-rtp.br_0.0002_x_12802_40-spin_scissor_0_Nc_32_ang_035 ../../article/upplots-new/up-vx-vy-w2.data1
+cp vab-rtp.br_0.0002_y_12802_40-spin_scissor_0_Nc_32_ang_035 ../../article/upplots-new/up-vx-vy-w2.data2

### 2017-07-24 mu/up/up-scripts/up-magsvab-inang.sh

@@ -35,6 +35,7 @@ if [ $1 == 1 ]; then
     calc () {
     echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputkk
     echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputsm
+    echo -e "E              V_{s^a}          Pol   V^{xa}          V^{ya}          gamma" > $outputbr
     for i in ${angles[@]}; do
         paste "${inputkk[0]}""$i"  "${inputkk[1]}""$i" | awk '{if($4 != 0) {printf("%1.6E\n", atan2($4,$2)) ;} else if($4==0) {printf("%1.6E\n"), 0,0 } }' > .temp1
         paste .temp1 | awk '{if($1 < 0) {printf("%010.6f\n", ($1*'"$deg"')+180) ;} else {printf("%010.6f\n"), $1*'"$deg"' } }' > .deg1
@@ -102,8 +103,8 @@ if [ $1 == 1 ]; then
               v.kk_yz_12802_40-spin_scissor_0_Nc_32_ang_  )
     inputsm=( v.sm_0.03_xz_12802_40-spin_scissor_0_Nc_32_ang_  
               v.sm_0.03_yz_12802_40-spin_scissor_0_Nc_32_ang_  )
-    inputbr=( v.br_0.0002_xy_12802_40-spin_scissor_0_Nc_32_ang_  
-              v.br_0.0002_yy_12802_40-spin_scissor_0_Nc_32_ang_  )
+    inputbr=( v.br_0.0002_xz_12802_40-spin_scissor_0_Nc_32_ang_  
+              v.br_0.0002_yz_12802_40-spin_scissor_0_Nc_32_ang_  )
 
     calc
 
@@ -127,9 +128,9 @@ elif [ $1 == 2 ]; then
     grep "$en" "$outputbr" > magsv.br_0.0002_ax_12802_40-"$fs"
 
     echo -e "\t You have created:"
-    echo -e "\t\t $outputkk"
-    echo -e "\t\t $outputsm"
-    echo -e "\t\t $outputbr"
+    echo -e "\t\t magsv.kk_ax_12802_40-$fs"
+    echo -e "\t\t magsv.sm_0.03_ax_12802_40-$fs"
[…]

### 2017-07-24 mu/up/up-scripts/up-vab-rtp.sh

@@ -1,13 +1,12 @@
 #/bin/bash
 
-angles=( 000 005 010 015 020 025 030 035 040 045 050 055 060 065 070 075 080 085 090 095 100 105 110 115 120 125 130 135 140 145 150 155 160 165 170 175 180 )
-
 an=035
 kp=12802
 ec=40
 sc=0
 nc=32
 sm=0.03
+br=0.0002
 
 deg=180/3.141592
 
@@ -22,13 +21,6 @@ paste .temp1 .deg1 | awk '{printf("%1.6E    %1.6E    %1.6E    %1.6E    %1.6E    
 
 ################################ |V^{x}|, rtp ##################################
 
-ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
-ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
-az=v.sm_"$sm"_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
-out=vab-rtp.sm_"$sm"_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
-
-calc
-
 ax=v.kk_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 ay=v.kk_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 az=v.kk_xz_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
@@ -36,7 +28,28 @@ out=vab-rtp.kk_x_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
 
 calc
 
+ax=v.sm_"$sm"_xx_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
+ay=v.sm_"$sm"_xy_"$kp"_"$ec"-spin_scissor_"$sc"_Nc_"$nc"_ang_"$an"
[…]

### 2017-07-24 mu/up/up-scripts/up-magsvab-inang.sh
0.0002 broadening plots completed.

@@ -2,7 +2,7 @@
 
 
 #### ENERGY TO FIND & FILE SUFIX TO USE:
-en="8.44422E-02"    ;  fs="0.084eV"
+en="8.45423E-02"    ;  fs="0.084eV"
 # en="1.95415E+00"    ;  fs="1.954eV"
 # en="1.95765E+00"    ;  fs="1.957eV"
 

### 2017-07-28 mu/article/article.tex
Starting review 5
New files with 0.0002 of broadening.
Including abstract and almost final modifications.

@@
 \title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
-\author{Reinaldo Zapata-Pe\~na\textsuperscript{1},
-        Bernardo S. Mendoza\textsuperscript{1},
-        Anatoli I. Shkrebtii\textsuperscript{2}}
-\affiliation{\textsuperscript{1}Centro de Investigaciones en \'Optica, Le\'on,
+\author{Reinaldo Zapata-Pe\~na and
+        Bernardo S. Mendoza}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
 Guanajuato 37150, M\'exico}
-\affiliation{\textsuperscript{2}University of Ontario, Institute of Technology,
+\author{Anatoli I. Shkrebtii}
+\affiliation{University of Ontario, Institute of Technology,
 Oshawa, ON, L1H 7L7, Canada}
@@
 \begin{abstract}
-perro
-%\blindtext
+We present a theoretical study of spin-velocity injection with linearly
+polarized light of two 50\% hydrogenated noncentrosymmetric graphene structures:
+Alt and Up. We analyzed the cases when the spin is polarized perpendicularly to
+the surface of the structures, in the $z$ direction, and wen the spin moves
+along the fixed $x$ and $y$ directions. The results are calculated in a full
+electronic band structure scheme within DFT in the LDA approximations showing an
+anisotropic behavior. We obtained maximum absolute values of
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s for the Up
+structure and $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for the
+Alt structure being both structures excellent candidates for spintronics
+applications.
 \end{abstract}
@@
 \label{sec:introduction}
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=\linewidth]{figures/upstruc2}
-    \\
-    \includegraphics[width=\linewidth]{figures/upstruc1}
-    \caption{Up structure}
-    \label{fig:up-struc}
-\end{figure}
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=\linewidth]{figures/altstruc2}
-    \\
-    \includegraphics[width=\linewidth]{figures/altstruc1}
-    \caption{Alt structure.}
-    \label{fig:alt-struc}
-\end{figure}
 
@@
 motion of charge; spin-up electrons move in a given direction while spin-down
-electrons travel in the opposite one. This phenomena can result from spin
+electrons travel in the opposite one. 
+This effect can result from one photon absorption of linearly polarized light
+by a semiconductor, with filled valence bands and empty conduction bands,
+illuminated by light with photon energy larger than the energy gap.
+For instance,
+this phenomena can result from spin
 injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04} interference of two
@@
 In this paper we present two 50\% hydrogenated graphene noncentrosymmetric
-structures both presenting a discernible band gap: the \emph{Up} structure,
+structures both presenting a discernible band gap: the Up structure,
 shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
-only in the upper side of the structure while the \emph{Alt} structure, shown
+only in the upper side of the structure while the Alt structure, shown
 in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
@@
 
-Using those structures we address a theoretical study of the spin velocity
-injection (SVI) by one-photon absorption of linearly polarized light.
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=\linewidth]{figures/upstruc2}
+    \\
+    \includegraphics[width=\linewidth]{figures/upstruc1}
+    \caption{Side (top panel) and top (bottom panel) views of the Up
+      structure along with the 
+      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
+      labeled 1 (2).
+}
+    \label{fig:up-struc}
+\end{figure}
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=\linewidth]{figures/altstruc2}
+    \\
+    \includegraphics[width=\linewidth]{figures/altstruc1}
+    \caption{Side (top panel) and top (bottom panel) views of the Alt
+      structure along with the 
+      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
+      labeled 1 (2).
+}
+    \label{fig:alt-struc}
+\end{figure}
+
+Using those structures we address a theoretical study of the 
+spin velocity
+injection (SVI) 
+by one-photon absorption of linearly polarized light.
 % 
@@
 along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
-polarized light can promote a distribution of electrons in $\mathbf{k}$ space
-regardless the symmetry of the material resulting in a null electrical current.
+polarized light can promote an even distribution of electrons in $\mathbf{k}$ space
+regardless the symmetry of the material resulting in a 
+null electrical current.\cite{bhatPRL05}
 Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
@@
 noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
-could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} 
-% 
-{
-% \color{red}
-% 
+not necessarily 
+ vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} 
 and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
-opposite, a pure spin current will be produced. Since the structures presented
+opposite, a PSC will be produced. Since the structures presented
 here are noncentrosymmetric, they are good candidates in which this effect can
-be induced.}
+be induced.
 
@@
 describe the details of calculations and the corresponding SVI spectra for the
-\emph{Up} and \emph{Alt} structures. Finally, we present our conclusions in
+Up and Alt structures. Finally, we present our conclusions in
 Section \ref{sec:conclusions}.
@@
 
-In this section, we report a summary of the theory that involves the PSC
-phenomena from which rises the SVI treated in this paper.
-
-{\color{red}
-In PSCs there is no net motion of electrical charge and spin-up electrons move
-in a given direction while spin-down electrons travel in the opposite one.
-This effect can result from one photon absorption of linearly polarized light
-by a semiconductor, with filled valence bands and empty conduction bands,
-illuminated by light with photon energy larger than the energy gap.
-% note 1
-Using a single continuous linearly polarized laser beam, it is possible
-to promote electrons in $\mathbf{k}$ space regardless the symmetry of the
-system resulting in a net current equal to zero. 
-% 
-If the phenomena is produced in a noncentrosymmetric semiconducting media, the
-electrons promoted to the conduction bands at opposite $\mathbf{k}$ points
-can produce a net spin polarization different to zero\cite{alvaradoPRL85},
-resulting in a PSC because the velocity of electrons
-at opposite $\mathbf{k}$ points are in opposite directions.
-}
+In this section, we report a summary of the theory  involved in the
+calculation of the spin velocity
+injection (SVI) resulting from the
+pure spin current (PSC).
 
 %%%BMSD
-The operator that describes the electronic PSC is written as
+The operator that describes the electronic SVI is written as
 \begin{align}\label{z.1}
@@
 \end{equation} 
-is the pseudotensor that describes the rate of change of the  PSC process in semiconductors.
-To derive above we used  
+is the pseudotensor that describes the rate of change of the  PSC process in
+semiconductors. To derive above we used
 $
@@
 $
-that follows from time-reversal invariance. 
-The prime $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
-sum only covers these states.  Since $\mu^{\mathrm{abcd}}(\omega)$ is real we
-have that $\mu^{\mathrm{abcd}}(\omega) =
+that follows from time-reversal invariance. The prime $'$ in the sum means that
+$c$ and $c'$ are quasi degenerate states and the sum only covers these states.
+Since $\mu^{\mathrm{abcd}}(\omega)$ is real we have that
+$\mu^{\mathrm{abcd}}(\omega) =
 \mu^{\mathrm{abdc}}(\omega)$. 
@@
 \end{equation}  
-that gives 
-the velocity, along the direction $\mathrm{a}$, at which the spin moves polarized along the 
-direction $\mathrm{b}$.
-The carrier injection rate $\dot n(\go)$ is written as,\cite{nastosPRB05}
+that gives the velocity, along the direction $\mathrm{a}$, at which the spin
+moves polarized along the direction $\mathrm{b}$. The carrier injection rate
+$\dot n(\go)$ is written as,\cite{nastosPRB05}
 \begin{equation}
@@
 $\xi^{\mathrm{xx}}(\go)=\xi^{\mathrm{yy}}(\go)\equiv\xi(\go)$, and $\xi^{\mathrm{xy}}(\go)=0$.
-Now, we formalize our two options for $\calv^{\rma\rmb}$.
-%
-
-% Two interesting possibilities to analyze the SVI are fixing the spin along $z$,
-% directed perpendicularly to the surface of the structure, or fixing the
-% velocity along $x$ or $y$ on the $xy$ plane of the structures. Also we can
-% analyze the SVI contribution coming from each layer of the structure. In
-% following subsections we present these three cases.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Now, we formalize our two options for $\calv^{\rma\rmb}(\go)$.
 
@@
 Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of
-the electron's in plane
-velocity with it's spin polarized along the $\mathrm{b}$ direction as
+the electron velocity in plane
+with the spin polarized along the $\mathrm{b}$ direction as
 \begin{equation}
@@
 \begin{equation}
-\gamma_{\gs\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
+\gamma_{\gs^\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
 \label{eq:gamma-perp}
@@
 \hline
-\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
+\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
 \cline{3-5}
@@
 
-\caption{Unit cell of \emph{Up} structure. Layer division, atom types and
-positions for the \emph{Up} structure. The structure unit cell was divided in
+\caption{Unit cell of Up structure. Layer division, atom types and
+positions for the Up structure. The structure unit cell was divided in
 two layers corresponding to hydrogen and carbon atoms.The corresponding layer
@@
 
-\caption{Unit cell of \emph{Alt} structure. Layer division, atom types and
-positions for the \emph{Alt} structure. The structure unit cell was divided in
+\caption{Unit cell of Alt structure. Layer division, atom types and
+positions for the Alt structure. The structure unit cell was divided in
 six layers corresponding each one to atoms in different $z$ positions. The
@@
 
-We preset the results for 
-and
-$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ 
-and
-$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ 
-for the
-C$_{16}$H$_{8}$-up  and C$_{16}$H$_{8}$-alt 
-structures being both
-noncentrosymmetric semi-infinite 2D carbon systems with 50\% hydrogenation in
-different arrangements. We recall that the \emph{Up} structure has hydrogen
-atoms only on the upper side of the carbon sheet while the \emph{Alt} structure
-has alternating hydrogen atoms on the upper and bottom sides. Also we take the
-hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
-carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
-\ref{fig:up-struc} and \ref{fig:alt-struc}. The coordinates for the
-\emph{Up} and \emph{Alt} unit cells of the structures are presented in Tables
-\ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
-
-We calculated the self-consistent ground state and the Kohn-Sham
-states using density functional theory in the local density approximation 
-(DFT-LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
+We preset the results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
+$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-up  and
+C$_{16}$H$_{8}$-alt structures being both noncentrosymmetric semi-infinite 2D
+carbon systems with 50\% hydrogenation in different arrangements. We recall
+that the Up structure has hydrogen atoms only on the upper side of the carbon
+sheet while the Alt structure has alternating hydrogen atoms on the upper and
+bottom sides. Also we take the hexagonal carbon lattice to be on the $xy$ plane
+for both structures, and the carbon-hydrogen bonds on the perpendicular $xz$
+plane, as depicted in Figs. \ref{fig:up-struc} and \ref{fig:alt-struc}. The
+coordinates for the Up and Alt unit cells of the structures are presented in
+Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
+
+We calculated the self-consistent ground state and the Kohn-Sham states using
+density functional theory in the local density approximation (DFT-LDA) with a
+planewave basis using the ABINIT code \cite{gonzeCPC09}.
 % 
@@
 The convergence parameters for the calculations of our results corresponding to
-the \emph{Up} and \emph{Alt} structures are cutoff energies of 40\,Ha and
-65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
-respectively. The energy eigenvalues and matrix elements for the \emph{Up} and
-\emph{Alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
-$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ and
-$\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron method
-(LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
-$\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the crystal potential, in
-$\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give small contribution
-to PSC.\cite{bhatPRL05} Therefore, $[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1}
-reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$.
-
+the Up and Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting
+in LDA energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
+eigenvalues and matrix elements for the Up and Alt structures were calculated
+using 12802 $\mathbf{k}$ points and 14452 $\mathbf{k}$ points in the IBZ to
+integrate $\mu^{\mathrm{abcd}}(\go)$ and $\xi^{\rma\rmb}(\go)$ using the
+linearized analytic tetrahedron method (LATM).\cite{nastosPRB07} We neglect the
+anomalous velocity term $\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the
+crystal potential, in $\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to
+give small contribution to PSC.\cite{bhatPRL05} Therefore,
+$[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat
+v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$. Finally, the prime in the sum of
+Eq.~\eqref{eq:mu} is restricted to quasidegenerated conduction bands $c$ and
+$c'$ that are closer than 30 meV, where this value is both a typical laser-
+pulse energy width and the room-temperature energy.\cite{nastosPRB07}
 % 
@@
 
-\begin{table}[b]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\centering
+\includegraphics[width=\linewidth]{plots/2-vab-str-comp}
+\caption{$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ 
+  vs. $\hbar\go$, for the values of $\ga$ that maximize the signal. The low
+  energy regions for the Alt and Up structures start at the energy gap of each
+  structure, while in the high energy regions, the values of
+  $\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ are also very large. The bottom panel
+  corresponds to CdSe and GaAs. }
+\label{fig:vab-str-comp}
+\end{figure}
+
+In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
+(\omega,\alpha)$ vs. $\hbar\go$, for the directions $\rma\rmb$ and angle $\ga$
+that maximizes the signal, for the Up  and Alt structures and for CdSe and
+GaAs, which are bulk systems shown for comparison.
+% 
+As expected from de delta function of Eq.~\eqref{eq:mu},
+$\calv^{\rma\rmb}(\go,\ga)$ rises right at the corresponding energy gap of each
+system. For the 2D structures, the spectrum covers two narrow energy regions
+with large values of the response, while for bulk systems the spectra covers a
+rather wide energy range, but with a much smaller response.
+% 
+For the Up structure $\rma\rmb=yz$ and $\ga=35^\circ$ maximizes the response,
+which means that an incoming beam of light with its electric field polarized at
+35$^\circ$ from the $x$ direction will induce electrons to move along $y$
+(parallel to the surface) with their spin polarized along $z$ (perpendicular to
+the surface), with the following speeds.
+% 
+Right at the energy onset $\calv^{yz}(\go,\ga)=668$\,Km/s, speed that remains
+almost constant for 65 meV, and then goes to zero. A second region is found
+above 1.946 eV, where there are two extreme values of the speed,
+$\calv^{yz}(\go,\ga)=266.3$ Km/s at $\hbar\go=1.954$\,eV, and
+$\calv^{\rma\rmb}(\go,\ga)=-241.4$ Km/s at $\hbar\go=1.958$\,eV; a positive
+(negative) $\calv^{\rma\rmb}(\go,\ga)$ means that the electrons move parallel
+(antiparallel) to the electric field.
+
+Likewise for the Alt structure we find that also $\rma\rmb=yz$ and
+$\ga=150^\circ$ maximizes the response, where two extreme values of
+$\calv^{\rmy\rmz}$ are found, one at {\color{red} $\hbar\go=0.7204$\,eV} of
+$\calv^{\rmy\rmz}=-711.9$ Km/s, and the other at $\hbar\go=0.911$\,eV of
+$\calv^{\rmy\rmz}=-330.6$ Km/s.
+% 
+For the bulk structures we calculate $\calv^{\rma\rmb}(\go)$ from
+Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe we find
+that for $\hbar\go=0.844$\,eV, $\bfgmu_{\mathrm{max}}\to \mu^{zzzz}$, and
+$\calv^{\rmz\rmz}(\go)=-59.0$ Km/s, and for GaAs at $\hbar\go=2.324$\,eV,
+$\bfgmu_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and $\calv^{\rma\rma}(\go,\ga)=-28.7$\,Km/s, with
+$\rma=x,y,z$. For these bulk semiconductors the $x$, $y$, and $z$ axis are
+taken along the standard cubic unit cell directions, [100], [010], and [001],
+respectively. In Table \ref{tab:vab-str-comp} we present the comparison of
+$\calv^{\rma\rmb}(\go,\ga)$ for the 2D structures and bulk crystals.
+% 
+We remark that, as shown in the figure, 
+the 2D structures have maxima in 
+$\calv^{\rma\rmb}(\go;\ga)$  
+that are bigger
+than for the bulk crystals; in particular the Alt
+structure gives a $\calv^{\rma\rmb}(\go;\ga)$ $\sim$12 times larger than
+that of CdSe and GaAs.
+\begin{table}%[b]
 \begin{tabular}{cccccc}
@@
 \hline
-\emph{Up}    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  684.2    \\
-             &      &       & 1.954  & $\mathrm{yz}$ &  293.9    \\
-             &      &       & 1.958  & $\mathrm{yz}$ & -273.0    \\
-\emph{Alt}   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -722.2    \\
-             &      &       & 0.911  & $\mathrm{yz}$ & -351.7    \\
- CdSe        & bulk & 90    & 0.912  & $\mathrm{zz}$ &  -32.3    \\
- GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -28.9    \\
+Up    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
+      &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
+      &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
+Alt   & 2D   & 150   & {\color{red}0.720}  & $\mathrm{yz}$ & -711.9 \\
+      &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
+CdSe  & bulk & --    & 0.844  & $\mathrm{zz}$ &  -59.0 \\
+GaAs  & bulk & --    & 2.324  & $\mathrm{xx}$ &  -28.7 \\
 \hline
 \end{tabular}
-
-\caption{Comparison of the reported maxima values of
-$\mathcal{V}^{\mathrm{ab}}$ for the different structures and their
-corresponding polarization angle $\alpha$ and energy values of the incoming
-beam at which the maxima is obtained.}
+\caption{Comparison of the reported maximum values of
+$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ for the different structures and their
+corresponding polarization angle $\alpha$ and $\hbar\go$ energy values.
+}
 \label{tab:vab-str-comp}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{plots/vab-str-comp}
-
-    \caption{Comparison of most intense responses of
-    $\mathcal{V}^{\mathrm{ab}}$ for 2D \emph{Alt} and \emph{Up}, and bulk CdSe
-    and GaAs structures and their corresponding polarization angle $\alpha$.}
-    \label{fig:vab-str-comp}
-\end{figure}
-
-Using  Eq. \eqref{eq:vab-aw}, we calculated
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and \emph{Alt} 2D
-structures and for CdSe and GaAs which are bulk systems; the results are
-presented in Fig. \ref{fig:vab-str-comp}. The polarization angle of the
-incoming beam, $\alpha$, presented in the response of each structure is that
-for which the response is maximized in each case.
-% 
-The most intense response corresponds to the \emph{Alt} structure centered at
-0.720\,eV corresponding to the short-wavelength infrared radiation (SWIR) and
-reaching a $\calv^{\rmy\rmz}=-722.2$ Km/s, which means the electrons moving
-along $y$ (parallel to the surface) with the spin polarized along $z$
-(perpendicular to the surface), with a speed of -722.2 Km/s.
-% 
-For an energy range from 0.66\,eV to 3.0\,eV, corresponding to energies of the
-Near Infrared (NIR) to visible radiation (VIS), the \emph{Up} structure has two
-peaks centered at 1.954\,eV and 1.958\,eV reaching $\calv^{\rmy\rmz}=293.9$
-Km/s and $\calv^{\rmy\rmz}=-273.0$ Km/s and the \emph{Alt} structure one more
-peak centered at 0.911\,eV reaching $\calv^{\rmy\rmz}=-351.7$ Km/s.
-% 
-Then, for the bulk structures we have that the CdSe has only one intense
-response centered at 0.912\,eV reaching $\calv^{\rmz\rmz}=-32.3$ Km/s, and the
-GaAs structure response reaches the maximum centered at 2.326\,eV reaching
-$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-28.9$ Km/s.
-% 
-In table \ref{tab:vab-str-comp} we present the comparison of these values for
-the 2D and bulk structures; a positive (negative) spin-velocity means that the
-velocity moves (anti-)parallel to the electric field.
-% 
-We remark that the 2D structures have resonances that give larger values for
-$\calv^{\rma\rmb}$ than the bulk crystals; in particular the \emph{Alt}
-structure is $\sim 22$ times more intense.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing spin %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Fixing spin} % (fold)
 \label{sec:res-fixspin}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \includegraphics[width=\linewidth]{upplots/up-vsz-w1}
-    \caption{Caption here}
+\caption{For the Up structure, the top panel shows 
+$\calv_{\gs^\rmz}(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel
+shows $\gamma_{\gs^\rmz}(\go,\ga)$ (right scale, red line), and
+$\calv_{\gs^\rmz}(\go,\ga)$ (left scale, black line), vs. $\ga$, for
+$\hbar\go=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
 \label{fig:up-vsz-w1}
@@
 \includegraphics[width=\linewidth]{upplots/up-vsz-w2}
-    \caption{caption here}
+\caption{For the Up structure, the top panel shows $\calv_{\gs^\rmz} (\go,\ga)$
+vs. $\hbar\go$ and $\ga$, and the bottom panel shows $\gamma_{\gs^\rmz}
+(\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz} (\go,\ga)$ (left
+scale, black line), vs. $\ga$, for $\hbar\go=1.954$\,eV, i.e. along the
+highest ridge shown in the 3D plot. }
 \label{fig:up-vsz-w2}
@@
 
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
-% %% Description of UP |V_{s^z}| 3D
-% %%%%%%%%%%%%%%%%%
-
-Using Eq. \eqref{eq:vs-mag}, we calculated $\mathcal{V}_{\sigma^{\mathrm{b}}}
-(\omega,\alpha)$ and made the analysis for the case when the spin is fixed
-along $z$, i.e. directed perpendicularly to the surface of the \emph{Up} and
-\emph{Alt} structures. Also, using Eq. \eqref{eq:gamma-ang}, we determined the
-angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ where the spin-velocity is directed
-along the surface of the each structure.
-%
-
-\subsubsection{\emph{Up} structure}\label{up:fs}
-
-We present in Figs. \ref{fig:up-vsz-w1} and \ref{fig:up-vsz-w2}
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ for the two energy ranges
-of the \emph{Up} structure that give the highest values for $\calv^{\rmy\rmz}$
-shown in Fig.~\ref{fig:vab-str-comp}.
-% 
-We obtain that the zone where the maximum response is reached corresponds to a
-energy range of the incident beam from 0.084\,eV to 0.093\,eV, corresponding to
-the LWIR, and polarization angles $\alpha$ between $35^{\circ}$ and
-$55^{\circ}$. Also,  two local maxima are held for same $\ga$ between
-$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.952\,eV and
-1.960\,eV, in the VIS range.
-% %%%%%%%%%%%%%%%%% 
-% %% 0.0 eV - 0.16 eV
-% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
-% %%%%%%%%%%%%%%%%%
-
-In bottom panel of Fig. \ref{fig:up-vsz-w1} we first analyze the response for
-$\hbar\go= 0.084$ eV which gives the maximum. We show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\ga$
-(left scale, black line). The absolute maximum is obtained when $\alpha =
-35^{\circ}$ resulting in a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 758.2$\,Km/s, that according to Eq.~\eqref{eq:vs-mag} comes
-from $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 326.7$\,Km/s and
-$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha) = 684.2$\,Km/s.
-% 
-In the same panel we present the corresponding velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red line), that for the
-absolute maximum at $\ga = 35^\circ$ is $\gamma_{\mathrm{z}}(\hbar\omega =
-0.084\text{eV},\alpha = 35^\circ) = 64.47^{\circ}$. This results means that at
-$\hbar\go=0.084$ eV and a polarization angle of the incoming electric field of
-$\ga = 35^\circ$ the electrons with a spin pointing along $z$ move at angle of
-$\gamma_{\mathrm{z}}(\hbar\omega = 0.084\text{eV},\alpha=35^\circ) \sim
-64.5^{\circ}$ with respect to the $x$ direction, with a  maximum speed
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  758.2 Km/s. Also, from
-Eq. \eqref{eq:gamma-par} we find that
-$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.47^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 646.0$ Km/s (see green
+In this subsection we calculate $\calv_{\gs^\rmz}(\omega,\alpha)$, Eq.
+\eqref{eq:vs-mag}, for the case where the spin is fixed along $z$, i.e.
+directed perpendicularly to the surface of the Up and Alt structures. Also, we
+calculate $\gamma_{\gs^\rmz}(\go,\ga)$, Eq. \eqref{eq:gamma-ang}, that
+determines the direction along which the injected electrons move along the
+surface of  each structure. We mention that we have also made the analysis for
+the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$,
+finding similar qualitative results to those presented bellow.
+%
+
+\subsubsection{Up structure}\label{up:fs}
+
+In the top panel of Fig. \ref{fig:up-vsz-w1} we plot
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+0.080\,eV$\leq\hbar\go\leq$0.096\,eV {\color{red}(same energy range for the Up
+structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} )} and
+$0^\circ\leq\ga\leq 180^\circ$.
+% 
+We see a broad peak that maximizes at $\ga=35^{\circ}$ and $\hbar\go=
+0.084$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
+739.7$\,Km/s, and that the variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ as a function of $\ga$, that comes from the interplay of the
+$\bfgmu$ tensor components as multiplied by the  trigonometric functions of
+Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and
+165.4\,Km/s, for 0.084\,eV$\leq\hbar\go\leq$0.090\,eV. 
+% 
+In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.084$\,eV,
+{\color{red}thus following the ridge shown in the 3D plot of the top panel,
+along with its corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
+(right scale, red line)}.
+% 
+It is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
+at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
+for the whole range of $\ga$. This results means that for $\hbar\go=0.084$ eV
+and for all values of $\ga$, the electrons, with the chosen spin pointing along
+$z$, will move at angle of {\color{red}$\gamma_{\gs^\rmz}(\omega,\alpha) \sim
+64.5^{\circ}$} with respect to the $x$ direction, with the range of  high
+speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
+% 
+Also, from Eq. \eqref{eq:gamma-par} we find that
+$\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha)=\ga = 64.56^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
 arrow), and that from Eq. \eqref{eq:gamma-perp},
-$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.47^\circ$, gives
-$\ga=154.47^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-195.6$ Km/s (see blue arrow); thus, for $\hbar\go=0.084$ eV, an $\alpha \sim
-65.5^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
-along $z$ moving parallel (perpendicular) to the incident electric field,  with
-a speed of 646.0 (195.6) Km/s.
-% 
-We also find that for all values of $\ga$, $\gamma_{\mathrm{z}}(\omega,\alpha)
-\sim 64.48^{\circ}$, being almost constant, and 180.0 Km/s
-$<\calv_{\gs^z}(\go,\ga)<$ 758.2 Km/s.
-
-In the bottom panel of Fig. \ref{fig:up-vsz-w2}, now we take
-$\hbar\go=1.954$ eV which gives the local maximum 
-shown in the to panel of same figure. 
-The local maximum is
-again at  $\alpha = 35^{\circ}$ with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
-300.4$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
-78.0^{\circ}$.
-% 
-In this case, $\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
-78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 187.6$
-Km/s (green circled box and arrow), and
-$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.0^{\circ}$, for $\alpha =168.0^
-{\circ}$ (blue squared box and arrow) with $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 92.4$.
-% 
-We find  that the velocity angle is almost constant having a range from
-$77^{\circ}$ to $78.04^{\circ}$ for  $0^{\circ} \leq
-\alpha \leq 180^{\circ}$, and 6.8 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 300.4 Km/s.
-% 
-Although no figures are presented, we also made the analysis for the
-cases when the spin polarization is directed 
-along $\mathrm{x}$ and $\mathrm{y}$, finding 
-the maxima for
-$\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
-$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
-$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
-$\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
-$\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.50^\circ$,
+gives $\ga=154.50^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
+arrow); thus, at $\hbar\go=0.084$ eV, an incident field polarized at $\alpha
+\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
+polarized along $z$, that move parallel or perpendicular to the incident
+electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.
+
+Now, we analyze the results for the second energy range of the Up structure
+shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
+of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\go\leq$1.960\,eV and
+$0^\circ\leq\ga\leq 180^\circ$.
+% 
+We see two broad peaks that maximize at $\ga=35^{\circ}$ and $\hbar\go=
+1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
+193.5$\,Km/s, and $\ga=35^{\circ}$ and $\hbar\go= 1.957$\,eV, with a value
+of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) = 170.6$\,Km/s. 
+% 
+We only analyze the highest  maximum in the bottom panel, where we  show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\ga$ (left scale,
+black line), at $\hbar\go= 1.954$\,eV, thus following the highest ridge shown
+in the 3D plot of the top panel, {\color{red}along with its corresponding
+velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red line)}. In
+this case we see that the values of $\gamma_{\gs^z}(\omega,\alpha)$ have more
+dispersion, as a function of $\ga$, than for the lower energy range shown in
+the bottom panel of Fig.~\ref{fig:up-vsz-w1}.
+% 
+However, $\gamma_{\gs^z}(\omega,\alpha)\sim 77.8^\circ$ is constant from
+$\ga=0^\circ$ and up to $\ga\sim 85^\circ$. In this case, we find that
+$\gamma^\parallel_{\gs^\mathrm{z}}(\omega,\alpha)=\ga=78.0^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (see green
+arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=167.8^\circ$, gives
+$\ga=77.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
+65.6$\,Km/s (see blue arrow). 
+% 
+Thus, by the correct choice of $\hbar\go$ and $\alpha$ we could inject
+electrons, in this case with their spin polarized along $z$, that move parallel
+or perpendicular to the incident electric field, with finite speeds.
+
+% the maxima for
+% $\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
+% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
+% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
+% $\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
+% $\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.
 
@@
 \includegraphics[width=\linewidth]{altplots/alt-vsz}
-    \caption{Caption here}
+\caption{For the Alt structure, the top panel shows $\calv_{\gs^\rmz}
+(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel shows
+$\gamma_{\gs^\rmz} (\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz}
+(\go,\ga)$ (left scale, black line), vs. $\ga$, for $\hbar\go=0.720$\,eV, i.e.
+along the ridge shown in the 3D plot.}
 \label{fig:alt-vsz}
@@
 
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
-% %% Description of ALT |V_{s^z}| 3D
-% %%%%%%%%%%%%%%%%%
-
-\subsubsection{\emph{Alt} structure}
-
-We proceed to analyze the $\emph{Alt}$ structure, just as we did the \emph{Up}
-structure. Fig. \ref{fig:alt-vsz} shows $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ (Eq. \eqref{eq:vs-mag}), where we see that the maximum
-response is reached for $\hbar\go=0.720$ eV and a local maximum is obtained at
-$\hbar\go=0.912$ eV, both located in the short-wavelength infrared radiation
-(SWIR) range and for polarization angles, $\ga$,  between $135^{\circ}$ and
-$160^{\circ}$.
-
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
-% %%%%%%%%%%%%%%%%%
-In bottom panel of Fig. \ref{fig:alt-vsz} we plot $\calv_{\gs^z}(\go,\ga)$ vs.
-$\ga$ (left scale, black line), fixing the energy to 0.720 eV. The absolute
-maximum is obtained for $\alpha = 150^{\circ}$ with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.6$ Km/s.
-% 
-In the same panel we present the velocity angle
-$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red line), that for
-the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 108.9^{\circ}$.
-% 
-Also, the green circle indicates the value of $\ga$ for which the electrons
-move parallel to the incoming electric field, i.e. $\alpha =
-\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 108.7^{\circ}$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 538.5$ Km/s. Likewise, the
-blue circle indicates the value of $\ga$ for which the electrons move
-perpendicular to the incoming electric field, i.e. $\alpha=19.8^{\circ}$, with
-$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=109.8^{\circ}$, and
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=61.5$ Km/s.
-% 
-We also have that $\gamma_{\mathrm{z}}(\omega,\alpha)$ is centered at
-$109.1^{\circ}$ having variations of $\pm 0.9^{\circ}$ for $0^{\circ} \leq
+\subsubsection{Alt structure}
+
+We proceed to analyze the Alt structure, just as we did the Up structure, but
+in this case we only chose the lower energy range shown in the left central
+panel of Fig.~\ref{fig:vab-str-comp}. 
+% 
+In the top panel of Fig. \ref{fig:alt-vsz}, we plot
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+0.715\,eV$\leq\hbar\go\leq$0.725\,eV and $0^\circ\leq\ga\leq 180^\circ$. We
+see a broad peak that maximize at $\ga=150^{\circ}$ and $\hbar\go=
+0.720$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
+644.9$\,Km/s.
+% 
+In the bottom panel we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.720$\,eV,
+{\color{red} thus following the highest ridge shown in the 3D plot of the top
+panel, along with its corresponding velocity angle $\gamma_{\gs^\rmz}
+(\omega,\alpha)$ (right scale, red line)}. In this case we see that
+$\gamma_{\gs^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
+variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
 \alpha \leq 180^{\circ}$.
 % 
-Again, for the cases in which the spin polarization is parallel to the surface
-the maximum values are $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) =
-297.8$ Km/s and $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$
-Km/s, corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
-$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
-$\alpha=150^{\circ}$, where the plots are not presented.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Fixing velocity %%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Fixing velocity} % (fold)
+In this case, we find that $\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha) =
+\ga = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
+450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=110.0^\circ$,
+gives $\ga=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
+we could inject electrons with a fixed spin that move parallel or perpendicular
+to the incident electric field.
+
+% Again, for the cases in which the spin polarization is parallel to the
+% surface the maximum values are
+% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 297.8$ Km/s and
+% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$ Km/s,
+% corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
+% $\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
+% $\alpha=150^{\circ}$, where the plots are not presented.
+
+\subsection{Fixing velocity} 
 \label{sec:res-fixvel}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Using the Eq. \eqref{eq:vv-mag}, we calculated the $\mathcal{V}^{\mathrm{a}}
-(\omega,\alpha)$ for the cases when the velocity is fixed along the $\rma=x$ or
-$\rma=y$ direction on the surface of the \emph{Up} and \emph{Alt} structures,
-and from the Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we
-determined the polar, $\theta_{\mathrm{a}} (\omega,\alpha)$, and azimuthal,
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, angles corresponding to the direction
-of the spin.
-% 
-The plots corresponding to the velocity fixed along the axes as a function of
-the energy and polarization angle for the \emph{Up} and \emph{Alt} structures
-are similar in shape to the top panels of Figs. \ref{fig:up-vsz-w1}, 
-\ref{fig:up-vsz-w2}, and \ref{fig:alt-vsz} and they are not presented here.
-
-\subsubsection{\emph{Up} structure}
+We calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. \eqref{eq:vv-mag})
+fixing the electron velocity direction, $\rma$, to the $x$ or $y$ direction
+along the surface of the Up and Alt structures. From Eqns. \eqref{eq:polar-ang}
+and \eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
+(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
+corresponding to the direction of the spin.
+
+\subsubsection{Up structure}
 
@@
 \includegraphics[width=\linewidth]{upplots/up-vx-vy-w1}
-    \caption{caption here}
+\caption{For the Up structure we show
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$
+(left scale, black line),  
+$\theta_{\mathrm{a}} (\omega,\alpha)$
+(right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$,
+(right scale, blue line),
+vs. $\hbar\go$, for $\ga=35^\circ$, 
+and $\rma=x,y$.
+}
 \label{fig:up-vab-comp-rtp-1}
 \end{figure}
-% %%%%%%%%%%%%%%%%%
-% %% 0.0 eV - 0.16 eV
-% %% Description of UP |V^{a}| 3D
-% %%%%%%%%%%%%%%%%% 
-We proceed to analyze the \emph{Up} structure for the case when the velocity is
-directed along the $x$ and $y$ coordinates. We found that each response has a
-maximum for $\hbar\omega=0.084$ eV, in the LWIR, and $\ga=35^{\circ}$.
-% 
-Fixing $\ga=35^{\circ}$, in Fig. \ref{fig:up-vab-comp-rtp-1} we plot
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$ (left scale, black
-line) where each responses has a maximum of 442.4\,Km/s and 705.5\,Km/s,
-respectively, for $\hbar\go=0.084$ eV.
-% 
-We also present the corresponding polar (right scale, red line) and azimuthal
-(right scale, blue line) spin polarization angles that have values of
-% 
-$\theta_{\mathrm{x}}(\omega,\alpha) = 42.4^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.1^{\circ}$ 
-% 
-when the  electron moves along $x$, and  
-$\theta_{\mathrm{y}}(\omega,\alpha) = 14.1^{\circ}$, and
-$\varphi_{\mathrm{y}} (\omega,\alpha) = 81.4^{\circ}$, 
-% 
-when the electron moves along $y$. This means that, the spin is directed upward
-the third Cartesian quadrant of the $xy$ plane when the electron moves along
-$x$, and is directed almost parallel to the $xy$ plane in the first quadrant
-when it moves along $y$.
+
+For the Up structure we find once again that  $\ga=35^{\circ}$ maximizes the
+response. In Fig. \ref{fig:up-vab-comp-rtp-1} we plot $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
+(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for $\rma=x,y$. 
+% 
+We see that for $\hbar\go=0.084$\,eV, the responses has a maximum of
+$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=431.7$\,Km/s, with
+$\theta_{\mathrm{x}}(\omega,\alpha) = 42.5^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s, with
+$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and
+$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that, the
+spin is directed upward the third Cartesian quadrant of the $xy$ plane when the
+electron moves along $x$, and is directed almost parallel to the $xy$ plane in
+the first quadrant when it moves along $y$. 
 % 
@@
 direction is almost constant for all the energies across the peak of the
-response, having a ranges of
-% 
-$42.4^{\circ} < \theta_{\mathrm{x}}(\omega,\alpha) < 53.6^{\circ} $ 
-and $208.1^{\circ} < \varphi_{\mathrm{x}} (\omega,\alpha) < 215.8^{\circ}$. 
-% 
-Then, when the electron moves along $y$ the spin's polar angle has again
-small variations,
-% 
-$7.6^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) < 14.1^{\circ}$, 
-% 
-but in contrast with this the azimuthal angle has significant variations,
-% 
-$81.4^{\circ} < \varphi_{\mathrm{y}} (\omega,\alpha) < 150.7^{\circ}$.
+response, having
+$42.5^{\circ}<\theta_{\mathrm{x}}(\omega,\alpha)<53.7^{\circ}$ and
+$208.3^{\circ}<\varphi_{\mathrm{x}}(\omega,\alpha)<215.7^{\circ}$, and when
+the electron moves along $y$ the spin polar angle has again small variations,
+$11.3^{\circ}< \theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the
+azimuthal angle has significant variations, $82.1^{\circ}<
+\varphi_{\mathrm{y}}(\omega,\alpha)<182.4^{\circ}$.
 
@@
 \includegraphics[width=\linewidth]{upplots/up-vx-vy-w2}
-    \caption{Caption here}
+\caption{For the Up structure we show $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
+(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for
+$\ga=35^\circ$, and $\rma=x,y$. }
 \label{fig:up-vx-vy-w2}
 \end{figure}
-% %%%%%%%%%%%%%%%%%
-% %% 1.80 eV - 2.10 eV
-% %% Description of UP |V^{a}| 3D
-% %%%%%%%%%%%%%%%%%
-In  Fig. \ref{fig:up-vx-vy-w2}, for the \emph{Up} structure, we plot
-$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ vs. $\go$, fixing
-$\alpha=35^{\circ}$; the range of $\go$ lies in part of the VIS range. We see
-that there are two local maxima at $\hbar\go=1.954$ eV and $\hbar\go=1.958$ eV.
-For the first that is the most intense we obtain
-% 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  93.9$ Km/s and  
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 456.3$ Km/s.
-% 
-For these local maxima, the corresponding polar and azimuthal spin polarization
-angles are
-% 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 48.5^{\circ}$, and 
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 54.4^{\circ}$,
-% 
+In Fig. \ref{fig:up-vx-vy-w2} we plot $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ vs. $\hbar\go$, in the range where there are two local maxima
+at $\hbar\go=1.954$\,eV and $\hbar\go=1.957$\,eV.
+% 
+The former is the largest of the two, with
+$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
+$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and 
+$\varphi_{\mathrm{x}} (\omega,\alpha)=54.3^{\circ}$,
 for the electron moving along $x$, and
-% 
-$\theta_{\mathrm{y}} (\omega,\alpha) = 49.9^{\circ}$, and 
-$\varphi_{\mathrm{y}} (\omega,\alpha) = 51.8^{\circ}$
-% 
-for the electron moving along $y$. We remark that these angles are almost
-constant for all the energy values across the peak of this local maxima, for
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s,
+$\theta_{\mathrm{y}} (\omega,\alpha)=49.8^{\circ}$, and 
+$\varphi_{\mathrm{y}} (\omega,\alpha)=51.9^{\circ}$
+for the electron moving along $y$.
+% 
+For the $\hbar\go=1.957$\,eV peak we obtain 
+$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$, and 
+$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with 
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s, and
+$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with 
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s. 
+{\color{red}Checar que esto sea correcto para ambos maximos!!
+We remark that these angles are almost
+constant for all the energy values across the peak of this two local maxima, for
 which the spin is directed upward in the first Cartesian quadrant of the $xy$
 plane when it moves along either $x$ or $y$ directions. 
-% 
-For the $\hbar\go=1.958$\,eV peak we obtain 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 129.9^{\circ}$, and 
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.6^{\circ}$, with 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 88.8$ Km/s, and
-% 
-$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.4$, with 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 431.4$ Km/s. 
-% 
-Again, for this local maxima, the spin angles are almost constant across the
-resonant peak directed for both cases downward the third quadrant of the $xy$
-plane.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\emph{Alt} structure}
+}
+
+\subsubsection{Alt structure}
 
@@
 \includegraphics[width=\linewidth]{altplots/alt-vx-vy-w1}
-    \caption{Caption here}
+\caption{For the Alt structure we show
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\go$, for $\ga=150^\circ$, and $\rma=x,y$. }
 \label{fig:alt-vx-vy-w1}
@@
 \includegraphics[width=\linewidth]{altplots/alt-vx-vy-w2}
-    \caption{Caption here}
+\caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
+(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for
+$\ga=150^\circ$, and $\rma=x,y$. }
 \label{fig:alt-vx-vy-w2}
@@
 
-In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2} we show  for the
-\emph{Alt} structure $\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha)$ as a function of $\omega$, for
-$\ga=150^\circ$, the value that maximizes both responses as a function of
-$\ga$.
-% 
-The absolute maxima at {\color{red} $\hbar\go=0.718$} eV gives
-% 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  355.9$ Km/s, and 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 1008.6$ Km/s, 
-% 
-and the other one at {\color{red} $\hbar\go=0.911$} eV gives
-% 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 337.2$ Km/s and
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 568.8$ Km/s.
-% 
-For $\hbar\go=0.718$ eV,
-$\theta_{\mathrm{x}} (\omega,\alpha) = 61.3^{\circ}$, 
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 358.1^{\circ}$, 
-% 
-$\theta_{\mathrm{y}} (\omega,\alpha) = 118.9^{\circ}$, and 
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 161.9^{\circ}$, 
-% 
-and so the spin is directed upward the forth Cartesian quadrant of the
-$xy$ plane when the spin velocity is directed along $x$, and directed downward
-the second Cartesian quadrant when the spin velocity is directed along $y$.
-% 
-Finally, for $\hbar\go=0.912$ eV, 
-% 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, 
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.2^{\circ}$, 
-% 
-$\theta_{\mathrm{y}} (\omega,\alpha) = 129.0^{\circ}$, and 
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.1^{\circ}$, 
-% 
-implying that the spin is directed downward the forth Cartesian quadrant of the
-$xy$ plane when the spin velocity is directed along $x$, and directed downward
-the third Cartesian quadrant when the spin velocity is directed along $y$.
+In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2} we plot
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\go$ in two different ranges, and  for $\rma=x,y$. In this case,
+$\ga=150^\circ$,  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$,
+and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\ga$.
+% 
+In Fig. \ref{fig:alt-vx-vy-w1} the absolute maxima is at
+{\color{red} $\hbar\go=0.7204$\,eV,} with $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha) = 301.7$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) =
+44.5^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$,
+and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s, with
+$\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. 
+% 
+Thus, the spin is directed upward the forth Cartesian quadrant of the $xy$
+plane when the spin velocity is directed along $x$, and directed downward the
+second Cartesian quadrant when the spin velocity is directed along $y$.
+% 
+Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maxima is at
+$\hbar\go=0.911$\,eV, with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) =
+276.3$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.3^{\circ}$, and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s, with
+$\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin
+is directed downward the forth Cartesian quadrant of the $xy$ plane when the
+spin velocity is directed along $x$, and directed downward the third Cartesian
+quadrant when the spin velocity is directed along $y$.
 
@@
 We have performed an \emph{ab initio} calculation for the SVI by one-photon
-absorption of linearly polarized light in the \emph{Up} and \emph{Alt} 2D
+absorption of linearly polarized light in the Up and Alt 2D
 hydrogenated graphene structures that and we made the calculation for the case
@@
 This SVI is very sensitive to the symmetry characteristics of the structures
-presenting an anisotropic behavior. We found that the \emph{Up} structure has
+presenting an anisotropic behavior. We found that the Up structure has
 the most intense response for the spin directed along $z$ resulting in 
 % 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 758.2$\,Km/s and 
-% 
-for an energy of the incoming beam of 0.084\,eV. Also the \emph{Alt} structure
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s and 
+% 
+for an energy of the incoming beam of 0.084\,eV. Also the Alt structure
 has the most intense response when the spin moves along the $y$ direction
@@
 % 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 1008.6$\,Km/s
-% 
-for an energy of the incoming beam of 0.718\,eV.
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
+% 
+for an energy of the incoming beam of 0.720\,eV.
 % 

### 2017-07-31 mu/article/article.tex
Including last BMS changes.

@@
-\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
+%\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
+\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
 \usepackage{amsmath}    % need for subequations 
@@
                         % documents and URLs 
-%\usepackage{blindtext}  % fill text 
 \usepackage[dvipsnames]{xcolor}
 \usepackage{multirow}
-%\usepackage[capitalize]{cleveref}
-% \usepackage{showframe}
-\usepackage[inline]{showlabels}
-\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
- % \input{/Users/bms/util/definitions}
-
+%\usepackage[inline]{showlabels}
+\input{/Users/bms/util/definitions}
+\def\tama{10cm}
 \raggedbottom           % don't add extra vertical space
@@
 \title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
-\author{Reinaldo Zapata-Pe\~na and
-        Bernardo S. Mendoza}
+\author{Reinaldo Zapata-Pe\~na}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
+Guanajuato 37150, M\'exico}
+\author{Bernardo S. Mendoza}
 \affiliation{Centro de Investigaciones en \'Optica, Le\'on,
@@
 \begin{abstract}
-We present a theoretical study of spin-velocity injection with linearly
-polarized light of two 50\% hydrogenated noncentrosymmetric graphene structures:
-Alt and Up. We analyzed the cases when the spin is polarized perpendicularly to
-the surface of the structures, in the $z$ direction, and wen the spin moves
-along the fixed $x$ and $y$ directions. The results are calculated in a full
-electronic band structure scheme within DFT in the LDA approximations showing an
-anisotropic behavior. We obtained maximum absolute values of
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s for the Up
-structure and $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for the
-Alt structure being both structures excellent candidates for spintronics
+We present a theoretical study of spin-velocity injection of a pure
+spin current induced by  a linearly
+polarized beam of light that impinges normally at the surface of  two 50\%
+hydrogenated noncentrosymmetric 2D graphene 
+structures, labeled Up and Alt.
+The hydrogenation opens an energy gap in both structures.
+We analyze two possibilities, one in which by fixing the spin along a
+chosen direction, the resulting spin-velocity is calculated, 
+and the other one, where we chose the spin-velocity direction
+on the surface plane, and calculate its speed and
+spin orientation. We do so by changing the energy $\hbar\go$ 
+and polarization angle $\ga$  of the incoming  beam. 
+The results are calculated in a full
+electronic band structure scheme within the DFT in the LDA approximation.
+The maxima of the spin-velocity speed is obtained when
+$\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up,
+and
+$\hbar\go=0.720$\,eV and $\ga=150^\circ$ for Alt.
+We find a speed of
+668\,Km/s
+and 
+645\,Km/s
+for Up and Alt, respectively, when the spin points perpendicular to
+the surface. Also,
+the response is maximized
+by fixing the spin-velocity direction along a high symmetry Cartesian axis,
+obtaining a speed of 
+688\,Km/s 
+and the spin  pointing at 13$^\circ$ form the surface normal, for Up,
+and
+906\,Km/s 
+and the spin pointing at 60$^\circ$ from the surface normal, for Alt.
+These speed values are larger than those of bulk semiconductors, like
+CdSe and GaAs, thus 
+making the hydrogenated graphene structures
+ excellent candidates for spintronics
 applications.
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/upstruc2}
+    \includegraphics[width=\tama]{figures/upstruc2}
     \\
-    \includegraphics[width=\linewidth]{figures/upstruc1}
+    \includegraphics[width=\tama]{figures/upstruc1}
     \caption{Side (top panel) and top (bottom panel) views of the Up
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/altstruc2}
+    \includegraphics[width=\tama]{figures/altstruc2}
     \\
-    \includegraphics[width=\linewidth]{figures/altstruc1}
+    \includegraphics[width=\tama]{figures/altstruc1}
     \caption{Side (top panel) and top (bottom panel) views of the Alt
@@
 by one-photon absorption of linearly polarized light.
-% 
-% We calculated the responses for the particular cases when the spin of
-% electrons is directed along the the $z$ Cartesian coordinate, perpendicular
-% to the $xy$ plane of the structure, or for the case when the velocity is
-% directed along the $x$ and $y$ Cartesian direction on the $xy$ plane of the
-% structures.
-{
-% \color{red}
-% 
 Because we have 2D structures we made the analysis for tow cases. The first is
@@
 is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
-in $xyz$.}
+in $xyz$.
 % 
@@
 \sum_{v}r^{\mathrm{a}}_{cv}(\bfk) r^{\mathrm{b}}_{vc'}(\bfk)
-\nonumber\\
-&\times 
 \left( \frac{1}{\omega - \omega_{c'v}(\bfk) - i \epsilon} 
@@
 calculation.  The spin-splitting of the valence ($v$) bands is very
-small, and is neglected throughout this work.\cite{??}
+small, and is neglected throughout this work.\cite{nastosPRB07}
 % 􏱈 are close to  
@@
 =
-\mathrm{Tr} \left( \frac{\partial \hat{{\rho}}}{\partial t} \hat\calo \right)
+\mathrm{Tr} \left( \dot{\hat\rho} \hat\calo \right)
 $,
@@
 \sum'_{cc'} \mathcal{O}_{c'c}(\bfk) 
-r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  \times
-\nonumber \\
-& \left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 
+r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  
+\left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 
 \frac{1}{\omega - \omega_{cv}(\bfk)  + i\epsilon} \right)
@@
   \delta(\omega-\omega_{cv}(\bfk) 
-\\
-\times\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 
+\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 
 \left(  
@@
 \frac{d^{3}k}{8 \pi^{3}}
-\\\nonumber
-&\times \sum_{vc}
+ \sum_{vc}
 r^{\mathrm{a}}_{vc'}(\bfk)  
@@
 \begin{align}
-\mathcal{V}_{\mathrm{a}}&(\omega,\alpha) \equiv \nonumber \\
-&\sqrt { 
+\mathcal{V}_{\mathrm{a}}(\omega,\alpha) \equiv 
+\sqrt { 
 [\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
@@
 \theta_{\mathrm{a}}  (\omega,\alpha)
-=& 
+= 
 \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
 {\mathcal{V}_{\mathrm{a}}(\omega,\alpha)} \right),
-& 0 \leq &\theta \leq \pi, 
+ \quad 0 \leq \theta \leq \pi, 
 \label{eq:polar-ang}
@@
 \varphi_{\mathrm{a}} (\omega,\alpha)
-=& 
+=
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
 {\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
-& 0 \leq &\varphi \leq 2\pi.
+\quad 0 \leq \varphi \leq 2\pi.
 \label{eq:azimuthal-ang} 
@@
 \centering
-\includegraphics[width=\linewidth]{plots/2-vab-str-comp}
+\includegraphics[width=\tama]{plots/2-vab-str-comp}
 \caption{$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ 
@@
 $\ga=150^\circ$ maximizes the response, where two extreme values of
-$\calv^{\rmy\rmz}$ are found, one at {\color{red} $\hbar\go=0.7204$\,eV} of
+$\calv^{\rmy\rmz}$ are found, one at  $\hbar\go=0.720$\,eV of
 $\calv^{\rmy\rmz}=-711.9$ Km/s, and the other at $\hbar\go=0.911$\,eV of
@@
       &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
-Alt   & 2D   & 150   & {\color{red}0.720}  & $\mathrm{yz}$ & -711.9 \\
+Alt   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
       &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
@@
 \centering
-\includegraphics[width=\linewidth]{upplots/up-vsz-w1}
+\includegraphics[width=\tama]{upplots/up-vsz-w1}
 \caption{For the Up structure, the top panel shows 
@@
 \centering
-\includegraphics[width=\linewidth]{upplots/up-vsz-w2}
+\includegraphics[width=\tama]{upplots/up-vsz-w2}
 \caption{For the Up structure, the top panel shows $\calv_{\gs^\rmz} (\go,\ga)$
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
-0.080\,eV$\leq\hbar\go\leq$0.096\,eV {\color{red}(same energy range for the Up
-structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} )} and
+0.080\,eV$\leq\hbar\go\leq$0.096\,eV (similar energy range for the Up
+structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
 $0^\circ\leq\ga\leq 180^\circ$.
@@
 (\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.084$\,eV,
-{\color{red}thus following the ridge shown in the 3D plot of the top panel,
-along with its corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
-(right scale, red line)}.
-% 
-It is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
+thus following the ridge shown in the 3D plot of the top panel. 
+Also,
+we plot the
+corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
+(right scale, red line),
+where it is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
 at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
@@
 and for all values of $\ga$, the electrons, with the chosen spin pointing along
-$z$, will move at angle of {\color{red}$\gamma_{\gs^\rmz}(\omega,\alpha) \sim
-64.5^{\circ}$} with respect to the $x$ direction, with the range of  high
+$z$, will move at angle of $\gamma_{\gs^\rmz}(\omega,\alpha) \sim
+64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
 speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
@@
 black line), at $\hbar\go= 1.954$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel, {\color{red}along with its corresponding
-velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red line)}. In
+in the 3D plot of the top panel. Also we plot the corresponding
+velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red
+line),
+where in
 this case we see that the values of $\gamma_{\gs^z}(\omega,\alpha)$ have more
@@
 \centering
-\includegraphics[width=\linewidth]{altplots/alt-vsz}
+\includegraphics[width=\tama]{altplots/alt-vsz}
 \caption{For the Alt structure, the top panel shows $\calv_{\gs^\rmz}
@@
 (\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.720$\,eV,
-{\color{red} thus following the highest ridge shown in the 3D plot of the top
-panel, along with its corresponding velocity angle $\gamma_{\gs^\rmz}
-(\omega,\alpha)$ (right scale, red line)}. In this case we see that
+ thus following the highest ridge shown in the 3D plot of the top
+panel. Also, we plot the corresponding velocity angle $\gamma_{\gs^\rmz}
+(\omega,\alpha)$ (right scale, red line), where now we see that
 $\gamma_{\gs^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
@@
 \centering
-\includegraphics[width=\linewidth]{upplots/up-vx-vy-w1}
+\includegraphics[width=\tama]{upplots/up-vx-vy-w1}
 \caption{For the Up structure we show
@@
 \centering
-\includegraphics[width=\linewidth]{upplots/up-vx-vy-w2}
+\includegraphics[width=\tama]{upplots/up-vx-vy-w2}
 \caption{For the Up structure we show $\mathcal{V}_{\mathrm{a}}
@@
 $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s. 
-{\color{red}Checar que esto sea correcto para ambos maximos!!
+Checar que esto sea correcto para ambos maximos!!
 We remark that these angles are almost
-constant for all the energy values across the peak of this two local maxima, for
+constant for all the energy values across the peak of these two local maxima, for
 which the spin is directed upward in the first Cartesian quadrant of the $xy$
 plane when it moves along either $x$ or $y$ directions.
-}
 
@@
 \centering
-\includegraphics[width=\linewidth]{altplots/alt-vx-vy-w1}
+\includegraphics[width=\tama]{altplots/alt-vx-vy-w1}
 \caption{For the Alt structure we show
@@
 \centering
-\includegraphics[width=\linewidth]{altplots/alt-vx-vy-w2}
+\includegraphics[width=\tama]{altplots/alt-vx-vy-w2}
 \caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
@@
 In Fig. \ref{fig:alt-vx-vy-w1} the absolute maxima is at
-{\color{red} $\hbar\go=0.7204$\,eV,} with $\mathcal{V}_{\mathrm{x}}
+$\hbar\go=0.720$\,eV, with $\mathcal{V}_{\mathrm{x}}
 (\omega,\alpha) = 301.7$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) =
@@
 directed along $x$ or $y$; this effect does not seem to have been reported
-previously. 
+previously on this kind of structures. 
 % 
@@
 % 
+The speed values obtained in here, are of the same order of magnitude
+as those of Ref.~\onlinecite{najmaiePRB03} in 
+unbiased semiconductor quantum well structures.
 The spin relaxation time in pure and doped graphene is long enough in the order
@@
 Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
-
+R.Z.P. thank CONACyT for scholarship support.
 \bibliography{article.bib}

### 2017-07-31 mu/article/article.tex
Making english corrections

@@
 spin current induced by  a linearly
-polarized beam of light that impinges normally at the surface of  two 50\%
+polarized beam of light that impinges normally on the surface of  two 50\%
 hydrogenated noncentrosymmetric 2D graphene 
@@
 The hydrogenation opens an energy gap in both structures.
-We analyze two possibilities, one in which by fixing the spin along a
+We analyze two possibilities: one in which by fixing the spin along a
 chosen direction, the resulting spin-velocity is calculated, 
-and the other one, where we chose the spin-velocity direction
+and another where we choose the spin-velocity direction
 on the surface plane, and calculate its speed and
@@
 and polarization angle $\ga$  of the incoming  beam. 
-The results are calculated in a full
+The results are calculated within a full
 electronic band structure scheme within the DFT in the LDA approximation.
-The maxima of the spin-velocity speed is obtained when
+The maxima of the spin-velocity speed are obtained when
 $\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up,
@@
 645\,Km/s
-for Up and Alt, respectively, when the spin points perpendicular to
+for Up and Alt, respectively, when the spin points perpendicularly to
 the surface. Also,
@@
 688\,Km/s 
-and the spin  pointing at 13$^\circ$ form the surface normal, for Up,
+with the spin  pointing at 13$^\circ$ from the surface normal, for Up,
 and
@@
 manipulation and transport of spin of electrons in a solid state 
-media plays the determining role adding a new degree of freedom to the
+media plays the determining role, adding a new degree of freedom to
 conventional charge manipulation.\cite{wolfSC04,fabianAPS07}
 % 
-At present there is an increasing interest in attain the same level of control
-over the transport of spin at micro or nano scales as has been done for the
-flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
+At present, there is an increasing interest in attaining the same level of
+control over the transport of spin at micro or nano scales, as it has been done for
+the flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
 semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
-dattaAPL90,gotteNat16,pershinPRB08} and some of them require spin polarized
+dattaAPL90,gotteNat16,pershinPRB08}, and some of them require spin polarized
 electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
@@
 semiconductor devices is the fact that the spin relaxation time in a
-semiconducting media is short disabling the spin transport and then resulting
-in a no observable spin current.\cite{murakamiSc03}
-% 
-In PSCs there is no net
-motion of charge; spin-up electrons move in a given direction while spin-down
+semiconducting media is short, disabling the spin transport, and then resulting
+in a non-observable spin current.\cite{murakamiSc03}
+% 
+In PSCs, there is no net
+motion of charge; spin-up electrons move in a given direction, while spin-down
 electrons travel in the opposite one. 
@@
 illuminated by light with photon energy larger than the energy gap.
-For instance,
-this phenomena can result from spin
+This phenomenon can result from spin
 injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04} interference of two
@@
 
-Graphene, an allotrope of carbon with hexagonal 2D lattice structure presents
+Graphene, an allotrope of carbon with hexagonal 2D lattice structure, presents
 properties like fractional quantum Hall effect at room temperature, excellent
 thermal transport properties, excellent conductivity\cite{heerscheNat07} and
-strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08} being then a
-perfect platform to be used in two-dimensions electronic systems; however most
+strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08}, being then a
+perfect platform to be used in two-dimension electronic systems; however, most
 electronic applications are disabled by the absence of a semiconducting gap.
@@
 % 
-In this paper we present two 50\% hydrogenated graphene noncentrosymmetric
-structures both presenting a discernible band gap: the Up structure,
+In this paper, we present two 50\% hydrogenated graphene noncentrosymmetric
+structures, both presenting a discernible band gap: the Up structure,
 shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
-only in the upper side of the structure while the Alt structure, shown
-in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
+only on the upper side of the structure, while the Alt structure, shown
+in Fig. \ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom
 sides of the carbon slab.\cite{zapataPSB2016}
@@
 
-Using those structures we address a theoretical study of the 
+Using those structures, we address a theoretical study of the 
 spin velocity
@@
 by one-photon absorption of linearly polarized light.
-Because we have 2D structures we made the analysis for tow cases. The first is
-fixing the spin of the electrons along the $z$ Cartesian direction with the
-velocity directed on the surface of the structure in the $xy$ plane. The second
-is fixing the spin velocity in the $x$ or $y$ direction and the spin directed
-in $xyz$.
+Since we have 2D structures, we do the analysis for two cases. The first is by
+fixing the spin of the electrons along the $z$ Cartesian direction, with the
+velocity directed on the surface of the structure on the $xy$ plane. The second
+is by fixing the spin velocity in the $x$ or $y$ direction and the spin directed
+to $xyz$.
 % 
 The SVI is an optical effect that quantifies the velocity at which a PSC moves
-along the Cartesian direction $\mathrm{a}$ with the spin of electron polarized
+along the Cartesian direction, $\mathrm{a}$, with the spin of electron polarized
 along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
-polarized light can promote an even distribution of electrons in $\mathbf{k}$ space
-regardless the symmetry of the material resulting in a 
+polarized light can promote an even distribution of electrons in $\mathbf{k}$ space,
+regardless of the symmetry of the material, resulting in a 
 null electrical current.\cite{bhatPRL05}
@@
 injection.\cite{bhatPRL05} If the crystalline structure of the material is
-noncentrosymmetric the spin polarization injected at a given $\mathbf{k}$ point
+noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$ point
 not necessarily 
@@
 where $\hat\bfv=[\hat\bfr,\hat H_0]/i\hbar$ is the velocity operator, with
-$\hat \bfr$ the position operator,  $\hat H_0$ the unperturbed
-ground state Hamiltonian, and
+$\hat \bfr$ being the position operator and $\hat H_0$ the unperturbed
+ground state Hamiltonian;
 the Roman superscripts  indicate Cartesian coordinates. 
@@
 take into account the excited coherent superposition
-of the spin-splited conduction bands inherent to the 
+of the spin-split conduction bands inherent to the 
 noncentrosymmetric 
@@
 where we assumed that the conduction bands $c$ and $c'$
-are quasidegenerate  states and we take $\ge\to 0$ at the end of the
+are quasidegenerate  states, and we take $\ge\to 0$ at the end of the
 calculation.  The spin-splitting of the valence ($v$) bands is very
@@
 %%%BMSU 
-The matriz elements of any operator $\calo$ are given by
+The matrix elements of any operator $\calo$ are given by
 $\calo_{nm}(\bfk)=\bra{n\bfk}\hat\calo\ket{m\bfk}$,
@@
 $H_{0}|n\mathbf{k}\rangle = \hbar \omega_{n}(\mathbf{k})|n\mathbf{k}\rangle$ 
-with $\hbar \omega_{n}(\mathbf{k})$ the energy of the
+with $\hbar \omega_{n}(\mathbf{k})$ being the energy of the
 electronic band $n$ at point $\mathbf{k}$ in the irreducible Brillouin zone
@@
 Replacing  $\hat\calo \rightarrow \hat{K}^{\mathrm{ab}}$, in 
-above expression, one can show that
+the above expression, one can show that
 \begin{equation}
@@
 \end{equation}
-where repeated cartesian are summed, and 
+where repeated Cartesians are summed, and 
 \begin{equation}\label{eq:mu}
@@
 \right]
-,  
 \end{aligned}
@@
 $
-K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}). 
+K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}) 
 $
-that follows from time-reversal invariance. The prime $'$ in the sum means that
-$c$ and $c'$ are quasi degenerate states and the sum only covers these states.
-Since $\mu^{\mathrm{abcd}}(\omega)$ is real we have that
+which follows from time-reversal invariance. The prime symbol $'$ in the sum means that
+$c$ and $c'$ are quasi degenerate states, and the sum only covers these states.
+Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
 $\mu^{\mathrm{abcd}}(\omega) =
@@
 We remark that Eq.~\eqref{eq:mu} 
- is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05}
+is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05},
 obtained by using the semiconductor optical Bloch equations.
@@
 \end{equation}  
-that gives the velocity, along the direction $\mathrm{a}$, at which the spin
-moves polarized along the direction $\mathrm{b}$. The carrier injection rate
+which gives the velocity, along direction $\mathrm{a}$, at which the spin
+moves in a polarized state along direction $\mathrm{b}$. The carrier injection rate
 $\dot n(\go)$ is written as,\cite{nastosPRB05}
@@
 \dot{n}(\omega) =
-\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
+\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega)
 \label{eq:dotn}
@@
 
-The function $\calv^{\rma\rmb}(\go)$ allow us to quantify two very
+The function $\calv^{\rma\rmb}(\go)$ allows us to quantify two very
 important aspects of PSC. On one hand, we can fix the spin direction
-along $\mathrm{b}$,   
+along $\mathrm{b}$  
 and calculate the resulting electron velocity.  
-On the other hand, we can fix de velocity of the electron
-along $\mathrm{b}$,  and study the resulting direction along which the
+On the other hand, we can fix the velocity of the electron
+along $\mathrm{b}$ and study the resulting direction along which the
 spin is polarized.
 To this end, the added advantage of  2D structures, besides choosing
-them noncentrosymmetric, is that we can use an incoming linearly
+them as noncentrosymmetric, is that we can use an incoming linearly
 polarized beam of light
@@
 Indeed, writing 
-$\bfE(\omega) = E_0(\omega)(\cos\ga\,\hat\bfx+\sin\ga\,\hat\bfy)$
+$\bfE(\omega) = E_0(\omega)(\cos\ga\,\hat\bfx+\sin\ga\,\hat\bfy)$,
 where $\alpha$ is the polarization angle, we obtain from
@@
 \mu^{\mathrm{abxy}}(\omega)\sin 2\alpha\right)
+,
 \label{eq:vab-aw}
@@
 \end{widetext}
-as for the structures chosen in this article,
+for the structures chosen in this article,
 $\xi^{\mathrm{xx}}(\go)=\xi^{\mathrm{yy}}(\go)\equiv\xi(\go)$, and $\xi^{\mathrm{xy}}(\go)=0$.
@@
 Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of
-the electron velocity in plane
+the electron velocity on the plane of the structure 
 with the spin polarized along the $\mathrm{b}$ direction as
@@
 corresponding to the electron velocity being parallel or perpendicular
-the incoming polarization, 
+to the incoming polarization, 
 respectively. The subscript $\gs^\rmb$ denotes the spin along $\rmb$.
@@
 
-Fixing the calculated velocity along $\rma=x$ or $\rma=y$
- we define it's corresponding magnitude as
+Fixing the calculated velocity along $\rma=x$ or $\rma=y$,
+we define its corresponding magnitude as
 \begin{align}
@@
 
-We preset the results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
+We present the results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
 $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-up  and
-C$_{16}$H$_{8}$-alt structures being both noncentrosymmetric semi-infinite 2D
+C$_{16}$H$_{8}$-alt structures, being both noncentrosymmetric semi-infinite 2D
 carbon systems with 50\% hydrogenation in different arrangements. We recall
 that the Up structure has hydrogen atoms only on the upper side of the carbon
-sheet while the Alt structure has alternating hydrogen atoms on the upper and
-bottom sides. Also we take the hexagonal carbon lattice to be on the $xy$ plane
+sheet, while the Alt structure has alternating hydrogen atoms on the upper and
+bottom sides. Also, we take the hexagonal carbon lattice to be on the $xy$ plane
 for both structures, and the carbon-hydrogen bonds on the perpendicular $xz$
@@
 We calculated the self-consistent ground state and the Kohn-Sham states using
-density functional theory in the local density approximation (DFT-LDA) with a
+density functional theory in the local density approximation (DFT-LDA), with a
 planewave basis using the ABINIT code \cite{gonzeCPC09}.
@@
 We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
-Gaussian pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit
+Gaussian pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit
 interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
@@
 give small contribution to PSC.\cite{bhatPRL05} Therefore,
-$[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat
+$[\hat\bfv,\hat\bfS]=0$, and Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat
 v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$. Finally, the prime in the sum of
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\go$, for the directions $\rma\rmb$ and angle $\ga$
+(\omega,\alpha)$ vs. $\hbar\go$ for the directions $\rma\rmb$ and the angle $\ga$
 that maximizes the signal, for the Up  and Alt structures and for CdSe and
@@
 % 
-As expected from de delta function of Eq.~\eqref{eq:mu},
+As expected from the delta function of Eq.~\eqref{eq:mu},
 $\calv^{\rma\rmb}(\go,\ga)$ rises right at the corresponding energy gap of each
 system. For the 2D structures, the spectrum covers two narrow energy regions
-with large values of the response, while for bulk systems the spectra covers a
+with large values of response, while for bulk systems, the spectra covers a
 rather wide energy range, but with a much smaller response.
 % 
-For the Up structure $\rma\rmb=yz$ and $\ga=35^\circ$ maximizes the response,
+For the Up structure, $\rma\rmb=yz$ and $\ga=35^\circ$ maximize the response,
 which means that an incoming beam of light with its electric field polarized at
 35$^\circ$ from the $x$ direction will induce electrons to move along $y$
-(parallel to the surface) with their spin polarized along $z$ (perpendicular to
-the surface), with the following speeds.
-% 
-Right at the energy onset $\calv^{yz}(\go,\ga)=668$\,Km/s, speed that remains
-almost constant for 65 meV, and then goes to zero. A second region is found
+(parallel to the surface), with their spin polarized along $z$ (perpendicular to
+the surface), with the following speeds:
+% 
+right at the energy onset, $\calv^{yz}(\go,\ga)=668$\,Km/s, a speed that remains
+almost constant for 65 meV, and then goes to zero and a second region is found
 above 1.946 eV, where there are two extreme values of the speed,
@@
 (antiparallel) to the electric field.
-
-Likewise for the Alt structure we find that also $\rma\rmb=yz$ and
+Likewise, for the Alt structure, we find that also $\rma\rmb=yz$ and
 $\ga=150^\circ$ maximizes the response, where two extreme values of
@@
 $\calv^{\rmy\rmz}=-330.6$ Km/s.
-% 
-For the bulk structures we calculate $\calv^{\rma\rmb}(\go)$ from
-Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe we find
+
+For the bulk structures, we calculate $\calv^{\rma\rmb}(\go)$ from
+Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe, we find
 that for $\hbar\go=0.844$\,eV, $\bfgmu_{\mathrm{max}}\to \mu^{zzzz}$, and
@@
 $\bfgmu_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and $\calv^{\rma\rma}(\go,\ga)=-28.7$\,Km/s, with
-$\rma=x,y,z$. For these bulk semiconductors the $x$, $y$, and $z$ axis are
+$\rma=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis are
 taken along the standard cubic unit cell directions, [100], [010], and [001],
-respectively. In Table \ref{tab:vab-str-comp} we present the comparison of
+respectively. In Table \ref{tab:vab-str-comp}, we present the comparison of
 $\calv^{\rma\rmb}(\go,\ga)$ for the 2D structures and bulk crystals.
@@
 that are bigger
-than for the bulk crystals; in particular the Alt
+than for the bulk crystals; in particular, the Alt
 structure gives a $\calv^{\rma\rmb}(\go;\ga)$ $\sim$12 times larger than
@@
 
-In this subsection we calculate $\calv_{\gs^\rmz}(\omega,\alpha)$, Eq.
+In this subsection, we calculate $\calv_{\gs^\rmz}(\omega,\alpha)$, Eq.
 \eqref{eq:vs-mag}, for the case where the spin is fixed along $z$, i.e.
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
-calculate $\gamma_{\gs^\rmz}(\go,\ga)$, Eq. \eqref{eq:gamma-ang}, that
+calculate $\gamma_{\gs^\rmz}(\go,\ga)$, Eq. \eqref{eq:gamma-ang}, which
 determines the direction along which the injected electrons move along the
@@
 the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$,
-finding similar qualitative results to those presented bellow.
+finding similar qualitative results to those presented below.
 %
@@
 
-In the top panel of Fig. \ref{fig:up-vsz-w1} we plot
+In the top panel of Fig. \ref{fig:up-vsz-w1}, we plot
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
@@
 739.7$\,Km/s, and that the variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ as a function of $\ga$, that comes from the interplay of the
+(\omega,\alpha)$ as a function of $\ga$, which comes from the interplay of the
 $\bfgmu$ tensor components as multiplied by the  trigonometric functions of
@@
 and for all values of $\ga$, the electrons, with the chosen spin pointing along
-$z$, will move at angle of $\gamma_{\gs^\rmz}(\omega,\alpha) \sim
+$z$, will move at an angle of $\gamma_{\gs^\rmz}(\omega,\alpha) \sim
 64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
@@
 \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
-polarized along $z$, that move parallel or perpendicular to the incident
+polarized along $z$, which move parallel or perpendicular to the incident
 electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.
@@
 1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
-193.5$\,Km/s, and $\ga=35^{\circ}$ and $\hbar\go= 1.957$\,eV, with a value
+193.5$\,Km/s, and at $\ga=35^{\circ}$ and $\hbar\go= 1.957$\,eV, with a value
 of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) = 170.6$\,Km/s. 
@@
 black line), at $\hbar\go= 1.954$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel. Also we plot the corresponding
+in the 3D plot of the top panel. Also, we plot the corresponding
 velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red
@@
 % 
-Thus, by the correct choice of $\hbar\go$ and $\alpha$ we could inject
-electrons, in this case with their spin polarized along $z$, that move parallel
+Thus, through the correct choice of $\hbar\go$ and $\alpha$ we could inject
+electrons, in this case with their spin polarized along $z$, which move parallel
 or perpendicular to the incident electric field, with finite speeds.
@@
 
-We proceed to analyze the Alt structure, just as we did the Up structure, but
-in this case we only chose the lower energy range shown in the left central
+We proceed to analyze the Alt structure, just as we did with the Up structure, but
+in this case, we only choose the lower energy range shown in the left central
 panel of Fig.~\ref{fig:vab-str-comp}. 
@@
 0.715\,eV$\leq\hbar\go\leq$0.725\,eV and $0^\circ\leq\ga\leq 180^\circ$. We
-see a broad peak that maximize at $\ga=150^{\circ}$ and $\hbar\go=
+see a broad peak that maximizes at $\ga=150^{\circ}$ and $\hbar\go=
 0.720$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
@@
 % 
-In the bottom panel we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
+In the bottom panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
 (\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.720$\,eV,
@@
 (\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
-we could inject electrons with a fixed spin that move parallel or perpendicular
+we could inject electrons with a fixed spin which move parallel or perpendicular
 to the incident electric field.
@@
 \includegraphics[width=\tama]{upplots/up-vx-vy-w1}
-\caption{For the Up structure we show
+\caption{For the Up structure, we show
 $\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$
@@
 
-For the Up structure we find once again that  $\ga=35^{\circ}$ maximizes the
-response. In Fig. \ref{fig:up-vab-comp-rtp-1} we plot $\mathcal{V}_{\mathrm{a}}
+For the Up structure, we find once again that  $\ga=35^{\circ}$ maximizes the
+response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
@@
 % 
-We see that for $\hbar\go=0.084$\,eV, the responses has a maximum of
+We see that for $\hbar\go=0.084$\,eV, the response has a maximum of
 $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=431.7$\,Km/s, with
@@
 $\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and
-$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that, the
+$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that the
 spin is directed upward the third Cartesian quadrant of the $xy$ plane when the
@@
 % 
-Also, from this figure we have that when the electron moves along $x$ the spin
+Also, from this figure we have that when the electron moves along $x$, the spin
 direction is almost constant for all the energies across the peak of the
@@
 $208.3^{\circ}<\varphi_{\mathrm{x}}(\omega,\alpha)<215.7^{\circ}$, and when
-the electron moves along $y$ the spin polar angle has again small variations,
+the electron moves along $y$, the spin polar angle has again small variations,
 $11.3^{\circ}< \theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the
@@
 \end{figure}
-In Fig. \ref{fig:up-vx-vy-w2} we plot $\mathcal{V}_{\mathrm{a}}
+In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ vs. $\hbar\go$, in the range where there are two local maxima

### 2017-08-01 mu/article/article.tex
Making last corrections.

@@
 %\usepackage[inline]{showlabels}
-\input{/Users/bms/util/definitions}
+% \input{/Users/bms/util/definitions}
+\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
 \def\tama{10cm}
@@
 \begin{abstract}
-We present a theoretical study of spin-velocity injection of a pure
-spin current induced by  a linearly
-polarized beam of light that impinges normally on the surface of  two 50\%
-hydrogenated noncentrosymmetric 2D graphene 
-structures, labeled Up and Alt.
-The hydrogenation opens an energy gap in both structures.
-We analyze two possibilities: one in which by fixing the spin along a
-chosen direction, the resulting spin-velocity is calculated, 
-and another where we choose the spin-velocity direction
-on the surface plane, and calculate its speed and
-spin orientation. We do so by changing the energy $\hbar\go$ 
-and polarization angle $\ga$  of the incoming  beam. 
-The results are calculated within a full
-electronic band structure scheme within the DFT in the LDA approximation.
-The maxima of the spin-velocity speed are obtained when
-$\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up,
-and
-$\hbar\go=0.720$\,eV and $\ga=150^\circ$ for Alt.
-We find a speed of
-668\,Km/s
-and 
-645\,Km/s
-for Up and Alt, respectively, when the spin points perpendicularly to
-the surface. Also,
-the response is maximized
-by fixing the spin-velocity direction along a high symmetry Cartesian axis,
-obtaining a speed of 
-688\,Km/s 
-with the spin  pointing at 13$^\circ$ from the surface normal, for Up,
-and
-906\,Km/s 
-and the spin pointing at 60$^\circ$ from the surface normal, for Alt.
-These speed values are larger than those of bulk semiconductors, like
-CdSe and GaAs, thus 
-making the hydrogenated graphene structures
- excellent candidates for spintronics
+We present a theoretical study of spin-velocity injection of a pure spin current
+induced by  a linearly polarized beam of light that impinges normally on the
+surface of  two 50\% hydrogenated noncentrosymmetric 2D graphene structures,
+labeled Up and Alt. The hydrogenation opens an energy gap in both structures. We
+analyze two possibilities: one in which by fixing the spin along a chosen
+direction, the resulting spin-velocity is calculated, and another where we
+choose the spin-velocity direction on the surface plane, and calculate its speed
+and spin orientation. We do so by changing the energy $\hbar\go$ and
+polarization angle $\ga$  of the incoming  beam. The results are calculated
+within a full electronic band structure scheme within the DFT in the LDA
+approximation. The maxima of the spin-velocity speed are obtained when
+$\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up, and $\hbar\go=0.720$\,eV and
+$\ga=150^\circ$ for Alt. We find a speed of 668\,Km/s and 645\,Km/s for Up and
+Alt, respectively, when the spin points perpendicularly to the surface. Also,
+the response is maximized by fixing the spin-velocity direction along a high
+symmetry Cartesian axis, obtaining a speed of 688\,Km/s with the spin  pointing
+at 13$^\circ$ from the surface normal, for Up, and 906\,Km/s and the spin
+pointing at 60$^\circ$ from the surface normal, for Alt. These speed values are
+larger than those of bulk semiconductors, like CdSe and GaAs, thus making the
+hydrogenated graphene structures excellent candidates for spintronics
 applications.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 Spintronics is an emerging research field of electronics in which the
-manipulation and transport of spin of electrons in a solid state 
-media plays the determining role, adding a new degree of freedom to
-conventional charge manipulation.\cite{wolfSC04,fabianAPS07}
-% 
+manipulation and transport of spin of electrons in a solid state media plays the
+determining role, adding a new degree of freedom to conventional charge
+manipulation.\cite{wolfSC04,fabianAPS07} 
 At present, there is an increasing interest in attaining the same level of
-control over the transport of spin at micro or nano scales, as it has been done for
-the flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
+control over the transport of spin at micro or nano scales, as it has been done
+for the flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
 semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
@@
 electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
-% 
 One of the difficulties to achieve the development of spin current and PSC
@@
 in a non-observable spin current.\cite{murakamiSc03}
-% 
-In PSCs, there is no net
-motion of charge; spin-up electrons move in a given direction, while spin-down
-electrons travel in the opposite one. 
-This effect can result from one photon absorption of linearly polarized light
-by a semiconductor, with filled valence bands and empty conduction bands,
-illuminated by light with photon energy larger than the energy gap.
-This phenomenon can result from spin
-injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04} interference of two
-optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon absorption of
-linearly polarized light\cite{bhatPRL05} and has been observed in gallium
-arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium arsenide
-(AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
+In PSCs, there is no net motion of charge; spin-up electrons move in a given
+direction, while spin-down electrons travel in the opposite one. This effect can
+result from one photon absorption of linearly polarized light by a
+semiconductor, with filled valence bands and empty conduction bands, illuminated
+by light with photon energy larger than the energy gap. This phenomenon can
+result from spin injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04}
+interference of two optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon
+absorption of linearly polarized light\cite{bhatPRL05} and has been observed in
+gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
+arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
 
@@
 hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
-% 
 Depending on the percentage of hydrogenation and spatial configurations of
@@
 configurations.
-% 
 In this paper, we present two 50\% hydrogenated graphene noncentrosymmetric
-structures, both presenting a discernible band gap: the Up structure,
-shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
-only on the upper side of the structure, while the Alt structure, shown
-in Fig. \ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom
-sides of the carbon slab.\cite{zapataPSB2016}
+structures, both presenting a discernible band gap: the Up structure, shown in
+Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer only on
+the upper side of the structure, while the Alt structure, shown in Fig. 
+\ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
+the carbon slab.\cite{zapataPSB2016}
 
@@
       structure along with the 
-      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
-      labeled 1 (2).
+      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms. 
 }
@@
       structure along with the 
-      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms,
-      labeled 1 (2).
+      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms.
 }
@@
 
-Using those structures, we address a theoretical study of the 
-spin velocity
-injection (SVI) 
-by one-photon absorption of linearly polarized light.
-Since we have 2D structures, we do the analysis for two cases. The first is by
-fixing the spin of the electrons along the $z$ Cartesian direction, with the
-velocity directed on the surface of the structure on the $xy$ plane. The second
-is by fixing the spin velocity in the $x$ or $y$ direction and the spin directed
-to $xyz$.
-% 
+Using those structures, we address a theoretical study of the spin velocity
+injection (SVI) by one-photon absorption of linearly polarized light. Since we
+have 2D structures, we do the analysis for two cases. The first is by fixing the
+spin of the electrons along the $z$ Cartesian direction, with the velocity
+directed onto the surface of the structure on the $xy$ plane. The second is by
+fixing the spin velocity in the $x$ or $y$ direction and the spin directed to
+$xyz$.
 The SVI is an optical effect that quantifies the velocity at which a PSC moves
@@
 along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
-polarized light can promote an even distribution of electrons in $\mathbf{k}$ space,
-regardless of the symmetry of the material, resulting in a 
-null electrical current.\cite{bhatPRL05}
-Then, the electrons excited to the conduction bands at opposite $\mathbf{k}$
-points will result in opposite spin polarizations producing no net spin
-injection.\cite{bhatPRL05} If the crystalline structure of the material is
-noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$ point
-not necessarily 
- vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} 
-and then, since the velocities of electrons at opposite $\mathbf{k}$ points are
-opposite, a PSC will be produced. Since the structures presented
-here are noncentrosymmetric, they are good candidates in which this effect can
-be induced.
+polarized light can promote an even distribution of electrons in $\mathbf{k}$
+space, regardless of the symmetry of the material, resulting in a null
+electrical current.\cite{bhatPRL05} Then, the electrons excited to the
+conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
+polarizations producing no net spin injection.\cite{bhatPRL05} If the
+crystalline structure of the material is noncentrosymmetric, the spin
+polarization injected at a given $\mathbf{k}$ point not necessarily
+vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} and then, since the velocities
+of electrons at opposite $\mathbf{k}$ points are opposite, a PSC will be
+produced. Since the structures presented here are noncentrosymmetric, they are
+good candidates in which this effect can be induced.
 
@@
 is the pseudotensor that describes the rate of change of the  PSC process in
-semiconductors. To derive above we used
+semiconductors. To derive what we presented above we used
 $
@@
 Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of
-the electron velocity on the plane of the structure 
+the electron velocity on the plane of the structure,
 with the spin polarized along the $\mathrm{b}$ direction as
@@
 \hline
-\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
-\cline{3-5}
-\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
+\quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
+\cline{2-4}
+\quad type \qquad & $x$ & $y$ & $z$  \\
 \hline
-1 & H & -0.61516 & -1.77416 &  0.73196 \\
-1 & H &  0.61518 &  0.35514 &  0.73175 \\
-2 & C & -0.61516 & -1.77264 & -0.49138 \\
-2 & C & -0.61516 & -0.35600 & -0.72316 \\
-2 & C &  0.61516 &  0.35763 & -0.49087 \\
+H & -0.61516 & -1.77416 &  0.73196 \\
+H &  0.61518 &  0.35514 &  0.73175 \\
+C & -0.61516 & -1.77264 & -0.49138 \\
+C & -0.61516 & -0.35600 & -0.72316 \\
+C &  0.61516 &  0.35763 & -0.49087 \\
 \hline
@@
 \center
-\begin{tabular}{ccccc}\\
+\begin{tabular}{cccc}\\
 \hline
-\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
-\cline{3-5}
-\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
+\quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
+\cline{2-4}
+\quad type \qquad & $x$ & $y$ & $z$  \\
 \hline
-1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
-2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
-3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
-4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
-5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
-6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
+H &  -0.61516 &  -1.42140 & \ 1.47237 \\
+C &  -0.61516 &  -1.73300 & \ 0.39631 \\
+C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
+C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
+C &  -0.61516 &  -0.37396 &  -0.39632 \\
+H &  -0.61516 &  -0.68566 &  -1.47237 \\
 \hline
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\go$ for the directions $\rma\rmb$ and the angle $\ga$
+(\omega,\alpha)$ vs. $\hbar\go$ for the directions $\rma\rmb$, and for the
+angle $\ga$
 that maximizes the signal, for the Up  and Alt structures and for CdSe and
@@
 (parallel to the surface), with their spin polarized along $z$ (perpendicular to
-the surface), with the following speeds:
-% 
-right at the energy onset, $\calv^{yz}(\go,\ga)=668$\,Km/s, a speed that remains
-almost constant for 65 meV, and then goes to zero and a second region is found
+the surface), with the following speeds.
+% 
+Right at the energy onset, $\calv^{yz}(\go,\ga)=668$\,Km/s, a speed that remains
+almost constant for 65 meV, and then goes to zero. A second region is found
 above 1.946 eV, where there are two extreme values of the speed,
@@
 % 
-For the $\hbar\go=1.957$\,eV peak we obtain 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$, and 
+For the $\hbar\go=1.957$\,eV peak, we obtain 
+$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and 
 $\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with 
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s, and
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and
 $\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
@@
 $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s.
-Checar que esto sea correcto para ambos maximos!!
 We remark that these angles are almost
@@
 \includegraphics[width=\tama]{altplots/alt-vx-vy-w1}
-\caption{For the Alt structure we show
+\caption{For the Alt structure, we show
 $\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
@@
 \includegraphics[width=\tama]{altplots/alt-vx-vy-w2}
-\caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
+\caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
@@
 
-In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2} we plot
+In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2}, we plot
 $\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
@@
 $\hbar\go$ in two different ranges, and  for $\rma=x,y$. In this case,
-$\ga=150^\circ$,  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$,
+$\ga=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
 and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\ga$.
 % 
-In Fig. \ref{fig:alt-vx-vy-w1} the absolute maxima is at
+In Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
 $\hbar\go=0.720$\,eV, with $\mathcal{V}_{\mathrm{x}}
 (\omega,\alpha) = 301.7$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) =
-44.5^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$,
+44.5^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$,
 and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s, with
-$\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$, and
+$\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
 $\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. 
 % 
-Thus, the spin is directed upward the forth Cartesian quadrant of the $xy$
+Thus, the spin is directed upward the fourth Cartesian quadrant of the $xy$
 plane when the spin velocity is directed along $x$, and directed downward the
@@
 % 
-Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maxima is at
+Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
 $\hbar\go=0.911$\,eV, with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) =
@@
 $\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin
-is directed downward the forth Cartesian quadrant of the $xy$ plane when the
+is directed downward the fourth Cartesian quadrant of the $xy$ plane when the
 spin velocity is directed along $x$, and directed downward the third Cartesian
@@
 
-We have performed an \emph{ab initio} calculation for the SVI by one-photon
-absorption of linearly polarized light in the Up and Alt 2D
-hydrogenated graphene structures that and we made the calculation for the case
-when the spin is polarized in the $z$ direction or when the velocity is
-directed along $x$ or $y$; this effect does not seem to have been reported
-previously on this kind of structures. 
-% 
-This SVI is very sensitive to the symmetry characteristics of the structures
+We performed an \emph{ab initio} calculation for the SVI by one-photon
+absorption of linearly polarized light in the Up and Alt 2D hydrogenated
+graphene structures, and we made the calculation for the case when the spin is
+polarized in the $z$ direction or when the velocity is directed along $x$ or
+$y$; this effect does not seem to have been previously reported in this kind of
+structures.
+% 
+This SVI is very sensitive to the symmetry characteristics of the structures,
 presenting an anisotropic behavior. We found that the Up structure has
-the most intense response for the spin directed along $z$ resulting in 
-% 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s and 
-% 
-for an energy of the incoming beam of 0.084\,eV. Also the Alt structure
-has the most intense response when the spin moves along the $y$ direction
+the most intense response for the spin directed along $z$, resulting in 
+% 
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s, and 
+% 
+for an energy of the incoming beam of 0.084\,eV. Also, the Alt structure
+has the most intense response when the spin moves along the $y$ direction,
 resulting in 
@@
 % 
-The speed values obtained in here, are of the same order of magnitude
+The speed values obtained here are of the same order of magnitude
 as those of Ref.~\onlinecite{najmaiePRB03} in 
@@
 The spin relaxation time in pure and doped graphene is long enough in the order
-from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} The,
-according to our results both are excellent candidates for the development of
+from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} Then,
+according to our results, both are excellent candidates for the development of
 spintronics devices that require PSC due to the high spin velocity transport.
@@
 Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
-R.Z.P. thank CONACyT for scholarship support.
+R.Z.P. thanks CONACyT for scholarship support.
 \bibliography{article.bib}

### 2017-08-02 mu/article/article.tex
Deleting coments.

@@
 \documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
-\usepackage{amsmath}    % need for subequations 
-\usepackage{graphicx}   % need for figures 
-\usepackage{verbatim}   % useful for program listings 
-\usepackage{color}      % use if color is used in text 
-\usepackage{subfigure}  % use for side-by-side figures 
-\usepackage{hyperref}   % use for hypertext links, including those to external 
-                        % documents and URLs 
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{verbatim}
+\usepackage{color}
+\usepackage{subfigure}
+\usepackage{hyperref}
 \usepackage[dvipsnames]{xcolor}
 \usepackage{multirow}
-%\usepackage[inline]{showlabels}
 % \input{/Users/bms/util/definitions}
-\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
+%\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
 \def\tama{10cm}
-\raggedbottom           % don't add extra vertical space
+\raggedbottom
 
@@
 \author{Reinaldo Zapata-Pe\~na}
-\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
-Guanajuato 37150, M\'exico}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150,
+M\'exico}
 \author{Bernardo S. Mendoza}
-\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
-Guanajuato 37150, M\'exico}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150,
+M\'exico}
 \author{Anatoli I. Shkrebtii}
-\affiliation{University of Ontario, Institute of Technology,
-Oshawa, ON, L1H 7L7, Canada}
+\affiliation{University of Ontario, Institute of Technology, Oshawa, ON, L1H
+7L7, Canada}
 
@@
 choose the spin-velocity direction on the surface plane, and calculate its speed
-and spin orientation. We do so by changing the energy $\hbar\go$ and
-polarization angle $\ga$  of the incoming  beam. The results are calculated
+and spin orientation. We do so by changing the energy $\hbar\omega$ and
+polarization angle $\alpha$  of the incoming  beam. The results are calculated
 within a full electronic band structure scheme within the DFT in the LDA
 approximation. The maxima of the spin-velocity speed are obtained when
-$\hbar\go=0.084$\,eV and $\ga=35^\circ$ for Up, and $\hbar\go=0.720$\,eV and
-$\ga=150^\circ$ for Alt. We find a speed of 668\,Km/s and 645\,Km/s for Up and
-Alt, respectively, when the spin points perpendicularly to the surface. Also,
-the response is maximized by fixing the spin-velocity direction along a high
-symmetry Cartesian axis, obtaining a speed of 688\,Km/s with the spin  pointing
-at 13$^\circ$ from the surface normal, for Up, and 906\,Km/s and the spin
-pointing at 60$^\circ$ from the surface normal, for Alt. These speed values are
-larger than those of bulk semiconductors, like CdSe and GaAs, thus making the
-hydrogenated graphene structures excellent candidates for spintronics
-applications.
+$\hbar\omega = 0.084$\,eV and $\alpha=35^\circ$ for Up, and $\hbar\omega =
+0.720$\,eV and $\alpha=150^\circ$ for Alt. We find a speed of 668\,Km/s and
+645\,Km/s for Up and Alt, respectively, when the spin points perpendicularly to
+the surface. Also, the response is maximized by fixing the spin-velocity
+direction along a high symmetry Cartesian axis, obtaining a speed of 688\,Km/s
+with the spin  pointing at 13$^\circ$ from the surface normal, for Up, and
+906\,Km/s and the spin pointing at 60$^\circ$ from the surface normal, for Alt.
+These speed values are larger than those of bulk semiconductors, like CdSe and
+GaAs, thus making the hydrogenated graphene structures excellent candidates for
+spintronics applications.
 \end{abstract}
@@
 fixing the spin velocity in the $x$ or $y$ direction and the spin directed to
-$xyz$.
-The SVI is an optical effect that quantifies the velocity at which a PSC moves
-along the Cartesian direction, $\mathrm{a}$, with the spin of electron polarized
-along the Cartesian direction $\mathrm{b}$. One photon absorption of linearly
-polarized light can promote an even distribution of electrons in $\mathbf{k}$
-space, regardless of the symmetry of the material, resulting in a null
-electrical current.\cite{bhatPRL05} Then, the electrons excited to the
+$xyz$. The SVI is an optical effect that quantifies the velocity at which a PSC
+moves along the Cartesian direction, $\mathrm{a}$, with the spin of electron
+polarized along the Cartesian direction $\mathrm{b}$. One photon absorption of
+linearly polarized light can promote an even distribution of electrons in
+$\mathbf{k}$ space, regardless of the symmetry of the material, resulting in a
+null electrical current.\cite{bhatPRL05} Then, the electrons excited to the
 conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  T H E O R Y  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Theory} % (fold)
 \label{sec:theory}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%BMSD
 The operator that describes the electronic SVI is written as
 \begin{align}\label{z.1}
-\hat K^{\rma\rmb}=\frac{1}{2}\left( \hat v^\rma \hat S^\rmb 
-+\hat  S^\rmb \hat v^\rma\right) 
+\hat K^{\mathrm{a}\mathrm{b}} = 
+\frac{1}{2}\left( \hat v^\mathrm{a} \hat S^\mathrm{b} 
++\hat  S^\mathrm{b} \hat v^\mathrm{a}\right) 
 ,
 \end{align} 
-where $\hat\bfv=[\hat\bfr,\hat H_0]/i\hbar$ is the velocity operator, with
-$\hat \bfr$ being the position operator and $\hat H_0$ the unperturbed
-ground state Hamiltonian;
-the Roman superscripts  indicate Cartesian coordinates. 
-To obtain the expectation value of 
-$\hat K^{\rma\rmb}$, we use the length gauge for the perturbing
-Hamiltonian, written as
+where $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ is the velocity
+operator, with $\hat {\mathbf r}$ being the position operator and $\hat H_0$ the
+unperturbed ground state Hamiltonian; the Roman superscripts  indicate Cartesian
+coordinates. To obtain the expectation value of $\hat K^{\mathrm{a}\mathrm{b}}$,
+we use the length gauge for the perturbing Hamiltonian, written as
 \begin{align}\label{z.2}
-\hat H_{\text{p}}=-e\hat\bfr\cdot\bfE(t)
+\hat H_{\text{p}}=-e\hat{\mathbf r}\cdot{\mathbf E}(t)
 ,
@@
 \begin{align}\label{z.3}
-\bfE(t)= \bfE(\go)e^{-i\go t} + \bfE^*(\go)e^{i\go t}
+{\mathbf E}(t) = 
+{\mathbf E}(\omega)e^{-i\omega t} + {\mathbf E}^*(\omega)e^{i\omega t}
 .
 \end{align}
-In order to 
-calculate the response of the system to $\bfE(t)$, one needs to
-take into account the excited coherent superposition
-of the spin-split conduction bands inherent to the 
-noncentrosymmetric 
-semiconductors considered in this work.
-%Although, this splitting is small [15,16], is required to obtain the
-%correct results\cite{nastosPRB07}.
-% The conduction bands in the 
-% noncentrosymmetric  
-% semiconductors  
-% are spin split by a small amount,[15,16] typically
-%   smaller than the energy width of the laser pulse, and so the pulse
-%   excites a coherent superposition of the two conduction bands. Even
-%   for very long pulses with narrow energy widths, dephasing effects
-%   lead to an energy width of the bands large enough that spin-split
-%   states can become quasidegenerate. 
-To include the coherences, we follow Ref.~\onlinecite{nastosPRB05} and
-use a multiple
-scale approach that solves the equation of motion for the single
-particle density matrix $\gr_{mn}(\bfk;t)$, leading to
+In order to calculate the response of the system to ${\mathbf E}(t)$, one needs
+to take into account the excited coherent superposition of the spin-split
+conduction bands inherent to the noncentrosymmetric semiconductors considered in
+this work.
+%Although, this splitting is small [15,16], is required to obtain the correct
+%results\cite{nastosPRB07}. The conduction bands in the noncentrosymmetric
+%semiconductors are spin split by a small amount,[15,16] typically smaller than
+%the energy width of the laser pulse, and so the pulse excites a coherent
+%superposition of the two conduction bands. Even for very long pulses with
+%narrow energy widths, dephasing effects lead to an energy width of the bands
+%large enough that spin-split states can become quasidegenerate.
+To include the coherences, we follow Ref.~\onlinecite{nastosPRB05} and use a
+multiple scale approach that solves the equation of motion for the single
+particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
 \begin{align}\label{z.4}
-&\frac{\partial \rho_{cc'}(\bfk)}{\partial t} =
-\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
-{i \hbar^{2}}
-\sum_{v}r^{\mathrm{a}}_{cv}(\bfk) r^{\mathrm{b}}_{vc'}(\bfk)
-\left( \frac{1}{\omega - \omega_{c'v}(\bfk) - i \epsilon} 
-- 
-\frac{1}{\omega - \omega_{cv}(\bfk) + i \epsilon} \right)
+&\frac{\partial \rho_{cc'}({\mathbf k})}{\partial t} =
+\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}{i \hbar^{2}}
+\sum_{v}r^{\mathrm{a}}_{cv}({\mathbf k}) r^{\mathrm{b}}_{vc'}({\mathbf k})
+\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k}) - i \epsilon} - 
+\frac{1}{\omega - \omega_{cv}({\mathbf k}) + i \epsilon} \right)
 ,
 \end{align}
-where we assumed that the conduction bands $c$ and $c'$
-are quasidegenerate  states, and we take $\ge\to 0$ at the end of the
-calculation.  The spin-splitting of the valence ($v$) bands is very
-small, and is neglected throughout this work.\cite{nastosPRB07}
-% 􏱈 are close to  
-% one another, and that the pulse is short enough so that the energy
-% width overlaps the two bands, the equation of motion can be
-% solved. Leaving the details of the derivation to Ap- 
-% pendix A, the result for the off-diagonal component 􏰠 􏱈, c  
-%%%BMSU 
-The matrix elements of any operator $\calo$ are given by
-$\calo_{nm}(\bfk)=\bra{n\bfk}\hat\calo\ket{m\bfk}$,
-where 
-$H_{0}|n\mathbf{k}\rangle = \hbar \omega_{n}(\mathbf{k})|n\mathbf{k}\rangle$ 
-with $\hbar \omega_{n}(\mathbf{k})$ being the energy of the
-electronic band $n$ at point $\mathbf{k}$ in the irreducible Brillouin zone
-(IBZ),  $|n\mathbf{k}\rangle$ is the Bloch state, and 
-$\go_{nm}(\bfk)=\go_{n}(\bfk)-\go_{m}(\bfk)$.
-Using 
-$\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$
-for the expectation value of an observable $\mathcal{O}$, 
-where $\mathrm{Tr}$ denotes the trace, we obtain
+where we assumed that the conduction bands $c$ and $c'$ are quasidegenerate
+states, and we take $\epsilon\to 0$ at the end of the calculation.  The spin-
+splitting of the valence ($v$) bands is very small, and is neglected throughout
+this work.\cite{nastosPRB07} The matrix elements of any operator ${\cal O}$ are
+given by ${\cal O}_{nm}({\mathbf k})=\langle n{\mathbf k}|\hat{\cal O}|
+m{\mathbf k}\rangle$, where $H_{0}|n{\mathbf k}\rangle = \hbar
+\omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ with $\hbar \omega_{n}({\mathbf
+k})$ being the energy of the electronic band $n$ at point ${\mathbf k}$ in the
+irreducible Brillouin zone (IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state,
+and $\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf k})-\omega_{m}({\mathbf k})$.
+Using $\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$ for the
+expectation value of an observable $\mathcal{O}$, where $\mathrm{Tr}$ denotes
+the trace, we obtain
 \begin{align}\label{z.5}
-\mathcal{O} 
-%=&
-%\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c \mathbf{k} 
-%| \hat{\rho} \hat{\mathcal{O}} |
-%c\mathbf{k} \rangle \nonumber \\
-=& 
-\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \rho_{cc'}(\mathbf{k}) 
-\mathcal{O}_{c'c}(\mathbf{k}),
+\mathcal{O} = & 
+\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \rho_{cc'}({\mathbf k}) 
+\mathcal{O}_{c'c}({\mathbf k}),
 \end{align}
-where we used 
-the closure
-relationship $\sum_{n}|n\mathbf{k}\rangle \langle n\mathbf{k}| = 1$,
-where $n=v,c$,
-and the fact that $\rho_{vn}(\bfk)=\rho_{nv}(\bfk)=0$ for $n=c,c'$. 
-Therefore, 
-using  Eqs. \eqref{z.4} and \eqref{z.5},
-the
-rate of change of $\mathcal{O}$,
-$\dot{\mathcal{O}} 
-=
-\mathrm{Tr} \left( \dot{\hat\rho} \hat\calo \right)
-$,
- is given by
+where we used the closure relationship $\sum_{n}|n{\mathbf k}\rangle \langle
+n{\mathbf k}| = 1$, where $n=v,c$, and the fact that $\rho_{vn}({\mathbf
+k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. Therefore, using  Eqs. \eqref{z.4}
+and \eqref{z.5}, the rate of change of $\mathcal{O}$, $\dot{\mathcal{O}} =
+\mathrm{Tr} \left( \dot{\hat\rho} \hat{\cal O} \right)$, is given by
 \begin{align}
-\dot{\mathcal{O}} 
-&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
-\sum'_{cc'} \mathcal{O}_{c'c}(\bfk) 
-r^{\mathrm{a}}_{cv}(\bfk)  r^{\mathrm{b}}_{vc'}(\bfk)  
-\left( \frac{1}{\omega - \omega_{c'v}(\bfk)  - i\epsilon} - 
-\frac{1}{\omega - \omega_{cv}(\bfk)  + i\epsilon} \right)
+\dot{\mathcal{O}} &=
+\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
+\sum'_{cc'} \mathcal{O}_{c'c}({\mathbf k}) 
+r^{\mathrm{a}}_{cv}({\mathbf k})  r^{\mathrm{b}}_{vc'}({\mathbf k})  
+\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k})  - i\epsilon} - 
+\frac{1}{\omega - \omega_{cv}({\mathbf k})  + i\epsilon} \right)
 E^{\mathrm{a}}(\omega) E^{\mathrm{b*}}(\omega)
@@
 \end{align}
-Replacing  $\hat\calo \rightarrow \hat{K}^{\mathrm{ab}}$, in 
-the above expression, one can show that
+Replacing $\hat{\cal O} \rightarrow \hat{K}^{\mathrm{ab}}$, in the above
+expression, one can show that
 \begin{equation}
-\dot{K}^{\mathrm{ab}}(\omega) =
-\mu^{\mathrm{abcd}}(\omega)
+\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
 E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
@@
 \frac{d^{3}k}{8 \pi^{3}} \sum'_{vcc'}
-  \delta(\omega-\omega_{cv}(\bfk) 
-\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}(\bfk) 
+\delta(\omega-\omega_{cv}({\mathbf k}) 
+\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}({\mathbf k}) 
 \left(  
-r^{\mathrm{c}}_{vc'}(\bfk)   
-r^{\mathrm{d}}_{cv }(\bfk)  +
+r^{\mathrm{c}}_{vc'}({\mathbf k})   
+r^{\mathrm{d}}_{cv }({\mathbf k})  +
 (c \leftrightarrow d)  
@@
 semiconductors. To derive what we presented above we used
-$
-K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}_{nm}(\mathbf{k}) 
-$
-which follows from time-reversal invariance. The prime symbol $'$ in the sum means that
-$c$ and $c'$ are quasi degenerate states, and the sum only covers these states.
-Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
-$\mu^{\mathrm{abcd}}(\omega) =
-\mu^{\mathrm{abdc}}(\omega)$. 
-We remark that Eq.~\eqref{eq:mu} 
-is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05},
-obtained by using the semiconductor optical Bloch equations.
-Using the closure relation,
+$K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+follows from time-reversal invariance. The prime symbol $'$ in the sum means
+that $c$ and $c'$ are quasi degenerate states, and the sum only covers these
+states. Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
+$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$. We remark that
+Eq.~\eqref{eq:mu} is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05},
+obtained by using the semiconductor optical Bloch equations. Using the closure
+relation,
 \begin{equation}
-K^{\mathrm{ab}}_{cc'}(\mathbf{k}) = \frac{1}{2}
-\sum_{l=v,c}
-\left(v^{\mathrm{a}}_{cl}(\mathbf{k})S^{\mathrm{b}}_{lc'}(\mathbf{k})
-+S^{\mathrm{b}}_{cl}(\mathbf{k}) v^{\mathrm{a}}_{lc'}(\mathbf{k})
+K^{\mathrm{ab}}_{cc'}({\mathbf k}) = 
+\frac{1}{2} \sum_{l=v,c}
+\left(v^{\mathrm{a}}_{cl}({\mathbf k})S^{\mathrm{b}}_{lc'}({\mathbf k})
++S^{\mathrm{b}}_{cl}({\mathbf k}) v^{\mathrm{a}}_{lc'}({\mathbf k})
 \right)
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{Spin velocity injection} % (fold)
-%\label{sec:theory-pure_spin_current}
 Now, we define the spin velocity injection (SVI) as
@@
 \end{equation}  
-which gives the velocity, along direction $\mathrm{a}$, at which the spin
-moves in a polarized state along direction $\mathrm{b}$. The carrier injection rate
-$\dot n(\go)$ is written as,\cite{nastosPRB05}
+which gives the velocity, along direction $\mathrm{a}$, at which the spin moves
+in a polarized state along direction $\mathrm{b}$. The carrier injection rate
+$\dot n(\omega)$ is written as,\cite{nastosPRB05}
 \begin{equation}
@@
 \begin{equation}\label{eq:xi}
-\begin{aligned}
-\xi^{\mathrm{ab}}(\omega)
-&
-=
+\xi^{\mathrm{ab}}(\omega) =
 \frac{2\pi e^{2}}{\hbar^{2}} \int 
-\frac{d^{3}k}{8 \pi^{3}}
- \sum_{vc}
-r^{\mathrm{a}}_{vc'}(\bfk)  
-r^{\mathrm{b}}_{cv }(\bfk)  
-\delta(\omega-\omega_{cv}(\bfk) 
+\frac{d^{3}k}{8 \pi^{3}} \sum_{vc}
+r^{\mathrm{a}}_{vc'}({\mathbf k})  
+r^{\mathrm{b}}_{cv }({\mathbf k})  
+\delta(\omega-\omega_{cv}({\mathbf k}) 
 , 
-\end{aligned}
 \end{equation}
-is related to the imaginary part of the linear optical 
-response tensor by
-$\mathrm{Im}[\ge^{\rma\rmb}(\go)]=2\pi\ge_0\hbar\xi^{\rma\rmb}(\go)$.
+is related to the imaginary part of the linear optical response tensor by
+$\mathrm{Im} [\epsilon^{\mathrm{a}\mathrm{b}}(\omega)] =
+2\pi\epsilon_0\hbar\xi^{\mathrm{a}\mathrm{b}}(\omega)$.
 
-The function $\calv^{\rma\rmb}(\go)$ allows us to quantify two very
-important aspects of PSC. On one hand, we can fix the spin direction
-along $\mathrm{b}$  
-and calculate the resulting electron velocity.  
-On the other hand, we can fix the velocity of the electron
-along $\mathrm{b}$ and study the resulting direction along which the
-spin is polarized.
-To this end, the added advantage of  2D structures, besides choosing
-them as noncentrosymmetric, is that we can use an incoming linearly
-polarized beam of light
-at normal incidence, and use the  direction of the polarized  electric
-field to control $\calv^{\rma\rmb}(\go)$.
-Indeed, writing 
-$\bfE(\omega) = E_0(\omega)(\cos\ga\,\hat\bfx+\sin\ga\,\hat\bfy)$,
-where $\alpha$ is the polarization angle, we obtain from
- Eq. \eqref{eq:vab-w}
-that
+The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify two
+very important aspects of PSC. On one hand, we can fix the spin direction along
+$\mathrm{b}$ and calculate the resulting electron velocity. On the other hand,
+we can fix the velocity of the electron along $\mathrm{b}$ and study the
+resulting direction along which the spin is polarized. To this end, the added
+advantage of  2D structures, besides choosing them as noncentrosymmetric, is
+that we can use an incoming linearly polarized beam of light at normal
+incidence, and use the  direction of the polarized  electric field to control
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$. Indeed, writing ${\mathbf E}(\omega)
+= E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$, where
+$\alpha$ is the polarization angle, we obtain from Eq. \eqref{eq:vab-w} that
 \begin{widetext}
-\begin{align}
-\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
-&= 
-\frac{2}{\hbar\xi(\go)}
+\begin{equation}
+\mathcal{V}^{\mathrm{ab}}(\omega,\alpha) = 
+\frac{2}{\hbar\xi(\omega)}
 \left(\mu^{\mathrm{abxx}}(\omega)\cos^{2}\alpha + 
@@
 \label{eq:vab-aw}
-\end{align}
+\end{equation}
 \end{widetext}
-for the structures chosen in this article,
-$\xi^{\mathrm{xx}}(\go)=\xi^{\mathrm{yy}}(\go)\equiv\xi(\go)$, and $\xi^{\mathrm{xy}}(\go)=0$.
-Now, we formalize our two options for $\calv^{\rma\rmb}(\go)$.
+for the structures chosen in this article, $\xi^{\mathrm{xx}}(\omega) =
+\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and $\xi^{\mathrm{xy}}(\omega)=0$.
+Now, we formalize our two options for ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.
 
@@
 
-Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of
-the electron velocity on the plane of the structure,
-with the spin polarized along the $\mathrm{b}$ direction as
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the
+electron velocity on the plane of the structure, with the spin polarized along
+the $\mathrm{b}$ direction as
 \begin{equation}
-\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)
-\equiv
+\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha) \equiv
 \sqrt{
@@
 \begin{equation}
-\gamma_{\gs^\mathrm{b}} (\omega,\alpha)
-=
+\gamma_{\sigma^\mathrm{b}} (\omega,\alpha) =
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
@@
 \end{equation}
-% where this angle is measured in the counter-clockwise direction from the
-% positive $x$. 
 We also define two special angles
 \begin{equation}
-\gamma_{\gs^\mathrm{b}}^\parallel(\omega,\alpha) = \alpha, 
+\gamma_{\sigma^\mathrm{b}}^\parallel(\omega,\alpha) = \alpha, 
 \label{eq:gamma-par} 
@@
 \begin{equation}
-\gamma_{\gs^\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
+\gamma_{\sigma^\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
 \label{eq:gamma-perp}
 \end{equation}
-corresponding to the electron velocity being parallel or perpendicular
-to the incoming polarization, 
-respectively. The subscript $\gs^\rmb$ denotes the spin along $\rmb$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+corresponding to the electron velocity being parallel or perpendicular to the
+incoming polarization, respectively. The subscript $\sigma^\mathrm{b}$ denotes
+the spin along $\mathrm{b}$.
 
@@
 
-Fixing the calculated velocity along $\rma=x$ or $\rma=y$,
+Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$,
 we define its corresponding magnitude as
@@
 \end{align}
-from where we see that the spin would be oriented
-in the $xyz$ system's coordinates
-according to a polar angle
-\begin{align}
-\theta_{\mathrm{a}}  (\omega,\alpha)
-= 
+from where we see that the spin would be oriented in the $xyz$ system's
+coordinates according to a polar angle
+\begin{equation}
+\theta_{\mathrm{a}}  (\omega,\alpha) = 
 \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
@@
 \label{eq:polar-ang}
-\end{align}
+\end{equation}
 and an azimuthal angle
-\begin{align}
-\varphi_{\mathrm{a}} (\omega,\alpha)
-=
+\begin{equation}
+\varphi_{\mathrm{a}} (\omega,\alpha) =
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
@@
 \label{eq:azimuthal-ang} 
-\end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   R E S U L T S   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{equation}
 
@@
 \end{tabular}
-
-\caption{Unit cell of Up structure. Layer division, atom types and
-positions for the Up structure. The structure unit cell was divided in
-two layers corresponding to hydrogen and carbon atoms.The corresponding layer
-atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
-number of layer.}
+\caption{Atomic positions in the unit cell of Up structure. 
+}
 \label{tab:up-unitcell}
 \end{table}
-% 
-% 
 \begin{table}[t]
@@
 \end{tabular}
-
-\caption{Unit cell of Alt structure. Layer division, atom types and
-positions for the Alt structure. The structure unit cell was divided in
-six layers corresponding each one to atoms in different $z$ positions. The
-corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
-the corresponding number of layer.}
+\caption{Atomic positions in the unit cell of Alt structure. 
+}
 \label{tab:alt-unitcell}
@@
 C$_{16}$H$_{8}$-alt structures, being both noncentrosymmetric semi-infinite 2D
-carbon systems with 50\% hydrogenation in different arrangements. We recall
-that the Up structure has hydrogen atoms only on the upper side of the carbon
-sheet, while the Alt structure has alternating hydrogen atoms on the upper and
-bottom sides. Also, we take the hexagonal carbon lattice to be on the $xy$ plane
-for both structures, and the carbon-hydrogen bonds on the perpendicular $xz$
-plane, as depicted in Figs. \ref{fig:up-struc} and \ref{fig:alt-struc}. The
-coordinates for the Up and Alt unit cells of the structures are presented in
-Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
+carbon systems with 50\% hydrogenation in different arrangements. We recall that
+the Up structure has hydrogen atoms only on the upper side of the carbon sheet,
+while the Alt structure has alternating hydrogen atoms on the upper and bottom
+sides. Also, we take the hexagonal carbon lattice to be on the $xy$ plane for
+both structures, and the carbon-hydrogen bonds on the perpendicular $xz$ plane,
+as depicted in Figs. \ref{fig:up-struc} and \ref{fig:alt-struc}. The coordinates
+for the Up and Alt unit cells of the structures are presented in Tables 
+\ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
 
@@
 density functional theory in the local density approximation (DFT-LDA), with a
-planewave basis using the ABINIT code \cite{gonzeCPC09}.
-% 
-We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
-Gaussian pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit
-interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
-in Eq. \eqref{eq:mu}.
-% 
-The convergence parameters for the calculations of our results corresponding to
-the Up and Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting
-in LDA energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
-eigenvalues and matrix elements for the Up and Alt structures were calculated
-using 12802 $\mathbf{k}$ points and 14452 $\mathbf{k}$ points in the IBZ to
-integrate $\mu^{\mathrm{abcd}}(\go)$ and $\xi^{\rma\rmb}(\go)$ using the
-linearized analytic tetrahedron method (LATM).\cite{nastosPRB07} We neglect the
-anomalous velocity term $\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the
-crystal potential, in $\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to
-give small contribution to PSC.\cite{bhatPRL05} Therefore,
-$[\hat\bfv,\hat\bfS]=0$, and Eq.~\eqref{z.1} reduces to $\hat K^{\rma\rmb}=\hat
-v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$. Finally, the prime in the sum of
-Eq.~\eqref{eq:mu} is restricted to quasidegenerated conduction bands $c$ and
-$c'$ that are closer than 30 meV, where this value is both a typical laser-
-pulse energy width and the room-temperature energy.\cite{nastosPRB07}
-% 
-% It is known that the DFT with LDA approximation misestimates the energy band
-% gap of semiconductors. To correct this one has to include the many-body
-% interaction using i.e. the so-called GW approximation but this technique has a
-% very high computational cost and is out of the scope in this paper.
-% Nevertheless, DFT still remains a mainstream tool for calculating diverse
-% properties derived from the electronic band structure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
+Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
+pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
+needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
+\eqref{eq:mu}. The convergence parameters for the calculations of our results
+corresponding to the Up and Alt structures are cutoff energies of 40\,Ha and
+65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
+respectively. The energy eigenvalues and matrix elements for the Up and Alt
+structures were calculated using 12802 ${\mathbf k}$ points and 14452 ${\mathbf
+k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\omega)$ and
+$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ using the linearized analytic tetrahedron
+method (LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
+$\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
+potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
+give small contribution to PSC.\cite{bhatPRL05} Therefore, $[\hat{\mathbf
+v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat
+K^{\mathrm{a}\mathrm{b}}=\hat v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b}
+\hat v^\mathrm{a}$. Finally, the prime in the sum of Eq.~\eqref{eq:mu} is
+restricted to quasidegenerated conduction bands $c$ and $c'$ that are closer
+than 30 meV, where this value is both a typical laser- pulse energy width and
+the room-temperature energy.\cite{nastosPRB07}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 \includegraphics[width=\tama]{plots/2-vab-str-comp}
-\caption{$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ 
-  vs. $\hbar\go$, for the values of $\ga$ that maximize the signal. The low
-  energy regions for the Alt and Up structures start at the energy gap of each
-  structure, while in the high energy regions, the values of
-  $\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ are also very large. The bottom panel
-  corresponds to CdSe and GaAs. }
+\caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
+  vs. $\hbar\omega$, for the values of $\alpha$ that maximize the signal. The
+  low energy regions for the Alt and Up structures start at the energy gap of
+  each structure, while in the high energy regions, the values of
+  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large. The bottom
+  panel corresponds to CdSe and GaAs. }
 \label{fig:vab-str-comp}
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\go$ for the directions $\rma\rmb$, and for the
-angle $\ga$
-that maximizes the signal, for the Up  and Alt structures and for CdSe and
-GaAs, which are bulk systems shown for comparison.
-% 
-As expected from the delta function of Eq.~\eqref{eq:mu},
-$\calv^{\rma\rmb}(\go,\ga)$ rises right at the corresponding energy gap of each
-system. For the 2D structures, the spectrum covers two narrow energy regions
-with large values of response, while for bulk systems, the spectra covers a
-rather wide energy range, but with a much smaller response.
-% 
-For the Up structure, $\rma\rmb=yz$ and $\ga=35^\circ$ maximize the response,
-which means that an incoming beam of light with its electric field polarized at
-35$^\circ$ from the $x$ direction will induce electrons to move along $y$
-(parallel to the surface), with their spin polarized along $z$ (perpendicular to
-the surface), with the following speeds.
-% 
-Right at the energy onset, $\calv^{yz}(\go,\ga)=668$\,Km/s, a speed that remains
-almost constant for 65 meV, and then goes to zero. A second region is found
-above 1.946 eV, where there are two extreme values of the speed,
-$\calv^{yz}(\go,\ga)=266.3$ Km/s at $\hbar\go=1.954$\,eV, and
-$\calv^{\rma\rmb}(\go,\ga)=-241.4$ Km/s at $\hbar\go=1.958$\,eV; a positive
-(negative) $\calv^{\rma\rmb}(\go,\ga)$ means that the electrons move parallel
-(antiparallel) to the electric field.
-Likewise, for the Alt structure, we find that also $\rma\rmb=yz$ and
-$\ga=150^\circ$ maximizes the response, where two extreme values of
-$\calv^{\rmy\rmz}$ are found, one at  $\hbar\go=0.720$\,eV of
-$\calv^{\rmy\rmz}=-711.9$ Km/s, and the other at $\hbar\go=0.911$\,eV of
-$\calv^{\rmy\rmz}=-330.6$ Km/s.
+(\omega,\alpha)$ vs. $\hbar\omega$ for the directions $\mathrm{a}\mathrm{b}$,
+and for the angle $\alpha$ that maximizes the signal, for the Up  and Alt
+structures and for CdSe and GaAs, which are bulk systems shown for comparison.
+As expected from the delta function of Eq.~\eqref{eq:mu}, ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises right at the corresponding
+energy gap of each system. For the 2D structures, the spectrum covers two narrow
+energy regions with large values of response, while for bulk systems, the
+spectra covers a rather wide energy range, but with a much smaller response. For
+the Up structure, $\mathrm{a}\mathrm{b}=yz$ and $\alpha=35^\circ$ maximize the
+response, which means that an incoming beam of light with its electric field
+polarized at 35$^\circ$ from the $x$ direction will induce electrons to move
+along $y$ (parallel to the surface), with their spin polarized along $z$
+(perpendicular to the surface), with the following speeds. Right at the energy
+onset, ${\cal V}^{yz}(\omega,\alpha)=668$\,Km/s, a speed that remains almost
+constant for 65 meV, and then goes to zero. A second region is found above 1.946
+eV, where there are two extreme values of the speed, ${\cal
+V}^{yz}(\omega,\alpha)=266.3$ Km/s at $\hbar\omega=1.954$\,eV, and ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)=-241.4$ Km/s at
+$\hbar\omega=1.958$\,eV; a positive (negative) ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move parallel
+(antiparallel) to the electric field. Likewise, for the Alt structure, we find
+that also $\mathrm{a}\mathrm{b}=yz$ and $\alpha=150^\circ$ maximizes the
+response, where two extreme values of ${\cal V}^{\mathrm{y}\mathrm{z}}$ are
+found, one at  $\hbar\omega=0.720$\,eV of ${\cal
+V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at $\hbar\omega=0.911$\,eV
+of ${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.
 
-For the bulk structures, we calculate $\calv^{\rma\rmb}(\go)$ from
-Eq.~\eqref{eq:vab-w} by simply using $\bfgmu_{\mathrm{max}}$. For CdSe, we find
-that for $\hbar\go=0.844$\,eV, $\bfgmu_{\mathrm{max}}\to \mu^{zzzz}$, and
-$\calv^{\rmz\rmz}(\go)=-59.0$ Km/s, and for GaAs at $\hbar\go=2.324$\,eV,
-$\bfgmu_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and $\calv^{\rma\rma}(\go,\ga)=-28.7$\,Km/s, with
-$\rma=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis are
-taken along the standard cubic unit cell directions, [100], [010], and [001],
-respectively. In Table \ref{tab:vab-str-comp}, we present the comparison of
-$\calv^{\rma\rmb}(\go,\ga)$ for the 2D structures and bulk crystals.
-% 
-We remark that, as shown in the figure, 
-the 2D structures have maxima in 
-$\calv^{\rma\rmb}(\go;\ga)$  
-that are bigger
-than for the bulk crystals; in particular, the Alt
-structure gives a $\calv^{\rma\rmb}(\go;\ga)$ $\sim$12 times larger than
-that of CdSe and GaAs.
+For the bulk structures, we calculate ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$
+from Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$. For
+CdSe, we find that for $\hbar\omega=0.844$\,eV,
+$\boldsymbol{\mu}_{\mathrm{max}}\to \mu^{zzzz}$, and ${\cal
+V}^{\mathrm{z}\mathrm{z}}(\omega)=-59.0$ Km/s, and for GaAs at
+$\hbar\omega=2.324$\,eV, $\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$
+and ${\cal V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with
+$\mathrm{a}=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis
+are taken along the standard cubic unit cell directions, [100], [010], and
+[001], respectively. In Table \ref{tab:vab-str-comp}, we present the comparison
+of ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures and
+bulk crystals. We remark that, as shown in the figure, the 2D structures have
+maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ that are bigger than
+for the bulk crystals; in particular, the Alt structure gives a ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ $\sim$12 times larger than that of
+CdSe and GaAs.
 \begin{table}%[b]
@@
 \end{tabular}
-\caption{Comparison of the reported maximum values of
-$\mathcal{V}^{\mathrm{ab}}(\go,\ga)$ for the different structures and their
-corresponding polarization angle $\alpha$ and $\hbar\go$ energy values.
-}
+\caption{Comparison of the reported maximum values of $\mathcal{V}^{\mathrm{ab}}
+(\omega,\alpha)$ for the different structures and their corresponding
+polarization angle $\alpha$ and $\hbar\omega$ energy values. }
 \label{tab:vab-str-comp}
@@
 \includegraphics[width=\tama]{upplots/up-vsz-w1}
-\caption{For the Up structure, the top panel shows 
-$\calv_{\gs^\rmz}(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel
-shows $\gamma_{\gs^\rmz}(\go,\ga)$ (right scale, red line), and
-$\calv_{\gs^\rmz}(\go,\ga)$ (left scale, black line), vs. $\ga$, for
-$\hbar\go=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
+\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), and ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black line), vs. $\alpha$,
+for $\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
 \label{fig:up-vsz-w1}
@@
 \includegraphics[width=\tama]{upplots/up-vsz-w2}
-\caption{For the Up structure, the top panel shows $\calv_{\gs^\rmz} (\go,\ga)$
-vs. $\hbar\go$ and $\ga$, and the bottom panel shows $\gamma_{\gs^\rmz}
-(\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz} (\go,\ga)$ (left
-scale, black line), vs. $\ga$, for $\hbar\go=1.954$\,eV, i.e. along the
-highest ridge shown in the 3D plot. }
+\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
+$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), and ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale, black line), vs. $\alpha$,
+for $\hbar\omega=1.954$\,eV, i.e. along the highest ridge shown in the 3D plot.
+}
 \label{fig:up-vsz-w2}
@@
 
-In this subsection, we calculate $\calv_{\gs^\rmz}(\omega,\alpha)$, Eq.
-\eqref{eq:vs-mag}, for the case where the spin is fixed along $z$, i.e.
+In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$,
+Eq. \eqref{eq:vs-mag}, for the case where the spin is fixed along $z$, i.e.
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
-calculate $\gamma_{\gs^\rmz}(\go,\ga)$, Eq. \eqref{eq:gamma-ang}, which
-determines the direction along which the injected electrons move along the
+calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$, Eq. \eqref{eq:gamma-ang},
+which determines the direction along which the injected electrons move along the
 surface of  each structure. We mention that we have also made the analysis for
-the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$,
-finding similar qualitative results to those presented below.
-%
+the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$, finding
+similar qualitative results to those presented below.
 
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
-0.080\,eV$\leq\hbar\go\leq$0.096\,eV (similar energy range for the Up
+0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
 structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
-$0^\circ\leq\ga\leq 180^\circ$.
-% 
-We see a broad peak that maximizes at $\ga=35^{\circ}$ and $\hbar\go=
-0.084$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
-739.7$\,Km/s, and that the variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ as a function of $\ga$, which comes from the interplay of the
-$\bfgmu$ tensor components as multiplied by the  trigonometric functions of
+$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that maximizes at
+$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s, and that the
+variation of $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function
+of $\alpha$, which comes from the interplay of the $\boldsymbol{\mu}$ tensor
+components as multiplied by the  trigonometric functions of 
 Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and 
-165.4\,Km/s, for 0.084\,eV$\leq\hbar\go\leq$0.090\,eV. 
-% 
-In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.084$\,eV,
-thus following the ridge shown in the 3D plot of the top panel. 
-Also,
-we plot the
-corresponding velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$
-(right scale, red line),
-where it is very interesting to see that $\gamma_{\gs^z}(\omega,\alpha)$ is centered
-at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
-for the whole range of $\ga$. This results means that for $\hbar\go=0.084$ eV
-and for all values of $\ga$, the electrons, with the chosen spin pointing along
-$z$, will move at an angle of $\gamma_{\gs^\rmz}(\omega,\alpha) \sim
-64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
-speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
-% 
-Also, from Eq. \eqref{eq:gamma-par} we find that
-$\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha)=\ga = 64.56^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
-arrow), and that from Eq. \eqref{eq:gamma-perp},
-$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.50^\circ$,
-gives $\ga=154.50^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
-arrow); thus, at $\hbar\go=0.084$ eV, an incident field polarized at $\alpha
+165.4\,Km/s, for 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel,
+we show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left
+scale, black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge shown
+in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where it is
+very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at
+64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for the
+whole range of $\alpha$. This results means that for $\hbar\omega=0.084$ eV and
+for all values of $\alpha$, the electrons, with the chosen spin pointing along
+$z$, will move at an angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha) \sim
+64.5^{\circ}$ with respect to the $x$ direction, with the range of  high speeds
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure. Also,
+from Eq. \eqref{eq:gamma-par} we find that $\gamma^\parallel_{\sigma^\mathrm{z}}
+(\omega,\alpha)=\alpha = 64.56^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 631.1$\,Km/s (see green arrow), and that from Eq.
+\eqref{eq:gamma-perp}, $\gamma^\perp_{\sigma^\mathrm{z}} (\omega,\alpha) =
+\alpha-90^\circ=64.50^\circ$, gives $\alpha=154.50^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 191.5$ Km/s (see blue
+arrow); thus, at $\hbar\omega=0.084$ eV, an incident field polarized at $\alpha
 \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
@@
 Now, we analyze the results for the second energy range of the Up structure
-shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
-of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\go\leq$1.960\,eV and
-$0^\circ\leq\ga\leq 180^\circ$.
-% 
-We see two broad peaks that maximize at $\ga=35^{\circ}$ and $\hbar\go=
-1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
-193.5$\,Km/s, and at $\ga=35^{\circ}$ and $\hbar\go= 1.957$\,eV, with a value
-of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) = 170.6$\,Km/s. 
-% 
-We only analyze the highest  maximum in the bottom panel, where we  show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\ga$ (left scale,
-black line), at $\hbar\go= 1.954$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel. Also, we plot the corresponding
-velocity angle $\gamma_{\gs^\rmz}(\omega,\alpha)$ (right scale, red
-line),
-where in
-this case we see that the values of $\gamma_{\gs^z}(\omega,\alpha)$ have more
-dispersion, as a function of $\ga$, than for the lower energy range shown in
-the bottom panel of Fig.~\ref{fig:up-vsz-w1}.
-% 
-However, $\gamma_{\gs^z}(\omega,\alpha)\sim 77.8^\circ$ is constant from
-$\ga=0^\circ$ and up to $\ga\sim 85^\circ$. In this case, we find that
-$\gamma^\parallel_{\gs^\mathrm{z}}(\omega,\alpha)=\ga=78.0^\circ$, with
+shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of
+Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
+$0^\circ\leq\alpha\leq 180^\circ$. We see two broad peaks that maximize at
+$\alpha=35^{\circ}$ and $\hbar\omega= 1.954$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 193.5$\,Km/s, and at
+$\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. We only
+analyze the highest  maximum in the bottom panel, where we  show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
+black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge shown
+in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where in
+this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$ have more
+dispersion, as a function of $\alpha$, than for the lower energy range shown in
+the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
+$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is constant from
+$\alpha=0^\circ$ and up to $\alpha\sim 85^\circ$. In this case, we find that
+$\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (see green
 arrow), and that from Eq. \eqref{eq:gamma-perp},
-$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=167.8^\circ$, gives
-$\ga=77.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-65.6$\,Km/s (see blue arrow). 
-% 
-Thus, through the correct choice of $\hbar\go$ and $\alpha$ we could inject
-electrons, in this case with their spin polarized along $z$, which move parallel
-or perpendicular to the incident electric field, with finite speeds.
+$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
+gives $\alpha=77.8^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s (see blue
+arrow). Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
+inject electrons, in this case with their spin polarized along $z$, which move
+parallel or perpendicular to the incident electric field, with finite speeds.
 
 % the maxima for
-% $\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
+% $\hbar\omega=0.084$ eV and $\alpha=35^{\circ}$, with
 % $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
@@
 \includegraphics[width=\tama]{altplots/alt-vsz}
-\caption{For the Alt structure, the top panel shows $\calv_{\gs^\rmz}
-(\go,\ga)$ vs. $\hbar\go$ and $\ga$, and the bottom panel shows
-$\gamma_{\gs^\rmz} (\go,\ga)$ (right scale, red line), and $\calv_{\gs^\rmz}
-(\go,\ga)$ (left scale, black line), vs. $\ga$, for $\hbar\go=0.720$\,eV, i.e.
-along the ridge shown in the 3D plot.}
+\caption{For the Alt structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
+red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale, black
+line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge shown in
+the 3D plot.}
 \label{fig:alt-vsz}
@@
 
-We proceed to analyze the Alt structure, just as we did with the Up structure, but
-in this case, we only choose the lower energy range shown in the left central
-panel of Fig.~\ref{fig:vab-str-comp}. 
-% 
-In the top panel of Fig. \ref{fig:alt-vsz}, we plot
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
-0.715\,eV$\leq\hbar\go\leq$0.725\,eV and $0^\circ\leq\ga\leq 180^\circ$. We
-see a broad peak that maximizes at $\ga=150^{\circ}$ and $\hbar\go=
-0.720$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\go,\ga) =
-644.9$\,Km/s.
-% 
-In the bottom panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ vs. $\ga$ (left scale, black line), at $\hbar\go= 0.720$\,eV,
- thus following the highest ridge shown in the 3D plot of the top
-panel. Also, we plot the corresponding velocity angle $\gamma_{\gs^\rmz}
-(\omega,\alpha)$ (right scale, red line), where now we see that
-$\gamma_{\gs^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
-variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
-\alpha \leq 180^{\circ}$.
-% 
-In this case, we find that $\gamma^\parallel_{\gs^\mathrm{z}} (\omega,\alpha) =
-\ga = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
-450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
-$\gamma^\perp_{\gs^\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=110.0^\circ$,
-gives $\ga=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
-we could inject electrons with a fixed spin which move parallel or perpendicular
-to the incident electric field.
-
+We proceed to analyze the Alt structure, just as we did with the Up structure,
+but in this case, we only choose the lower energy range shown in the left
+central panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of Fig. 
+\ref{fig:alt-vsz}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+vs. 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
+180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
+$\hbar\omega= 0.720$\,eV, with a value of$\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 644.9$\,Km/s. In the bottom panel, we  show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
+black line), at $\hbar\omega= 0.720$\,eV, thus following the highest ridge shown
+in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
+$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), where now
+we see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$
+having variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq \alpha \leq 180^
+{\circ}$. In this case, we find that $\gamma^\parallel_{\sigma^\mathrm{z}}
+(\omega,\alpha) = \alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 450.05$\,Km/s (see green arrow), and that from Eq. 
+\eqref{eq:gamma-perp},$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha) = 
+\alpha-90^\circ=110.0^\circ$, gives $\alpha=20.0^\circ$, with $\mathcal{V}_
+{\sigma^{\mathrm{z}}} (\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as 
+for the Up structure, we could inject electrons with a fixed spin which move
+parallel or perpendicular to the incident electric field.
 % Again, for the cases in which the spin polarization is parallel to the
@@
 We calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. \eqref{eq:vv-mag})
-fixing the electron velocity direction, $\rma$, to the $x$ or $y$ direction
-along the surface of the Up and Alt structures. From Eqns. \eqref{eq:polar-ang}
-and \eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
-(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
-corresponding to the direction of the spin.
+fixing the electron velocity direction, $\mathrm{a}$, to the $x$ or $y$
+direction along the surface of the Up and Alt structures. From Eqns.
+\eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the polar,
+$\theta_{\mathrm{a}} (\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}}
+(\omega,\alpha)$, angles corresponding to the direction of the spin.
 
@@
 \caption{For the Up structure, we show
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$
-(left scale, black line),  
-$\theta_{\mathrm{a}} (\omega,\alpha)$
-(right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$,
-(right scale, blue line),
-vs. $\hbar\go$, for $\ga=35^\circ$, 
-and $\rma=x,y$.
-}
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x,y$. }
 \label{fig:up-vab-comp-rtp-1}
@@
 
-For the Up structure, we find once again that  $\ga=35^{\circ}$ maximizes the
+For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes the
 response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for $\rma=x,y$. 
-% 
-We see that for $\hbar\go=0.084$\,eV, the response has a maximum of
-$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=431.7$\,Km/s, with
-$\theta_{\mathrm{x}}(\omega,\alpha) = 42.5^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
+(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
+scale, blue line), vs. $\hbar\omega$, for $\mathrm{a}=x,y$. We see that for
+$\hbar\omega=0.084$\,eV, the response has a maximum of $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha)=431.7$\,Km/s, with $\theta_{\mathrm{x}}(\omega,\alpha) =
+42.5^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
 $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s, with
-$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and
-$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that the
-spin is directed upward the third Cartesian quadrant of the $xy$ plane when the
-electron moves along $x$, and is directed almost parallel to the $xy$ plane in
-the first quadrant when it moves along $y$. 
-% 
-Also, from this figure we have that when the electron moves along $x$, the spin
-direction is almost constant for all the energies across the peak of the
-response, having
-$42.5^{\circ}<\theta_{\mathrm{x}}(\omega,\alpha)<53.7^{\circ}$ and
-$208.3^{\circ}<\varphi_{\mathrm{x}}(\omega,\alpha)<215.7^{\circ}$, and when
-the electron moves along $y$, the spin polar angle has again small variations,
-$11.3^{\circ}< \theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the
-azimuthal angle has significant variations, $82.1^{\circ}<
-\varphi_{\mathrm{y}}(\omega,\alpha)<182.4^{\circ}$.
+$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and $\varphi_{\mathrm{y}}
+(\omega,\alpha) = 82.1^{\circ}$. This means that the spin is directed upward the
+third Cartesian quadrant of the $xy$ plane when the electron moves along $x$,
+and is directed almost parallel to the $xy$ plane in the first quadrant when it
+moves along $y$. Also, from this figure we have that when the electron moves
+along $x$, the spin direction is almost constant for all the energies across the
+peak of the response, having $42.5^{\circ}<\theta_{\mathrm{x}} (\omega,\alpha) <
+53.7^{\circ}$ and $208.3^{\circ}<\varphi_{\mathrm{x}} (\omega,\alpha) <
+215.7^{\circ}$, and when the electron moves along $y$, the spin polar angle has
+again small variations, $11.3^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) <
+13.9^{\circ}$, but the azimuthal angle has significant variations, $82.1^{\circ}
+< \varphi_{\mathrm{y}} (\omega,\alpha)<182.4^{\circ}$.
 
@@
 (\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for
-$\ga=35^\circ$, and $\rma=x,y$. }
+(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for
+$\alpha=35^\circ$, and $\mathrm{a}=x,y$. }
 \label{fig:up-vx-vy-w2}
@@
 In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ vs. $\hbar\go$, in the range where there are two local maxima
-at $\hbar\go=1.954$\,eV and $\hbar\go=1.957$\,eV.
-% 
-The former is the largest of the two, with
-$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
-$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and 
-$\varphi_{\mathrm{x}} (\omega,\alpha)=54.3^{\circ}$,
-for the electron moving along $x$, and
-$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s,
-$\theta_{\mathrm{y}} (\omega,\alpha)=49.8^{\circ}$, and 
-$\varphi_{\mathrm{y}} (\omega,\alpha)=51.9^{\circ}$
-for the electron moving along $y$.
-% 
-For the $\hbar\go=1.957$\,eV peak, we obtain 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and 
+(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there are two local
+maxima at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV. The former is the
+largest of the two, with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
+$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and $\varphi_{\mathrm{x}}
+(\omega,\alpha)=54.3^{\circ}$, for the electron moving along $x$, and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s, $\theta_{\mathrm{y}}
+(\omega,\alpha) = 49.8^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha) =
+51.9^{\circ}$ for the electron moving along $y$. For the $\hbar\omega=1.957$\,eV
+peak, we obtain $\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and
 $\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and
-$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s.
-We remark that these angles are almost
-constant for all the energy values across the peak of these two local maxima, for
-which the spin is directed upward in the first Cartesian quadrant of the $xy$
-plane when it moves along either $x$ or $y$ directions.
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and $\theta_{\mathrm{y}}
+(\omega,\alpha) = 129.3$, and $\varphi_{\mathrm{y}} (\omega,\alpha) = 230.7$,
+with $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s. We remark that
+these angles are almost constant for all the energy values across the peak of
+these two local maxima, for which the spin is directed upward in the first
+Cartesian quadrant of the $xy$ plane when it moves along either $x$ or $y$
+directions.
 
@@
 \includegraphics[width=\tama]{altplots/alt-vx-vy-w1}
-\caption{For the Alt structure, we show
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
-$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\go$, for $\ga=150^\circ$, and $\rma=x,y$. }
+\caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
+(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
+scale, blue line), vs. $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a} =
+x,y$. }
 \label{fig:alt-vx-vy-w1}
@@
 \caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\go$, for
-$\ga=150^\circ$, and $\rma=x,y$. }
+(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
+(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
+scale, blue line), vs. $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a} =
+x,y$. }
 \label{fig:alt-vx-vy-w2}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\go$ in two different ranges, and  for $\rma=x,y$. In this case,
-$\ga=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
-and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\ga$.
-% 
-In Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
-$\hbar\go=0.720$\,eV, with $\mathcal{V}_{\mathrm{x}}
-(\omega,\alpha) = 301.7$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) =
-44.5^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$,
-and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s, with
+$\hbar\omega$ in two different ranges, and  for $\mathrm{a} =x,y$. In this case,
+$\alpha=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
+and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\alpha$. In
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.720$\,eV,
+with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 301.7$\,Km/s,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 44.5^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$, and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s, with
 $\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. 
-% 
-Thus, the spin is directed upward the fourth Cartesian quadrant of the $xy$
-plane when the spin velocity is directed along $x$, and directed downward the
-second Cartesian quadrant when the spin velocity is directed along $y$.
-% 
-Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
-$\hbar\go=0.911$\,eV, with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) =
-276.3$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.3^{\circ}$, and
-$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s, with
-$\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin
-is directed downward the fourth Cartesian quadrant of the $xy$ plane when the
-spin velocity is directed along $x$, and directed downward the third Cartesian
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. Thus, the spin is
+directed upward the fourth Cartesian quadrant of the $xy$ plane when the spin
+velocity is directed along $x$, and directed downward the second Cartesian
+quadrant when the spin velocity is directed along $y$. Finally, in  Fig.
+\ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV, with
+$\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s, $\theta_{\mathrm{x}}
+(\omega,\alpha) = 154.6^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) =
+292.3^{\circ}$, and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s,
+with $\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin is
+directed downward the fourth Cartesian quadrant of the $xy$ plane when the spin
+velocity is directed along $x$, and directed downward the third Cartesian
 quadrant when the spin velocity is directed along $y$.
@@
 $y$; this effect does not seem to have been previously reported in this kind of
-structures.
-% 
-This SVI is very sensitive to the symmetry characteristics of the structures,
-presenting an anisotropic behavior. We found that the Up structure has
-the most intense response for the spin directed along $z$, resulting in 
-% 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s, and 
-% 
-for an energy of the incoming beam of 0.084\,eV. Also, the Alt structure
-has the most intense response when the spin moves along the $y$ direction,
-resulting in 
-% 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
-% 
-for an energy of the incoming beam of 0.720\,eV.
-% 
-The speed values obtained here are of the same order of magnitude
-as those of Ref.~\onlinecite{najmaiePRB03} in 
-unbiased semiconductor quantum well structures.
-The spin relaxation time in pure and doped graphene is long enough in the order
-from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} Then,
-according to our results, both are excellent candidates for the development of
-spintronics devices that require PSC due to the high spin velocity transport.
+structures. This SVI is very sensitive to the symmetry characteristics of the
+structures, presenting an anisotropic behavior. We found that the Up structure
+has the most intense response for the spin directed along $z$, resulting in
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s, and for an
+energy of the incoming beam of 0.084\,eV. Also, the Alt structure has the most
+intense response when the spin moves along the $y$ direction, resulting in
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for an energy of the
+incoming beam of 0.720\,eV. The speed values obtained here are of the same order
+of magnitude as those of Ref.~\onlinecite{najmaiePRB03} in unbiased
+semiconductor quantum well structures. The spin relaxation time in pure and
+doped graphene is long enough in the order from nanoseconds to milliseconds.
+\cite{wojtaszekPRB13,ertlerPRB09} Then, according to our results, both are
+excellent candidates for the development of spintronics devices that require PSC
+due to the high spin velocity transport.
 
@@
 This work has been supported by \emph{Consejo Nacional de Ciencia y
-Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
-R.Z.P. thanks CONACyT for scholarship support.
+Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930. R.Z.P. thanks CONACyT for
+scholarship support.
 \bibliography{article.bib}

### 2017-08-15 mu/article/article-review6-A.tex
Starting Anatoli's review.

%\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage{hyperref}   % use for hypertext links, including those to external 
                        % documents and URLs 
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
%\usepackage[inline]{showlabels}
% \input{/Users/bms/util/definitions}
%\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
\def\tama{10cm}
\raggedbottom           % don't add extra vertical space

\begin{document}

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\author{Bernardo S. Mendoza}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\author{Anatoli I. Shkrebtii}
\affiliation{University of Ontario, Institute of Technology,
Oshawa, ON, L1H 7L7, Canada}

\date{\today}

\begin{abstract}
We present a theoretical study of spin-velocity injection (SVI) of a pure spin current (PSC)
induced by  a linearly polarized light that impinges normally on the
surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D graphene structures. The first structure, hydrogenated at only one side, 
labeled $Up$ (also known as graphone), and the second, one labelled $Alt$, is 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both structures. We
analyze two possibilities: the first one  is by fixing the spin along a chosen
direction, and the resulting spin-velocity is calculated. Secondly,  we
choose the spin-velocity direction within (OR along?) the surface plane, and calculate its (which one) the spin-velocity injection speed
and spin orientation. This is done by changing the energy $\hbar\omega$ and
polarization angle $\alpha$  of the incoming  light. The results are calculated
within a full electronic band structure scheme using the Density Functional Theory (DFT) in the Local Density Approximation (LDA). The maxima of the spin-velocity speed are reached when
$\hbar\omega=0.084$\,eV and $\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and 645\,Km/s for Up and
Alt structures, respectively, when the spin points perpendicularly to the surface. Also,
the response is maximized by fixing the spin-velocity direction along a high
symmetry Cartesian axis, reaching a speed of 688\,Km/s with the spin  pointing
at 13$^\circ$ from the surface normal, the for Up, and 906\,Km/s and the spin
pointing at 60$^\circ$ from the surface normal, for the Alt. These speed values are significantly 
larger than those of bulk semiconductors, such as CdSe and GaAs, thus making the
hydrogenated graphene structures excellent candidates for spintronics
applications.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:introduction}

Spintronics is an emerging research field of electronics in which the
manipulation and transport of spin of electrons in a solid state materials  is crucial (central), adding a new degree of freedom to conventional charge
manipulation.\cite{wolfSC04,fabianAPS07} 
At present, there is an increasing interest in attaining the same level of
control over the transport of spin at micro- or nano-scales, as it has been done
for the flow of charge in typical 3D-bulk based electronic devices.\cite{awschalomNP2007} Several
semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
dattaAPL90,gotteNat16,pershinPRB08}, and some of them require spin polarized
electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
One of the difficulties  in achieving (creating) measurable  the of spin current and development of PSC based
semiconductor devices is the fact that the spin relaxation time in conventional 
semiconducting materials is short to enable the spin transport, thus resulting
in a non-observable spin current.\cite{murakamiSc03}
For PSC there is no net motion of charge; spin-up electrons move in a given
direction, while spin-down electrons travel in the opposite one. This effect can be due to one-photon absorption of linearly polarized light by a
semiconductor, with filled valence bands and empty conduction bands, illuminated
by light with photon energy larger than the energy gap. This phenomenon can
be due to spin injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04}
interference of two optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon
absorption of linearly polarized light\cite{bhatPRL05}. The last effect has been observed in
gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}

Graphene, an allotrope of carbon with hexagonal 2D lattice structure, demonstrates 
properties such as fractional quantum Hall effect at room temperature, excellent
thermal transport properties, excellent conductivity\cite{heerscheNat07} and
strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08}, being a
perfect platform  for two-dimension (2D) electronic systems; however, most
electronic applications are disabled by the absence of a semiconducting gap.
Recent studies demonstrate that a narrow band gap  can be opened in graphene by
applying an electric field,\cite{zhangN09} reducing the surface
area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
possibility to open the gap is by doping; this has been successfully achieved
using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
silicon,\cite{colettiPRB10} noble-metals,\cite{varykhalovPRB10} and
hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
Depending on the percentage of hydrogenation and spatial arrangements of
the hydrogen-carbon bonds, hydrogenated graphene demonstrates  different structural  
configurations and a tunable electron gap, as it has been proven in [1].
In this paper, we present two 50\% hydrogenated graphene noncentrosymmetric
structures, both presenting a discernible band gap. The first one, labelled as the Up structure (also known as graphone, see [2] and Refs therein), shown in
Fig. \ref{fig:up-struc}. Graphone has hydrogen atoms bonded to the carbon layer only on
the upper side of the structure, we consider here the magnetic isomer of graphone, with the so-called “chair” structure. In contrast,  the Alt structure, shown in Fig. 
\ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
the carbon sheet.\cite{zapataPSB2016}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\tama]{figures/upstruc2}
    \\
    \includegraphics[width=\tama]{figures/upstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Up
      structure along with the 
      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is also shown.
}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\tama]{figures/altstruc2}
    \\
    \includegraphics[width=\tama]{figures/altstruc1}
    \caption{Side (top panel) and top (bottom panel) views of the Alt
      structure along with the 
      $xyz$ directions. The dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell is also displayed.

}
    \label{fig:alt-struc}
\end{figure}

Using those structures, we address theoretically  the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light. Since wehave 2D structures, we do the analysis for two cases (not clear to me this sentence). The first case is by fixing the
spin of the electrons along vertical to the surface direction (?)$z$, , with the velocity
directed onto (is this parallel or not?) the surface of the structure in the $xy$ plane. In the second 
case we fix the spin velocity in the $x$ or $y$ direction and the resulting spin is then directed outward of the $xy$ plane. % $xyz$. (Do we need to repeat “Cartesian” many times?)
The SVI is an optical effect that quantifies the velocity, at which a PSC moves
along the direction $\bf{a}$ with the $\bf{a}$ components to be determined,  % ####???, $\mathrm{a}$ and 
with the spin of electron polarized
along the direction $\bf{b}$. % $\mathrm{b}$. One-photon absorption of linearly
polarized light produce an even distribution of electrons in $\mathbf{k}$
space, regardless of the symmetry of the material, resulting in a null
electrical current.\cite{bhatPRL05} Then, the electrons excited to the
conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
polarizations producing no net spin injection in centrosymmetric materials (?).\cite{bhatPRL05} If the
crystalline structure of the material is noncentrosymmetric, the spin
polarization injected at a given $\mathbf{k}$ point not necessarily
vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88}. Therefore, since the velocities
of electrons at opposite $\mathbf{k}$ points are opposite, a PSC will be
produced. Since both the structures presented here are noncentrosymmetric, they are
good candidates in which this effect can be induced.

This paper is organized as follows. In Section \ref{sec:theory} we present the
formalism and the main expressions  that describe PSC and SVI. In Section \ref{sec:results} we
describe the numerical details  and  discuss the corresponding SVI spectra for the
Up and Alt structures. Finally, we summarize our finding in
Section \ref{sec:conclusions}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  T H E O R Y  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theory} % (fold)
\label{sec:theory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we  summarize the theoretical approach, involved in 
calculation of the spin velocity
injection (SVI) resulting from the
pure spin current (PSC).

%%%BMSD
The operator that describes the electronic SVI is written as
\begin{align}\label{z.1}
\hat K^{\mathrm{a}\mathrm{b}}=\frac{1}{2}\left( \hat v^\mathrm{a} \hat S^\mathrm{b} 
+\hat  S^\mathrm{b} \hat v^\mathrm{a}\right) 
,
\end{align} 
where $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ 
is the velocity operator, with
$\hat {\mathbf r}$ 
%\end{document}
being the position operator and $\hat H_0$ the unperturbed
ground state Hamiltonian;
the Roman superscripts  indicate Cartesian coordinates. 
To obtain the expectation value of 
$\hat K^{\mathrm{a}\mathrm{b}}$, we use the length gauge for the perturbing
Hamiltonian, written as
\begin{align}\label{z.2}
\hat H_{\text{p}}=-e\hat{\mathbf r}\cdot{\mathbf E}(t)
,
\end{align}   
where the applied electric field of the laser is given by
\begin{align}\label{z.3}
{\mathbf E}(t)= {\mathbf E}(\omega)e^{-i\omega t} + {\mathbf E}^*(\omega)e^{i\omega t}
.
\end{align}
In order to 
calculate the response of the system to ${\mathbf E}(t)$, one needs to
take into account the excited coherent superposition
of the spin-split conduction bands inherent to the 
noncentrosymmetric 
semiconductors considered in this work.
%Although, this splitting is small [15,16], is required to obtain the
%correct results\cite{nastosPRB07}.
% The conduction bands in the 
% noncentrosymmetric  
% semiconductors  
% are spin split by a small amount,[15,16] typically
%   smaller than the energy width of the laser pulse, and so the pulse
%   excites a coherent superposition of the two conduction bands. Even
%   for very long pulses with narrow energy widths, dephasing effects
%   lead to an energy width of the bands large enough that spin-split
%   states can become quasi-degenerate. 
To include the coherence, we follow Ref.~\onlinecite{nastosPRB05} and
use a multiple
scale approach that solves the equation of motion for the single
particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
\begin{align}\label{z.4}
&\frac{\partial \rho_{cc'}({\mathbf k})}{\partial t} =
\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
{i \hbar^{2}}
\sum_{v}r^{\mathrm{a}}_{cv}({\mathbf k}) r^{\mathrm{b}}_{vc'}({\mathbf k})
\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k}) - i \epsilon} 
- 
\frac{1}{\omega - \omega_{cv}({\mathbf k}) + i \epsilon} \right)
,
\end{align}
where we assumed that the conduction bands $c$ and $c'$
are quasi-degenerate  states, and we take $\epsilon\to 0$ at the end of the
calculation.  The spin-splitting of the valence ($v$) bands is very
small, and is neglected throughout this work.\cite{nastosPRB07}
The matrix elements of any operator ${\cal O}$ are given by
${\cal O}_{nm}({\mathbf k})=\langle n{\mathbf k}|\hat{\cal O}| m{\mathbf k}\rangle$,
where 
$H_{0}|n{\mathbf k}\rangle = \hbar \omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ 
with $\hbar \omega_{n}({\mathbf k})$ being the energy of the
electronic band $n$ at point ${\mathbf k}$ in the irreducible Brillouin zone
(IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state, and 
$\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf k})-\omega_{m}({\mathbf k})$.
Using 
$\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$
for the expectation value of an observable $\mathcal{O}$, 
where $\mathrm{Tr}$ denotes the trace, we obtain
\begin{align}\label{z.5}
\mathcal{O} 
%=&
%\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c {\mathbf k} 
%| \hat{\rho} \hat{\mathcal{O}} |
%c{\mathbf k} \rangle \nonumber \\
=& 
\int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \rho_{cc'}({\mathbf k}) 
\mathcal{O}_{c'c}({\mathbf k}),
\end{align}
where we used 
the closure
relationship $\sum_{n}|n{\mathbf k}\rangle \langle n{\mathbf k}| = 1$,
where $n=v,c$,
and the fact that $\rho_{vn}({\mathbf k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. 
Therefore, 
using  Eqs. \eqref{z.4} and \eqref{z.5},
the
rate of change of $\mathcal{O}$,
$\dot{\mathcal{O}} 
=
\mathrm{Tr} \left( \dot{\hat\rho} \hat{\cal O} \right)
$,
 is given by
\begin{align}
\dot{\mathcal{O}} 
&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
\sum'_{cc'} \mathcal{O}_{c'c}({\mathbf k}) 
r^{\mathrm{a}}_{cv}({\mathbf k})  r^{\mathrm{b}}_{vc'}({\mathbf k})  
\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k})  - i\epsilon} - 
\frac{1}{\omega - \omega_{cv}({\mathbf k})  + i\epsilon} \right)
E^{\mathrm{a}}(\omega) E^{\mathrm{b*}}(\omega)
\label{eq:dotO}
.
\end{align}
The prime symbol $'$ in the sum means that
$c$ and $c'$ are quasi-degenerate states, and the sum only covers these states.

Replacing  $\hat{\cal O} \rightarrow \hat{K}^{\mathrm{ab}}$, in 
the above expression, one can show that
\begin{equation}
\dot{K}^{\mathrm{ab}}(\omega) =
\mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
\label{eq:dotk}
\end{equation}
where repeated Cartesians are summed, and 
\begin{equation}\label{eq:mu}
\begin{aligned}
\mu^{\mathrm{abcd}}  (\omega) &
=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}k}{8 \pi^{3}} \sum'_{vcc'}
  \delta(\omega-\omega_{cv}({\mathbf k}) 
\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}({\mathbf k}) 
\left(  
r^{\mathrm{c}}_{vc'}({\mathbf k})   
r^{\mathrm{d}}_{cv }({\mathbf k})  +
(c \leftrightarrow d)  
\right) 
\right]
\end{aligned}
\end{equation} 
is the pseudotensor that describes the rate of change of the  PSC process in
semiconductors. To derive what we presented above we used
$
K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k}) 
$
which follows from time-reversal invariance. 
Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
$\mu^{\mathrm{abcd}}(\omega) =
\mu^{\mathrm{abdc}}(\omega)$. 
We point out that Eq.~\eqref{eq:mu} 
is –identical to Eq. (3) of Bhat et al.\cite{bhatPRL05},
derived using the semiconductor optical Bloch equations.
Using the closure relation,
\begin{equation}
K^{\mathrm{ab}}_{cc'}({\mathbf k}) = \frac{1}{2}
\sum_{l=v,c}
\left(v^{\mathrm{a}}_{cl}({\mathbf k})S^{\mathrm{b}}_{lc'}({\mathbf k})
+S^{\mathrm{b}}_{cl}({\mathbf k}) v^{\mathrm{a}}_{lc'}({\mathbf k})
\right)
,
\label{eq:velspimatelem}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Spin velocity injection} % (fold)
%\label{sec:theory-pure_spin_current}
we define the spin velocity injection (SVI) as
\begin{equation}\label{eq:vab-w}
\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
\end{equation}  
which gives the velocity, along direction $a$, % $\mathrm{a}$, 
at which the spin
moves in a polarized state along direction $b$. % $\mathrm{b}$. 
The carrier injection rate
$\dot n(\omega)$ is written as\cite{nastosPRB05}
\begin{equation}
\dot{n}(\omega) =
\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega)
\label{eq:dotn}
\end{equation}
where the tensor 
\begin{equation}\label{eq:xi}
\begin{aligned}
\xi^{\mathrm{ab}}(\omega)
&
=
\frac{2\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}k}{8 \pi^{3}}
 \sum_{vc}
r^{\mathrm{a}}_{vc'}({\mathbf k})  
r^{\mathrm{b}}_{cv }({\mathbf k})  
\delta(\omega-\omega_{cv}({\mathbf k})), 
\end{aligned}
\end{equation}
is related to the imaginary part of the linear optical 
response tensor by
$\mathrm{Im}[\epsilon^{\mathrm{a}\mathrm{b}}(\omega)]=2\pi\epsilon_0\hbar\xi^{\mathrm{a}\mathrm{b}}(\omega)$.

The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify two very
important aspects of PSC. On one hand, we can fix the spin direction
along $\mathrm{b}$  
and calculate the resulting electron velocity.  
On the other hand, we can fix the velocity of the electron
along $\mathrm{b}$ and study the resulting direction along which the
spin is polarized.
To this end, the additional advantage of  2D structures, besides being
 noncentrosymmetric, is that we can use an incoming linearly
polarized  light
at normal incidence, and use the  direction of the polarized  electric
field to control ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.
Indeed, writing 
${\mathbf E}(\omega) = E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$,
where $\alpha$ is the polarization angle, we obtain from
 Eq. \eqref{eq:vab-w}
that
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= 
\frac{2}{\hbar\xi(\omega)}
\left(\mu^{\mathrm{abxx}}(\omega)\cos^{2}\alpha + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}\alpha + 
\mu^{\mathrm{abxy}}(\omega)\sin 2\alpha\right)
,
\label{eq:vab-aw}
\end{align}
\end{widetext}
for the structures chosen in this article,
$\xi^{\mathrm{xx}}(\omega)=\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and $\xi^{\mathrm{xy}}(\omega)=0$.
Next, we identify two options for ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.

\subsection{Fixing the spin polarization}\label{sec:theory-fixspin}

Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define (calculate?) the magnitude of
the electron velocity along the plane of the structure,
with the spin polarized along $\mathrm{b}$ direction as
\begin{equation}
\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)
\equiv
\sqrt{
[\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{equation}
and define the angle at which the velocity is directed on the $xy$ plane as
\begin{equation}
\gamma_{\sigma^\mathrm{b}} (\omega,\alpha)
=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)} \right)
.
\label{eq:gamma-ang}
\end{equation}
% where this angle is measured in the counter-clockwise direction from the
% positive $x$. 
We also define two special angles
\begin{equation}
\gamma_{\sigma^\mathrm{b}}^\parallel(\omega,\alpha) = \alpha, 
\label{eq:gamma-par} 
\end{equation}
and
\begin{equation}
\gamma_{\sigma^\mathrm{b}}^\perp(\omega,\alpha) = \alpha \pm 90^{\circ},
\label{eq:gamma-perp}
\end{equation}
corresponding to the electron velocity being parallel or perpendicular
to the incoming light polarization, 
respectively. The subscript $\sigma^\mathrm{b}$ denotes the spin along $\mathrm{b}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Fixing the electron velocity.}\label{sec:theory-fixvel}

Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$,
we define its corresponding magnitude as
\begin{align}
\mathcal{V}_{\mathrm{a}}(\omega,\alpha) \equiv 
\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
},
\label{eq:vv-mag}
\end{align}
from where we see that the spin would be oriented
in the $xyz$ system's coordinates
defined with a polar angle
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
= 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{\mathcal{V}_{\mathrm{a}}(\omega,\alpha)} \right),
 \quad 0 \leq \theta \leq \pi, 
\label{eq:polar-ang}
\end{align}
and an azimuthal angle
\begin{align}
\varphi_{\mathrm{a}} (\omega,\alpha)
=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\quad 0 \leq \varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   R E S U L T S   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results} % (fold)
\label{sec:results}

\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
\quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
\cline{2-4}
\quad type \qquad & $x$ & $y$ & $z$  \\
\hline
H & -0.61516 & -1.77416 &  0.73196 \\
H &  0.61518 &  0.35514 &  0.73175 \\
C & -0.61516 & -1.77264 & -0.49138 \\
C & -0.61516 & -0.35600 & -0.72316 \\
C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Atomic positions in the unit cell of Up structure as the structural input for our calculations (the primitive hexagonal unit cell contains two C and one H atoms, see Fig. 1). ADD EXTRA C atom
}
\label{tab:up-unitcell}
\end{table}
% 
% 
\begin{table}[t]
\center
\begin{tabular}{cccc}\\
\hline
\quad Atom \qquad & \multicolumn{3}{c}{Position (\AA)} \\
\cline{2-4}
\quad type \qquad & $x$ & $y$ & $z$  \\
\hline
H &  -0.61516 &  -1.42140 & \ 1.47237 \\
C &  -0.61516 &  -1.73300 & \ 0.39631 \\
C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
C &  -0.61516 &  -0.37396 &  -0.39632 \\
H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Atomic positions in the unit cell of Alt structure, which coincides with its primitive cell. 
}
\label{tab:alt-unitcell}
\end{table}

We present the calculated results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-Up  and
C$_{16}$H$_{8}$-Alt structures, both noncentrosymmetric 2D carbon
systems with 50\% hydrogenation, which are differently structurally arranged. We remind
that the Up structure has hydrogen atoms only on the upper side of the carbon
sheet, while the Alt structure has alternating hydrogen atoms on the upper and
bottom sides. We take the carbon lattice to be along the $xy$ plane
for both structures, and the carbon-hydrogen bonds are outward the plane, they are perpendicular to  $xz$
plane for the Up structure, as depicted in Figs. \ref{fig:up-struc}, and off the normal for the Alt structure \ref{fig:alt-struc}. The
coordinates for the Up and Alt unit cells of the structures are presented in
Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.

We calculated the self-consistent ground state and the Kohn-Sham states within 
density functional theory in the local density approximation (DFT-LDA), with a
planewave basis using the ABINIT code \cite{gonzeCPC09}.
% 
We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
Gaussian pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit
interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
in Eq. \eqref{eq:mu}.
% 
The convergence parameters for the calculations,  corresponding to
the Up and Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting
in LDA energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
eigenvalues and matrix elements for the Up and Alt structures were calculated
using 12802 ${\mathbf k}$ points and 14452 ${\mathbf k}$ points in the IBZ; to
integrate $\mu^{\mathrm{abcd}}(\omega)$ and $\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the
linearized analytic tetrahedron method (LATM) has been used.\cite{nastosPRB07} We neglect the
anomalous velocity term $\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the
crystal potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
give small contribution to PSC.\cite{bhatPRL05} Therefore,
$[\hat{\mathbf v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat K^{\mathrm{a}\mathrm{b}}=\hat
v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b} \hat v^\mathrm{a}$. Finally, the prime in the sum of
Eq.~\eqref{eq:mu} is restricted to quasi-degenerated conduction bands $c$ and
$c'$ that are closer than 30 meV, which  is both typical laser-
pulse energy width and the thermal room-temperature energy level broadening.\cite{nastosPRB07}
% 
% It is known that the DFT with LDA approximation misestimates the energy band
% gap of semiconductors. To correct this one has to include the many-body
% interaction using i.e. the so-called GW approximation but this technique has a
% very high computational cost and is out of the scope in this paper.
% Nevertheless, DFT still remains a mainstream tool for calculating diverse
% properties derived from the electronic band structure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{SVI: Spin velocity injection} % (fold)
\label{sec:res-spin_velocity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=\tama]{plots/2-vab-str-comp}
\caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
  vs. $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The largest velocity are at the low
  energy regions of the spectra for the Alt and Up structures, starting (going up?) at the energy gap of each
  structure. In the high energy regions, the values of
  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to the 3D case of CdSe and GaAsThe, shown at the bottom panel . } 
\label{fig:vab-str-comp}
\end{figure}

In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
(\omega,\alpha)$ vs. $\hbar\omega$ for the directions $\mathrm{a}\mathrm{b}$ (confusing to me), and for the
angle $\alpha$, at which the signal is 
maximized , for the Up  and Alt structures, and for CdSe and
GaAs bulk systems, shown for comparison.
% 
As expected from Eq.~\eqref{eq:mu},
${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises from zero right at the corresponding energy gap of each
system. For the 2D structures considered, the spectrum contains two narrow energy regions
with strong response, while for the bulk systems, the spectra covers a
rather wide energy range, but with a much weaker response.
% 
For the Up structure, at $\mathrm{a}\mathrm{b}=yz$ and $\alpha=35^\circ$ the response is maximized,
which means that an incoming light with its electric field polarized at
35$^\circ$ from the $x$ direction will induce electrons to move along $y$
(parallel to the surface), with their spin polarized along $z$ (perpendicular to
the surface). The corresponding speeds are the following:
% 
Right at the energy onset, ${\cal V}^{yz}(\omega,\alpha)=668$\,Km/s, remains
almost constant for 65 meV, and then decreases to zero. A second region with high velocity is 
above 1.946 eV with two, opposite in sign, maxima of the speed:
${\cal V}^{yz}(\omega,\alpha)=266.3$ Km/s at $\hbar\omega=1.954$\,eV, and
${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)=-241.4$ Km/s at $\hbar\omega=1.958$\,eV; a positive
(negative) ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move parallel
(antiparallel) to the electric field.
Likewise, for the Alt structure, we also find that $\mathrm{a}\mathrm{b}=yz$ and
$\alpha=150^\circ$ maximizes the response, where two extreme values of
${\cal V}^{\mathrm{y}\mathrm{z}}$ are found, one at  $\hbar\omega=0.720$\,eV of
${\cal V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at $\hbar\omega=0.911$\,eV of
${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.

For the bulk structures, we calculate ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ from
Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$. For CdSe, we find
that for $\hbar\omega=0.844$\,eV, $\boldsymbol{\mu}_{\mathrm{max}}\to \mu^{zzzz}$, and
${\cal V}^{\mathrm{z}\mathrm{z}}(\omega)=-59.0$ Km/s, and for GaAs at $\hbar\omega=2.324$\,eV,
$\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and ${\cal V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with
$\mathrm{a}=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis are
taken along the standard cubic unit cell directions, [100], [010], and [001],
respectively. In Table \ref{tab:vab-str-comp}, we compare 
${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures considered and bulk crystals.
% 
We stress that, as shown in the figure, for 
the 2D structures have maxima in 
${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$  
are higher
than for the bulk crystals. In particular, the Alt
structure demonstrates a ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than
that of CdSe and GaAs.
\begin{table}%[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
System \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& type & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
$Up$    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
      &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
      &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
$Alt$   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
      &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
CdSe  & bulk & --    & 0.844  & $\mathrm{zz}$ &  -59.0 \\
GaAs  & bulk & --    & 2.324  & $\mathrm{xx}$ &  -28.7 \\
\hline
\end{tabular}
\caption{Comparison of the reported maximum values of
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the different structures and their
corresponding polarization angle $\alpha$ and energy $\hbar\omega$ .
}
\label{tab:vab-str-comp}
\end{table}

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vsz-w1}
\caption{Color online. For the Up structure, the top panel shows 
${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ SvsS. $\hbar\omega$ and $\alpha$, and the bottom panel
shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line, long dashes?), and
${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid line?), $vs$. $\alpha$, for
$\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
\label{fig:up-vsz-w1}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vsz-w2}
\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows $\gamma_{\sigma^\mathrm{z}}
(\omega,\alpha)$ (right scale, red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left
scale, black solid line), vs. $\alpha$, for $\hbar\omega=1.954$\,eV, i.e. along the
highest ridge shown in the 3D plot. }
\label{fig:up-vsz-w2}
\end{figure}

In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$, Eq.
\eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
directed perpendicularly to the surface of the Up and Alt structures. Also, we
calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ from Eq. \eqref{eq:gamma-ang}, which
determines the direction  of the injected electrons movement along the
surface of  each structure. We mention that we have also  analyzed 
the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$,
finding similar qualitative results to those presented below.
%

\subsubsection{Up structure}\label{up:fs}

In the top panel of Fig. \ref{fig:up-vsz-w1}, we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
$0^\circ\leq\alpha\leq 180^\circ$.
% 
We see a broad peak that reaches the maximum of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
739.7$\,Km/s at $\alpha=35^{\circ}$ and $\hbar\omega=
0.084$\,eV,  The variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ as a function of $\alpha$, which comes from the interplay of the
$\boldsymbol{\mu}$ tensor components as multiplied by the  trigonometric functions of
Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and
165.4\,Km/s, for 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. 
% 
In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ $vs.$ $\alpha$ (left scale, black line), at $\hbar\omega= 0.084$\,eV,
thus following the ridge in the 3D plot of the top panel. 
Also,
we plot the
corresponding velocity angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$
(right scale, red line),
where it is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
for the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
and for all values of $\alpha$, the electrons, with the chosen spin pointing along
$z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha) \sim
64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
% 
Also, from Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
gives $\alpha=154.50^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
arrow). Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at $\alpha
\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
polarized along $z$, which move parallel or perpendicular to the incident
electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.

Now, we analyze the results for the second energy range of the Up structure
shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
$0^\circ\leq\alpha\leq 180^\circ$.
% 
We see two broad peaks that maximize at $\alpha=35^{\circ}$ and $\hbar\omega=
1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
193.5$\,Km/s, and at $\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value
of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. 
% 
We only analyze the highest  maximum in the bottom panel, where we  show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge shown
in the 3D plot of the top panel. Also, we plot the corresponding
velocity angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red
line),
where in
this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$ have more
dispersion, as a function of $\alpha$, than for the lower energy range shown in
the bottom panel of Fig.~\ref{fig:up-vsz-w1}.
% 
However, $\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
$\alpha=0^\circ$ up to $\alpha\sim 85^\circ$. In this case, we find that
$\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (as indicated by green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$, gives
$\alpha=77.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
65.6$\,Km/s (see blue arrow). 
% 
Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could inject
electrons, in this case with their spin polarized along $z$, which move parallel
or perpendicular to the incident electric field, with finite speeds (what does “finite” mean?).

% the maxima for
% $\hbar\omega=0.084$ eV and $\alpha=35^{\circ}$, with
% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
% $\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
% $\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.

\begin{figure}[tb]
\centering
\includegraphics[width=\tama]{altplots/alt-vsz}
\caption{Color online. For the Alt structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), and ${\cal V}_{\sigma^\mathrm{z}}
(\omega,\alpha)$ (left scale, black line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e.
along the ridge shown in the 3D plot.}
\label{fig:alt-vsz}
\end{figure}

\subsubsection{Alt structure}

We proceed to analyze the Alt structure, just as we did with the Up structure, but
in this case, we only choose the lower energy range shown in the left central
panel of Fig.~\ref{fig:vab-str-comp}. 
% 
In the top panel of Fig. \ref{fig:alt-vsz}, we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq 180^\circ$. We
see a broad peak that maximizes at $\alpha=150^{\circ}$ and $\hbar\omega=
0.720$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
644.9$\,Km/s.
% 
In the bottom panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ vs. $\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV,
 thus following the highest ridge shown in the 3D plot of the top
panel. Also, we plot the corresponding velocity angle $\gamma_{\sigma^\mathrm{z}}
(\omega,\alpha)$ (right scale, red line), where now we see that
$\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
In this case, we find that $\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
gives $\alpha=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
we could inject electrons with a fixed spin, which moves parallel or perpendicular
to the incident electric field.

% Again, for the cases in which the spin polarization is parallel to the
% surface the maximum values are
% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 297.8$ Km/s and
% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$ Km/s,
% corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
% $\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
% $\alpha=150^{\circ}$, where the plots are not presented.

\subsection{Fixing the electron velocity} 
\label{sec:res-fixvel}

Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. \eqref{eq:vv-mag})
after fixing the electron velocity direction, $\mathrm{a}$, to the $x$ or $y$ direction
along the surface of the Up and Alt structures. From Eqns. \eqref{eq:polar-ang}
and \eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
corresponding to the direction of the injected (?) spin.

\subsubsection{Up structure}

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vx-vy-w1}
\caption{For the Up structure, we show
$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$
(left scale, black line),  
$\theta_{\mathrm{a}} (\omega,\alpha)$
(right scale, red line), and
$\varphi_{\mathrm{a}} (\omega,\alpha)$,
(right scale, blue line),
vs. $\hbar\omega$, for $\alpha=35^\circ$, 
and $\mathrm{a}=x$ and $\mathrm{a}=y$.
}
\label{fig:up-vab-comp-rtp-1}
\end{figure}

For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes the
response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot $\mathcal{V}_{\mathrm{a}}
(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for $\mathrm{a}=x,y$. 
% 
We see that for $\hbar\omega=0.084$\,eV, the response has a maximum of
$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=431.7$\,Km/s at
$\theta_{\mathrm{x}}(\omega,\alpha) = 42.5^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s at
$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and
$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that the
spin is directed upward the third Cartesian quadrant of the $xy$ plane when the
electron moves along $x$, and is almost parallel to the $xy$ plane in
the first Cartesian quadrant when it moves along $y$. 
% 
Also from this figure, we see that when the electron moves along $x$, the spin
direction is almost constant for all the energies across the peak of the
response, having
$42.5^{\circ}<\theta_{\mathrm{x}}(\omega,\alpha)<53.7^{\circ}$ and
$208.3^{\circ}<\varphi_{\mathrm{x}}(\omega,\alpha)<215.7^{\circ}$. When
the electron moves along $y$, the spin polar angle has again small variations,
$11.3^{\circ}< \theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the
azimuthal angle varies significantly, $82.1^{\circ}<
\varphi_{\mathrm{y}}(\omega,\alpha)<182.4^{\circ}$.

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{upplots/up-vx-vy-w2}
\caption{For the Up structure we show $\mathcal{V}_{\mathrm{a}}
(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for
$\alpha=35^\circ$, and $\mathrm{a}=x,y$. }
\label{fig:up-vx-vy-w2}
\end{figure}
In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there two local maxima with opposite sign
at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV occur.
% 
The first is the largest of the two, with
$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and 
$\varphi_{\mathrm{x}} (\omega,\alpha)=54.3^{\circ}$,
for the electron moving along $x$; and
$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s,
$\theta_{\mathrm{y}} (\omega,\alpha)=49.8^{\circ}$, and 
$\varphi_{\mathrm{y}} (\omega,\alpha)=51.9^{\circ}$
for the electron moving along $y$.
% 
For the peak at $\hbar\omega=1.957$\,eV, we obtain 
$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and 
$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with 
$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and
$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$; and
$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with 
$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s.
We remark that these angles are almost
constant for all the energy values across the peak of these two local maxima, for
which the spin is directed upward in the first Cartesian quadrant of the $xy$
plane when it (who?) moves along either $x$ or $y$ directions.

\subsubsection{Alt structure}

\begin{figure}[tb]
\centering
\includegraphics[width=\tama]{altplots/alt-vx-vy-w1} % I believe that all the similar captions
% should be modified, one possible version is below
\caption{The Alt structure: the velocity 
$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar angle 
$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the azimuthal angle
$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are shown. }
\label{fig:alt-vx-vy-w1}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\tama]{altplots/alt-vx-vy-w2}   % Change the captions accordingly the above
\caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for
$\alpha=150^\circ$, and $\mathrm{a}=x,y$. }
\label{fig:alt-vx-vy-w2}
\end{figure}

In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2}, we plot
$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
$\hbar\omega$ in two different ranges, and  for $\mathrm{a}=x,y$. In this case,
$\alpha=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\alpha$.
% 
In Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
(\omega,\alpha) = 301.7$\,Km/s is at
$\hbar\omega=0.720$\,eV , $\theta_{\mathrm{x}} (\omega,\alpha) =
44.5^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$;
and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
 at $\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. 
% 
Thus, the spin is directed upward the fourth Cartesian quadrant of the $xy$
plane when the spin velocity is directed along $x$, while it is directed downward the
second Cartesian quadrant when the spin velocity is directed along $y$.
% 
Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
$\hbar\omega=0.911$\,eV at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) =
276.3$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.3^{\circ}$, and
$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s at 
$\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin
is directed downward the fourth Cartesian quadrant of the $xy$ plane when the
spin velocity is directed along $x$, while is directed downward the third Cartesian
quadrant when the spin velocity is directed along $y$.

\section{Conclusions} % (fold)
\label{sec:conclusions}

We reported the results of an \emph{ab initio} calculations for the spin velocity injection (SVI) due to the one-photon
absorption of the linearly polarized light in the Up and Alt 2D 50\% hydrogenated
graphene structures. Different possible arrangements of the of the spin injection have been considered: we made the calculations for the cases when the spin is
polarized in $z$ direction or when the velocity is directed along $x$ or
$y$. To the best of our knowledge, this effect  has been previously reported in this  2D partially hydrogenated 
structures.
% 
We have shown that the  SVI demonstrates an anisotropic behavior, which is very sensitive to the symmetry of the structures of interest. We have found that the Up structure shows
the strongest response for the spin directed along $z$, resulting in the velocity 
% 
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s 
% 
for the incoming photon energy of 0.084\,eV. Also, the Alt structure
has the strongest response when the spin moves along $y$ direction,
resulting in 
% 
$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
% 
for the incoming photon energy of 0.720\,eV.
% 
The speed values obtained here are of the same order of magnitude
as those of Ref.~\onlinecite{najmaiePRB03} in 
unbiased semiconductor quantum well structures, while they are of order of magnitude 
higher compared to 3D bulk materials.
The spin relaxation time in pure and doped graphene is long enough in the order
from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} Therefore,
according to our results, due to the high spin velocity transport both structures considered are the excellent candidates for the development of
spintronics devices that require pure spin current (PSC).

\section{Acknowledgment} % (fold)

This work has been supported by \emph{Consejo Nacional de Ciencia y
Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
R.Z.P. thanks CONACyT for scholarship support.
\bibliography{article.bib}

\end{document}

### 2017-08-15 mu/article/make-strucs/arrows1.tex
Starting Anatoli's review.

\documentclass{article}

\usepackage{tikz}
\usepackage{amsmath}

\pagestyle{empty}

\begin{document}
\thispagestyle{empty}

\begin{figure}
\begin{tikzpicture}
\draw [fill=white,white] (-0.8,-0.6) rectangle (2.6,1.7);
\draw[line width=0.5mm, ->] (0.25,0.00) -- (1.00,0.00)   node[anchor = west]  {\Large{\textbf{x [010]}}};
\draw[line width=0.5mm, ->] (0.00,0.25) -- (0.00,1.00)   node[anchor = south] {\Large{\textbf{y [100]}}};
\draw            (0.00,0.00)    (-0.17,-0.17) node[anchor = north east] {\Large{\textbf{z}}};
\draw[line width=0.5mm] (0,0) circle [radius=0.25];
\draw[line width=0.5mm, fill=black] (0,0) circle [radius=0.05];
\end{tikzpicture}
\end{figure}

\end{document}
0.17

### 2017-08-15 mu/article/make-strucs/arrows2.tex
Starting Anatoli's review.

--- 2017-08-15 mu/article/make-strucs/arrows1.tex
@@
 \usepackage{amsmath}
-
 \pagestyle{empty}
-
 \begin{document}
@@
 \draw [fill=white,white] (-0.8,-0.6) rectangle (2.6,1.7);
-\draw[line width=0.5mm, ->] (0.25,0.00) -- (1.00,0.00)   node[anchor = west]  {\Large{\textbf{x [010]}}};
-\draw[line width=0.5mm, ->] (0.00,0.25) -- (0.00,1.00)   node[anchor = south] {\Large{\textbf{y [100]}}};
-\draw            (0.00,0.00)    (-0.17,-0.17) node[anchor = north east] {\Large{\textbf{z}}};
+\draw[line width=0.5mm, ->] (0.25,0.00) -- (1.00,0.00)   node[anchor = west]  {\Large{\textbf{x [100]}}};
+\draw[line width=0.5mm, ->] (0.00,0.25) -- (0.00,1.00)   node[anchor = south] {\Large{\textbf{z [001]}}};
+\draw            (0.00,0.00)    (-0.17,-0.17) node[anchor = north east] {\Large{\textbf{y}}};
 \draw[line width=0.5mm] (0,0) circle [radius=0.25];
-\draw[line width=0.5mm, fill=black] (0,0) circle [radius=0.05];
+\draw[line width=0.5mm, -] (-0.17,0.17)  -- (0.17,-0.17);
+\draw[line width=0.5mm, -] (-0.17,-0.17) -- (0.17,0.17);
 \end{tikzpicture}
@@
 \end{document}
-0.17

### 2017-08-15 mu/alt/alt-scripts/alt-vab-rtp.sh

@@ -1,5 +1,6 @@
 #/bin/bash
 
+
 an=150
 kp=14452
 ec=65

### 2017-08-15 mu/article/figures/makefigs.sh

@@ -1,26 +1,0 @@
-#!/bin/bash
-
-pdflatex arrows1.tex
-rmtex arrows1.
-pdfcrop arrows1.pdf arrows1.pdf
-
-pdflatex arrows2.tex
-rmtex arrows2.
-pdfcrop arrows2.pdf arrows2.pdf
-
-pdflatex altstruc1.tex
-rmtex altstruc1.
-pdfcrop altstruc1.pdf altstruc1.pdf
-
-pdflatex altstruc2.tex
-rmtex altstruc2.
-pdfcrop altstruc2.pdf altstruc2.pdf
-
-pdflatex upstruc1.tex
-rmtex upstruc1.
-pdfcrop upstruc1.pdf upstruc1.pdf
-
-pdflatex upstruc2.tex
-rmtex upstruc2.
-pdfcrop upstruc2.pdf upstruc2.pdf
-

### 2017-08-15 mu/article/makeplots.sh

@@ -1,5 +1,0 @@
-#!/bin/bash
-
-mpplotlin.sh plots/vab-str-comp.g
-mv plots/fig.pdf plots/vab-str-comp
-

### 2017-08-17 mu/article/article-review6-Anatoli.tex
Made Anatoli's changes.

--- 2017-08-15 mu/article/article-review6-A.tex
@@
 \begin{abstract}
-We present a theoretical study of spin-velocity injection (SVI) of a pure spin current (PSC)
-induced by  a linearly polarized light that impinges normally on the
-surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D graphene structures. The first structure, hydrogenated at only one side, 
-labeled $Up$ (also known as graphone), and the second, one labelled $Alt$, is 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both structures. We
-analyze two possibilities: the first one  is by fixing the spin along a chosen
-direction, and the resulting spin-velocity is calculated. Secondly,  we
-choose the spin-velocity direction within (OR along?) the surface plane, and calculate its (which one) the spin-velocity injection speed
-and spin orientation. This is done by changing the energy $\hbar\omega$ and
-polarization angle $\alpha$  of the incoming  light. The results are calculated
-within a full electronic band structure scheme using the Density Functional Theory (DFT) in the Local Density Approximation (LDA). The maxima of the spin-velocity speed are reached when
-$\hbar\omega=0.084$\,eV and $\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
-$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and 645\,Km/s for Up and
-Alt structures, respectively, when the spin points perpendicularly to the surface. Also,
-the response is maximized by fixing the spin-velocity direction along a high
+We present a theoretical study of spin-velocity injection (SVI) of a pure spin
+current (PSC) induced by  a linearly polarized light that impinges normally on
+the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D
+graphene structures. The first structure, hydrogenated at only one side,
+labeled $Up$ (also known as graphone), and the second, one labelled $Alt$, is
+25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
+structures. We analyze two possibilities: the first one  is by fixing the spin
+along a chosen direction, and the resulting spin-velocity is calculated.
+Secondly,  we choose the spin-velocity direction within (OR along?) the surface
+plane, and calculate its (which one) the spin-velocity injection speed and spin
+orientation. This is done by changing the energy $\hbar\omega$ and polarization
+angle $\alpha$  of the incoming  light. The results are calculated within a
+full electronic band structure scheme using the Density Functional Theory (DFT)
+in the Local Density Approximation (LDA). The maxima of the spin-velocity speed
+are reached when $\hbar\omega=0.084$\,eV and $\alpha=35^\circ$ for the Up
+structure, and $\hbar\omega=0.720$\,eV and $\alpha=150^\circ$ for the Alt
+geometry. We find a speed of 668\,Km/s and 645\,Km/s for Up and Alt structures,
+respectively, when the spin points perpendicularly to the surface. Also, the
+response is maximized by fixing the spin-velocity direction along a high
 symmetry Cartesian axis, reaching a speed of 688\,Km/s with the spin  pointing
 at 13$^\circ$ from the surface normal, the for Up, and 906\,Km/s and the spin
-pointing at 60$^\circ$ from the surface normal, for the Alt. These speed values are significantly 
-larger than those of bulk semiconductors, such as CdSe and GaAs, thus making the
-hydrogenated graphene structures excellent candidates for spintronics
-applications.
+pointing at 60$^\circ$ from the surface normal, for the Alt. These speed values
+are significantly larger than those of bulk semiconductors, such as CdSe and
+GaAs, thus making the hydrogenated graphene structures excellent candidates for
+spintronics applications.
 \end{abstract}
@@
 Spintronics is an emerging research field of electronics in which the
-manipulation and transport of spin of electrons in a solid state materials  is crucial (central), adding a new degree of freedom to conventional charge
-manipulation.\cite{wolfSC04,fabianAPS07} 
-At present, there is an increasing interest in attaining the same level of
-control over the transport of spin at micro- or nano-scales, as it has been done
-for the flow of charge in typical 3D-bulk based electronic devices.\cite{awschalomNP2007} Several
-semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
+manipulation and transport of spin of electrons in a solid state materials  is
+crucial (central), adding a new degree of freedom to conventional charge
+manipulation.\cite{wolfSC04,fabianAPS07} At present, there is an increasing
+interest in attaining the same level of control over the transport of spin at
+micro- or nano-scales, as it has been done for the flow of charge in typical
+3D-bulk based electronic devices.\cite{awschalomNP2007} Several semiconductor
+spintronics devices have been proposed \cite{majumdarAPL06,
 dattaAPL90,gotteNat16,pershinPRB08}, and some of them require spin polarized
-electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
-One of the difficulties  in achieving (creating) measurable  the of spin current and development of PSC based
-semiconductor devices is the fact that the spin relaxation time in conventional 
-semiconducting materials is short to enable the spin transport, thus resulting
-in a non-observable spin current.\cite{murakamiSc03}
-For PSC there is no net motion of charge; spin-up electrons move in a given
-direction, while spin-down electrons travel in the opposite one. This effect can be due to one-photon absorption of linearly polarized light by a
-semiconductor, with filled valence bands and empty conduction bands, illuminated
-by light with photon energy larger than the energy gap. This phenomenon can
-be due to spin injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04}
-interference of two optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon
-absorption of linearly polarized light\cite{bhatPRL05}. The last effect has been observed in
-gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
-arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
+electrical current \cite{awschalomSSBM13} or pure spin current (PSC). One of
+the difficulties  in achieving (creating) measurable  the of spin current and
+development of PSC based semiconductor devices is the fact that the spin
+relaxation time in conventional semiconducting materials is short to enable the
+spin transport, thus resulting in a non-observable spin
+current.\cite{murakamiSc03} For PSC there is no net motion of charge; spin-up
+electrons move in a given direction, while spin-down electrons travel in the
+opposite one. This effect can be due to one-photon absorption of linearly
+polarized light by a semiconductor, with filled valence bands and empty
+conduction bands, illuminated by light with photon energy larger than the
+energy gap. This phenomenon can be due to spin injection,\cite{malPRB03} Hall
+Effects,\cite{sinovaPRB04} interference of two optical beams,\cite{bhatPRL00,
+najmaiePRB03} or one photon absorption of linearly polarized
+light\cite{bhatPRL05}. The last effect has been observed in gallium arsenide
+(GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium arsenide
+(AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
 
-Graphene, an allotrope of carbon with hexagonal 2D lattice structure, demonstrates 
-properties such as fractional quantum Hall effect at room temperature, excellent
-thermal transport properties, excellent conductivity\cite{heerscheNat07} and
-strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08}, being a
-perfect platform  for two-dimension (2D) electronic systems; however, most
-electronic applications are disabled by the absence of a semiconducting gap.
-Recent studies demonstrate that a narrow band gap  can be opened in graphene by
-applying an electric field,\cite{zhangN09} reducing the surface
-area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
-possibility to open the gap is by doping; this has been successfully achieved
-using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
-silicon,\cite{colettiPRB10} noble-metals,\cite{varykhalovPRB10} and
-hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
-Depending on the percentage of hydrogenation and spatial arrangements of
-the hydrogen-carbon bonds, hydrogenated graphene demonstrates  different structural  
-configurations and a tunable electron gap, as it has been proven in [1].
-In this paper, we present two 50\% hydrogenated graphene noncentrosymmetric
-structures, both presenting a discernible band gap. The first one, labelled as the Up structure (also known as graphone, see [2] and Refs therein), shown in
-Fig. \ref{fig:up-struc}. Graphone has hydrogen atoms bonded to the carbon layer only on
-the upper side of the structure, we consider here the magnetic isomer of graphone, with the so-called “chair” structure. In contrast,  the Alt structure, shown in Fig. 
-\ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
-the carbon sheet.\cite{zapataPSB2016}
+Graphene, an allotrope of carbon with hexagonal 2D lattice structure,
+demonstrates properties such as fractional quantum Hall effect at room
+temperature, excellent thermal transport properties, excellent
+conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
+novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
+electronic systems; however, most electronic applications are disabled by the
+absence of a semiconducting gap. Recent studies demonstrate that a narrow band
+gap  can be opened in graphene by applying an electric field,\cite{zhangN09}
+reducing the surface area,\cite{hanPRL07} or applying uniaxial
+strain.\cite{niACSN08} Another possibility to open the gap is by doping; this
+has been successfully achieved using nitrogen,\cite{weiNL2009} boron-
+nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-
+metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
+samarakoonACSN10} Depending on the percentage of hydrogenation and spatial
+arrangements of the hydrogen-carbon bonds, hydrogenated graphene demonstrates
+different structural configurations and a tunable electron gap, as it has been
+proven in [1]. In this paper, we present two 50\% hydrogenated graphene
+noncentrosymmetric structures, both presenting a discernible band gap. The
+first one, labelled as the Up structure (also known as graphone, see [2] and
+Refs therein), shown in Fig. \ref{fig:up-struc}. Graphone has hydrogen atoms
+bonded to the carbon layer only on the upper side of the structure, we consider
+here the magnetic isomer of graphone, with the so-called “chair” structure. In
+contrast,  the Alt structure, shown in Fig. \ref{fig:alt-struc}, has hydrogen
+alternating on the upper and bottom sides of the carbon
+sheet.\cite{zapataPSB2016}
 
@@
     \centering
-    \includegraphics[width=\tama]{figures/upstruc2}
-    \\
-    \includegraphics[width=\tama]{figures/upstruc1}
+    \includegraphics[width=\tama]{figures/fig1}
     \caption{Side (top panel) and top (bottom panel) views of the Up
@@
     \centering
-    \includegraphics[width=\tama]{figures/altstruc2}
-    \\
-    \includegraphics[width=\tama]{figures/altstruc1}
+    \includegraphics[width=\tama]{figures/fig2}
     \caption{Side (top panel) and top (bottom panel) views of the Alt
-      structure along with the 
-      $xyz$ directions. The dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell is also displayed.
-
-}
+      structure along with the $xyz$ directions. The dark (light) spheres are
+      the C (H) atoms. The primitive rectangular unit cell is also displayed.}
     \label{fig:alt-struc}
@@
 
-Using those structures, we address theoretically  the spin velocity
-injection (SVI) by one-photon absorption of linearly polarized light. Since wehave 2D structures, we do the analysis for two cases (not clear to me this sentence). The first case is by fixing the
-spin of the electrons along vertical to the surface direction (?)$z$, , with the velocity
-directed onto (is this parallel or not?) the surface of the structure in the $xy$ plane. In the second 
-case we fix the spin velocity in the $x$ or $y$ direction and the resulting spin is then directed outward of the $xy$ plane. % $xyz$. (Do we need to repeat “Cartesian” many times?)
+Using those structures, we address theoretically  the spin velocity injection
+(SVI) by one-photon absorption of linearly polarized light. Since wehave 2D
+structures, we do the analysis for two cases (not clear to me this sentence).
+The first case is by fixing the spin of the electrons along vertical to the
+surface direction (?)$z$, , with the velocity directed onto (is this parallel
+or not?) the surface of the structure in the $xy$ plane. In the second case we
+fix the spin velocity in the $x$ or $y$ direction and the resulting spin is
+then directed outward of the $xy$ plane. 
+% $xyz$. (Do we need to repeat “Cartesian” many times?)
 The SVI is an optical effect that quantifies the velocity, at which a PSC moves
-along the direction $\bf{a}$ with the $\bf{a}$ components to be determined,  % ####???, $\mathrm{a}$ and 
-with the spin of electron polarized
-along the direction $\bf{b}$. % $\mathrm{b}$. One-photon absorption of linearly
+along the direction $\bf{a}$ with the $\bf{a}$ components to be determined,  
+% ####???, $\mathrm{a}$ and 
+with the spin of electron polarized along the direction $\bf{b}$. 
+% $\mathrm{b}$. One-photon absorption of linearly
 polarized light produce an even distribution of electrons in $\mathbf{k}$
@@
 conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
-polarizations producing no net spin injection in centrosymmetric materials (?).\cite{bhatPRL05} If the
-crystalline structure of the material is noncentrosymmetric, the spin
-polarization injected at a given $\mathbf{k}$ point not necessarily
-vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88}. Therefore, since the velocities
-of electrons at opposite $\mathbf{k}$ points are opposite, a PSC will be
-produced. Since both the structures presented here are noncentrosymmetric, they are
-good candidates in which this effect can be induced.
+polarizations producing no net spin injection in centrosymmetric materials
+(?).\cite{bhatPRL05} If the crystalline structure of the material is
+noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
+point not necessarily vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88}.
+Therefore, since the velocities of electrons at opposite $\mathbf{k}$ points
+are opposite, a PSC will be produced. Since both the structures presented here
+are noncentrosymmetric, they are good candidates in which this effect can be
+induced.
 
 This paper is organized as follows. In Section \ref{sec:theory} we present the
-formalism and the main expressions  that describe PSC and SVI. In Section \ref{sec:results} we
-describe the numerical details  and  discuss the corresponding SVI spectra for the
-Up and Alt structures. Finally, we summarize our finding in
-Section \ref{sec:conclusions}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  T H E O R Y  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%               %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+formalism and the main expressions  that describe PSC and SVI. In Section
+\ref{sec:results} we describe the numerical details  and  discuss the
+corresponding SVI spectra for the Up and Alt structures. Finally, we summarize
+our finding in Section \ref{sec:conclusions}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In this section, we  summarize the theoretical approach, involved in
+calculation of the spin velocity injection (SVI) resulting from the pure spin
+current (PSC).
 
-In this section, we  summarize the theoretical approach, involved in 
-calculation of the spin velocity
-injection (SVI) resulting from the
-pure spin current (PSC).
-
-%%%BMSD
 The operator that describes the electronic SVI is written as
 \begin{align}\label{z.1}
-\hat K^{\mathrm{a}\mathrm{b}}=\frac{1}{2}\left( \hat v^\mathrm{a} \hat S^\mathrm{b} 
+\hat K^{\mathrm{a}\mathrm{b}} = 
+\frac{1}{2}\left( \hat v^\mathrm{a} \hat S^\mathrm{b} 
 +\hat  S^\mathrm{b} \hat v^\mathrm{a}\right) 
@@
 $\hat {\mathbf r}$ 
-%\end{document}
 being the position operator and $\hat H_0$ the unperturbed
@@
 \begin{align}\label{z.3}
-{\mathbf E}(t)= {\mathbf E}(\omega)e^{-i\omega t} + {\mathbf E}^*(\omega)e^{i\omega t}
+{\mathbf E}(t) = 
+{\mathbf E}(\omega)e^{-i\omega t} + {\mathbf E}^*(\omega)e^{i\omega t}
 .
 \end{align}
-In order to 
-calculate the response of the system to ${\mathbf E}(t)$, one needs to
-take into account the excited coherent superposition
-of the spin-split conduction bands inherent to the 
-noncentrosymmetric 
-semiconductors considered in this work.
-%Although, this splitting is small [15,16], is required to obtain the
-%correct results\cite{nastosPRB07}.
-% The conduction bands in the 
-% noncentrosymmetric  
-% semiconductors  
-% are spin split by a small amount,[15,16] typically
-%   smaller than the energy width of the laser pulse, and so the pulse
-%   excites a coherent superposition of the two conduction bands. Even
-%   for very long pulses with narrow energy widths, dephasing effects
-%   lead to an energy width of the bands large enough that spin-split
-%   states can become quasi-degenerate. 
+In order to calculate the response of the system to ${\mathbf E}(t)$, one needs
+to take into account the excited coherent superposition of the spin-split
+conduction bands inherent to the noncentrosymmetric semiconductors considered
+in this work.
+%Although, this splitting is small [15,16], is required to obtain the correct
+%results\cite{nastosPRB07}. The conduction bands in the noncentrosymmetric
+%semiconductors are spin split by a small amount,[15,16] typically smaller than
+%the energy width of the laser pulse, and so the pulse excites a coherent
+%superposition of the two conduction bands. Even for very long pulses with
+%narrow energy widths, dephasing effects lead to an energy width of the bands
+%large enough that spin-split states can become quasi-degenerate.
 To include the coherence, we follow Ref.~\onlinecite{nastosPRB05} and
@@
 \end{align}
-where we assumed that the conduction bands $c$ and $c'$
-are quasi-degenerate  states, and we take $\epsilon\to 0$ at the end of the
-calculation.  The spin-splitting of the valence ($v$) bands is very
-small, and is neglected throughout this work.\cite{nastosPRB07}
-The matrix elements of any operator ${\cal O}$ are given by
-${\cal O}_{nm}({\mathbf k})=\langle n{\mathbf k}|\hat{\cal O}| m{\mathbf k}\rangle$,
-where 
-$H_{0}|n{\mathbf k}\rangle = \hbar \omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ 
-with $\hbar \omega_{n}({\mathbf k})$ being the energy of the
-electronic band $n$ at point ${\mathbf k}$ in the irreducible Brillouin zone
-(IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state, and 
-$\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf k})-\omega_{m}({\mathbf k})$.
-Using 
-$\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$
-for the expectation value of an observable $\mathcal{O}$, 
-where $\mathrm{Tr}$ denotes the trace, we obtain
+where we assumed that the conduction bands $c$ and $c'$ are quasi-degenerate
+states, and we take $\epsilon\to 0$ at the end of the calculation.  The spin-
+splitting of the valence ($v$) bands is very small, and is neglected throughout
+this work.\cite{nastosPRB07} The matrix elements of any operator ${\cal O}$ are
+given by ${\cal O}_{nm}({\mathbf k})=\langle n{\mathbf k}|\hat{\cal O}|
+m{\mathbf k}\rangle$, where $H_{0}|n{\mathbf k}\rangle = \hbar
+\omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ with $\hbar \omega_{n}({\mathbf
+k})$ being the energy of the electronic band $n$ at point ${\mathbf k}$ in the
+irreducible Brillouin zone (IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state,
+and $\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf k})-\omega_{m}({\mathbf k})$.
+Using $\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$ for the
+expectation value of an observable $\mathcal{O}$, where $\mathrm{Tr}$ denotes
+the trace, we obtain
 \begin{align}\label{z.5}
-\mathcal{O} 
-%=&
-%\int \frac{d^{3}k}{8\pi^{3}}\sum_{c} \langle c {\mathbf k} 
-%| \hat{\rho} \hat{\mathcal{O}} |
-%c{\mathbf k} \rangle \nonumber \\
-=& 
+\mathcal{O} = & 
 \int \frac{d^{3}k}{8\pi^{3}} \sum_{cc'} \rho_{cc'}({\mathbf k}) 
@@
 \end{align}
-where we used 
-the closure
-relationship $\sum_{n}|n{\mathbf k}\rangle \langle n{\mathbf k}| = 1$,
-where $n=v,c$,
-and the fact that $\rho_{vn}({\mathbf k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. 
-Therefore, 
-using  Eqs. \eqref{z.4} and \eqref{z.5},
-the
-rate of change of $\mathcal{O}$,
-$\dot{\mathcal{O}} 
-=
-\mathrm{Tr} \left( \dot{\hat\rho} \hat{\cal O} \right)
-$,
- is given by
+where we used the closure relationship $\sum_{n}|n{\mathbf k}\rangle \langle
+n{\mathbf k}| = 1$, where $n=v,c$, and the fact that $\rho_{vn}({\mathbf
+k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. Therefore, using  Eqs. \eqref{z.4}
+and \eqref{z.5}, the rate of change of $\mathcal{O}$, $\dot{\mathcal{O}} =
+\mathrm{Tr} \left( \dot{\hat\rho} \hat{\cal O} \right)$, is given by
 \begin{align}
@@
 \end{align}
-The prime symbol $'$ in the sum means that
-$c$ and $c'$ are quasi-degenerate states, and the sum only covers these states.
-
-Replacing  $\hat{\cal O} \rightarrow \hat{K}^{\mathrm{ab}}$, in 
-the above expression, one can show that
+The prime symbol $'$ in the sum means that $c$ and $c'$ are quasi-degenerate
+states, and the sum only covers these states. Replacing  $\hat{\cal O}
+\rightarrow \hat{K}^{\mathrm{ab}}$, in the above expression, one can show that
 \begin{equation}
@@
 is the pseudotensor that describes the rate of change of the  PSC process in
-semiconductors. To derive what we presented above we used
-$
-K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k}) 
-$
-which follows from time-reversal invariance. 
-Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
-$\mu^{\mathrm{abcd}}(\omega) =
-\mu^{\mathrm{abdc}}(\omega)$. 
-We point out that Eq.~\eqref{eq:mu} 
-is –identical to Eq. (3) of Bhat et al.\cite{bhatPRL05},
-derived using the semiconductor optical Bloch equations.
-Using the closure relation,
+semiconductors. To derive what we presented above we used $
+K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+follows from time-reversal invariance. Since $\mu^{\mathrm{abcd}}(\omega)$ is
+real, we have that $\mu^{\mathrm{abcd}}(\omega) =
+\mu^{\mathrm{abdc}} (\omega)$. We point out that Eq.~\eqref{eq:mu} is
+–identical to Eq. (3) of Bhat et al.\cite{bhatPRL05}, derived using the
+semiconductor optical Bloch equations. Using the closure relation,
 \begin{equation}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{Spin velocity injection} % (fold)
-%\label{sec:theory-pure_spin_current}
-we define the spin velocity injection (SVI) as
+We define the spin velocity injection (SVI) as
 \begin{equation}\label{eq:vab-w}
@@
 \end{equation}  
-which gives the velocity, along direction $a$, % $\mathrm{a}$, 
-at which the spin
-moves in a polarized state along direction $b$. % $\mathrm{b}$. 
-The carrier injection rate
-$\dot n(\omega)$ is written as\cite{nastosPRB05}
+which gives the velocity, along direction $a$, at which the spin moves in a
+polarized state along direction $b$. The carrier injection rate $\dot
+n(\omega)$ is written as\cite{nastosPRB05}
 \begin{equation}
@@
 \end{equation}
-is related to the imaginary part of the linear optical 
-response tensor by
-$\mathrm{Im}[\epsilon^{\mathrm{a}\mathrm{b}}(\omega)]=2\pi\epsilon_0\hbar\xi^{\mathrm{a}\mathrm{b}}(\omega)$.
+is related to the imaginary part of the linear optical response tensor by
+$\mathrm{Im} [\epsilon^{\mathrm{a}\mathrm{b}}(\omega)] =
+2\pi\epsilon_0\hbar\xi^{\mathrm{a}\mathrm{b}}(\omega)$.
 
-The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify two very
-important aspects of PSC. On one hand, we can fix the spin direction
-along $\mathrm{b}$  
-and calculate the resulting electron velocity.  
-On the other hand, we can fix the velocity of the electron
-along $\mathrm{b}$ and study the resulting direction along which the
-spin is polarized.
-To this end, the additional advantage of  2D structures, besides being
- noncentrosymmetric, is that we can use an incoming linearly
-polarized  light
-at normal incidence, and use the  direction of the polarized  electric
-field to control ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.
-Indeed, writing 
-${\mathbf E}(\omega) = E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$,
-where $\alpha$ is the polarization angle, we obtain from
- Eq. \eqref{eq:vab-w}
-that
+The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify
+two very important aspects of PSC. On one hand, we can fix the spin direction
+along $\mathrm{b}$ and calculate the resulting electron velocity. On the other
+hand, we can fix the velocity of the electron along $\mathrm{b}$ and study the
+resulting direction along which the spin is polarized. To this end, the
+additional advantage of  2D structures, besides being noncentrosymmetric, is
+that we can use an incoming linearly polarized  light at normal incidence, and
+use the  direction of the polarized  electric field to control ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega)$. Indeed, writing ${\mathbf E}(\omega) =
+E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$, where
+$\alpha$ is the polarization angle, we obtain from Eq. \eqref{eq:vab-w} that
 \begin{widetext}
@@
 for the structures chosen in this article,
-$\xi^{\mathrm{xx}}(\omega)=\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and $\xi^{\mathrm{xy}}(\omega)=0$.
-Next, we identify two options for ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.
+$\xi^{\mathrm{xx}}(\omega)=\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and
+$\xi^{\mathrm{xy}}(\omega)=0$. Next, we identify two options for ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega)$.
 
@@
 
-Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define (calculate?) the magnitude of
-the electron velocity along the plane of the structure,
-with the spin polarized along $\mathrm{b}$ direction as
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define (calculate?) the magnitude
+of the electron velocity along the plane of the structure, with the spin
+polarized along $\mathrm{b}$ direction as
 \begin{equation}
@@
 \end{equation}
-corresponding to the electron velocity being parallel or perpendicular
-to the incoming light polarization, 
-respectively. The subscript $\sigma^\mathrm{b}$ denotes the spin along $\mathrm{b}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Fixing vel %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+corresponding to the electron velocity being parallel or perpendicular to the
+incoming light polarization, respectively. The subscript $\sigma^\mathrm{b}$
+denotes the spin along $\mathrm{b}$.
 
@@
 
-Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$,
-we define its corresponding magnitude as
+Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$, we
+define its corresponding magnitude as
 \begin{align}
@@
 \end{align}
-from where we see that the spin would be oriented
-in the $xyz$ system's coordinates
-defined with a polar angle
-\begin{align}
-\theta_{\mathrm{a}}  (\omega,\alpha)
-= 
+from where we see that the spin would be oriented in the $xyz$ system's
+coordinates defined with a polar angle
+\begin{equation}
+\theta_{\mathrm{a}}  (\omega,\alpha) = 
 \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
@@
 C &  0.61516 &  0.35763 & -0.49087 \\
+C &  0.61518 &  1.77416 & -0.73196 \\
 \hline
 \end{tabular}
-\caption{Atomic positions in the unit cell of Up structure as the structural input for our calculations (the primitive hexagonal unit cell contains two C and one H atoms, see Fig. 1). ADD EXTRA C atom
-}
+\caption{Atomic positions in the unit cell of Up structure as the structural
+input for our calculations (the primitive hexagonal unit cell contains two C
+and one H atoms, see Fig. 1). ADD EXTRA C atom }
 \label{tab:up-unitcell}
@@
 \end{tabular}
-\caption{Atomic positions in the unit cell of Alt structure, which coincides with its primitive cell. 
-}
+\caption{Atomic positions in the unit cell of Alt structure, which coincides
+with its primitive cell. }
 \label{tab:alt-unitcell}
@@
 
-We present the calculated results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
+We present the calculated results of
+$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
 $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-Up  and
-C$_{16}$H$_{8}$-Alt structures, both noncentrosymmetric 2D carbon
-systems with 50\% hydrogenation, which are differently structurally arranged. We remind
-that the Up structure has hydrogen atoms only on the upper side of the carbon
-sheet, while the Alt structure has alternating hydrogen atoms on the upper and
-bottom sides. We take the carbon lattice to be along the $xy$ plane
-for both structures, and the carbon-hydrogen bonds are outward the plane, they are perpendicular to  $xz$
-plane for the Up structure, as depicted in Figs. \ref{fig:up-struc}, and off the normal for the Alt structure \ref{fig:alt-struc}. The
-coordinates for the Up and Alt unit cells of the structures are presented in
-Tables \ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
+C$_{16}$H$_{8}$-Alt structures, both noncentrosymmetric 2D carbon systems with
+50\% hydrogenation, which are differently structurally arranged. We remind that
+the Up structure has hydrogen atoms only on the upper side of the carbon sheet,
+while the Alt structure has alternating hydrogen atoms on the upper and bottom
+sides. We take the carbon lattice to be along the $xy$ plane for both
+structures, and the carbon-hydrogen bonds are outward the plane, they are
+perpendicular to  $xz$ plane for the Up structure, as depicted in Figs.
+\ref{fig:up-struc}, and off the normal for the Alt structure 
+\ref{fig:alt-struc}. The coordinates for the Up and Alt unit cells of the
+structures are presented in Tables \ref{tab:up-unitcell} and 
+\ref{tab:alt-unitcell}.
 
@@
 density functional theory in the local density approximation (DFT-LDA), with a
-planewave basis using the ABINIT code \cite{gonzeCPC09}.
-% 
-We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
-Gaussian pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit
-interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
-in Eq. \eqref{eq:mu}.
-% 
-The convergence parameters for the calculations,  corresponding to
-the Up and Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting
-in LDA energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
+planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
+Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
+pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
+needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
+\eqref{eq:mu}.
+The convergence parameters for the calculations,  corresponding to the Up and
+Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting in LDA
+energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
 eigenvalues and matrix elements for the Up and Alt structures were calculated
 using 12802 ${\mathbf k}$ points and 14452 ${\mathbf k}$ points in the IBZ; to
-integrate $\mu^{\mathrm{abcd}}(\omega)$ and $\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the
-linearized analytic tetrahedron method (LATM) has been used.\cite{nastosPRB07} We neglect the
-anomalous velocity term $\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the
-crystal potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
-give small contribution to PSC.\cite{bhatPRL05} Therefore,
-$[\hat{\mathbf v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat K^{\mathrm{a}\mathrm{b}}=\hat
-v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b} \hat v^\mathrm{a}$. Finally, the prime in the sum of
-Eq.~\eqref{eq:mu} is restricted to quasi-degenerated conduction bands $c$ and
-$c'$ that are closer than 30 meV, which  is both typical laser-
-pulse energy width and the thermal room-temperature energy level broadening.\cite{nastosPRB07}
-% 
-% It is known that the DFT with LDA approximation misestimates the energy band
-% gap of semiconductors. To correct this one has to include the many-body
-% interaction using i.e. the so-called GW approximation but this technique has a
-% very high computational cost and is out of the scope in this paper.
-% Nevertheless, DFT still remains a mainstream tool for calculating diverse
-% properties derived from the electronic band structure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Results: Spin velocity %%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+integrate $\mu^{\mathrm{abcd}}(\omega)$ and
+$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the linearized analytic tetrahedron method
+(LATM) has been used.\cite{nastosPRB07} We neglect the anomalous velocity term
+$\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
+potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
+give small contribution to PSC.\cite{bhatPRL05} Therefore, $[\hat{\mathbf
+v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat
+K^{\mathrm{a}\mathrm{b}}=\hat v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b}
+\hat v^\mathrm{a}$. Finally, the prime in the sum of Eq.~\eqref{eq:mu} is
+restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
+than 30 meV, which  is both typical laser- pulse energy width and the thermal
+room-temperature energy level broadening.\cite{nastosPRB07}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
 \centering
-\includegraphics[width=\tama]{plots/2-vab-str-comp}
+\includegraphics[width=\tama]{figures/fig3}
 \caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
-  vs. $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The largest velocity are at the low
-  energy regions of the spectra for the Alt and Up structures, starting (going up?) at the energy gap of each
-  structure. In the high energy regions, the values of
-  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to the 3D case of CdSe and GaAsThe, shown at the bottom panel . } 
+  vs. $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
+  largest velocity are at the low energy regions of the spectra for the Alt and
+  Up structures, starting (going up?) at the energy gap of each structure. In
+  the high energy regions, the values of
+  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to
+  the 3D case of CdSe and GaAsThe, shown at the bottom panel . }
 \label{fig:vab-str-comp}
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\omega$ for the directions $\mathrm{a}\mathrm{b}$ (confusing to me), and for the
-angle $\alpha$, at which the signal is 
-maximized , for the Up  and Alt structures, and for CdSe and
-GaAs bulk systems, shown for comparison.
-% 
-As expected from Eq.~\eqref{eq:mu},
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises from zero right at the corresponding energy gap of each
-system. For the 2D structures considered, the spectrum contains two narrow energy regions
-with strong response, while for the bulk systems, the spectra covers a
-rather wide energy range, but with a much weaker response.
-% 
-For the Up structure, at $\mathrm{a}\mathrm{b}=yz$ and $\alpha=35^\circ$ the response is maximized,
-which means that an incoming light with its electric field polarized at
-35$^\circ$ from the $x$ direction will induce electrons to move along $y$
-(parallel to the surface), with their spin polarized along $z$ (perpendicular to
-the surface). The corresponding speeds are the following:
-% 
-Right at the energy onset, ${\cal V}^{yz}(\omega,\alpha)=668$\,Km/s, remains
-almost constant for 65 meV, and then decreases to zero. A second region with high velocity is 
-above 1.946 eV with two, opposite in sign, maxima of the speed:
-${\cal V}^{yz}(\omega,\alpha)=266.3$ Km/s at $\hbar\omega=1.954$\,eV, and
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)=-241.4$ Km/s at $\hbar\omega=1.958$\,eV; a positive
-(negative) ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move parallel
-(antiparallel) to the electric field.
-Likewise, for the Alt structure, we also find that $\mathrm{a}\mathrm{b}=yz$ and
-$\alpha=150^\circ$ maximizes the response, where two extreme values of
-${\cal V}^{\mathrm{y}\mathrm{z}}$ are found, one at  $\hbar\omega=0.720$\,eV of
-${\cal V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at $\hbar\omega=0.911$\,eV of
-${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.
+(\omega,\alpha)$ vs. $\hbar\omega$ for the directions $\mathrm{a}\mathrm{b}$
+(confusing to me), and for the angle $\alpha$, at which the signal is maximized
+, for the Up  and Alt structures, and for CdSe and GaAs bulk systems, shown for
+comparison. As expected from Eq.~\eqref{eq:mu}, ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises from zero right at the
+corresponding energy gap of each system. For the 2D structures considered, the
+spectrum contains two narrow energy regions with strong response, while for the
+bulk systems, the spectra covers a rather wide energy range, but with a much
+weaker response. For the Up structure, at $\mathrm{a}\mathrm{b}=yz$ and
+$\alpha=35^\circ$ the response is maximized, which means that an incoming light
+with its electric field polarized at 35$^\circ$ from the $x$ direction will
+induce electrons to move along $y$ (parallel to the surface), with their spin
+polarized along $z$ (perpendicular to the surface). The corresponding speeds
+are the following: Right at the energy onset, ${\cal
+V}^{yz}(\omega,\alpha)=668$\,Km/s, remains almost constant for 65 meV, and then
+decreases to zero. A second region with high velocity is above 1.946 eV with
+two, opposite in sign, maxima of the speed: ${\cal
+V}^{yz}(\omega,\alpha)=266.3$ Km/s at $\hbar\omega=1.954$\,eV, and ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)=-241.4$ Km/s at
+$\hbar\omega=1.958$\,eV; a positive (negative) ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move
+parallel (antiparallel) to the electric field. Likewise, for the Alt structure,
+we also find that $\mathrm{a}\mathrm{b}=yz$ and $\alpha=150^\circ$ maximizes
+the response, where two extreme values of ${\cal V}^{\mathrm{y}\mathrm{z}}$ are
+found, one at  $\hbar\omega=0.720$\,eV of ${\cal
+V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at
+$\hbar\omega=0.911$\,eV of ${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.
 
-For the bulk structures, we calculate ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ from
-Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$. For CdSe, we find
-that for $\hbar\omega=0.844$\,eV, $\boldsymbol{\mu}_{\mathrm{max}}\to \mu^{zzzz}$, and
-${\cal V}^{\mathrm{z}\mathrm{z}}(\omega)=-59.0$ Km/s, and for GaAs at $\hbar\omega=2.324$\,eV,
-$\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and ${\cal V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with
-$\mathrm{a}=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis are
-taken along the standard cubic unit cell directions, [100], [010], and [001],
-respectively. In Table \ref{tab:vab-str-comp}, we compare 
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures considered and bulk crystals.
-% 
-We stress that, as shown in the figure, for 
-the 2D structures have maxima in 
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$  
-are higher
-than for the bulk crystals. In particular, the Alt
-structure demonstrates a ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than
-that of CdSe and GaAs.
+For the bulk structures, we calculate ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$
+from Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$.
+For CdSe, we find that for $\hbar\omega=0.844$\,eV,
+$\boldsymbol{\mu}_{\mathrm{max}}\to \mu^{zzzz}$, and ${\cal
+V}^{\mathrm{z}\mathrm{z}}(\omega)=-59.0$ Km/s, and for GaAs at
+$\hbar\omega=2.324$\,eV,
+$\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and ${\cal
+V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with $\mathrm{a}=x,y,z$.
+For these bulk semiconductors, the $x$, $y$, and $z$ axis are taken along the
+standard cubic unit cell directions, [100], [010], and [001], respectively. In
+Table \ref{tab:vab-str-comp}, we compare ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures considered and
+bulk crystals. We stress that, as shown in the figure, for the 2D structures
+have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ are higher than
+for the bulk crystals. In particular, the Alt structure demonstrates a ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than that
+of CdSe and GaAs.
 \begin{table}%[b]
@@
 \caption{Comparison of the reported maximum values of
-$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the different structures and their
-corresponding polarization angle $\alpha$ and energy $\hbar\omega$ .
-}
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the different structures and
+their corresponding polarization angle $\alpha$ and energy $\hbar\omega$ . }
 \label{tab:vab-str-comp}
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vsz-w1}
-\caption{Color online. For the Up structure, the top panel shows 
-${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ SvsS. $\hbar\omega$ and $\alpha$, and the bottom panel
-shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line, long dashes?), and
-${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid line?), $vs$. $\alpha$, for
-$\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
+\includegraphics[width=\tama]{figures/fig4}
+\caption{Color online. For the Up structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ SvsS. $\hbar\omega$ and $\alpha$, and
+the bottom panel shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right
+scale, red line, long dashes?), and ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid line?), $vs$.
+$\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the 3D
+plot. }
 \label{fig:up-vsz-w1}
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vsz-w2}
-\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
-vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows $\gamma_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ (right scale, red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left
-scale, black solid line), vs. $\alpha$, for $\hbar\omega=1.954$\,eV, i.e. along the
-highest ridge shown in the 3D plot. }
+\includegraphics[width=\tama]{figures/fig5}
+\caption{For the Up structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
+red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
+(left scale, black solid line), vs. $\alpha$, for $\hbar\omega=1.954$\,eV, i.e.
+along the highest ridge shown in the 3D plot. }
 \label{fig:up-vsz-w2}
@@
 
-In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$, Eq.
-\eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
+In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$,
+Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
-calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ from Eq. \eqref{eq:gamma-ang}, which
-determines the direction  of the injected electrons movement along the
-surface of  each structure. We mention that we have also  analyzed 
-the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$,
-finding similar qualitative results to those presented below.
-%
+calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ from Eq. 
+\eqref{eq:gamma-ang}, which determines the direction  of the injected 
+electrons movement along the surface of  each structure. We mention that we
+have also  analyzed the cases when the spin  is directed along $\mathrm{x}$ or
+$\mathrm{y}$, finding similar qualitative results to those presented below.
 
@@
 structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
-$0^\circ\leq\alpha\leq 180^\circ$.
-% 
-We see a broad peak that reaches the maximum of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-739.7$\,Km/s at $\alpha=35^{\circ}$ and $\hbar\omega=
-0.084$\,eV,  The variation of $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ as a function of $\alpha$, which comes from the interplay of the
-$\boldsymbol{\mu}$ tensor components as multiplied by the  trigonometric functions of
-Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and
-165.4\,Km/s, for 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. 
-% 
-In the bottom panel, we show $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ $vs.$ $\alpha$ (left scale, black line), at $\hbar\omega= 0.084$\,eV,
-thus following the ridge in the 3D plot of the top panel. 
-Also,
-we plot the
-corresponding velocity angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$
-(right scale, red line),
-where it is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
-at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$,
-for the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
-and for all values of $\alpha$, the electrons, with the chosen spin pointing along
-$z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha) \sim
-64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
+$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
+of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s at
+$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV,  The variation of
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\alpha$,
+which comes from the interplay of the $\boldsymbol{\mu}$ tensor components as
+multiplied by the  trigonometric functions of Eq.~\eqref{eq:vab-aw}, gives a
+sizable set of values between 739.7\,Km/s and 165.4\,Km/s, for
+0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ $vs.$ $\alpha$ (left scale,
+black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
+plot of the top panel. Also, we plot the corresponding velocity angle
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where it
+is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
+at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for
+the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
+and for all values of $\alpha$, the electrons, with the chosen spin pointing
+along $z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)
+\sim 64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
 speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
-% 
 Also, from Eq. \eqref{eq:gamma-par} we find that
-$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see green
-arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$,
+with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see
+green arrow), and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
-arrow). Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at $\alpha
-\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
-polarized along $z$, which move parallel or perpendicular to the incident
+arrow). Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
+$\alpha \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their
+spin polarized along $z$, which move parallel or perpendicular to the incident
 electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.
@@
 (\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
-$0^\circ\leq\alpha\leq 180^\circ$.
-% 
-We see two broad peaks that maximize at $\alpha=35^{\circ}$ and $\hbar\omega=
-1.954$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-193.5$\,Km/s, and at $\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value
-of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. 
-% 
-We only analyze the highest  maximum in the bottom panel, where we  show
+$0^\circ\leq\alpha\leq 180^\circ$. We see two broad peaks that maximize at
+$\alpha=35^{\circ}$ and $\hbar\omega= 1.954$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 193.5$\,Km/s, and at
+$\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. We only
+analyze the highest  maximum in the bottom panel, where we  show
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
-black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel. Also, we plot the corresponding
-velocity angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red
-line),
-where in
-this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$ have more
-dispersion, as a function of $\alpha$, than for the lower energy range shown in
-the bottom panel of Fig.~\ref{fig:up-vsz-w1}.
-% 
-However, $\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
+black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
+shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
+angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line),
+where in this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$
+have more dispersion, as a function of $\alpha$, than for the lower energy
+range shown in the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
+$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
 $\alpha=0^\circ$ up to $\alpha\sim 85^\circ$. In this case, we find that
 $\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (as indicated by green
-arrow), and that from Eq. \eqref{eq:gamma-perp},
-$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$, gives
-$\alpha=77.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-65.6$\,Km/s (see blue arrow). 
-% 
-Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could inject
-electrons, in this case with their spin polarized along $z$, which move parallel
-or perpendicular to the incident electric field, with finite speeds (what does “finite” mean?).
-
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (as indicated
+by green arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
+gives $\alpha=77.8^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s (see blue
+arrow). Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
+inject electrons, in this case with their spin polarized along $z$, which move
+parallel or perpendicular to the incident electric field, with finite speeds
+(what does “finite” mean?).
 % the maxima for
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vsz}
-\caption{Color online. For the Alt structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
-$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), and ${\cal V}_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ (left scale, black line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e.
-along the ridge shown in the 3D plot.}
+\includegraphics[width=\tama]{figures/fig6}
+\caption{Color online. For the Alt structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
+red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale,
+black line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge
+shown in the 3D plot.}
 \label{fig:alt-vsz}
@@
 
-We proceed to analyze the Alt structure, just as we did with the Up structure, but
-in this case, we only choose the lower energy range shown in the left central
-panel of Fig.~\ref{fig:vab-str-comp}. 
-% 
-In the top panel of Fig. \ref{fig:alt-vsz}, we plot
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
-0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq 180^\circ$. We
-see a broad peak that maximizes at $\alpha=150^{\circ}$ and $\hbar\omega=
-0.720$\,eV, with a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
-644.9$\,Km/s.
-% 
-In the bottom panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ vs. $\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV,
- thus following the highest ridge shown in the 3D plot of the top
-panel. Also, we plot the corresponding velocity angle $\gamma_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ (right scale, red line), where now we see that
+We proceed to analyze the Alt structure, just as we did with the Up structure,
+but in this case, we only choose the lower energy range shown in the left
+central panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of Fig. 
+\ref{fig:alt-vsz}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
+vs. 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
+180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
+$\hbar\omega= 0.720$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
+panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+$\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV, thus following
+the highest ridge shown in the 3D plot of the top panel. Also, we plot the
+corresponding velocity angle $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$
+(right scale, red line), where now we see that
 $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
 variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
-\alpha \leq 180^{\circ}$.
-% 
-In this case, we find that $\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
-\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
-450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
+\alpha \leq 180^{\circ}$. In this case, we find that
+$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
+\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)
+= 450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
@@
 (\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
-we could inject electrons with a fixed spin, which moves parallel or perpendicular
-to the incident electric field.
-
+we could inject electrons with a fixed spin, which moves parallel or
+perpendicular to the incident electric field.
 % Again, for the cases in which the spin polarization is parallel to the
@@
 
-Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. \eqref{eq:vv-mag})
-after fixing the electron velocity direction, $\mathrm{a}$, to the $x$ or $y$ direction
-along the surface of the Up and Alt structures. From Eqns. \eqref{eq:polar-ang}
-and \eqref{eq:azimuthal-ang}, we determined the polar, $\theta_{\mathrm{a}}
-(\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}} (\omega,\alpha)$, angles
-corresponding to the direction of the injected (?) spin.
+Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. 
+\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\mathrm{a}$,
+to the $x$ or $y$ direction along the surface of the Up and Alt structures.
+From Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the
+polar, $\theta_{\mathrm{a}} (\omega,\alpha)$, and azimuthal,
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, angles corresponding to the direction
+of the injected (?) spin.
 
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vx-vy-w1}
+\includegraphics[width=\tama]{figures/fig7}
 \caption{For the Up structure, we show
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$
-(left scale, black line),  
-$\theta_{\mathrm{a}} (\omega,\alpha)$
-(right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$,
-(right scale, blue line),
-vs. $\hbar\omega$, for $\alpha=35^\circ$, 
-and $\mathrm{a}=x$ and $\mathrm{a}=y$.
-}
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and $\mathrm{a}=y$. }
 \label{fig:up-vab-comp-rtp-1}
@@
 
-For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes the
-response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for $\mathrm{a}=x,y$. 
-% 
-We see that for $\hbar\omega=0.084$\,eV, the response has a maximum of
-$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=431.7$\,Km/s at
-$\theta_{\mathrm{x}}(\omega,\alpha) = 42.5^{\circ}$, and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
+For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes
+the response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\mathrm{a}=x,y$. We see that for $\hbar\omega=0.084$\,eV,
+the response has a maximum of $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha)=431.7$\,Km/s at $\theta_{\mathrm{x}}(\omega,\alpha) =
+42.5^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
 $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s at
-$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and
-$\varphi_{\mathrm{y}} (\omega,\alpha) = 82.1^{\circ}$. This means that the
-spin is directed upward the third Cartesian quadrant of the $xy$ plane when the
-electron moves along $x$, and is almost parallel to the $xy$ plane in
-the first Cartesian quadrant when it moves along $y$. 
-% 
-Also from this figure, we see that when the electron moves along $x$, the spin
-direction is almost constant for all the energies across the peak of the
-response, having
-$42.5^{\circ}<\theta_{\mathrm{x}}(\omega,\alpha)<53.7^{\circ}$ and
-$208.3^{\circ}<\varphi_{\mathrm{x}}(\omega,\alpha)<215.7^{\circ}$. When
-the electron moves along $y$, the spin polar angle has again small variations,
-$11.3^{\circ}< \theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the
-azimuthal angle varies significantly, $82.1^{\circ}<
-\varphi_{\mathrm{y}}(\omega,\alpha)<182.4^{\circ}$.
+$\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and $\varphi_{\mathrm{y}}
+(\omega,\alpha) = 82.1^{\circ}$. This means that the spin is directed upward
+the third Cartesian quadrant of the $xy$ plane when the electron moves along
+$x$, and is almost parallel to the $xy$ plane in the first Cartesian quadrant
+when it moves along $y$. Also from this figure, we see that when the electron
+moves along $x$, the spin direction is almost constant for all the energies
+across the peak of the response, having $42.5^{\circ}<\theta_{\mathrm{x}}
+(\omega,\alpha)<53.7^{\circ}$ and $208.3^{\circ}<\varphi_{\mathrm{x}}
+(\omega,\alpha)<215.7^{\circ}$. When the electron moves along $y$, the spin
+polar angle has again small variations, $11.3^{\circ}<
+\theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the azimuthal angle
+varies significantly, $82.1^{\circ}< \varphi_{\mathrm{y}}
+(\omega,\alpha)<182.4^{\circ}$.
 
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vx-vy-w2}
+\includegraphics[width=\tama]{figures/fig8}
 \caption{For the Up structure we show $\mathcal{V}_{\mathrm{a}}
@@
 In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there two local maxima with opposite sign
-at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV occur.
-% 
-The first is the largest of the two, with
-$\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
-$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and 
-$\varphi_{\mathrm{x}} (\omega,\alpha)=54.3^{\circ}$,
-for the electron moving along $x$; and
-$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s,
-$\theta_{\mathrm{y}} (\omega,\alpha)=49.8^{\circ}$, and 
-$\varphi_{\mathrm{y}} (\omega,\alpha)=51.9^{\circ}$
-for the electron moving along $y$.
-% 
-For the peak at $\hbar\omega=1.957$\,eV, we obtain 
-$\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and 
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with 
+(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there two local maxima
+with opposite sign at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV
+occur. The first is the largest of the two, with $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha)=61.2$\,Km/s, $\theta_{\mathrm{x}}
+(\omega,\alpha)=48.3^{\circ}$, and $\varphi_{\mathrm{x}}
+(\omega,\alpha)=54.3^{\circ}$, for the electron moving along $x$; and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s, $\theta_{\mathrm{y}}
+(\omega,\alpha)=49.8^{\circ}$, and $\varphi_{\mathrm{y}}
+(\omega,\alpha)=51.9^{\circ}$ for the electron moving along $y$. For the peak
+at $\hbar\omega=1.957$\,eV, we obtain $\theta_{\mathrm{x}} (\omega,\alpha) =
+129.8^{\circ}$ and $\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with
 $\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and
 $\theta_{\mathrm{y}}(\omega,\alpha) =129.3$; and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s.
-We remark that these angles are almost
-constant for all the energy values across the peak of these two local maxima, for
-which the spin is directed upward in the first Cartesian quadrant of the $xy$
-plane when it (who?) moves along either $x$ or $y$ directions.
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with $\mathcal{V}^{\mathrm{y}}
+(\omega,\alpha) = 263.7$\,Km/s. We remark that these angles are almost constant
+for all the energy values across the peak of these two local maxima, for which
+the spin is directed upward in the first Cartesian quadrant of the $xy$ plane
+when it (who?) moves along either $x$ or $y$ directions.
 
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vx-vy-w1} % I believe that all the similar captions
+\includegraphics[width=\tama]{figures/fig9}
+% I believe that all the similar captions
 % should be modified, one possible version is below
-\caption{The Alt structure: the velocity 
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar angle 
-$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the azimuthal angle
+\caption{The Alt structure: the velocity $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are shown. }
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
+shown. }
 \label{fig:alt-vx-vy-w1}
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vx-vy-w2}   % Change the captions accordingly the above
+\includegraphics[width=\tama]{figures/fig10}
+% Change the captions accordingly the above
 \caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
@@
 $\alpha=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
-and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\alpha$.
-% 
-In Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
-(\omega,\alpha) = 301.7$\,Km/s is at
-$\hbar\omega=0.720$\,eV , $\theta_{\mathrm{x}} (\omega,\alpha) =
-44.5^{\circ}$ and $\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$;
-and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
- at $\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. 
-% 
-Thus, the spin is directed upward the fourth Cartesian quadrant of the $xy$
-plane when the spin velocity is directed along $x$, while it is directed downward the
-second Cartesian quadrant when the spin velocity is directed along $y$.
-% 
-Finally, in  Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at
-$\hbar\omega=0.911$\,eV at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) =
-276.3$\,Km/s, $\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
+and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\alpha$. In
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV ,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 44.5^{\circ}$ and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$; and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s at
+$\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. Thus, the spin is
+directed upward the fourth Cartesian quadrant of the $xy$ plane when the spin
+velocity is directed along $x$, while it is directed downward the second
+Cartesian quadrant when the spin velocity is directed along $y$. Finally, in
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV
+at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
 $\varphi_{\mathrm{x}}(\omega,\alpha) = 292.3^{\circ}$, and
@@
 is directed downward the fourth Cartesian quadrant of the $xy$ plane when the
-spin velocity is directed along $x$, while is directed downward the third Cartesian
-quadrant when the spin velocity is directed along $y$.
+spin velocity is directed along $x$, while is directed downward the third
+Cartesian quadrant when the spin velocity is directed along $y$.
 
@@
 
-We reported the results of an \emph{ab initio} calculations for the spin velocity injection (SVI) due to the one-photon
-absorption of the linearly polarized light in the Up and Alt 2D 50\% hydrogenated
-graphene structures. Different possible arrangements of the of the spin injection have been considered: we made the calculations for the cases when the spin is
-polarized in $z$ direction or when the velocity is directed along $x$ or
-$y$. To the best of our knowledge, this effect  has been previously reported in this  2D partially hydrogenated 
-structures.
-% 
-We have shown that the  SVI demonstrates an anisotropic behavior, which is very sensitive to the symmetry of the structures of interest. We have found that the Up structure shows
-the strongest response for the spin directed along $z$, resulting in the velocity 
-% 
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s 
-% 
-for the incoming photon energy of 0.084\,eV. Also, the Alt structure
-has the strongest response when the spin moves along $y$ direction,
-resulting in 
-% 
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s
-% 
-for the incoming photon energy of 0.720\,eV.
-% 
-The speed values obtained here are of the same order of magnitude
-as those of Ref.~\onlinecite{najmaiePRB03} in 
-unbiased semiconductor quantum well structures, while they are of order of magnitude 
-higher compared to 3D bulk materials.
-The spin relaxation time in pure and doped graphene is long enough in the order
-from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertlerPRB09} Therefore,
-according to our results, due to the high spin velocity transport both structures considered are the excellent candidates for the development of
-spintronics devices that require pure spin current (PSC).
+We reported the results of an \emph{ab initio} calculations for the spin
+velocity injection (SVI) due to the one-photon absorption of the linearly
+polarized light in the Up and Alt 2D 50\% hydrogenated graphene structures.
+Different possible arrangements of the of the spin injection have been
+considered: we made the calculations for the cases when the spin is polarized
+in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
+of our knowledge, this effect  has been previously reported in this  2D
+partially hydrogenated structures. We have shown that the  SVI demonstrates an
+anisotropic behavior, which is very sensitive to the symmetry of the structures
+of interest. We have found that the Up structure shows the strongest response
+for the spin directed along $z$, resulting in the velocity
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s for the
+incoming photon energy of 0.084\,eV. Also, the Alt structure has the strongest
+response when the spin moves along $y$ direction, resulting in
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for the incoming
+photon energy of 0.720\,eV. The speed values obtained here are of the same
+order of magnitude as those of Ref.~\onlinecite{najmaiePRB03} in unbiased
+semiconductor quantum well structures, while they are of order of magnitude
+higher compared to 3D bulk materials. The spin relaxation time in pure and
+doped graphene is long enough in the order from nanoseconds to milliseconds.
+\cite{wojtaszekPRB13,ertlerPRB09} Therefore, according to our results, due to
+the high spin velocity transport both structures considered are the excellent
+candidates for the development of spintronics devices that require pure spin
+current (PSC).
 

### 2017-08-17 mu/article/article.tex
Starting Anatoli's review.
Made Anatoli's changes.

@@
 \documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage{color}
-\usepackage{subfigure}
-\usepackage{hyperref}
+\usepackage{amsmath}    % need for subequations 
+\usepackage{graphicx}   % need for figures 
+\usepackage{verbatim}   % useful for program listings 
+\usepackage{color}      % use if color is used in text 
+\usepackage{subfigure}  % use for side-by-side figures 
+\usepackage{hyperref}   % use for hypertext links, including those to external 
+                        % documents and URLs 
 \usepackage[dvipsnames]{xcolor}
 \usepackage{multirow}
+\usepackage{soul}
+%\usepackage[inline]{showlabels}
 % \input{/Users/bms/util/definitions}
@@
 \def\tama{10cm}
-\raggedbottom
+\raggedbottom           % don't add extra vertical space
 
@@
 \author{Reinaldo Zapata-Pe\~na}
-\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150,
-M\'exico}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
+Guanajuato 37150, M\'exico}
 \author{Bernardo S. Mendoza}
-\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150,
-M\'exico}
+\affiliation{Centro de Investigaciones en \'Optica, Le\'on,
+Guanajuato 37150, M\'exico}
 \author{Anatoli I. Shkrebtii}
-\affiliation{University of Ontario, Institute of Technology, Oshawa, ON, L1H
-7L7, Canada}
+\affiliation{University of Ontario, Institute of Technology,
+Oshawa, ON, L1H 7L7, Canada}
 
@@
 \begin{abstract}
-We present a theoretical study of spin-velocity injection of a pure spin current
-induced by  a linearly polarized beam of light that impinges normally on the
-surface of  two 50\% hydrogenated noncentrosymmetric 2D graphene structures,
-labeled Up and Alt. The hydrogenation opens an energy gap in both structures. We
-analyze two possibilities: one in which by fixing the spin along a chosen
-direction, the resulting spin-velocity is calculated, and another where we
-choose the spin-velocity direction on the surface plane, and calculate its speed
-and spin orientation. We do so by changing the energy $\hbar\omega$ and
-polarization angle $\alpha$  of the incoming  beam. The results are calculated
-within a full electronic band structure scheme within the DFT in the LDA
-approximation. The maxima of the spin-velocity speed are obtained when
-$\hbar\omega = 0.084$\,eV and $\alpha=35^\circ$ for Up, and $\hbar\omega =
-0.720$\,eV and $\alpha=150^\circ$ for Alt. We find a speed of 668\,Km/s and
-645\,Km/s for Up and Alt, respectively, when the spin points perpendicularly to
-the surface. Also, the response is maximized by fixing the spin-velocity
-direction along a high symmetry Cartesian axis, obtaining a speed of 688\,Km/s
-with the spin  pointing at 13$^\circ$ from the surface normal, for Up, and
-906\,Km/s and the spin pointing at 60$^\circ$ from the surface normal, for Alt.
-These speed values are larger than those of bulk semiconductors, like CdSe and
-GaAs, thus making the hydrogenated graphene structures excellent candidates for
-spintronics applications.
+We present a theoretical study of spin-velocity injection (SVI) of a pure spin
+current (PSC) induced by  a linearly polarized light that impinges normally on
+the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D
+graphene structures. The first structure, hydrogenated at only one side,
+labeled $Up$, also known as graphone, and the second, one labelled $Alt$, is
+25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
+structures. We analyze two possibilities: the first one  is by fixing the spin
+along a chosen direction, and the resulting spin-velocity is calculated.
+Secondly, we choose the spin-velocity direction within {\color{red}(OR along?)}
+the surface plane, and calculate {\color{red}(which one?)} the spin-velocity
+injection and spin orientation. This is done by changing the energy
+$\hbar\omega$ and polarization angle $\alpha$  of the incoming  light. The
+results are calculated within a full electronic band structure scheme using the
+Density Functional Theory (DFT) in the Local Density Approximation (LDA). The
+maxima of the spin-velocities are reached when $\hbar\omega=0.084$\,eV and
+$\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
+$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and
+645\,Km/s for Up and Alt structures, respectively, when the spin points
+perpendicularly to the surface. Also, the symmetry Cartesian axis, reaching a
+speed of 688\,Km/s with the spin  pointing response is maximized by fixing the
+spin-velocity direction along a high at 13$^\circ$ from the surface normal, the
+for Up, and 906\,Km/s and the spin pointing at 60$^\circ$ from the surface
+normal, for the Alt. These speed values are significantly larger than those of
+bulk semiconductors, such as CdSe and GaAs, thus making the hydrogenated
+graphene structures excellent candidates for spintronics applications.
 \end{abstract}
@@
 Spintronics is an emerging research field of electronics in which the
-manipulation and transport of spin of electrons in a solid state media plays the
-determining role, adding a new degree of freedom to conventional charge
-manipulation.\cite{wolfSC04,fabianAPS07} 
-At present, there is an increasing interest in attaining the same level of
-control over the transport of spin at micro or nano scales, as it has been done
-for the flow of charge in typical electronic devices.\cite{awschalomNP2007} Some
-semiconductor spintronics devices have been proposed \cite{majumdarAPL06,
+manipulation and transport of spin of electrons in a solid state materials  is
+central, adding a new degree of freedom to conventional charge
+manipulation.\cite{wolfSC04,fabianAPS07} At present, there is an increasing
+interest in attaining the same level of control over the transport of spin at
+micro- or nano-scales, as it has been done for the flow of charge in typical
+3D-bulk based electronic devices.\cite{awschalomNP2007} Several semiconductor
+spintronics devices have been proposed \cite{majumdarAPL06,
 dattaAPL90,gotteNat16,pershinPRB08}, and some of them require spin polarized
-electrical current \cite{awschalomSSBM13} or pure spin current (PSC).
-One of the difficulties to achieve the development of spin current and PSC
-semiconductor devices is the fact that the spin relaxation time in a
-semiconducting media is short, disabling the spin transport, and then resulting
-in a non-observable spin current.\cite{murakamiSc03}
-In PSCs, there is no net motion of charge; spin-up electrons move in a given
-direction, while spin-down electrons travel in the opposite one. This effect can
-result from one photon absorption of linearly polarized light by a
-semiconductor, with filled valence bands and empty conduction bands, illuminated
-by light with photon energy larger than the energy gap. This phenomenon can
-result from spin injection,\cite{malPRB03} Hall Effects,\cite{sinovaPRB04}
-interference of two optical beams,\cite{bhatPRL00, najmaiePRB03} or one photon
-absorption of linearly polarized light\cite{bhatPRL05} and has been observed in
-gallium arsenide (GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium
-arsenide (AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
+electrical current \cite{awschalomSSBM13} or pure spin current (PSC). One of
+the difficulties in {\color{red}\st{achieving}} {\color{blue}creating} measurable  the of spin current and
+development of PSC based semiconductor devices is the fact that the spin
+relaxation time in conventional semiconducting materials is short to enable the
+spin transport, thus resulting in a non-observable spin
+current.\cite{murakamiSc03} For PSC there is no net motion of charge; spin-up
+electrons move in a given direction, while spin-down electrons travel in the
+opposite one. This effect can be due to one-photon absorption of linearly
+polarized light by a semiconductor, with filled valence bands and empty
+conduction bands, illuminated by light with photon energy larger than the
+energy gap. This phenomenon can be due to spin injection,\cite{malPRB03} Hall
+Effects,\cite{sinovaPRB04} interference of two optical beams,\cite{bhatPRL00,
+najmaiePRB03} or one photon absorption of linearly polarized
+light\cite{bhatPRL05}. The last effect has been observed in gallium arsenide
+(GaAs),\cite{zhaoPRL2006, stevensPRL03} aluminum-gallium arsenide
+(AlGaAs),\cite{stevensPRL03} and Co$_2$FeSi.\cite{kimuraNGPAM12}
 
-Graphene, an allotrope of carbon with hexagonal 2D lattice structure, presents
-properties like fractional quantum Hall effect at room temperature, excellent
-thermal transport properties, excellent conductivity\cite{heerscheNat07} and
-strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08}, being then a
-perfect platform to be used in two-dimension electronic systems; however, most
-electronic applications are disabled by the absence of a semiconducting gap.
-Recent studies demonstrate that the band gap of graphene can be opened by
-applying an electric field,\cite{zhangN09} reducing the surface
-area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
-possibility to open the gap is by doping; this has been successfully achieved
-using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
-silicon,\cite{colettiPRB10} noble-metals,\cite{varykhalovPRB10} and
-hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
-Depending on the percentage of hydrogenation and spatial configurations of
-hydrogen-carbon bonds, hydrogenated graphene can result in different spatial
-configurations.
-In this paper, we present two 50\% hydrogenated graphene noncentrosymmetric
-structures, both presenting a discernible band gap: the Up structure, shown in
-Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer only on
-the upper side of the structure, while the Alt structure, shown in Fig. 
+Graphene, an allotrope of carbon with hexagonal 2D lattice structure,
+demonstrates properties such as fractional quantum Hall effect at room
+temperature, excellent thermal transport properties, excellent
+conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
+novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
+electronic systems; however, most electronic applications are disabled by the
+absence of a semiconducting gap. Recent studies demonstrate that a narrow band
+gap  can be opened in graphene by applying an electric field,\cite{zhangN09}
+reducing the surface area,\cite{hanPRL07} or applying uniaxial
+strain.\cite{niACSN08} Another possibility to open the gap is by doping; this
+has been successfully achieved using nitrogen,\cite{weiNL2009} boron-
+nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-
+metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
+samarakoonACSN10} Depending on the percentage of hydrogenation and spatial
+arrangements of the hydrogen-carbon bonds, hydrogenated graphene demonstrates
+different structural configurations and a tunable electron gap, as it has been
+proven in [1]. In this paper, we present two 50\% hydrogenated graphene
+noncentrosymmetric structures, both presenting a discernible band gap. The
+first one, labelled as the Up structure, also known as
+graphone,\cite{gmitraPRL13} shown in Fig. \ref{fig:up-struc}. Graphone has
+hydrogen atoms bonded to the carbon layer only on the upper side of the
+structure, we consider here the magnetic isomer of graphone, with the so-called
+“chair” structure. In contrast,  the Alt structure, shown in Fig. 
 \ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
-the carbon slab.\cite{zapataPSB2016}
+the carbonsheet.\cite{zapataPSB2016}
 
@@
     \centering
-    \includegraphics[width=\tama]{figures/upstruc2}
-    \\
-    \includegraphics[width=\tama]{figures/upstruc1}
+    \includegraphics[width=\tama]{figures/fig1}
     \caption{Side (top panel) and top (bottom panel) views of the Up
+      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is also shown.
       structure along with the 
-      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms. 
 }
@@
     \centering
-    \includegraphics[width=\tama]{figures/altstruc2}
-    \\
-    \includegraphics[width=\tama]{figures/altstruc1}
+    \includegraphics[width=\tama]{figures/fig2}
     \caption{Side (top panel) and top (bottom panel) views of the Alt
-      structure along with the 
-      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms.
-}
+      structure along with the $xyz$ directions. The dark (light) spheres are
+      the C (H) atoms. The primitive rectangular unit cell is also displayed.}
     \label{fig:alt-struc}
@@
 
-Using those structures, we address a theoretical study of the spin velocity
-injection (SVI) by one-photon absorption of linearly polarized light. Since we
-have 2D structures, we do the analysis for two cases. The first is by fixing the
-spin of the electrons along the $z$ Cartesian direction, with the velocity
-directed onto the surface of the structure on the $xy$ plane. The second is by
-fixing the spin velocity in the $x$ or $y$ direction and the spin directed to
-$xyz$. The SVI is an optical effect that quantifies the velocity at which a PSC
-moves along the Cartesian direction, $\mathrm{a}$, with the spin of electron
-polarized along the Cartesian direction $\mathrm{b}$. One photon absorption of
-linearly polarized light can promote an even distribution of electrons in
-$\mathbf{k}$ space, regardless of the symmetry of the material, resulting in a
-null electrical current.\cite{bhatPRL05} Then, the electrons excited to the
+Using those structures, we address theoretically the spin velocity injection
+(SVI) by one-photon absorption of linearly polarized light. Since wehave 2D
+structures, we do the analysis for two cases {\color{red}(not clear to me this
+sentence)}. The first case is by fixing the spin of the electrons along
+vertical to the surface direction {\color{red}(?)}$z$, , with the velocity
+directed onto {\color{red}(is this parallel or not?)} the surface of the
+structure in the $xy$ plane. In the second case we fix the spin velocity in the
+$x$ or $y$ direction and the resulting spin is then directed outward of the
+$xy$ plane. The SVI is an optical effect that quantifies the velocity, at which
+a PSC moves along the direction $\bf{a}$ with the $\bf{a}$ components to be
+determined, with the spin of electron polarized along the direction $\bf{b}$.
+polarized light produce an even distribution of electrons in $\mathbf{k}$
+space, regardless of the symmetry of the material, resulting in a null
+electrical current.\cite{bhatPRL05} Then, the electrons excited to the
 conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
-polarizations producing no net spin injection.\cite{bhatPRL05} If the
-crystalline structure of the material is noncentrosymmetric, the spin
-polarization injected at a given $\mathbf{k}$ point not necessarily
-vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88} and then, since the velocities
-of electrons at opposite $\mathbf{k}$ points are opposite, a PSC will be
-produced. Since the structures presented here are noncentrosymmetric, they are
-good candidates in which this effect can be induced.
+polarizations producing no net spin injection in centrosymmetric materials
+{\color{red}(?)}.\cite{bhatPRL05} If the crystalline structure of the material
+is noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
+point not necessarily vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88}.
+Therefore, since the velocities of electrons at opposite $\mathbf{k}$ points
+are opposite, a PSC will be produced. Since both the structures presented here
+are noncentrosymmetric, they are good candidates in which this effect can be
+induced.
 
 This paper is organized as follows. In Section \ref{sec:theory} we present the
-theory and formulas that describe PSC and SVI. In Section \ref{sec:results} we
-describe the details of calculations and the corresponding SVI spectra for the
-Up and Alt structures. Finally, we present our conclusions in
-Section \ref{sec:conclusions}.
+formalism and the main expressions  that describe PSC and SVI. In Section
+\ref{sec:results} we describe the numerical details  and  discuss the
+corresponding SVI spectra for the Up and Alt structures. Finally, we summarize
+our finding in Section \ref{sec:conclusions}.
 
-\section{Theory} % (fold)
+\section{Theory}
 \label{sec:theory}
 
-In this section, we report a summary of the theory  involved in the
-calculation of the spin velocity
-injection (SVI) resulting from the
-pure spin current (PSC).
+In this section, we  summarize the theoretical approach, involved in
+calculation of the spin velocity injection (SVI) resulting from the pure spin
+current (PSC).
 
@@
 \end{align} 
-where $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ is the velocity
-operator, with $\hat {\mathbf r}$ being the position operator and $\hat H_0$ the
-unperturbed ground state Hamiltonian; the Roman superscripts  indicate Cartesian
-coordinates. To obtain the expectation value of $\hat K^{\mathrm{a}\mathrm{b}}$,
-we use the length gauge for the perturbing Hamiltonian, written as
+where $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ 
+is the velocity operator, with
+$\hat {\mathbf r}$ 
+being the position operator and $\hat H_0$ the unperturbed
+the Roman superscripts  indicate Cartesian coordinates. 
+ground state Hamiltonian;
+To obtain the expectation value of 
+$\hat K^{\mathrm{a}\mathrm{b}}$, we use the length gauge for the perturbing
+Hamiltonian, written as
 \begin{align}\label{z.2}
@@
 \end{align}   
-where the electric field of the applied laser is given by
+where the applied electric field of the laser is given by
 \begin{align}\label{z.3}
@@
 to take into account the excited coherent superposition of the spin-split
-conduction bands inherent to the noncentrosymmetric semiconductors considered in
-this work.
+conduction bands inherent to the noncentrosymmetric semiconductors considered
+in this work.
 %Although, this splitting is small [15,16], is required to obtain the correct
@@
 %narrow energy widths, dephasing effects lead to an energy width of the bands
-%large enough that spin-split states can become quasidegenerate.
-To include the coherences, we follow Ref.~\onlinecite{nastosPRB05} and use a
-multiple scale approach that solves the equation of motion for the single
+%large enough that spin-split states can become quasi-degenerate.
+To include the coherence, we follow Ref.~\onlinecite{nastosPRB05} and
+use a multiple
+scale approach that solves the equation of motion for the single
 particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
@@
 &\frac{\partial \rho_{cc'}({\mathbf k})}{\partial t} =
-\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}{i \hbar^{2}}
+\frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
+{i \hbar^{2}}
 \sum_{v}r^{\mathrm{a}}_{cv}({\mathbf k}) r^{\mathrm{b}}_{vc'}({\mathbf k})
-\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k}) - i \epsilon} - 
+\left( \frac{1}{\omega - \omega_{c'v}({\mathbf k}) - i \epsilon} 
+- 
 \frac{1}{\omega - \omega_{cv}({\mathbf k}) + i \epsilon} \right)
@@
 \end{align}
-where we assumed that the conduction bands $c$ and $c'$ are quasidegenerate
+where we assumed that the conduction bands $c$ and $c'$ are quasi-degenerate
 states, and we take $\epsilon\to 0$ at the end of the calculation. The spin-
@@
 \begin{align}
-\dot{\mathcal{O}} &=
-\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
+\dot{\mathcal{O}} 
+&=\frac{e^{2}}{i\hbar^{2}} \int \frac{d^{3}k}{8\pi^{3}} 
 \sum'_{cc'} \mathcal{O}_{c'c}({\mathbf k}) 
@@
 \end{align}
-Replacing $\hat{\cal O} \rightarrow \hat{K}^{\mathrm{ab}}$, in the above
-expression, one can show that
+The prime symbol $'$ in the sum means that $c$ and $c'$ are quasi-degenerate
+states, and the sum only covers these states. Replacing  $\hat{\cal O}
+\rightarrow \hat{K}^{\mathrm{ab}}$, in the above expression, one can show that
 \begin{equation}
-\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
+\dot{K}^{\mathrm{ab}}(\omega) =
+\mu^{\mathrm{abcd}}(\omega)
 E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
@@
 is the pseudotensor that describes the rate of change of the  PSC process in
-semiconductors. To derive what we presented above we used
-$K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
-follows from time-reversal invariance. The prime symbol $'$ in the sum means
-that $c$ and $c'$ are quasi degenerate states, and the sum only covers these
-states. Since $\mu^{\mathrm{abcd}}(\omega)$ is real, we have that
-$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$. We remark that
-Eq.~\eqref{eq:mu} is the same as Eq. (3) of Bhat et al.\cite{bhatPRL05},
-obtained by using the semiconductor optical Bloch equations. Using the closure
-relation,
+semiconductors. To derive what we presented above we used $
+K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+follows from time-reversal invariance. Since $\mu^{\mathrm{abcd}}(\omega)$ is
+real, we have that $\mu^{\mathrm{abcd}}(\omega) =
+\mu^{\mathrm{abdc}} (\omega)$. We point out that Eq.~\eqref{eq:mu} is
+–identical to Eq. (3) of Bhat et al.\cite{bhatPRL05}, derived using the
+semiconductor optical Bloch equations. Using the closure relation,
 \begin{equation}
-K^{\mathrm{ab}}_{cc'}({\mathbf k}) = 
-\frac{1}{2} \sum_{l=v,c}
+K^{\mathrm{ab}}_{cc'}({\mathbf k}) = \frac{1}{2}
+\sum_{l=v,c}
 \left(v^{\mathrm{a}}_{cl}({\mathbf k})S^{\mathrm{b}}_{lc'}({\mathbf k})
@@
 \right)
-.
+,
 \label{eq:velspimatelem}
@@
 
-Now, we define the spin velocity injection (SVI) as
+We define the spin velocity injection (SVI) as
 \begin{equation}\label{eq:vab-w}
@@
 \end{equation}  
-which gives the velocity, along direction $\mathrm{a}$, at which the spin moves
-in a polarized state along direction $\mathrm{b}$. The carrier injection rate
-$\dot n(\omega)$ is written as,\cite{nastosPRB05}
+which gives the velocity, along direction $a$, at which the spin moves in a
+polarized state along direction $b$. The carrier injection rate $\dot
+n(\omega)$ is written as\cite{nastosPRB05}
 \begin{equation}
@@
 \begin{equation}\label{eq:xi}
-\xi^{\mathrm{ab}}(\omega) =
+\begin{aligned}
+\xi^{\mathrm{ab}}(\omega)
+&
+=
 \frac{2\pi e^{2}}{\hbar^{2}} \int 
-\frac{d^{3}k}{8 \pi^{3}} \sum_{vc}
+\frac{d^{3}k}{8 \pi^{3}}
+ \sum_{vc}
 r^{\mathrm{a}}_{vc'}({\mathbf k})  
 r^{\mathrm{b}}_{cv }({\mathbf k})  
-\delta(\omega-\omega_{cv}({\mathbf k}) 
-, 
+\delta(\omega-\omega_{cv}({\mathbf k})), 
+\end{aligned}
 \end{equation}
@@
 
-The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify two
-very important aspects of PSC. On one hand, we can fix the spin direction along
-$\mathrm{b}$ and calculate the resulting electron velocity. On the other hand,
-we can fix the velocity of the electron along $\mathrm{b}$ and study the
-resulting direction along which the spin is polarized. To this end, the added
-advantage of  2D structures, besides choosing them as noncentrosymmetric, is
-that we can use an incoming linearly polarized beam of light at normal
-incidence, and use the  direction of the polarized  electric field to control
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$. Indeed, writing ${\mathbf E}(\omega)
-= E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$, where
+The function ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ allows us to quantify
+two very important aspects of PSC. On one hand, we can fix the spin direction
+along $\mathrm{b}$ and calculate the resulting electron velocity. On the other
+hand, we can fix the velocity of the electron along $\mathrm{b}$ and study the
+resulting direction along which the spin is polarized. To this end, the
+additional advantage of  2D structures, besides being noncentrosymmetric, is
+that we can use an incoming linearly polarized  light at normal incidence, and
+use the  direction of the polarized  electric field to control ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega)$. Indeed, writing ${\mathbf E}(\omega) =
+E_0(\omega)(\cos\alpha\,\hat{\mathbf x}+\sin\alpha\,\hat{\mathbf y})$, where
 $\alpha$ is the polarization angle, we obtain from Eq. \eqref{eq:vab-w} that
 \begin{widetext}
-\begin{equation}
-\mathcal{V}^{\mathrm{ab}}(\omega,\alpha) = 
+\begin{align}
+\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
+&= 
 \frac{2}{\hbar\xi(\omega)}
@@
 \label{eq:vab-aw}
-\end{equation}
+\end{align}
 \end{widetext}
-for the structures chosen in this article, $\xi^{\mathrm{xx}}(\omega) =
-\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and $\xi^{\mathrm{xy}}(\omega)=0$.
-Now, we formalize our two options for ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$.
+for the structures chosen in this article,
+$\xi^{\mathrm{xx}}(\omega)=\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and
+$\xi^{\mathrm{xy}}(\omega)=0$. Next, we identify two options for ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega)$.
 
-\subsection{Fixing spin}\label{sec:theory-fixspin}
+\subsection{Fixing the spin polarization}\label{sec:theory-fixspin}
 
-Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the
-electron velocity on the plane of the structure, with the spin polarized along
-the $\mathrm{b}$ direction as
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define {\color{red}(calculate?)} the magnitude
+of the electron velocity along the plane of the structure, with the spin
+polarized along $\mathrm{b}$ direction as
 \begin{equation}
-\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha) \equiv
+\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)
+\equiv
 \sqrt{
@@
 \begin{equation}
-\gamma_{\sigma^\mathrm{b}} (\omega,\alpha) =
+\gamma_{\sigma^\mathrm{b}} (\omega,\alpha)
+=
 \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
@@
 corresponding to the electron velocity being parallel or perpendicular to the
-incoming polarization, respectively. The subscript $\sigma^\mathrm{b}$ denotes
-the spin along $\mathrm{b}$.
+incoming light polarization, respectively. The subscript $\sigma^\mathrm{b}$
+denotes the spin along $\mathrm{b}$.
 
-\subsection{Fixing velocity.}\label{sec:theory-fixvel}
+\subsection{Fixing the electron velocity.}\label{sec:theory-fixvel}
 
-Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$,
-we define its corresponding magnitude as
+Fixing the calculated velocity along $\mathrm{a}=x$ or $\mathrm{a}=y$, we
+define its corresponding magnitude as
 \begin{align}
@@
 from where we see that the spin would be oriented in the $xyz$ system's
-coordinates according to a polar angle
+coordinates defined with a polar angle
 \begin{equation}
@@
 
-\section{Results} % (fold)
+\section{Results}
 \label{sec:results}
@@
 C &  0.61516 &  0.35763 & -0.49087 \\
+C &  0.61518 &  1.77416 & -0.73196 \\
 \hline
 \end{tabular}
-\caption{Atomic positions in the unit cell of Up structure. 
-}
+\caption{Atomic positions in the unit cell of Up structure as the structural
+input for our calculations. {\color{blue}The primitive hexagonal unit cell
+contains two C and one H atoms as shown in Fig. \ref{fig:up-struc})}. }
 \label{tab:up-unitcell}
@@
 \end{tabular}
-\caption{Atomic positions in the unit cell of Alt structure. 
-}
+\caption{Atomic positions in the unit cell of Alt structure, which coincides
+with its primitive cell. }
 \label{tab:alt-unitcell}
@@
 
-We present the results of $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
-$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-up  and
-C$_{16}$H$_{8}$-alt structures, being both noncentrosymmetric semi-infinite 2D
-carbon systems with 50\% hydrogenation in different arrangements. We recall that
+We present the calculated results of
+$\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
+$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-Up  and
+C$_{16}$H$_{8}$-Alt structures, both noncentrosymmetric 2D carbon systems with
+50\% hydrogenation, which are differently structurally arranged. We remind that
 the Up structure has hydrogen atoms only on the upper side of the carbon sheet,
 while the Alt structure has alternating hydrogen atoms on the upper and bottom
-sides. Also, we take the hexagonal carbon lattice to be on the $xy$ plane for
-both structures, and the carbon-hydrogen bonds on the perpendicular $xz$ plane,
-as depicted in Figs. \ref{fig:up-struc} and \ref{fig:alt-struc}. The coordinates
-for the Up and Alt unit cells of the structures are presented in Tables 
-\ref{tab:up-unitcell} and \ref{tab:alt-unitcell}.
+sides. We take the carbon lattice to be along the $xy$ plane for both
+structures, and the carbon-hydrogen bonds are outward the plane, they are
+perpendicular to  $xz$ plane for the Up structure, as depicted in Figs.
+\ref{fig:up-struc}, and off the normal for the Alt structure 
+\ref{fig:alt-struc}. The coordinates for the Up and Alt unit cells of the
+structures are presented in Tables \ref{tab:up-unitcell} and 
+\ref{tab:alt-unitcell}.
 
-We calculated the self-consistent ground state and the Kohn-Sham states using
+We calculated the self-consistent ground state and the Kohn-Sham states within
 density functional theory in the local density approximation (DFT-LDA), with a
@@
 needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
-\eqref{eq:mu}. The convergence parameters for the calculations of our results
-corresponding to the Up and Alt structures are cutoff energies of 40\,Ha and
-65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
-respectively. The energy eigenvalues and matrix elements for the Up and Alt
-structures were calculated using 12802 ${\mathbf k}$ points and 14452 ${\mathbf
-k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\omega)$ and
-$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ using the linearized analytic tetrahedron
-method (LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
+\eqref{eq:mu}.
+The convergence parameters for the calculations,  corresponding to the Up and
+Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting in LDA
+energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
+eigenvalues and matrix elements for the Up and Alt structures were calculated
+using 12802 ${\mathbf k}$ points and 14452 ${\mathbf k}$ points in the IBZ; to
+integrate $\mu^{\mathrm{abcd}}(\omega)$ and
+$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the linearized analytic tetrahedron method
+(LATM) has been used.\cite{nastosPRB07} We neglect the anomalous velocity term
 $\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
@@
 \hat v^\mathrm{a}$. Finally, the prime in the sum of Eq.~\eqref{eq:mu} is
-restricted to quasidegenerated conduction bands $c$ and $c'$ that are closer
-than 30 meV, where this value is both a typical laser- pulse energy width and
-the room-temperature energy.\cite{nastosPRB07}
+restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
+than 30 meV, which  is both typical laser- pulse energy width and the thermal
+room-temperature energy level broadening.\cite{nastosPRB07}
 
-\subsection{SVI: Spin velocity injection} % (fold)
+\subsection{SVI: Spin velocity injection}
 \label{sec:res-spin_velocity}
@@
 \centering
-\includegraphics[width=\tama]{plots/2-vab-str-comp}
+\includegraphics[width=\tama]{figures/fig3}
 \caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
-  vs. $\hbar\omega$, for the values of $\alpha$ that maximize the signal. The
-  low energy regions for the Alt and Up structures start at the energy gap of
-  each structure, while in the high energy regions, the values of
-  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large. The bottom
-  panel corresponds to CdSe and GaAs. }
+  vs. $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
+  largest velocity are at the low energy regions of the spectra for the Alt and
+  Up structures, starting {\color{red}(going up?)} at the energy gap of each
+  structure. In the high energy regions, the values of
+  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to
+  the 3D case of CdSe and GaAsThe, shown at the bottom panel . }
 \label{fig:vab-str-comp}
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\omega$ for the directions $\mathrm{a}\mathrm{b}$,
-and for the angle $\alpha$ that maximizes the signal, for the Up  and Alt
-structures and for CdSe and GaAs, which are bulk systems shown for comparison.
-As expected from the delta function of Eq.~\eqref{eq:mu}, ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises right at the corresponding
-energy gap of each system. For the 2D structures, the spectrum covers two narrow
-energy regions with large values of response, while for bulk systems, the
-spectra covers a rather wide energy range, but with a much smaller response. For
-the Up structure, $\mathrm{a}\mathrm{b}=yz$ and $\alpha=35^\circ$ maximize the
-response, which means that an incoming beam of light with its electric field
-polarized at 35$^\circ$ from the $x$ direction will induce electrons to move
-along $y$ (parallel to the surface), with their spin polarized along $z$
-(perpendicular to the surface), with the following speeds. Right at the energy
-onset, ${\cal V}^{yz}(\omega,\alpha)=668$\,Km/s, a speed that remains almost
-constant for 65 meV, and then goes to zero. A second region is found above 1.946
-eV, where there are two extreme values of the speed, ${\cal
+(\omega,\alpha)$ vs. $\hbar\omega$ for the {\color{blue}velocity and spin
+directions} $\mathrm{a}$ and $\mathrm{b}$, and for the angle $\alpha$, at which
+the signal is maximized , for the Up  and Alt structures, and for CdSe and GaAs
+bulk systems, shown for comparison. As expected from Eq.~\eqref{eq:mu}, ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises from zero right at the
+corresponding energy gap of each system. For the 2D structures considered, the
+spectrum contains two narrow energy regions with strong response, while for the
+bulk systems, the spectra covers a rather wide energy range, but with a much
+weaker response. For the Up structure, at $\mathrm{a}\mathrm{b}=yz$ and
+$\alpha=35^\circ$ the response is maximized, which means that an incoming light
+with its electric field polarized at 35$^\circ$ from the $x$ direction will
+induce electrons to move along $y$, parallel to the surface, with their spin
+polarized along $z$, perpendicular to the surface. The corresponding speeds
+are the following: Right at the energy onset, ${\cal
+V}^{yz}(\omega,\alpha)=668$\,Km/s, remains almost constant for 65 meV, and then
+decreases to zero. A second region with high velocity is above 1.946 eV with
+two, opposite in sign, maxima of the speed: ${\cal
 V}^{yz}(\omega,\alpha)=266.3$ Km/s at $\hbar\omega=1.954$\,eV, and ${\cal
@@
 $\hbar\omega=1.958$\,eV; a positive (negative) ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move parallel
-(antiparallel) to the electric field. Likewise, for the Alt structure, we find
-that also $\mathrm{a}\mathrm{b}=yz$ and $\alpha=150^\circ$ maximizes the
-response, where two extreme values of ${\cal V}^{\mathrm{y}\mathrm{z}}$ are
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ means that the electrons move
+parallel (antiparallel) to the electric field. Likewise, for the Alt structure,
+we also find that $\mathrm{a}\mathrm{b}=yz$ and $\alpha=150^\circ$ maximizes
+the response, where two extreme values of ${\cal V}^{\mathrm{y}\mathrm{z}}$ are
 found, one at  $\hbar\omega=0.720$\,eV of ${\cal
-V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at $\hbar\omega=0.911$\,eV
-of ${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.
+V}^{\mathrm{y}\mathrm{z}}=-711.9$ Km/s, and the other at
+$\hbar\omega=0.911$\,eV of ${\cal V}^{\mathrm{y}\mathrm{z}}=-330.6$ Km/s.
 
 For the bulk structures, we calculate ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$
-from Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$. For
-CdSe, we find that for $\hbar\omega=0.844$\,eV,
+from Eq.~\eqref{eq:vab-w} by simply using $\boldsymbol{\mu}_{\mathrm{max}}$.
+For CdSe, we find that for $\hbar\omega=0.844$\,eV,
 $\boldsymbol{\mu}_{\mathrm{max}}\to \mu^{zzzz}$, and ${\cal
 V}^{\mathrm{z}\mathrm{z}}(\omega)=-59.0$ Km/s, and for GaAs at
-$\hbar\omega=2.324$\,eV, $\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$
-and ${\cal V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with
-$\mathrm{a}=x,y,z$. For these bulk semiconductors, the $x$, $y$, and $z$ axis
-are taken along the standard cubic unit cell directions, [100], [010], and
-[001], respectively. In Table \ref{tab:vab-str-comp}, we present the comparison
-of ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures and
-bulk crystals. We remark that, as shown in the figure, the 2D structures have
-maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ that are bigger than
-for the bulk crystals; in particular, the Alt structure gives a ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ $\sim$12 times larger than that of
-CdSe and GaAs.
+$\hbar\omega=2.324$\,eV,
+$\boldsymbol{\mu}_{\mathrm{max}}\to\mu^{\mathrm{aaaa}}$ and ${\cal
+V}^{\mathrm{a}\mathrm{a}}(\omega,\alpha)=-28.7$\,Km/s, with $\mathrm{a}=x,y,z$.
+For these bulk semiconductors, the $x$, $y$, and $z$ axis are taken along the
+standard cubic unit cell directions, [100], [010], and [001], respectively. In
+Table \ref{tab:vab-str-comp}, we compare ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures considered and
+bulk crystals. We stress that, as shown in the figure, for the 2D structures
+have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ are higher than
+for the bulk crystals. In particular, the Alt structure demonstrates a ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than that
+of CdSe and GaAs.
 \begin{table}%[b]
@@
 \multirow{2}{*}{Structure \quad} & 
-Kind of \quad & 
+System \quad & 
 Pol. &
@@
 \cline{5-6}
-& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
+& type & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
 \hline
-Up    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
+$Up$  & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
       &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
       &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
-Alt   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
+$Alt$ & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
       &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
@@
 \end{tabular}
-\caption{Comparison of the reported maximum values of $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ for the different structures and their corresponding
-polarization angle $\alpha$ and $\hbar\omega$ energy values. }
+\caption{Comparison of the reported maximum values of
+$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the different structures and
+their corresponding polarization angle $\alpha$ and energy $\hbar\omega$ . }
 \label{tab:vab-str-comp}
@@
 
-\subsection{Fixing spin} % (fold)
+\subsection{Fixing spin}
 \label{sec:res-fixspin}
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vsz-w1}
-\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
-$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), and ${\cal
-V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black line), vs. $\alpha$,
-for $\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the 3D plot. }
+\includegraphics[width=\tama]{figures/fig4}
+\caption{Color online. For the Up structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ SvsS. $\hbar\omega$ and $\alpha$, and
+the bottom panel shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right
+scale, red line, {\color{red}long dashes?}), and ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid
+line{\color{red}?}), $vs$. $\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along
+the ridge shown in the 3D plot. }
 \label{fig:up-vsz-w1}
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vsz-w2}
-\caption{For the Up structure, the top panel shows ${\cal V}_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the bottom panel shows
-$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), and ${\cal
-V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale, black line), vs. $\alpha$,
-for $\hbar\omega=1.954$\,eV, i.e. along the highest ridge shown in the 3D plot.
-}
+\includegraphics[width=\tama]{figures/fig5}
+\caption{For the Up structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
+red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
+(left scale, black solid line), vs. $\alpha$, for $\hbar\omega=1.954$\,eV, i.e.
+along the highest ridge shown in the 3D plot. }
 \label{fig:up-vsz-w2}
@@
 In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$,
-Eq. \eqref{eq:vs-mag}, for the case where the spin is fixed along $z$, i.e.
+Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
-calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$, Eq. \eqref{eq:gamma-ang},
-which determines the direction along which the injected electrons move along the
-surface of  each structure. We mention that we have also made the analysis for
-the cases when the spin  is directed along $\mathrm{x}$ or $\mathrm{y}$, finding
-similar qualitative results to those presented below.
+calculate $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ from Eq. 
+\eqref{eq:gamma-ang}, which determines the direction  of the injected 
+electrons movement along the surface of  each structure. We mention that we
+have also  analyzed the cases when the spin  is directed along $\mathrm{x}$ or
+$\mathrm{y}$, finding similar qualitative results to those presented below.
 
@@
 structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
-$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that maximizes at
-$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV, with a value of
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s, and that the
-variation of $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function
-of $\alpha$, which comes from the interplay of the $\boldsymbol{\mu}$ tensor
-components as multiplied by the  trigonometric functions of 
-Eq.~\eqref{eq:vab-aw}, gives a sizable set of values between 739.7\,Km/s and 
-165.4\,Km/s, for 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel,
-we show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left
-scale, black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge shown
-in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
-$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where it is
-very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at
-64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for the
-whole range of $\alpha$. This results means that for $\hbar\omega=0.084$ eV and
-for all values of $\alpha$, the electrons, with the chosen spin pointing along
-$z$, will move at an angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha) \sim
-64.5^{\circ}$ with respect to the $x$ direction, with the range of  high speeds
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure. Also,
-from Eq. \eqref{eq:gamma-par} we find that $\gamma^\parallel_{\sigma^\mathrm{z}}
-(\omega,\alpha)=\alpha = 64.56^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 631.1$\,Km/s (see green arrow), and that from Eq.
-\eqref{eq:gamma-perp}, $\gamma^\perp_{\sigma^\mathrm{z}} (\omega,\alpha) =
-\alpha-90^\circ=64.50^\circ$, gives $\alpha=154.50^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 191.5$ Km/s (see blue
-arrow); thus, at $\hbar\omega=0.084$ eV, an incident field polarized at $\alpha
-\sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their spin
-polarized along $z$, which move parallel or perpendicular to the incident
+$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
+of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s at
+$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV,  The variation of
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\alpha$,
+which comes from the interplay of the $\boldsymbol{\mu}$ tensor components as
+multiplied by the  trigonometric functions of Eq.~\eqref{eq:vab-aw}, gives a
+sizable set of values between 739.7\,Km/s and 165.4\,Km/s, for
+0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ $vs.$ $\alpha$ (left scale,
+black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
+plot of the top panel. Also, we plot the corresponding velocity angle
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where it
+is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
+at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for
+the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
+and for all values of $\alpha$, the electrons, with the chosen spin pointing
+along $z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)
+\sim 64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
+speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
+Also, from Eq. \eqref{eq:gamma-par} we find that
+$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$,
+with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see
+green arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
+gives $\alpha=154.50^\circ$, with
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
+arrow). Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
+$\alpha \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their
+spin polarized along $z$, which move parallel or perpendicular to the incident
 electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.
@@
 Now, we analyze the results for the second energy range of the Up structure
-shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of
-Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
+shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
+of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
 (\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
-black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
-$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where in
-this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$ have more
-dispersion, as a function of $\alpha$, than for the lower energy range shown in
-the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
-$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is constant from
-$\alpha=0^\circ$ and up to $\alpha\sim 85^\circ$. In this case, we find that
+black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
+shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
+angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line),
+where in this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$
+have more dispersion, as a function of $\alpha$, than for the lower energy
+range shown in the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
+$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
+$\alpha=0^\circ$ up to $\alpha\sim 85^\circ$. In this case, we find that
 $\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (see green
-arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (as indicated
+by green arrow), and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
@@
 inject electrons, in this case with their spin polarized along $z$, which move
-parallel or perpendicular to the incident electric field, with finite speeds.
-
+parallel or perpendicular to the incident electric field, with finite speeds
+{\color{red}(what does “finite” mean?)}.
 % the maxima for
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vsz}
-\caption{For the Alt structure, the top panel shows ${\cal
+\includegraphics[width=\tama]{figures/fig6}
+\caption{Color online. For the Alt structure, the top panel shows ${\cal
 V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
 bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
-red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale, black
-line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge shown in
-the 3D plot.}
+red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale,
+black line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge
+shown in the 3D plot.}
 \label{fig:alt-vsz}
@@
 180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
-$\hbar\omega= 0.720$\,eV, with a value of$\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 644.9$\,Km/s. In the bottom panel, we  show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
-black line), at $\hbar\omega= 0.720$\,eV, thus following the highest ridge shown
-in the 3D plot of the top panel. Also, we plot the corresponding velocity angle
-$\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale, red line), where now
-we see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$
-having variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq \alpha \leq 180^
-{\circ}$. In this case, we find that $\gamma^\parallel_{\sigma^\mathrm{z}}
-(\omega,\alpha) = \alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 450.05$\,Km/s (see green arrow), and that from Eq. 
-\eqref{eq:gamma-perp},$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha) = 
-\alpha-90^\circ=110.0^\circ$, gives $\alpha=20.0^\circ$, with $\mathcal{V}_
-{\sigma^{\mathrm{z}}} (\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as 
-for the Up structure, we could inject electrons with a fixed spin which move
-parallel or perpendicular to the incident electric field.
+$\hbar\omega= 0.720$\,eV, with a value of
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
+panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+$\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV, thus following
+the highest ridge shown in the 3D plot of the top panel. Also, we plot the
+corresponding velocity angle $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$
+(right scale, red line), where now we see that
+$\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
+variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
+\alpha \leq 180^{\circ}$. In this case, we find that
+$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
+\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)
+= 450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
+gives $\alpha=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
+(\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
+we could inject electrons with a fixed spin, which moves parallel or
+perpendicular to the incident electric field.
 % Again, for the cases in which the spin polarization is parallel to the
@@
 
-\subsection{Fixing velocity} 
+\subsection{Fixing the electron velocity} 
 \label{sec:res-fixvel}
 
-We calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. \eqref{eq:vv-mag})
-fixing the electron velocity direction, $\mathrm{a}$, to the $x$ or $y$
-direction along the surface of the Up and Alt structures. From Eqns.
-\eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the polar,
-$\theta_{\mathrm{a}} (\omega,\alpha)$, and azimuthal, $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, angles corresponding to the direction of the spin.
+Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. 
+\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\mathrm{a}$,
+to the $x$ or $y$ direction along the surface of the Up and Alt structures.
+From Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, {\color{blue}we
+determined the corresponding polar angle, $\theta_{\mathrm{a}}
+(\omega,\alpha)$, and azimuthal angle, $\varphi_{\mathrm{a}} (\omega,\alpha)$}.
 
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vx-vy-w1}
-\caption{For the Up structure, we show
+\includegraphics[width=\tama]{figures/fig7}
+\caption{The Up structure: the velocity $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and  the azimuthal angle
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
+shown. }
+\label{fig:up-vab-comp-rtp-1}
+\end{figure}
+
+For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes
+the response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot
 $\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x,y$. }
-\label{fig:up-vab-comp-rtp-1}
-\end{figure}
-
-For the Up structure, we find once again that  $\alpha=35^{\circ}$ maximizes the
-response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
-(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
-scale, blue line), vs. $\hbar\omega$, for $\mathrm{a}=x,y$. We see that for
-$\hbar\omega=0.084$\,eV, the response has a maximum of $\mathcal{V}_{\mathrm{x}}
-(\omega,\alpha)=431.7$\,Km/s, with $\theta_{\mathrm{x}}(\omega,\alpha) =
+$\hbar\omega$, for $\mathrm{a}=x,y$. We see that for $\hbar\omega=0.084$\,eV,
+the response has a maximum of $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha)=431.7$\,Km/s at $\theta_{\mathrm{x}}(\omega,\alpha) =
 42.5^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) = 208.3^{\circ}$, and
-$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s, with
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=687.9$\,Km/s at
 $\theta_{\mathrm{y}}(\omega,\alpha) = 13.9^{\circ}$, and $\varphi_{\mathrm{y}}
-(\omega,\alpha) = 82.1^{\circ}$. This means that the spin is directed upward the
-third Cartesian quadrant of the $xy$ plane when the electron moves along $x$,
-and is directed almost parallel to the $xy$ plane in the first quadrant when it
-moves along $y$. Also, from this figure we have that when the electron moves
-along $x$, the spin direction is almost constant for all the energies across the
-peak of the response, having $42.5^{\circ}<\theta_{\mathrm{x}} (\omega,\alpha) <
-53.7^{\circ}$ and $208.3^{\circ}<\varphi_{\mathrm{x}} (\omega,\alpha) <
-215.7^{\circ}$, and when the electron moves along $y$, the spin polar angle has
-again small variations, $11.3^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) <
-13.9^{\circ}$, but the azimuthal angle has significant variations, $82.1^{\circ}
-< \varphi_{\mathrm{y}} (\omega,\alpha)<182.4^{\circ}$.
+(\omega,\alpha) = 82.1^{\circ}$. This means that the spin is directed upward
+the third quadrant of the $xy$ plane when the electron moves along
+$x$, and is almost parallel to the $xy$ plane in the first quadrant
+when it moves along $y$. Also from this figure, we see that when the electron
+moves along $x$, the spin direction is almost constant for all the energies
+across the peak of the response, having $42.5^{\circ}<\theta_{\mathrm{x}}
+(\omega,\alpha)<53.7^{\circ}$ and $208.3^{\circ}<\varphi_{\mathrm{x}}
+(\omega,\alpha)<215.7^{\circ}$. When the electron moves along $y$, the spin
+polar angle has again small variations, $11.3^{\circ}<
+\theta_{\mathrm{y}}(\omega,\alpha)<13.9^{\circ}$, but the azimuthal angle
+varies significantly, $82.1^{\circ}< \varphi_{\mathrm{y}}
+(\omega,\alpha)<182.4^{\circ}$.
 
@@
 \centering
-\includegraphics[width=\tama]{upplots/up-vx-vy-w2}
-\caption{For the Up structure we show $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and $\varphi_{\mathrm{a}}
-(\omega,\alpha)$, (right scale, blue line), vs. $\hbar\omega$, for
-$\alpha=35^\circ$, and $\mathrm{a}=x,y$. }
+\includegraphics[width=\tama]{figures/fig8}
+\caption{The Up structure: the spin velocity $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
+shown. }
 \label{fig:up-vx-vy-w2}
@@
 In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there are two local
-maxima at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV. The former is the
-largest of the two, with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)=61.2$\,Km/s,
-$\theta_{\mathrm{x}} (\omega,\alpha)=48.3^{\circ}$, and $\varphi_{\mathrm{x}}
-(\omega,\alpha)=54.3^{\circ}$, for the electron moving along $x$, and
+(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there two local maxima
+with opposite sign at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV
+occur. The first is the largest of the two, with $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha)=61.2$\,Km/s, $\theta_{\mathrm{x}}
+(\omega,\alpha)=48.3^{\circ}$, and $\varphi_{\mathrm{x}}
+(\omega,\alpha)=54.3^{\circ}$, for the electron moving along $x$; and
 $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)=293.2$\,Km/s, $\theta_{\mathrm{y}}
-(\omega,\alpha) = 49.8^{\circ}$, and $\varphi_{\mathrm{y}} (\omega,\alpha) =
-51.9^{\circ}$ for the electron moving along $y$. For the $\hbar\omega=1.957$\,eV
-peak, we obtain $\theta_{\mathrm{x}} (\omega,\alpha) = 129.8^{\circ}$ and
-$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with
-$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and $\theta_{\mathrm{y}}
-(\omega,\alpha) = 129.3$, and $\varphi_{\mathrm{y}} (\omega,\alpha) = 230.7$,
-with $\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 263.7$\,Km/s. We remark that
-these angles are almost constant for all the energy values across the peak of
-these two local maxima, for which the spin is directed upward in the first
-Cartesian quadrant of the $xy$ plane when it moves along either $x$ or $y$
-directions.
+(\omega,\alpha)=49.8^{\circ}$, and $\varphi_{\mathrm{y}}
+(\omega,\alpha)=51.9^{\circ}$ for the electron moving along $y$. For the peak
+at $\hbar\omega=1.957$\,eV, we obtain $\theta_{\mathrm{x}} (\omega,\alpha) =
+129.8^{\circ}$ and $\varphi_{\mathrm{x}} (\omega,\alpha) = 231.7^{\circ}$, with
+$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 54.6$\,Km/s and
+$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$; and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.7$, with $\mathcal{V}^{\mathrm{y}}
+(\omega,\alpha) = 263.7$\,Km/s. We remark that these angles are almost constant
+for all the energy values across the peak of these two local maxima, for which
+the spin is directed upward in the first quadrant of the $xy$ plane when
+{\color{red} \st{it} (who?)} {\color{blue}the electron} moves along either $x$ or
+$y$ directions.
 
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vx-vy-w1}
-\caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
-(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
-scale, blue line), vs. $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a} =
-x,y$. }
+\includegraphics[width=\tama]{figures/fig9}
+\caption{The Alt structure: the velocity $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
+shown. }
 \label{fig:alt-vx-vy-w1}
@@
 \centering
-\includegraphics[width=\tama]{altplots/alt-vx-vy-w2}
-\caption{For the Alt structure, we show $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), $\theta_{\mathrm{a}} (\omega,\alpha)$
-(right scale, red line), and $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right
-scale, blue line), vs. $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a} =
-x,y$. }
+\includegraphics[width=\tama]{figures/fig10}
+\caption{The Alt structure: $\mathcal{V}_{\mathrm{a}}
+(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
+(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
+shown.}
 \label{fig:alt-vx-vy-w2}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$ in two different ranges, and  for $\mathrm{a} =x,y$. In this case,
+$\hbar\omega$ in two different ranges, and  for $\mathrm{a}=x,y$. In this case,
 $\alpha=150^\circ$  maximizes both $\mathcal{V}_{\mathrm{x}} (\omega,\alpha)$
 and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha)$, as a function of $\alpha$. In
-Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.720$\,eV,
-with $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 301.7$\,Km/s,
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
+(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV ,
 $\theta_{\mathrm{x}} (\omega,\alpha) = 44.5^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$, and
-$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s, with
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$; and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s at
 $\theta_{\mathrm{y}} (\omega,\alpha) = 119.7^{\circ}$ and
 $\varphi_{\mathrm{y}}(\omega,\alpha) = 163.4^{\circ}$. Thus, the spin is
-directed upward the fourth Cartesian quadrant of the $xy$ plane when the spin
-velocity is directed along $x$, and directed downward the second Cartesian
-quadrant when the spin velocity is directed along $y$. Finally, in  Fig.
-\ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV, with
-$\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s, $\theta_{\mathrm{x}}
-(\omega,\alpha) = 154.6^{\circ}$, and $\varphi_{\mathrm{x}}(\omega,\alpha) =
-292.3^{\circ}$, and $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s,
-with $\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
-$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin is
-directed downward the fourth Cartesian quadrant of the $xy$ plane when the spin
-velocity is directed along $x$, and directed downward the third Cartesian
+directed upward the fourth quadrant of the $xy$ plane when the spin
+velocity is directed along $x$, while it is directed downward the second
+quadrant when the spin velocity is directed along $y$. Finally, in
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV
+at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s,
+$\theta_{\mathrm{x}} (\omega,\alpha) = 154.6^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 292.3^{\circ}$, and
+$\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 468.6$\,Km/s at
+$\theta_{\mathrm{y}} (\omega,\alpha) = 129.2^{\circ}$, and
+$\varphi_{\mathrm{y}}(\omega,\alpha) = 228.3^{\circ}$, implying that the spin
+is directed downward the fourth quadrant of the $xy$ plane when the
+spin velocity is directed along $x$, while is directed downward the third
 quadrant when the spin velocity is directed along $y$.
 
-\section{Conclusions} % (fold)
+\section{Conclusions}
 \label{sec:conclusions}
 
-We performed an \emph{ab initio} calculation for the SVI by one-photon
-absorption of linearly polarized light in the Up and Alt 2D hydrogenated
-graphene structures, and we made the calculation for the case when the spin is
-polarized in the $z$ direction or when the velocity is directed along $x$ or
-$y$; this effect does not seem to have been previously reported in this kind of
-structures. This SVI is very sensitive to the symmetry characteristics of the
-structures, presenting an anisotropic behavior. We found that the Up structure
-has the most intense response for the spin directed along $z$, resulting in
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s, and for an
-energy of the incoming beam of 0.084\,eV. Also, the Alt structure has the most
-intense response when the spin moves along the $y$ direction, resulting in
-$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for an energy of the
-incoming beam of 0.720\,eV. The speed values obtained here are of the same order
-of magnitude as those of Ref.~\onlinecite{najmaiePRB03} in unbiased
-semiconductor quantum well structures. The spin relaxation time in pure and
+We reported the results of an \emph{ab initio} calculations for the spin
+velocity injection (SVI) due to the one-photon absorption of the linearly
+polarized light in the Up and Alt 2D 50\% hydrogenated graphene structures.
+Different possible arrangements of the of the spin injection have been
+considered: we made the calculations for the cases when the spin is polarized
+in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
+of our knowledge, this effect  has been previously reported in this  2D
+partially hydrogenated structures. We have shown that the  SVI demonstrates an
+anisotropic behavior, which is very sensitive to the symmetry of the structures
+of interest. We have found that the Up structure shows the strongest response
+for the spin directed along $z$, resulting in the velocity
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 668.0$\,Km/s for the
+incoming photon energy of 0.084\,eV. Also, the Alt structure has the strongest
+response when the spin moves along $y$ direction, resulting in
+$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s for the incoming
+photon energy of 0.720\,eV. The speed values obtained here are of the same
+order of magnitude as those of Ref.~\onlinecite{najmaiePRB03} in unbiased
+semiconductor quantum well structures, while they are of order of magnitude
+higher compared to 3D bulk materials. The spin relaxation time in pure and
 doped graphene is long enough in the order from nanoseconds to milliseconds.
-\cite{wojtaszekPRB13,ertlerPRB09} Then, according to our results, both are
-excellent candidates for the development of spintronics devices that require PSC
-due to the high spin velocity transport.
+\cite{wojtaszekPRB13,ertlerPRB09} Therefore, according to our results, due to
+the high spin velocity transport both structures considered are the excellent
+candidates for the development of spintronics devices that require pure spin
+current (PSC).
 
-\section{Acknowledgment} % (fold)
+\section{Acknowledgment}
 
 This work has been supported by \emph{Consejo Nacional de Ciencia y
-Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930. R.Z.P. thanks CONACyT for
-scholarship support.
+Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
+R.Z.P. thanks CONACyT for scholarship support.
 \bibliography{article.bib}
@@
 \end{document}
+
+%@article{buonocorePE16,
+%  title={Effects of the substrate on graphone magnetism: A density functional
+%  theory study},
+%  author={Buonocore, F. and Conte, A. M. and Lisi, N.},
+%  journal={Phys. E: Low-dim. Sys.},
+%  volume={78},
+%  pages={65--72},
+%  year={2016},
+%  publisher={Elsevier}
+%}
+
+gmitraPRL13

### 2017-08-20 mu/article/article.tex
Checking with bms.

@@
 different structural configurations and a tunable electron gap, as it has been
-proven in [1]. In this paper, we present two 50\% hydrogenated graphene
+proven in \cite{shkrebtiiPSSC12}. In this paper, we present two 50\% hydrogenated graphene
 noncentrosymmetric structures, both presenting a discernible band gap. The

### 2017-08-20 mu/article/article.tex
Starting second Anatoli's review.

--- 2017-08-17 mu/article/article.tex
@@
 \documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
+%\documentclass[preprint,prb,showpacs]{revtex4}
 \usepackage{amsmath}    % need for subequations 
@@
 \usepackage{subfigure}  % use for side-by-side figures 
-\usepackage{hyperref}   % use for hypertext links, including those to external 
-                        % documents and URLs 
+\usepackage[pdffitwindow,colorlinks,citecolor={red},linkcolor={blue}]{hyperref}
 \usepackage[dvipsnames]{xcolor}
@@
 graphene structures. The first structure, hydrogenated at only one side,
-labeled $Up$, also known as graphone, and the second, one labelled $Alt$, is
+labeled Up, also known as graphone, and the second, one labelled Alt, is
 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
 structures. We analyze two possibilities: the first one is by fixing the spin
-along a chosen direction, and the resulting spin-velocity is calculated.
-Secondly, we choose the spin-velocity direction within {\color{red}(OR along?)}
-the surface plane, and calculate {\color{red}(which one?)} the spin-velocity
-injection and spin orientation. This is done by changing the energy
+along a chosen direction, and the resulting SVI is calculated.
+Secondly, we choose the SVI direction along
+the surface plane, and calculate the resulting
+spin orientation. This is done by changing the energy
 $\hbar\omega$ and polarization angle $\alpha$  of the incoming  light. The
@@
 $\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and
-645\,Km/s for Up and Alt structures, respectively, when the spin points
-perpendicularly to the surface. Also, the symmetry Cartesian axis, reaching a
-speed of 688\,Km/s with the spin  pointing response is maximized by fixing the
-spin-velocity direction along a high at 13$^\circ$ from the surface normal, the
-for Up, and 906\,Km/s and the spin pointing at 60$^\circ$ from the surface
-normal, for the Alt. These speed values are significantly larger than those of
-bulk semiconductors, such as CdSe and GaAs, thus making the hydrogenated
-graphene structures excellent candidates for spintronics applications.
+645\,Km/s for the Up and the Alt structures, respectively, when the spin points
+perpendicularly to the surface. Also, the response is maximized by
+fixing the spin-velocity direction 
+along a high symmetry  axis, obtaining a speed of 688Km/s
+with the spin pointing at $13^\circ$ from the surface normal, for the Up, 
+and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
+the Alt. These speed values are larger than those of bulk semiconductors,
+such as CdSe and GaAs, thus making the hydrogenated graphene structures
+excellent candidates for spintronics applications. 
 \end{abstract}
@@
 electrical current \cite{awschalomSSBM13} or pure spin current (PSC). One of
-the difficulties in {\color{red}\st{achieving}} {\color{blue}creating} measurable  the of spin current and
+the difficulties in creating measurable  spin current and
 development of PSC based semiconductor devices is the fact that the spin
@@
 
+The spin velocity injection (SVI) is an optical effect that quantifies the velocity at which
+a PSC moves along the direction $\hat{\mathbf{a}}$, 
+with the spin of the electron polarized along the direction $\hat{\mathbf{b}}$.
+One photon absorption of polarized
+light produces an even distribution of electrons in $\mathbf{k}$
+space, regardless of the symmetry of the material, resulting in a null
+electrical current.\cite{bhatPRL05} 
+Then, the electrons excited to the
+conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
+polarizations producing no net spin injection in centrosymmetric 
+materials.\cite{bhatPRL05} 
+If the crystalline structure of the material
+is noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
+point not necessarily vanishes.\cite{alvaradoPRL85,schmiedeskampPRL88}
+Therefore, since the velocities of electrons at opposite $\mathbf{k}$ points
+are opposite, a PSC will be produced.
+
 Graphene, an allotrope of carbon with hexagonal 2D lattice structure,
@@
 strain.\cite{niACSN08} Another possibility to open the gap is by doping; this
-has been successfully achieved using nitrogen,\cite{weiNL2009} boron-
-nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} noble-
-metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
+has been successfully achieved using nitrogen,\cite{weiNL2009} 
+boron-nitrogen,\cite{guoIJ11} silicon,\cite{colettiPRB10} 
+noble-metals,\cite{varykhalovPRB10} and hydrogen.\cite{eliasS09, guisingerNL09,
 samarakoonACSN10} Depending on the percentage of hydrogenation and spatial
@@
 different structural configurations and a tunable electron gap, as it has been
-proven in [1]. In this paper, we present two 50\% hydrogenated graphene
+proven in Ref. \onlinecite{shkrebtiiPSSC12}. 
+In this paper, we present two 50\% hydrogenated graphene
 noncentrosymmetric structures, both presenting a discernible band gap. The
 first one, labelled as the Up structure, also known as
-graphone,\cite{gmitraPRL13} shown in Fig. \ref{fig:up-struc}. Graphone has
+graphone,\cite{gmitraPRL13}  has
 hydrogen atoms bonded to the carbon layer only on the upper side of the
-structure, we consider here the magnetic isomer of graphone, with the so-called
-“chair” structure. In contrast,  the Alt structure, shown in Fig. 
+structure; we consider here the magnetic isomer of graphone, with the so-called
+``chair'' structure  shown in Fig. \ref{fig:up-struc}.
+In contrast,  the Alt structure, shown in Fig. 
 \ref{fig:alt-struc}, has hydrogen alternating on the upper and bottom sides of 
-the carbonsheet.\cite{zapataPSB2016}
+the carbon sheet.\cite{zapataPSB2016}
+
+Both the Up and the Alt  structures
+are noncentrosymmetric, and therefore,
+they are good candidates in which SVI can be
+induced. In this article, 
+we address theoretically the SVI 
+by one-photon absorption of linearly polarized light, analyzing
+in our structures,
+two possible scenarios of practical interest. 
+The first case is by fixing the spin of the electrons along $z$, i.e. 
+perpendicular 
+to the surface plane, with the resulting velocity
+directed along the surface of the
+structures in the $xy$ plane. 
+In the second case we fix the SVI velocity along the
+$x$ or $y$ direction, and then, the resulting spin is directed outward of the
+$xy$ plane.
 
@@
     \centering
-    \includegraphics[width=\tama]{figures/fig1}
-    \caption{Side (top panel) and top (bottom panel) views of the Up
-      Cartesian $xyz$ directions. The dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is also shown.
+    \includegraphics[width=5cm]{figures/fig1}
+    \caption{
+Top (top panel) and side (bottom panel) views of the Up
       structure along with the 
-}
+      Cartesian $x$, $y$, and $z$ directions. The dark (light) spheres
+      are the C (H) atoms. 
+The primitive hexagonal unit cell is also shown.
+{\color{red}Anatoli: we are confused about the primitive hexagonal
+  unit cell shown. For instance, according to us, if we take C$_2$ and
+apply the red arrow, it will end up in the site of C$_4$, but these C
+atoms according to Table \ref{tab:up-unitcell} are not equivalent, or are they?}} 
     \label{fig:up-struc}
@@
     \centering
-    \includegraphics[width=\tama]{figures/fig2}
-    \caption{Side (top panel) and top (bottom panel) views of the Alt
-      structure along with the $xyz$ directions. The dark (light) spheres are
-      the C (H) atoms. The primitive rectangular unit cell is also displayed.}
+    \includegraphics[width=5cm]{figures/fig2}
+    \caption{
+Top (top panel) and side (bottom panel) views of the Alt
+      structure along with the 
+      Cartesian $x$, $y$, and$ z$ directions. The dark (light) spheres
+      are the C (H) atoms. 
+The primitive hexagonal unit cell is also shown.
+}
     \label{fig:alt-struc}
 \end{figure}
-
-Using those structures, we address theoretically the spin velocity injection
-(SVI) by one-photon absorption of linearly polarized light. Since wehave 2D
-structures, we do the analysis for two cases {\color{red}(not clear to me this
-sentence)}. The first case is by fixing the spin of the electrons along
-vertical to the surface direction {\color{red}(?)}$z$, , with the velocity
-directed onto {\color{red}(is this parallel or not?)} the surface of the
-structure in the $xy$ plane. In the second case we fix the spin velocity in the
-$x$ or $y$ direction and the resulting spin is then directed outward of the
-$xy$ plane. The SVI is an optical effect that quantifies the velocity, at which
-a PSC moves along the direction $\bf{a}$ with the $\bf{a}$ components to be
-determined, with the spin of electron polarized along the direction $\bf{b}$.
-polarized light produce an even distribution of electrons in $\mathbf{k}$
-space, regardless of the symmetry of the material, resulting in a null
-electrical current.\cite{bhatPRL05} Then, the electrons excited to the
-conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
-polarizations producing no net spin injection in centrosymmetric materials
-{\color{red}(?)}.\cite{bhatPRL05} If the crystalline structure of the material
-is noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
-point not necessarily vanishes,\cite{alvaradoPRL85, schmiedeskampPRL88}.
-Therefore, since the velocities of electrons at opposite $\mathbf{k}$ points
-are opposite, a PSC will be produced. Since both the structures presented here
-are noncentrosymmetric, they are good candidates in which this effect can be
-induced.
 
@@
 corresponding SVI spectra for the Up and Alt structures. Finally, we summarize
-our finding in Section \ref{sec:conclusions}.
+our findings in Section \ref{sec:conclusions}.
 
@@
 being the position operator and $\hat H_0$ the unperturbed
+ground state Hamiltonian; 
 the Roman superscripts  indicate Cartesian coordinates. 
-ground state Hamiltonian;
 To obtain the expectation value of 
@@
 \end{align}   
-where the applied electric field of the laser is given by
+where the applied electric field of the beam of light is given by
 \begin{align}\label{z.3}
@@
 in this work.
-%Although, this splitting is small [15,16], is required to obtain the correct
-%results\cite{nastosPRB07}. The conduction bands in the noncentrosymmetric
-%semiconductors are spin split by a small amount,[15,16] typically smaller than
-%the energy width of the laser pulse, and so the pulse excites a coherent
-%superposition of the two conduction bands. Even for very long pulses with
-%narrow energy widths, dephasing effects lead to an energy width of the bands
-%large enough that spin-split states can become quasi-degenerate.
-To include the coherence, we follow Ref.~\onlinecite{nastosPRB05} and
+To include the coherence, we follow Ref.~\onlinecite{nastosPRB07} and
 use a multiple
@@
 where we assumed that the conduction bands $c$ and $c'$ are quasi-degenerate
-states, and we take $\epsilon\to 0$ at the end of the calculation. The spin-
-splitting of the valence ($v$) bands is very small, and is neglected throughout
+states, and we take $\epsilon\to 0$ at the end of the calculation. The 
+spin-splitting of the valence ($v$) bands is very small, and is neglected throughout
 this work.\cite{nastosPRB07} The matrix elements of any operator ${\cal O}$ are
@@
 where we used the closure relationship $\sum_{n}|n{\mathbf k}\rangle \langle
-n{\mathbf k}| = 1$, where $n=v,c$, and the fact that $\rho_{vn}({\mathbf
-k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. Therefore, using  Eqs. \eqref{z.4}
+n{\mathbf k}| = 1$, where $n$ goes over all $v$ and $c$ states,
+ and the fact that $\rho_{vn}(\mathbf{k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. Therefore, using  Eqs. \eqref{z.4}
 and \eqref{z.5}, the rate of change of $\mathcal{O}$, $\dot{\mathcal{O}} =
@@
 \end{equation}
-where repeated Cartesians are summed, and 
+where repeated Cartesians upperscripts  are summed, and 
 \begin{equation}\label{eq:mu}
 \begin{aligned}
-\mu^{\mathrm{abcd}}  (\omega) &
+\mu^{\mathrm{abcd}}  (\omega) 
 =
@@
 \delta(\omega-\omega_{cv}({\mathbf k}) 
-\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'}({\mathbf k}) 
+\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'}({\mathbf k}) 
 \left(  
@@
 semiconductors. To derive what we presented above we used $
-K^{\mathrm{ab}}_{nm}({\mathbf -k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+K^{\mathrm{ab}}_{nm}(-\mathbf{k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
 follows from time-reversal invariance. Since $\mu^{\mathrm{abcd}}(\omega)$ is
@@
 \mu^{\mathrm{abdc}} (\omega)$. We point out that Eq.~\eqref{eq:mu} is
-–identical to Eq. (3) of Bhat et al.\cite{bhatPRL05}, derived using the
+–identical to Eq. (3) of Bhat et al.,\cite{bhatPRL05} derived using the
 semiconductor optical Bloch equations. Using the closure relation,
@@
 \right)
-,
+.
 \label{eq:velspimatelem}
@@
 \end{equation}  
-which gives the velocity, along direction $a$, at which the spin moves in a
-polarized state along direction $b$. The carrier injection rate $\dot
-n(\omega)$ is written as\cite{nastosPRB05}
+which gives the velocity, along direction $\hat{\mathbf{a}}$, at which the spin moves in a
+polarized state along direction $\hat{\mathbf{b}}$. 
+The carrier injection rate $\dot n(\omega)$ is written as\cite{nastosPRB07}
 \begin{equation}
@@
 two very important aspects of PSC. On one hand, we can fix the spin direction
-along $\mathrm{b}$ and calculate the resulting electron velocity. On the other
-hand, we can fix the velocity of the electron along $\mathrm{b}$ and study the
+along $\hat{\mathbf{b}}$ and calculate the resulting electron velocity. On the other
+hand, we can fix the velocity of the electron along $\hat{\mathbf{a}}$
+ and study the
 resulting direction along which the spin is polarized. To this end, the
@@
 \end{widetext}
-for the structures chosen in this article,
+since for the structures chosen in this article,
 $\xi^{\mathrm{xx}}(\omega)=\xi^{\mathrm{yy}}(\omega)\equiv\xi(\omega)$, and
@@
 
-Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define {\color{red}(calculate?)} the magnitude
+Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we calculate the magnitude
 of the electron velocity along the plane of the structure, with the spin
-polarized along $\mathrm{b}$ direction as
+polarized along $\hat{\mathbf{b}}$ direction as
 \begin{equation}
@@
 corresponding to the electron velocity being parallel or perpendicular to the
-incoming light polarization, respectively. The subscript $\sigma^\mathrm{b}$
-denotes the spin along $\mathrm{b}$.
+incoming light polarization direction, respectively. 
+The subscript $\sigma^\mathrm{b}$
+denotes the spin along $\hat{\mathbf{b}}$.
 
@@
 \end{align}
-from where we see that the spin would be oriented in the $xyz$ system's
-coordinates defined with a polar angle
+from where we see that the spin would be oriented in the $xyz$ system of
+coordinates by the defined  polar angle
 \begin{equation}
@@
 \hline
-H & -0.61516 & -1.77416 &  0.73196 \\
-H &  0.61518 &  0.35514 &  0.73175 \\
-C & -0.61516 & -1.77264 & -0.49138 \\
-C & -0.61516 & -0.35600 & -0.72316 \\
-C &  0.61516 &  0.35763 & -0.49087 \\
-C &  0.61518 &  1.77416 & -0.73196 \\
+H$_1$ & -0.61516 & -1.77416 &  0.73196 \\
+H$_2$ &  0.61518 &  0.35514 &  0.73175 \\
+C$_1$ & -0.61516 & -1.77264 & -0.49138 \\
+C$_2$ & -0.61516 & -0.35600 & -0.72316 \\
+C$_3$ &  0.61516 &  0.35763 & -0.49087 \\
+C$_4$ &  0.61518 &  1.77416 & -0.73196 \\
 \hline
 \end{tabular}
-\caption{Atomic positions in the unit cell of Up structure as the structural
-input for our calculations. {\color{blue}The primitive hexagonal unit cell
-contains two C and one H atoms as shown in Fig. \ref{fig:up-struc})}. }
+\caption{
+Atomic positions in the unit cell of the Up structure shown
+in Fig. \ref{fig:up-struc}. 
+}
 \label{tab:up-unitcell}
@@
 \hline
-H &  -0.61516 &  -1.42140 & \ 1.47237 \\
-C &  -0.61516 &  -1.73300 & \ 0.39631 \\
-C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
-C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
-C &  -0.61516 &  -0.37396 &  -0.39632 \\
-H &  -0.61516 &  -0.68566 &  -1.47237 \\
+H$_1$ &  -0.61516 &  -1.42140 & \ 1.47237 \\
+C$_1$ &  -0.61516 &  -1.73300 & \ 0.39631 \\
+C$_2$ & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
+C$_3$ & \ 0.61516 & \ 0.42201 &  -0.15814 \\
+C$_4$ &  -0.61516 &  -0.37396 &  -0.39632 \\
+H$_2$ &  -0.61516 &  -0.68566 &  -1.47237 \\
 \hline
 \end{tabular}
-\caption{Atomic positions in the unit cell of Alt structure, which coincides
-with its primitive cell. }
+\caption{
+Atomic positions in the unit cell of the Alt structure
+ shown in Fig. \ref{fig:alt-struc}. 
+}
 \label{tab:alt-unitcell}
@@
 $\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)$ and
-$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the C$_{16}$H$_{8}$-Up  and
-C$_{16}$H$_{8}$-Alt structures, both noncentrosymmetric 2D carbon systems with
+$\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ for the Up  and
+Alt structures, both noncentrosymmetric 2D carbon systems with
 50\% hydrogenation, which are differently structurally arranged. We remind that
@@
 structures are presented in Tables \ref{tab:up-unitcell} and 
-\ref{tab:alt-unitcell}.
+\ref{tab:alt-unitcell}, respectively.
 
@@
 The convergence parameters for the calculations,  corresponding to the Up and
-Alt structures are cutoff energies of 40\,Ha and 65\,Ha, resulting in LDA
-energy band gaps of 0.084\,eV and 0.718\,eV, respectively. The energy
-eigenvalues and matrix elements for the Up and Alt structures were calculated
-using 12802 ${\mathbf k}$ points and 14452 ${\mathbf k}$ points in the IBZ; to
+Alt structures are cutoff energies up to 65\,Ha, resulting in LDA
+energy band gaps of 0.084\,eV and 0.718\,eV, respectively, 
+and 14452 ${\mathbf k}$ points in the IBZ
+where the energy
+eigenvalues and matrix elements were calculated;
+to
 integrate $\mu^{\mathrm{abcd}}(\omega)$ and
 $\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the linearized analytic tetrahedron method
-(LATM) has been used.\cite{nastosPRB07} We neglect the anomalous velocity term
+(LATM) has been used.\cite{nastosPRB07} 
+We neglect the anomalous velocity term
 $\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
@@
 \caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
-  vs. $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
+  {\it vs.} $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
   largest velocity are at the low energy regions of the spectra for the Alt and
-  Up structures, starting {\color{red}(going up?)} at the energy gap of each
+  Up structures, becoming different from zero at the energy gap of each
   structure. In the high energy regions, the values of
   $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to
-  the 3D case of CdSe and GaAsThe, shown at the bottom panel . }
+  the 3D case of CdSe and GaAs, shown at the bottom panel.}
 \label{fig:vab-str-comp}
@@
 In Fig. \ref{fig:vab-str-comp}, we show $\mathcal{V}^{\mathrm{ab}}
-(\omega,\alpha)$ vs. $\hbar\omega$ for the {\color{blue}velocity and spin
-directions} $\mathrm{a}$ and $\mathrm{b}$, and for the angle $\alpha$, at which
-the signal is maximized , for the Up  and Alt structures, and for CdSe and GaAs
-bulk systems, shown for comparison. As expected from Eq.~\eqref{eq:mu}, ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ rises from zero right at the
+(\omega,\alpha)$ {\it vs.} $\hbar\omega$ for the 
+velocity and spin
+directions
+$\hat{\mathbf{a}}$ and $\hat{\mathbf{b}}$, and for the angle $\alpha$, at which
+the signal is maximized, for the Up  and Alt structures, and for CdSe and GaAs
+bulk systems, shown for comparison. As expected from
+Eq.~\eqref{eq:mu}, 
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ becomes different 
+from zero right at the
 corresponding energy gap of each system. For the 2D structures considered, the
@@
 \hline
-$Up$  & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
+Up  & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
       &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
       &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
-$Alt$ & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
+Alt & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
       &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
@@
 \caption{Color online. For the Up structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ SvsS. $\hbar\omega$ and $\alpha$, and
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and
 the bottom panel shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right
-scale, red line, {\color{red}long dashes?}), and ${\cal
+scale, red line), and ${\cal
 V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid
-line{\color{red}?}), $vs$. $\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along
+line), {\it vs.} $\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along
 the ridge shown in the 3D plot. }
@@
 \caption{For the Up structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and the
 bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
 red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
-(left scale, black solid line), vs. $\alpha$, for $\hbar\omega=1.954$\,eV, i.e.
+(left scale, black solid line), {\it vs.} $\alpha$, for $\hbar\omega=1.954$\,eV, i.e.
 along the highest ridge shown in the 3D plot. }
@@
 In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$,
-Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
+Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
@@
 electrons movement along the surface of  each structure. We mention that we
-have also  analyzed the cases when the spin  is directed along $\mathrm{x}$ or
-$\mathrm{y}$, finding similar qualitative results to those presented below.
+have also  analyzed the cases when the spin  is directed along $x$ or
+$y$, finding similar qualitative results to those presented below.
 
@@
 In the top panel of Fig. \ref{fig:up-vsz-w1}, we plot
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
 0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
-structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
+structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} and
 $0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
@@
 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ $vs.$ $\alpha$ (left scale,
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
 black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
@@
 Now, we analyze the results for the second energy range of the Up structure
-shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
+shown in Fig.~\ref{fig:vab-str-comp}. In the top panel
 of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha)$ vs. 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
+(\omega,\alpha)$ {\it vs.} 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
 $0^\circ\leq\alpha\leq 180^\circ$. We see two broad peaks that maximize at
@@
 analyze the highest  maximum in the bottom panel, where we  show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs. $\alpha$ (left scale,
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
 black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
@@
 inject electrons, in this case with their spin polarized along $z$, which move
-parallel or perpendicular to the incident electric field, with finite speeds
-{\color{red}(what does “finite” mean?)}.
-% the maxima for
-% $\hbar\omega=0.084$ eV and $\alpha=35^{\circ}$, with
-% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
-% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
-% $\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
-% $\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.
+parallel or perpendicular to the incident electric field, with sizable speeds.
 
@@
 \caption{Color online. For the Alt structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ vs. $\hbar\omega$ and $\alpha$, and the
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and the
 bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
 red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale,
-black line), vs. $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge
+black line), {\it vs.} $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge
 shown in the 3D plot.}
@@
 \ref{fig:alt-vsz}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
-vs. 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
+{\it vs.} 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
 180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
-panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ vs.
+panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
 $\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV, thus following
@@
 Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. 
-\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\mathrm{a}$,
+\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\hat{\mathbf{a}}$,
 to the $x$ or $y$ direction along the surface of the Up and Alt structures.
-From Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, {\color{blue}we
+From Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, 
+we
 determined the corresponding polar angle, $\theta_{\mathrm{a}}
-(\omega,\alpha)$, and azimuthal angle, $\varphi_{\mathrm{a}} (\omega,\alpha)$}.
+(\omega,\alpha)$, and azimuthal angle, $\varphi_{\mathrm{a}} (\omega,\alpha)$.
 
@@
 \includegraphics[width=\tama]{figures/fig7}
-\caption{The Up structure: the velocity $\mathcal{V}_{\mathrm{a}}
+\caption{
+For the Up structure we show the velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
 (\omega,\alpha)$ (right scale, red line), and  the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
-shown. }
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and $\mathrm{a}=y$.}
 \label{fig:up-vab-comp-rtp-1}
@@
 $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
 $\hbar\omega$, for $\mathrm{a}=x,y$. We see that for $\hbar\omega=0.084$\,eV,
@@
 \includegraphics[width=\tama]{figures/fig8}
-\caption{The Up structure: the spin velocity $\mathcal{V}_{\mathrm{a}}
+\caption{For 
+the Up structure we show the spin velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
 (\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
-shown. }
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$. 
+}
 \label{fig:up-vx-vy-w2}
@@
 In Fig. \ref{fig:up-vx-vy-w2}, we plot $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ vs. $\hbar\omega$, in the range where there two local maxima
+(\omega,\alpha)$ {\it vs.} $\hbar\omega$, in the range where there two local maxima
 with opposite sign at $\hbar\omega=1.954$\,eV and $\hbar\omega=1.957$\,eV
@@
 the spin is directed upward in the first quadrant of the $xy$ plane when
-{\color{red} \st{it} (who?)} {\color{blue}the electron} moves along either $x$ or
+the electron moves along either $x$ or
 $y$ directions.
@@
 \includegraphics[width=\tama]{figures/fig9}
-\caption{The Alt structure: the velocity $\mathcal{V}_{\mathrm{a}}
+\caption{For the Alt structure we show  the velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
 (\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
-shown. }
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$.
+}
 \label{fig:alt-vx-vy-w1}
@@
 \includegraphics[width=\tama]{figures/fig10}
-\caption{The Alt structure: $\mathcal{V}_{\mathrm{a}}
+\caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
 (\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
-shown.}
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
+$\mathrm{a}=y$.
+}
 \label{fig:alt-vx-vy-w2}
@@
 $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), vs.
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
 $\hbar\omega$ in two different ranges, and  for $\mathrm{a}=x,y$. In this case,
@@
 Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
-(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV ,
+(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV,
 $\theta_{\mathrm{x}} (\omega,\alpha) = 44.5^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$; and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$, and
 $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s at
@@
 velocity is directed along $x$, while it is directed downward the second
-quadrant when the spin velocity is directed along $y$. Finally, in
-Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV
+quadrant when the spin velocity is directed along $y$. 
+Finally, in
+Fig. \ref{fig:alt-vx-vy-w2}, the absolute maximum is at $\hbar\omega=0.911$\,eV
 at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s,
@@
 in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
-of our knowledge, this effect  has been previously reported in this  2D
+of our knowledge, this effect  has not been previously reported in this  2D
 partially hydrogenated structures. We have shown that the  SVI demonstrates an
@@
 \section{Acknowledgment}
-
 This work has been supported by \emph{Consejo Nacional de Ciencia y
@@
 R.Z.P. thanks CONACyT for scholarship support.
+
 \bibliography{article.bib}

### 2017-08-20 mu/article/article-review7-Anatoli.tex
Sending changes to BMS

--- 2017-08-20 mu/article/article.tex
@@
 \documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
-%\documentclass[preprint,prb,showpacs]{revtex4}
 \usepackage{amsmath}    % need for subequations 
@@
 \usepackage{subfigure}  % use for side-by-side figures 
-\usepackage[pdffitwindow,colorlinks,citecolor={red},linkcolor={blue}]{hyperref}
+\usepackage{hyperref}   % use for hypertext links, including those to external 
+                        % documents and URLs 
 \usepackage[dvipsnames]{xcolor}
@@
 current (PSC) induced by  a linearly polarized light that impinges normally on
-the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D
+the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional (2D)
 graphene structures. The first structure, hydrogenated at only one side,
-labeled Up, also known as graphone, and the second, one labelled Alt, is
+labeled Up, also known as graphone, and the second, labelled Alt, is
 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
-structures. We analyze two possibilities: the first one is by fixing the spin
+structures. We analyze two possibilities: the first,  the spin is fixed
 along a chosen direction, and the resulting SVI is calculated.
-Secondly, we choose the SVI direction along
+In the second, we choose the SVI direction along
 the surface plane, and calculate the resulting
@@
 along a high symmetry  axis, obtaining a speed of 688Km/s
-with the spin pointing at $13^\circ$ from the surface normal, for the Up, 
-and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
-the Alt. These speed values are larger than those of bulk semiconductors,
+with the spin pointing at $13^\circ$ from the surface normal for the Up, 
+and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal for
+the Alt systems. These speed values are of order of magnitude larger than those of bulk semiconductors
 such as CdSe and GaAs, thus making the hydrogenated graphene structures
@@
 conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
-novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
-electronic systems; however, most electronic applications are disabled by the
+novoselov2S07, balandinNL08}, being a perfect platform  for two-dimensional (2D)
+electronic systems; however, numerous important  electronic applications are disabled by the
 absence of a semiconducting gap. Recent studies demonstrate that a narrow band
@@
 proven in Ref. \onlinecite{shkrebtiiPSSC12}. 
-In this paper, we present two 50\% hydrogenated graphene
-noncentrosymmetric structures, both presenting a discernible band gap. The
+In this paper, we offer two 50\% hydrogenated graphene
+noncentrosymmetric structures, both demonstrating a discernible band gap. The
 first one, labelled as the Up structure, also known as
@@
 induced. In this article, 
-we address theoretically the SVI 
+we address theoretically the spin velocity injection
 by one-photon absorption of linearly polarized light, analyzing
-in our structures,
+in our structures
 two possible scenarios of practical interest. 
-The first case is by fixing the spin of the electrons along $z$, i.e. 
+The first case is by fixing the spin of the electrons along $z$, i.e., 
 perpendicular 
@@
 apply the red arrow, it will end up in the site of C$_4$, but these C
-atoms according to Table \ref{tab:up-unitcell} are not equivalent, or are they?}} 
+atoms according to Table \ref{tab:up-unitcell} are not equivalent, or are they?
+I am absolutely sure that the two atoms are equivalent, this structure, e.g., has the same symmetry as graphane.
+They might be slightly not equivalent since the calculations have been done for twice-bigger unit cell.
+And after your question I have left only three numbers after comma, five is too much and they are below the error in the coordinate determination
+ }} 
     \label{fig:up-struc}
@@
       structure along with the 
-      Cartesian $x$, $y$, and$ z$ directions. The dark (light) spheres
+      Cartesian $x$, $y$, and $z$ directions. The dark (light) spheres
       are the C (H) atoms. 
-The primitive hexagonal unit cell is also shown.
+The primitive rectangular unit cell is also shown.
 }
@@
 
-This paper is organized as follows. In Section \ref{sec:theory} we present the
+This paper is organized as follows. In Section \ref{sec:theory} we outline the
 formalism and the main expressions  that describe PSC and SVI. In Section
@@
 
-The operator that describes the electronic SVI is written as
+To calculate the velocity of the spin injection 
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ along the direction $\hat{\mathbf{a}}$, at which the spin moves in a
+polarized state along direction $\hat{\mathbf{b}}$,  
+we start with the operator that describes the electronic SVI, written as
 \begin{align}\label{z.1}
@@
 +\hat  S^\mathrm{b} \hat v^\mathrm{a}\right) 
-,
+.
 \end{align} 
-where $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ 
+Here $\hat{\mathbf v}=[\hat{\mathbf r},\hat H_0]/i\hbar$ 
 is the velocity operator, with
@@
 particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to 
+% just for comments to think about, not to introduce the suggestions right away: 
+% above we have rho_mn, below rho_cc’
+% time variable has disappeared below. And rho_cc’ contains a and b labels,
+% which are not Cartesian
 \begin{align}\label{z.4}
@@
 \omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ with $\hbar \omega_{n}({\mathbf
-k})$ being the energy of the electronic band $n$ at point ${\mathbf k}$ in the
+k})$ being the energy of the electronic band $n$ and $m$ at point ${\mathbf k}$ in the
 irreducible Brillouin zone (IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state,
@@
 \end{equation}
-where repeated Cartesians upperscripts  are summed, and 
+where the repeated Cartesians upperscripts  are summed, and 
 \begin{equation}\label{eq:mu}
@@
 \end{equation} 
-is the pseudotensor that describes the rate of change of the  PSC process in
+is the pseudotensor that describes the rate of change of the  PSC %process 
+in
 semiconductors. To derive what we presented above we used $
-K^{\mathrm{ab}}_{nm}(-\mathbf{k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+K^{\mathrm{ab}}_{nm}(-\mathbf{k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$,     which
 follows from time-reversal invariance. Since $\mu^{\mathrm{abcd}}(\omega)$ is
@@
 from where we see that the spin would be oriented in the $xyz$ system of
-coordinates by the defined  polar angle
+coordinates along  the polar angle, defined as
 \begin{equation}
@@
 \end{equation}
-and an azimuthal angle
+and the azimuthal angle
 \begin{equation}
@@
 \hline
-H$_1$ & -0.61516 & -1.77416 &  0.73196 \\
-H$_2$ &  0.61518 &  0.35514 &  0.73175 \\
-C$_1$ & -0.61516 & -1.77264 & -0.49138 \\
-C$_2$ & -0.61516 & -0.35600 & -0.72316 \\
-C$_3$ &  0.61516 &  0.35763 & -0.49087 \\
-C$_4$ &  0.61518 &  1.77416 & -0.73196 \\
+H$_1$ & -0.615 & -1.774 &  0.731 \\
+H$_2$ &  0.615 &  0.355 &  0.731 \\
+C$_1$ & -0.615 & -1.772 & -0.491 \\
+C$_2$ & -0.615 & -0.356 & -0.723 \\
+C$_3$ &  0.615 &  0.357 & -0.490 \\
+C$_4$ &  0.615 &  1.774 & -0.731 \\
 \hline
@@
 \hline
-H$_1$ &  -0.61516 &  -1.42140 & \ 1.47237 \\
-C$_1$ &  -0.61516 &  -1.73300 & \ 0.39631 \\
-C$_2$ & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
-C$_3$ & \ 0.61516 & \ 0.42201 &  -0.15814 \\
-C$_4$ &  -0.61516 &  -0.37396 &  -0.39632 \\
-H$_2$ &  -0.61516 &  -0.68566 &  -1.47237 \\
+H$_1$ &  -0.615 &  -1.421 & \ 1.472 \\
+C$_1$ &  -0.615 &  -1.733 & \ 0.396 \\
+C$_2$ & \ 0.615 & \ 1.733 & \ 0.158 \\
+C$_3$ & \ 0.615 & \ 0.422 &  -0.158 \\
+C$_4$ &  -0.615 &  -0.373 &  -0.396 \\
+H$_2$ &  -0.615 &  -0.685 &  -1.472 \\
 \hline
@@
 pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
-needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
+needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ from Eq.
 \eqref{eq:mu}.
@@
 restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer 
-than 30 meV, which  is both typical laser- pulse energy width and the thermal
+than 30 meV to each other, which  is both typical laser- pulse energy width and the thermal
 room-temperature energy level broadening.\cite{nastosPRB07}
@@
 \includegraphics[width=\tama]{figures/fig3}
-\caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
-  {\it vs.} $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
+\caption Spin velocity injection {$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
+  {\it vs.} photon energy $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
   largest velocity are at the low energy regions of the spectra for the Alt and
@@
 Eq.~\eqref{eq:mu}, 
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ becomes different 
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ starts rising  
 from zero right at the
@@
 induce electrons to move along $y$, parallel to the surface, with their spin
-polarized along $z$, perpendicular to the surface. The corresponding speeds
-are the following: Right at the energy onset, ${\cal
+polarized along $z$, perpendicular to the surface. Right at the energy onset, ${\cal
 V}^{yz}(\omega,\alpha)=668$\,Km/s, remains almost constant for 65 meV, and then
@@
 have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ are higher than
-for the bulk crystals. In particular, the Alt structure demonstrates a ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than that
+for the bulk crystals more than order of magnitude. In particular, the Alt structure demonstrates a ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$  about  12 times larger than that
 of CdSe and GaAs.
+%%%%%%%%%   #### Finished here
 \begin{table}%[b]
@@
 \hline
-Up  & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
+$Up$  & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  660.5 \\
       &      &       & 1.954  & $\mathrm{yz}$ &  266.3 \\
       &      &       & 1.958  & $\mathrm{yz}$ & -241.4 \\
-Alt & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
+$Alt$ & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -711.9 \\
       &      &       & 0.911  & $\mathrm{yz}$ & -330.6 \\
@@
 
+{\color{red}Anatoli: stop here!! I have not gone through the rest!!}
+
 \subsubsection{Up structure}\label{up:fs}
@@
 0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
-structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} and
+structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
 $0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
@@
 Now, we analyze the results for the second energy range of the Up structure
-shown in Fig.~\ref{fig:vab-str-comp}. In the top panel
+shown in the top right panel of Fig.~\ref{fig:vab-str-comp}. In the top panel
 of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
@@
 Here we calculated $\mathcal{V}_{\mathrm{a}}(\omega,\alpha)$ (Eq. 
-\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\hat{\mathbf{a}}$,
+\eqref{eq:vv-mag}) after fixing the electron velocity direction, $\mathrm{a}$,
 to the $x$ or $y$ direction along the surface of the Up and Alt structures.
@@
 \includegraphics[width=\tama]{figures/fig7}
-\caption{
-For the Up structure we show the velocity $\mathcal{V}_{\mathrm{a}}
+\caption{The Up structure: the velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and $\mathrm{a}=y$.}
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
+shown. }
 \label{fig:up-vab-comp-rtp-1}
@@
 \includegraphics[width=\tama]{figures/fig8}
-\caption{For 
-the Up structure we show the spin velocity $\mathcal{V}_{\mathrm{a}}
+\caption{The Up structure: the spin velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$. 
-}
+$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ is
+shown. }
 \label{fig:up-vx-vy-w2}
@@
 \includegraphics[width=\tama]{figures/fig9}
-\caption{For the Alt structure we show  the velocity $\mathcal{V}_{\mathrm{a}}
+\caption{The Alt structure: the velocity $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$.
-}
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
+shown. }
 \label{fig:alt-vx-vy-w1}
@@
 \includegraphics[width=\tama]{figures/fig10}
-\caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
+\caption{The Alt structure: $\mathcal{V}_{\mathrm{a}}
 (\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
@@
 $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
-$\mathrm{a}=y$.
-}
+$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$ are
+shown.}
 \label{fig:alt-vx-vy-w2}
@@
 Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum $\mathcal{V}_{\mathrm{x}}
-(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV,
+(\omega,\alpha) = 301.7$\,Km/s is at $\hbar\omega=0.720$\,eV ,
 $\theta_{\mathrm{x}} (\omega,\alpha) = 44.5^{\circ}$ and
-$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$, and
+$\varphi_{\mathrm{x}}(\omega,\alpha) = 51.2^{\circ}$; and
 $\mathcal{V}_{\mathrm{y}} (\omega,\alpha) = 905.6$\,Km/s at
@@
 velocity is directed along $x$, while it is directed downward the second
-quadrant when the spin velocity is directed along $y$. 
-Finally, in
-Fig. \ref{fig:alt-vx-vy-w2}, the absolute maximum is at $\hbar\omega=0.911$\,eV
+quadrant when the spin velocity is directed along $y$. Finally, in
+Fig. \ref{fig:alt-vx-vy-w1}, the absolute maximum is at $\hbar\omega=0.911$\,eV
 at $\mathcal{V}_{\mathrm{x}} (\omega,\alpha) = 276.3$\,Km/s,
@@
 in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
-of our knowledge, this effect  has not been previously reported in this  2D
+of our knowledge, this effect  has been previously reported in this  2D
 partially hydrogenated structures. We have shown that the  SVI demonstrates an
@@
 \section{Acknowledgment}
+
 This work has been supported by \emph{Consejo Nacional de Ciencia y
@@
 R.Z.P. thanks CONACyT for scholarship support.
-
 \bibliography{article.bib}

### 2017-08-20 mu/article/article.tex
Sending changes to BMS

@@
 graphene structures. The first structure, hydrogenated at only one side,
-labeled Up, also known as graphone, and the second, one labelled Alt, is
+labeled Up, also known as graphone, and the second, labelled Alt, is
 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
-structures. We analyze two possibilities: the first one is by fixing the spin
+structures. We analyze two possibilities: the first, the spin is fixed
 along a chosen direction, and the resulting SVI is calculated.
-Secondly, we choose the SVI direction along
+In the second, we choose the SVI direction along
 the surface plane, and calculate the resulting
@@
 and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
-the Alt. These speed values are larger than those of bulk semiconductors,
+the Alt system. These speed values are  of order of magnitude larger than those of bulk semiconductors,
 such as CdSe and GaAs, thus making the hydrogenated graphene structures
@@
 conductivity\cite{heerscheNat07} and strength \cite{geimNM07, reinaNL08,
-novoselov2S07, balandinNL08}, being a perfect platform  for two-dimension (2D)
-electronic systems; however, most electronic applications are disabled by the
+novoselov2S07, balandinNL08}, being a perfect platform  for two-dimensional (2D)
+electronic systems; however, numerous important electronic applications are disabled by the
 absence of a semiconducting gap. Recent studies demonstrate that a narrow band
@@
 induced. In this article, 
-we address theoretically the SVI 
+we address theoretically the spin-velocity injection
 by one-photon absorption of linearly polarized light, analyzing
@@
     \includegraphics[width=5cm]{figures/fig1}
-    \caption{
-Top (top panel) and side (bottom panel) views of the Up
-      structure along with the 
-      Cartesian $x$, $y$, and $z$ directions. The dark (light) spheres
-      are the C (H) atoms. 
-The primitive hexagonal unit cell is also shown.
-{\color{red}Anatoli: we are confused about the primitive hexagonal
-  unit cell shown. For instance, according to us, if we take C$_2$ and
-apply the red arrow, it will end up in the site of C$_4$, but these C
-atoms according to Table \ref{tab:up-unitcell} are not equivalent, or are they?}} 
+    \caption{(color online). Top (top panel) and side (bottom panel) views of
+the Up structure along with the Cartesian $x$, $y$, and $z$ directions. The
+dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is
+also shown.}
     \label{fig:up-struc}
@@
     \includegraphics[width=5cm]{figures/fig2}
-    \caption{
-Top (top panel) and side (bottom panel) views of the Alt
-      structure along with the 
-      Cartesian $x$, $y$, and$ z$ directions. The dark (light) spheres
-      are the C (H) atoms. 
-The primitive hexagonal unit cell is also shown.
-}
+    \caption{(color online). Top (top panel) and side (bottom panel) views of
+the Alt structure along with the Cartesian $x$, $y$, and$ z$ directions. The
+dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell
+is also shown. }
     \label{fig:alt-struc}
@@
 
-The operator that describes the electronic SVI is written as
+To calculate the velocity of the spin injection
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ along the direction $\hat{\mathbf{a}}$, at
+which the spin moves in a
+polarized state along direction $\hat{\mathbf{b}}$,
+we start with the operator that describes the electronic SVI, written as
 \begin{align}\label{z.1}
@@
 conduction bands inherent to the noncentrosymmetric semiconductors considered
-in this work.
-To include the coherence, we follow Ref.~\onlinecite{nastosPRB07} and
-use a multiple
-scale approach that solves the equation of motion for the single
-particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
+in this work. To include the coherence, we follow Ref.~\onlinecite{nastosPRB07}
+and use a multiple scale approach that solves the equation of motion for the
+single particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
+{\color{red} just for comments to think about, not to introduce the suggestions
+right away: above we have $\rho_{mn}$, below $\rho_{cc’}$ time variable has
+disappeared below. And $\rho_{cc’}$ contains a and b labels, which are not
+Cartesian}
 \begin{align}\label{z.4}
@@
 \end{equation} 
-is the pseudotensor that describes the rate of change of the  PSC process in
+is the pseudotensor that describes the rate of change of the PSC in
 semiconductors. To derive what we presented above we used $
-K^{\mathrm{ab}}_{nm}(-\mathbf{k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$ which
+K^{\mathrm{ab}}_{nm}(-\mathbf{k}) = K^{\mathrm{ab*}}_{nm}({\mathbf k})$, which
 follows from time-reversal invariance. Since $\mu^{\mathrm{abcd}}(\omega)$ is
@@
 from where we see that the spin would be oriented in the $xyz$ system of
-coordinates by the defined  polar angle
+coordinates along the polar angle, defined as
 \begin{equation}
@@
 restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
-than 30 meV, which  is both typical laser- pulse energy width and the thermal
+than 30 meV to each other, which  is both typical laser- pulse energy width and the thermal
 room-temperature energy level broadening.\cite{nastosPRB07}
@@
 \includegraphics[width=\tama]{figures/fig3}
-\caption{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ 
-  {\it vs.} $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The
-  largest velocity are at the low energy regions of the spectra for the Alt and
-  Up structures, becoming different from zero at the energy gap of each
-  structure. In the high energy regions, the values of
+\caption{(color online).  Spin velocity injection
+  $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ {\it vs.} photon energy
+  $\hbar\omega$, for the angles $\alpha$ that maximize the signal. The largest
+  velocity are at the low energy regions of the spectra for the Alt and Up
+  structures, becoming different from zero at the energy gap of each structure.
+  In the high energy regions, the values of
   $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ are also very large compared to
@@
 Eq.~\eqref{eq:mu}, 
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ becomes different 
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ starts rising 
 from zero right at the
@@
 have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ are higher than
-for the bulk crystals. In particular, the Alt structure demonstrates a ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ more than ten times larger than that
+for the bulk crystals more than order of magnitude. In particular, the Alt structure demonstrates a ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ about 12 times larger than that
 of CdSe and GaAs.
+
+{\color{red} Finished here; A.}
 \begin{table}%[b]
@@
 \includegraphics[width=\tama]{figures/fig4}
-\caption{Color online. For the Up structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and
-the bottom panel shows $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right
-scale, red line), and ${\cal
-V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid
-line), {\it vs.} $\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along
-the ridge shown in the 3D plot. }
+\caption{(color online). Color online. For the Up structure, the top panel
+shows ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ {\it vs.} $\hbar\omega$ and
+$\alpha$, and the bottom panel shows
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), and ${\cal
+V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid line), {\it
+vs.} $\alpha$, for $\hbar\omega=0.084$\,eV, i.e. along the ridge shown in the
+3D plot. }
 \label{fig:up-vsz-w1}
@@
 \includegraphics[width=\tama]{figures/fig5}
-\caption{For the Up structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and the
-bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
-red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$
-(left scale, black solid line), {\it vs.} $\alpha$, for $\hbar\omega=1.954$\,eV, i.e.
-along the highest ridge shown in the 3D plot. }
+\caption{(color online). For the Up structure, the top panel shows ${\cal
+V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$,
+and the bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right
+scale, red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ (left scale, black solid line), {\it vs.} $\alpha$, for
+$\hbar\omega=1.954$\,eV, i.e. along the highest ridge shown in the 3D plot. }
 \label{fig:up-vsz-w2}
@@
 \includegraphics[width=\tama]{figures/fig6}
-\caption{Color online. For the Alt structure, the top panel shows ${\cal
-V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$, and the
-bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right scale,
-red line), and ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ (left scale,
-black line), {\it vs.} $\alpha$, for $\hbar\omega=0.720$\,eV, i.e. along the ridge
-shown in the 3D plot.}
+\caption{(color online). Color online. For the Alt structure, the top panel
+shows ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$
+and $\alpha$, and the bottom panel shows $\gamma_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ (right scale, red line), and ${\cal V}_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ (left scale, black line), {\it vs.} $\alpha$, for
+$\hbar\omega=0.720$\,eV, i.e. along the ridge shown in the 3D plot.}
 \label{fig:alt-vsz}
@@
 \includegraphics[width=\tama]{figures/fig7}
-\caption{
-For the Up structure we show the velocity $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and  the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and $\mathrm{a}=y$.}
+\caption{(color online). For the Up structure we show the velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and  the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and
+$\mathrm{a}=y$.}
 \label{fig:up-vab-comp-rtp-1}
@@
 \includegraphics[width=\tama]{figures/fig8}
-\caption{For 
-the Up structure we show the spin velocity $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$. 
-}
+\caption{(color online). For the Up structure we show the spin velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or
+$\mathrm{a}=y$. }
 \label{fig:up-vx-vy-w2}
@@
 \includegraphics[width=\tama]{figures/fig9}
-\caption{For the Alt structure we show  the velocity $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or $\mathrm{a}=y$.
-}
+\caption{(color online). For the Alt structure we show  the velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+line), {\it vs.} $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
+$\mathrm{a}=y$. }
 \label{fig:alt-vx-vy-w1}
@@
 \includegraphics[width=\tama]{figures/fig10}
-\caption{For the Alt structure we show $\mathcal{V}_{\mathrm{a}}
-(\omega,\alpha)$ (left scale, black line), the polar angle $\theta_{\mathrm{a}}
-(\omega,\alpha)$ (right scale, red line), and the azimuthal angle
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
-$\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
-$\mathrm{a}=y$.
-}
+\caption{(color online). For the Alt structure we show
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+line), {\it vs.} $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
+$\mathrm{a}=y$. }
 \label{fig:alt-vx-vy-w2}

### 2017-08-20 mu/article/article-review7_1.tex
Including all necesary to send the article to PRB

--- 2017-08-20 mu/article/article.tex
@@
 25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
-structures. We analyze two possibilities: the first, the spin is fixed
+structures. We analyze two possibilities: in the first, the spin is fixed
 along a chosen direction, and the resulting SVI is calculated.
@@
 Spintronics is an emerging research field of electronics in which the
-manipulation and transport of spin of electrons in a solid state materials  is
+manipulation and transport of the electron spin in a solid state materials  is
 central, adding a new degree of freedom to conventional charge
@@
     \centering
-    \includegraphics[width=5cm]{figures/fig1}
-    \caption{(color online). Top (top panel) and side (bottom panel) views of
+    \includegraphics[width=5cm]{fig1}
+    \caption{(color online) Top (top panel) and side (bottom panel) views of
 the Up structure along with the Cartesian $x$, $y$, and $z$ directions. The
@@
     \centering
-    \includegraphics[width=5cm]{figures/fig2}
-    \caption{(color online). Top (top panel) and side (bottom panel) views of
+    \includegraphics[width=5cm]{fig2}
+    \caption{(color online) Top (top panel) and side (bottom panel) views of
 the Alt structure along with the Cartesian $x$, $y$, and$ z$ directions. The
@@
 
-In this section, we  summarize the theoretical approach, involved in
+In this section, we  summarize the theoretical approach, involved in the
 calculation of the spin velocity injection (SVI) resulting from the pure spin
@@
 conduction bands inherent to the noncentrosymmetric semiconductors considered
-in this work. To include the coherence, we follow Ref.~\onlinecite{nastosPRB07}
+in this work. 
+To include the coherence, we follow Ref.~\onlinecite{nastosPRB07}
 and use a multiple scale approach that solves the equation of motion for the
-single particle density matrix ${\rho}_{mn}({\mathbf k};t)$, leading to
-{\color{red} just for comments to think about, not to introduce the suggestions
-right away: above we have $\rho_{mn}$, below $\rho_{cc’}$ time variable has
-disappeared below. And $\rho_{cc’}$ contains a and b labels, which are not
-Cartesian}
+single particle density matrix 
+$\hat{\rho}({\mathbf k};t)$,  
+leading to
 \begin{align}\label{z.4}
-&\frac{\partial \rho_{cc'}({\mathbf k})}{\partial t} =
+&\frac{\partial \rho_{cc'}({\mathbf k;t})}{\partial t} =
 \frac{e^{2}E^{\mathrm{a}}(\omega)E^{\mathrm{b*}}(\omega)}
@@
 where we assumed that the conduction bands $c$ and $c'$ are quasi-degenerate
-states, and we take $\epsilon\to 0$ at the end of the calculation. The 
-spin-splitting of the valence ($v$) bands is very small, and is neglected throughout
-this work.\cite{nastosPRB07} The matrix elements of any operator ${\cal O}$ are
+states, and we take $\epsilon\to 0$ at the end of the calculation. 
+Since the 
+spin-splitting of the valence ($v$) bands is very small, we neglect it throughout
+this work,\cite{nastosPRB07} and then
+$\rho_{vv'}({\mathbf k};t)= 
+\rho_{cv}({\mathbf k};t) =0$. 
+ The matrix elements of any operator ${\cal O}$ are
 given by ${\cal O}_{nm}({\mathbf k})=\langle n{\mathbf k}|\hat{\cal O}|
@@
 where we used the closure relationship $\sum_{n}|n{\mathbf k}\rangle \langle
-n{\mathbf k}| = 1$, where $n$ goes over all $v$ and $c$ states,
- and the fact that $\rho_{vn}(\mathbf{k})=\rho_{nv}({\mathbf k})=0$ for $n=c,c'$. Therefore, using  Eqs. \eqref{z.4}
+n{\mathbf k}| = 1$, where $n$ goes over all $v$ and $c$ states.
+Therefore, using  Eqs. \eqref{z.4}
 and \eqref{z.5}, the rate of change of $\mathcal{O}$, $\dot{\mathcal{O}} =
@@
 \mu^{\mathrm{abdc}} (\omega)$. We point out that Eq.~\eqref{eq:mu} is
-–identical to Eq. (3) of Bhat et al.,\cite{bhatPRL05} derived using the
+–identical to Eq. (3) of Ref. \onlinecite{bhatPRL05} derived using the
 semiconductor optical Bloch equations. Using the closure relation,
@@
 \sqrt{
-[\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)]^{2}\ +
-[\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)]^{2}\ 
+\left(\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)\right)^{2}\ +
+\left(\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)\right)^{2}\ 
 }, 
@@
 \sqrt { 
-[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
-[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
-[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
+\left(\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)\right)^{2} +
+\left(\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)\right)^{2} +
+\left(\mathcal{V}^{\mathrm{az}}(\omega,\alpha)\right)^{2} 
 },
@@
 from where we see that the spin would be oriented in the $xyz$ system of
-coordinates along the polar angle, defined as
+coordinates along the polar angle, 
 \begin{equation}
@@
 sides. We take the carbon lattice to be along the $xy$ plane for both
-structures, and the carbon-hydrogen bonds are outward the plane, they are
-perpendicular to  $xz$ plane for the Up structure, as depicted in Figs.
-\ref{fig:up-struc}, and off the normal for the Alt structure 
-\ref{fig:alt-struc}. The coordinates for the Up and Alt unit cells of the
+structures, and the carbon-hydrogen bonds are
+perpendicular to  $xz$ plane for the Up structure
+(Fig. \ref{fig:up-struc}),
+ and off the normal for the Alt structure 
+(Fig. \ref{fig:alt-struc}). The coordinates for the Up and Alt unit cells of the
 structures are presented in Tables \ref{tab:up-unitcell} and 
@@
 \centering
-\includegraphics[width=\tama]{figures/fig3}
-\caption{(color online).  Spin velocity injection
+\includegraphics[width=\tama]{fig3}
+\caption{(color online)  Spin velocity injection
   $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ {\it vs.} photon energy
@@
 with its electric field polarized at 35$^\circ$ from the $x$ direction will
-induce electrons to move along $y$, parallel to the surface, with their spin
-polarized along $z$, perpendicular to the surface. Right at the energy onset, ${\cal
+induce electrons to move along $y$ (parallel to the surface), with their spin
+polarized along $z$ (perpendicular to the surface). Right at the energy onset, ${\cal
 V}^{yz}(\omega,\alpha)=668$\,Km/s, remains almost constant for 65 meV, and then
@@
 V}^{\mathrm{a}\mathrm{b}}(\omega,\alpha)$ for the 2D structures considered and
-bulk crystals. We stress that, as shown in the figure, for the 2D structures
-have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ are higher than
-for the bulk crystals more than order of magnitude. In particular, the Alt structure demonstrates a ${\cal
-V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ about 12 times larger than that
+bulk crystals. We stress that, as shown in the figure, the 2D structures
+have maxima in ${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$  higher than
+for the bulk crystals by more than order of magnitude. 
+In particular, the Alt structure demonstrates a 
+${\cal V}^{\mathrm{a}\mathrm{b}}(\omega;\alpha)$ 
+about 12 times larger than that
 of CdSe and GaAs.
 
-{\color{red} Finished here; A.}
-\begin{table}%[b]
+\begin{table}
 \begin{tabular}{cccccc}
@@
 \centering
-\includegraphics[width=\tama]{figures/fig4}
-\caption{(color online). Color online. For the Up structure, the top panel
+\includegraphics[width=\tama]{fig4}
+\caption{(color online) For the Up structure, the top panel
 shows ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ {\it vs.} $\hbar\omega$ and
 $\alpha$, and the bottom panel shows
-$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), and ${\cal
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red short-dashed line), and ${\cal
 V}_{\sigma^\mathrm{z}}(\omega,\alpha)$ (left scale, black solid line), {\it
@@
 \centering
-\includegraphics[width=\tama]{figures/fig5}
-\caption{(color online). For the Up structure, the top panel shows ${\cal
+\includegraphics[width=\tama]{fig5}
+\caption{(color online) For the Up structure, the top panel shows ${\cal
 V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$ and $\alpha$,
-and the bottom panel shows $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$ (right
-scale, red line, long dashes), and ${\cal V}_{\sigma^\mathrm{z}}
+and the bottom panel shows $\gamma_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ 
+(right scale, red short-dashed line), and ${\cal V}_{\sigma^\mathrm{z}}
 (\omega,\alpha)$ (left scale, black solid line), {\it vs.} $\alpha$, for
@@
 0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
-structure shown in the left panel of Fig.~\ref{fig:vab-str-comp} and
+structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
 $0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
 of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s at
-$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV,  The variation of
+$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV.  The variation of
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\alpha$,
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
-black line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
+black solid line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
 plot of the top panel. Also, we plot the corresponding velocity angle
-$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line), where it
+$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red
+short-dashed line), where it
 is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
@@
 $\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$,
-with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s (see
-green arrow), and that from Eq. \eqref{eq:gamma-perp},
+with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s 
+(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
 gives $\alpha=154.50^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s (see blue
-arrow). Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s 
+(as indicated by the orange long-dashed 
+arrow). 
+Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
 $\alpha \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
-black line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
+black solid line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
 shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
-angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red line),
+angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red short-dashed  line),
 where in this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$
@@
 $\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s (as indicated
-by green arrow), and that from Eq. \eqref{eq:gamma-perp},
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s 
+(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
 gives $\alpha=77.8^\circ$, with
-$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s (see blue
-arrow). Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
+$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s 
+(as indicated by the orange long-dashed  arrow). 
+Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
 inject electrons, in this case with their spin polarized along $z$, which move
@@
 \centering
-\includegraphics[width=\tama]{figures/fig6}
-\caption{(color online). Color online. For the Alt structure, the top panel
+\includegraphics[width=\tama]{fig6}
+\caption{(color online) For the Alt structure, the top panel
 shows ${\cal V}_{\sigma^\mathrm{z}} (\omega,\alpha)$ {\it vs.} $\hbar\omega$
 and $\alpha$, and the bottom panel shows $\gamma_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ (right scale, red line), and ${\cal V}_{\sigma^\mathrm{z}}
-(\omega,\alpha)$ (left scale, black line), {\it vs.} $\alpha$, for
+(\omega,\alpha)$ (right scale, red short-dashed  line), and ${\cal V}_{\sigma^\mathrm{z}}
+(\omega,\alpha)$ (left scale, black solid line), {\it vs.} $\alpha$, for
 $\hbar\omega=0.720$\,eV, i.e. along the ridge shown in the 3D plot.}
@@
 panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
-$\alpha$ (left scale, black line), at $\hbar\omega= 0.720$\,eV, thus following
+$\alpha$ (left scale, black solid line), at $\hbar\omega= 0.720$\,eV, thus following
 the highest ridge shown in the 3D plot of the top panel. Also, we plot the
 corresponding velocity angle $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$
-(right scale, red line), where now we see that
+(right scale, red short-dashed  line), where now we see that
 $\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
@@
 \alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)
-= 450.05$\,Km/s (see green arrow), and that from Eq. \eqref{eq:gamma-perp},
+= 450.05$\,Km/s (as indicated by the  green dot-dashed arrow), 
+and that from Eq. \eqref{eq:gamma-perp},
 $\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
 gives $\alpha=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
-(\omega,\alpha) = 60.84$\,Km/s (see blue arrow). Thus, as for the Up structure,
+(\omega,\alpha) = 60.84$\,Km/s 
+(as indicated by the orange long-dashed  arrow). Thus, as for the Up structure,
 we could inject electrons with a fixed spin, which moves parallel or
@@
 \eqref{eq:vv-mag}) after fixing the electron velocity direction, $\hat{\mathbf{a}}$,
-to the $x$ or $y$ direction along the surface of the Up and Alt structures.
-From Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, 
+to the $x$ or $y$ direction along the surface of the Up and Alt structures,
+and from Eqns. \eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, 
 we
 determined the corresponding polar angle, $\theta_{\mathrm{a}}
-(\omega,\alpha)$, and azimuthal angle, $\varphi_{\mathrm{a}} (\omega,\alpha)$.
+(\omega,\alpha)$, and azimuthal angle, $\varphi_{\mathrm{a}}
+(\omega,\alpha)$, of the resulting spin orientation.
 
@@
 \centering
-\includegraphics[width=\tama]{figures/fig7}
-\caption{(color online). For the Up structure we show the velocity
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
-angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and  the
-azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+\includegraphics[width=\tama]{fig7}
+\caption{(color online) For the Up structure we show the velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and  the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
 line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and
@@
 the response. In Fig. \ref{fig:up-vab-comp-rtp-1}, we plot
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
-$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed  line), {\it vs.}
 $\hbar\omega$, for $\mathrm{a}=x,y$. We see that for $\hbar\omega=0.084$\,eV,
@@
 \centering
-\includegraphics[width=\tama]{figures/fig8}
-\caption{(color online). For the Up structure we show the spin velocity
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
-angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
-azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+\includegraphics[width=\tama]{fig8}
+\caption{(color online) For the Up structure we show the spin velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
 line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or
@@
 \centering
-\includegraphics[width=\tama]{figures/fig9}
-\caption{(color online). For the Alt structure we show  the velocity
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
-angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
-azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+\includegraphics[width=\tama]{fig9}
+\caption{(color online) For the Alt structure we show  the velocity
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
 line), {\it vs.} $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
@@
 \centering
-\includegraphics[width=\tama]{figures/fig10}
-\caption{(color online). For the Alt structure we show
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line), the polar
-angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and the
-azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue
+\includegraphics[width=\tama]{fig10}
+\caption{(color online) For the Alt structure we show
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
+angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and the
+azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
 line), {\it vs.} $\hbar\omega$, for $\alpha=150^\circ$, and $\mathrm{a}=x$ or
@@
 In Figs. \ref{fig:alt-vx-vy-w1} and \ref{fig:alt-vx-vy-w2}, we plot
-$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black line),
-$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue line), {\it vs.}
+$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line),
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red short-dashed  line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue long-dashed  line), {\it vs.}
 $\hbar\omega$ in two different ranges, and  for $\mathrm{a}=x,y$. In this case,
@@
 higher compared to 3D bulk materials. The spin relaxation time in pure and
-doped graphene is long enough in the order from nanoseconds to milliseconds.
-\cite{wojtaszekPRB13,ertlerPRB09} Therefore, according to our results, due to
-the high spin velocity transport both structures considered are the excellent
+doped graphene goes  from nanoseconds to milliseconds,
+\cite{wojtaszekPRB13,ertlerPRB09} that, according to our results, 
+is long enough in view of the
+high spin velocity transport that we obtain for both
+structures. Therefore, the Up and the Alt graphene structures
+considered here are  excellent
 candidates for the development of spintronics devices that require pure spin

### 2017-08-20 mu/article/prb/article.tex
Including all necesary to send the article to PRB

--- 2017-08-20 mu/article/article-review7_1.tex
@@
 \usepackage{soul}
-%\usepackage[inline]{showlabels}
-% \input{/Users/bms/util/definitions}
-%\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
 \def\tama{10cm}
@@
 current (PSC) induced by  a linearly polarized light that impinges normally on
-the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D
+the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional (2D)
 graphene structures. The first structure, hydrogenated at only one side,
@@
 structures. We analyze two possibilities: in the first, the spin is fixed
-along a chosen direction, and the resulting SVI is calculated.
-In the second, we choose the SVI direction along
+along a chosen direction, and the resulting SVI is calculated;
+in the second, we choose the SVI direction along
 the surface plane, and calculate the resulting
@@
 two possible scenarios of practical interest. 
-The first case is by fixing the spin of the electrons along $z$, i.e. 
+The first case is by fixing the spin of the electrons along $z$, i.e.,
 perpendicular 
@@
 directed along the surface of the
-structures in the $xy$ plane. 
+structures on the $xy$ plane. 
 In the second case we fix the SVI velocity along the
@@
     \caption{(color online) Top (top panel) and side (bottom panel) views of
-the Alt structure along with the Cartesian $x$, $y$, and$ z$ directions. The
+the Alt structure along with the Cartesian $x$, $y$, and $-z$ directions. The
 dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell
@@
 density functional theory in the local density approximation (DFT-LDA), with a
-planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
+planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
+Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
 pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
@@
 restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
-than 30 meV to each other, which  is both typical laser- pulse energy width and the thermal
+than 30 meV to each other, which  is both typical laser pulse energy width and the thermal
 room-temperature energy level broadening.\cite{nastosPRB07}
@@
 0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
-black solid line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale,
+black solid line) {\it vs.} $\alpha$, at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
 plot of the top panel. Also, we plot the corresponding velocity angle
@@
 analyze the highest  maximum in the bottom panel, where we  show
-$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
-black solid line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
+$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale,
+black solid line) {\it vs.} $\alpha$, at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
 shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
-panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
-$\alpha$ (left scale, black solid line), at $\hbar\omega= 0.720$\,eV, thus following
+panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale, black solid line) {\it vs.}
+$\alpha$, at $\hbar\omega= 0.720$\,eV, thus following
 the highest ridge shown in the 3D plot of the top panel. Also, we plot the
@@
 azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
-line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and
+line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or
 $\mathrm{a}=y$.}
@@
 $\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line),
-$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red short-dashed  line), and
-$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue long-dashed  line), {\it vs.}
+$\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed line), and
+$\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed  line), {\it vs.}
 $\hbar\omega$ in two different ranges, and  for $\mathrm{a}=x,y$. In this case,
@@
 \end{document}
-
-%@article{buonocorePE16,
-%  title={Effects of the substrate on graphone magnetism: A density functional
-%  theory study},
-%  author={Buonocore, F. and Conte, A. M. and Lisi, N.},
-%  journal={Phys. E: Low-dim. Sys.},
-%  volume={78},
-%  pages={65--72},
-%  year={2016},
-%  publisher={Elsevier}
-%}
-
-gmitraPRL13

### 2017-08-30 mu/article/article-review7_2-Anatoli.tex
First manuscript sent to PRB

--- 2017-08-20 mu/article/prb/article.tex
@@
 development of PSC based semiconductor devices is the fact that the spin
-relaxation time in conventional semiconducting materials is short to enable the
+relaxation time in conventional semiconducting materials is too short to enable the
 spin transport, thus resulting in a non-observable spin
@@
 proven in Ref. \onlinecite{shkrebtiiPSSC12}.
+
 In this paper, we offer two 50\% hydrogenated graphene
@@
 by one-photon absorption of linearly polarized light, analyzing
-in our structures,
+in our structures
 two possible scenarios of practical interest. 
@@
 (Fig. \ref{fig:alt-struc}). The coordinates for the Up and Alt unit cells of the
-structures are presented in Tables \ref{tab:up-unitcell} and 
+structures are given in Tables \ref{tab:up-unitcell} and 
 \ref{tab:alt-unitcell}, respectively.
@@
 In this subsection, we calculate ${\cal V}_{\sigma^\mathrm{z}}(\omega,\alpha)$,
-Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.
+Eq. \eqref{eq:vs-mag}, for the case with the spin fixed along $z$, i.e.,
 directed perpendicularly to the surface of the Up and Alt structures. Also, we
@@
 in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
-of our knowledge, this effect  has not been previously reported in this  2D
+of our knowledge, this effect  has not been previously reported in these  2D
 partially hydrogenated structures. We have shown that the  SVI demonstrates an
 anisotropic behavior, which is very sensitive to the symmetry of the structures
-of interest. We have found that the Up structure shows the strongest response
+of interest and their band structure. % Do you think that the band structure 
+% peculiarities are important? 
+We have found that the Up structure shows the strongest response
 for the spin directed along $z$, resulting in the velocity
@@
 semiconductor quantum well structures, while they are of order of magnitude
-higher compared to 3D bulk materials. The spin relaxation time in pure and
-doped graphene goes  from nanoseconds to milliseconds,
-\cite{wojtaszekPRB13,ertlerPRB09} that, according to our results, 
-is long enough in view of the
-high spin velocity transport that we obtain for both
-structures. Therefore, the Up and the Alt graphene structures
+higher compared to 3D bulk materials. Considering the fact that the spin relaxation time in pure and
+doped graphene ranges from nanoseconds to milliseconds,
+\cite{wojtaszekPRB13,ertlerPRB09}, and in view of the
+high spin velocity transport that we obtained for the both
+structures, this time is sufficiently long enough to have the SVI effect observed experimentally. Therefore, the Up and the Alt graphene structures
 considered here are  excellent

### 2017-08-30 mu/article/prb-sent1/manuscript.tex
First manuscript sent to PRB

--- 2017-08-30 mu/article/article-review7_2-Anatoli.tex
@@
 %\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
-\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
-%\documentclass[preprint,prb,showpacs]{revtex4}
+%\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
+\documentclass[preprint,prb,showpacs]{revtex4}
 \usepackage{amsmath}    % need for subequations 
@@
 \author{Bernardo S. Mendoza}
+\email[E-mail: ]{bms@cio.mx}
 \affiliation{Centro de Investigaciones en \'Optica, Le\'on,
@@
 
+\pacs{75.76+j,85.75.-d,78.67.Wj,78.90.+t}
+
 \maketitle
@@
 development of PSC based semiconductor devices is the fact that the spin
-relaxation time in conventional semiconducting materials is too short to enable the
-spin transport, thus resulting in a non-observable spin
+relaxation time in conventional semiconducting materials cloud be too short to enable the
+spin transport, and may result in a non-observable spin
 current.\cite{murakamiSc03} For PSC there is no net motion of charge; spin-up
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s 
-(as indicated by the orange long-dashed 
+(as indicated by the blue long-dashed 
 arrow). 
@@
 $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s 
-(as indicated by the orange long-dashed  arrow). 
+(as indicated by the blue long-dashed  arrow). 
 Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
@@
 (\omega,\alpha) = 60.84$\,Km/s 
-(as indicated by the orange long-dashed  arrow). Thus, as for the Up structure,
+(as indicated by the blue long-dashed  arrow). Thus, as for the Up structure,
 we could inject electrons with a fixed spin, which moves parallel or
 perpendicular to the incident electric field.
-% Again, for the cases in which the spin polarization is parallel to the
-% surface the maximum values are
-% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 297.8$ Km/s and
-% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$ Km/s,
-% corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
-% $\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
-% $\alpha=150^{\circ}$, where the plots are not presented.
 
@@
 considered: we made the calculations for the cases when the spin is polarized
-in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
+in $z$ direction or when the velocity is directed along $x$ or $y$. 
+To the best  
 of our knowledge, this effect  has not been previously reported in these  2D  
-partially hydrogenated structures. We have shown that the  SVI demonstrates an
+partially hydrogenated structures.  
+We have shown that the  SVI demonstrates an
 anisotropic behavior, which is very sensitive to the symmetry of the structures
-of interest and their band structure. % Do you think that the band structure 
-% peculiarities are important? 
+of interest.
 We have found that the Up structure shows the strongest response
@@
 semiconductor quantum well structures, while they are of order of magnitude
-higher compared to 3D bulk materials. Considering the fact that the spin relaxation time in pure and
+higher compared to 3D bulk materials. 
+Considering the fact that the spin relaxation time in pure and
 doped graphene ranges from nanoseconds to milliseconds,
 \cite{wojtaszekPRB13,ertlerPRB09}, and in view of the
-high spin velocity transport that we obtained for the both
-structures, this time is sufficiently long enough to have the SVI effect observed experimentally. Therefore, the Up and the Alt graphene structures
+high spin velocity transport that we obtained for  both
+structures, this time is sufficiently long enough to have the SVI
+effect observed experimentally. 
+Therefore, the Up and the Alt graphene structures
 considered here are  excellent
@@
 R.Z.P. thanks CONACyT for scholarship support.
+A.I.S thanks to Centro de Investigaciones en Optica (CIO) for the               
+hospitality during his sabbatical research leave.
 
-\bibliography{article.bib}
+\bibliography{manuscript.bib}
 
 \end{document}
+
+cover letter
+
+We present a theoretical study of spin-velocity injection (SVI) of a pure spin 
+current (PSC) induced by  a linearly polarized light that impinges normally on 
+the surface of  two 50% hydrogenated noncentrosymmetric two-dimensional (2D) 
+graphene structures. The first structure, hydrogenated at only one side, 
+labeled Up, also known as graphone, and the second, labelled Alt, is 
+25% hydrogenated at both sides. The hydrogenation opens an energy gap in both 
+structures. We analyze two possibilities: in the first, the spin is fixed 
+along a chosen direction, and the resulting SVI is calculated; 
+in the second, we choose the SVI direction along 
+the surface plane, and calculate the resulting 
+spin orientation. 
+The speed values that we obtain  are of order of magnitude larger than those of bulk semiconductors, 
+such as CdSe and GaAs, thus making the hydrogenated graphene structures 
+excellent candidates for spintronics applications. 
+To the best  
+of our knowledge, this effect  has not been previously reported in these  2D  
+partially hydrogenated structures.  
+We have published several related works in Physical Review B with very
+good visibility, for which we know that the present manuscript is
+suitable for PRB as well.

### 2017-08-30 mu/article/prb/article.tex
First manuscript sent to PRB

@@
 development of PSC based semiconductor devices is the fact that the spin
-relaxation time in conventional semiconducting materials is short to enable the
+relaxation time in semiconducting materials can be too short to enable the
 spin transport, thus resulting in a non-observable spin
@@
 in $z$ direction or when the velocity is directed along $x$ or $y$. To the best
-of our knowledge, this effect  has not been previously reported in this  2D
+of our knowledge, this effect has not been previously reported in these 2D
 partially hydrogenated structures. We have shown that the  SVI demonstrates an
@@
 semiconductor quantum well structures, while they are of order of magnitude
-higher compared to 3D bulk materials. The spin relaxation time in pure and
-doped graphene goes  from nanoseconds to milliseconds,
-\cite{wojtaszekPRB13,ertlerPRB09} that, according to our results, 
-is long enough in view of the
-high spin velocity transport that we obtain for both
-structures. Therefore, the Up and the Alt graphene structures
-considered here are  excellent
-candidates for the development of spintronics devices that require pure spin
-current (PSC).
+higher compared to 3D bulk materials. Considering the fact that the spin
+relaxation time in pure and doped graphene ranges from nanoseconds to
+milliseconds, \cite{wojtaszekPRB13,ertlerPRB09} and, in view of the high spin
+velocity transport that we obtained for the both structures, this time is
+sufficiently long enough to have the SVI effect observed experimentally.
+Therefore, the Up and the Alt graphene structures considered here are
+excellent candidates for the development of spintronics devices that require
+pure spin current (PSC).
 
@@
 Tecnolog\'ia} (CONACyT), M\'exico, Grant No. 153930.
-R.Z.P. thanks CONACyT for scholarship support.
+A.I.S thanks to Centro de Investigaciones en Optica (CIO) for the hospitality 
+during his sabbatical research leave.
+R.Z.P. thanks CONACyT an CIO for scholarship support.
 

### 2017-10-21 mu/article/prb/article.tex
Making correcttions in figures of structures.

@@
 graphene structures. The first structure, hydrogenated at only one side,
-labeled Up, also known as graphone, and the second, labelled Alt, is
-25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
-structures. We analyze two possibilities: in the first, the spin is fixed
-along a chosen direction, and the resulting SVI is calculated;
-in the second, we choose the SVI direction along
-the surface plane, and calculate the resulting
-spin orientation. This is done by changing the energy
-$\hbar\omega$ and polarization angle $\alpha$  of the incoming  light. The
-results are calculated within a full electronic band structure scheme using the
-Density Functional Theory (DFT) in the Local Density Approximation (LDA). The
-maxima of the spin-velocities are reached when $\hbar\omega=0.084$\,eV and
-$\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
-$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and
-645\,Km/s for the Up and the Alt structures, respectively, when the spin points
-perpendicularly to the surface. Also, the response is maximized by
-fixing the spin-velocity direction 
-along a high symmetry  axis, obtaining a speed of 688Km/s
-with the spin pointing at $13^\circ$ from the surface normal, for the Up, 
-and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
-the Alt system. These speed values are of order of magnitude larger than those of bulk semiconductors,
-such as CdSe and GaAs, thus making the hydrogenated graphene structures
-excellent candidates for spintronics applications. 
+labeled Up, also known as graphone, and the second, labelled Alt, is 25\%
+hydrogenated at both sides. The hydrogenation opens an energy gap in both
+structures. We analyze two possibilities: in the first, the spin is fixed along
+a chosen direction, and the resulting SVI is calculated; in the second, we
+choose the SVI direction along the surface plane, and calculate the resulting
+spin orientation. This is done by changing the energy $\hbar\omega$ and
+polarization angle $\alpha$  of the incoming  light. The results are calculated
+within a full electronic band structure scheme using the Density Functional
+Theory (DFT) in the Local Density Approximation (LDA). The maxima of the spin-
+velocities are reached when $\hbar\omega=0.084$\,eV and $\alpha=35^\circ$ for
+the Up structure, and $\hbar\omega=0.720$\,eV and $\alpha=150^\circ$ for the
+Alt geometry. We find a speed of 668\,Km/s and 645\,Km/s for the Up and the Alt
+structures, respectively, when the spin points perpendicularly to the surface.
+Also, the response is maximized by fixing the spin-velocity direction along a
+high symmetry  axis, obtaining a speed of 688Km/s with the spin pointing at
+$13^\circ$ from the surface normal, for the Up, and 906 Km/s and the spin
+pointing at $60^\circ$ from the surface normal, for the Alt system. These speed
+values are of order of magnitude larger than those of bulk semiconductors, such
+as CdSe and GaAs, thus making the hydrogenated graphene structures excellent
+candidates for spintronics applications.
 \end{abstract}
@@
 development of PSC based semiconductor devices is the fact that the spin
-relaxation time in semiconducting materials can be too short to enable the
+relaxation time in semPiconducting materials can be too short to enable the
 spin transport, thus resulting in a non-observable spin
@@
 
-The spin velocity injection (SVI) is an optical effect that quantifies the velocity at which
-a PSC moves along the direction $\hat{\mathbf{a}}$, 
-with the spin of the electron polarized along the direction $\hat{\mathbf{b}}$.
-One photon absorption of polarized
-light produces an even distribution of electrons in $\mathbf{k}$
-space, regardless of the symmetry of the material, resulting in a null
-electrical current.\cite{bhatPRL05} 
-Then, the electrons excited to the
+The spin velocity injection (SVI) is an optical effect that quantifies the
+velocity at which a PSC moves along the direction $\hat{\mathbf{a}}$, with the
+spin of the electron polarized along the direction $\hat{\mathbf{b}}$. One
+photon absorption of polarized light produces an even distribution of electrons
+in $\mathbf{k}$ space, regardless of the symmetry of the material, resulting in
+a null electrical current.\cite{bhatPRL05} Then, the electrons excited to the
 conduction bands at opposite $\mathbf{k}$ points will result in opposite spin
 polarizations producing no net spin injection in centrosymmetric
-materials.\cite{bhatPRL05} 
-If the crystalline structure of the material
-is noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
+materials.\cite{bhatPRL05} If the crystalline structure of the material is
+noncentrosymmetric, the spin polarization injected at a given $\mathbf{k}$
 point not necessarily vanishes.\cite{alvaradoPRL85,schmiedeskampPRL88}
@@
 
-To calculate the velocity of the spin injection
-${\cal V}^{\mathrm{a}\mathrm{b}}(\omega)$ along the direction $\hat{\mathbf{a}}$, at
-which the spin moves in a
-polarized state along direction $\hat{\mathbf{b}}$,
+To calculate the velocity of the spin injection ${\cal
+V}^{\mathrm{a}\mathrm{b}}(\omega)$ along the direction $\hat{\mathbf{a}}$, at
+which the spin moves in a polarized state along direction $\hat{\mathbf{b}}$,
 we start with the operator that describes the electronic SVI, written as
@@
 where we assumed that the conduction bands $c$ and $c'$ are quasi-degenerate
-states, and we take $\epsilon\to 0$ at the end of the calculation. 
-Since the 
-spin-splitting of the valence ($v$) bands is very small, we neglect it throughout
-this work,\cite{nastosPRB07} and then
-$\rho_{vv'}({\mathbf k};t)= 
+states, and we take $\epsilon\to 0$ at the end of the calculation. Since the
+spin-splitting of the valence ($v$) bands is very small, we neglect it
+throughout this work,\cite{nastosPRB07} and then $\rho_{vv'}({\mathbf k};t)=
 \rho_{cv}({\mathbf k};t) =0$. 
@@
 \omega_{n}({\mathbf k})|n{\mathbf k}\rangle$ with $\hbar \omega_{n}({\mathbf
-k})$ being the energy of the electronic band $n$ and $m$ at point ${\mathbf k}$ in the
-irreducible Brillouin zone (IBZ),  $|n{\mathbf k}\rangle$ is the Bloch state,
-and $\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf k})-\omega_{m}({\mathbf k})$.
-Using $\mathcal{O} = \mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$ for the
-expectation value of an observable $\mathcal{O}$, where $\mathrm{Tr}$ denotes
-the trace, we obtain
+k})$ being the energy of the electronic band $n$ and $m$ at point ${\mathbf k}$
+in the irreducible Brillouin zone (IBZ),  $|n{\mathbf k}\rangle$ is the Bloch
+state, and $\omega_{nm}({\mathbf k})=\omega_{n}({\mathbf
+k})-\omega_{m}({\mathbf k})$. Using $\mathcal{O} =
+\mathrm{Tr}(\hat{\rho}\hat{\mathcal{O}})$ for the expectation value of an
+observable $\mathcal{O}$, where $\mathrm{Tr}$ denotes the trace, we obtain
 \begin{align}\label{z.5}
